### 2019-05-28 slides/ExpSlides.tex
first push

\documentclass{beamer}
\usepackage{default}
\usepackage{amsmath}
\usepackage{graphicx}

%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\title{Understanding Expectation Formation from Probabilistic Surveys}

% A subtitle is optional and this may be deleted

\author{Tao Wang \\ Johns Hopkins University}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\date{April, 2019}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
	\begin{frame}<beamer>{Outline}
	\tableofcontents[currentsection]
\end{frame}
}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}
\begin{frame}{Outline}
	\tableofcontents
	% You might wish to add the option [pausesections]
\end{frame}

\section{Motivation}

%\begin{frame}{Why studying expectation}
%\begin{itemize}
%	\item Both theories and empirical evidence on deviation from full-information rational expectation(FIRE)
%	\item ``Sluggish'' macro: i.e. ``excessive smoothing'' in consumption, sticky price adjustment by firms and UIP puzzle, forward guidance puzzle, etc
%	\item Heterogeneity in expectation matters for asset pricing
%	\item From \textcolor{blue}{revealed preference(belief)} to \textcolor{blue}{elicited beliefs}  	
%\end{itemize}
%\end{frame}

\begin{frame}{What I am doing}
\begin{itemize}
	\item Use \textcolor{blue}{density information} to 
	\begin{itemize}
		\item test expectation rigidity models 
		\item ... and identify differences in various theories 
	\end{itemize}
	\item Both \textcolor{blue}{individual} and population moments 
	\item \textcolor{blue}{Households} and professional forecasters 
	\begin{itemize}
		\item drivers of difference in rigidity across two types of agents
	\end{itemize}
	%\item Focus on aggregate variable inflation first, and then try \textcolor{blue}{individual variables} 
\end{itemize}
\end{frame}

\begin{frame}{Why density is important}
\begin{itemize}
\item \textbf{Identification:} different theories have testable predictions on the second moments   
	\begin{itemize}
		\item Scenario 1. Two people think the chance of raining is 50\%. 
		\item Scenario 2. One person thinks 100\% and the other 0\%. 
	\end{itemize}
\item \textbf{Modeling Implications:}  both mean and variance affect economic decisions
\begin{itemize}
	\item precautionary saving with income risks
	\item portfolio choice with risky asset
\end{itemize} 
\end{itemize}
\end{frame}

%
%\begin{frame}{Objections}
%\begin{itemize}
%	\item ``Subjective surveys are not trustworthy'' 
%	\begin{itemize}
%		\item Actually carefully designed. \cite{armantier2017overview}
%	\end{itemize}
%	\item ``People are bad at answering surveys, and worse on probabilities''  
%	\begin{itemize}
%		\item Not that bad. \cite{manski2004measuring}, \cite{delavande2014probabilistic}
%		\item Better than not.
%	\end{itemize}
%	\item ``A single parameter is enough for matching macro dynamics''
%	\begin{itemize}
%		\item No, heterogeneity in expectation could interact with other characteristics. 
%	\end{itemize}
%\end{itemize}
%\end{frame}

\begin{frame}{Literature}
\begin{itemize}
	\item \textbf{Theory}
	\begin{itemize}
		\item Sticky expectation \cite{carroll2003macroeconomic}, \cite{reis2006inattentive}
		\item Rational inattention \cite{sims2003implications},  \cite{gabaix2014sparsity}
		\item Noisy information \cite{lucas1972expectations}, \cite{woodford2001imperfect}
	\item Learning \cite{evans2012learning}
	\item Strategic interaction \cite{morris2002social}, \cite{hellwig2009knowing}
	\item Diagostic expectation  \cite{bordalo2018diagnostic}
	\item Model uncertainty \cite{hansen2001robust}, \cite{hansen2008robustness}
	\end{itemize}
\item \textbf{Empirics}
\begin{itemize}
	\item \textbf{Heterogeneity in Expectation:} \cite{mankiw2003disagreement}
	\item \textbf{Testing Theories:}  \textcolor{blue}{\cite{coibion2012can}, \cite{fuhrer2018intrinsic}}
\end{itemize}
\end{itemize}
\end{frame}

\section{Theories}

\begin{frame}{Unified Framework}

h-period ahead density forecast by agent $i$ at time $t$ based on information set $I_{i,t}$

\begin{eqnarray*}
	\widehat f_{i,t}(y_{t+h}|I_{i,t})
\end{eqnarray*}

\begin{itemize}
	\item Theories differ in $I_{i,t}$
	\item May also differ on information processing, i.e. $I_{i,t} \rightarrow \widehat f_{i,t}$
\end{itemize}

\end{frame}

\begin{frame}{Definition and notation}
\begin{itemize}
	\item \textcolor{red}{Individual}
	\begin{itemize}
		\item  mean forecast $\quad E_{i,t}(y_{t+h})$
		\item forecast error $\quad FE_{i,t+h|t} = y_{t+h}- E_{i,t}(y_{t+h})$
		\item \textcolor{blue}{uncertainty} $\quad Var_{i,t}(y_{t+h})$
	\end{itemize}
	\item \textcolor{red}{Population}
	\begin{itemize}
		\item average forecast  $\quad \bar E_{t}(y_{t+h})$
		\item average forecast error $\quad \overline {FE}_{t}= y_{t+h}-\bar E_{t}(y_{t+h})$
		\item \textcolor{blue}{cross-section disagreements}  $\quad Var_t(E_{i,t}(y_{t+h}))$
		\item \textcolor{blue}{average uncertainty}  $\quad \overline{Var}_t(y_{t+h})$
	\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Assumption about true process}

$$y_{t+1} = \rho y_t + \omega_t  $$ 
$$\omega_t \sim N(0,\sigma^2_{\omega})$$

\begin{itemize}
	\item $0 < \rho \leq 1$
	\item if $\rho =0$, no way to forecast at all
	\item $\omega_t$ is i.i.d 
\end{itemize}

\end{frame}

\subsection{Sticky Expectation}

\begin{frame}{Sticky Expectation: assumptions}
\begin{itemize}
	\item At time $t$, agent $i$ learns about $y_t$ at a fixed Poisson rate $\lambda$ 
	\item A non-updater since $t-\tau$  
	$$E_{i,t}(y_{t+h}|y_{t-\tau}) =\rho^{h+\tau} y_{t-\tau} $$
	\item An updater is a special cae  $\tau=0$ 
\end{itemize}
\end{frame}

\begin{frame}{Impulse responses to shocks: individual moments}

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$ 
\begin{figure}
	\includegraphics[scale=0.25]{figures/ir_indse} 
\end{figure}
\end{frame}

\begin{frame}{Impulse responses to shocks: population moments}

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$

\begin{figure}
	\includegraphics[scale=0.25]{figures/ir_popse} 
\end{figure}

\end{frame}

\subsection{Other theories}

\begin{frame}{Noisy Information: assumptions}
\begin{itemize}
	\item Individual only observes noisy signals 
	\begin{eqnarray*}
		\begin{aligned}
			& s_{i,t}=[s^{pb}_t, s^{pr}_{i,t}]' \in I_{i,t} \\
			&\text{public signal:} \quad s^{pb}_t = y_t + \epsilon_t, \quad \epsilon_t \sim N(0,\sigma^2_\epsilon)\\ 
			& \text{private signal:} \quad s^{pr}_{i,t} = y_t + \xi_{i,t} \quad \xi_{i,t} \sim N(0,\sigma^2_\xi)
		\end{aligned}
	\end{eqnarray*}

	\item Kalman filtering (simply normal updating if $\rho$=0)
\end{itemize}
\end{frame}

\begin{frame}{Impulse responses to shocks: individual moments}

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figures/ir_indseni} 
\end{figure}

\end{frame}

\begin{frame}{Impulse responses to shocks: population moments}

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figures/ir_popseni} 
\end{figure}

\end{frame}

%\begin{frame}{Noisy Information: predictions}
%\begin{itemize}
%	\item \textbf{Similar to Sticky Expectation}
%	\begin{enumerate}
%\item \textbf{Macro rigidity}: population forecasts partially respond to shocks
% \item \textbf{Non-response of variance}: both individual and population variance \textcolor{blue}{does not respond to} shocks.   
% \end{enumerate}
%\item \textbf{Different from Sticky Expectation}

%	\begin{enumerate}
%	\item \textbf{Micro rigidity}: both individual and population forecast \textcolor{blue}{partially} respond to shocks 
%	\item \textbf{Horizon-sensitive rigidity}: rigidity decreases with horizon
%	\item \textbf{Increasing disagreements:} population disagreements \textcolor{blue}{increase} over time as approaching $t+h$
%	\item \textbf{Shock-specific responses:} different impacts of fundamental shocks, or simply news shocks 
%\end{enumerate}
%\end{itemize}

%\end{frame}

\begin{frame}{A detailed look into noisy information}

\begin{figure}
	\includegraphics[height=8cm,width=8cm]{figures/ni_illustration} 
\end{figure}

\end{frame}

\begin{frame}{Implied rigidity of different models}

\begin{figure}
	\includegraphics[height=5cm,width=8cm]{figures/rigidity} 
\end{figure}

\end{frame}

\begin{frame}{Other theories on to-do-list}
\begin{itemize}
	\item \textbf{Rational Inattention:} attentiveness endogenously respond to variances
	\item \textbf{Learning}: the structural parameter $\rho$ is not known, thus the agent learns about it as if an econometrician does
\end{itemize}
\end{frame}

\begin{frame}{Identification strategies 1: testing rigidity models}

\begin{itemize}
	\item\cite{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} respond to shocks and serially correlated. 
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} does not depend on shocks; and serially correlated. 
	\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Identification strategies 2: differentiating theories}
\begin{itemize}
	\item\cite{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} do not depend on past realizations according to baseline SE and NI; but do so according to heterogeneous priors or precision models. 
		\item Implied rigidity does not differ across shocks according to SE but differs according to NI. 
		\item \textcolor{blue}{Disagreements} rise after shocks according to baseline SE, strategic interactions and heterogeneous priors but invariant according to baseline NI.
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} do not depend on shocks per se according to baseline SE and NI, instead on degree of information rigidity.
	\end{itemize}
\end{itemize}

\end{frame}

\section{Data and Methodology}

\begin{frame}{Data}
\begin{table}[]
\resizebox{\textwidth}{!}{	\begin{tabular}{lll}

		\hline 
		& SCE & SPF        \\
		\hline 
		Time period                                    & 2013-present                            & 2007-present             \\
		Frequency                                      & Monthly                                 & Quarterly                \\
		Sample Size                                    & 1,300                                   & 30-50                    \\
		Aggregate Var in Density                       & \textcolor{blue}{1-yr and 3-yr inflation}          & \textcolor{blue}{1-yr and 3-yr CPI and PCE}         \\
		Pannel Structure                               & stay up to 12 months                    & average stay for 5 years \\
		Demographic Info                        & Education, Income, Age        & Industry    \\
		\hline 
	\end{tabular}}
\end{table}

\end{frame}

\section{Stylized Facts}

\begin{frame}{Population moments: average}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_med.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average forecast errors}
\begin{figure}
	\includegraphics[scale=0.3]{figures/fe_fe.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average uncertainty}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_var.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_diag.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/disg_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_diag.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: forecast and realization}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_true.png} 
\end{figure}
\end{frame}

\begin{frame}{Empirical execution}

\begin{itemize}
	\item \textbf{Measurement Errors}:  winsorization is still necessary
	\item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
    \item \textbf{Identification of Shocks}: following \cite{coibion2012can}
\end{itemize}

\end{frame}

\bibliographystyle{apalike}
\bibliography{ExpSlides}

\section{Appendix}

\begin{frame}{Sticky Expectation: individual}

For a non-updater since $t-\tau$ ($\tau=0$ for updater),
\begin{itemize}
\item \textbf{Mean} $$E_{i,t}(y_{t+h}|y_{t-\tau}) = \rho^{h+\tau} y_{t-\tau}$$  
\item \textbf{Forecast Error} $$FE_{i,t+h|t} = \underbrace{\sum^{h+\tau}_{s=0} \rho^s \omega_{t+h-s}}_{\substack{\text{weighted sum of} \\ \text{future realized shocks}} }$$
\item \textcolor{blue}{\textbf{Variance}} $$Var_{i,t}(y_{t+h}|y_{t-\tau}) = \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}$$	
\end{itemize}

\end{frame}

\begin{frame}{Sticky Expectation: individual}

$$\text{updater: } \quad \Delta Var_{i,t}(y_{t+h}|y_t)= \sum^{\tau}_{s=0} \rho^{2s}\sigma^2_{\omega}$$
$$\text{non-updater: }  \Delta Var_{i,t|t-\tau-1}(y_{t+h}|y_{t-\tau-1})  = \sigma^2_{\omega}$$

\begin{enumerate}
\item Change in expectation(and variance) depends on if update or not 
\item Cannot observe systematically sluggish response to shocks at individual level 
\end{enumerate}

\end{frame}

\begin{frame}{Sticky Expectation: population}
\begin{itemize}
	\item \textbf{Average forecast} 
	\begin{eqnarray*}
		\begin{aligned}
			\bar E_t(y_{t+h}) & = \lambda \underbrace{E_t(y_{t+h})}_{\text{rational expectation at t}} + (1-\lambda) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{average expectation at } t-1} \\
			& = \lambda E_t(y_{t+h}) + (1-\lambda) (\lambda E_{t-1}(y_{t+h})+ ...) \\
			& =\underbrace{ \lambda \sum^{\infty}_{s=0} (1-\lambda)^s E_{t-s}(y_{t+h})}_{\text{weighted sum of past rational expectations}}
		\end{aligned}
	\end{eqnarray*}
	\item \textbf{Change in average forecast}
	$$\Delta \bar E_t(y_{t+h})=\underbrace{(1-\lambda)}_{\text{stickiness}} \Delta \bar E_{t-1}(y_{t+h}) + \lambda \rho^h \omega_t$$ 
\end{itemize}
\end{frame}

\begin{frame}{Sticky Expectation: population}
\begin{itemize}
\item \textbf{Disagreements}
\begin{eqnarray*}
	\begin{aligned}
		Var_t(y_{t+h} ) & = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^{\tau} (E_{t|t-\tau}(y_{t+h}) - \bar E_t(y_{t+h}))^2  
	\end{aligned}
\end{eqnarray*}
\item \textbf{Change in disagreements}
$$\Delta Var_t (y_{t+h}) = \rho^{2h} (1-\lambda)\lambda \underbrace{\omega^2_t}_{\text{shock at time t}}$$
\end{itemize}

\begin{enumerate}
\item Disagreements rise after the shock and then gradually decline 
\item Response of disagreements depends on the size of the shock
\end{enumerate}
\end{frame}

\begin{frame}{Sticky Expectation: population}
\begin{itemize}
\item \textcolor{blue}{\textbf{Average variance}}
\begin{eqnarray*}
\begin{aligned}
	\overline {Var}_{t}(y_{t+h}) &  =  (1-\lambda)\underbrace{\overline {Var}_{t-1}(y_{t+h})}_{\text{average variance at t-1}} + \underbrace{\lambda Var_{t}(y_{t+h})}_{\text{variance of updater at t} }
\end{aligned}
\end{eqnarray*}
\item \textbf{Change in average variance}
$$\Delta \overline {Var}_{t}(y_{t+h}) = \underbrace{(1-\lambda)\Delta \overline {Var}_{t-1}(y_{t+h}) - \lambda \rho^{2h}\sigma^2_{\omega}}_{\text{does not depend on shock at t}}$$
\end{itemize}

\begin{enumerate}
\item Average variance does not respond to shocks
\item Average variance has serial correlation with the same rigidity parameter $1-\lambda$ 
\end{enumerate}

\end{frame}

\begin{frame}{Noisy Information: individuals}
\begin{itemize}
	\item \textbf{Mean}
	\begin{eqnarray*}
		\begin{aligned}
			E_{i,t}(y_{t+h}) & = \rho^{h}E_{i,t|t}(y_{t}) \\
			E_{i,t|t}(y_{t}) 
			& =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
			& = (1-PH) E_{i,t|t-1}(y_{t}) + Ps_{i,t} \\
			\text{where }  & P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} \\
			\text {where } & \Sigma^y_{i,t|t-1} \text{ is the variance of } y_t \text{ based on prior belief}\\
			\text {and } & \Sigma^v =  \left[ \begin{matrix} 
				\sigma^2_{\epsilon} &  0 \\ 0 & \sigma^2_\xi \end{matrix}\right] 
		\end{aligned}
	\end{eqnarray*}
\end{itemize}
\end{frame}

\begin{frame}{Noisy Information: individuals}
\begin{itemize}
\item \textbf{Change in mean}
\begin{eqnarray*}
	\begin{aligned}
		\Delta E_{i,t|t}(y_{t+h}) & = \underbrace{\rho^h (1-PH)\Delta E_{i,t-1|t-1}(y_{t})}_{\text{Lagged response}} \\
		& + \underbrace{\rho^hPH \Delta y_{i,t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
	\end{aligned}
\end{eqnarray*}
\end{itemize}

\begin{enumerate}
	\item Rigidity parameter $1-PH$
	\item Serial correlation at individual level 
	\item Always respond to shocks 
\end{enumerate}

\end{frame}

\begin{frame}{Noisy Information: individuals}
\begin{itemize}
	\item \textbf{Variance}

	\begin{eqnarray*}
		\begin{aligned}
			\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) ^{-1}H \Sigma^y_{i,t|t-1} 
		\end{aligned}
	\end{eqnarray*}
	\item \textbf{Change in variance} 
	$$\Delta \Sigma^y_{i,t|t} <0$$

\end{itemize}
\begin{enumerate}
	\item It does not depend on the realizations of the signal. 
	\item It decreases unambiguously from $t-1$ to $t$. 
	\item The two properties carry through to h-period ahead forecast 
\end{enumerate}

\end{frame}

\begin{frame}{Noisy Information: population}
\begin{itemize}
\item \textbf{Mean}

\begin{eqnarray*}
	\begin{aligned}
		\bar E_{t|t} (y_{t+h}) & = \rho^h [(1-PH) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
		& = (1-PH) \bar E_{t-1}(y_{t+h}) + P [\epsilon_t, 0]' \\
		& = (1-PH) \bar E_{t-1}(y_{t+h}) + P \epsilon_t
	\end{aligned}
\end{eqnarray*}
\end{itemize}

\begin{enumerate}
	\item Same properties to the individual forecast 
\end{enumerate}

\end{frame}

\begin{frame}{Noisy Information: population}
\begin{itemize}
\item \textbf{Disagreements}
\begin{eqnarray*}
\begin{aligned}
	Var_t(y_{t+h}) & = E((E_{i,t|t}(y_{t+h}) - \bar E_t(y_{t+h}))^2) \\
	& = \rho^{2h} P^2_\xi \sigma^2_\xi  
\end{aligned}
\end{eqnarray*}
\end{itemize}

\begin{enumerate}
	\item increase with the forecast horizon
	\item depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$ 
	\item increase with the rigidity parameter $P$ in this model
\end{enumerate}

\end{frame}

\begin{frame}{Noisy Information: population}
\begin{itemize}
\item \textbf{Change in disagreements}
\begin{eqnarray*}
\begin{aligned}
\Delta Var_t(y_{t+h}) & = \rho^{2h}(1-\rho^2) P^2_\xi \sigma^2_\xi >0
\end{aligned}
\end{eqnarray*}
\end{itemize}

\begin{enumerate}
	\item disagreements increase as time goes from $t-1$ to $t$. 
	\item disagreements increase as approaching the variable of forecast
\end{enumerate}

\end{frame}

\begin{frame}{Noisy Information: population}
\begin{itemize}
\item \textbf{Average variance}
\begin{eqnarray*}
\begin{aligned}
\bar Var_t (y_{t+h}) = \bar \Sigma^y_t
\end{aligned}
\end{eqnarray*}
\item \textbf{Change in average variance}
\begin{eqnarray*}
\Delta Var_t(y_{t+h}) < 0 
\end{eqnarray*}

\end{itemize}

\begin{enumerate}
	\item average variance is the same as individual variance, not depend on signals
	\item the variance unambiguously drop over time 
\end{enumerate}

\end{frame}

\end{document}

### 2019-06-09 workingfolder/python/InfShocks.py
generated excel file containing all shocks to inflation.News shock cannot be used for now

@@ -128,7 +128,7 @@ ts_var2=ts_var2.copy().dropna()
 # + {"code_folding": [0]}
 # period filter 
 start_t='1948-01-01'
-end_t = '1994-12-30'   # the same period as in Gali (1991)
+end_t = '2019-03-30'   # the same period as in Gali (1991)
 
 ts_var1=ts_var1.copy().loc[start_t:end_t]
 ts_var2=ts_var2.copy().loc[start_t:end_t]
@@ -715,7 +715,7 @@ identified using max-share approach and the news shock is '+ \
 
 # ### Oil shocks (Hamilton 1996)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## loading oil price shocks data 
 os_dataM = pd.read_excel('../OtherData/OilShock.xls',sheet_name='data')
 
@@ -724,8 +724,12 @@ os_dataM['observation_date'] = pd.to_datetime(os_dataM['observation_date'],forma
 os_dataM['quarter'] = os_dataM['observation_date'].dt.year.astype(int).astype(str) + \
          "Q" + os_dataM['observation_date'].dt.quarter.astype(int).astype(str)
 
+## normolization using std 
+
+os_dataM['OPShock_nm'] =  os_dataM['OPShock']/os_dataM['OPShock'].std()
+
 ## compute quarterly shock
-os_shockQ  = os_dataM.groupby(['quarter'], sort=False)['OPShock'].max()
+os_shockQ  = os_dataM.groupby(['quarter'], sort=False)['OPShock_nm'].max()
 
 ## creating quarterly date index
 os_datesQ = os_dataM['quarter'].drop_duplicates()
@@ -742,21 +746,38 @@ str_shocks_est.tail()
 
 # ### Monetary policy shocks 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## loading mp shocks data
 mps_data = pd.read_excel('../OtherData/2MPShocksJW.xls',sheet_name='data')
 mps_data['Date'] = pd.to_datetime(mps_data['Date'],format='%m/%d/%Y')
-mps_var = mps_data[['MP1','ED4','ED8']] 
+mps_datesQ = mps_data['Date'].dt.year.astype(int).astype(str) + \
+         "Q" + mps_data['Date'].dt.quarter.astype(int).astype(str)
+
+## quarter series used to collapse 
[…]

### 2019-06-10 workingfolder/python/InfShocks.py
started IRF type analysis

@@ -79,7 +79,7 @@ from scipy.optimize import minimize
 #
 # The existing SVAR package in *statsmodels* only handles cases with direct zero restrictions on $B$ matrices. Therefore I write my own codes using long-run restrictions here.  
 
-# + {"code_folding": [0, 12, 21]}
+# + {"code_folding": [12, 21]}
 ## loading technology shock data
 ts_data = pd.read_excel('../OtherData/Emp.xls',sheet_name='data')
 ts_data2 = pd.read_excel('../OtherData/EmpSaQ.xls',sheet_name='data')
@@ -105,7 +105,7 @@ inf_datesQ = inf_dataQ['date'].dt.year.astype(int).astype(str) + \
              "Q" + inf_dataQ['date'].dt.quarter.astype(int).astype(str)
 inf_datesQ = dates_from_str(inf_datesQ)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 # set date index to productivity and labor series
 ts_var1 = ts_data[['DLPROD1','DLHOURS']]
 ts_var2 = ts_data2[['DLPROD2','DLEMP']]
@@ -170,7 +170,7 @@ rs1=model1.fit(4)
 rs1.summary()
 
 
-# + {"code_folding": [2]}
+# + {"code_folding": [0, 2]}
 ## define function of Blanchard and Quah long-run restriction
 
 def ma_rep(coefs, maxn=10):
@@ -287,7 +287,7 @@ def SVAR_BQLR(rs,T_irf=10):
                 'eps_est':epsilon_est,'A1':A1,'C1':C1,'nlags':nlags, 'neqs': k,\
                 'residuals':u,'P_est':P_svar_est,'irf':svar_ma_rep}
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### Invokes BQLR 
 
 T_irf = 10  # 10 quarters irf 
@@ -769,15 +769,24 @@ mps_datesM = dates_from_str(mps_datesM)
 mps_var.index = pd.DatetimeIndex(mps_datesM)
 mps_shockQ  = mps_var.groupby(['quarter'], sort=False)[['MP1','ED4','ED8']].sum(axis=1)
 
+## convert to numeric 
+
+mps_shockQ['MP1']=pd.to_numeric(mps_shockQ['MP1'],errors='coerce')   
+mps_shockQ['ED4']=pd.to_numeric(mps_shockQ['ED4'],errors='coerce')   
[…]

### 2019-06-12 workingfolder/python/InfShocks.py
Create combined version of IRFs of inflation to various shocks(all standardized) and using param bootstrapping

@@ -79,7 +79,7 @@ from scipy.optimize import minimize
 #
 # The existing SVAR package in *statsmodels* only handles cases with direct zero restrictions on $B$ matrices. Therefore I write my own codes using long-run restrictions here.  
 
-# + {"code_folding": [12, 21]}
+# + {"code_folding": [12]}
 ## loading technology shock data
 ts_data = pd.read_excel('../OtherData/Emp.xls',sheet_name='data')
 ts_data2 = pd.read_excel('../OtherData/EmpSaQ.xls',sheet_name='data')
@@ -101,9 +101,14 @@ inf_dataM = pd.read_stata('../OtherData/InfM.dta')
 filterQ = inf_dataM['month'].isin([3,6,9,12])
 inf_dataQ = inf_dataM[filterQ]
 infQ = inf_dataQ['CPIAU'].pct_change()
+
 inf_datesQ = inf_dataQ['date'].dt.year.astype(int).astype(str) + \
              "Q" + inf_dataQ['date'].dt.quarter.astype(int).astype(str)
 inf_datesQ = dates_from_str(inf_datesQ)
+
+## Other inflation measurs as backup
+
+infQ_all = inf_dataQ[['CPIAU','CPICore','PCEPI']].pct_change()
 
 # + {"code_folding": []}
 # set date index to productivity and labor series
@@ -114,16 +119,28 @@ ts_var1.index = pd.DatetimeIndex(datesQ1,freq='Q')
 ts_var2.index = pd.DatetimeIndex(datesQ2,freq='Q')
 
 # set date index to inf series 
-infQ.index= pd.DatetimeIndex(inf_datesQ)
+infQ.index = pd.DatetimeIndex(inf_datesQ)
+infQ_all.index = pd.DatetimeIndex(inf_datesQ)
+infQ_all.columns=['CPIAU','CoreCPI','PCE']
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## merge with inflation
+
+### include all inflation measures
+LRVar_dt = pd.concat([ts_var1,infQ_all],join='inner',axis=1)
+
 # order of vector for var:  [productivity, labor input, inflation]
 ts_var1 = pd.concat([ts_var1,infQ], join='inner', axis=1)
[…]

### 2019-06-12 workingfolder/python/InfShocks.py
compare IRs to tech shocks from LRSVAR and MaxShare, with opposite directions. Something is wrong here

@@ -678,7 +678,7 @@ def SVAR_MaxShare(rs,h,pty_id=0,contemp=True):
     return {'var_coefs':var_coefs,'sigma_u':sigma_u,'fe':fe,'nlags':nlags, 'neqs': k,\
                 'residuals':u,'alpha_est':alpha_est,'epsilon_est':epsilon_est}
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## invoke max_share estimation
 horizon = 40  #10 years
 SVAR_maxshare_rst = SVAR_MaxShare(rs1,horizon)
@@ -687,18 +687,18 @@ alpha_est = SVAR_maxshare_rst['alpha_est']
 
 # + {"code_folding": []}
 ## save it to data frames 
-str_shocks_est['pty_shock_max']=tech_shock.T
+str_shocks_est['pty_max_shock']=tech_shock.T
 
 # compare two tech shocks estimated from different approaches 
 plt.figure(figsize=(10,6))
-plt.plot(str_shocks_est['pty_shock_max'],label='pty_maxshare')
+plt.plot(str_shocks_est['pty_max_shock'],label='pty_maxshare')
 plt.plot(str_shocks_est['pty_shock'],'r-.',label='pty_lr')
 plt.legend(loc=1)
 
-# + {"code_folding": []}
+# + {"code_folding": [1]}
 print('The correlation coefficient of tech shocks identified using long-run \
 \n restriction and max-share approach is '+ \
-      str(round(str_shocks_est['pty_shock_max'].corr(str_shocks_est['pty_shock']),3)))
+      str(round(str_shocks_est['pty_max_shock'].corr(str_shocks_est['pty_shock']),3)))
 # -
 
 # ### News shocks by Sims et al.(2014)
@@ -721,14 +721,14 @@ str_shocks_est['news_shock']=news_shock.T
 # + {"code_folding": [0]}
 # compare two tech shocks estimated from different approaches 
 plt.figure(figsize=(10,6))
-plt.plot(str_shocks_est['pty_shock_max'],label='pty_maxshare')
+plt.plot(str_shocks_est['pty_max_shock'],label='pty_maxshare')
 plt.plot(str_shocks_est['news_shock'],'r-.',label='news shock')
 plt.legend(loc=1)
 # -
 
 print('The correlation coefficient of tech shocks \
 identified using max-share approach and the news shock is '+ \
[…]

### 2019-06-17 slides/ExpSlides.tex
generated graphs and aregressions for quarterly data
Updating slides including IR plots
Include IR plots without mp shocks

@@
 \usepackage{graphicx}
+\usepackage{adjustbox}  % Allows for fitting tables into slide
 
@@
 
+\begin{frame}{Population moments: average uncertainty}
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/var_var.png} 
+\end{figure}
+\end{frame}
+
 \begin{frame}{Population moments: disagreements}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_diag.png} 
+	\includegraphics[scale=0.3]{figures/mean_disg.png} 
+\end{figure}
+\end{frame}
+
+\begin{frame}{Population moments: disagreements}
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/mean_disg.png} 
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/var_diag.png} 
+	\includegraphics[scale=0.3]{figures/var_disg.png} 
+\end{figure}
+\end{frame}
+
+\begin{frame}{Population moments: uncertainty and disagreements}
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/var_disg2.png} 
 \end{figure}
@@
 
+\section{Empirical Results}
+
 \begin{frame}{Empirical execution}
@@
 \begin{itemize}
-	\item \textbf{Measurement Errors}:  winsorization is still necessary
+
 \item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
-    \item \textbf{Identification of Shocks}: following \cite{coibion2012can}
+ \item \textbf{Identification of Shocks}: following \cite{coibion2012can} and monetary policy shocks. 
 \end{itemize}
+
+\end{frame}
+
+\subsection{Test of Null Hypothesis of Rational Expectation}
+
+\begin{frame}{Test of Rational Expectation}
+\begin{table}[tbhp] \centering \adjustbox{max height=\dimexpr\textheight-5.5cm\relax, max width=\textwidth}{
+	\begin{tabular}{lllllll}
+		\hline 
+		& SPFCPI\_FElvl       & SPFPCE\_FElvl & SPFCPI\_Vardiff & SPFPCE\_Vardiff & SPFCPI\_Disgdiff & SPFPCE\_Disgdiff            \\
+		\hline 
+		L.InfExp\_FE        & 0.941***      & 1.195***        &                 &                  &                  &           \\
+		& (0.0840)      & (0.142)         &                 &                  &                  &           \\
+		L2.InfExp\_FE       & -0.313**      & -0.625**        &                 &                  &                  &           \\
+		& (0.116)       & (0.198)         &                 &                  &                  &           \\
+		L3.InfExp\_FE       & 0.114         & 0.0782          &                 &                  &                  &           \\
+		& (0.114)       & (0.196)         &                 &                  &                  &           \\
+		L4.InfExp\_FE       & -0.137        & -0.0162         &                 &                  &                  &           \\
+		& (0.0820)      & (0.131)         &                 &                  &                  &           \\
+		L.InfExp\_Var\_ch   &               &                 & -0.855***       & -0.565**         &                  &           \\
+		&               &                 & (0.189)         & (0.162)          &                  &           \\
+		L2.InfExp\_Var\_ch  &               &                 & -0.780**        & -0.452*          &                  &           \\
+		&               &                 & (0.220)         & (0.186)          &                  &           \\
+		L3.InfExp\_Var\_ch  &               &                 & -0.556*         & -0.429*          &                  &           \\
+		&               &                 & (0.219)         & (0.189)          &                  &           \\
+		L4.InfExp\_Var\_ch  &               &                 & -0.167          & 0.00385          &                  &           \\
+		&               &                 & (0.188)         & (0.172)          &                  &           \\
+		L.InfExp\_Disg\_ch  &               &                 &                 &                  & -0.571***        & -0.640*** \\
+		&               &                 &                 &                  & (0.0699)         & (0.127)   \\
+		L2.InfExp\_Disg\_ch &               &                 &                 &                  & -0.376***        & -0.0944   \\
+		&               &                 &                 &                  & (0.0764)         & (0.141)   \\
+		L3.InfExp\_Disg\_ch &               &                 &                 &                  & -0.0455          & 0.180     \\
+		&               &                 &                 &                  & (0.0661)         & (0.138)   \\
+		L4.InfExp\_Disg\_ch &               &                 &                 &                  & -0.110*          & -0.0364   \\
+		&               &                 &                 &                  & (0.0479)         & (0.123)   \\
+		\hline 
+		N                   & 143           & 41              & 44              & 44               & 146              & 44        \\
+		R-sq                & 0.593         & 0.750           & 0.384           & 0.322            & 0.356            & 0.496    \\
+		\hline 
+	\end{tabular}
+}
+\end{table}
+\end{frame}
+
+\begin{frame}{Identified Inflation shocks}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/inf_shocksQ.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Results from \cite{coibion2012can}}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/RigidityJPEFigure2.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Inflation IR to  shocks}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/CPIAU_ashocks.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Inflation IR to  shocks}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/PCEPI_ashocks.png} 
+\end{figure}
+
+\end{frame}
+
+\subsection{Professional forecasters as a baseline }
+
+\begin{frame}{Forecasting errors IR to  shocks}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/SPFFE_ashocks.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Disagreements IR to  shocks}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Uncertainty IR to shocks}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/SPFVar_ashocks.png} 
+\end{figure}
 

### 2019-06-17 slides/ExpSlides.tex
lstarted working on individual moments

@@
 
-\begin{frame}{Identified Inflation shocks}
+\begin{frame}{Inflation shocks}
 
@@
 
-\begin{frame}{Inflation IR to  shocks}
+\begin{frame}{Inflation IR to  shocks exluding monetary policy}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/CPIAU_ashocks_nmp.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Inflation IR to  shocks including monetary policy}
 
@@
 
-\begin{frame}{Inflation IR to  shocks}
+\begin{frame}{Inflation IR to  shocks excluding monetary policy}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/PCEPI_ashocks_nmp.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Inflation IR to  shocks including monetary policy}
 
@@
 
-\subsection{Professional forecasters as a baseline }
+\subsection{Benchmark Results from Professional Forecasters }
 
-\begin{frame}{Forecasting errors IR to  shocks}
+\begin{frame}{Forecasting errors IR to  shocks excluding monetary policy}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/SPFFE_ashocks_nmp.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Forecasting errors IR to  shocks including monetary policy}
 
@@
 
-\begin{frame}{Disagreements IR to  shocks}
+\begin{frame}{Disagreements IR to  shocks excluding monetary policy}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks_nmp.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Disagreements IR to  shocks including monetary policy}
 
@@
 
-\begin{frame}{Uncertainty IR to shocks}
+\begin{frame}{Uncertainty IR to shocks excluding monetary policy}
+
+\begin{figure}
+	\includegraphics[scale=0.3]{figures/SPFVar_ashocks_nmp.png} 
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Uncertainty IR to shocks including monetary policy}
 

### 2019-06-18 slides/ExpSlides.tex
seperate MP and non-MP shocks for IRF. Looking into sub period consistent with coibion to replicate their results

@@
 
-\begin{frame}{Forecasting errors IR to  shocks including monetary policy}
+\begin{frame}{Forecasting errors IR to monetary policy shocks}
 
@@
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks_nmp.png} 
+	\includegraphics[scale=0.3]{figures/SPFDisg_ab_ashocks_nmp.png} 
 \end{figure}
@@
 
-\begin{frame}{Disagreements IR to  shocks including monetary policy}
+\begin{frame}{Disagreements IR to  monetary policy shocks}
 
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks.png} 
+	\includegraphics[scale=0.3]{figures/SPFDisg_ab_ashocks.png} 
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFVar_ashocks_nmp.png} 
+	\includegraphics[scale=0.3]{figures/SPFVar_ab_ashocks_nmp.png} 
 \end{figure}
@@
 
-\begin{frame}{Uncertainty IR to shocks including monetary policy}
+\begin{frame}{Uncertainty IR to monetary policy shocks}
 
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFVar_ashocks.png} 
+	\includegraphics[scale=0.3]{figures/SPFVar_ab_ashocks.png} 
 \end{figure}

### 2019-06-19 paper/Draft.tex
started drafting.creating Paper folder and Draft tex file.

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}

%opening
\title{Testing Theories of Expectation Formation using Probabilistic Answers}
\author{Tao Wang}

\begin{document}

\maketitle

\section{Introduction}

The theories on how different agents form expectations have proliferated over the past decade. On one hand, these theories built upon different micro foundations produce some similar macro patterns. For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.

On the other hand, however, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts. My goal of this exercise is to derive the testable predictions based on various theories, and utilize the probablistic questions from both professional forecasters survey and household survey to test them.

The potential contribution lies in the extra insights I may get from using probablistic questions.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \cite{manski2004measuring}.} One obvious advantage of density expectations compared to point one is availability of higher moments, i.e. variance of the forecast indicates the dispersion of the forecasts. Along time dimension, the dynamics of conditional relative likelihood is a useful indicator of information gain or forecasting efficiency. Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions. Although the detailed implementation of these tests involves technical difficulties, the ideas are quite clear.  Lastly, with second moments in individual level expectations, we are allowed to potentialy explore the heterogeneity across agents within one theory. For instance, sticky information typically assume a posson update rate for all agents in the economy. This is partly due to the fact that available data only allows us to recover single parameter of regidity instead of inter-group heterogeneity.

\section{Theories}

\subsection{A Unified Framework}

Agent i's $h$-period ahead density forecast of variable $y_i$ at time $t$ is the conditional density of $y_{i,t+h}$ given the information set $I_{i,t}$ available at time $t$.

$$\widehat f_{i,t}(y^i_{t+h}|I_{i,t})$$

Notice here the $y_{t+h}$ has supscript $i$. This is to remind that in general the variables $y_{t+h}$ can be either aggregate variables or idiosyncratic ones, in the former case, we could drop subscript $i$.

$I_{i,t}$ is the information set available at time t for individual $i$. The information set can be also agent specific, therefore, it has subscript $i$.  The specific content contained in $I_t$ varies from different models. Seemingly a simple and justified assumption is that $x_t \in  I_t$. This, however, may not be ture for all models. For instance, sticky expectation and rational inattention literature all predict that agents are not able to update new information instataneously. Thus the information set may not winclude the recent realization of the variable itself.

Assumption also needs to be made about the underlying model that generates the conditional density of the variables by agent $i$.

Given the forecast density, the expectation of forecast at time $t$ is.

$$E_{i,t}(y_{t+h}|I_{i,t}) =\int \widehat f_{i,t}(y_{t+h}|I_{i,t})y_{t+h} d y_{t+h}\equiv \bar y_{i,t,t+h}$$

The forecasting variance is

$$Var_{i,t}(y_{t+h}|I_{i,t})=\int \widehat f_{i,t}(y_{t+h}|I_{i,t}) (y_{t+h} - \bar y_{i,t,t+h})^2d y_{t+h}$$

The true process of $y_{t}$ depends on the variables. Here, we consider a simple case where true process of $y_t$ is AR(1).

$$y_{t+1} = \rho y_t + \omega_t$$

$$\omega_t \sim N(0,\sigma^2_{\omega})$$

\subsection{Full-information rational expectation benchmark }

\subsubsection{Individual moments}

Full information rational expectation implies $y_t \in I_t$

\textbf{Expectation}
$$E_{i,t}(y_{t+h}|y_t) = E_{i,t}(y_{t+h}|y_t) = \rho^h y_t $$

\textbf{Variance} 
$$Var_{i,t}(y_{t+h}|y_t) = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$

Ex post forecast error of individual i $$FE_{i,t} = y_{t+h} - E_{i,t}(y_{t+h}|y_t) = \sum^h_{s=1} \rho^s \omega_{t+h-s}$$ has is mean zero and orthogonal to information at time $t$.

\subsubsection{Population moments}

A special case below.

\subsection{Sticky Expectation}

Agent does not update information instantaneously, instead at a Possion rate $\lambda$. Specificaly, at any point of time $t$, the agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

\subsubsection{Individual moments}

For an individual whose most recent update occurs at $\tau$ period before, $I_{i,t|t-\tau} = I_{i,t-\tau} = y_{t-\tau}$. Thus

$$E_{i,t|t-\tau}(y_{t+h}|I_{i,t}) = E_{i,t}(i,y_{t+h}|y_{t-\tau}) = \rho^{h+\tau} y_{t-\tau}$$

$$Var_{i,t|t-\tau}(y_{t+h}|I_{i,t}) = Var_{i,t}(y_{t+h}|y_{t-\tau}) = \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}$$

$Var_{i,t|t-\tau}(y_{t+h}|_{i,t})$ increases as $\tau$ increases. The model collapses to full-information rational expectation if $\tau=0$ for all individuals.

Now, we turn to the case when agent updates infrequently.

\begin{itemize}
\item When the update happens, the variance responds substantially.

$$Var_{i,t}(y_{t+h}|y_t) - Var_{i,t|t-\tau}(y_{t+h}|y_{t-\tau}) = \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega} - \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} = \sum^{\tau}_{s=0} \rho^{2s}\sigma^2_{\omega}$$

\item When the update does not happen, the variance responds little.

$$Var_{i,t|t-\tau-1}(y_{t+h}|y_{t-\tau-1}) - Var_{i,t|\tau}(y_{t+h}|y_{t-\tau}) = \sigma^2_{\omega}$$

At individual level, it is hard to recover the information rigidity parameter $\lambda$ directly. One testable prediction of information rigidity is that the change in forecast variance varies substantially depending on if updated or not. The longer period for which the agent stays unupdated(greater $\tau$), the bigger the change is in the forecasting variance.

However, the difference in average responses in variance to new information may speak to potential heterogeneity in information rigidity. According to the theory above, higher information rigidity implies high volatility of variance responses.  
\end{itemize}

\subsubsection{Population moments}

\begin{enumerate}	
\item Average forecast

The mean forecast across population is a weighted average of past rational expectations

\begin{eqnarray}
\begin{aligned}
\bar E_t(y_{t+h}) & = \lambda \underbrace{E_t(y_{t+h})}_{\textrm{rational expectation at t}} + (1-\lambda) \underbrace{\bar E_{t-1}{y_{t+h}}}_{\textrm{average expectation at} t-1} \\
& = \lambda E_t(y_{t+h}) + (1-\lambda) (\lambda E_{t-1}(y_{t+h})+ (1-\lambda) \bar E_{t-2}(y_{t+h}))... \\
& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s E_{t-s}(y_{t+h}) \\
& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s \rho^{s+h}y_{t-s}
\end{aligned}
\end{eqnarray}

The change in average forecast is

\begin{eqnarray}
\begin{aligned}
\Delta \bar E_t(y_{t+h})&  = (1-\lambda) \Delta \bar E_{t-1}(y_{t+h}) + \lambda (E_t(y_{t+h}) - E_{t-1}(y_{t+h})) \\ 
& = (1-\lambda) \Delta \bar E_{t-1}(y_{t+h}) + \lambda \rho^h \omega_t 
\end{aligned}
\end{eqnarray}

This implies the change in average forecast is serially correlated, depending on the information rigidity, i.e. lower $\lambda$ implies higher serial correlation. Also lower $\lambda$ implies the expectation underreact to the shocks at $t$.

\item Cross-sectional disagreements

According to information rigity model, if everyone is instantaneously udpated, there should not be disagreements. In general, the dispersion in forecasting is non-zero because of different lags in updating. One can also derive variance of forecasts across agents at time $t$

\begin{eqnarray}
\begin{aligned}
Var_t(E_{i,t}(y_{t+h}) ) & = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^{\tau} (E_{t|t-\tau}(y_{t+h}) - \bar E_t(y_{t+h}))^2  
\end{aligned}
\end{eqnarray}

From time $t$ to $t+1$, the change in dispersion comes from two sources. One is newly realized shock at time $t+1$. The other component is from people who did not update at time $t$ and update at time $t+1$.

\begin{eqnarray}
\begin{aligned}
\Delta Var_{t+1}(E_{i,t+1}(y_{t+h})) = \textrm{change due to new updaters} + \textrm{shock at time } t+1 
\end{aligned}
\end{eqnarray}

Notice the change is positive, meaning the dispersion rises in response to a shock. Importantly, the increase is the same regardless of the realization of the shock.

More generally, we can derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.

\begin{eqnarray}
\rho^{2(h+j)} (1-\lambda^{j+1})\lambda^{j+1} \omega^2_t
\end{eqnarray}

A shock increases the disagreements across agents and then it gradually returns to its steady state level.

\item Average variance

Since we have individual level variance, we can also derive average variance of the population. Taking the average of variance across individual agents at time $t$. Here I use the $\bar{}$ to represent population mean of variance.

\begin{eqnarray}
\begin{aligned}
\bar Var_{t}(y_{t+h}) & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who does not update until }t-\tau} \underbrace{Var_{t|t-\tau}(y_{t+h})}_{\text{ Variance of most recent update at }t-\tau} \\
& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
\end{aligned}
\end{eqnarray}

Correspondingly, the change in average uncertainty will be

\begin{eqnarray}
\begin{aligned}
\Delta \bar Var_{t}(y_{t+h}) & = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} - \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} = 0  
\end{aligned}
\end{eqnarray}

An information rigidity model based on fixed Poisson update rate predicts that the average variance does not change over time. This can be tested.

\end{enumerate}

\subsubsection{Summary of predictions of information rigidity}

\begin{itemize}
\item Individual expectation may or may not change depend upon if updating. 
\item Individual variances changes non-monotonically depending on if updating. Always increase with arrival of new information. 
\item Population mean of forecast responds with lags. Change is serially correlated. 
\item Population dispersion of forecasts rise in response to new shocks and return to steady state level gradually. 
\item Population average variance does not change over time. 
\end{itemize}

\subsection{Noisy information}

A class of so-called noisy information model describes the expectation formation as a process extracting or filtering true fundamental state variable $y_t$ from a sequence of realized signals. The starting assumption is that agent cannot observe the true variable perfectly. Unlike information rigidity model, it is assumed that agents keep track of the realizations of the signals instantaneously all the time.

We assume agent $i$ observe two signals $s^{pb}$ and $s^{pr}_i$, with $s^{pb}$ being public signal common to all agents, and $s^{pr}_i$ private signals being individual specific. The generating process of two signals are

\begin{eqnarray}
\begin{aligned}
s^{pb}_t = y_t + \epsilon_t, \quad \epsilon_t \sim N(0,\sigma^2_\epsilon)\\ 
s^{pr}_{i,t} = y_t + \xi_{i,t} \quad \xi_{i,t} \sim N(0,\sigma^2_\epsilon)
\end{aligned}
\end{eqnarray}

We can stack the two signals into one vector $s_{i,t} = [s^{pb}_t,s^{pr}_{i,t}]'$ and $v_{i,t}= [\epsilon_t,\xi_{i,t}]'$. So in a compact form, it can be written as

\begin{eqnarray}
\begin{aligned}
s_{i,t} = H y_{t} + v_{i,t} \\
\text{where } & H=[1,1]' \quad \\
\end{aligned}
\end{eqnarray}

In our general framework, the noisy information implies that the information set $I_{i,t}$ available to individual $i$ at time $t$ only includes past and recent realizations of the signals. The individual density forecast of $y_{t+h}$ is

$$\widehat f_{i,t}(y_{t+h}|I_{i,t}) = \widehat  f_{i,t}(y_{t+h}|s_{i,t},s_{i,t-1}...) \equiv \widehat  f_{i,t|t}(y_{t+h})$$

We use $t|k$ to denote the moments at time t based on information(signals) till time $k$.

Then we are ready to apply Kalman Filter in this context. The posterior distribution of $y_{t}$ after seeing all signals till $t$ is

\begin{eqnarray}
\widehat  f_{i,t|t}(y_{t+h})  \sim  N(E_{i,t|t}(y_{t+h}), Var_{i,t|t}(y_{t+h}))
\end{eqnarray}

where the expectation and variances are functions of noisiness of signals and fundamentals. The expectation also depends on the realized values. But this is not the case for variance.

\subsubsection{Individual moments }

\begin{enumerate}

\item Expectation

Now any agent trying to forecast future variables will have to form her expectation of the contemporaneous state variable, $E_{i,t|t}(y_t)$. Then the best h-period ahead forecast is simply iterated h periods forward based on the AR(1) process.

Thus, we first work out $E_{i,t|t}(y_t)$.

\begin{eqnarray}
\begin{aligned}
E_{i,t|t}(y_{t}) 
& =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
& = (1-PH) E_{i,t|t-1}(y_{t}) + Ps_{i,t} \\
& = (1-PH) E_{i,t|t-1}(y_{t}) + PH y_{i,t} + P v_{i,t} \\
\text{where the Kalman gain }  & P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} \\
\text {where } & \Sigma^y_{i,t|t-1} \text{ is the variance of } y_t \text{ based on prior belief}\\
\text {and } & \Sigma^v =  \left[ \begin{matrix} 
  \sigma^2_{\epsilon} &  0 \\ 0 & \sigma^2_\xi \end{matrix}\right] 
\end{aligned}
\end{eqnarray}

The h-period ahead forecast is

\begin{eqnarray}
\begin{aligned}
E_{i,t|t}(y_{t+h}) & = \rho^{h}E_{i,t|t}(y_{t+h}) 
\end{aligned}
\end{eqnarray}

Individual forecast partially responds to new signals, i.e. $P<1$. $P=1$ is a special case when both signals are perfect thus $\Sigma^v = 0$, then the formula collapses to full rational expectation.

Now, the rigidity parameter is governed by $1-PH$ with multiple signals. It is a function of variance of $y$ from the prior of previous period and noisiness of the signals. Therefore, it is time variant as the variance is updated by the agent each period.

There are a few important distinctions between noisy information and sticky expectation.

$\bullet$  First, the persistence of expectation exists at individual level. There is serially correlation between $E_{i|t|t}(y_t)$ and $E_{i,t|t-1}(y_{t})$, or more generally, between $E_{i,t|t}(y_{t+h})$ and $E_{i,t|t-1}(y_{t+h})$. This pattern can be only observed from population moments according to sticky expectation models.

To see this, the change in individual forecast from $t-1$ to $t$ is

\begin{eqnarray}
\begin{aligned}
\Delta E_{i,t|t}(y_{t+h}) & = \underbrace{\rho^h (1-PH)\Delta E_{i,t-1|t-1}(y_{t})}_{\text{Lagged response}} + \underbrace{\rho^hPH \Delta y_{i,t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
\end{aligned}
\end{eqnarray}

The serial correlation is $\rho^h(1-PH)$, it does not only depend on $PH$, but also the forecast horizon $h$. Therefore, one testable assumption is to see auto regression of change in forecast to see if the coefficient depends on horizon.

$\bullet$  Second, the expectation adjusts in each period as long as there is new information. In sticky expectation, however, the expectation adjusts only when the agent updates.

\item Variance

The posterior variance at time $t$ is a linear function of prior variance and variance of signals.

\begin{eqnarray}
\begin{aligned}
\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} 
\end{aligned}
\end{eqnarray}

There are a few important properties in the variance.

- First, it does not depend on the realizations of the signal.

- Second, it decreases unambigously from $t-1$ to $t$. To see this

\begin{eqnarray}
\Sigma^y_{i,t|t} - \Sigma^y_{i,t|t-1} = - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} <0
\end{eqnarray}

These two properties carry through to the h-period ahead forecast as well. As the forecast variance is the following

\begin{eqnarray}
Var_{i,t|t} (y_{t+h}) = \rho^{2h} \underbrace{Var_{i,t}(y_{t})}_{\Sigma_{i,t|t}} + \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega}
\end{eqnarray}

\begin{eqnarray}
\Delta Var_{i,t|t} (y_{t+h}) = \rho^{2h}\Delta \Sigma_{i,t|t} - \rho^{2h} \sigma^2_{\omega}
\end{eqnarray}

From $t$ to $t+1$, when $h\geq 1$, the decline in variance come from two sources. The first source is the pure gain from the new signals, i.e. $\Delta \Sigma^y_{i,t|t}$. It is scalled by the factor $\rho^{2h}$. The second source is present in full information rational expectation model: as time goes from $t-1$ to $t$, there is a reduction of uncertainty about $\omega_t$.

\end{enumerate}

\subsubsection{Population moments}

\begin{enumerate}

\item Average forecast

\begin{eqnarray}
\begin{aligned}
\bar E_{t|t} (y_{t+h}) & = \rho^h [(1-PH) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
& = (1-PH) \bar E_{t-1}(y_{t+h}) + P [\epsilon_t, 0]' \\
& = (1-PH) \bar E_{t-1}(y_{t+h}) + P \epsilon_t
\end{aligned}
\end{eqnarray}

\item Change in average forecast

\begin{eqnarray}
\begin{aligned}
\Delta \bar E_t|t (y_{t+h}) & = \rho^h (1-PH) \Delta \bar E_{t-1}(y_{t+h}) + \rho^h P \Delta \epsilon_t
\end{aligned}
\end{eqnarray}

Same to the individual forecast, the change in average forecasts has serial correlation with the same auto regression parameter $\rho^h(1-PH)$.

\item Cross-sectional disagreements

In this model, the only disagreements across agents come from the difference in realized private signals. Therefore, in short-cut, the disagreements are

\begin{eqnarray}
\begin{aligned}
Var_t(y_{t+h}) & = E((E_{i,t|t}(y_{t+h}) - \bar E_t(y_{t+h}))^2) \\
& = \rho^{2h} P^2_\xi \sigma^2_\xi  
\end{aligned}
\end{eqnarray}

Several properties.

$\bullet$ First, the disagreements increase with the forecast horizon. 
$\bullet$  Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. 
$\bullet$  Third, similar to sticky expectation model, the disagreements also increase with the rigidity parameter $P$ in this model.

\item Change in disagreements

\begin{eqnarray}
\begin{aligned}
\Delta Var_t(y_{t+h}) & = \rho^{2h}(1-\rho^2) P^2_\xi \sigma^2_\xi >0
\end{aligned}
\end{eqnarray}

The disagreements increase as time goes from $t-1$ to $t$. Also, as the time approaches $t+h$, the disagreements increase. This seems counterintuitive. But the reason is that here the disagreenments always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.

\item Average variance

Since the variance does not depend on signals and the precision is the same aross the agents, average variance is equal to the variance of each individual.

\begin{eqnarray}
\begin{aligned}
\bar Var_t (y_{t+h}) = \bar \Sigma^y_t
\end{aligned}
\end{eqnarray}

Also, same as the individual variance, the variance unambiguiously drop as time goes by.

\begin{eqnarray}
\Delta Var_t(y_{t+h}) < 0 
\end{eqnarray}

\subsubsection{Summary of predictions from noisy information}

$\bullet$  Invididual expectation adjusts in each period, but only partially adjusts to new information. \\
$\bullet$ Unlike sticky expectation, slugishness in adjustment or serial correlation of adjustment exists in individual level. The correlation parameter decreases with forecast horizon, which is not the case in sticky expectation.\\
$\bullet$  Individual variance unambiguously drops each period as one approaches the period of realization. In sticky expectation, it increases regardless of updating or not. \\ 
$\bullet$  Population average forecast partially adjusts to news and has serial correlation as the individual level. \\
$\bullet$  Population disagreements rise in each period as time approaches the period of realization. Disagreetments will never be zero. \\
$\bullet$  Average variance declines unambiguously each period. 
\end{enumerate}

\subsection{Other Theories}

\begin{enumerate}
\item Rational inattention. 
\begin{itemize}
	\item Chris Sim's model.\cite{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy. Agents optimally trade off the fixed cost of being attentative versus the gain from uncertainty gain.   
	\item Ricardo Reis's model. \cite{reis2006inattentive}
	\item Xavier Gabaix's sparse matrix model. \cite{gabaix2014sparsity}
\end{itemize}

\item Epidemiologic view. \cite{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.

\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \cite{angeletos2009incomplete}

\end{enumerate}

\section{Empirical Results}

\subsection{Data}

\begin{itemize}

		\item \textbf{New York Fed Survey of Consumer Expectation}
	\begin{itemize}
			\item Include not only perceived probabilities of binary event as in Michigan Survey does, but also elicit densitity forecasts. 
	\end{itemize}
	\item \textbf{Professional Forecasters}

\end{itemize}

A summary of the data information is as below.

\begin{table}[]
			\caption{Information of Data}
	\begin{tabular}{lll}

		\hline 
		& SCE & SPF        \\
		\hline 
		Time period                                    & 2013-present                            & 2007-present             \\
		Frequency                                      & Monthly                                 & Quarterly                \\
		Sample Size                                    & 1,300                                   & 30-50                    \\
		Aggregate Var in Density                       & 1-yr  and 3-yr ahead inflation          & 1-yr CPI and PCE         \\
		Individual Var in Density                      & 1-yr earning growth                     & No                       \\
		Pannel Structure                               & stay up to 12 months                    & average stay for 5 years \\
		Demographic Info                        & Education, Income, Age, Location        & Industry    \\
		\hline 
	\end{tabular}
\end{table}

\subsection{Density Estimates}

\subsection{Test of Null Hypothesis of Rational Expectation}

\subsubsection{Replicating  \cite{fuhrer2018intrinsic}}

\subsection{Professional Forecasters as a Benchmark}

\subsubsection{Replicating \cite{coibion2012can}}

\subsubsection{Additional Evidence from Uncertainty}

\subsection{Evidence from Households}

\section{Conclusion}

\bibliographystyle{apalike}
\bibliography{TestingExpectationTheories}

\end{document}

### 2019-06-19 paper/Draft.tex
FIRE benchmmark theory first draft.Remains to proofread.

@@
 %opening
-\title{Testing Theories of Expectation Formation using Probabilistic Answers}
+\title{Testing Theories of Expectation Formation using Probabilistic Forecasts}
 \author{Tao Wang}
@@
 
-\section{Theories}
+\section{Theories of Expectation Formation}
 
-\subsection{A Unified Framework}
+\subsection{Definition of moments}
 
-Agent i's $h$-period ahead density forecast of variable $y_i$ at time $t$ is the conditional density of $y_{i,t+h}$ given the information set $I_{i,t}$ available at time $t$.
+An agent $i$ is forming expectations about a stochastic variable $y^i_{t+h}$.
+The supscript $i$ can be dropped if it is an aggregate (i.e.
+inflation) variable instead of individual specific  (i.e.
+household income or house value).
+This paper focuses on forecasting of aggregate variables, in particular, inflation.
+So we can simply denote the variable as $y_{t+h}$.
+To put it another way, all agents are foreasting the same object.
+\footnote{Only in the context of forecasting aggregate variable, it is meaningful to study the average expectations and disagreements across agents.}
 
-$$\widehat f_{i,t}(y^i_{t+h}|I_{i,t})$$
+Denote $ f_{i,t+h|t}$ as agent i's $h$-period-ahead density forecast. $ f_{i,t+h|t}$ is the conditional density of $y_{i,t+h}$ given the information set $I_{i,t}$ available at time $t$.
 
-Notice here the $y_{t+h}$ has supscript $i$.
-This is to remind that in general the variables $y_{t+h}$ can be either aggregate variables or idiosyncratic ones, in the former case, we could drop subscript $i$.
+$$f_{i,t+h|t} \equiv f_{i,t}(y_{t+h}|I_{i,t})$$
 
-$I_{i,t}$ is the information set available at time t for individual $i$.
-The information set can be also agent specific, therefore, it has subscript $i$.
-The specific content contained in $I_t$ varies from different models.
-Seemingly a simple and justified assumption is that $x_t \in  I_t$.
-This, however, may not be ture for all models.
-For instance, sticky expectation and rational inattention literature all predict that agents are not able to update new information instataneously.
-Thus the information set may not winclude the recent realization of the variable itself.
+$I_{i,t}$ is the information set available for individual $i$ at time t.
+The information set can be  agent specific, thus it has subscript $i$.
+The specific content contained in $I_t$ varies from different models of expectation.
+For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instataneously.
+So the information set may not contain the most recent realization of the variable of forecast $y_t$.
+\footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$.
+Examples of such include multi-prior or model uncertainty.
+\cite{xx}.
+}
 
-Assumption also needs to be made about the underlying model that generates the conditional density of the variables by agent $i$.
+Accordingly, h-period ahead mean forecast at $t$, denoted as $ y_{i,t+h|t}$, is the conditional expectation of $y_{t+h}$ by the agent $i$.
 
-Given the forecast density, the expectation of forecast at time $t$ is.
+$$y_{i,t+h|t} \equiv E_{i,t}(y_{t+h}) =\int f_{i, t+h|t} d y_{t+h}$$
 
-$$E_{i,t}(y_{t+h}|I_{i,t}) =\int \widehat f_{i,t}(y_{t+h}|I_{i,t})y_{t+h} d y_{t+h}\equiv \bar y_{i,t,t+h}$$
+Similarly, individual forecasting variance $\sigma_{i,t+h|t}$, hereafter termed as indiviual uncertainty in this paper, is the conditional variance.
 
-The forecasting variance is
+$$\sigma^2_{i,t+h|t} \equiv Var_{i,t}( y_{t+h} )$$
 
-$$Var_{i,t}(y_{t+h}|I_{i,t})=\int \widehat f_{i,t}(y_{t+h}|I_{i,t}) (y_{t+h} - \bar y_{i,t,t+h})^2d y_{t+h}$$
+Individual forecast error $FE_{i,t+h|t}$ is the difference of ex post realized value of $y_{t+h}$ and individual foreacast at time $t$.
 
-The true process of $y_{t}$ depends on the variables. Here, we consider a simple case where true process of $y_t$ is AR(1).
+$$FE_{i,t+h|t} = y_{i,t+h|t} - y_{t+h}$$
+
+The population analogues of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents.
+Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively.
+Hereafter, they are termed as population mean forecast, population uncertainty and population forecast error, respectively.
+In addition, disagreements is defined as the cross-sectional variance of mean forecasts of individual agents.
+Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $.
+To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.
+\footnote{This is the same termiology used by \cite{xx}.}
+
+In summary, we have 3 individual moments and 4 population moments listed in below.
+
+\begin{table}[]
+	\centering
+		\caption{Definition and Notation of Moments}
+	\begin{tabular}{ll}
+
+		\hline 
+		Individual Moments                                  & Population Moments                             \\
+		\hline 
+	Mean orecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
+		Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
+		Uncertainty: $\sigma^2_{i,t+h|t}$         & Average uncertainty:  $\bar \sigma^2_{i,t+h|t}$ \\
+		& Disagreements:  $\overline{Disg}_{t+h|t}$       \\
+		\hline 
+	\end{tabular}
+\end{table}
+
+Finally, we assume the underlying true process of $y_{t}$ is $AR(1)$ with persistency parameter $0<\rho <1$ and i.i.d. shock $\omega_t$.
 
@@
 
-\subsubsection{Individual moments}
+In the full information rational expectation (FIRE) benchmark,  we assume all agents perfectly observe $y_t$ at time $t$ and understand the true process of $y$.
+Therefore, individual forecast is $\rho^h y_t $.
+This is also shared by all agents.
+Therefore, it is also equal to average forecast.
 
-Full information rational expectation implies $y_t \in I_t$
+Both individual and population forecast errors are simply the realized shocks between $t+1$ to $t+h$.
 
-\textbf{Expectation}
-$$E_{i,t}(y_{t+h}|y_t) = E_{i,t}(y_{t+h}|y_t) = \rho^h y_t $$
+$$\overline{FE}_{i,t+h|t} = \sum^{h-1}_{s=1} \rho^s \omega_{t+h-s}$$ It is easy to see that the forecast error is orthogonal to information available till time $t$.
+This provides the a well known null hypothesis of FIRE.
+\cite{xx}
 
-\textbf{Variance} 
-$$Var_{i,t}(y_{t+h}|y_t) = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+The second testable null hypothesis of FIRE here is that forecast errors at two points of time $h$ or more periods apart are not serially correlated.
+This is not the case within $h$ periods as the realized shocks in overlapping periods enter both forecast errors.
 
-Ex post forecast error of individual i $$FE_{i,t} = y_{t+h} - E_{i,t}(y_{t+h}|y_t) = \sum^h_{s=1} \rho^s \omega_{t+h-s}$$ has is mean zero and orthogonal to information at time $t$.
+$$Cov(\overline{FE}_{t+h|t}, \overline{FE}_{t+s+h|t+s}) = 0 \quad \forall s \geq h$$
 
-\subsubsection{Population moments}
+The predictions holds at both individual and population levels.
 
-A special case below.
+Another hypothesis test of FIRE relies upon disagreements.
+\footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements of inflation uses consumers and professional forecasters' survey.
+} As agents perfect update the same information, there is no disagreements at any point of the time.
+
+$$\overline{Disg}_{t+h|t}=0 \quad \forall t$$
+
+A corollary is that disagreements do not respond to realized shocks any any point of the time.  Empricial tests of this kind include \cite{xx}.\cite{xx} etc.
+
+In addition to forecast error and disagreements, FIRE also predicts that all individual shares the same degree of uncertainty.
+The same degree of uncertainty simply comes from uncertainty about future unrealized shocks between $t$ and $t+h$.
+In \cite{}'s termology, not only all agents agree about the mean forecast, but also agree about the uncertainty according to FIRE.
+
+$$\bar \sigma^2_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+
+The time series pattern of uncertainty according to FIRE is less obvious.
+Weather it is time variate depends on if the variance of the shocks $\omega_t$ is time varying.
+Although in our baseline case we make such an assumption, in general it may not be true.
+
+It turns out, however, the serial correlation of uncertainty across different horizons of forecasting does follow testable pattern according to FIRE.
+In particular, consistent with our current notation, let us denote the forecast of $y_{t+h}$ over horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$.
+
+$$\bar \sigma^2_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+
+As the forecasting horizon decreases relative to a given future point of time, there is a pure efficiency gain or reduction in uncertainty as more and more shocks have realized.
+So the uncertainty should drop unambigously.
+
+Quanlitatively, $\bar \sigma^2_{t+h|t+k}$ should be smaller than $\bar \sigma^2_{t+h|t}$ $\forall 1<k\leq h$.
+
+Compared to other null hypotheses discussed above, this is a weaker test.
+It is true that rational forecasting relies upon utilizing all the information available at any point of time in the most efficient way.
 
 \subsection{Sticky Expectation}
+
+*****************************************************
 

### 2019-06-19 paper/Draft.tex
Furher's RE tests are twofold. 1. Fixing terminate date and test of revision is efficient.2.weak on testing difference in fix-horizon forecast depends on past information with coeff big enough.

@@
 Another hypothesis test of FIRE relies upon disagreements.
-\footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements of inflation uses consumers and professional forecasters' survey.
+\footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey.
 } As agents perfect update the same information, there is no disagreements at any point of the time.
@@
 So the uncertainty should drop unambigously.
-
-Quanlitatively, $\bar \sigma^2_{t+h|t+k}$ should be smaller than $\bar \sigma^2_{t+h|t}$ $\forall 1<k\leq h$.
+Quanlitatively, this implies that $\bar \sigma^2_{t+h|t+k} < \bar \sigma^2_{t+h|t}$ $\forall 1<k\leq h$.
 
 Compared to other null hypotheses discussed above, this is a weaker test.
-It is true that rational forecasting relies upon utilizing all the information available at any point of time in the most efficient way.
+It is true that rational foreacsting implies reduction in uncertainty with shorter horizon.
+But there is no direct test if the drop in uncertainty is efficient enough so as to be consistent with FIRE.
 

### 2019-06-20 paper/Draft.tex
drafting till SE. equations needs to be checked

@@
 To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.
-\footnote{This is the same termiology used by \cite{xx}.}
+\footnote{This is the same terminology used by \cite{xx}.}
 
-In summary, we have 3 individual moments and 4 population moments listed in below.
+In summary, we have 3 individual moments and 4 population moments listed in below in Table \ref{MomSum}.
 
-\begin{table}[]
+\begin{table}[]\label{MomSum}
 	\centering
@@
 		\hline 
-	Mean orecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
+	Mean forecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
 		Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
@@
 
-\subsection{Full-information rational expectation benchmark }
+\subsection{Benchmark of full-information rational expectation(FIRE)}
 
-In the full information rational expectation (FIRE) benchmark,  we assume all agents perfectly observe $y_t$ at time $t$ and understand the true process of $y$.
-Therefore, individual forecast is $\rho^h y_t $.
-This is also shared by all agents.
+ In the FIRE benchmark,  it is assumed that all agents perfectly observe $y_t$ at time $t$ and understand the true process of $y$.
+Therefore, individual forecast is $\rho^h y_t $, which is shared by all agents.
 Therefore, it is also equal to average forecast.
@@
 
-$$\overline{FE}_{i,t+h|t} = \sum^{h-1}_{s=1} \rho^s \omega_{t+h-s}$$ It is easy to see that the forecast error is orthogonal to information available till time $t$.
+$$\overline{FE}^{*}_{i,t+h|t} = \sum^{h-1}_{s=1} \rho^s \omega_{t+h-s}$$
+
+I use supscrit of $*$ to denote all the moments according to FIRE.
+It is easy to see that the forecast error is orthogonal to information available till time $t$.
 This provides the a well known null hypothesis of FIRE.
@@
 
-The second testable null hypothesis of FIRE here is that forecast errors at two points of time $h$ or more periods apart are not serially correlated.
+The second implication from FIRE here is that forecast errors of non-overlapping horizon forecasts are not correlated.
+For instance, forecast error at time $t$ and that at time $t+h$ or further are not serially correlated.
 This is not the case within $h$ periods as the realized shocks in overlapping periods enter both forecast errors.
 
-$$Cov(\overline{FE}_{t+h|t}, \overline{FE}_{t+s+h|t+s}) = 0 \quad \forall s \geq h$$
+$$Cov(\overline{FE}^{*}_{t+h|t}, \overline{FE}^{*}_{t+s+h|t+s}) = 0 \quad \forall s \geq h$$
 
-The predictions holds at both individual and population levels.
-
-Another hypothesis test of FIRE relies upon disagreements.
+FIRE also has predictions about  population disagreements.
 \footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey.
@@
 
-$$\overline{Disg}_{t+h|t}=0 \quad \forall t$$
+$$\overline{Disg}^{*}_{t+h|t}=0 \quad \forall t$$
 
-A corollary is that disagreements do not respond to realized shocks any any point of the time.  Empricial tests of this kind include \cite{xx}.\cite{xx} etc.
+A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empricial tests of this kind include \cite{xx}.\cite{xx} etc. }
 
-In addition to forecast error and disagreements, FIRE also predicts that all individual shares the same degree of uncertainty.
-The same degree of uncertainty simply comes from uncertainty about future unrealized shocks between $t$ and $t+h$.
-In \cite{}'s termology, not only all agents agree about the mean forecast, but also agree about the uncertainty according to FIRE.
+In addition to forecast error and disagreements, according to FIRE all individual shares the same degree of uncertainty.
+The uncertainty simply comes from uncertainty about future unrealized shocks between $t$ and $t+h$.
+To put it another way, according to FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \cite{}'s terminology.}
 
-$$\bar \sigma^2_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+$$\bar \sigma^{*2}_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
 
-The time series pattern of uncertainty according to FIRE is less obvious.
-Weather it is time variate depends on if the variance of the shocks $\omega_t$ is time varying.
+The time series behavior of uncertainty according to FIRE is less obvious.
+Weather it is time-variant depends on if the variance of the shocks $\omega_t$ is time varying.
 Although in our baseline case we make such an assumption, in general it may not be true.
+\footnote{\cite{xx} on time-varying volatility.}
 
-It turns out, however, the serial correlation of uncertainty across different horizons of forecasting does follow testable pattern according to FIRE.
+In the same time, the serial correlation of uncertainty across different horizons of forecasting does follow testable pattern according to FIRE.
 In particular, consistent with our current notation, let us denote the forecast of $y_{t+h}$ over horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$.
 
-$$\bar \sigma^2_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+$$\bar \sigma^{*2}_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
 
@@
 So the uncertainty should drop unambigously.
-Quanlitatively, this implies that $\bar \sigma^2_{t+h|t+k} < \bar \sigma^2_{t+h|t}$ $\forall 1<k\leq h$.
 
-Compared to other null hypotheses discussed above, this is a weaker test.
+An equivalent interpretation to this is through the perspective of revision.
+Defining the forecast revision as the difference of different vintages of foreacsts fixing the terminate date, the revision in uncertainty should be always negative and the drop should be exactly equal to discounted variance of the realized shocks.
+\footnote{Compared to other null hypotheses discussed above, this is a weaker test.
 It is true that rational foreacsting implies reduction in uncertainty with shorter horizon.
 But there is no direct test if the drop in uncertainty is efficient enough so as to be consistent with FIRE.
+}
 
-\subsection{Sticky Expectation}
+$$\bar \sigma^{*2}_{t+h|t+1} - \bar \sigma^{*2}_{t+h|t} = - \rho^{2h}\sigma^2_\omega$$
 
-*****************************************************
+\subsection{Sticky Expectation (SE)}
 
-Agent does not update information instantaneously, instead at a Possion rate $\lambda$.
-Specificaly, at any point of time $t$, the agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.
+The theory of sticky expectation (\cite{xx}, \cite{xx} ), regardless of its different microfoundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
+One of the most tractable models assume there is a homogenous Possion rate $\lambda$ of updating among the population.
+Specificaly, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.
 
@@
 
-For an individual whose most recent update occurs at $\tau$ period before, $I_{i,t|t-\tau} = I_{i,t-\tau} = y_{t-\tau}$. Thus
+Denote the mean forecast of a non-updater since $t-\tau$ as $y_{i,t+h|t-\tau}$ since her forecast conditions upon the information up till $t-\tau$.
 
-$$E_{i,t|t-\tau}(y_{t+h}|I_{i,t}) = E_{i,t}(i,y_{t+h}|y_{t-\tau}) = \rho^{h+\tau} y_{t-\tau}$$
+$$y_{i,t+h|t-\tau} = \rho^{h+\tau} y_{t-\tau}$$
 
-$$Var_{i,t|t-\tau}(y_{t+h}|I_{i,t}) = Var_{i,t}(y_{t+h}|y_{t-\tau}) = \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}$$
+Now her information set is not up to date, the uncertainty to a non-updater is higher than an updater and it increases with the duration of non-updating $\tau$.
 
-$Var_{i,t|t-\tau}(y_{t+h}|_{i,t})$ increases as $\tau$ increases. The model collapses to full-information rational expectation if $\tau=0$ for all individuals.
+$$\sigma^2_{i,t|t-\tau}= \sum^{h+\tau}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
 
-Now, we turn to the case when agent updates infrequently.
+In FIRE, updating at each period $t$ resolves only the uncertainty about the shocks realizing in $t$.
+In constrast, in SE each updating resolves the uncertainty about all the realized shocks since last update.
+Fixing the terminate date, i.e.
+forecasting  $y_{t+1}$ at time $t$ relative to forecasting $y_{t+1}$ at $t-\tau$, the revision in uncertainty is
 
-\begin{itemize}
-\item When the update happens, the variance responds substantially.
+$$\sigma^2_{i,t+1|t} - \sigma^2_{i,t+1|t-\tau} = \rho^{2} \sigma^2_{\omega} - \sum^{\tau+1}_{s=1}\rho^{2s} \sigma^2_{\omega} = -\sum^{\tau+1}_{s=2} \rho^{2s}\sigma^2_{\omega}$$
 
-$$Var_{i,t}(y_{t+h}|y_t) - Var_{i,t|t-\tau}(y_{t+h}|y_{t-\tau}) = \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega} - \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} = \sum^{\tau}_{s=0} \rho^{2s}\sigma^2_{\omega}$$
+FIRE assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in previous period.
+So setting $\tau =1$ in above equation gives the reduction in uncertainty in FIRE.
+One can easily see that the reduction in ucnertainty is greater in SE for any $\tau>1$ than FIRE.
 
-\item When the update does not happen, the variance responds little.
-
-$$Var_{i,t|t-\tau-1}(y_{t+h}|y_{t-\tau-1}) - Var_{i,t|\tau}(y_{t+h}|y_{t-\tau}) = \sigma^2_{\omega}$$
-
-At individual level, it is hard to recover the information rigidity parameter $\lambda$ directly.
-One testable prediction of information rigidity is that the change in forecast variance varies substantially depending on if updated or not.
-The longer period for which the agent stays unupdated(greater $\tau$), the bigger the change is in the forecasting variance.
-
-However, the difference in average responses in variance to new information may speak to potential heterogeneity in information rigidity.
+In summary, the key difference between FIRE and SE with respect to behavior of uncertainty is that the later does not reduce uncertainty  as efficiently as in the former primarily because of the rigidity incorporating new information.
+One qualitative pattern from this difference is that any evidence of ambiguous pattern  or non-negative revision in uncertainty is inconsistent with FIRE.
+\footnote{Because of this, the difference in average responses in variance to new information may speak to potential heterogeneity in information rigidity.
 According to the theory above, higher information rigidity implies high volatility of variance responses.
-\end{itemize}
+}
 
@@
 
-\begin{enumerate}	
-\item Average forecast
+It is important to note that the rigidity in updating according to SE cannot be systamatically observable in the individual level, both in terms of forecasts errors and uncertainty.
+This is because the behaviors of each individual foreacst specifically depends on if the she updates or not in that period.
 
-The mean forecast across population is a weighted average of past rational expectations
+Relying upon the Law of Large Numbers, we can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$.
+\footnote{\cite{carroll2003macroeconomic} is one notable example of this.}
+
+One well known prediction from SE literature is that the average foreacast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
+\footnote{See \cite{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$.
+Setting $\lambda=1$, then the SE collapses to FIRE and the average forecast is equal to $y$'s long-run mean of zero.
 
@@
 \begin{aligned}
-\bar E_t(y_{t+h}) & = \lambda \underbrace{E_t(y_{t+h})}_{\textrm{rational expectation at t}} + (1-\lambda) \underbrace{\bar E_{t-1}{y_{t+h}}}_{\textrm{average expectation at} t-1} \\
-& = \lambda E_t(y_{t+h}) + (1-\lambda) (\lambda E_{t-1}(y_{t+h})+ (1-\lambda) \bar E_{t-2}(y_{t+h}))... \\
-& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s E_{t-s}(y_{t+h}) \\
+\bar y_{t+h|t} & = \lambda \underbrace{y^*_{t+h|t}}_{\textrm{rational expectation at t}} + (1-\lambda) \underbrace{\bar y_{t+h|t-1}}_{\textrm{average forecast at } t-1} \\
+& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s y^*_{t+h|t-s} \\
 & = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s \rho^{s+h}y_{t-s}
@@
 
-The change in average forecast is
+It is also easy to show that the average forecast errors are serially correlated.
+Setting $\lambda=1$, then the SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully respond to newly realized shocks at time $t$.
+\footnote{Need to check if is revision or change from}
 
@@
 \begin{aligned}
-\Delta \bar E_t(y_{t+h})&  = (1-\lambda) \Delta \bar E_{t-1}(y_{t+h}) + \lambda (E_t(y_{t+h}) - E_{t-1}(y_{t+h})) \\ 
-& = (1-\lambda) \Delta \bar E_{t-1}(y_{t+h}) + \lambda \rho^h \omega_t 
+\overline{FE}_{t+h|t}  = (1-\lambda) \overline {FE}_{t+h-1|t-1} + \lambda \rho^h \omega_t 
 \end{aligned}
@@
 
-This implies the change in average forecast is serially correlated, depending on the information rigidity, i.e.
-lower $\lambda$ implies higher serial correlation.
-Also lower $\lambda$ implies the expectation underreact to the shocks at $t$.
-
-\item Cross-sectional disagreements
-
-According to information rigity model, if everyone is instantaneously udpated, there should not be disagreements.
-In general, the dispersion in forecasting is non-zero because of different lags in updating.
-One can also derive variance of forecasts across agents at time $t$
+\cite{coibion2012can} also derives predictions about the disagreements in rigidity models.
+Unlike zero disagreements in FIRE, SE is characterized by non-zero dispersion in forecasting because of different lags in updating across populations.
+\footnote{need to check if correct also.}
 
@@
 \begin{aligned}
-Var_t(E_{i,t}(y_{t+h}) ) & = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^{\tau} (E_{t|t-\tau}(y_{t+h}) - \bar E_t(y_{t+h}))^2  
+\overline{Disg}_{t+h|t} & = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^{\tau} (y_{t+h|t-\tau} - \bar y_{t+h|t }))^2  
 \end{aligned}
@@
 
-\begin{eqnarray}
-\begin{aligned}
-\Delta Var_{t+1}(E_{i,t+1}(y_{t+h})) = \textrm{change due to new updaters} + \textrm{shock at time } t+1 
-\end{aligned}
-\end{eqnarray}
-
-Notice the change is positive, meaning the dispersion rises in response to a shock. Importantly, the increase is the same regardless of the realization of the shock.
-
-More generally, we can derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.
+In SE, disagreements rise after realization of the shock and gradually returns to its steady state level.
+In the same time, it does not depend upon the particular realization of the shock.
+\cite{coibion2012can} derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.
 
@@
 
-A shock increases the disagreements across agents and then it gradually returns to its steady state level.
-
-\item Average variance
-
-Since we have individual level variance, we can also derive average variance of the population.
-Taking the average of variance across individual agents at time $t$.
-Here I use the $\bar{}$ to represent population mean of variance.
+Finally, SE predicts a sluggish behavior of revision in uncertainty with a similar spirit of forecast errors.
 
@@
 \begin{aligned}
-\bar Var_{t}(y_{t+h}) & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who does not update until }t-\tau} \underbrace{Var_{t|t-\tau}(y_{t+h})}_{\text{ Variance of most recent update at }t-\tau} \\
+\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
 & = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
@@
 
-Correspondingly, the change in average uncertainty will be
+Correspondingly, the revision in average uncertainty will be below. \footnote{Make sure you have clarify the difference between revision and change.}
 
@@
 \begin{aligned}
-\Delta \bar Var_{t}(y_{t+h}) & = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} - \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} = 0
+\bar \sigma^2_{t+h|t+1} - \bar \sigma^2_{t+h|t} = (1-\lambda)(
+\bar \sigma^2_{t+h|t} - \bar \sigma^2_{t+h|t-1}) -\lambda \rho^{2h} \sigma^2 
 \end{aligned}
@@
 
-An information rigidity model based on fixed Poisson update rate predicts that the average variance does not change over time. This can be tested.
-
-\end{enumerate}
+Revision in uncertainty is now a weighted average of most recent resolutions of shocks and its lagged counterpart.
+In particular, the second component is the information gain from most recent realization of the shock underweighted ($\lambda<1$).
+The first component is the inefficient sourced from stickiness of updating The higher rigidity (lower $\lambda$), the efficieny gain or uncertainty reduction from one vintage of forecast to the next is less compared to its FIRE correspondents.
 
@@
 \item Individual variances changes non-monotonically depending on if updating. Always increase with arrival of new information. 
-\item Population mean of forecast responds with lags. Change is serially correlated. 
-\item Population dispersion of forecasts rise in response to new shocks and return to steady state level gradually. 
-\item Population average variance does not change over time. 
+\item Population mean forecast responds shocks with lags. 
+\item Forecast errors are serially correlated. 
+\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
+\item Population average uncertaity revision is serially correlated and underreacts to volatility of the shocks.
+
 \end{itemize}

### 2019-06-20 paper/Draft.tex
keep drafting till summary of SE and NI. IR plots need to be regenerated.NI part needs to be polished.

@@
 \usepackage{adjustbox}
+\usepackage{graphicx}
 
@@
 Unlike zero disagreements in FIRE, SE is characterized by non-zero dispersion in forecasting because of different lags in updating across populations.
-\footnote{need to check if correct also.}
+\footnote{need to check if correct also.
+Need to derive change in disagreements.}
 
@@
 
-From time $t$ to $t+1$, the change in dispersion comes from two sources.
+From time $t$ to $t+1$, the change in disagreements comes from two sources.
 One is newly realized shock at time $t+1$.
@@
 
-Finally, SE predicts a sluggish behavior of revision in uncertainty with a similar spirit of forecast errors.
+Finally, SE predicts an sluggish inefficiency in revision in uncertainty.
+Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.
 
@@
 
-Correspondingly, the revision in average uncertainty will be below. \footnote{Make sure you have clarify the difference between revision and change.}
+Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibites serial correlation described as below in a similar spirt of forecast errors.
+It is equal to a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart.
+\footnote{Make sure you have clarify the difference between revision and change.}
 
@@
 
-Revision in uncertainty is now a weighted average of most recent resolutions of shocks and its lagged counterpart.
-In particular, the second component is the information gain from most recent realization of the shock underweighted ($\lambda<1$).
-The first component is the inefficient sourced from stickiness of updating The higher rigidity (lower $\lambda$), the efficieny gain or uncertainty reduction from one vintage of forecast to the next is less compared to its FIRE correspondents.
+ In particular, the second component is the information gain from most recent realization of the shock underweighted by $\lambda<1$.
+The first component is the inefficiency sourced from stickiness of updating.
+The higher rigidity (lower $\lambda$), the smaller the efficieny gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.
 
-\subsubsection{Summary of predictions of information rigidity}
+\subsubsection{Summary of predictions of SE}
 
 \begin{itemize}
-\item Individual expectation may or may not change depend upon if updating. 
-\item Individual variances changes non-monotonically depending on if updating. Always increase with arrival of new information. 
-\item Population mean forecast responds shocks with lags. 
+\item Individual uncertainty need not unambiguously drop with shorter horizon. 
+\item Population mean forecast paritially responds to shocks and with lags. 
 \item Forecast errors are serially correlated. 
@@
 
-\subsection{Noisy information}
+\subsection{Noisy information(NI)}
 
-A class of so-called noisy information model describes the expectation formation as a process extracting or filtering true fundamental state variable $y_t$ from a sequence of realized signals.
+A class of noisy information models (\cite{},\cite{}) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
 The starting assumption is that agent cannot observe the true variable perfectly.
@@
 
-We assume agent $i$ observe two signals $s^{pb}$ and $s^{pr}_i$, with $s^{pb}$ being public signal common to all agents, and $s^{pr}_i$ private signals being individual specific.
-The generating process of two signals are
+We assume agent $i$ observe two signals $s^{pb}$ and $s^{pr}_i$, with $s^{pb}$ being public signal common to all agents, and $s^{pr}_i$ private signals being individual specific with subscript $i$.
+The generating process of two signals are assumed to be the following.
 
@@
 
-We can stack the two signals into one vector $s_{i,t} = [s^{pb}_t,s^{pr}_{i,t}]'$ and $v_{i,t}= [\epsilon_t,\xi_{i,t}]'$. So in a compact form, it can be written as
+Stacking the two signals into one vector $s_{i,t} = [s^{pb}_t,s^{pr}_{i,t}]'$ and $v_{i,t}= [\epsilon_t,\xi_{i,t}]'$, the equations above can be rewritten as
 
@@
 
-In our general framework, the noisy information implies that the information set $I_{i,t}$ available to individual $i$ at time $t$ only includes past and recent realizations of the signals.
-The individual density forecast of $y_{t+h}$ is
-
-$$\widehat f_{i,t}(y_{t+h}|I_{i,t}) = \widehat  f_{i,t}(y_{t+h}|s_{i,t},s_{i,t-1}...) \equiv \widehat  f_{i,t|t}(y_{t+h})$$
-
-We use $t|k$ to denote the moments at time t based on information(signals) till time $k$.
-
-Then we are ready to apply Kalman Filter in this context. The posterior distribution of $y_{t}$ after seeing all signals till $t$ is
-
-\begin{eqnarray}
-\widehat  f_{i,t|t}(y_{t+h})  \sim  N(E_{i,t|t}(y_{t+h}), Var_{i,t|t}(y_{t+h}))
-\end{eqnarray}
-
-where the expectation and variances are functions of noisiness of signals and fundamentals. The expectation also depends on the realized values. But this is not the case for variance.
-
 \subsubsection{Individual moments }
 
-\begin{enumerate}
+Now any agent trying to forecast future $y$ has to form her expectation of the contemporaneous $y$.
+Denote it as  $y_{i,t|t}$, which needs to be inferred from the signals to agent $i$.
+The agent's best h-period ahead forecast is simply iterated $h$ periods forward based on the AR(1) process and it is equal to $\rho^h y_{i,t|t}$.
+This is the same as FIRE.
 
-\item Expectation
-
-Now any agent trying to forecast future variables will have to form her expectation of the contemporaneous state variable, $E_{i,t|t}(y_t)$.
-Then the best h-period ahead forecast is simply iterated h periods forward based on the AR(1) process.
-
-Thus, we first work out $E_{i,t|t}(y_t)$.
+What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$.
+Specificaly, mean forecast of individual $i$ is the posterior mean of based on her prior and realized signals $s_i$.
 
@@
 \begin{aligned}
-E_{i,t|t}(y_{t}) 
-& =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
-& = (1-PH) E_{i,t|t-1}(y_{t}) + Ps_{i,t} \\
-& = (1-PH) E_{i,t|t-1}(y_{t}) + PH y_{i,t} + P v_{i,t} \\
-\text{where the Kalman gain }  & P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} \\
-\text {where } & \Sigma^y_{i,t|t-1} \text{ is the variance of } y_t \text{ based on prior belief}\\
-\text {and } & \Sigma^v =  \left[ \begin{matrix} 
-  \sigma^2_{\epsilon} &  0 \\ 0 & \sigma^2_\xi \end{matrix}\right] 
+y_{i,t|t}  
+& =  \underbrace{y_{i,t|t-1}}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
+& = (1-PH) y_{t|t-1} + Ps_{i,t} \\
+& = (1-PH) y_{t|t-1} + PH y_{i,t} + P v_{i,t} 
 \end{aligned}
@@
 
-The h-period ahead forecast is
+where the Kalman gain
 
@@
 \begin{aligned}
-E_{i,t|t}(y_{t+h}) & = \rho^{h}E_{i,t|t}(y_{t+h}) 
+ P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} 
  \end{aligned}
@@
 
-Individual forecast partially responds to new signals, i.e. $P<1$. $P=1$ is a special case when both signals are perfect thus $\Sigma^v = 0$, then the formula collapses to full rational expectation.
-
-Now, the rigidity parameter is governed by $1-PH$ with multiple signals.
-It is a function of variance of $y$ from the prior of previous period and noisiness of the signals.
-Therefore, it is time variant as the variance is updated by the agent each period.
-
-There are a few important distinctions between noisy information and sticky expectation.
-
-$\bullet$  First, the persistence of expectation exists at individual level.
-There is serially correlation between $E_{i|t|t}(y_t)$ and $E_{i,t|t-1}(y_{t})$, or more generally, between $E_{i,t|t}(y_{t+h})$ and $E_{i,t|t-1}(y_{t+h})$.
-This pattern can be only observed from population moments according to sticky expectation models.
-
-To see this, the change in individual forecast from $t-1$ to $t$ is
+and $\Sigma^y_{i,t|t-1}$  is the variance of  $y_t$ based on prior belief.
 
@@
 \begin{aligned}
-\Delta E_{i,t|t}(y_{t+h}) & = \underbrace{\rho^h (1-PH)\Delta E_{i,t-1|t-1}(y_{t})}_{\text{Lagged response}} + \underbrace{\rho^hPH \Delta y_{i,t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
+ \Sigma^v =  \left[ \begin{matrix} 
+  \sigma^2_{\epsilon} &  0 \\ 
+  0 & \sigma^2_\xi \end{matrix}\right] 
+\end{aligned}
+\end{eqnarray}
+
+Individual forecast partially responds to new signals, i.e. $P<1$. $P=1$ is a special case when both signals are perfect thus $\Sigma^v = 0$, then the formula collapses to FIRE.
+
+Now, the parameter that governs rigidity is $1-PH$.
+It is a function of priror uncertainty about $y$ and noisiness of the signals.
+It is time variant as the variance is updated by the agent each period.
+
+There are a few important distinctions between NI and SE.
+
+First, the serial correlation of forecast error exists at both individual and population level, while it is only observable in population moments according to SE.
+
+To see this, the change in individual forecast from $t-1$ to $t$ is \footnote{need to check.}
+
+\begin{eqnarray}
+\begin{aligned}
+\Delta y_{i,t+h|t} & = \underbrace{\rho^h (1-PH)\Delta y_{i,t+h|t-1}}_{\text{Lagged response}} + \underbrace{\rho^hPH \Delta y_{i,t|t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
 \end{aligned}
@@
 The serial correlation is $\rho^h(1-PH)$, it does not only depend on $PH$, but also the forecast horizon $h$.
-Therefore, one testable assumption is to see auto regression of change in forecast to see if the coefficient depends on horizon.
+As $\rho<1$, the rigidity declines with longer horizon.
+In this regard, the rigidity implied by NI and SE are different because the form is fixed and the later is horizon dependent.
 
-$\bullet$  Second, the expectation adjusts in each period as long as there is new information. In sticky expectation, however, the expectation adjusts only when the agent updates.
-
-\item Variance
+Second, the expectation adjusts in each period as long as there is new information. In sticky expectation, however, the expectation adjusts only when the agent updates.
 
@@
 
-There are a few important properties in the variance.
-
-- First, it does not depend on the realizations of the signal.
-
-- Second, it decreases unambigously from $t-1$ to $t$. To see this
+As in FIRE and SE, uncertainty itself does not depend upon the realization of the shocks or signals.
+The revision in uncertainy from time $t-1$ to $t$ fixing the terminate of the forecast date is negative  unambigously.
+To see this
 
@@
 
+But the efficiency gain in reduction of uncertainty depends upon the noisiness of the signals. As long as the signal is not perfect, forecast in NI is neither as efficient as FIRE.
+
 These two properties carry through to the h-period ahead forecast as well. As the forecast variance is the following
@@
 \begin{eqnarray}
-Var_{i,t|t} (y_{t+h}) = \rho^{2h} \underbrace{Var_{i,t}(y_{t})}_{\Sigma_{i,t|t}} + \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega}
+\Sigma_{i,t+h|t} = \rho^{2h} \underbrace{\Sigma_{i,t}}_{\Sigma_{i,t|t}} + \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Delta Var_{i,t|t} (y_{t+h}) = \rho^{2h}\Delta \Sigma_{i,t|t} - \rho^{2h} \sigma^2_{\omega}
+\Delta \Sigma_{i,t+h|t} = \rho^{2h}\Delta  \Sigma_{i,t|t}  - \rho^{2h} \sigma^2_{\omega}
 \end{eqnarray}
@@
 
-\end{enumerate}
-
 \subsubsection{Population moments}
-
-\begin{enumerate}
-
-\item Average forecast
 
@@
 
-\item Change in average forecast
+One of the major implications from NI models is that both individual forecast and ucnertainty behaves the same pattern as population forecasts.
 
-\begin{eqnarray}
-\begin{aligned}
-\Delta \bar E_t|t (y_{t+h}) & = \rho^h (1-PH) \Delta \bar E_{t-1}(y_{t+h}) + \rho^h P \Delta \epsilon_t
-\end{aligned}
-\end{eqnarray}
+In parituclar, the same as indivdiual forecast erro, average forecast errors have serial correlation with the same auto regression parameter $\rho^h(1-PH)$.
 
-Same to the individual forecast, the change in average forecasts has serial correlation with the same auto regression parameter $\rho^h(1-PH)$.
-
-\item Cross-sectional disagreements
-
-In this model, the only disagreements across agents come from the difference in realized private signals. Therefore, in short-cut, the disagreements are
-
-\begin{eqnarray}
-\begin{aligned}
-Var_t(y_{t+h}) & = E((E_{i,t|t}(y_{t+h}) - \bar E_t(y_{t+h}))^2) \\
-& = \rho^{2h} P^2_\xi \sigma^2_\xi  
-\end{aligned}
-\end{eqnarray}
-
-Several properties.
-
-$\bullet$ First, the disagreements increase with the forecast horizon. 
-$\bullet$  Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. 
-$\bullet$  Third, similar to sticky expectation model, the disagreements also increase with the rigidity parameter $P$ in this model.
-
-\item Change in disagreements
-
-\begin{eqnarray}
-\begin{aligned}
-\Delta Var_t(y_{t+h}) & = \rho^{2h}(1-\rho^2) P^2_\xi \sigma^2_\xi >0
-\end{aligned}
-\end{eqnarray}
-
-The disagreements increase as time goes from $t-1$ to $t$.
-Also, as the time approaches $t+h$, the disagreements increase.
-This seems counterintuitive.
-But the reason is that here the disagreenments always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.
-
-\item Average variance
-
-Since the variance does not depend on signals and the precision is the same aross the agents, average variance is equal to the variance of each individual.
+As to the uncertainty, as it does not depend on realized signals and the precision is the same aross all agents, average variance is equal to the variance of each individual.
 
@@
 
-Also, same as the individual variance, the variance unambiguiously drop as time goes by.
+Also, same as the individual variance, the variance unambiguiously drop in each vintage of revision.
+But since the signal is noisy, agents partially react to the news and uncertainty does not drop as efficiently as FIRE.
 
@@
 \end{eqnarray}
+
+NI also predicts non-zero disagreements in the presence of private signals.
+The behavior of disagreements across agents come from the difference in realized private signals.
+Specifically, it is equal to the following.
+
+\begin{eqnarray}
+\begin{aligned}
+\overline {Disg}_{t+h|t} = \rho^{2h} P^2_\xi \sigma^2_\xi  
+\end{aligned}
+\end{eqnarray}
+
+First, the disagreements increase with the forecast horizon.
+Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
+Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.
+
+The disagreements increase as time goes from $t-1$ to $t$.
+Also, as the time approaches $t+h$, the disagreements increase.
+This seems counterintuitive.
+But the reason is that here the disagreenments always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.
 
@@
 $\bullet$  Average variance declines unambiguously each period.
-\end{enumerate}
+
+\subsection{Comparing FIRE, SE and NI}
+
+Figure \ref{ir_popind} plots the impulse responses of individual and population moments of forecasts accroding to different theories.
+As we focus on the dynamics of revision as one approaches the terminate date, i.e.
+forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e.
+$y_{t+h}$,$y_{t+h+1}$.
+
+This is the most intuitively seen in the dynamics of uncertainty. In particular, as one appraoch the realization $t+h$, uncertainty necessarily drop for FIRE and attains zero at the last period.
+
+\begin{figure}[h]\ref{ir_popind}
+	\centering
+	\includegraphics[width=13cm]{figures/ir_indseni.png}
+	\includegraphics[width=13cm]{figures/ir_popseni.png} \\
+	\caption{Impulse responses of moments to a shock to inflation}
+\end{figure}
 

### 2019-06-21 paper/Draft.tex
Stylized Factts section half way. Focus on uncertainty. Three sets of graphs till now. Uncertainty and other moments. IQR of uncertainty. Histogram of Uncerainty.

@@
 
-\begin{figure}[h]\ref{ir_popind}
+\begin{figure}[h]\label{ir_popind}
 	\centering
@@
 
-\subsection{Other Theories}
+\subsection{Disucussion of other theories}
 
@@
 
-\subsection{Density Estimates}
+\subsection{Stylized Facts}
+
+\subsubsection{Different Moments}
+
+\begin{figure}[h]\label{UnceratitnyOtherMoments}
+	\centering
+	\includegraphics[width=6cm]{figures/fe_var2Q.png}
+	\includegraphics[width=6cm]{figures/var_disg2Q.png}\\
+	\smallskip
+	\includegraphics[width=6cm]{figures/fe_var3Q.png}
+	\includegraphics[width=6cm]{figures/var_disg3Q.png}\\
+	\smallskip	
+	\includegraphics[width=6cm]{figures/fe_var.png}
+	\includegraphics[width=6cm]{figures/var_disg.png}\\
+		\caption{Unceratinty and Other Moments}
+\end{figure}
+
+\begin{figure}[h]\label{IQR_Unceratitny}
+	\centering
+	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
+	\smallskip
+	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
+		\smallskip
+	\includegraphics[width=8cm]{figures/IQRvarSCEQ.png}\\
+	\caption{Dispersion in Mean Forecast and Unceratinty }
+\end{figure}
+
+\begin{figure}[h]\label{Unceratitny_Histogram}
+	\centering
+	\includegraphics[width=6cm]{figures/PRCCPIMean1_hist.png} 
+	\includegraphics[width=6cm]{figures/PRCCPIVar1_hist.png}  \\
+	\smallskip
+		\includegraphics[width=6cm]{figures/PRCPCEMean1_hist.png} 
+	\includegraphics[width=6cm]{figures/PRCPCEVar1_hist.png}  \\
+	\smallskip
+		\includegraphics[width=6cm]{figures/SCEMean1_hist.png} 
+	\includegraphics[width=6cm]{figures/SCEVar1_hist.png}  \\
+	\caption{Distribution of Mean Forecast and Uncertainty }
+\end{figure}
 

### 2019-06-21 paper/Draft.tex
Ready to plot histograms of revision in fore casts and uncertainty.

@@
 
+Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty asgainst forecast errors and disagreements.
+
+Once implication from FIRE is that all individuals not only agree on mean but also share same degree of uncertainty.
+While in fact, we observe long-lasting heterogeneity in uncertainty both from professional forecasters and households.
+Figure \ref{IQR_Unceratitny} show that there is  not only dispersion of individual forecasts i.e.
+disagreements, but alslo great heterogeneity in uncertainty.
+One stylized fact from these observations is that that the dispersion in ucnertainty seems consistent over time.
+
+Another prediction from FIRE is that there is unambigous uncertainty reduction as one appraoches to the date of realization.
+Figure \ref{RevisionHist} plots the average revision in forecasts and uncertainty.
+The the more negative the revision lies in, the more rational of the forecast.
+
 \begin{figure}[h]\label{UnceratitnyOtherMoments}
@@
 
+\begin{figure}[h]\label{RevisionHist}
+	\centering
+	\includegraphics[width=6cm]{figures/PRCCPIMeanRev_hist.png} 
+	\includegraphics[width=6cm]{figures/PRCCPIVarRev_hist.png}  \\
+	\smallskip
+	\includegraphics[width=6cm]{figures/PRCPCEMeanRev_hist.png} 
+	\includegraphics[width=6cm]{figures/PRCPCEVarRev_hist.png}  \\
+	\smallskip
+		\includegraphics[width=6cm]{figures/SCEMeanRev_hist.png} 
+	\includegraphics[width=6cm]{figures/SCEVarRev_hist.png}  \\
+	\caption{Distribution of Revision in Uncertainty}
+\end{figure}
+
 \subsection{Test of Null Hypothesis of Rational Expectation}

### 2019-06-21 paper/Draft.tex
Stacking all IRF plots. Replicating Coibion close enough.

@@
 
+In Figure \ref{ReplicateCoibionBefore2007}, I replicate the results from  \cite{coibion2012can}.
+The period is between 1987-2007.
+In the right column, I do the same exercise with monetary policy shocks.
+
+In Figure \ref{ReplicateCoibionpost2007}, I do the same exercise but include additional uncertainty. This is also the period when SPF provides density forecasts that allow me to estimate uncertainty.
+
+\begin{figure}[h]\label{ReplicateCoibionBefore2007}
+	\centering
+	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_nmp.png}  
+	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks.png} \\
+	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_nmp.png} 
+	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks.png}  \\
+	\smallskip
+	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp.png} 
+		\includegraphics[width=6cm]{figures/SPFFE_ashocks.png} \\
+	\smallskip
+	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
+		\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} 
+	\caption{ Replicating \cite{coibion2012can}: 1987-2007}
+\end{figure}
+
+\begin{figure}[h]\label{ReplicateCoibionpost2007}
+	\centering
+	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_nmp_post2007.png}  
+	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_post2007.png} \\
+	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_nmp_post2007.png} 
+	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_post2007.png}  \\
+	\smallskip
+	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp_post2007.png} 
+	\includegraphics[width=6cm]{figures/SPFFE_ashocks_post2007.png} \\
+	\smallskip
+	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp_post2007.png} 
+	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_post2007.png} \\
+	\smallskip 
+		\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp_post2007.png} 
+	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_post2007.png} 
+	\caption{ Replicating \cite{coibion2012can}: 2008-2019}
+\end{figure}
+
 \subsubsection{Additional Evidence from Uncertainty}

### 2019-06-21 paper/Draft.tex
Some outoutlines of the discussions about the graphs. hist of revision needs to made.

@@
 
+The left  three figures look into the relationship between forecast error and uncertainty. In general, one may expect that  greater ex ante uncertainty implies greater ex post forecast errors.
+
+Many literature use disagreements and uncertainty interchangably but they are different objects.
+From the graph, we can also see in general uncertainty captures different information from disagreements.
+This is more so in professional forecaster data.
+There is a more obvious correlation between disgreements and uncertainty.
+
 Once implication from FIRE is that all individuals not only agree on mean but also share same degree of uncertainty.
@@
 Figure \ref{IQR_Unceratitny} show that there is  not only dispersion of individual forecasts i.e.
-disagreements, but alslo great heterogeneity in uncertainty.
-One stylized fact from these observations is that that the dispersion in ucnertainty seems consistent over time.
+disagreements, but alslo notable heterogeneity in uncertainty.
+One stylized fact from these observations is that  the dispersion in ucnertainty seems persistent over time.
 

### 2019-06-21 paper/Draft.tex
First set of histograms of revisions in meanforecast and uncertainty

@@
 Another prediction from FIRE is that there is unambigous uncertainty reduction as one appraoches to the date of realization.
-Figure \ref{RevisionHist} plots the average revision in forecasts and uncertainty.
+Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty.
 The the more negative the revision lies in, the more rational of the forecast.
@@
 	\centering
-	\includegraphics[width=6cm]{figures/PRCCPIMeanRev_hist.png} 
-	\includegraphics[width=6cm]{figures/PRCCPIVarRev_hist.png}  \\
+	\includegraphics[width=6cm]{figures/PRCCPIMean_rv_hist.png} 
+	\includegraphics[width=6cm]{figures/PRCCPIVar_rv_hist.png}  \\
 	\smallskip
-	\includegraphics[width=6cm]{figures/PRCPCEMeanRev_hist.png} 
-	\includegraphics[width=6cm]{figures/PRCPCEVarRev_hist.png}  \\
+	\includegraphics[width=6cm]{figures/PRCPCEMean_rv_hist.png} 
+	\includegraphics[width=6cm]{figures/PRCPCEVar_rv_hist.png}  \\
 	\smallskip
-		\includegraphics[width=6cm]{figures/SCEMeanRev_hist.png} 
-	\includegraphics[width=6cm]{figures/SCEVarRev_hist.png}  \\
-	\caption{Distribution of Revision in Uncertainty}
+		\includegraphics[width=6cm]{figures/SCEMean_rv_hist.png} 
+	\includegraphics[width=6cm]{figures/SCEVar_rv_hist.png}  \\
+	\caption{Distribution of Revision in Forecasts}
 \end{figure}

### 2019-06-22 paper/Draft.tex
NI Theory Plot Remains Debugging but Still updated figures. Null test is to be done tmr.

@@
 
-\subsubsection{Replicating  \cite{fuhrer2018intrinsic}}
+In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section.
+I first reproduce the results from two papers, \cite{mankiw2003disagreement} and \cite{fuhrer2018intrinsic} and then proceed to show the results with the additional restrictions from ucnertainty.
+
+The first set of tests utilize the dynamics of forecast errors.
+First, the forecast error should be on average unbiased.
+The forecast error should converge to zero.
+Second, forecast errors of non-overlapping forecasting horizon are not serially correlated.
+Third, forecast errors should not be predicted by any information available at the time of forecast, including the forecast itself and other variable that is in the agent's information content.
+
+The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting}.
+In particular, I follow the model specifications in \cite{fuhrer2018intrinsic}.
+According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information.
+For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.
+A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
+
+\begin{table}[]\label{NullTestTable}
+	\caption{Test of Rationality and Efficicency}
+	\begin{tabular}{lll}
+
+		\hline 
+		& SCE & SPF        \\
+		\hline 
+		                                  &                             &             \\
+	\end{tabular}
+\end{table}
 

### 2019-06-22 workingfolder/python/Theories.py

@@ -302,13 +302,14 @@ for t in range(1,T):
     PopVarSE[t] = (1-λ)*PopVarSE[t-1] + λ*PopVarRE[t]
     #PopVarSE[t] = sum( [λ*(1-λ)**t*IndVarRE[s] for s in range(t)])
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## Noisy information parameters 
 
 H = np.asmatrix ([[1,1]]).T 
-sigma_eps = 0.1
-pb_pr_ratio = 1
-sigma_xi = sigma_eps/pb_pr_ratio
+sigma_eps = 0.00000000000001 # public signal
+sigma_xi =0.1
+#pb_pr_ratio = 1
+#sigma_xi = sigma_eps/pb_pr_ratio  # private signal
 
 s_pb = y+sigma_eps*np.random.randn(T)
 s_pr = y+sigma_xi*np.random.randn(T)
@@ -317,7 +318,7 @@ sigma_v =np.asmatrix([[sigma_eps**2,0],[0,sigma_xi**2]])
 
 nb_s=len(s) ## # of signals 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 # Noisy Information(NI)
 
 ## individual and population forecast 
@@ -370,65 +371,71 @@ PopVarNI = IndVarNI
 
 
 # +
+plt.style.use('ggplot')
 plt.figure(figsize=(12,12))
 plt.title("Real-time Forecast with Noisy Information",fontsize=13)
 
 plt.subplot(2,2,1)
 plt.title('Nowcast')
-plt.plot(y,'-',label=r'$y_t$')
-plt.plot(IndRTExpNI,'r*',label=r'$E_{i,t|t}(y_t)$')
+plt.plot(y,'-',label=r'$y_{t+k}$')
+plt.plot(IndRTExpNI,'r*',label=r'$y_{i,t|t}$')
 plt.plot(s_pb,'-.',label=r'$s^{pb}_t$')
 plt.plot(s_pr,'-.',label=r'$s^{pr}_{i,t}$')
-plt.legend(loc=0,fontsize=15)
+plt.legend(loc='best',fontsize=15)
 
 plt.subplot(2,2,2)
 plt.title('Forecast')
-plt.axhline(y[T-1],label=r'$y_{10}$',color='blue',linestyle='--')
[…]

### 2019-06-23 paper/Draft.tex
almost finish the theory graphs. Illustrating NI. Different rigidities. IR plots of Pop moms.

@@
 
+Figure \ref{IllustrateNI} illustrates both the signal extraction problem at each period of $t+k$ and how it is used to predict the prediction of $y_{t+h}$.
+
+\begin{figure}[h]\label{IllustrateNI}
+	\centering
+	\includegraphics[width=13cm]{figures/ni_illustration.png}  
+	\caption{Illustration Noisy Information}
+\end{figure}
+
 \subsubsection{Population moments}
@@
 
-Figure \ref{ir_popind} plots the impulse responses of individual and population moments of forecasts accroding to different theories.
+Figure \ref{ir_pop} plots the impulse responses of population moments of forecasts accroding to different theories.
 As we focus on the dynamics of revision as one approaches the terminate date, i.e.
@@
 
-\begin{figure}[h]\label{ir_popind}
+\begin{figure}[h]\label{ir_pop}
 	\centering
-	\includegraphics[width=13cm]{figures/ir_indseni.png}
-	\includegraphics[width=13cm]{figures/ir_popseni.png} \\
+	\includegraphics[width=14cm]{figures/ir_popseni.png} 
 	\caption{Impulse responses of moments to a shock to inflation}
+\end{figure}
+
+One of the common predictions of SE and NI is there is information rigidity or stickiness of expecatations.
+But both theory have suble difference in implied rigidity.
+I illustrate this in Figure \ref{rigidity}.
+One notable difference is that SE's rigidty is exogeously fixed.
+NI's rigidity is endogeously determined by the noisiness of the signals and it is time varying.
+
+\begin{figure}[h]\label{rigidity}
+	\centering
+	\includegraphics[width=13cm]{figures/rigidity.png} 
+	\caption{Rigidity from Two Models}
 \end{figure}
@@
 	\caption{Test of Rationality and Efficicency}
+	\centering 
 	\begin{tabular}{lll}

### 2019-06-23 workingfolder/python/Theories.py

@@ -197,19 +197,19 @@ import matplotlib.pyplot as plt
 import scipy as sp
 # %matplotlib inline
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## parameters 
 ρ = 0.9
-λ = 0.4
+λ = 0.25
 T = 11
 t_shock = 1
 h = T-1 
-σ = 0.01**0.5
-
+σ = 1
+sigma_y = np.sqrt(σ**2/(1-ρ**2))  # unconditional standard error 
 
 ## shocks
 shock = np.zeros(T)
-shock[t_shock] = 0.1
+shock[t_shock] = 1
 
 ## y_t
 y = np.zeros(T) 
@@ -227,11 +227,17 @@ for t in range(T):
 ## forecasting error    
 IndFERE = y[T-1] - IndExpRE
 
-## individual variance 
-
+## individual variance
 IndVarRE = np.zeros(T)
 for t in range(T):
-    IndVarRE[t] = σ**2*(ρ**2*(1-ρ**(2*(T-t-1))))/(1-ρ**2)
+    for i in range(T-t):
+        IndVarRE[t] += σ**2*ρ**(2*i)
+IndVarRE = IndVarRE-σ**2
+
+#IndVarRE2 = np.zeros(T)
+#for t in range(T):
+#    IndVarRE2[t] = σ**2*(ρ**2*(1-ρ**(2*(T-t-1))))/(1-ρ**2)
+#IndVarRE2 = np.zeros(T)
     
 ## population average 
 
@@ -302,169 +308,203 @@ for t in range(1,T):
     PopVarSE[t] = (1-λ)*PopVarSE[t-1] + λ*PopVarRE[t]
     #PopVarSE[t] = sum( [λ*(1-λ)**t*IndVarRE[s] for s in range(t)])
 
-# + {"code_folding": []}
-## Noisy information parameters 
 
-H = np.asmatrix ([[1,1]]).T 
-sigma_eps = 0.00000000000001 # public signal
-sigma_xi =0.1
-#pb_pr_ratio = 1
-#sigma_xi = sigma_eps/pb_pr_ratio  # private signal
+# + {"code_folding": [0]}
+## Noisy information(NI) 
 
-s_pb = y+sigma_eps*np.random.randn(T)
-s_pr = y+sigma_xi*np.random.randn(T)
-s = np.asmatrix(np.array([s_pb,s_pr]))  # signals 
[…]

### 2019-06-24 paper/Draft.tex
SPF FE and  Efficiency Results Both Ind and Pop

@@
 \begin{aligned}
-\bar E_{t|t} (y_{t+h}) & = \rho^h [(1-PH) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
-& = (1-PH) \bar E_{t-1}(y_{t+h}) + P [\epsilon_t, 0]' \\
-& = (1-PH) \bar E_{t-1}(y_{t+h}) + P \epsilon_t
+\bar y_{t+h|t} & = \rho^h [(1-PH) \underbrace{\bar  y_{t+h|t-1}}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
+& = (1-PH) \bar y_{t+h|t-1}+ P [\epsilon_t, 0]' \\
+& = (1-PH) \bar y_{t+h|t-1} + P \epsilon_t
 \end{aligned}
@@
 
-As to the uncertainty, as it does not depend on realized signals and the precision is the same aross all agents, average variance is equal to the variance of each individual.
-
-\begin{eqnarray}
-\begin{aligned}
-\bar Var_t (y_{t+h}) = \bar \Sigma^y_t
-\end{aligned}
-\end{eqnarray}
+As to the uncertainty, as it does not depend on realized signals and the precision is the same aross all agents, average variance $\bar \Sigma_{t+h|t}$ is equal to the variance of each individual.
 
@@
 \begin{eqnarray}
-\Delta Var_t(y_{t+h}) < 0 
+\bar \Sigma^2_{t+h|t} -  \bar \Sigma^2_{t+h|t-1}< 0 
 \end{eqnarray}

### 2019-06-24 paper/Draft.tex
Preparing 2 tables for null hypothesis test. FE and RV.

@@
 
-\begin{itemize}
+Professional Forecasters(SPF) and New York Fed Survey of Consumer Expectation(SCE).
 
-		\item \textbf{New York Fed Survey of Consumer Expectation}
-	\begin{itemize}
-			\item Include not only perceived probabilities of binary event as in Michigan Survey does, but also elicit densitity forecasts. 
-	\end{itemize}
-	\item \textbf{Professional Forecasters}
+The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both currenct year forecast and 1-year-ahead inflation foreacst each quarter.
 
-\end{itemize}
+SCE data, although each individual is surveyed for 12 months in a row, is only asked to forecast 1-year-ahead inflation.
+This is especially so in the density forecast.
+So we can only perform a weak test.
+
+We follow \cite{Manski} to estiamte the density distribution of each individual surveyee for SPF.
+New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty.
+Therefore, I directly use them.
+
+We drop the outliers of uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.
 

### 2019-06-24 workingfolder/python/InfShocks.py
Generate a monthly version of the inflation shocks from python.InfShocksM.dta.Started working on IndSCE do file.

@@ -748,12 +748,20 @@ os_dataM['OPShock_nm'] =  os_dataM['OPShock']/os_dataM['OPShock'].std()
 ## compute quarterly shock
 os_shockQ  = os_dataM.groupby(['quarter'], sort=False)['OPShock_nm'].max()
 
-## creating quarterly date index
+## creating quarterly date 
+os_datesM =  os_dataM['observation_date'].dt.year.astype(int).astype(str) + \
+         "M" + os_dataM['observation_date'].dt.month.astype(int).astype(str)
+os_datesM = dates_from_str(os_datesM)
 os_datesQ = os_dataM['quarter'].drop_duplicates()
 os_datesQ = dates_from_str(os_datesQ)
 
 ## prepare quarterly series 
 os_shockQ.index = pd.DatetimeIndex(os_datesQ,freq='Q')
+
+## save a monthly version 
+os_M = pd.DataFrame(os_dataM['OPShock_nm'].copy())
+os_M.columns=(['OPShock_nm'])
+os_M.index = pd.DatetimeIndex(os_datesM)
 
 ## merge with other shocks
 str_shocks_est = pd.concat([str_shocks_est,os_shockQ], join='inner', axis=1)
@@ -803,7 +811,26 @@ str_shocks_est['month']=str_shocks_est.index.month
 
 str_shocks_est.head()
 
-# + {"code_folding": []}
-### save shocks
+# + {"code_folding": [0]}
+### save shocks (quarterly)
 
-str_shocks_est.to_stata('../OtherData/InfShocks.dta')
+str_shocks_est.to_stata('../OtherData/InfShocks.dta')   # this is the quarterly version as tech shocks is in quarterly
+
+# + {"code_folding": [0]}
+### save shocks (monthly)
+
+## only merge op and monetary policy shocks 
+
+str_shocks_estM = pd.concat((os_M,mps_var),sort=True)
+str_shocks_estM = str_shocks_estM.drop(['quarter'],axis=1)
+
+## convert to numeric 
+str_shocks_estM['MP1']=pd.to_numeric(str_shocks_estM['MP1'],errors='coerce')   
+
+str_shocks_estM['ED4']=pd.to_numeric(str_shocks_estM['ED4'],errors='coerce')   
+
+str_shocks_estM['ED8']=pd.to_numeric(str_shocks_estM['ED8'],errors='coerce')   
+
+## save a monthly version shocks exl tech shocks.
+
[…]

### 2019-06-24 workingfolder/python/InfShocks.py
Monthly inflation shocks generated by Stata instead of Python. Need to be consistent in future

@@ -772,7 +772,7 @@ str_shocks_est.tail()
 # ### Monetary policy shocks 
 
 # + {"code_folding": []}
-## loading mp shocks data
+## loading mp shocks data 
 mps_data = pd.read_excel('../OtherData/2MPShocksJW.xls',sheet_name='data')
 mps_data['Date'] = pd.to_datetime(mps_data['Date'],format='%m/%d/%Y')
 mps_datesQ = mps_data['Date'].dt.year.astype(int).astype(str) + \
@@ -787,11 +787,13 @@ mps_var = mps_data[['quarter','MP1','ED4','ED8']]
 ## dates 
 mps_datesM = mps_data['Date'].dt.year.astype(int).astype(str) + \
          "M" + mps_data['Date'].dt.month.astype(int).astype(str)
-
 mps_datesM = dates_from_str(mps_datesM)
 
 ## monthly index 
 mps_var.index = pd.DatetimeIndex(mps_datesM)
+
+# multiple times of monetary policy within some quarters. Thus cumulative sum is taken as the shock of that quarter
+
 mps_shockQ  = mps_var.groupby(['quarter'], sort=False)[['MP1','ED4','ED8']].sum(axis=1)
 
 ## convert to numeric 
@@ -811,26 +813,7 @@ str_shocks_est['month']=str_shocks_est.index.month
 
 str_shocks_est.head()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### save shocks (quarterly)
 
-str_shocks_est.to_stata('../OtherData/InfShocks.dta')   # this is the quarterly version as tech shocks is in quarterly
-
-# + {"code_folding": [0]}
-### save shocks (monthly)
-
-## only merge op and monetary policy shocks 
-
-str_shocks_estM = pd.concat((os_M,mps_var),sort=True)
-str_shocks_estM = str_shocks_estM.drop(['quarter'],axis=1)
-
-## convert to numeric 
-str_shocks_estM['MP1']=pd.to_numeric(str_shocks_estM['MP1'],errors='coerce')   
-
-str_shocks_estM['ED4']=pd.to_numeric(str_shocks_estM['ED4'],errors='coerce')   
-
-str_shocks_estM['ED8']=pd.to_numeric(str_shocks_estM['ED8'],errors='coerce')   
-
-## save a monthly version shocks exl tech shocks.
-
[…]

### 2019-06-25 paper/Draft.tex
Add IQR var for SCE
SCE IR analysis results generated.But not debugged.

@@
 		\smallskip
-	\includegraphics[width=8cm]{figures/IQRvarSCEQ.png}\\
+	\includegraphics[width=8cm]{figures/IQRvarSCEM.png}\\
 	\caption{Dispersion in Mean Forecast and Unceratinty }
@@
 	\centering
-	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_nmp_post2007.png}  
-	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_post2007.png} \\
-	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_nmp_post2007.png} 
-	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_post2007.png}  \\
+	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_nmp_post2007.png}  
+	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_post2007.png} \\
+	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_nmp_post2007.png} 
+	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_post2007.png}  \\
 	\smallskip
@@
 
+\begin{figure}[h]\label{SCE_IR}
+	\centering
+	\includegraphics[width=3cm,height=2cm]{figures/CPIAU_ashocks_nmpM.png}  
+	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocksM.png} \\
+	\smallskip
+	\includegraphics[width=3cm,height=2cm]{figures/SCEFE_ashocks_nmpM.png} 
+	\includegraphics[width=6cm,height=2cm]{figures/SCEFE_ashocksM.png} \\
+	\smallskip
+	\includegraphics[width=3cm,height=2cm]{figures/SCEDisg_ab_ashocks_nmpM.png} 
+	\includegraphics[width=6cm,height=2cm]{figures/SCEDisg_ab_ashocksM.png} \\
+	\smallskip 
+	\includegraphics[width=3cm,height=2cm]{figures/SCEVar_ab_ashocks_nmpM.png} 
+	\includegraphics[width=6cm,height=2cm]{figures/SCEVar_ab_ashocksM.png} 
+	\caption{ Impulse Responses of Inflation and SCE Forecasts to Inflation Shocks}
+\end{figure}
+
 \subsubsection{Additional Evidence from Uncertainty}

### 2019-06-25 paper/Draft.tex
Efficiency test using FE table is in draft. Revision table remains to be added.

@@
 	\centering 
-	\begin{tabular}{lll}
-
+\begin{tabular}{llll}
 	\hline 
-		& SCE & SPF        \\
+	& SPF CPI          & SPF PCE          & SCE            \\
 	\hline 
-		                                  &                             &             \\
+	\multicolumn{4}{l}{Test 1: Bias}                                                           \\
+	\hline 
+	Constant                            & 0.122***         & 0.586***         & 2.220***       \\
+	& (0.017)          & (0.061)          & (0.019)        \\
+	\hline 
+	N                                   & 4697             & 1208             & 67380          \\
+	\hline 
+	\multicolumn{4}{l}{Test2: FE Depends on past information}                                  \\
+	\hline 
+	Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
+	& (0.020)          & (0.061)          & NA             \\
+	Constant                            & -0.655***        & -0.777***        & NA             \\
+	& (0.060)          & (0.116)          & NA             \\
+	\hline 
+	N                                   & 3429             & 1208             & NA             \\
+	$R^2$                 & 0.0721           & 0.118            & NA             \\
+	\hline 
+	\multicolumn{4}{l}{Test3: FE of non-overlapping forecast horizons are serially correlated} \\
+	\hline 
+	Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
+	& (0.020)          & (0.035)          & NA             \\
+	Constant                            & 0.145***         & 0.275***         & NA             \\
+	& (0.021)          & (0.035)          & NA             \\
+	\hline 
+	N                                   & 3356             & 1208             & NA             \\
+	$R^2$                   & 0.00591          & 0.00264          & NA             \\
+	\hline 
+	\multicolumn{4}{l}{Test4: Overlapping FE are only weakly serially correlated}                          \\
+	\hline 
+	Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
+	& (0.025)          & (0.037)          & (0.021)        \\
+	Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
+	& (0.027)          & (0.048)          & (0.046)        \\
+	Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
+	& (0.025)          & (0.038)          & (0.045)        \\
+	Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
+	& (0.019)          & (0.026)          & (0.097)        \\
+	\hline 
+	N                                   & 2536             & 1004             & 2836           \\
+	$R^2$                & 0.439            & 0.552            & 0.232    \\
+	\hline      
 \end{tabular}

### 2019-06-26 paper/Draft.tex
Debugged outliers of SPF that caused weired results for individual SPF. it was not so for Pop because I used the correct data.
Created positions for inf-var charts. polishing regression tables. mostly finished.

@@
 	\centering
-	\includegraphics[width=14cm]{figures/ir_popseni.png} 
+	\includegraphics[width=15cm]{figures/ir_popseni.png} 
 	\caption{Impulse responses of moments to a shock to inflation}
@@
 
-The left  three figures look into the relationship between forecast error and uncertainty. In general, one may expect that  greater ex ante uncertainty implies greater ex post forecast errors.
+The left  three figures look into the relationship between forecast error and uncertainty. One may expect that  greater ex ante uncertainty implies greater ex post forecast errors.
+
+Another widely spoken fact is that uncertainty is positively correlated with the level of the inflation. We look this hypothesis by ploting uncertainty against the realized inflation.
 
@@
 	\centering
-	\includegraphics[width=6cm]{figures/fe_var2Q.png}
-	\includegraphics[width=6cm]{figures/var_disg2Q.png}\\
+		\centering
 	\smallskip
-	\includegraphics[width=6cm]{figures/fe_var3Q.png}
-	\includegraphics[width=6cm]{figures/var_disg3Q.png}\\
+	\includegraphics[width=3.5cm]{figures/Inf_var2Q.png}
+	\includegraphics[width=3.5cm]{figures/fe_var2Q.png}
+	\includegraphics[width=3.5cm]{figures/var_disg2Q.png}\\
 	\smallskip
-	\includegraphics[width=6cm]{figures/fe_var.png}
-	\includegraphics[width=6cm]{figures/var_disg.png}\\
+	\includegraphics[width=3.5cm]{figures/Inf_var3Q.png}
+	\includegraphics[width=3.5cm]{figures/fe_var3Q.png}
+	\includegraphics[width=3.5cm]{figures/var_disg3Q.png}\\
+	\smallskip	
+	\includegraphics[width=3.5cm]{figures/Inf_var.png}
+	\includegraphics[width=3.5cm]{figures/fe_var.png}
+	\includegraphics[width=3.5cm]{figures/var_disg.png}\\
 		\caption{Unceratinty and Other Moments}
@@
 	\smallskip
-		\includegraphics[width=6cm]{figures/SCEMean1_hist.png} 
-	\includegraphics[width=6cm]{figures/SCEVar1_hist.png}  \\
+		\includegraphics[width=6cm]{figures/SCEmean_hist.png} 
+	\includegraphics[width=6cm]{figures/SCEvar_hist.png}  \\
 	\caption{Distribution of Mean Forecast and Uncertainty }
@@
 
+\newpage
+
+\begin{adjustbox}{angle=90}\label{RevEfficiency}
+	\begin{tabular}{lllllllll}
+		\hline 
+		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
+		\hline 
+		\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
+	                                            \hline 
+		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
+		\hline 
+		L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
+		&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
+		L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
+		&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
+		L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
+		&               &           &          & (0.048)  &               &           &           & (0.069)   \\
+		SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
+		&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
+		SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
+		&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
+		& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
+		Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
+		\hline 
+		N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
+		$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
+		\hline 
+		\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
+		\hline 
+		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
+		\hline 
+		L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
+		&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
+		L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
+		&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
+		L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
+		&               &           &          & (0.121)  &               &           &           & (0.149)   \\
+		Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
+		& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
+		\hline 
+		N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
+	$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
+		\hline 
+	\end{tabular}
+\end{adjustbox}
+
+\begin{adjustbox}{width={22cm},totalheight={12cm},angle=90}\label{WeakRevEfficiency}
+	\begin{tabular}{llllllllllllll}
+		\hline 
+		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
+		\hline 
+		\multicolumn{14}{l}{Test 3.
+Weak revision efficiency of change in forecast}                                                                                                                                    \\
+		\hline 
+		& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
+		\hline 
+		L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
+		&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                      &               & (0.015)   & (0.022)   & (0.037)   \\
+		L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
+		&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                      &               &           & (0.021)   & (0.031)   \\
+		L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\
+		&             &           &           & (0.032)   &               &           &           & (0.036)   &                      &               &           & (0.012)   & (0.027)   \\
+		&             &           &           &           &               &           &           &           & L4.InfExp\_Var\_ch   &               &           &           & -0.130*** \\
+		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.025)   \\
+		&             &           &           &           &               &           &           &           & L5.InfExp\_Var\_ch   &               &           &           & -0.058**  \\
+		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.018)   \\
+		&             &           &           &           &               &           &           &           & L6.InfExp\_Var\_ch   &               &           &           & -0.025    \\
+		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.012)   \\
+		Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant               & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
+		& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                      & (0.123)       & (0.110)   & (0.104)   & (0.163)   \\
+		\hline 
+		N                    & 1636        & 1430      & 1266      & 1141      & 1402          & 1190      & 1022      & 898       & N                    & 53016         & 43166     & 28850     & 14445     \\
+	$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ & 0.000         & 0.182     & 0.278     & 0.321     \\
+		\hline 
+		\multicolumn{14}{l}{Test 4. Weak revision efficiency of change in uncertainty}                \\
+		\hline                                                                                                                 
+		& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean change   & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean change   & t-1       & t-1- t-2  & t-1-t-3   \\
+		\hline 
+		L.InfExp\_Var\_ch    &             & -0.393**  & -0.568*** & -0.543**  &               & -0.444*** & -0.602*** & -0.658*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
+		&             & (0.136)   & (0.146)   & (0.177)   &               & (0.094)   & (0.127)   & (0.145)   &                      &               & -0.015    & -0.022    & -0.037    \\
+		L2.InfExp\_Var\_ch   &             &           & -0.322**  & -0.278*   &               &           & -0.289*   & -0.404**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
+		&             &           & (0.104)   & (0.132)   &               &           & (0.110)   & (0.137)   &                      &               &           & -0.021    & -0.031    \\
+		L3.InfExp\_Var\_ch   &             &           &           & 0.048     &               &           &           & -0.292    & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\
+		&             &           &           & (0.096)   &               &           &           & (0.154)   &                      &               &           & -0.012    & -0.027    \\
+		&             &           &           &           &               &           &           &           & L4.InfExp\_Var\_ch   &               &           &           & -0.130*** \\
+		&             &           &           &           &               &           &           &           &                      &               &           &           & -0.025    \\
+		&             &           &           &           &               &           &           &           & L5.InfExp\_Var\_ch   &               &           &           & -0.058**  \\
+		&             &           &           &           &               &           &           &           &                      &               &           &           & -0.018    \\
+		&             &           &           &           &               &           &           &           & L6.InfExp\_Var\_ch   &               &           &           & -0.025    \\
+		&             &           &           &           &               &           &           &           &                      &               &           &           & -0.012    \\
+		Constant               & -0.002      & -0.001    & 0.004     & 0.004     & 0.000         & 0.002     & 0.004     & 0.005     &   Constant                   & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
+		& (0.005)     & (0.005)   & (0.004)   & (0.004)   & (0.004)       & (0.004)   & (0.004)   & (0.004)   &                      & -0.123        & -0.11     & -0.104    & -0.163    \\
+		\hline 
+		N                    & 1202        & 950       & 765       & 625       & 1078          & 842       & 657       & 519       &                      & 53016         & 43166     & 28850     & 14445     \\
+		$R^2$ & 0.000       & 0.120     & 0.265     & 0.242     & 0.000         & 0.233     & 0.321     & 0.385     &                      & 0             & 0.182     & 0.278     & 0.321  \\
+		\hline    
+	\end{tabular}
+\end{adjustbox}
+
 \subsection{Professional Forecasters as a Benchmark}

### 2019-06-26 paper/Draft.tex
The discussion of FE and RV efficiency results are outlined.The implication for IR results remain to be written down.

@@
 
-In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section.
-I first reproduce the results from two papers, \cite{mankiw2003disagreement} and \cite{fuhrer2018intrinsic} and then proceed to show the results with the additional restrictions from ucnertainty.
+In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section mostly following \cite{mankiw2003disagreement}.
 
@@
 
-The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting}.
+ The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting} and \cite{fuhrer2018intrinsic}.
 In particular, I follow the model specifications in \cite{fuhrer2018intrinsic}.
@@
 A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
+
+The weak efficiency tests use change in forecast and uncertainty instead of revisions.
+This is not a direct test of the null of FIRE as we have discussed that the rigidity models do not have direct testable predictions about the change in forecast and uncertainty with fixed forecast horizon.
+But in the same time, the auto regression features do speak to the persistence of the forecasts over the time horizon.
+In particular, if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
 

### 2019-06-26 workingfolder/python/Theories.py
Finalized the Theory Graphs. Need to set the randome seed to generate the best graph. Make it clear NI chart is based on a particular realization of Public signals.

@@ -511,7 +511,7 @@ plt.savefig('figures/ir_indseni.png')
 # +
 plt.style.use('ggplot')
 fig=plt.figure(figsize=(16,10))
-fig.suptitle("Impulse Response to Shock at t: Individual Moments",fontsize=20)
+fig.suptitle("Impulse Response to Shock at t: Population Moments",fontsize=20)
 
 plt.subplot(2,3,1)
 plt.title(r'$\omega_t$',fontsize=15)

### 2019-06-26 paper/Draft.tex
Started drafting IR parts.first subsection done.

@@
 
-\section{Theories of Expectation Formation}
+\section{Theories of Expectation Formation}\label{theory}
 
@@
 
-\section{Empirical Results}
+\section{Empirical Results}\label{empirical}
 
@@
 \begin{table}[]\label{NullTestTable}
-	\caption{Test of Rationality and Efficicency}
+	\caption{Tests of Rationality and Efficicency using Forecast Errors}
 	\centering 
@@
 	\hline 
-	\multicolumn{4}{l}{Test2: FE Depends on past information}                                  \\
+	\multicolumn{4}{l}{Test 2: FE depends on past information}                                  \\
 	\hline 
@@
 	\hline 
-	\multicolumn{4}{l}{Test3: FE of non-overlapping forecast horizons are serially correlated} \\
+	\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons are serially correlated} \\
 	\hline 
@@
 	\hline 
-	\multicolumn{4}{l}{Test4: Overlapping FE are only weakly serially correlated}                          \\
+	\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
 	\hline 
@@
 
-\subsection{Professional Forecasters as a Benchmark}
+\section{Responses of Expectations to Inflation Shocks }\label{IRShocks}
 
-\subsubsection{Replicating \cite{coibion2012can}}
+ \cite{Coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
+Unlike the time series regressions that test null hypotheses of FIRE in previous section, this approach allows a more straightforward comparison between the emprical evidence from surveys and the theoriecal predictions illustrated in Figure \ref{ir_pop}.
+The difficulty of this approach lies in identifying a shock $\omega_t$ that is a pure innovation to inflation at time $t$.
+
+In this paper I use three types of shocks: technology shock\cite{gali1999technology}, oil price shock\cite{hamilton1996happened} and monetary policy shocks \cite{laseen2011anticipated}.
+The first two are the same in \cite{Coibion2012can}.
+\footnote{ Another shock in \cite{Coibon2012can} is the news shock by \cite{barsky2011news}.
+This will be included in later version of the paper }
+
+(1) Technology shock is identified from a three variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
+\footnote{An recent alternative to long-run restriction approach is the ''max-share appraoch'' developed by \cite{francis2014flexible}.
+It is shown to have better small-sample properties.
+In particular,  the approach defines technology shock as the variation of current period labor productivity (output per hour) that explains the maximum fraction of future labor productivity over an exogenously determiend horizon.
+The resutls using this shock will be included in a later version of the paper.
+For the replication purpose now, I stay with \cite{gali1999technology}}.
+The sample period used to identify the shock is 1949-2019, while the period where it enters my analysis is the same to the period of survey data: 2007-2019 for SPF and 2013-2019 for SCE.
+
+(2) Oil price shock in each period is defined as the maximum of log change in crude oil prices over the past 1-year and 0.
+Therefore it is bounded zero.\footnote{The series of oil price is Spot Crude Oil Price: West Texas Intermediate (WTI).}
+
+(3) Monetary policy shocks: target surprise and path surprise in the termiology of \cite{laseen2011anticipated}.
+Target surprise is defined as unexpected change in federal funds rate in a particular dates of FOMC meenting.
+It is the OLS residual of federal funds rate change in the past federal funds rate.
+The 2-year ahead path surprise is the regression residual of future implied federal funds rate on the target surprise.
+Depending on the frequency of the data being monthly or quarterly, I take the sum of all the changes within each period.
+
+The reason for including monetary policy shocks, although it turns out to provide less robust evidence, is twofold.
+First, it is well known that the role of expectation in the working and implementation of monetary policy in the post criss period has been of a great relevance.
+Especially, around zero-lower-bound, the central banks have utilized nontraditional tools such as forward guidance which primarily works through influencing expectations of market agents.
+
+In Figure \ref{Inflationshocks}, all four shocks plus the unexplained component of inflation are plotted in quarterly between 1985-2019.
+All shocks are normalized by its respective sample standard deviations.
+
+\begin{figure}[h]\label{Inflationshocks}
+	\centering
+	\includegraphics[width=12cm]{figures/inf_shocksQ.png}
+	\caption{ Shocks to Inflation}
+\end{figure}
+
+\subsection{Replicating \cite{coibion2012can}}
 
@@
 
-\subsubsection{Additional Evidence from Uncertainty}
+\subsection{Additional Evidence from Uncertainty}
 

### 2019-06-26 paper/Draft.tex
IR sections continued. Almost finished the replication subsection.

@@
 %opening
-\title{Testing Theories of Expectation Formation using Probabilistic Forecasts}
+\title{Rigidity of Expectation Formation: Additional Evidence from Desntify Forecasts}
 \author{Tao Wang}
@@
 
-The theories on how different agents form expectations have proliferated over the past decade.
+The theories on how agents form expectations in ways deviating from rational expectation(RE) benchmark have proliferated over the past decade.
 On one hand, these theories built upon different micro foundations produce some similar macro patterns.
 For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.
-
-On the other hand, however, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.
-My goal of this exercise is to derive the testable predictions based on various theories, and utilize the probablistic questions from both professional forecasters survey and household survey to test them.
+On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.
+This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probablistic forecast from both professional forecasters survey and household survey.
+Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models.
 
@@
 
-We follow \cite{Manski} to estiamte the density distribution of each individual surveyee for SPF.
+We follow \cite{engelberg2009comparing} to estiamte the density distribution of each individual surveyee for SPF.
 New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty.
@@
 
+Throughout the paper, I use two measures of Inflation, headline CPI inflation and PCE inflation. The forecasts-based measures are computed and used correspondingly.
+
 \subsection{Stylized Facts}
@@
 
-Another widely spoken fact is that uncertainty is positively correlated with the level of the inflation. We look this hypothesis by ploting uncertainty against the realized inflation.
+Another widely made statement is that uncertainty is positively correlated with the level of the inflation. I look into this hypothesis by ploting uncertainty against the realized inflation.
 
@@
 	\includegraphics[width=6cm]{figures/PRCPCEVar_rv_hist.png}  \\
-	\smallskip
-		\includegraphics[width=6cm]{figures/SCEMean_rv_hist.png} 
-	\includegraphics[width=6cm]{figures/SCEVar_rv_hist.png}  \\
 	\caption{Distribution of Revision in Forecasts}
@@
 
- \cite{Coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
+ \cite{coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
 Unlike the time series regressions that test null hypotheses of FIRE in previous section, this approach allows a more straightforward comparison between the emprical evidence from surveys and the theoriecal predictions illustrated in Figure \ref{ir_pop}.
@@
 In this paper I use three types of shocks: technology shock\cite{gali1999technology}, oil price shock\cite{hamilton1996happened} and monetary policy shocks \cite{laseen2011anticipated}.
-The first two are the same in \cite{Coibion2012can}.
-\footnote{ Another shock in \cite{Coibon2012can} is the news shock by \cite{barsky2011news}.
-This will be included in later version of the paper }
+The first two are the same in \cite{coibion2012can}.
+\footnote{ Another shock in \cite{coibon2012can} is the news shock by \cite{barsky2011news}.
+This will be included in later version of the paper.}
 
 (1) Technology shock is identified from a three variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
-\footnote{An recent alternative to long-run restriction approach is the ''max-share appraoch'' developed by \cite{francis2014flexible}.
+Based on Bayes information criteria, I use the lag of 4 quarters as in \cite{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share appraoch'' developed by \cite{francis2014flexible}.
 It is shown to have better small-sample properties.
@@
 
-In Figure \ref{ReplicateCoibionBefore2007}, I replicate the results from  \cite{coibion2012can}.
-The period is between 1987-2007.
-In the right column, I do the same exercise with monetary policy shocks.
+For a direct comparison of my results and \cite{coibion2012can}, I first explore the impulse responses along one-standard-deviation confidence band of inflation $y_{t+k}$, and SPF forecast errors $\overline {FE}_{t+h|t+k}$ to one standard deviation of each shock at time $t$, and SPF disagreements $\overline Disg_{t+h|t+k}$ and average uncertainty $\bar\sigma^2_{t+h|t+k}$ to the absolute value of shocks.
+The sample period is the same to that in Figure 2 from \cite{coibion2012can}: 1987-2007.
+The only difference is that CPI and PCE inflation are used instead of GDP deflator as in their paper.
+
+The underlying regression that produces impulse response estimates is the Equation \ref{IRRegression}, according to which inflation(or moments) in current quarter is a function of 4-period lagged of itself  and the current and previous period realized shocks.
+The estimate of autoregression coefficient $\beta_\tau$ and shock-specific coefficient $\beta_{S,k}$ for diffrent lags can be used to compute impulse response of the inflation as well as forecasting moments.
+
+\begin{eqnarray}\label{IRRegression}
+y_{t}  = \alpha + \sum^4_{\tau=1} \beta_{\tau} y_{t-\tau} +  \sum^1_{k=0} \sum_{S \in \{O,T\}}\beta_{S,k}\omega_{S,t-k} + \epsilon_t 
+\end{eqnarray}
+
+FIRE predicts $\beta_{S,k}=0\quad \forall k=1$ for the regressions with forecasts moments as dependent variable. i.e. forecasts react only to contemporaneous shocks instataneously therefore.
+
+Standard errors are computed using the parametric bootstrapping approach as in \cite{coibion2012can} paper.
+
+Responses to productivity and oil price shocks presented in the left panel of the Figure \ref{ReplicateCoibionBefore2007} are broadly consistent with \cite{coibion2012can} despite a wider confidence band possibly due to the change in different measures.
+First, one standard deviation of productivity unsurprisingly brings down headline inflation by around $10 \%$  in the first quarter and the negative impacts gradually mute since then till the 7-th quarter.
+Oil price shock of one standard deviation increases headline inflation by around $30\%$ in the first quarter and the inflationary impacts last for 6 quarters.
+PCE inflation responds to both the shocks in a similar manner with slightly different magnitudes.
+The responses coefficients are statistically significant as the $95\%$ confidence intervel stays on one side of zero for both shock for the same period.
+
+Second, population forecast errors respond to shocks in a sluggish manner as predicted in rigidity models.
+This is illustrated using both CPI and PCE forecasts in the second graph of the left panel in Figure \ref{ReplicateCoibionBefore2007}.
+As we define the forecast error as forecast minus realized value, forecast error rises(drops) after a positive(negative) shock and gradully return to zero around 4-5th quarters after the shock.
+
+Both SE and NI models predict disagreements rise after a shock and gradully converge to zero over the long-run.
 

### 2019-06-26 paper/Draft.tex
Done with discussions of the IR plots replicating.

@@
 The only difference is that CPI and PCE inflation are used instead of GDP deflator as in their paper.
+Besides, standard errors are computed using the parametric bootstrapping approach as in \cite{coibion2012can}.
 
@@
 FIRE predicts $\beta_{S,k}=0\quad \forall k=1$ for the regressions with forecasts moments as dependent variable. i.e. forecasts react only to contemporaneous shocks instataneously therefore.
-
-Standard errors are computed using the parametric bootstrapping approach as in \cite{coibion2012can} paper.
 
@@
 
-Both SE and NI models predict disagreements rise after a shock and gradully converge to zero over the long-run.
-
-In Figure \ref{ReplicateCoibionpost2007}, I do the same exercise but include additional uncertainty. This is also the period when SPF provides density forecasts that allow me to estimate uncertainty.
+FIRE predicts zero disagreements while both SE and NI models imply disagreements pick up following shocks regardless of the sign and gradully drop over longer horizon.
+Looking into the graph, the average response of disgreements to the absolute value of technology and oil shocks does exhibite a pattern similar to the later.
+Note now that the initial response is not statistically significant(same as the original result.).
+Besides, there is also one subtle difference between the SE and NI on disagreements in that disagreements always exist with the presense of private signals, in contrast, SE predicts that the disagreements is zero over the long run.
+The evidence from impulse response of disagreements seem to be more consistent with SE than NI.
 
@@
 \end{figure}
+
+\subsection{Additional Evidence from Uncertainty}
+
+In Figure \ref{ReplicateCoibionpost2007}, I do the same exercise but include additional uncertainty. This is also the period when SPF provides density forecasts that allow me to estimate uncertainty.
 
@@
 
+\subsection{Evidence from Households}
+
 \begin{figure}[h]\label{SCE_IR}
@@
 
-\subsection{Additional Evidence from Uncertainty}
-
-\subsection{Evidence from Households}
-
 \section{Conclusion}

### 2019-06-26 paper/Draft.tex
Finalized VarOtherMoments Figures

@@
 	\smallskip
-	\includegraphics[width=3.5cm]{figures/Inf_var2Q.png}
-	\includegraphics[width=3.5cm]{figures/fe_var2Q.png}
-	\includegraphics[width=3.5cm]{figures/var_disg2Q.png}\\
+	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
+	\includegraphics[width=3.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
+	\includegraphics[width=3.5cm]{figures/CPI_disg_varSPFCPIQ.png}\\
 	\smallskip
-	\includegraphics[width=3.5cm]{figures/Inf_var3Q.png}
-	\includegraphics[width=3.5cm]{figures/fe_var3Q.png}
-	\includegraphics[width=3.5cm]{figures/var_disg3Q.png}\\
+	\includegraphics[width=3.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
+	\includegraphics[width=3.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
+	\includegraphics[width=3.5cm]{figures/PCE_disg_varSPFPCEQ.png}\\
 	\smallskip	
-	\includegraphics[width=3.5cm]{figures/Inf_var.png}
-	\includegraphics[width=3.5cm]{figures/fe_var.png}
-	\includegraphics[width=3.5cm]{figures/var_disg.png}\\
+	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}
+	\includegraphics[width=3.5cm]{figures/SCE_FE_varSCEM.png}
+	\includegraphics[width=3.5cm]{figures/Q9_disg_varSCEM.png}\\
 		\caption{Unceratinty and Other Moments}
@@
 		\hline 
-		L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
-		&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                      &               & (0.015)   & (0.022)   & (0.037)   \\
-		L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
-		&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                      &               &           & (0.021)   & (0.031)   \\
-		L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\
+		L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
+		&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\
+
+		L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Mean\_ch &         &           & -0.336*** & -0.439*** \\
+
+		&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                                   &         &           & (0.018)    & (0.031)    \\
+		L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Mean\_ch &         &           & -0.143*** & -0.270*** \\
+
 		&             &           &           & (0.032)   &               &           &           & (0.036)   &                                &         &           & (0.012)    & (0.027)    \\
-		&             &           &           &           &               &           &           &           & L4.InfExp\_Var\_ch   &               &           &           & -0.130*** \\
-		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.025)   \\
-		&             &           &           &           &               &           &           &           & L5.InfExp\_Var\_ch   &               &           &           & -0.058**  \\
-		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.018)   \\
-		&             &           &           &           &               &           &           &           & L6.InfExp\_Var\_ch   &               &           &           & -0.025    \\
-		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.012)   \\
-		Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant               & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
-		& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                      & (0.123)       & (0.110)   & (0.104)   & (0.163)   \\
+
+		&             &           &           &           &               &           &           &           & L4.InfExp\_Mean\_ch &         &           &           & -0.183*** \\
+
+		&             &           &           &           &               &           &           &           &                                 &         &           &           & (0.027)    \\
+		&             &           &           &           &               &           &           &           & L5.InfExp\_Mean\_ch &         &           &           & -0.096*** \\
+		&             &           &           &           &               &           &           &           &                      &         &           &           & (0.021)    \\
+		&             &           &           &           &               &           &           &           & L6.InfExp\_Mean\_ch &         &           &           & -0.044**  \\
+		&             &           &           &           &               &           &           &           &                                     &         &           &           & (0.013)    \\
+		Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant              & -0.055* & -0.034    & -0.001    & -0.002    \\
+		& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                                 & -0.023  & -0.023    & -0.028    & -0.033    \\
 		\hline 
 		N                    & 1636        & 1430      & 1266      & 1141      & 1402          & 1190      & 1022      & 898       & N                   & 53016   & 43166     & 28850     & 14445     \\
-	$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ & 0.000         & 0.182     & 0.278     & 0.321     \\
+	$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ &  0.000       & 0.202     & 0.273     & 0.306   \\
 		\hline 
@@
 Looking into the graph, the average response of disgreements to the absolute value of technology and oil shocks does exhibite a pattern similar to the later.
-Note now that the initial response is not statistically significant(same as the original result.).
-Besides, there is also one subtle difference between the SE and NI on disagreements in that disagreements always exist with the presense of private signals, in contrast, SE predicts that the disagreements is zero over the long run.
+Note now that the initial response is no longer statistically significant(same as the original result.) and the pick-up of disagreement after both shocks seem to take place one quarter after the shock.
+
+The level at whch disagreements converge over the long-run shed light upon one subtle difference between the SE and NI.
+Disagreements always exist in NI with the presense of private signals , in contrast, disagreements is zero over the long run.
 The evidence from impulse response of disagreements seem to be more consistent with SE than NI.

### 2019-06-27 paper/Draft.tex
Improving latex formatting and addressing a few technical issues. use citet instead of cite for line break of aphalike. also ht for tables and charts to adjust the positions.

@@
 \usepackage{graphicx}
+\usepackage[a4paper,bindingoffset=0.2in,%
+left=1in,right=1in,top=1.2in,bottom=1.2in,%
+footskip=.25in]{geometry}
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	filecolor=blue,      
+	urlcolor=blue,
+	citecolor=blue
+}
+\usepackage{natbib}
 
@@
 
-The potential contribution lies in the extra insights I may get from using probablistic questions.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \cite{manski2004measuring}.} One obvious advantage of density expectations compared to point one is availability of higher moments, i.e.
+The potential contribution lies in the extra insights I may get from using probablistic questions.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \citet{manski2004measuring}.} One obvious advantage of density expectations compared to point one is availability of higher moments, i.e.
 variance of the forecast indicates the dispersion of the forecasts.
@@
 Examples of such include multi-prior or model uncertainty.
-\cite{xx}.
+\citet{xx}.
 }
@@
 To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.
-\footnote{This is the same terminology used by \cite{xx}.}
+\footnote{This is the same terminology used by \citet{xx}.}
 
@@
 
-\begin{table}[]\label{MomSum}
+\begin{table}[]
 	\centering
 		\caption{Definition and Notation of Moments}
+		\label{MomSum}
 	\begin{tabular}{ll}
@@
 This provides the a well known null hypothesis of FIRE.
-\cite{xx}
+\citet{xx}
 
@@
 FIRE also has predictions about  population disagreements.
-\footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey.
+\footnote{For instance, \citet{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey.
 } As agents perfect update the same information, there is no disagreements at any point of the time.
@@
 
-A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empricial tests of this kind include \cite{xx}.\cite{xx} etc. }
+A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empricial tests of this kind include \citet{xx}.\citet{xx} etc. }
 
@@
 The uncertainty simply comes from uncertainty about future unrealized shocks between $t$ and $t+h$.
-To put it another way, according to FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \cite{}'s terminology.}
+To put it another way, according to FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{}'s terminology.}
 
@@
 Although in our baseline case we make such an assumption, in general it may not be true.
-\footnote{\cite{xx} on time-varying volatility.}
+\footnote{\citet{xx} on time-varying volatility.}
 
@@
 
-The theory of sticky expectation (\cite{xx}, \cite{xx} ), regardless of its different microfoundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
+The theory of sticky expectation (\citet{xx}, \citet{xx} ), regardless of its different microfoundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
 One of the most tractable models assume there is a homogenous Possion rate $\lambda$ of updating among the population.
@@
 Relying upon the Law of Large Numbers, we can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$.
-\footnote{\cite{carroll2003macroeconomic} is one notable example of this.}
+\footnote{\citet{carroll2003macroeconomic} is one notable example of this.}
 
 One well known prediction from SE literature is that the average foreacast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
-\footnote{See \cite{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$.
+\footnote{See \citet{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$.
 Setting $\lambda=1$, then the SE collapses to FIRE and the average forecast is equal to $y$'s long-run mean of zero.
@@
 
-\cite{coibion2012can} also derives predictions about the disagreements in rigidity models.
+\citet{coibion2012can} also derives predictions about the disagreements in rigidity models.
 Unlike zero disagreements in FIRE, SE is characterized by non-zero dispersion in forecasting because of different lags in updating across populations.
@@
 In the same time, it does not depend upon the particular realization of the shock.
-\cite{coibion2012can} derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.
+\citet{coibion2012can} derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.
 
@@
 
-A class of noisy information models (\cite{},\cite{}) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
+A class of noisy information models (\citet{},\citet{}) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
 The starting assumption is that agent cannot observe the true variable perfectly.
@@
 
-\begin{figure}[h]\label{IllustrateNI}
+\begin{figure}[ht]
 	\centering
 	\includegraphics[width=13cm]{figures/ni_illustration.png}  
-	\caption{Illustration Noisy Information}
+	\caption{Nowcasting and Forecasting in Noisy Information}
+	\label{IllustrateNI}
 \end{figure}
@@
 
-\begin{figure}[h]\label{ir_pop}
+\begin{figure}[ht]
 	\centering
-	\includegraphics[width=15cm]{figures/ir_popseni.png} 
+	\includegraphics[width=16cm]{figures/ir_popseni.png} 
 	\caption{Impulse responses of moments to a shock to inflation}
+	\label{ir_pop}
 \end{figure}
@@
 
-\begin{figure}[h]\label{rigidity}
+\begin{figure}[ht]
 	\centering
@@
 	\caption{Rigidity from Two Models}
+	\label{rigidity}
 \end{figure}
@@
 \begin{itemize}
-	\item Chris Sim's model.\cite{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy.
+	\item Chris Sim's model.\citet{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy.
 Agents optimally trade off the fixed cost of being attentative versus the gain from uncertainty gain.
-	\item Ricardo Reis's model. \cite{reis2006inattentive}
-	\item Xavier Gabaix's sparse matrix model. \cite{gabaix2014sparsity}
+	\item Ricardo Reis's model. \citet{reis2006inattentive}
+	\item Xavier Gabaix's sparse matrix model. \citet{gabaix2014sparsity}
 \end{itemize}
@@
 \item Epidemiologic view.
-\cite{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.
+\citet{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.
 
-\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \cite{angeletos2009incomplete}
+\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \citet{angeletos2009incomplete}
 
@@
 
-We follow \cite{engelberg2009comparing} to estiamte the density distribution of each individual surveyee for SPF.
+We follow \citet{engelberg2009comparing} to estiamte the density distribution of each individual surveyee for SPF.
 New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty.
@@
 
-\begin{table}[]
+\begin{table}[ht]
 			\caption{Information of Data}
+			\label{DataInfo}
 	\begin{tabular}{lll}
@@
 
-\begin{figure}[h]\label{UnceratitnyOtherMoments}
-	\centering
+\begin{figure}[ht]
 	\centering
 	\smallskip
-	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
-	\includegraphics[width=3.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
-	\includegraphics[width=3.5cm]{figures/CPI_disg_varSPFCPIQ.png}\\
+	\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
+	\includegraphics[width=4.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
+	\includegraphics[width=4.5cm]{figures/CPI_disg_varSPFCPIQ.png}\\
 	\smallskip
-	\includegraphics[width=3.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
-	\includegraphics[width=3.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
-	\includegraphics[width=3.5cm]{figures/PCE_disg_varSPFPCEQ.png}\\
+	\includegraphics[width=4.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
+	\includegraphics[width=4.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
+	\includegraphics[width=4.5cm]{figures/PCE_disg_varSPFPCEQ.png}\\
 	\smallskip	
-	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}
-	\includegraphics[width=3.5cm]{figures/SCE_FE_varSCEM.png}
-	\includegraphics[width=3.5cm]{figures/Q9_disg_varSCEM.png}\\
+	\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}
+	\includegraphics[width=4.5cm]{figures/SCE_FE_varSCEM.png}
+	\includegraphics[width=4.5cm]{figures/Q9_disg_varSCEM.png}\\
 		\caption{Unceratinty and Other Moments}
+		\label{UnceratitnyOtherMoments}
 \end{figure}
 
-\begin{figure}[h]\label{IQR_Unceratitny}
+\begin{figure}[ht]
 	\centering
@@
 	\caption{Dispersion in Mean Forecast and Unceratinty }
+	\label{IQR_Unceratitny}
 \end{figure}
 
-\begin{figure}[h]\label{Unceratitny_Histogram}
+\begin{figure}[ht]
 	\centering
-	\includegraphics[width=6cm]{figures/PRCCPIMean1_hist.png} 
-	\includegraphics[width=6cm]{figures/PRCCPIVar1_hist.png}  \\
+	\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
+	\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  \\
 	\smallskip
-		\includegraphics[width=6cm]{figures/PRCPCEMean1_hist.png} 
-	\includegraphics[width=6cm]{figures/PRCPCEVar1_hist.png}  \\
+		\includegraphics[width=7cm]{figures/PRCPCEMean1_hist.png} 
+	\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  \\
 	\smallskip
-		\includegraphics[width=6cm]{figures/SCEmean_hist.png} 
-	\includegraphics[width=6cm]{figures/SCEvar_hist.png}  \\
+		\includegraphics[width=7cm]{figures/SCEmean_hist.png} 
+	\includegraphics[width=7cm]{figures/SCEvar_hist.png}  \\
 	\caption{Distribution of Mean Forecast and Uncertainty }
+	\label{Unceratitny_Histogram}
 \end{figure}
 
-\begin{figure}[h]\label{RevisionHist}
+\begin{figure}[ht]
 	\centering
-	\includegraphics[width=6cm]{figures/PRCCPIMean_rv_hist.png} 
-	\includegraphics[width=6cm]{figures/PRCCPIVar_rv_hist.png}  \\
+	\includegraphics[width=7cm]{figures/PRCCPIMean_rv_hist.png} 
+	\includegraphics[width=7cm]{figures/PRCCPIVar_rv_hist.png}  \\
 	\smallskip
-	\includegraphics[width=6cm]{figures/PRCPCEMean_rv_hist.png} 
-	\includegraphics[width=6cm]{figures/PRCPCEVar_rv_hist.png}  \\
+	\includegraphics[width=7cm]{figures/PRCPCEMean_rv_hist.png} 
+	\includegraphics[width=7cm]{figures/PRCPCEVar_rv_hist.png}  \\
 	\caption{Distribution of Revision in Forecasts}
+	\label{RevisionHist}
 \end{figure}
@@
 
-In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section mostly following \cite{mankiw2003disagreement}.
+In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section mostly following \citet{mankiw2003disagreement}.
 
@@
 
- The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting} and \cite{fuhrer2018intrinsic}.
-In particular, I follow the model specifications in \cite{fuhrer2018intrinsic}.
-According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information.
-For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.
-A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
-
-The weak efficiency tests use change in forecast and uncertainty instead of revisions.
-This is not a direct test of the null of FIRE as we have discussed that the rigidity models do not have direct testable predictions about the change in forecast and uncertainty with fixed forecast horizon.
-But in the same time, the auto regression features do speak to the persistence of the forecasts over the time horizon.
-In particular, if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
-
-\begin{table}[]\label{NullTestTable}
+\begin{table}[ht]
 	\caption{Tests of Rationality and Efficicency using Forecast Errors}
+	\label{NullTestTable}
 	\centering 
@@
 
-\newpage
+The second batch of tests in Table \ref{RevEfficiency} focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \citet{nordhaus1987forecasting} and \citet{fuhrer2018intrinsic}.
+In particular, I follow the model specifications in \citet{fuhrer2018intrinsic}.
+According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information.
+For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.
+A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
 
-\begin{adjustbox}{angle=90}\label{RevEfficiency}
+\begin{table}[ht]
+	\caption{Tests of Revision Efficiency using Mean Revision and Uncertainty}
+	\label{RevEfficency}
+\begin{adjustbox}{angle=90}
+
 	\begin{tabular}{lllllllll}
@@
 \end{adjustbox}
+\end{table}
 
-\begin{adjustbox}{width={22cm},totalheight={12cm},angle=90}\label{WeakRevEfficiency}
+The weak efficiency tests use change in forecast and uncertainty instead of revisions.
+This is not a direct test of the null of FIRE as we have discussed that the rigidity models do not have direct testable predictions about the change in forecast and uncertainty with fixed forecast horizon.
+But in the same time, the auto regression features do speak to the persistence of the forecasts over the time horizon.
+In particular, if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
+
+\begin{table}
+	\centering 
+	\caption{Weak Tests of Revision Efficiency using Change in Foreacsts and Uncertainty}
+	\label{WeakRevEfficiency}
+\begin{adjustbox}{width={24cm},totalheight={14cm},angle=90}
 	\begin{tabular}{llllllllllllll}
@@
 \end{adjustbox}
+\end{table}
 
@@
 
- \cite{coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
+ \citet{coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
 Unlike the time series regressions that test null hypotheses of FIRE in previous section, this approach allows a more straightforward comparison between the emprical evidence from surveys and the theoriecal predictions illustrated in Figure \ref{ir_pop}.
@@
 
-In this paper I use three types of shocks: technology shock\cite{gali1999technology}, oil price shock\cite{hamilton1996happened} and monetary policy shocks \cite{laseen2011anticipated}.
-The first two are the same in \cite{coibion2012can}.
-\footnote{ Another shock in \cite{coibon2012can} is the news shock by \cite{barsky2011news}.
+In this paper I use three types of shocks: technology shock\citet{gali1999technology}, oil price shock\citet{hamilton1996happened} and monetary policy shocks \citet{laseen2011anticipated}.
+The first two are the same in \citet{coibion2012can}.
+\footnote{ Another shock in \citet{coibon2012can} is the news shock by \citet{barsky2011news}.
 This will be included in later version of the paper.}
@@
 (1) Technology shock is identified from a three variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
-Based on Bayes information criteria, I use the lag of 4 quarters as in \cite{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share appraoch'' developed by \cite{francis2014flexible}.
+Based on Bayes information criteria, I use the lag of 4 quarters as in \citet{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share appraoch'' developed by \citet{francis2014flexible}.
 It is shown to have better small-sample properties.
@@
 The resutls using this shock will be included in a later version of the paper.
-For the replication purpose now, I stay with \cite{gali1999technology}}.
+For the replication purpose now, I stay with \citet{gali1999technology}}.
 The sample period used to identify the shock is 1949-2019, while the period where it enters my analysis is the same to the period of survey data: 2007-2019 for SPF and 2013-2019 for SCE.
@@
 
-(3) Monetary policy shocks: target surprise and path surprise in the termiology of \cite{laseen2011anticipated}.
+(3) Monetary policy shocks: target surprise and path surprise in the termiology of \citet{laseen2011anticipated}.
 Target surprise is defined as unexpected change in federal funds rate in a particular dates of FOMC meenting.
@@
 
-\begin{figure}[h]\label{Inflationshocks}
+\begin{figure}[ht]
 	\centering
@@
 	\caption{ Shocks to Inflation}
+	\label{Inflationshocks}
 \end{figure}
 
-\subsection{Replicating \cite{coibion2012can}}
+\subsection{Replicating \citet{coibion2012can}}
 
-For a direct comparison of my results and \cite{coibion2012can}, I first explore the impulse responses along one-standard-deviation confidence band of inflation $y_{t+k}$, and SPF forecast errors $\overline {FE}_{t+h|t+k}$ to one standard deviation of each shock at time $t$, and SPF disagreements $\overline Disg_{t+h|t+k}$ and average uncertainty $\bar\sigma^2_{t+h|t+k}$ to the absolute value of shocks.
-The sample period is the same to that in Figure 2 from \cite{coibion2012can}: 1987-2007.
+For a direct comparison of my results and \citet{coibion2012can}, I first explore the impulse responses along one-standard-deviation confidence band of inflation $y_{t+k}$, and SPF forecast errors $\overline {FE}_{t+h|t+k}$ to one standard deviation of each shock at time $t$, and SPF disagreements $\overline Disg_{t+h|t+k}$ and average uncertainty $\bar\sigma^2_{t+h|t+k}$ to the absolute value of shocks.
+The sample period is the same to that in Figure 2 from \citet{coibion2012can}: 1987-2007.
 The only difference is that CPI and PCE inflation are used instead of GDP deflator as in their paper.
-Besides, standard errors are computed using the parametric bootstrapping approach as in \cite{coibion2012can}.
+Besides, standard errors are computed using the parametric bootstrapping approach as in \citet{coibion2012can}.
 
@@
 
-Responses to productivity and oil price shocks presented in the left panel of the Figure \ref{ReplicateCoibionBefore2007} are broadly consistent with \cite{coibion2012can} despite a wider confidence band possibly due to the change in different measures.
+Responses to productivity and oil price shocks presented in the left panel of the Figure \ref{ReplicateCoibionBefore2007} are broadly consistent with \citet{coibion2012can} despite a wider confidence band possibly due to the change in different measures.
 First, one standard deviation of productivity unsurprisingly brings down headline inflation by around $10 \%$  in the first quarter and the negative impacts gradually mute since then till the 7-th quarter.
@@
 
-\begin{figure}[h]\label{ReplicateCoibionBefore2007}
+\begin{figure}[ht]
 	\centering
@@
 		\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} 
-	\caption{ Replicating \cite{coibion2012can}: 1987-2007}
+	\caption{ Replicating \citet{coibion2012can}: 1987-2007}
+	\label{ReplicateCoibionBefore2007}
 \end{figure}
@@
 
-\begin{figure}[h]\label{ReplicateCoibionpost2007}
+\begin{figure}[ht]
 	\centering
@@
 	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_post2007.png} 
-	\caption{ Replicating \cite{coibion2012can}: 2008-2019}
+	\caption{ Replicating \citet{coibion2012can}: 2008-2019}
+	\label{ReplicateCoibionpost2007}
 \end{figure}
@@
 
-\begin{figure}[h]\label{SCE_IR}
+\begin{figure}[ht]
 	\centering
@@
 	\caption{ Impulse Responses of Inflation and SCE Forecasts to Inflation Shocks}
+	\label{SCE_IR}
 \end{figure}

### 2019-06-27 paper/Draft.tex
finalizing charts on dispersion.
Finalizing on histograms of revisions of SPF.

@@
 
-We drop the outliers of uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.
+For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.
+For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extream values.
+\footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in totla.}
 
@@
 	\centering
-	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
+	\includegraphics[width=7cm]{figures/IQRmeanCPIQ.png} 
+	\includegraphics[width=7cm]{figures/IQRvarCPIQ.png} \\
 	\smallskip
-	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
+   \includegraphics[width=7cm]{figures/IQRmeanPCEQ.png}
+	\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}\\
 		\smallskip
-	\includegraphics[width=8cm]{figures/IQRvarSCEM.png}\\
+		\includegraphics[width=7cm]{figures/IQRmeanSCEM.png}
+	\includegraphics[width=7cm]{figures/IQRvarSCEM.png}\\
 	\caption{Dispersion in Mean Forecast and Unceratinty }
@@
 	\centering
-	\includegraphics[width=7cm]{figures/PRCCPIMean_rv_hist.png} 
-	\includegraphics[width=7cm]{figures/PRCCPIVar_rv_hist.png}  \\
+	\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
+	\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  \\
 	\smallskip
-	\includegraphics[width=7cm]{figures/PRCPCEMean_rv_hist.png} 
-	\includegraphics[width=7cm]{figures/PRCPCEVar_rv_hist.png}  \\
+	\includegraphics[width=7cm]{figures/PRCPCEMean01_rv_true_hist.png} 
+	\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png}  \\
 	\caption{Distribution of Revision in Forecasts}

### 2019-06-27 paper/Draft.tex
to finish rest of the drafting.

@@
 %opening
-\title{Rigidity of Expectation Formation: Additional Evidence from Desntify Forecasts}
+\title{Rigidity of Expectation: Additional Evidence from Desntify Forecasts}
 \author{Tao Wang}
@@
 
-The second batch of tests in Table \ref{RevEfficiency} focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \citet{nordhaus1987forecasting} and \citet{fuhrer2018intrinsic}.
+The second batch of tests in Table \ref{RevEfficency} focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \citet{nordhaus1987forecasting} and \citet{fuhrer2018intrinsic}.
 In particular, I follow the model specifications in \citet{fuhrer2018intrinsic}.

### 2019-06-27 paper/Draft.tex
Finalizing content of IRF charts. one before 2007 and one for whole period.latex formatting remains to be done.

@@
 
-For a direct comparison of my results and \citet{coibion2012can}, I first explore the impulse responses along one-standard-deviation confidence band of inflation $y_{t+k}$, and SPF forecast errors $\overline {FE}_{t+h|t+k}$ to one standard deviation of each shock at time $t$, and SPF disagreements $\overline Disg_{t+h|t+k}$ and average uncertainty $\bar\sigma^2_{t+h|t+k}$ to the absolute value of shocks.
-The sample period is the same to that in Figure 2 from \citet{coibion2012can}: 1987-2007.
-The only difference is that CPI and PCE inflation are used instead of GDP deflator as in their paper.
-Besides, standard errors are computed using the parametric bootstrapping approach as in \citet{coibion2012can}.
+For a direct comparison of my results and \citet{coibion2012can}, I first explore the impulse responses of CPI inflation $y_{t+k}$, SPF forecast errors and disagreements to one standard deviation of each shock at time $t$.
+In particular, the responses of disagreements is with respect to the absolute value of the shocks.
+Because CPI inflation forecast is available only after 1984, the sample period 1984-2007 is six years shorter than that in Figure 2 from \citet{coibion2012can}: 1976-2007.
+I do not include the results for PCE inflation as there is no PCE forecast during this period.
 
-The underlying regression that produces impulse response estimates is the Equation \ref{IRRegression}, according to which inflation(or moments) in current quarter is a function of 4-period lagged of itself  and the current and previous period realized shocks.
-The estimate of autoregression coefficient $\beta_\tau$ and shock-specific coefficient $\beta_{S,k}$ for diffrent lags can be used to compute impulse response of the inflation as well as forecasting moments.
+The underlying regression that produces impulse response estimates is  Equation \ref{IRRegression}, according to which inflation(or moments) in current quarter is a function of 4-period lags of itself  and the realized shocks in current and previous period.
+The estimate of autoregression coefficients $\beta_\tau$ and shock-specific coefficients $\beta_{S,k}$ for diffrent lags can be used to compute impulse responses of the variables of interest.
+In the impulse response graph, standard errors are computed using the parametric bootstrapping approach as in \citet{coibion2012can}.
 
@@
 
-FIRE predicts $\beta_{S,k}=0\quad \forall k=1$ for the regressions with forecasts moments as dependent variable. i.e. forecasts react only to contemporaneous shocks instataneously therefore.
+FIRE predicts $\beta_{S,k}=0\quad \forall k=1$ for the regressions with forecasts moments as dependent variable.
+i.e.
+forecasts react only to contemporaneous shocks instataneously.
+Therefore, the average FE should not be dependent upon past shocks and  only experience a one-time rise and return zero immediately.
+The disagreements will not respond to the shock at all.
 
-Responses to productivity and oil price shocks presented in the left panel of the Figure \ref{ReplicateCoibionBefore2007} are broadly consistent with \citet{coibion2012can} despite a wider confidence band possibly due to the change in different measures.
-First, one standard deviation of productivity unsurprisingly brings down headline inflation by around $10 \%$  in the first quarter and the negative impacts gradually mute since then till the 7-th quarter.
-Oil price shock of one standard deviation increases headline inflation by around $30\%$ in the first quarter and the inflationary impacts last for 6 quarters.
+The results  presented in the left panel of the Figure \ref{ReplicateCoibionBefore2007} are consistent with FIRE predictions.
+Responses to productivity and oil price shocks are broadly consistent with \citet{coibion2012can} despite a wider confidence band possibly due to the change in inflation measures and difference in sample period.
+First, one standard deviation of productivity unsurprisingly brings down headline inflation by around 10 percentage points  in the first quarter and the negative impacts gradually mute since then till the 7-th quarter.
+Oil price shock of one standard deviation increases headline inflation by around 3 percentage points in the first quarter and the inflationary impacts last for 6 quarters.
 PCE inflation responds to both the shocks in a similar manner with slightly different magnitudes.
@@
 Second, population forecast errors respond to shocks in a sluggish manner as predicted in rigidity models.
-This is illustrated using both CPI and PCE forecasts in the second graph of the left panel in Figure \ref{ReplicateCoibionBefore2007}.
-As we define the forecast error as forecast minus realized value, forecast error rises(drops) after a positive(negative) shock and gradully return to zero around 4-5th quarters after the shock.
+This is illustrated using both SPF's FE of CPI in the second graph of  left panel in Figure \ref{ReplicateCoibionBefore2007}.
+As we define the forecast error as point forecast minus realized value, forecast error rises(drops) after a positive(negative) shock and gradully return to zero around 4-5th quarters after the shock.
 
-FIRE predicts zero disagreements while both SE and NI models imply disagreements pick up following shocks regardless of the sign and gradully drop over longer horizon.
-Looking into the graph, the average response of disgreements to the absolute value of technology and oil shocks does exhibite a pattern similar to the later.
-Note now that the initial response is no longer statistically significant(same as the original result.) and the pick-up of disagreement after both shocks seem to take place one quarter after the shock.
+Lastly, SE and NI models imply disagreement pick up after shocks and gradually drop over longer horizon.
+Looking into the graph, the average response of Disg to absolute value of  technology and oil shocks exhibit patterns similar to this prediction.
+Note now that the initial response is no longer statistically significant(same as the original result) and the pick-up of disagreement after both shocks do not take place immediately in the same quarter but in one quarter after the shock.
+\footnote{In addition, the degree of long-run disagreements sheds light upon one subtle difference between the SE and NI.
+Disagreements always exist in NI with the presense of private signals , in contrast, disagreement is zero over the long run in SE.
+The evidence from impulse response of disagreements seem to be more consistent with SE than with NI.}
 
-The level at whch disagreements converge over the long-run shed light upon one subtle difference between the SE and NI.
-Disagreements always exist in NI with the presense of private signals , in contrast, disagreements is zero over the long run.
-The evidence from impulse response of disagreements seem to be more consistent with SE than NI.
+The responses to monetary policy shocks turn out to be nosier than for technology and oil price shocks, as presented in the right panel of \ref{ReplicateCoibionBefore2007}.
+On the top figure, I first plot the impulse response of inflation to paths surprises and target surprise, seperately.
+On average, inflation reduces by around 10 percentage points after one unit increase of target surprise and increases by 10 percentage points following one unit of path surprise to federal funds rate.
+Both responses are  statistically significant in $10\%$  level.
+The unexpected future tightening causing a rise in inflation is conistent with the literature of price puzzle.
+\footnote{See \cite{nakamura2018high} as an example of inflationary responses to a monetary tightening move of the Fed.}
+
+In the middle figure plots the responses of CPI forecast erros by SPF.
+Although the average response seems to go in the same direction of the respective monetary shocks, consistent with the pattern seen for techonology and oil price shocks, none of the responses are statistically significant and the estimates have big standard errors of 10-20 percentage points.
+
+Similarly, the responses of disagreements to both monetary policy shocks in the bottom panel are not statistically signifcant throughout the 10 quarters.
+
+How do we intereprete this finding of non-response of forecasting errror and disagreements to monetary policy shocks in the conext of rigidity models?
+Non-response of FE suggests that on average professional forecaters have incorporated the shock in their forecasts.
+Non-response of disagreements could be due to that forecasters ``agree'' on the realization of monetary policy shocks.
+Althouth the benchmark theory of SE and NI do not differentiate shocks, the evidence here seems to suggest that the degree of rigidity depends on the nature of the shocks.
+
+There are other explanations.
+First, overal, the monetary policy shocks contribute only a small part of variation in inflation compared to supply shocks.
+This was actually used by \cite{coibion2012can} to justify why monetary policy shock was not used in their exercise.
+Second,  I am just running into the same difficulty in identifying real impacts of monetry policy shocks from low frequency data as all other papers addressing this issue.
+\footnote{Examples of identifying monetary policy shocks.
+\cite{xxx} }
 
@@
 	\centering
-	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_nmp.png}  
-	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks.png} \\
-	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_nmp.png} 
-	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks.png}  \\
+	\includegraphics[width=6cm,height=4cm]{figures/CPIAU_ashocks_nmp.png}  
+	\includegraphics[width=6cm,height=4cm]{figures/CPIAU_ashocks.png} \\
 	\smallskip
@@
 		\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} 
-	\caption{ Replicating \citet{coibion2012can}: 1987-2007}
+	\caption{Inflation and Forecasts Moments Responses: 1984-2007}
 	\label{ReplicateCoibionBefore2007}
@@
 
-In Figure \ref{ReplicateCoibionpost2007}, I do the same exercise but include additional uncertainty. This is also the period when SPF provides density forecasts that allow me to estimate uncertainty.
+In Figure \ref{ReplicateCoibionwholeperiod}, I extend the sample period to that is after 2007 to 2019.
+For uncertainty and PCE inflation, data is only avaiable after 2007.
+This is also the period when SPF provides density forecasts that allow me to estimate uncertainty.
 
@@
 	\centering
-	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_nmp_post2007.png}  
-	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_post2007.png} \\
-	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_nmp_post2007.png} 
-	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_post2007.png}  \\
+	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_nmp.png}  
+	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks.png} \\
+	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_nmp.png} 
+	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks.png}  \\
 	\smallskip
-	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp_post2007.png} 
-	\includegraphics[width=6cm]{figures/SPFFE_ashocks_post2007.png} \\
+	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp.png} 
+	\includegraphics[width=6cm]{figures/SPFFE_ashocks.png} \\
 	\smallskip
-	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp_post2007.png} 
-	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_post2007.png} \\
+	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
+	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} \\
 	\smallskip 
-	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp_post2007.png} 
-	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_post2007.png} 
-	\caption{ Replicating \citet{coibion2012can}: 2008-2019}
-	\label{ReplicateCoibionpost2007}
+	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp.png} 
+	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks.png} 
+	\caption{Inflation and Forecasts Moments Responses: 1984-2019}
+	\label{ReplicateCoibionwholeperiod}
 \end{figure}

### 2019-06-27 paper/Draft.tex
Finishing the IR section for whole period with uncertainty.

@@
 %opening
-\title{Rigidity of Expectation: Additional Evidence from Desntify Forecasts}
+\title{Rigidity of Expectation: Additional Evidence from Density Forecasts}
 \author{Tao Wang}
@@
 
-$$\bar \sigma^{*2}_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+\begin{eqnarray}\label{VarREEq}
+\bar \sigma^{*2}_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}
+\end{eqnarray}
 
@@
 Disagreements always exist in NI with the presense of private signals , in contrast, disagreement is zero over the long run in SE.
-The evidence from impulse response of disagreements seem to be more consistent with SE than with NI.}
-
-The responses to monetary policy shocks turn out to be nosier than for technology and oil price shocks, as presented in the right panel of \ref{ReplicateCoibionBefore2007}.
-On the top figure, I first plot the impulse response of inflation to paths surprises and target surprise, seperately.
+}
+
+The responses to monetary policy shocks turn out to be nosier than for technology and oil price shocks, as presented in the right panel of Figure \ref{ReplicateCoibionBefore2007}.
+On the top, I first plot the impulse response of inflation to path surprises $ED8ut$ and target surprise $MP1ut$, seperately.
 On average, inflation reduces by around 10 percentage points after one unit increase of target surprise and increases by 10 percentage points following one unit of path surprise to federal funds rate.
@@
 
-In the middle figure plots the responses of CPI forecast erros by SPF.
+In the middle figure presents the responses of CPI forecast erros by SPF.
 Although the average response seems to go in the same direction of the respective monetary shocks, consistent with the pattern seen for techonology and oil price shocks, none of the responses are statistically significant and the estimates have big standard errors of 10-20 percentage points.
@@
 
-How do we intereprete this finding of non-response of forecasting errror and disagreements to monetary policy shocks in the conext of rigidity models?
-Non-response of FE suggests that on average professional forecaters have incorporated the shock in their forecasts.
+How do we intereprete the finding of non-response of forecasting errror and disagreements to monetary policy shocks in the conext of rigidity models?
+Non-response of FE suggests that on average professional forecaters have incorporated the monetary policy changes in their forecasts.
 Non-response of disagreements could be due to that forecasters ``agree'' on the realization of monetary policy shocks.
-Althouth the benchmark theory of SE and NI do not differentiate shocks, the evidence here seems to suggest that the degree of rigidity depends on the nature of the shocks.
-
-There are other explanations.
-First, overal, the monetary policy shocks contribute only a small part of variation in inflation compared to supply shocks.
+Althouth the benchmark theory of SE and NI do not differentiate shocks, the evidence here seems to suggest that the degree of rigidity depends on  nature of the shocks.
+
+Or there are other explanations.
+First, overal the monetary policy shocks contribute only a small part of variation in inflation compared to supply shocks.
 This was actually used by \cite{coibion2012can} to justify why monetary policy shock was not used in their exercise.
@@
 
-In Figure \ref{ReplicateCoibionwholeperiod}, I extend the sample period to that is after 2007 to 2019.
-For uncertainty and PCE inflation, data is only avaiable after 2007.
-This is also the period when SPF provides density forecasts that allow me to estimate uncertainty.
+In Figure \ref{ReplicateCoibionwholeperiod}, I extend the sample period to include the post-2007 period till 2019.
+Since PCE inflation forecast is avaiable during this period, I report results for both CPI and PCE as in previous analysis.
+Besides, post2007 is the period when SPF surveys density forecasts that allow us to study the dynamics of uncertainty.
+
+The left panel of  Figure \ref{ReplicateCoibionwholeperiod} presents impulse reponses of average uncertainty of SPF in addition to that inflation, forecast error, disagreements in response to technology and oil price shocks.
+As shown in the top three figures, the results are consistent with that in Figure \ref{ReplicateCoibionBefore2007} for period before 2007.
+Oil shock(technology shock) increases(decreases) inflation in the first quarter by 10 percentage  points, whose imapcts last till 7-8th quarters.
+Confidence interval of the responses is smaller compared to previous figure probably due to larger sample size.
+Average forecast errors react partially to the shock and gradually return to zero over the 4-5th quarters afterward.
+Disagreements picked up in the second quarter and return to zero 2 or 3 quarters  later.
+
+The primary focus of this paper is the behavior of uncertainty.
+Its responses to the absolute value of various shocks is presented in the bottom of the panel.
+Since  average uncertainty do not directly depend on the realizations and sizes of the shocks in various models, as shown in Equation \ref{VarREEq}  Equation \ref{VarSEEq}, and Equation \ref{VarNIEq}, the response of uncertainty cannot be used as a screening device of  FIRE and rigidity models.
+Instead, it should be taken as a basic consistency check of different theories with respect to the behavior of uncertainty.
+
+ The response graph seems consistent with this simpel prediction, except for the uncertainty about CPI in responses to oil price shock.
+The responses of average uncertainty is not significantly different from zero throughout 10 quarters.
+\footnote{The impulse response that provides direct checking of rigidity models versus FIRE is the responses of revision in uncertainty, i.e.
+uncertainty about inflation in $t+h$ at time $t$ relative to $t-1$, $t-2$, etc.
+The results will be presented in a revised version of the paper.}
+
+Impacts of monetary policies are shown in the right panel of Figure \ref{ReplicateCoibionwholeperiod}.
+Path surprise to federal funds rate, i.e.
+future monetary policy stances, again brings about the inflationary effect as before.
+One standard deviation of ture tightenning shock increases headlien CPI inflation by around 15 percentage points in the first period.
+In the same time, unexpected rate change does not affect inflation significantly once we include the post-2007 period.
+One possible explanation for this is the small variation of target surprise after financial crisis, as illustrated in Figure \ref{Inflationshocks}.
+Except for the dramatic monetary loosenning during financial crisis, there was little variation in the unexpected federal fund rate change.
+
+Similar to results for pre-2007 period, the initial response of average forecast error to future tightening shock is statistically signifcant in the first period but insignificant soon after.
+Intrestingly, even though the target surprise does not impacts on inflation iteself, forecast errors do react in an inflationary manner.
+The magnitude of the response is as large as 25 percentage points.
+Rigidity models predict forecast errors shoud depend on past shocks, while this does not seem to be the case for monetary policy shocks.
+Forecasters reaction to monetary policy shocks apear to more efficient than for supply shocks.
+
+Disagreements show little response to monetary policy shocks as well, with the only exception being PCE forecast with respect to path surprise.
 

### 2019-06-27 paper/Draft.tex
Finished first drafting of IR section.Empirical tests and stylized facts section left.

@@
 %opening
-\title{Rigidity of Expectation: Additional Evidence from Density Forecasts}
+\title{Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households}
 \author{Tao Wang}
@@
 
-$$y_{t+1} = \rho y_t + \omega_t$$
+\begin{eqnarray}\label{AR_process}
+	y_{t+1} = \rho y_t + \omega_t
+\end{eqnarray}
 
@@
 (3) Monetary policy shocks: target surprise and path surprise in the termiology of \citet{laseen2011anticipated}.
-Target surprise is defined as unexpected change in federal funds rate in a particular dates of FOMC meenting.
+Target surprise is defined as unexpected change in federal funds rate in a particular date of FOMC meenting.
 It is the OLS residual of federal funds rate change in the past federal funds rate.
@@
 		\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} 
-	\caption{Inflation and Forecasts Moments Responses: 1984-2007}
+	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
 	\label{ReplicateCoibionBefore2007}
@@
 
-In Figure \ref{ReplicateCoibionwholeperiod}, I extend the sample period to include the post-2007 period till 2019.
-Since PCE inflation forecast is avaiable during this period, I report results for both CPI and PCE as in previous analysis.
-Besides, post2007 is the period when SPF surveys density forecasts that allow us to study the dynamics of uncertainty.
+In Figure \ref{ReplicateCoibionwholeperiod}, I extend the sample period to include the post-2007 years till 2019.
+Importantly, post2007 is the period when SPF starts surveying density forecasts that allow us to study the dynamics of uncertainty.
+In addition, the post crisis period has been characterized by a number of different features in terms of the behavior of macroeconomy(i.e.
+persistently low inflation) and monetary policy implmentation (i.e.
+emphasis on monetary policy communication and zero lower bound), therefore it is worth examining if the patterns documented by \cite{coibion2012can} remain for the entire period.
+Also, since PCE inflation forecast is not avaiable untill 2007, I report results for both CPI and PCE as in previous analysis.
 
@@
 Similar to results for pre-2007 period, the initial response of average forecast error to future tightening shock is statistically signifcant in the first period but insignificant soon after.
-Intrestingly, even though the target surprise does not impacts on inflation iteself, forecast errors do react in an inflationary manner.
-The magnitude of the response is as large as 25 percentage points.
-Rigidity models predict forecast errors shoud depend on past shocks, while this does not seem to be the case for monetary policy shocks.
+Interestingly, even though the target surprise does not affect inflation iteself, forecast errors do react to it in an inflationary manner.
+The magnitude of the response is as large as 25 percentage points in the first quarter.
+Rigidity models predict forecast errors depend on past shocks, while there does not seem to be strong evidence for this when it comes to monetary policy shocks.
 Forecasters reaction to monetary policy shocks apear to more efficient than for supply shocks.
@@
 Disagreements show little response to monetary policy shocks as well, with the only exception being PCE forecast with respect to path surprise.
+The estimates of these responses are not  significantly from zero throughout the entire horizon.
+Non-response of disagreements could arise if forecasters have incorparated the monetary policy shocks (thus the shock no longer qualified as a ``shock'') , or all forecasters simultaneously incorporating the realization of the monetary shocks.
+In the context of NI model, the disagreements can only arise with the presence of private signals.
+Therefore, monetary policy being a more public signal can help explain the mutted response of disagreements in comparison of the other shocks.
+\footnote{Another explanation is that monetary policy actually coordinates agents' expectations, thus accordingly reduce disagreements, according to \citet{morris2002social}.
+This mechanism can mute the response of disagreements.}
+
+Lastly, average uncertainty do not react to monetary policy shocks in the extended period.
+None of the response is significantly different from zero.
+This is the same with technology and oil price shocks.
 
@@
 	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks.png} 
-	\caption{Inflation and Forecasts Moments Responses: 1984-2019}
+	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
 	\label{ReplicateCoibionwholeperiod}
@@
 
+It is widely documented in the literature that behaviors of households expectations more idiosyncratic in comarison with that of professional forecasters.
+\footnote{For this reason, \cite{carroll2003macroeconomic}, for instance, use median professional forecasts as to approximate ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.
+The monthly data of SCE allows an analysis in a higher frequency but for a shorter period 2013-2019.
+
+As technology shock can only be recovered from quarterly time series of output, I only present results using oil price shock and monetary policy shocks in Figure \ref{SCE_IR}.
+The responses to oil price shocks, target surprise and path surprise are plottd in column 1, 2 and 3, respectively.
+
+Oil price shock increases CPI by  7-8 percentage points in the first period and the imapcts last over the entire 10 months. This is not surprising from the previous results on quarterly data.
+
+Estimated in higher frequency, the response to target surprise is on average 2.5 percentage points and statistically significant in $10\%$ level.
+This confirms the wide practice of the literature that identifies monetary non-netrality using high frequency data.
+In contrast, the inflation responses to path surprise is not significant.
+
+As to the households forecast, the starkly wider confidence band across  shocks and moments seen in Figure \ref{SCE_IR} are not that surprising given the wide dispersion of the forecasts moments of a dramatically larger magnitude seen in Figure \ref{UnceratitnyOtherMoments}.
+
+One of the major patterns arising here is that there is no notable difference in responses to oil price shock versus monetary policy shocks, as seen in professional forecasters.
+Average forecast errors react to none of these shocks and neither do disagreements and uncertainty.
+
+One interesting exception is the response of disagreements to oil price changes.
+Households' disagreements concerning inflation drop by 1 percentage point in the first period after an oil price shock and the response has a reasonably small standard error.
+The drop only lasts for 1 month and immediately return to zero since then.
+This suggests that households are digesting the shock in an efficient manner.
+
+It is widely conjectured (in spite of limited evidence) that salient items such as gasline price plays an improprotionate role in affectign household inflation expectation.
+The evidence presented here seems to be consistent with such a prediction.
+
 \begin{figure}[ht]
@@
 	\includegraphics[width=6cm,height=2cm]{figures/SCEVar_ab_ashocksM.png} 
-	\caption{ Impulse Responses of Inflation and SCE Forecasts to Inflation Shocks}
+	\caption{ Responses of Inflation and Household Forecast Moments: 2013-2019}
 	\label{SCE_IR}
@@
 
+\subsection{Discussion of the results and next step}
+
+This section presents one major additional insight in addition to \cite{coibion2012can}: expectation rigidity is dependent on the type of shock.
+In particular, professional forecasters are slow in digesting oil and technology shock to resolve disagreements and reduce forecast error while react to monetary policy shocks relatively more efficient.
+This is the easiest seen in the non-response or instantaneous response if any of forecast error and disagreements to monetary policy shocks.
+The similar can be said for households, in constrast, for oil price shock instead of monetary policy shocks.
+
+Shock-dependent rigidity is not a default feature in the benchmark rigidity models such as SE and NI, i.e.
+$\omega_t$ in Equation \ref{AR_process}.
+It is true that the distinction of public and private signals within NI provides one possibility of reconciling difference in resposnes to shocks.
+If we interprete different ``shocks'' considered here as noisy signals instead of shocks to fundamental variable as defiend in \ref{AR_process}, then the difference across ``shocks'' in their degree of publicity may acount for the difference in rigidity.
+But this implicitly implies redefining the  framework presentd in this paper.
+
+Moreover, the finding that average uncertainty of fixing horizon by forecasters and households do not react to all the shocks is consistent with the current framework although it does not differentiate rigidity models from FIRE benchmark.
+
+Efficient revision implies  uncertainty drop as much as the volatility of the shock as one approach the terminate date.
+Given the volatility of of different shock are different, this provides the possibility of identifying rigidity by directly comparing the observed revision in uncertainty and that is consistent with the volatility of the shock.
+This will be the next step of the analysis.
+
 \section{Conclusion}

### 2019-06-28 paper/Draft.tex
Finished drafting IR section. Conclusion. Abstracts. Working on stylyzed facts. Tests tables left.

@@
 
+\begin{abstract}
+	Surveys on density forecasts of macroeconomic variable that are not available until recent dacade provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
+This paper first documents the persistent dispersion not only in mean forecast but also in uncertainty about future inflation across economists and households.
+Second,  utilizing the panel data of individual uncertainty, I provde additional test results that reject the null hypothesis of full-information rational expectation (FIRE).
+Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity, but in the same time bears the evidence for shock-dependent nature of the rigidity.
+This sets the stage for estimating shock-specific regidity using uncertainty as the next step of analysis.
+
+\end{abstract}
+
+\newpage
+
 \section{Introduction}
 
-The theories on how agents form expectations in ways deviating from rational expectation(RE) benchmark have proliferated over the past decade.
-On one hand, these theories built upon different micro foundations produce some similar macro patterns.
+Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade.
+This has been also engined by an incresingly welcoming recognition of the use of surveys of macroeconomists in testing theories empirically.
+On one hand, various theories built upon different micro foundations produce some similar macro patterns.
 For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.
 On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.
+
 This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probablistic forecast from both professional forecasters survey and household survey.
 Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models.
-
-The potential contribution lies in the extra insights I may get from using probablistic questions.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \citet{manski2004measuring}.} One obvious advantage of density expectations compared to point one is availability of higher moments, i.e.
-variance of the forecast indicates the dispersion of the forecasts.
-Along time dimension, the dynamics of conditional relative likelihood is a useful indicator of information gain or forecasting efficiency.
+But in the same time, the degree of rigidity apears to be shock-specific and bears the difference to households and professional forecasters.
+
+The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if suveyees are asked to assign their perceived probabilities to a range of variables of the forecast.
+.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \citet{manski2004measuring}.} With density forecasts.
+the variance of indivdual forecast can be estimated as an indicator of the uncertainty.
+Across different vintages of the forecast, the revsion in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency.
 Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions.
-Although the detailed implementation of these tests involves technical difficulties, the ideas are quite clear.
-Lastly, with second moments in individual level expectations, we are allowed to potentialy explore the heterogeneity across agents within one theory.
-For instance, sticky information typically assume a posson update rate for all agents in the economy.
-This is partly due to the fact that available data only allows us to recover single parameter of regidity instead of inter-group heterogeneity.
 
@@
 
-\begin{eqnarray}
+\begin{eqnarray}\label{VarSEEq}
 \begin{aligned}
@@
 
-\subsection{Stylized Facts}
-
-\subsubsection{Different Moments}
-
-Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty asgainst forecast errors and disagreements.
-
-The left  three figures look into the relationship between forecast error and uncertainty. One may expect that  greater ex ante uncertainty implies greater ex post forecast errors.
-
-Another widely made statement is that uncertainty is positively correlated with the level of the inflation. I look into this hypothesis by ploting uncertainty against the realized inflation.
-
-Many literature use disagreements and uncertainty interchangably but they are different objects.
-From the graph, we can also see in general uncertainty captures different information from disagreements.
-This is more so in professional forecaster data.
-There is a more obvious correlation between disgreements and uncertainty.
-
-Once implication from FIRE is that all individuals not only agree on mean but also share same degree of uncertainty.
-While in fact, we observe long-lasting heterogeneity in uncertainty both from professional forecasters and households.
-Figure \ref{IQR_Unceratitny} show that there is  not only dispersion of individual forecasts i.e.
-disagreements, but alslo notable heterogeneity in uncertainty.
-One stylized fact from these observations is that  the dispersion in ucnertainty seems persistent over time.
+\subsection{Stylized facts}
+
+Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty asgainst realized inflation,  forecast errors and disagreements in the first, second and third rows, respectively.
+
+It is widely documented in literature \cite{xxx, xxx} and resonated by anecdotal narrative that high inflation is typically associated with high inflation uncertainty.
+However, the observable correlation of realized inflation and the directly estimated average uncertainty from both  forecasters and households are, if any, negative during the period between 2007-2019.
+In particular, the correlation coefficients are -0.1, -0.05 and -0.24 for SPF's  CPI forecast, SPF's PCE forecast and SCE's CPI expectation.
+This may suggest that during a period of persistently low inflation, the conventiaonl positive redux of inflation and uncertainty is not a good description of the relation of the two.
+
+The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between forecast error and uncertainty.
+Although according to our benchmark frameowork in \ref{theory}, there is no mathematical correlation between the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
+The correlation coefficent of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, resptively.
+Compared to professional forecasts, households forecasts exhibit such a positive correlation.
+
+ The last row in of Figure \ref{UnceratitnyOtherMoments} explores the relationship between disagreements and uncertainty.
+Many empriical literature in macroecoomics use disagreements and uncertainty as if they are similar concepts.
+Partly this confusion in practice is due to difficulty of finding the appropriate measure of this in the first place.
+But as we have presented in \ref{theory}, the two are distinct concepts.
+The empricial pattern of the two,  as shown in the plots, also confirms that the two are different objects.
+The correlation coefficients of the two turn out to be negative, -0.29 and -0.46 for SPF forecasts.
+In stark contrast, households seem to bear a strong correlation of 0.62 between the two moments.
+
+Although the sheer magnitudes of the differences between professionals' moments and those of houseolds are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency.
+In particular, the positive correlation across households' ex ante uncertainty, ex post forecat errors, and cross-section disagreements cannot be completely reconciled by the framework we set up in \ref{theory}.
+
+The presence of persistent disagreements in expectations has been used as  important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
+A similar fact checking can be done with respect to individual uncertaintiy.
+FIRE predicts individual share equal degree of uncertainty as we clearly seen in Equation \ref{VarREEq}.
+In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEEq}).
+NI allows for possibility of homogeneity in uncertainty only under sringent condistion of the same precesions of the signals and the same prior of uncertainty.
+Therefore, precense of dispersion of uncertainty across agents can be read against FIRE.
+
+Figure \ref{IQR_Unceratitny} plots the median forecsts along its 25/75 percentiles on the left column and its counterpart in uncertainty in the righ coumn.
+it is clear that not only there is long-lasting dispersion in individual forecasts i.e.
+disagreements, but alslo notable heterogeneity in uncertainty across agents.
+----------------------------
 
@@
 	\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
+	\includegraphics[width=4.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
+		\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}\\
+	  	\smallskip
 		\includegraphics[width=4.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
-	\includegraphics[width=4.5cm]{figures/CPI_disg_varSPFCPIQ.png}\\
-	\smallskip
-	\includegraphics[width=4.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
 	\includegraphics[width=4.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
-	\includegraphics[width=4.5cm]{figures/PCE_disg_varSPFPCEQ.png}\\
-	\smallskip	
-	\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}
-	\includegraphics[width=4.5cm]{figures/SCE_FE_varSCEM.png}
+		\includegraphics[width=4.5cm]{figures/SCE_FE_varSCEM.png}\\
+	\smallskip	
+	\includegraphics[width=4.5cm]{figures/CPI_disg_varSPFCPIQ.png}
+	\includegraphics[width=4.5cm]{figures/PCE_disg_varSPFPCEQ.png}
 	\includegraphics[width=4.5cm]{figures/Q9_disg_varSCEM.png}\\
@@
 
-\subsection{Test of Null Hypothesis of Rational Expectation}
+\subsection{Test of null hypothesis of rational expectation}
 
@@
 
-\subsection{Additional Evidence from Uncertainty}
+\subsection{Additional evidence from uncertainty}
 
@@
 
-\subsection{Evidence from Households}
+\subsection{Evidence from households}
 
@@
 
+In summary, three major conclusions can be drawn from this paper.
+First, full information rational expectation implicitly assumes agents share the common information and agree on the model that generates the data.
+Therefore, agents do not only agree on the mean forecast of a macroeconomic variable but also share the same degree of uncertainty.
+The empirical dispersion of individual uncertainty in future inflation seems to be inconsistent with this simple prediction.
+
+Second, rigidity of expectation from either inattention or underreaction due to noisiness of the signals imply agents do not revise forecasts as efficienctly as they do in FIRE in the face of new information.
+This can be seen from both a sluggish pattern of forecast revision or uncertainty reduction across differen vintages of the forecast.
+A weaker test of this spirit uses change of forecasts with fixed horizon.
+These tests support rigidity models in addition to other null hypotheses of rational expectation including unbiasedness,  non-serial-correlation of forecast error.
+etc.
+
+Lastly, the directly estimated response of households and professional forecasters' expectation to shocks to inflation suggest that rigidity differs across the shocks.
+In particular, professional forecasters are more responsive to monetary policy shocks and households are more responsive to oil price shocks.
+This motivates next-step anlysis of how much resolution of uncertainty can be attributed to the volatility of various shocks.
+This shows the use of uncertainty.
+
+So far, the dynamics of moments are separately estimated for each moment.
+Therefore, as a natural extension of the current analysis, one can  undertake a generalized method of moment (GMM) estimation that simultaneously utilize multi-moment restrictions to recover a better estimate of the rigidity parameters.
+This will provide a better parameter that can be used in structural macro models that build in rigidity of expectations.
+
 \bibliographystyle{apalike}

### 2019-06-28 paper/Draft.tex
finished drafting of stylized fact section. test section and introduction left.

@@
 This paper first documents the persistent dispersion not only in mean forecast but also in uncertainty about future inflation across economists and households.
-Second,  utilizing the panel data of individual uncertainty, I provde additional test results that reject the null hypothesis of full-information rational expectation (FIRE).
+Second,  utilizing the panel data of individual uncertainty, I provide additional test results that reject the null hypothesis of full-information rational expectation (FIRE).
 Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity, but in the same time bears the evidence for shock-dependent nature of the rigidity.
@@
 Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade.
-This has been also engined by an incresingly welcoming recognition of the use of surveys of macroeconomists in testing theories empirically.
+This has been also engined by an incresingly welcoming recognition of the use of surveys by macroeconomists in testing theories empirically.
 On one hand, various theories built upon different micro foundations produce some similar macro patterns.
@@
 
-\begin{eqnarray}
+\begin{eqnarray}\label{VarNIEq}
 \Sigma_{i,t+h|t} = \rho^{2h} \underbrace{\Sigma_{i,t}}_{\Sigma_{i,t|t}} + \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega}
@@
 
-Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty asgainst realized inflation,  forecast errors and disagreements in the first, second and third rows, respectively.
+Although the sheer magnitudes of the differences between professionals' moments and those of houseolds are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency.
+Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty against realized inflation,  forecast errors and disagreements in the first, second and third rows, respectively.
 
@@
 
-Although the sheer magnitudes of the differences between professionals' moments and those of houseolds are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency.
-In particular, the positive correlation across households' ex ante uncertainty, ex post forecat errors, and cross-section disagreements cannot be completely reconciled by the framework we set up in \ref{theory}.
-
-The presence of persistent disagreements in expectations has been used as  important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
+Overall, professional forecasters' moments exhibit patterns more consistency from a statistical point of view.
+In constrast, the positive correlation across households' ex ante uncertainty, ex post forecat errors, and cross-section disagreements cannot be easily reconciled by the framework we set up in Section \ref{theory}.
+
+Persistent disagreements in expectations has been used as an important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
 A similar fact checking can be done with respect to individual uncertaintiy.
-FIRE predicts individual share equal degree of uncertainty as we clearly seen in Equation \ref{VarREEq}.
+FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREEq}.
 In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEEq}).
-NI allows for possibility of homogeneity in uncertainty only under sringent condistion of the same precesions of the signals and the same prior of uncertainty.
+NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precesion of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
 Therefore, precense of dispersion of uncertainty across agents can be read against FIRE.
 
-Figure \ref{IQR_Unceratitny} plots the median forecsts along its 25/75 percentiles on the left column and its counterpart in uncertainty in the righ coumn.
-it is clear that not only there is long-lasting dispersion in individual forecasts i.e.
+Figure \ref{IQR_Unceratitny} plots the median inflation expectation along its 25/75 percentiles in the left and its counterpart in uncertainty in the righ coumn.
+Not only there is long-lasting dispersion in individual forecasts, i.e.
 disagreements, but alslo notable heterogeneity in uncertainty across agents.
-----------------------------
-
-Another prediction from FIRE is that there is unambigous uncertainty reduction as one appraoches to the date of realization.
-Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty.
-The the more negative the revision lies in, the more rational of the forecast.
+And not surprisingly, the dispersion of both forecasts and uncertainty of households are both of a much greater magnitude than that of the professionals.
+The 25/75 inter-quantile-range of households point forecasts is 4-5 percentage points compared to 1 percentage point of professionals.
+And the IQR of uncertainty of housheolds are around 150-200 times(12-14 times for standard deviation) as that of professional forecasters.
+
+Beside, there are cross-agent-type difference and similarity in terms of distribution of uncertainty.
+Households' uncertainty are more skewed toward to the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty.
+This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernal density estimated distribution of uncertainty by year on.
+What is common for both types of agents is that the dispersion in uncertainty is persistent over time and do not show much time-variation.
+
+Another pattern worth discussing in Figure \ref{IQR_Unceratitny} is that there is a notable rise in the dispersion of professional forecasts in the recent 2-3 years, primarily driven by an increase of upper side of the forecast (i.e.
+75 percentile forecast increases from 1\% to 2\%).
+\footnote{This should be interpreted with causion since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UnceratitnyOtherMoments} actually exihibits a gradual decline.
+} This is consistent with the observation in top left two figures Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flatten.
+
+Another prediction from FIRE is that there is an unambigous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
+Although quantitatively, it is hard to check this directly, at least qualitatively, one can look at the distribution of the uncertainy revision concentrate in the negative range.
+Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty from 1-year-ahead forecast in year $t-1$ to the current-year nowcast in year $t$.
+The more negative range in which the revision lies, the more ``rational'' of the forecast.
+Looking from the histograms, the uncertainty revision is indeed centerred around zero while slightly showing left-skewness.
+Overall, more forecasters fell more certainy for nowcast compared to his forecast one year before.
+Unfortunately, since SCE does not provide the data structure that allows us to look at revision, we cannot make a comparison between two types of agents.
+A form test of revision equal to zero or being negative will be carried out in the Section \ref{NullTest}.
 
@@
 	\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png}  \\
-	\caption{Distribution of Revision in Forecasts}
+	\caption{Distribution of Revision in Forecasts and Uncertainty}
 	\label{RevisionHist}
@@
 
-\subsection{Test of null hypothesis of rational expectation}
+\subsection{Test of null hypothesis of rational expectation}\label{NullTest}
 
@@
 Target surprise is defined as unexpected change in federal funds rate in a particular date of FOMC meenting.
-It is the OLS residual of federal funds rate change in the past federal funds rate.
+It is the OLS residual of federal funds rate change in the past expected change in federal funds rate.
 The 2-year ahead path surprise is the regression residual of future implied federal funds rate on the target surprise.

### 2019-06-28 paper/Draft.tex
Finished FE-based test part

@@
 
-$$\overline{FE}^{*}_{i,t+h|t} = \sum^{h-1}_{s=1} \rho^s \omega_{t+h-s}$$
+\begin{eqnarray}\label{NoPastInfFE}
+\overline{FE}^{*}_{i,t+h|t} = \sum^{h-1}_{s=1} \rho^s \omega_{t+h-s}
+\end{eqnarray}
 
@@
 
-$$Cov(\overline{FE}^{*}_{t+h|t}, \overline{FE}^{*}_{t+s+h|t+s}) = 0 \quad \forall s \geq h$$
+\begin{eqnarray}\label{NoSerialCorrFE}
+Cov(\overline{FE}^{*}_{t+h|t}, \overline{FE}^{*}_{t+s+h|t+s}) = 0 \quad \forall s \geq h
+\end{eqnarray}
 
@@
 
-Another prediction from FIRE is that there is an unambigous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
-Although quantitatively, it is hard to check this directly, at least qualitatively, one can look at the distribution of the uncertainy revision concentrate in the negative range.
+FIRE also predicts an unambigous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
+Although quantitatively it is hard to check this, one can look if the distribution of the uncertainy revision concentrate in the negative range.
 Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty from 1-year-ahead forecast in year $t-1$ to the current-year nowcast in year $t$.
 The more negative range in which the revision lies, the more ``rational'' of the forecast.
-Looking from the histograms, the uncertainty revision is indeed centerred around zero while slightly showing left-skewness.
-Overall, more forecasters fell more certainy for nowcast compared to his forecast one year before.
-Unfortunately, since SCE does not provide the data structure that allows us to look at revision, we cannot make a comparison between two types of agents.
-A form test of revision equal to zero or being negative will be carried out in the Section \ref{NullTest}.
+Looking from the histograms, uncertainty revision shows left-skewness relative to zero.
+This implies on average,  more forecasters feel more certain for her nowcast relative to her forecast made one year before.
+Unfortunately, since SCE does not provide the data structure for this purpose, we cannot make a comparison between two types of agents.
+A formal test of revision equal to zero or being negative will be carried out in the Section \ref{NullTest}.
 
@@
 
-In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section mostly following \citet{mankiw2003disagreement}.
-
-The first set of tests utilize the dynamics of forecast errors.
-First, the forecast error should be on average unbiased.
-The forecast error should converge to zero.
-Second, forecast errors of non-overlapping forecasting horizon are not serially correlated.
-Third, forecast errors should not be predicted by any information available at the time of forecast, including the forecast itself and other variable that is in the agent's information content.
+This section first reproduces the results of a list of statistical tests of FIRE used in the existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests replying upon data of individual uncertainty in Table \ref{RevEfficency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
+It can be seen as an extension of what \citet{fuhrer2018intrinsic} does to mean forecast to uncertainty.
+
+The first set of tests, hereafter, referred as FE-based tests, utilize the moment restrictions on forecast errors.
+In plain words, the null hypothesis of the three tests are the following.
+First, since the forecasts are on average unbiased according to FIRE, forecast errors across agents should converge to zero in large sample.
+Second, forecast errors of non-overlapping forecasting horizon are not serially correlated (Equation \ref{NoSerialCorrFE} ).
+Third, forecast errors cannot be predicted by any information available at the time of forecast, including the mean forecast itself and other variable that is in the agent's information content.
+This follows from Equation \ref{NoPastInfFE}.
+In addition, I include what is called weak version of the FE-based test which explores the serial correlation of forecast erros in overlapping periods,  i.e.
+1-year-ahead forecasts within one year.
+The forecast errors are correlated to the extent of the realized shocks in the overlapping periods.
+So the positve serial correlation does not direct violate FIRE.
+For this reason, looking into the correlation of overlapping forecast errors still contain the useful information about the size of the realized shocks.
+
+FE-based tests results are prensented in Table \ref{NullTestTable}.
+Individual level data are used thanks to the panel structure of both surveys.
+But since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE.
+Also,the regresions are adjusted corresponding to the quarterly and monthly frequency of SPF and SCE.
+Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.
+
+First,  all three forecast series easily reject the unbiasedness test in the significance level of $1\%$. There is upward bias across professional forecasters and households \footnote{\citet{
+coibion2018firms}finds the same for firms.}, while unsurprisingly, the bias is almost 20 times of that for professional forecaters(2.2 versus 0.12) for headline CPI.
+
+Second, the point forecast one year ago predicts the forecat errors for professionals in the significance level of 1\%.
+For headline CPI inflation, for instance, one percentage point inflation forecast corresponds to 0.3 percentage points of the forecast errors one year later.
+Thus test 2 in Table \ref{NullTestTable} easily rejects the second hypothesis test of FIRE that past information does not predict future forecast errors.
+
+Third, forecast errors can be predicted by forecast errors one year ago with a significant coefficient of around $0.08$ for headline CPI and $0.05$ for PCE, as seen in test 3 of Table \ref{NullTestTable}.
+Errors of non-overlapping forecastign periods are correlated, against the null of FIRE.
+
+Lastly, test 4 in Table \ref{NullTestTable} presents higher serial correlation of forecast errros produced within a year.
+For SPF forecasts, the serial correlation does not exist beyond 1 quarter, implying relative efficiency of forecasts.
+For the households, the forecast errors are more persisent over the entire year in that current forecat errors are correlated with all past forecast errors over the past three quarters.
+Again, although the persistency of forecast errors in 1-year inflation withon a year do not directly violate FIRE, the fact that households forecast errors being more persistent with professionals provide useful clues about the relative rigidity of the two types of agents.
 
@@
 	\hline 
-	\multicolumn{4}{l}{Test 1: Bias}                                                           \\
+	\multicolumn{4}{l}{Test 1: Unbiasedness}                                                           \\
 	\hline 
@@
 	\hline 
-	\multicolumn{4}{l}{Test 2: FE depends on past information}                                  \\
+	\multicolumn{4}{l}{Test 2: FE does not depend on past information}                                  \\
 	\hline 
@@
 	\hline 
-	\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons are serially correlated} \\
+	\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons not serially correlated} \\
 	\hline 
@@
 
-\section{Responses of Expectations to Inflation Shocks }\label{IRShocks}
+\section{Shock-based tests of expectation rigity }\label{IRShocks}
 

### 2019-06-28 paper/Draft.tex
working on revision efficency test. need to improve explaining revision tests

@@
 
-First,  all three forecast series easily reject the unbiasedness test in the significance level of $1\%$. There is upward bias across professional forecasters and households \footnote{\citet{
-coibion2018firms}finds the same for firms.}, while unsurprisingly, the bias is almost 20 times of that for professional forecaters(2.2 versus 0.12) for headline CPI.
+First,  all three forecast series easily reject the unbiasedness test in the significance level of $1\%$.
+There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecaters(2.2 versus 0.12) for headline CPI.
 
@@
 For the households, the forecast errors are more persisent over the entire year in that current forecat errors are correlated with all past forecast errors over the past three quarters.
-Again, although the persistency of forecast errors in 1-year inflation withon a year do not directly violate FIRE, the fact that households forecast errors being more persistent with professionals provide useful clues about the relative rigidity of the two types of agents.
+Again, although the persistency of 1-year forecast errors within one year do not directly violate FIRE, the fact that households' forecast errors being more persistent than professionals provide useful clues about the relative rigidity of the two types of agents.
 
@@
 
-The second batch of tests in Table \ref{RevEfficency} focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \citet{nordhaus1987forecasting} and \citet{fuhrer2018intrinsic}.
-In particular, I follow the model specifications in \citet{fuhrer2018intrinsic}.
-According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information.
-For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.
-A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
+The second batch of tests in Table \ref{RevEfficency} focus on testing forecasting efficiency using revisions of mean forecasts and uncertainty, as referred as Revision-based test.
+
+In plain words, it checks if the revision from 1-year-ahead forecast to nowcast of current-year inflation is efficient by two criteria.
+(1) Forecast revision does not depend on past information, including the past revisions of forecast.
+(2) Drop in uncertainy are not serially correlated.
+
+ \citet{fuhrer2018intrinsic}'s test for mean forecast revision takes the following form(using 1 period revision as an exampl).
+
+\begin{eqnarray}\label{RevEffMeanTest}
+y_{i,t+1|t+1} - y_{i,t+1|t}=\alpha + \beta (y_{i,t+1|t} - y_{i,t+1|t-1})+\epsilon_{i,t+1}
+\end{eqnarray}
+
+$\beta =0$ according to FIRE, because rational forecast revision only responds to newly realized shocks thus it is note predictable by past revisions.\footnote{Adding $y_{t+1|t}$ to both sides of Equation \ref{RevEffMeanTest} gives an equivalent null hypothesis used by \citet{fuhrer2018instrinsic}: coefficient of regression of $y_{t+1|t+1}$ on  $y_{t+1|t}$ is $1-\beta=1$.
+} Since we have four vintages of the forecasts from SPF, we can check if the revision in nowcasting are serially correlated with 1-year-ahead forecats in previous three quarters.
+
+-----------------------------
 
@@
 
-The weak efficiency tests use change in forecast and uncertainty instead of revisions.
+A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
+Table \ref{WeakRevEfficiency} present the results.
+
+Weak efficiency tests use change in forecast and uncertainty instead of revisions.
 This is not a direct test of the null of FIRE as we have discussed that the rigidity models do not have direct testable predictions about the change in forecast and uncertainty with fixed forecast horizon.

### 2019-06-28 paper/Draft.tex
almost finished test results section.need a short summary.

@@
 	Surveys on density forecasts of macroeconomic variable that are not available until recent dacade provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
-This paper first documents the persistent dispersion not only in mean forecast but also in uncertainty about future inflation across economists and households.
-Second,  utilizing the panel data of individual uncertainty, I provide additional test results that reject the null hypothesis of full-information rational expectation (FIRE).
-Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity, but in the same time bears the evidence for shock-dependent nature of the rigidity.
+This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households.
+Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE).
+Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.
 This sets the stage for estimating shock-specific regidity using uncertainty as the next step of analysis.
@@
 
-\begin{eqnarray}\label{VarREEq}
+\begin{eqnarray}\label{VarREPop}
 \bar \sigma^{*2}_{t+h|t+k} = \sum^{h-k}_{s=1}\rho^{2s} \sigma^2_{\omega}
@@
 
-$$\sigma^2_{i,t|t-\tau}= \sum^{h+\tau}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+\begin{eqnarray}\label{VarSEInd}
+	\sigma^2_{i,t|t-\tau}= \sum^{h+\tau}_{s=1}\rho^{2s} \sigma^2_{\omega}
+\end{eqnarray}
 
@@
 
-\begin{eqnarray}
+\begin{eqnarray}\label{VarSEPop}
 \begin{aligned}
@@
 
-\begin{eqnarray}\label{VarSEEq}
+\begin{eqnarray}\label{VarSERv}
 \begin{aligned}
@@
 A similar fact checking can be done with respect to individual uncertaintiy.
-FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREEq}.
-In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEEq}).
+FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREInd}.
+In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEInd}).
 NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precesion of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
@@
 Individual level data are used thanks to the panel structure of both surveys.
-But since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE.
-Also,the regresions are adjusted corresponding to the quarterly and monthly frequency of SPF and SCE.
+Since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE.
+Also,the regresions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE.
 Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.
@@
 
-The second batch of tests in Table \ref{RevEfficency} focus on testing forecasting efficiency using revisions of mean forecasts and uncertainty, as referred as Revision-based test.
-
-In plain words, it checks if the revision from 1-year-ahead forecast to nowcast of current-year inflation is efficient by two criteria.
-(1) Forecast revision does not depend on past information, including the past revisions of forecast.
-(2) Drop in uncertainy are not serially correlated.
-
- \citet{fuhrer2018intrinsic}'s test for mean forecast revision takes the following form(using 1 period revision as an exampl).
+The second batch of tests in Table \ref{RevEfficency} focus on estimating forecasting efficiency using revisions of mean forecasts and uncertainty, hereafter referred as revision-based tests.
+In plain words, the revision from 1-year-ahead forecast to nowcast of current-year inflation is efficient according two criteria (1) Forecast revision does not depend on past information, including the past revisions.
+(2) Drop in uncertainy is sufficiently rapid to reflect the uncertainty of all realized shocks.
+
+The mean revision test by \citet{fuhrer2018intrinsic} takes the following form (using 1 period as an example):
 
@@
 
-$\beta =0$ according to FIRE, because rational forecast revision only responds to newly realized shocks thus it is note predictable by past revisions.\footnote{Adding $y_{t+1|t}$ to both sides of Equation \ref{RevEffMeanTest} gives an equivalent null hypothesis used by \citet{fuhrer2018instrinsic}: coefficient of regression of $y_{t+1|t+1}$ on  $y_{t+1|t}$ is $1-\beta=1$.
-} Since we have four vintages of the forecasts from SPF, we can check if the revision in nowcasting are serially correlated with 1-year-ahead forecats in previous three quarters.
-
------------------------------
+In the above equation $\beta =0$ according to FIRE, because rational forecast revision only responds to newly realized shocks thus it is not predictable by past revisions.\footnote{Adding $y_{t+1|t}$ to both sides of Equation \ref{RevEffMeanTest} gives an equivalent null hypothesis used by \citet{fuhrer2018intrinsic}: coefficient of regression of $y_{t+1|t+1}$ on  $y_{t+1|t}$ is $1-\beta=1$.
+}.
+Since we have four vintages of the forecasts from SPF, the above specification can include lagged revisions up to 4 quarters.
+
+The test with uncertainy simply replaces the revision of forecast with revision in uncertainty $\sigma^2_{i,t+1|t+1} - \sigma^2_{i.t+1|t}$, for instance.
+This regresion follows from Equation \ref{VarSERv} for SE and Equation \ref{VarNIRv} for NI.
+Although it  cannot be directly used as a test against FIRE null, the autocorrelation coefficient speaks to the speed of drop in uncertainty.
+Depending on the model, one can interprete it as the particular structural parameter of rigidty, as shown in Figure \ref{rigidity}.
+
+Top panel in Table \ref{RevEffMeanTest} and bottom panel presents the results for mean forecast.
+Following \citet{fuhrer2018intrinsic}, I include median forecast available at time $t$ and $t-1$ as an indicator of past information for the revision regression.
+In the first column of each panel, I report the regression on a constant.
+
+What's surprising is the mean revision in forecast being negative and significant.
+Forecaters on average make downward adjustment of 1.26 percentage points of CPI and  1.1 perentage points of PCE from her previous year forecast of the same-period inflation.
+
+The second to fourth columns of each panel in Table \ref{RevEfficency} checks auto correlation of revisions including different lags.
+Revisions of forecasts are serially correlated over 4 quarters and the coefficients are all positive and significant.
+Also, the median forecasts as the past information always predicts a negative revision with significant coefficients.
+This is evidence against null hypothesis of FIRE and my estiamtes are comparable with those by \citet{fuhrer2018intrinsic}.
+
+In the bottom panel reports auto regression results for revision in uncertainty.
+Again, the first column first test the mean revision against the null being zero.
+The mean revisions in uncertainty are both negative(0.5-0.6 percentage poitns equivalence in standard devation of uncertainty) and statistically sigificant, confirming our observation from Figure \ref{RevisionHist} that forecaters are more certain about current inflation compared her previous year forecast.
+
+The second to fourth column rejects the null of non-serial correlation for both CPI and PCE forecasts.
+The revision to CPI seems more efficient as serial correlation is with only one quarter lag.
+For PCE, the revisions in uncertainty are serially correlated with all past three quarters.
 
@@
 
-A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
-Table \ref{WeakRevEfficiency} present the results.
-
-Weak efficiency tests use change in forecast and uncertainty instead of revisions.
-This is not a direct test of the null of FIRE as we have discussed that the rigidity models do not have direct testable predictions about the change in forecast and uncertainty with fixed forecast horizon.
-But in the same time, the auto regression features do speak to the persistence of the forecasts over the time horizon.
-In particular, if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
+Table \ref{WeakRevEfficiency} presents the results with the revision replaced with change in mean forecasts and uncertainty, i.e.
+$y_{t|t-1}$ to $y_{t+1|t}$.
+The auto-correlation of change in mean forecast and uncertainty does embed  tests of null of FIRE (Equation \ref{VarREPop}).
+But if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
 
@@
 
-In Figure \ref{Inflationshocks}, all four shocks plus the unexplained component of inflation are plotted in quarterly between 1985-2019.
-All shocks are normalized by its respective sample standard deviations.
+In Figure \ref{Inflationshocks}, all four shocks are plotted in quarterly between 1985-2019. All shocks are normalized by its respective sample standard deviations.
 
@@
 Its responses to the absolute value of various shocks is presented in the bottom of the panel.
-Since  average uncertainty do not directly depend on the realizations and sizes of the shocks in various models, as shown in Equation \ref{VarREEq}  Equation \ref{VarSEEq}, and Equation \ref{VarNIEq}, the response of uncertainty cannot be used as a screening device of  FIRE and rigidity models.
+Since  average uncertainty do not directly depend on the realizations and sizes of the shocks in various models, as shown in Equation \ref{VarREEq}  Equation \ref{VarSEPop}, and Equation \ref{VarNIEq}, the response of uncertainty cannot be used as a screening device of  FIRE and rigidity models.
 Instead, it should be taken as a basic consistency check of different theories with respect to the behavior of uncertainty.

### 2019-06-28 paper/Draft.tex
Finalized before2007 IR charts. Need to label them more clearly

@@
 
-\begin{eqnarray}
+\begin{eqnarray}\label{VarNIRv}
 \begin{aligned}
@@
 
-\begin{eqnarray}
+\begin{eqnarray}\label{VarNIIndPop}
 \Delta \Sigma_{i,t+h|t} = \rho^{2h}\Delta  \Sigma_{i,t|t}  - \rho^{2h} \sigma^2_{\omega}
@@
 
-This section first reproduces the results of a list of statistical tests of FIRE used in the existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests replying upon data of individual uncertainty in Table \ref{RevEfficency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
-It can be seen as an extension of what \citet{fuhrer2018intrinsic} does to mean forecast to uncertainty.
+This section first reproduces a number of statistical tests of FIRE used seen existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests relying on uncertainty in Table \ref{RevEfficency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
+It is an extension of what \citet{fuhrer2018intrinsic} does to mean forecast to uncertainty.
 
@@
 
-Top panel in Table \ref{RevEffMeanTest} and bottom panel presents the results for mean forecast.
+Top panel in Table \ref{RevEfficency} and bottom panel presents the results for mean forecast.
 Following \citet{fuhrer2018intrinsic}, I include median forecast available at time $t$ and $t-1$ as an indicator of past information for the revision regression.
@@
 
-The second to fourth column rejects the null of non-serial correlation for both CPI and PCE forecasts.
+The second to fourth column show positive serial correlation of revision in uncertainty for both CPI and PCE forecasts.
 The revision to CPI seems more efficient as serial correlation is with only one quarter lag.
@@
 	\centering
-	\includegraphics[width=6cm,height=4cm]{figures/CPIAU_ashocks_nmp.png}  
-	\includegraphics[width=6cm,height=4cm]{figures/CPIAU_ashocks.png} \\
-	\smallskip
-	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp.png} 
-		\includegraphics[width=6cm]{figures/SPFFE_ashocks.png} \\
-	\smallskip
-	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
-		\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} 
+	\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
+	\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_before2007.png} \\
+	\smallskip
+	\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
+		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_before2007.png} \\
+	\smallskip
+	\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
+		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
 	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}

### 2019-06-29 paper/Draft.tex
finalized ir graphs for whole period

@@
 	\centering
-	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_nmp.png}  
-	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks.png} \\
-	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_nmp.png} 
-	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks.png}  \\
-	\smallskip
-	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp.png} 
-	\includegraphics[width=6cm]{figures/SPFFE_ashocks.png} \\
-	\smallskip
-	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
-	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} \\
-	\smallskip 
-	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp.png} 
-	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks.png} 
+	\includegraphics[width=7cm]{figures/Inf_ashocks_nmp.png}  
+	\includegraphics[width=7cm]{figures/Inf_ashocks.png} \\
+	\smallskip
+	\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp.png} 
+	\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} \\
+	\smallskip
+	\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
+	\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} \\
+	\smallskip 
+	\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks_nmp.png} 
+	\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks.png} 
 	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}

### 2019-06-29 paper/Draft.tex
first typo cheacking. need to do it again after finalizing everything

@@
 	\begin{abstract}
-	Surveys on density forecasts of macroeconomic variable that are not available until recent dacade provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
+		Surveys on density forecasts of macroeconomic variable that are not available until recent two decades provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
 This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households.
 Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE).
-Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.
-This sets the stage for estimating shock-specific regidity using uncertainty as the next step of analysis.
+Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.
+This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.
 
@@
 	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade.
-This has been also engined by an incresingly welcoming recognition of the use of surveys by macroeconomists in testing theories empirically.
+This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing theories empirically.
 On one hand, various theories built upon different micro foundations produce some similar macro patterns.
@@
 
-This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probablistic forecast from both professional forecasters survey and household survey.
+	This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probabilistic forecast from both professional forecasters survey and household survey.
 Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models.
-But in the same time, the degree of rigidity apears to be shock-specific and bears the difference to households and professional forecasters.
-
-The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if suveyees are asked to assign their perceived probabilities to a range of variables of the forecast.
-.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \citet{manski2004measuring}.} With density forecasts.
-the variance of indivdual forecast can be estimated as an indicator of the uncertainty.
-Across different vintages of the forecast, the revsion in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency.
+But in the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.
+
+	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of variables of the forecast.
+.\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.} With density forecasts.
+the variance of individual forecast can be estimated as an indicator of the uncertainty.
+Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency.
 Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions.
@@
 So we can simply denote the variable as $y_{t+h}$.
-To put it another way, all agents are foreasting the same object.
+To put it another way, all agents are forecasting the same object.
 \footnote{Only in the context of forecasting aggregate variable, it is meaningful to study the average expectations and disagreements across agents.}
@@
 The specific content contained in $I_t$ varies from different models of expectation.
-For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instataneously.
+For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instantaneously.
 So the information set may not contain the most recent realization of the variable of forecast $y_t$.
@@
 
-Similarly, individual forecasting variance $\sigma_{i,t+h|t}$, hereafter termed as indiviual uncertainty in this paper, is the conditional variance.
+	Similarly, individual forecasting variance $\sigma_{i,t+h|t}$, hereafter termed as individual uncertainty in this paper, is the conditional variance.
 
@@
 
-Individual forecast error $FE_{i,t+h|t}$ is the difference of ex post realized value of $y_{t+h}$ and individual foreacast at time $t$.
+	Individual forecast error $FE_{i,t+h|t}$ is the difference of ex post realized value of $y_{t+h}$ and individual forecast at time $t$.
 
@@
 
-A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empricial tests of this kind include \citet{xx}.\citet{xx} etc. }
+	A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empirical tests of this kind include \citet{xx}.\citet{xx} etc. }
 
@@
 	As the forecasting horizon decreases relative to a given future point of time, there is a pure efficiency gain or reduction in uncertainty as more and more shocks have realized.
-So the uncertainty should drop unambigously.
+So the uncertainty should drop unambiguously.
 
 	An equivalent interpretation to this is through the perspective of revision.
-Defining the forecast revision as the difference of different vintages of foreacsts fixing the terminate date, the revision in uncertainty should be always negative and the drop should be exactly equal to discounted variance of the realized shocks.
+Defining the forecast revision as the difference of different vintages of forecasts fixing the terminate date, the revision in uncertainty should be always negative and the drop should be exactly equal to discounted variance of the realized shocks.
 \footnote{Compared to other null hypotheses discussed above, this is a weaker test.
-It is true that rational foreacsting implies reduction in uncertainty with shorter horizon.
+It is true that rational forecasting implies reduction in uncertainty with shorter horizon.
 But there is no direct test if the drop in uncertainty is efficient enough so as to be consistent with FIRE.
@@
 
-The theory of sticky expectation (\citet{xx}, \citet{xx} ), regardless of its different microfoundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
-One of the most tractable models assume there is a homogenous Possion rate $\lambda$ of updating among the population.
-Specificaly, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.
+	The theory of sticky expectation (\citet{xx}, \citet{xx} ), regardless of its different micro-foundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
+One of the most tractable models assume there is a homogenous Poisson rate $\lambda$ of updating among the population.
+Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.
 
@@
 So setting $\tau =1$ in above equation gives the reduction in uncertainty in FIRE.
-One can easily see that the reduction in ucnertainty is greater in SE for any $\tau>1$ than FIRE.
+One can easily see that the reduction in uncertainty is greater in SE for any $\tau>1$ than FIRE.
 
@@
 
-It is important to note that the rigidity in updating according to SE cannot be systamatically observable in the individual level, both in terms of forecasts errors and uncertainty.
-This is because the behaviors of each individual foreacst specifically depends on if the she updates or not in that period.
+	It is important to note that the rigidity in updating according to SE cannot be systematically observable in the individual level, both in terms of forecasts errors and uncertainty.
+This is because the behaviors of each individual forecast specifically depends on if the she updates or not in that period.
 
@@
 
-One well known prediction from SE literature is that the average foreacast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
+	One well known prediction from SE literature is that the average forecast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
 \footnote{See \citet{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$.
@@
 
-Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibites serial correlation described as below in a similar spirt of forecast errors.
+	Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibits serial correlation described as below in a similar spirt of forecast errors.
 It is equal to a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart.
@@
 The first component is the inefficiency sourced from stickiness of updating.
-The higher rigidity (lower $\lambda$), the smaller the efficieny gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.
+The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.
 
@@
 		\item Individual uncertainty need not unambiguously drop with shorter horizon. 
-\item Population mean forecast paritially responds to shocks and with lags. 
+		\item Population mean forecast partially responds to shocks and with lags. 
 		\item Forecast errors are serially correlated. 
 		\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
-\item Population average uncertaity revision is serially correlated and underreacts to volatility of the shocks.
+		\item Population average uncertainty revision is serially correlated and underreacts to volatility of the shocks.
 
@@
 	What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$.
-Specificaly, mean forecast of individual $i$ is the posterior mean of based on her prior and realized signals $s_i$.
+Specifically, mean forecast of individual $i$ is the posterior mean of based on her prior and realized signals $s_i$.
 
@@
 	Now, the parameter that governs rigidity is $1-PH$.
-It is a function of priror uncertainty about $y$ and noisiness of the signals.
+It is a function of prior uncertainty about $y$ and noisiness of the signals.
 It is time variant as the variance is updated by the agent each period.
@@
 	As in FIRE and SE, uncertainty itself does not depend upon the realization of the shocks or signals.
-The revision in uncertainy from time $t-1$ to $t$ fixing the terminate of the forecast date is negative  unambigously.
+The revision in uncertainty from time $t-1$ to $t$ fixing the terminate of the forecast date is negative  unambiguously.
 To see this
@@
 $\Delta \Sigma^y_{i,t|t}$.
-It is scalled by the factor $\rho^{2h}$.
+It is scaled by the factor $\rho^{2h}$.
 The second source is present in full information rational expectation model: as time goes from $t-1$ to $t$, there is a reduction of uncertainty about $\omega_t$.
@@
 
-One of the major implications from NI models is that both individual forecast and ucnertainty behaves the same pattern as population forecasts.
-
-In parituclar, the same as indivdiual forecast erro, average forecast errors have serial correlation with the same auto regression parameter $\rho^h(1-PH)$.
-
-As to the uncertainty, as it does not depend on realized signals and the precision is the same aross all agents, average variance $\bar \Sigma_{t+h|t}$ is equal to the variance of each individual.
-
-Also, same as the individual variance, the variance unambiguiously drop in each vintage of revision.
+	One of the major implications from NI models is that both individual forecast and uncertainty behaves the same pattern as population forecasts.
+
+	In particular, the same as individual forecast error, average forecast errors have serial correlation with the same auto regression parameter $\rho^h(1-PH)$.
+
+	As to the uncertainty, as it does not depend on realized signals and the precision is the same across all agents, average variance $\bar \Sigma_{t+h|t}$ is equal to the variance of each individual.
+
+	Also, same as the individual variance, the variance unambiguously drop in each vintage of revision.
 But since the signal is noisy, agents partially react to the news and uncertainty does not drop as efficiently as FIRE.
@@
 This seems counterintuitive.
-But the reason is that here the disagreenments always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.
+But the reason is that here the disagreements always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.
 
@@
 
-$\bullet$  Invididual expectation adjusts in each period, but only partially adjusts to new information. \\
-$\bullet$ Unlike sticky expectation, slugishness in adjustment or serial correlation of adjustment exists in individual level.
+	$\bullet$  Individual expectation adjusts in each period, but only partially adjusts to new information. \\
+	$\bullet$ Unlike sticky expectation, sluggishness in adjustment or serial correlation of adjustment exists in individual level.
 The correlation parameter decreases with forecast horizon, which is not the case in sticky expectation.\\
@@
 	$\bullet$  Population average forecast partially adjusts to news and has serial correlation as the individual level. \\
-$\bullet$  Population disagreements rise in each period as time approaches the period of realization. Disagreetments will never be zero. \\
+	$\bullet$  Population disagreements rise in each period as time approaches the period of realization. Disagreements will never be zero. \\
 	$\bullet$  Average variance declines unambiguously each period.
@@
 
-Figure \ref{ir_pop} plots the impulse responses of population moments of forecasts accroding to different theories.
+	Figure \ref{ir_pop} plots the impulse responses of population moments of forecasts according to different theories.
 As we focus on the dynamics of revision as one approaches the terminate date, i.e.
@@
 
-This is the most intuitively seen in the dynamics of uncertainty. In particular, as one appraoch the realization $t+h$, uncertainty necessarily drop for FIRE and attains zero at the last period.
+	This is the most intuitively seen in the dynamics of uncertainty. In particular, as one approach the realization $t+h$, uncertainty necessarily drop for FIRE and attains zero at the last period.
 
@@
 
-One of the common predictions of SE and NI is there is information rigidity or stickiness of expecatations.
-But both theory have suble difference in implied rigidity.
+	One of the common predictions of SE and NI is there is information rigidity or stickiness of expectations.
+But both theories have subtle difference in implied rigidity.
 I illustrate this in Figure \ref{rigidity}.
-One notable difference is that SE's rigidty is exogeously fixed.
-NI's rigidity is endogeously determined by the noisiness of the signals and it is time varying.
+One notable difference is that SE's rigidity is exogenously fixed.
+NI's rigidity is endogenously determined by the noisiness of the signals and it is time varying.
 
@@
 
-\subsection{Disucussion of other theories}
+	\subsection{Discussion of other theories}
 
@@
 
-\item Epidemiologic view.
-\citet{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.
+		\item Epidemiological view.
+\citet{carroll2003macroeconomic} Regardless of the micro-foundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.
 
@@
 
-The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both currenct year forecast and 1-year-ahead inflation foreacst each quarter.
+	The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both current year forecast and 1-year-ahead inflation forecast each quarter.
 
@@
 
-We follow \citet{engelberg2009comparing} to estiamte the density distribution of each individual surveyee for SPF.
+	We follow \citet{engelberg2009comparing} to estimates the density distribution of each individual surveyee for SPF.
 New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty.
@@
 	For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.
-For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extream values.
-\footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in totla.}
+For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extreme values.
+\footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}
 
@@
 
-Although the sheer magnitudes of the differences between professionals' moments and those of houseolds are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency.
+	Although the sheer magnitudes of the differences between professionals' moments and those of households are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency.
 Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty against realized inflation,  forecast errors and disagreements in the first, second and third rows, respectively.
@@
 In particular, the correlation coefficients are -0.1, -0.05 and -0.24 for SPF's  CPI forecast, SPF's PCE forecast and SCE's CPI expectation.
-This may suggest that during a period of persistently low inflation, the conventiaonl positive redux of inflation and uncertainty is not a good description of the relation of the two.
+This may suggest that during a period of persistently low inflation, the conventional positive redux of inflation and uncertainty is not a good description of the relation of the two.
 
 	The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between forecast error and uncertainty.
-Although according to our benchmark frameowork in \ref{theory}, there is no mathematical correlation between the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
-The correlation coefficent of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, resptively.
+Although according to our benchmark framework in \ref{theory}, there is no mathematical correlation between the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
+The correlation coefficient of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, respectively.
 Compared to professional forecasts, households forecasts exhibit such a positive correlation.
@@
 	The last row in of Figure \ref{UnceratitnyOtherMoments} explores the relationship between disagreements and uncertainty.
-Many empriical literature in macroecoomics use disagreements and uncertainty as if they are similar concepts.
+Many empirical literature in macroeconomics use disagreements and uncertainty as if they are similar concepts.
 Partly this confusion in practice is due to difficulty of finding the appropriate measure of this in the first place.
 But as we have presented in \ref{theory}, the two are distinct concepts.
-The empricial pattern of the two,  as shown in the plots, also confirms that the two are different objects.
+The empirical pattern of the two,  as shown in the plots, also confirms that the two are different objects.
 The correlation coefficients of the two turn out to be negative, -0.29 and -0.46 for SPF forecasts.
@@
 	Overall, professional forecasters' moments exhibit patterns more consistency from a statistical point of view.
-In constrast, the positive correlation across households' ex ante uncertainty, ex post forecat errors, and cross-section disagreements cannot be easily reconciled by the framework we set up in Section \ref{theory}.
+In contrast, the positive correlation across households' ex ante uncertainty, ex post forecast errors, and cross-section disagreements cannot be easily reconciled by the framework we set up in Section \ref{theory}.
 
 	Persistent disagreements in expectations has been used as an important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
-A similar fact checking can be done with respect to individual uncertaintiy.
+A similar fact checking can be done with respect to individual uncertainty.
 FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREInd}.
 In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEInd}).
-NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precesion of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
-Therefore, precense of dispersion of uncertainty across agents can be read against FIRE.
-
-Figure \ref{IQR_Unceratitny} plots the median inflation expectation along its 25/75 percentiles in the left and its counterpart in uncertainty in the righ coumn.
+NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precision of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
+Therefore, presence of dispersion of uncertainty across agents can be read against FIRE.
+
+	Figure \ref{IQR_Unceratitny} plots the median inflation expectation along its 25/75 percentiles in the left and its counterpart in uncertainty in the right column.
 Not only there is long-lasting dispersion in individual forecasts, i.e.
-disagreements, but alslo notable heterogeneity in uncertainty across agents.
+disagreements, but also notable heterogeneity in uncertainty across agents.
 And not surprisingly, the dispersion of both forecasts and uncertainty of households are both of a much greater magnitude than that of the professionals.
 The 25/75 inter-quantile-range of households point forecasts is 4-5 percentage points compared to 1 percentage point of professionals.
-And the IQR of uncertainty of housheolds are around 150-200 times(12-14 times for standard deviation) as that of professional forecasters.
+And the IQR of uncertainty of households are around 150-200 times(12-14 times for standard deviation) as that of professional forecasters.
 
@@
 Households' uncertainty are more skewed toward to the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty.
-This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernal density estimated distribution of uncertainty by year on.
+This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernel density estimated distribution of uncertainty by year on.
 What is common for both types of agents is that the dispersion in uncertainty is persistent over time and do not show much time-variation.
@@
 75 percentile forecast increases from 1\% to 2\%).
-\footnote{This should be interpreted with causion since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UnceratitnyOtherMoments} actually exihibits a gradual decline.
+\footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UnceratitnyOtherMoments} actually exhibits a gradual decline.
 } This is consistent with the observation in top left two figures Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flatten.
 
-FIRE also predicts an unambigous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
-Although quantitatively it is hard to check this, one can look if the distribution of the uncertainy revision concentrate in the negative range.
+	FIRE also predicts an unambiguous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
+Although quantitatively it is hard to check this, one can look if the distribution of the uncertainty revision concentrate in the negative range.
 Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty from 1-year-ahead forecast in year $t-1$ to the current-year nowcast in year $t$.
@@
 This follows from Equation \ref{NoPastInfFE}.
-In addition, I include what is called weak version of the FE-based test which explores the serial correlation of forecast erros in overlapping periods,  i.e.
+In addition, I include what is called weak version of the FE-based test which explores the serial correlation of forecast errors in overlapping periods,  i.e.
 1-year-ahead forecasts within one year.
 The forecast errors are correlated to the extent of the realized shocks in the overlapping periods.
-So the positve serial correlation does not direct violate FIRE.
+So the positive serial correlation does not direct violate FIRE.
 For this reason, looking into the correlation of overlapping forecast errors still contain the useful information about the size of the realized shocks.
 
-FE-based tests results are prensented in Table \ref{NullTestTable}.
+	FE-based tests results are presented in Table \ref{NullTestTable}.
 Individual level data are used thanks to the panel structure of both surveys.
 Since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE.
-Also,the regresions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE.
+Also,the regressions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE.
 Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.
@@
 	First,  all three forecast series easily reject the unbiasedness test in the significance level of $1\%$.
-There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecaters(2.2 versus 0.12) for headline CPI.
-
-Second, the point forecast one year ago predicts the forecat errors for professionals in the significance level of 1\%.
+There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecasters(2.2 versus 0.12) for headline CPI.
+
+	Second, the point forecast one year ago predicts the forecast errors for professionals in the significance level of 1\%.
 For headline CPI inflation, for instance, one percentage point inflation forecast corresponds to 0.3 percentage points of the forecast errors one year later.
@@
 	Third, forecast errors can be predicted by forecast errors one year ago with a significant coefficient of around $0.08$ for headline CPI and $0.05$ for PCE, as seen in test 3 of Table \ref{NullTestTable}.
-Errors of non-overlapping forecastign periods are correlated, against the null of FIRE.
+Errors of non-overlapping forecasting periods are correlated, against the null of FIRE.
 
@@
 For SPF forecasts, the serial correlation does not exist beyond 1 quarter, implying relative efficiency of forecasts.
-For the households, the forecast errors are more persisent over the entire year in that current forecat errors are correlated with all past forecast errors over the past three quarters.
+For the households, the forecast errors are more persistent over the entire year in that current forecast errors are correlated with all past forecast errors over the past three quarters.
 Again, although the persistency of 1-year forecast errors within one year do not directly violate FIRE, the fact that households' forecast errors being more persistent than professionals provide useful clues about the relative rigidity of the two types of agents.
@@
 	\begin{table}[ht]
-	\caption{Tests of Rationality and Efficicency using Forecast Errors}
+		\caption{Tests of Rationality and Efficiency using Forecast Errors}
 		\label{NullTestTable}
@@
 
-The test with uncertainy simply replaces the revision of forecast with revision in uncertainty $\sigma^2_{i,t+1|t+1} - \sigma^2_{i.t+1|t}$, for instance.
-This regresion follows from Equation \ref{VarSERv} for SE and Equation \ref{VarNIRv} for NI.
+	The test with uncertainty simply replaces the revision of forecast with revision in uncertainty $\sigma^2_{i,t+1|t+1} - \sigma^2_{i.t+1|t}$, for instance.
+This regression follows from Equation \ref{VarSERv} for SE and Equation \ref{VarNIRv} for NI.
 Although it  cannot be directly used as a test against FIRE null, the autocorrelation coefficient speaks to the speed of drop in uncertainty.
-Depending on the model, one can interprete it as the particular structural parameter of rigidty, as shown in Figure \ref{rigidity}.
+Depending on the model, one can interpret it as the particular structural parameter of rigidity, as shown in Figure \ref{rigidity}.
 
@@
 	What's surprising is the mean revision in forecast being negative and significant.
-Forecaters on average make downward adjustment of 1.26 percentage points of CPI and  1.1 perentage points of PCE from her previous year forecast of the same-period inflation.
+Forecasts on average make downward adjustment of 1.26 percentage points of CPI and  1.1 percentage points of PCE from her previous year forecast of the same-period inflation.
 
@@
 Also, the median forecasts as the past information always predicts a negative revision with significant coefficients.
-This is evidence against null hypothesis of FIRE and my estiamtes are comparable with those by \citet{fuhrer2018intrinsic}.
+This is evidence against null hypothesis of FIRE and my estimates are comparable with those by \citet{fuhrer2018intrinsic}.
 
@@
 Again, the first column first test the mean revision against the null being zero.
-The mean revisions in uncertainty are both negative(0.5-0.6 percentage poitns equivalence in standard devation of uncertainty) and statistically sigificant, confirming our observation from Figure \ref{RevisionHist} that forecaters are more certain about current inflation compared her previous year forecast.
+The mean revisions in uncertainty are both negative(0.5-0.6 percentage poitns equivalence in standard deviation of uncertainty) and statistically significant, confirming our observation from Figure \ref{RevisionHist} that forecasters are more certain about current inflation compared her previous year forecast.
 
@@
 The auto-correlation of change in mean forecast and uncertainty does embed  tests of null of FIRE (Equation \ref{VarREPop}).
-But if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
+But if the individual forecasts and their uncertainty turn out to be persistent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
 
@@
 		\centering 
-	\caption{Weak Tests of Revision Efficiency using Change in Foreacsts and Uncertainty}
+		\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
 		\label{WeakRevEfficiency}
@@
 
-\section{Shock-based tests of expectation rigity }\label{IRShocks}
+	\section{Shock-based tests of expectation rigidity }\label{IRShocks}
 
 	\citet{coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
-Unlike the time series regressions that test null hypotheses of FIRE in previous section, this approach allows a more straightforward comparison between the emprical evidence from surveys and the theoriecal predictions illustrated in Figure \ref{ir_pop}.
+Unlike the time series regressions that test null hypotheses of FIRE in previous section, this approach allows a more straightforward comparison between the empirical evidence from surveys and the theoretical predictions illustrated in Figure \ref{ir_pop}.
 The difficulty of this approach lies in identifying a shock $\omega_t$ that is a pure innovation to inflation at time $t$.
 
-In this paper I use three types of shocks: technology shock\citet{gali1999technology}, oil price shock\citet{hamilton1996happened} and monetary policy shocks \citet{laseen2011anticipated}.
+	In this paper I use three types of shocks: technology shock from \citet{gali1999technology}, oil price shock from \citet{hamilton1996happened} and monetary policy shocks from  \citet{laseen2011anticipated}.
 The first two are the same in \citet{coibion2012can}.
@@
 	(1) Technology shock is identified from a three variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
-Based on Bayes information criteria, I use the lag of 4 quarters as in \citet{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share appraoch'' developed by \citet{francis2014flexible}.
+Based on Bayes information criterion, I use the lag of 4 quarters as in \citet{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share approach'' developed by \citet{francis2014flexible}.
 It is shown to have better small-sample properties.
-In particular,  the approach defines technology shock as the variation of current period labor productivity (output per hour) that explains the maximum fraction of future labor productivity over an exogenously determiend horizon.
-The resutls using this shock will be included in a later version of the paper.
+In particular,  the approach defines technology shock as the variation of current period labor productivity (output per hour) that explains the maximum fraction of future labor productivity over an exogenously determined horizon.
+The results using this shock will be included in a later version of the paper.
 For the replication purpose now, I stay with \citet{gali1999technology}}.
@@
 
-(3) Monetary policy shocks: target surprise and path surprise in the termiology of \citet{laseen2011anticipated}.
-Target surprise is defined as unexpected change in federal funds rate in a particular date of FOMC meenting.
+	(3) Monetary policy shocks: target surprise and path surprise in the terminology of \citet{laseen2011anticipated}.
+Target surprise is defined as unexpected change in federal funds rate in a particular date of FOMC meetings.
 It is the OLS residual of federal funds rate change in the past expected change in federal funds rate.
@@
 	The underlying regression that produces impulse response estimates is  Equation \ref{IRRegression}, according to which inflation(or moments) in current quarter is a function of 4-period lags of itself  and the realized shocks in current and previous period.
-The estimate of autoregression coefficients $\beta_\tau$ and shock-specific coefficients $\beta_{S,k}$ for diffrent lags can be used to compute impulse responses of the variables of interest.
+The estimate of autoregression coefficients $\beta_\tau$ and shock-specific coefficients $\beta_{S,k}$ for different lags can be used to compute impulse responses of the variables of interest.
 In the impulse response graph, standard errors are computed using the parametric bootstrapping approach as in \citet{coibion2012can}.
@@
 i.e.
-forecasts react only to contemporaneous shocks instataneously.
+forecasts react only to contemporaneous shocks instantaneously.
 Therefore, the average FE should not be dependent upon past shocks and  only experience a one-time rise and return zero immediately.
@@
 PCE inflation responds to both the shocks in a similar manner with slightly different magnitudes.
-The responses coefficients are statistically significant as the $95\%$ confidence intervel stays on one side of zero for both shock for the same period.
+The responses coefficients are statistically significant as the $95\%$ confidence interval stays on one side of zero for both shock for the same period.
 
@@
 This is illustrated using both SPF's FE of CPI in the second graph of  left panel in Figure \ref{ReplicateCoibionBefore2007}.
-As we define the forecast error as point forecast minus realized value, forecast error rises(drops) after a positive(negative) shock and gradully return to zero around 4-5th quarters after the shock.
+As we define the forecast error as point forecast minus realized value, forecast error rises(drops) after a positive(negative) shock and gradually return to zero around 4-5th quarters after the shock.
 
@@
 \footnote{In addition, the degree of long-run disagreements sheds light upon one subtle difference between the SE and NI.
-Disagreements always exist in NI with the presense of private signals , in contrast, disagreement is zero over the long run in SE.
+Disagreements always exist in NI with the presence of private signals , in contrast, disagreement is zero over the long run in SE.
 }
@@
 	The responses to monetary policy shocks turn out to be nosier than for technology and oil price shocks, as presented in the right panel of Figure \ref{ReplicateCoibionBefore2007}.
-On the top, I first plot the impulse response of inflation to path surprises $ED8ut$ and target surprise $MP1ut$, seperately.
+On the top, I first plot the impulse response of inflation to path surprises $ED8ut$ and target surprise $MP1ut$, separately.
 On average, inflation reduces by around 10 percentage points after one unit increase of target surprise and increases by 10 percentage points following one unit of path surprise to federal funds rate.
 Both responses are  statistically significant in $10\%$  level.
-The unexpected future tightening causing a rise in inflation is conistent with the literature of price puzzle.
+The unexpected future tightening causing a rise in inflation is consistent with the literature of price puzzle.
 \footnote{See \cite{nakamura2018high} as an example of inflationary responses to a monetary tightening move of the Fed.}
 
-In the middle figure presents the responses of CPI forecast erros by SPF.
-Although the average response seems to go in the same direction of the respective monetary shocks, consistent with the pattern seen for techonology and oil price shocks, none of the responses are statistically significant and the estimates have big standard errors of 10-20 percentage points.
-
-Similarly, the responses of disagreements to both monetary policy shocks in the bottom panel are not statistically signifcant throughout the 10 quarters.
-
-How do we intereprete the finding of non-response of forecasting errror and disagreements to monetary policy shocks in the conext of rigidity models?
-Non-response of FE suggests that on average professional forecaters have incorporated the monetary policy changes in their forecasts.
+	In the middle figure presents the responses of CPI forecast errors by SPF.
+Although the average response seems to go in the same direction of the respective monetary shocks, consistent with the pattern seen for technology and oil price shocks, none of the responses are statistically significant and the estimates have big standard errors of 10-20 percentage points.
+
+	Similarly, the responses of disagreements to both monetary policy shocks in the bottom panel are not statistically significant throughout the 10 quarters.
+
+	How do we interpret the finding of non-response of forecasting errror and disagreements to monetary policy shocks in the context of rigidity models?
+Non-response of FE suggests that on average professional forecasters have incorporated the monetary policy changes in their forecasts.
 Non-response of disagreements could be due to that forecasters ``agree'' on the realization of monetary policy shocks.
-Althouth the benchmark theory of SE and NI do not differentiate shocks, the evidence here seems to suggest that the degree of rigidity depends on  nature of the shocks.
+Although the benchmark theory of SE and NI do not differentiate shocks, the evidence here seems to suggest that the degree of rigidity depends on  nature of the shocks.
 
 	Or there are other explanations.
-First, overal the monetary policy shocks contribute only a small part of variation in inflation compared to supply shocks.
+First, overall the monetary policy shocks contribute only a small part of variation in inflation compared to supply shocks.
 This was actually used by \cite{coibion2012can} to justify why monetary policy shock was not used in their exercise.
-Second,  I am just running into the same difficulty in identifying real impacts of monetry policy shocks from low frequency data as all other papers addressing this issue.
+Second,  I am just running into the same difficulty in identifying real impacts of monetary policy shocks from low frequency data as all other papers addressing this issue.
 \footnote{Examples of identifying monetary policy shocks.
@@
 In addition, the post crisis period has been characterized by a number of different features in terms of the behavior of macroeconomy(i.e.
-persistently low inflation) and monetary policy implmentation (i.e.
+persistently low inflation) and monetary policy implementation (i.e.
 emphasis on monetary policy communication and zero lower bound), therefore it is worth examining if the patterns documented by \cite{coibion2012can} remain for the entire period.
-Also, since PCE inflation forecast is not avaiable untill 2007, I report results for both CPI and PCE as in previous analysis.
-
-The left panel of  Figure \ref{ReplicateCoibionwholeperiod} presents impulse reponses of average uncertainty of SPF in addition to that inflation, forecast error, disagreements in response to technology and oil price shocks.
+Also, since PCE inflation forecast is not available until 2007, I report results for both CPI and PCE as in previous analysis.
+
+	The left panel of  Figure \ref{ReplicateCoibionwholeperiod} presents impulse responses of average uncertainty of SPF in addition to that inflation, forecast error, disagreements in response to technology and oil price shocks.
 As shown in the top three figures, the results are consistent with that in Figure \ref{ReplicateCoibionBefore2007} for period before 2007.
-Oil shock(technology shock) increases(decreases) inflation in the first quarter by 10 percentage  points, whose imapcts last till 7-8th quarters.
+Oil shock(technology shock) increases(decreases) inflation in the first quarter by 10 percentage  points, whose impacts last till 7-8th quarters.
 Confidence interval of the responses is smaller compared to previous figure probably due to larger sample size.
@@
 
- The response graph seems consistent with this simpel prediction, except for the uncertainty about CPI in responses to oil price shock.
+	The response graph seems consistent with this simple prediction, except for the uncertainty about CPI in responses to oil price shock.
 The responses of average uncertainty is not significantly different from zero throughout 10 quarters.
@@
 future monetary policy stances, again brings about the inflationary effect as before.
-One standard deviation of ture tightenning shock increases headlien CPI inflation by around 15 percentage points in the first period.
+One standard deviation of true tightening shock increases headline CPI inflation by around 15 percentage points in the first period.
 In the same time, unexpected rate change does not affect inflation significantly once we include the post-2007 period.
 One possible explanation for this is the small variation of target surprise after financial crisis, as illustrated in Figure \ref{Inflationshocks}.
-Except for the dramatic monetary loosenning during financial crisis, there was little variation in the unexpected federal fund rate change.
-
-Similar to results for pre-2007 period, the initial response of average forecast error to future tightening shock is statistically signifcant in the first period but insignificant soon after.
-Interestingly, even though the target surprise does not affect inflation iteself, forecast errors do react to it in an inflationary manner.
+Except for the dramatic monetary loosening during financial crisis, there was little variation in the unexpected federal fund rate change.
+
+	Similar to results for pre-2007 period, the initial response of average forecast error to future tightening shock is statistically significant in the first period but insignificant soon after.
+Interestingly, even though the target surprise does not affect inflation itself, forecast errors do react to it in an inflationary manner.
 The magnitude of the response is as large as 25 percentage points in the first quarter.
 Rigidity models predict forecast errors depend on past shocks, while there does not seem to be strong evidence for this when it comes to monetary policy shocks.
-Forecasters reaction to monetary policy shocks apear to more efficient than for supply shocks.
+Forecasters reaction to monetary policy shocks appear to more efficient than for supply shocks.
 
@@
 The estimates of these responses are not  significantly from zero throughout the entire horizon.
-Non-response of disagreements could arise if forecasters have incorparated the monetary policy shocks (thus the shock no longer qualified as a ``shock'') , or all forecasters simultaneously incorporating the realization of the monetary shocks.
+Non-response of disagreements could arise if forecasters have incorporated the monetary policy shocks (thus the shock no longer qualified as a ``shock'') , or all forecasters simultaneously incorporating the realization of the monetary shocks.
 In the context of NI model, the disagreements can only arise with the presence of private signals.
-Therefore, monetary policy being a more public signal can help explain the mutted response of disagreements in comparison of the other shocks.
+Therefore, monetary policy being a more public signal can help explain the muted response of disagreements in comparison of the other shocks.
 \footnote{Another explanation is that monetary policy actually coordinates agents' expectations, thus accordingly reduce disagreements, according to \citet{morris2002social}.
@@
 
-It is widely documented in the literature that behaviors of households expectations more idiosyncratic in comarison with that of professional forecasters.
+	It is widely documented in the literature that behaviors of households expectations more idiosyncratic in comparison with that of professional forecasters.
 \footnote{For this reason, \cite{carroll2003macroeconomic}, for instance, use median professional forecasts as to approximate ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.
@@
 	As technology shock can only be recovered from quarterly time series of output, I only present results using oil price shock and monetary policy shocks in Figure \ref{SCE_IR}.
-The responses to oil price shocks, target surprise and path surprise are plottd in column 1, 2 and 3, respectively.
-
-Oil price shock increases CPI by  7-8 percentage points in the first period and the imapcts last over the entire 10 months. This is not surprising from the previous results on quarterly data.
+The responses to oil price shocks, target surprise and path surprise are plotted in column 1, 2 and 3, respectively.
+
+	Oil price shock increases CPI by  7-8 percentage points in the first period and the impacts last over the entire 10 months. This is not surprising from the previous results on quarterly data.
 
 	Estimated in higher frequency, the response to target surprise is on average 2.5 percentage points and statistically significant in $10\%$ level.
-This confirms the wide practice of the literature that identifies monetary non-netrality using high frequency data.
+This confirms the wide practice of the literature that identifies monetary non-neutrality using high frequency data.
 In contrast, the inflation responses to path surprise is not significant.
@@
 
-It is widely conjectured (in spite of limited evidence) that salient items such as gasline price plays an improprotionate role in affectign household inflation expectation.
+	It is widely conjectured (in spite of limited evidence) that salient items such as gasoline price plays an important role in affecting household inflation expectation.
 The evidence presented here seems to be consistent with such a prediction.
@@
 This is the easiest seen in the non-response or instantaneous response if any of forecast error and disagreements to monetary policy shocks.
-The similar can be said for households, in constrast, for oil price shock instead of monetary policy shocks.
+The similar can be said for households, in contrast, for oil price shock instead of monetary policy shocks.
 
@@
 $\omega_t$ in Equation \ref{AR_process}.
-It is true that the distinction of public and private signals within NI provides one possibility of reconciling difference in resposnes to shocks.
-If we interprete different ``shocks'' considered here as noisy signals instead of shocks to fundamental variable as defiend in \ref{AR_process}, then the difference across ``shocks'' in their degree of publicity may acount for the difference in rigidity.
-But this implicitly implies redefining the  framework presentd in this paper.
+It is true that the distinction of public and private signals within NI provides one possibility of reconciling difference in response to shocks.
+If we interpret different ``shocks'' considered here as noisy signals instead of shocks to fundamental variable as defined in \ref{AR_process}, then the difference across ``shocks'' in their degree of publicity may account for the difference in rigidity.
+But this implicitly implies redefining the  framework presented in this paper.
 
@@
 
-Second, rigidity of expectation from either inattention or underreaction due to noisiness of the signals imply agents do not revise forecasts as efficienctly as they do in FIRE in the face of new information.
-This can be seen from both a sluggish pattern of forecast revision or uncertainty reduction across differen vintages of the forecast.
+	Second, rigidity of expectation from either inattention or under-reaction due to noisiness of the signals imply agents do not revise forecasts as efficiently as they do in FIRE in the face of new information.
+This can be seen from both a sluggish pattern of forecast revision or uncertainty reduction across different vintages of the forecast.
 A weaker test of this spirit uses change of forecasts with fixed horizon.
@@
 In particular, professional forecasters are more responsive to monetary policy shocks and households are more responsive to oil price shocks.
-This motivates next-step anlysis of how much resolution of uncertainty can be attributed to the volatility of various shocks.
+This motivates next-step analysis of how much resolution of uncertainty can be attributed to the volatility of various shocks.
 This shows the use of uncertainty.

### 2019-06-29 paper/Draft.tex
Finished literature. Introduction has only preview of the results left before. Summary of the Theories left.

@@
 	\begin{abstract}
-		Surveys on density forecasts of macroeconomic variable that are not available until recent two decades provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
+		Surveys on density forecasts of macroeconomic variable that are not available until recent provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
 This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households.
 Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE).
-Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.
+Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.
 This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.
@@
 Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions.
+
+	This paper is related to three strands of literature.
+First, recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data.
+For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}.
+More recent examples include \citet{coibion2018firms} on firms' managers.
+In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}, In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demografics and macroeconomic experiences they have had.
+For instance, \citet{malmendier2015learning}.
+However, all of these research simply rely upon point forecsts instead of densitity forecast or surveyed uncertainty.
+This is one theme on which that this paper differs from the existing literature.
+
+	Second, the literature that has been originally developed under the theme of forecast efficiency provides a framework analyzing the dynamics of uncertainty useful for the purpose of this paper.
+The focus of the forecasting efficiency literature is evaluating forecasters' performance and improving forecasting methodology, but it can be adapted into testing the context of understanding expectation formation of different types of agents.
+This is especially relevant to this paper as I focus on the uncertainty.
+
+	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probiblistic questions measuring subjective uncertainty in economic surveys.
+Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{xx}, \citet{xx} have all shown that this is actually less of a concern.
+\citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses.
+Broadly speaking, the advocators have argued that going beyond revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
+This insight holds for not only point forecast, but also and even more importantly, for uncertainty.
+
+	The paper is organized as followed.
+Section \label{theory} first sets up a common framework in which testable various theories can be compared.
+Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments.
+Section \ref{empirical} discusses the survey data used for this paper, and presents both the stylized patterns and time series regressions that test the implications of these theories.
+Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.
+Section \ref{Conclusion} concludes the paper and discusses the plan for the next step.
 

### 2019-06-29 paper/Draft.tex
finalized FIRE and SE section. NI to be finished

@@
 So we can simply denote the variable as $y_{t+h}$.
-To put it another way, all agents are forecasting the same object.
-\footnote{Only in the context of forecasting aggregate variable, it is meaningful to study the average expectations and disagreements across agents.}
+\footnote{Only in the context of aggregate variable, it is justified to study the population moments such as average expectations and disagreements.
+Studying expectations of idiosyncratic variables requires individual panel data, as well as the idiosyncratic realizations of the variable.
+}
 
@@
 
+	Overal the results derived in coming sections are  not sensitive to if the shock is serially correlated.
+Also, it allows for the possibility of time varying volatility, i.e.
+the variance of $\omega$ is thus $\sigma^2_{t,\omega}$ with time subsript.
+
 	\subsection{Benchmark of full-information rational expectation(FIRE)}
@@
 	\begin{eqnarray}\label{NoPastInfFE}
-		\overline{FE}^{*}_{i,t+h|t} = \sum^{h-1}_{s=1} \rho^s \omega_{t+h-s}
+		\overline{FE}^{*}_{i,t+h|t} = \sum^{h}_{k=1} \rho^k \omega_{t+k}
 	\end{eqnarray}
@@
 This provides the a well known null hypothesis of FIRE.
-\citet{xx}
 
 	The second implication from FIRE here is that forecast errors of non-overlapping horizon forecasts are not correlated.
+(Equation \ref{NoSerialCorrFE}).
 For instance, forecast error at time $t$ and that at time $t+h$ or further are not serially correlated.
 This is not the case within $h$ periods as the realized shocks in overlapping periods enter both forecast errors.
+These FE-based restrictions of FIRE provide the foudnations for the tests used in Table \ref{NullTest}.
 
@@
 
-	FIRE also has predictions about  population disagreements.
-\footnote{For instance, \citet{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey.
-} As agents perfect update the same information, there is no disagreements at any point of the time.
-
-	$$\overline{Disg}^{*}_{t+h|t}=0 \quad \forall t$$
-
-	A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empirical tests of this kind include \citet{xx}.\citet{xx} etc. }
-
-	In addition to forecast error and disagreements, according to FIRE all individual shares the same degree of uncertainty.
-The uncertainty simply comes from uncertainty about future unrealized shocks between $t$ and $t+h$.
-To put it another way, according to FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{}'s terminology.}
-
-	$$\bar \sigma^{*2}_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
-
-	The time series behavior of uncertainty according to FIRE is less obvious.
-Weather it is time-variant depends on if the variance of the shocks $\omega_t$ is time varying.
-Although in our baseline case we make such an assumption, in general it may not be true.
+	Concerning uncertainty, the first simple implication by FIRE is that all individual shares the same degree of uncertainty.
+The uncertainty about future $y$ simply comes from uncertainty about unrealized shocks between $t$ and $t+h$.
+With the same model in mind (Equation \ref{AR_process})and same information $y_t$, everyone's uncertainty is equal to the weighted sum of the future volatility before its realization.
+(Equation \ref{VarREIndPop}).
+In FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}
+
+	\begin{eqnarray}\label{VarREIndPop}
+	\bar \sigma^{*2}_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}
+	\end{eqnarray}
+
+	The time series behavior of h-year-ahead uncertainty, i.e.
+$\sigma^2_{t+h|t}$, $\sigma^2_{t+h+1|t+1}$, etc, depends on the true process of $y$.
+Specifically, it depends if $\sigma^2_\omega$ is time varying.
+If time-invariant, h-period-ahead uncertainty is simply as constant.
+In baseline case we make such an assumption, in general it may not be true.
 \footnote{\citet{xx} on time-varying volatility.}
 
-	In the same time, the serial correlation of uncertainty across different horizons of forecasting does follow testable pattern according to FIRE.
-In particular, consistent with our current notation, let us denote the forecast of $y_{t+h}$ over horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$.
+	The testable implication of rationality lies in the revision in uncertainty.
+Hereafter, we refer revision (instead of change) as the difference of moments across vintages of forecast with the fixed terminate date of realization.
+For instance, the difference between the uncertainty about $y_{t+h}$ at time $t$ and the uncertainty about $y_{t+h}$ at time $t-1$.
+
+	More generally,  denote the forecast of $y_{t+h}$ over horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$. Then the uncertainty at different points of the $k$ is the following.
 
@@
 
-	As the forecasting horizon decreases relative to a given future point of time, there is a pure efficiency gain or reduction in uncertainty as more and more shocks have realized.
-So the uncertainty should drop unambiguously.
-
-	An equivalent interpretation to this is through the perspective of revision.
-Defining the forecast revision as the difference of different vintages of forecasts fixing the terminate date, the revision in uncertainty should be always negative and the drop should be exactly equal to discounted variance of the realized shocks.
-\footnote{Compared to other null hypotheses discussed above, this is a weaker test.
-It is true that rational forecasting implies reduction in uncertainty with shorter horizon.
-But there is no direct test if the drop in uncertainty is efficient enough so as to be consistent with FIRE.
-}
-
-	$$\bar \sigma^{*2}_{t+h|t+1} - \bar \sigma^{*2}_{t+h|t} = - \rho^{2h}\sigma^2_\omega$$
+	As the forecaster approaches $t+h$ ($k$ approaches to $h$), there is an unambiguous reduction in uncertainty (or efficiency gain in the forecating literature) as more and more shocks have realized.Equivalently, revision is always negative and should be exactly equal to the variance of the realized shocks according to FIRE.
+
+	Moving from $t$ to $t+1$, for instance, revision in uncertainty can be also expressed as a function of previous revision.
+
+	\begin{eqnarray}\label{VarREPopRv}
+		\begin{aligned}
+	\bar \sigma^{*2}_{t+h|t+1} - \bar \sigma^{*2}_{t+h|t} & = - \rho^{2h}\sigma^2_\omega \\
+	& =  \rho (\bar \sigma^{*2}_{t+h|t} - \bar \sigma^{*2}_{t+h|t-1})
+	\end{aligned}
+	\end{eqnarray}
+
+	Lastly, FIRE has predictions about disagreements. As agents perfect update the same information, there is no disagreements at any point of the time.
+
+	\begin{eqnarray}\label{DisgREPop}
+	\overline{Disg}^{*}_{t+h|t}=0 \quad \forall t
+	\end{eqnarray}
+
+	Another simple prediction is that both disagreements and uncertainty do not respond to realized shocks any any point of the time.
 
@@
 
-	The theory of sticky expectation (\citet{xx}, \citet{xx} ), regardless of its different micro-foundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
-One of the most tractable models assume there is a homogenous Poisson rate $\lambda$ of updating among the population.
+	The theory of sticky expectation (\citet{mankiw2002sticky}, \citet{carroll2003macroeconomic} etc.), regardless of various ways micro-foundations, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
+One tractable assumption is that there is a homogenous Poisson rate $\lambda$ of updating among the population.
 Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.
 
-	\subsubsection{Individual moments}
-
 	Denote the mean forecast of a non-updater since $t-\tau$ as $y_{i,t+h|t-\tau}$ since her forecast conditions upon the information up till $t-\tau$.
 
-	$$y_{i,t+h|t-\tau} = \rho^{h+\tau} y_{t-\tau}$$
+	\begin{eqnarray} 
+	y_{i,t+h|t-\tau} = \rho^{h+\tau} y_{t-\tau}
+    \end{eqnarray}
 
@@
 
-	In FIRE, updating at each period $t$ resolves only the uncertainty about the shocks realizing in $t$.
+	In FIRE, updating at each period $t$ resolves only the uncertainty about the shocks that have just realized in $t$.
 In constrast, in SE each updating resolves the uncertainty about all the realized shocks since last update.
-Fixing the terminate date, i.e.
-forecasting  $y_{t+1}$ at time $t$ relative to forecasting $y_{t+1}$ at $t-\tau$, the revision in uncertainty is
-
-	$$\sigma^2_{i,t+1|t} - \sigma^2_{i,t+1|t-\tau} = \rho^{2} \sigma^2_{\omega} - \sum^{\tau+1}_{s=1}\rho^{2s} \sigma^2_{\omega} = -\sum^{\tau+1}_{s=2} \rho^{2s}\sigma^2_{\omega}$$
-
-	FIRE assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in previous period.
+From $t-\tau$ to $t$, the revision in uncertainty is
+
+	\begin{eqnarray}
+	\sigma^2_{i,t+1|t} - \sigma^2_{i,t+1|t-\tau} = \rho^{2} \sigma^2_{\omega} - \sum^{\tau+1}_{s=1}\rho^{2s} \sigma^2_{\omega} = -\sum^{\tau+1}_{s=2} \rho^{2s}\sigma^2_{\omega}
+	\end{eqnarray}
+
+	FIRE basically assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in previous period.
 So setting $\tau =1$ in above equation gives the reduction in uncertainty in FIRE.
-One can easily see that the reduction in uncertainty is greater in SE for any $\tau>1$ than FIRE.
-
-	In summary, the key difference between FIRE and SE with respect to behavior of uncertainty is that the later does not reduce uncertainty  as efficiently as in the former primarily because of the rigidity incorporating new information.
-One qualitative pattern from this difference is that any evidence of ambiguous pattern  or non-negative revision in uncertainty is inconsistent with FIRE.
-\footnote{Because of this, the difference in average responses in variance to new information may speak to potential heterogeneity in information rigidity.
-According to the theory above, higher information rigidity implies high volatility of variance responses.
-}
-
-	\subsubsection{Population moments}
-
-	It is important to note that the rigidity in updating according to SE cannot be systematically observable in the individual level, both in terms of forecasts errors and uncertainty.
+The reduction in uncertainty is greater in SE for any $\tau>1$ than FIRE.
+
+	In individual level, the key difference between FIRE and SE is that the later does not reduce uncertainty  as efficiently as in the former primarily because of the rigidity incorporating new information.
+In the same time, note that the rigidity in updating according to SE cannot be systematically observable in the individual level, both in terms of forecasts errors and uncertainty.
 This is because the behaviors of each individual forecast specifically depends on if the she updates or not in that period.
 
-	Relying upon the Law of Large Numbers, we can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$.
+	Relying upon the law of large numbers, one can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$.
 \footnote{\citet{carroll2003macroeconomic} is one notable example of this.}
 
-	One well known prediction from SE literature is that the average forecast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
+	One well known prediction from SE is that the average forecast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
 \footnote{See \citet{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$.
@@
 
-	\begin{eqnarray}
+	\begin{eqnarray}\label{MeanSEPop}
 		\begin{aligned}
 			\bar y_{t+h|t} & = \lambda \underbrace{y^*_{t+h|t}}_{\textrm{rational expectation at t}} + (1-\lambda) \underbrace{\bar y_{t+h|t-1}}_{\textrm{average forecast at } t-1} \\
-			& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s y^*_{t+h|t-s} \\
-			& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s \rho^{s+h}y_{t-s}
-		\end{aligned}
-	\end{eqnarray}
-
-	It is also easy to show that the average forecast errors are serially correlated.
-Setting $\lambda=1$, then the SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully respond to newly realized shocks at time $t$.
-\footnote{Need to check if is revision or change from}
-
-	\begin{eqnarray}
-		\begin{aligned}
-			\overline{FE}_{t+h|t}  = (1-\lambda) \overline {FE}_{t+h-1|t-1} + \lambda \rho^h \omega_t 
-		\end{aligned}
-	\end{eqnarray}
-
-	\citet{coibion2012can} also derives predictions about the disagreements in rigidity models.
-Unlike zero disagreements in FIRE, SE is characterized by non-zero dispersion in forecasting because of different lags in updating across populations.
-\footnote{need to check if correct also.
-Need to derive change in disagreements.}
+			& = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^\tau y^*_{t+h|t-\tau} \\
+			& = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^\tau \rho^{h+\tau}y_{t-\tau}
+		\end{aligned}
+	\end{eqnarray}
+
+	It is easy to show that the average forecast errors are serially correlated(Equation \ref{FESEPop}).
+For checking, setting $\lambda=1$, then the SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully respond to newly realized shocks at time $t$.
+
+	\begin{eqnarray}\label{FESEPop}
+		\begin{aligned}
+			\overline{FE}_{t+h|t}  = (1-\lambda) \overline {FE}_{t+h|t-1} + \lambda \rho^h \omega_t 
+		\end{aligned}
+	\end{eqnarray}
+
+	 Similarly, the inefficiency of reducing uncertainty in SE take the following form in aggregate level.
+Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.
+
+	 \begin{eqnarray}\label{VarSEPop}
+	 \begin{aligned}
+	 \bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
+	 & = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
+	 \end{aligned}
+	 \end{eqnarray}
+
+	 Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibits serial correlation described in Equation \ref{VarSERv}.
+It is a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart.
+
+	 \begin{eqnarray}\label{VarSERv}
+	 \begin{aligned}
+	 \bar \sigma^2_{t+h|t+1} - \bar \sigma^2_{t+h|t} = (1-\lambda)(
+	 \bar \sigma^2_{t+h|t} - \bar \sigma^2_{t+h|t-1}) -\lambda \rho^{2h} \sigma^2 
+	 \end{aligned}
+	 \end{eqnarray}
+
+	 In particular, the second component is the information gain from most recent realization of the shock underweighted by $\lambda<1$.
+The first component is the inefficiency sourced from stickiness of updating.
+The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.
+
+	 Lastly, SE also predicts non-zero disagreements and sluggish adjustment compared to FIRE. This is because of different lags in updating across populations.
 
@@
 
-	In SE, disagreements rise after realization of the shock and gradually returns to its steady state level.
-In the same time, it does not depend upon the particular realization of the shock.
-\citet{coibion2012can} derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.
-
-	\begin{eqnarray}
-		\rho^{2(h+j)} (1-\lambda^{j+1})\lambda^{j+1} \omega^2_t
-	\end{eqnarray}
-
-	Finally, SE predicts an sluggish inefficiency in revision in uncertainty.
-Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.
-
-	\begin{eqnarray}\label{VarSEPop}
-		\begin{aligned}
-			\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
-			& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
-		\end{aligned}
-	\end{eqnarray}
-
-	Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibits serial correlation described as below in a similar spirt of forecast errors.
-It is equal to a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart.
-\footnote{Make sure you have clarify the difference between revision and change.}
-
-	\begin{eqnarray}\label{VarSERv}
-		\begin{aligned}
-			\bar \sigma^2_{t+h|t+1} - \bar \sigma^2_{t+h|t} = (1-\lambda)(
-			\bar \sigma^2_{t+h|t} - \bar \sigma^2_{t+h|t-1}) -\lambda \rho^{2h} \sigma^2 
-		\end{aligned}
-	\end{eqnarray}
-
-	In particular, the second component is the information gain from most recent realization of the shock underweighted by $\lambda<1$.
-The first component is the inefficiency sourced from stickiness of updating.
-The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.
+	 \citet{coibion2012can} derive the impulse response of dispersion at time $t+k$ to a shock that realized at $t$.
+Disagreements rise after realization of the shock and gradually returns to its steady state level.
+
+	 \begin{eqnarray}
+	 \rho^{2(h+k)} (1-\lambda^{k+1})\lambda^{k+1} \omega^2_t
+	 \end{eqnarray}
 
@@
 	\begin{itemize}
-		\item Individual uncertainty need not unambiguously drop with shorter horizon. 
 		\item Population mean forecast partially responds to shocks and with lags. 
@@
 		\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
-		\item Population average uncertainty revision is serially correlated and underreacts to volatility of the shocks.
-
+		\item Population average uncertainty revision underreacts to volatility of the shocks.
 	\end{itemize}
@@
 
-	A class of noisy information models (\citet{},\citet{}) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
+	A class of models nosity information(NI here after) (\citet{lucas1972expectations}, \citet{sims2003implications}, \cite{woodford2001imperfect} etc.) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
 The starting assumption is that agent cannot observe the true variable perfectly.
@@
 
-	Figure \ref{ir_pop} plots the impulse responses of population moments of forecasts according to different theories.
-As we focus on the dynamics of revision as one approaches the terminate date, i.e.
-forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e.
-$y_{t+h}$,$y_{t+h+1}$.
+	Taking stock, both SE and NI predict rigidity in expectation incorporating arrival of new information.
+In the former context, the rigidity comes from the simple non-updating of the most realization of the variable.
+In the later case, the rigidity comes from a partial reaction to new information due to its nosiness.
+In addition to forecast and disagreements, the rigidity is also reflected in the dynamics of uncertainty.
+
+	According to FIRE, the revision in uncertainty from $t-1$ to $t$ is eactly equal to  the variance of the shock that is realized at time $t$.
+Taking $h=1$ as a simple and plug it in Equation \ref{VarREPop}, we have
+
+	\begin{eqnarray}\label{VarREPopRv1}
+	\bar \sigma^{*2}(y_{t+1}|t) - \bar \sigma^{*2}(y_{t+1}|t-1) = - \rho^2\sigma^2_\omega
+	\end{eqnarray}
+
+	In SE, the one-period revision in uncertainty is less due the non-npdate of population.
+
+	\begin{eqnarray}\label{VarSEPopRv1}
+     \bar \sigma^{2}(y_{t+1}|t) - \bar \sigma^{2}(y_{t+1}|t-1) = (1-\lambda) - \rho^2\sigma^2_\omega
+    \end{eqnarray}
+
+	Figure \ref{ir_pop} illustrats the impulse response of population moments to a hypothetical one-time shock at time $t$ according to different theories.
+
+	on the dynamics of revision as one approaches the terminate date, i.e. forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e. $y_{t+h}$,$y_{t+h+1}$.
 

### 2019-06-29 paper/Draft.tex
Finalized NI.Summary left.

@@
 
-	\begin{table}[]
+	\begin{table}[ht]
 		\centering
@@
 
-	The second implication from FIRE here is that forecast errors of non-overlapping horizon forecasts are not correlated.
+	The second implication from FIRE here is that forecast errors of non-overlapping horizon are not correlated.
 (Equation \ref{NoSerialCorrFE}).
@@
 The first component is the inefficiency sourced from stickiness of updating.
-The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.
+The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction compared to in FIRE.
 
@@
 
-	 \begin{eqnarray}
+	 \begin{eqnarray}\label{DisgSEPop}
 	 \begin{aligned}
@@
 
-	A class of models nosity information(NI here after) (\citet{lucas1972expectations}, \citet{sims2003implications}, \cite{woodford2001imperfect} etc.) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
+	A class of models (\citet{lucas1972expectations}, \citet{sims2003implications}, \cite{woodford2001imperfect} etc.), noisy information(NI) hereafter, describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
 The starting assumption is that agent cannot observe the true variable perfectly.
-Unlike information rigidity model, it is assumed that agents keep track of the realizations of the signals instantaneously all the time.
+Unlike SE, it is assumed that agents keep track of the realizations of signals instantaneously all the time.
 
@@
 
-	\begin{eqnarray}
+	\begin{eqnarray}\label{NISigDef}
 		\begin{aligned}
@@
 	\end{eqnarray}
-
-	\subsubsection{Individual moments }
 
@@
 	What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$.
-Specifically, mean forecast of individual $i$ is the posterior mean of based on her prior and realized signals $s_i$.
+Specifically, mean forecast of individual $i$ is the posterior mean based on her prior and realized signals $s_{i,t}$.
 
@@
 			& = (1-PH) y_{t|t-1} + Ps_{i,t} \\
-			& = (1-PH) y_{t|t-1} + PH y_{i,t} + P v_{i,t} 
-		\end{aligned}
-	\end{eqnarray}
-
-	where the Kalman gain
+			& = (1-PH) y_{t|t-1} + PH y_{t} + P v_{i,t} 
+		\end{aligned}
+	\end{eqnarray}
+
+	where the Kalman gain is a $P$ of size of two that determines the degrees of reaction to signals.
 
@@
 
-	and $\Sigma^y_{i,t|t-1}$  is the variance of  $y_t$ based on prior belief.
+     $\Sigma^y_{i,t|t-1}$  is the variance of  $y_t$ based on prior belief. Here the capital case of $\sigma$ is used to be consistent with vector operations.
 
@@
 
-	Individual forecast partially responds to new signals, i.e. $P<1$. $P=1$ is a special case when both signals are perfect thus $\Sigma^v = 0$, then the formula collapses to FIRE.
-
-	Now, the parameter that governs rigidity is $1-PH$.
-It is a function of prior uncertainty about $y$ and noisiness of the signals.
-It is time variant as the variance is updated by the agent each period.
-
-	There are a few important distinctions between NI and SE.
-
-	First, the serial correlation of forecast error exists at both individual and population level, while it is only observable in population moments according to SE.
-
-	To see this, the change in individual forecast from $t-1$ to $t$ is \footnote{need to check.}
-
-	\begin{eqnarray}
-		\begin{aligned}
-			\Delta y_{i,t+h|t} & = \underbrace{\rho^h (1-PH)\Delta y_{i,t+h|t-1}}_{\text{Lagged response}} + \underbrace{\rho^hPH \Delta y_{i,t|t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
-		\end{aligned}
-	\end{eqnarray}
-
-	The serial correlation is $\rho^h(1-PH)$, it does not only depend on $PH$, but also the forecast horizon $h$.
+	Individual forecast partially responds to new signals as  $PH<1$. $PH=1$ is a special case when both signals are perfect thus $\Sigma^v = 0$, then the formula collapses to FIRE.
+
+	A comparable parameter with $1-\lambda$ in SE that governs rigidity in NI is $1-PH$.
+It is a function of previous period uncertainty about $y_t$ and noisiness of the signals determined by $\Sigma^v$.
+Note $P$ is time variant as the variance is updated by the agent each period.
+The time varying nature of rigidty will be dicussed later.
+For now, I drop time $t$ from $P$ to avoid clusterring.
+
+	The underreaction to news generate serial correlation of forecast errors with the coefficient being $\rho^2(1-PH)$.
+it does not only depend on $PH$, but also the forecast horizon $h$.
 As $\rho<1$, the rigidity declines with longer horizon.
@@
 
-	Second, the expectation adjusts in each period as long as there is new information. In sticky expectation, however, the expectation adjusts only when the agent updates.
-
-	The posterior variance at time $t$ is a linear function of prior variance and variance of signals.
+	What differentiates average forecast from individual's is the role played by private signals.
+On average, private signals cancel out across agents, therefore, only public signals enter in average forecast, thus, average forecast errors (Equation \ref{FENIPop}).
+
+	\begin{eqnarray}\label{FENIPop}
+	\begin{aligned}
+	\bar y_{t+h|t} & = \rho^h [(1-PH) \underbrace{\bar  y_{t+h|t-1}}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
+	& = (1-PH) \bar y_{t+h|t-1}+ P [\epsilon_t, 0]' \\
+	& = (1-PH) \bar y_{t+h|t-1} + P \epsilon_t
+	\end{aligned}
+	\end{eqnarray}
+
+	Kalman filtering updates the variance according to normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in previous period and variance of signals.
+
+	\begin{eqnarray}
+		\begin{aligned}
+			\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} 
+		\end{aligned}
+	\end{eqnarray}
+
+    This directly gives the revision in uncertainty from time $t-1$ to $t$.
+The newly arrived information, although noisy, still brings aobut information gains, thus leading to an unambiguously drop on uncertainty.
+But due to the signal is not perfect, i.e.
+$\Sigma^v \neq 0$, there is inefficiency in reducing uncertainty compared to FIRE.
 
 	\begin{eqnarray}\label{VarNIRv}
-		\begin{aligned}
-			\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} 
-		\end{aligned}
-	\end{eqnarray}
-
-	As in FIRE and SE, uncertainty itself does not depend upon the realization of the shocks or signals.
-The revision in uncertainty from time $t-1$ to $t$ fixing the terminate of the forecast date is negative  unambiguously.
-To see this
-
-	\begin{eqnarray}
 		\Sigma^y_{i,t|t} - \Sigma^y_{i,t|t-1} = - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} <0
@@
 
-	But the efficiency gain in reduction of uncertainty depends upon the noisiness of the signals. As long as the signal is not perfect, forecast in NI is neither as efficient as FIRE.
-
-	These two properties carry through to the h-period ahead forecast as well. As the forecast variance is the following
+	In order to be directly comparable with the revision in uncertainty in FIRE (Equation \ref{VarREPopRv}) and SE (Equation \ref{VarSERv}), the nowcasting uncertainty about $y_t$ needs to be converted to $h$-period-ahead forecating uncertainty.
+This is simply to add the discounted nowcasting uncertainty by $\rho^{2h}$ to the uncertainty about future unrealized shocks.
 
 	\begin{eqnarray}\label{VarNIEq}
-		\Sigma_{i,t+h|t} = \rho^{2h} \underbrace{\Sigma_{i,t}}_{\Sigma_{i,t|t}} + \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega}
-	\end{eqnarray}
-
-	\begin{eqnarray}\label{VarNIIndPop}
-		\Delta \Sigma_{i,t+h|t} = \rho^{2h}\Delta  \Sigma_{i,t|t}  - \rho^{2h} \sigma^2_{\omega}
-	\end{eqnarray}
-
-	From $t$ to $t+1$, when $h\geq 1$, the decline in variance come from two sources.
-The first source is the pure gain from the new signals, i.e.
-$\Delta \Sigma^y_{i,t|t}$.
-It is scaled by the factor $\rho^{2h}$.
-The second source is present in full information rational expectation model: as time goes from $t-1$ to $t$, there is a reduction of uncertainty about $\omega_t$.
-
-	Figure \ref{IllustrateNI} illustrates both the signal extraction problem at each period of $t+k$ and how it is used to predict the prediction of $y_{t+h}$.
+		\Sigma_{i,t+h|t} = \rho^{2h} \Sigma_{i,t|t} + \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}
+	\end{eqnarray}
+
+	As a result, the revision in h-period-ahead uncertainty from $t-1$ to $t$ only partially reacts to the resolution of  uncertainty from newly realized shock $\omega_t$ in the passed period.
+
+	Assuming the nosiness of the private signal is equal across agents, then the dynamic of population uncertainty is the same to individual counterpart $\bar \Sigma_{t+h|t}$, since in NI, every agent is faced with the same filtering problem.
+
+	Figure \ref{IllustrateNI} illustrates the Kalman filtering problem over the $10$ period horizon from to $t$ to $t+10$  following one-time shock of one standard deviation $\omega_t$.
+For illustration purpose, I assume that both private and public signals have the equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e.
+$\frac{\sigma^2_\omega}{1-\rho}$.
+A particular draw of public and private signals their respetive conditional distributions of given $y_t$ are plotted.
+
+	From the top left figure, the agent's nowcasting $y_{t+k|t+k}$, namely her best real-time guess based on prior and the realized signal at each period ranghly tracks the $y_{t+k}$ and responds partially to signals in each period.
+Correspondingly, her forecating of $y$ at $t+10$ also centers around the true value.
+
+	FIRE implies agent learns realized $y$ in each period perfectly.
+Thus the nowcasting remains zero thoughout the whole horizon.
+Nowcasting uncertainty picks up in the realization of shock and gradully declines as more and more informaiton signals are realized.
+This comes from the information gains from Kalman filtering.
+
+    The sharp rise in nowcasting uncertainty in the begining of the period is only humbly reflected in the forecasting uncertainty seems counter intuitive in the first sight.
+Actually this is due to nowcasing uncertainty is discounted by the factor of $\rho^2(h-k)$.
+(Equation \ref{VarNIEq}).
+It is also interesing that for the particular configurations of noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may expected compared to FIRE.
+This has important quantitative implications for NI models.
+In particular, the nosiness of the signals need to be consistent with the degree of rigidity.
+I will return this point in the next section.
 
@@
 
-	\subsubsection{Population moments}
-
-	\begin{eqnarray}
-		\begin{aligned}
-			\bar y_{t+h|t} & = \rho^h [(1-PH) \underbrace{\bar  y_{t+h|t-1}}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
-			& = (1-PH) \bar y_{t+h|t-1}+ P [\epsilon_t, 0]' \\
-			& = (1-PH) \bar y_{t+h|t-1} + P \epsilon_t
-		\end{aligned}
-	\end{eqnarray}
-
-	One of the major implications from NI models is that both individual forecast and uncertainty behaves the same pattern as population forecasts.
-
-	In particular, the same as individual forecast error, average forecast errors have serial correlation with the same auto regression parameter $\rho^h(1-PH)$.
-
-	As to the uncertainty, as it does not depend on realized signals and the precision is the same across all agents, average variance $\bar \Sigma_{t+h|t}$ is equal to the variance of each individual.
-
-	Also, same as the individual variance, the variance unambiguously drop in each vintage of revision.
-But since the signal is noisy, agents partially react to the news and uncertainty does not drop as efficiently as FIRE.
-
-	\begin{eqnarray}
-		\bar \Sigma^2_{t+h|t} -  \bar \Sigma^2_{t+h|t-1}< 0 
-	\end{eqnarray}
-
 	NI also predicts non-zero disagreements in the presence of private signals.
@@
 
-	First, the disagreements increase with the forecast horizon.
+	The implications for disagreements are straightfoward.
+First, the disagreements decreases with the forecast horizon for the reason of discounting.
 Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
@@
 
-	The disagreements increase as time goes from $t-1$ to $t$.
-Also, as the time approaches $t+h$, the disagreements increase.
-This seems counterintuitive.
-But the reason is that here the disagreements always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.
-
 	\subsubsection{Summary of predictions from noisy information}
 
-	$\bullet$  Individual expectation adjusts in each period, but only partially adjusts to new information. \\
-	$\bullet$ Unlike sticky expectation, sluggishness in adjustment or serial correlation of adjustment exists in individual level.
-The correlation parameter decreases with forecast horizon, which is not the case in sticky expectation.\\
-	$\bullet$  Individual variance unambiguously drops each period as one approaches the period of realization. In sticky expectation, it increases regardless of updating or not. \\ 
-	$\bullet$  Population average forecast partially adjusts to news and has serial correlation as the individual level. \\
-	$\bullet$  Population disagreements rise in each period as time approaches the period of realization. Disagreements will never be zero. \\
-	$\bullet$  Average variance declines unambiguously each period.
+	\begin{itemize}
+	\item Individual and population expectation adjusts in each period, but only partially adjusts to new information. 
+	\item  Individual and population uncertainty unambiguously drop each period as one approaches the period of realization.  
+	\item  Population disagreements rise in each period as time approaches the period of realization. Disagreements will never be zero. 
+\end{itemize}
 

### 2019-06-30 paper/Draft.tex
Finalized first drafting. Figure table notes. Forecsting efficiency literature needs to be added.landscape tables. Titles of figures.

@@
 	\begin{abstract}
-		Surveys on density forecasts of macroeconomic variable that are not available until recent provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
+		Surveys on density forecasts of macroeconomic variable that are not available until recent provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
 This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households.
@@
 	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade.
-This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing theories empirically.
-On one hand, various theories built upon different micro foundations produce some similar macro patterns.
-For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.
+This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.
+On one hand, various theories built upon different micro foundations produce somewhat similar macro patterns.
+For instance, the notion of expectation rigidity micro-founded by different theories mostly generate sluggish response to new information.
 On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.
 
-	This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probabilistic forecast from both professional forecasters survey and household survey.
+	This paper extends this research effort by bringing an additional moment of forecasts into perspective, i.e.
+uncertainty.
+Specifically, in this paper I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty.
+Second empirically I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey.
 Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models.
-But in the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.
-
-	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of variables of the forecast.
-.\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.} With density forecasts.
-the variance of individual forecast can be estimated as an indicator of the uncertainty.
+In the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.
+
+	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of values of the variable of forecast\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.}.
+With density forecasts,  variance of individual forecast can be estimated as an indicator of the uncertainty.
 Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency.
-Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions.
+Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely looked by the literature, such as forecast errors and disagreements provide many insights as to how the agents expectation actually work.
 
@@
 More recent examples include \citet{coibion2018firms} on firms' managers.
-In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}, In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demografics and macroeconomic experiences they have had.
-For instance, \citet{malmendier2015learning}.
-However, all of these research simply rely upon point forecsts instead of densitity forecast or surveyed uncertainty.
-This is one theme on which that this paper differs from the existing literature.
+In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics and macroeconomic history experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic},etc.).
+In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.
+However, all of these research simply rely upon point forecasts instead of density forecast or surveyed uncertainty.
+This is one theme on which this paper differs from the existing literature.
 
@@
 	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probiblistic questions measuring subjective uncertainty in economic surveys.
-Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{xx}, \citet{xx} have all shown that this is actually less of a concern.
+Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people}and other work have all shown that this is actually less of a concern.
 \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses.
@@
 Examples of such include multi-prior or model uncertainty.
-\citet{xx}.
-}
+\citet{hansen2001robust}, \citet{hansen2008robustness}, etc.}
 
@@
 To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.
-\footnote{This is the same terminology used by \citet{xx}.}
 
@@
 
-	Overal the results derived in coming sections are  not sensitive to if the shock is serially correlated.
-Also, it allows for the possibility of time varying volatility, i.e.
-the variance of $\omega$ is thus $\sigma^2_{t,\omega}$ with time subsript.
+	Although we make the assumption of i.i.d.
+shock here.
+The framework allows for the possibility of time-varying volatility, i.e.
+the variance of $\omega_t$ is thus $\sigma^2_{t,\omega}$ with time subsript.
 
@@
 
-	As the forecaster approaches $t+h$ ($k$ approaches to $h$), there is an unambiguous reduction in uncertainty (or efficiency gain in the forecating literature) as more and more shocks have realized.Equivalently, revision is always negative and should be exactly equal to the variance of the realized shocks according to FIRE.
+	As the forecaster approaches $t+h$ ($k$ approaches to $h$), there is an unambiguous reduction in uncertainty (or efficiency gain in the forecasting literature) as more and more shocks have realized.
+Equivalently, revision is always negative and should be exactly equal to the variance of the realized shocks according to FIRE.
 
@@
 
-	Another simple prediction is that both disagreements and uncertainty do not respond to realized shocks any any point of the time.
+	Another simple result is that both disagreements and uncertainty do not respond to realized shocks any any point of the time. But this does not differentiate FIRE from other models.
 
@@
 
-	The theory of sticky expectation (\citet{mankiw2002sticky}, \citet{carroll2003macroeconomic} etc.), regardless of various ways micro-foundations, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
+	The theory of sticky expectation (\citet{mankiw2002sticky}, \citet{carroll2003macroeconomic} etc.), regardless of various micro-foundations, builds upon the assumption that agents do not update information instantaneously as they do in FIRE.
 One tractable assumption is that there is a homogenous Poisson rate $\lambda$ of updating among the population.
@@
 	It is easy to show that the average forecast errors are serially correlated(Equation \ref{FESEPop}).
-For checking, setting $\lambda=1$, then the SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully respond to newly realized shocks at time $t$.
+For double checking, setting $\lambda=1$, SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.
 
@@
 
-	 Similarly, the inefficiency of reducing uncertainty in SE take the following form in aggregate level.
+	Similarly, the inefficiency of reducing uncertainty in SE takes the following form in aggregate level.
 Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.
@@
 		\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
-		\item Population average uncertainty revision underreacts to volatility of the shocks.
+		\item Population average uncertainty revision under-reacts volatility of the shocks.
 	\end{itemize}
@@
 
-	where the Kalman gain is a $P$ of size of two that determines the degrees of reaction to signals.
+	where the Kalman gain $P$ is a vector of size of two that determines the degrees of reaction to signals.
 
@@
 Note $P$ is time variant as the variance is updated by the agent each period.
-The time varying nature of rigidty will be dicussed later.
-For now, I drop time $t$ from $P$ to avoid clusterring.
-
-	The underreaction to news generate serial correlation of forecast errors with the coefficient being $\rho^2(1-PH)$.
+The time varying nature of rigidity will be discussed later.
+For now, I drop time $t$ from $P$ to avoid clustering.
+
+	The under-reaction to news generate serial correlation of forecast errors with the coefficient being $\rho^2(1-PH)$.
 it does not only depend on $PH$, but also the forecast horizon $h$.
@@
 
-	Kalman filtering updates the variance according to normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in previous period and variance of signals.
+	Kalman filtering also updates the variance according to rule normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in previous period and variance of signals.
 
@@
 	This directly gives the revision in uncertainty from time $t-1$ to $t$.
-The newly arrived information, although noisy, still brings aobut information gains, thus leading to an unambiguously drop on uncertainty.
+The newly arrived information, although noisy, still brings about information gains, thus leading to an unambiguously drop on uncertainty.
 But due to the signal is not perfect, i.e.
 $\Sigma^v \neq 0$, there is inefficiency in reducing uncertainty compared to FIRE.
+This mea
 
@@
 
-	In order to be directly comparable with the revision in uncertainty in FIRE (Equation \ref{VarREPopRv}) and SE (Equation \ref{VarSERv}), the nowcasting uncertainty about $y_t$ needs to be converted to $h$-period-ahead forecating uncertainty.
-This is simply to add the discounted nowcasting uncertainty by $\rho^{2h}$ to the uncertainty about future unrealized shocks.
+	In order to be directly comparable with the revision in uncertainty in FIRE (Equation \ref{VarREPopRv}) and SE (Equation \ref{VarSERv}), the nowcasting uncertainty about $y_t$ needs to be converted to $h$-period-ahead forecasting uncertainty.
+This is simply to add the nowcasting uncertainty discounted by $\rho^{2h}$ to the uncertainty about future unrealized shocks.
 
@@
 For illustration purpose, I assume that both private and public signals have the equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e.
-$\frac{\sigma^2_\omega}{1-\rho}$.
-A particular draw of public and private signals their respetive conditional distributions of given $y_t$ are plotted.
-
-	From the top left figure, the agent's nowcasting $y_{t+k|t+k}$, namely her best real-time guess based on prior and the realized signal at each period ranghly tracks the $y_{t+k}$ and responds partially to signals in each period.
-Correspondingly, her forecating of $y$ at $t+10$ also centers around the true value.
+$\sqrt{\frac{\sigma^2_\omega}{1-\rho^2}}$.
+A particular draw of public and private signals from their respective conditional distributions given $y_t$ are plotted.
+
+	From the top left figure, the agent's nowcasting $y_{t+k|t+k}$, namely her best real-time guess based on prior and the realized signal at each period roughly tracks the $y_{t+k}$ and responds partially to signals in each period.
+Correspondingly, her forecasting of $y$ at $t+10$ also centers around the true value.
 
 	FIRE implies agent learns realized $y$ in each period perfectly.
-Thus the nowcasting remains zero thoughout the whole horizon.
-Nowcasting uncertainty picks up in the realization of shock and gradully declines as more and more informaiton signals are realized.
+Thus the nowcasting remains zero throughout the whole horizon.
+Nowcasting uncertainty picks up in the realization of shock and gradually declines as more and more information signals are realized.
 This comes from the information gains from Kalman filtering.
 
-    The sharp rise in nowcasting uncertainty in the begining of the period is only humbly reflected in the forecasting uncertainty seems counter intuitive in the first sight.
-Actually this is due to nowcasing uncertainty is discounted by the factor of $\rho^2(h-k)$.
+	The sharp rise in nowcasting uncertainty in the beginning of the period is only humbly reflected in the forecasting uncertainty seems counterintuitive in the first sight.
+Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^2(h-k)$.
 (Equation \ref{VarNIEq}).
-It is also interesing that for the particular configurations of noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may expected compared to FIRE.
+It is also interesting that for the particular configurations of noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may have expected compared to FIRE.
 This has important quantitative implications for NI models.
@@
 
-	The implications for disagreements are straightfoward.
+	The implications for disagreements are straightforward.
 First, the disagreements decreases with the forecast horizon for the reason of discounting.
@@
 In addition to forecast and disagreements, the rigidity is also reflected in the dynamics of uncertainty.
-
-	According to FIRE, the revision in uncertainty from $t-1$ to $t$ is eactly equal to  the variance of the shock that is realized at time $t$.
-Taking $h=1$ as a simple and plug it in Equation \ref{VarREPop}, we have
-
-	\begin{eqnarray}\label{VarREPopRv1}
-	\bar \sigma^{*2}(y_{t+1}|t) - \bar \sigma^{*2}(y_{t+1}|t-1) = - \rho^2\sigma^2_\omega
-	\end{eqnarray}
-
-	In SE, the one-period revision in uncertainty is less due the non-npdate of population.
-
-	\begin{eqnarray}\label{VarSEPopRv1}
-     \bar \sigma^{2}(y_{t+1}|t) - \bar \sigma^{2}(y_{t+1}|t-1) = (1-\lambda) - \rho^2\sigma^2_\omega
-    \end{eqnarray}
-
-	Figure \ref{ir_pop} illustrats the impulse response of population moments to a hypothetical one-time shock at time $t$ according to different theories.
-
-	on the dynamics of revision as one approaches the terminate date, i.e. forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e. $y_{t+h}$,$y_{t+h+1}$.
-
-	This is the most intuitively seen in the dynamics of uncertainty. In particular, as one approach the realization $t+h$, uncertainty necessarily drop for FIRE and attains zero at the last period.
+Uncertainty in SE does not resolve as rapid as in FIRE because the newly realized shocks do not get updated by some of the agents.
+While in NI, the drop in uncertainty is dampened because the there is positive uncertainty associated with the real-time realization of the variable.
+
+	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories.
+Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to the one unconditional standard deviation of $y$.
+And the $\lambda$ is set to be $0.25$, implying on average an update interval of four quarters.
+
+	Both FE and disagreements from SE and NI exhibit sluggish adjustment following the shock as we have anticipated.
+Both pick up in the time of the shock and gradually declines over the horizon as the forecaster approaches terminate date $t+10$.
+The difference is that in NI, both the forecast and forecast errors move up and downs around the the smooth version of the SE since noise is not perfect.
+
+	The dynamic of disagreements and uncertainty, however,  illustrate one parametric differences between SE and NI.
+In particular,  the initial pick in disagreements is higher for NI compared to SE for the particular parameter values.
+This implies that the noise of the private signal that drives the disagreements in NI exceeds that the extent to which the agents do not simultaneously update in SE.
+\footnote{Another subtle point is that if the disagreements jump the highest in the time of the shock turns out depend on value of $\lambda$.
+In the fixed horizon forecasting, $\lambda=0.5$ is the maximizer of disagreements.}
+
+	For the same parameters, however, the inefficiency seen in dynamics of uncertainty seem to be way more substantial for SE than in NI.
+Overall, the uncertainty drops almost as efficiently as in FIRE.
+The difference of SE and the FIRE benchmark is more notable.
+This is the graphical illustration of Equation \ref{VarSERv}.
 
@@
 
-	One of the common predictions of SE and NI is there is information rigidity or stickiness of expectations.
-But both theories have subtle difference in implied rigidity.
-I illustrate this in Figure \ref{rigidity}.
-One notable difference is that SE's rigidity is exogenously fixed.
-NI's rigidity is endogenously determined by the noisiness of the signals and it is time varying.
+	In order to understand why the rigidity seen from uncertainty is de facto much lower in NI that in SE for a sensible values of the noisiness of signals , I plot the implied rigidity from two models in Figure \ref{rigidity} for three different values of nosiness of signals in NI while fixing rigidity in SE to be $1-\lambda =0.75$.
+In particular, the noisiness range from $0.1$, $1$ and $10$ times of the long-run variance of $y$.
+
+	As it is made clear by the Figure, one notable difference of the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time varying.
+In particular, the implied rigidity from NI in the time of the shock, given there is substantial information gain from Kalman filtering in the same period, is quite low.
+For a noisiness of both signals as 10 times as high of the unconditional standard deviation of $y$, the rigidity only reaches the fixed rigidity in SE till the 8-th period.
+But since by that time, the initial information provided by the shock at time $t$ has been mostly absorbed by NI agent, so in fact the uncertainty revision in NI is quite efficient compared to SE models.
+This echoes our earlier observation in Figure \ref{IllustrateNI}.
 
@@
 
-	\subsection{Discussion of other theories}
-
-	\begin{enumerate}
-		\item Rational inattention. 
-		\begin{itemize}
-			\item Chris Sim's model.\citet{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy.
-Agents optimally trade off the fixed cost of being attentative versus the gain from uncertainty gain.
-			\item Ricardo Reis's model. \citet{reis2006inattentive}
-			\item Xavier Gabaix's sparse matrix model. \citet{gabaix2014sparsity}
-		\end{itemize}
-
-		\item Epidemiological view.
-\citet{carroll2003macroeconomic} Regardless of the micro-foundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.
-
-		\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \citet{angeletos2009incomplete}
-
-	\end{enumerate}
+	In summary, although NI and SE both predict the similar qualitative predictions of rigidity when it comes the behavior of FE and disagreements, de facto, the efficiency of forecasting from NI is higher than SE.
+The only additional uncertainty in NI to that FIRE is the nowcasting uncertainty, which is discounted in future.
+While in SE, the uncertainty do come from the lagged update of information, which involve all uncertainty of the shocks that are not yet updated in agents' information set.
 
@@
 
-	Professional Forecasters(SPF) and New York Fed Survey of Consumer Expectation(SCE).
-
-	The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both current year forecast and 1-year-ahead inflation forecast each quarter.
-
-	SCE data, although each individual is surveyed for 12 months in a row, is only asked to forecast 1-year-ahead inflation.
-This is especially so in the density forecast.
-So we can only perform a weak test.
-
-	We follow \citet{engelberg2009comparing} to estimates the density distribution of each individual surveyee for SPF.
-New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty.
-Therefore, I directly use them.
-
-	For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.
+	The focus of this paper naturally restricts my options of the survey data to use compared to other empirical  literature of testing theories of expectation formation.
+The surveys who have elicited density forecasts of macroeconomic variables for a sufficiently long period has been rare.
+More rare, for the purpose of the paper, is the data structure that allows for compare the revisions across vintages of forecasts that have a terminate date of realization, either in individual level or aggregate level.
+
+	Professional Forecasters(SPF)  meet the both criteria thanks to the density forecasts of a number of macroeconomic variables, including headline CPI and PCE inflation they have started eliciting since 2007.
+In particular, the density forecasts are both made for current year forecast, basically nowcasting, as well as one-year-ahead forecast.
+This allows for directly testing the implications from the revisions in uncertainty.
+
+	The New York Fed Survey of Consumer Expectation(SCE) that started in 2013 has at least met the first criteria.
+In particular, households are asked to provide their perceived probabilities to 1-year-ahead inflation for a range of values.
+\footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one.
+NY Fed stuff has excluded those who do not meet this criteria.} The high-frequency monthly panel structure also provides an invaluable chance to explore the dynamics of uncertainty.
+Around one third of the households are surveyed for 12 months.
+
+	I follow \citet{engelberg2009comparing} to estimate the density distribution of each individual surveyee for SPF.
+This is the same approach adopted by New York Fed stuff \citet{armantier2017overview} has followed the same procedures for SCE and directly provided their estimate of uncertainty.
+I directly use them.
+
+	Unsurprisingly, both surveys need some  winsorization.
+For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentile as these are typically abnormals that are due to measurement errors or other reasons.
 For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extreme values.
+All the results in this paper are robust to a different thresholds such as 10 and 1 percentile.
 \footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}
 
-	A summary of the data information is as below.
+	A summary of the data information is in Table \ref{DataInfo}.
 
@@
 
-	\section{Shock-based tests of expectation rigidity }\label{IRShocks}
+	\section{Shock-based tests of expectation rigidity }\label{ShockBased}
 
@@
 	It is widely documented in the literature that behaviors of households expectations more idiosyncratic in comparison with that of professional forecasters.
-\footnote{For this reason, \cite{carroll2003macroeconomic}, for instance, use median professional forecasts as to approximate ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.
+\footnote{\cite{carroll2003macroeconomic}, for instance, uses median professional forecasts as an approximate of the ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.
 The monthly data of SCE allows an analysis in a higher frequency but for a shorter period 2013-2019.
@@
 
-	\section{Conclusion}
+	\section{Conclusion}\label{Conclusion}
 

### 2019-07-01 paper/Draft.tex
final submission of 2nd paper

@@
 \usepackage{natbib}
+\usepackage{rotating}
+\usepackage{threeparttable}
 
@@
 		Surveys on density forecasts of macroeconomic variable that are not available until recent provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
-This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households.
+This paper first documents the persistent dispersion in uncertainty about future inflation as well as other stylized facts across economists and households.
 Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE).
 Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.
-This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.
+This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of the analysis.
 
@@
 On one hand, various theories built upon different micro foundations produce somewhat similar macro patterns.
-For instance, the notion of expectation rigidity micro-founded by different theories mostly generate sluggish response to new information.
+For instance, the notion of expectation rigidity micro-founded by different theories mostly generate a sluggish response to new information.
 On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.
@@
 uncertainty.
-Specifically, in this paper I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty.
+Specifically, in this paper, I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty.
 Second empirically I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey.
@@
 	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of values of the variable of forecast\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.}.
-With density forecasts,  variance of individual forecast can be estimated as an indicator of the uncertainty.
+With density forecasts,  the variance of individual forecast can be estimated as an indicator of the uncertainty.
 Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency.
@@
 	This paper is related to three strands of literature.
-First, recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data.
+First, the recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data.
 For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}.
@@
 
-	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probiblistic questions measuring subjective uncertainty in economic surveys.
-Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people}and other work have all shown that this is actually less of a concern.
+	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probabilistic questions measuring subjective uncertainty in economic surveys.
+Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have all shown that this is actually less of a concern.
 \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses.
-Broadly speaking, the advocators have argued that going beyond revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
+Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
 This insight holds for not only point forecast, but also and even more importantly, for uncertainty.
@@
 Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments.
-Section \ref{empirical} discusses the survey data used for this paper, and presents both the stylized patterns and time series regressions that test the implications of these theories.
+Section \ref{empirical} discusses the survey data used for this paper and presents both the stylized patterns and time series regressions that test the implications of these theories.
 Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.
@@
 	An agent $i$ is forming expectations about a stochastic variable $y^i_{t+h}$.
-The supscript $i$ can be dropped if it is an aggregate (i.e.
-inflation) variable instead of individual specific  (i.e.
+The superscript $i$ can be dropped if it is an aggregate (i.e.
+inflation) variable instead of individual-specific  (i.e.
 household income or house value).
@@
 So we can simply denote the variable as $y_{t+h}$.
-\footnote{Only in the context of aggregate variable, it is justified to study the population moments such as average expectations and disagreements.
+\footnote{Only in the context of aggregate variable, it make sense to study the population moments such as average expectations and disagreements.
 Studying expectations of idiosyncratic variables requires individual panel data, as well as the idiosyncratic realizations of the variable.
@@
 \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$.
-Examples of such include multi-prior or model uncertainty.
-\citet{hansen2001robust}, \citet{hansen2008robustness}, etc.}
+For instance, \citet{patton2010forecasters} finds that the disagreements are driven by not only difference in information but also heterogeneity in prior and models.
+More theoretical work includes multi-prior or model uncertainty such as \citet{hansen2001robust}, \citet{hansen2008robustness}, etc.}
 
@@
 
-	The population analogues of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents.
+	The population analogs of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents.
 Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively.
-Hereafter, they are termed as population mean forecast, population uncertainty and population forecast error, respectively.
-In addition, disagreements is defined as the cross-sectional variance of mean forecasts of individual agents.
+Hereafter, they are termed as the population mean forecast, population uncertainty and population forecast error, respectively.
+In addition, disagreement is defined as the cross-sectional variance of mean forecasts of individual agents.
 Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $.
@@
 
-	In summary, we have 3 individual moments and 4 population moments listed in below in Table \ref{MomSum}.
+	To abuse the language, I refer to the 3 individual indicators and 4 population indicators as moments and they are  listed in Table \ref{MomSum}
 
@@
 
-	Finally, we assume the underlying true process of $y_{t}$ is $AR(1)$ with persistency parameter $0<\rho <1$ and i.i.d. shock $\omega_t$.
+	Finally, we assume the underlying true process of $y_{t}$ is $AR(1)$ with persistence parameter $0<\rho <1$ and i.i.d. shock $\omega_t$.
 
@@
 	Although we make the assumption of i.i.d.
-shock here.
-The framework allows for the possibility of time-varying volatility, i.e.
-the variance of $\omega_t$ is thus $\sigma^2_{t,\omega}$ with time subsript.
+shock, the framework allows for the possibility of time-varying volatility, i.e.
+the variance of $\omega_t$ is thus $\sigma^2_{t,\omega}$ with time subscript.
 
@@
 	In the FIRE benchmark,  it is assumed that all agents perfectly observe $y_t$ at time $t$ and understand the true process of $y$.
-Therefore, individual forecast is $\rho^h y_t $, which is shared by all agents.
-Therefore, it is also equal to average forecast.
+Therefore, the individual forecast is $\rho^h y_t $, which is shared by all agents.
+Therefore, it is also equal to the average forecast.
 
@@
 
-	I use supscrit of $*$ to denote all the moments according to FIRE.
+	I use superscript of $*$ to denote all the moments according to FIRE.
 It is easy to see that the forecast error is orthogonal to information available till time $t$.
@@
 This is not the case within $h$ periods as the realized shocks in overlapping periods enter both forecast errors.
-These FE-based restrictions of FIRE provide the foudnations for the tests used in Table \ref{NullTest}.
+These FE-based restrictions of FIRE provide the foundations for the tests used in Table \ref{NullTest}.
 
@@
 The uncertainty about future $y$ simply comes from uncertainty about unrealized shocks between $t$ and $t+h$.
-With the same model in mind (Equation \ref{AR_process})and same information $y_t$, everyone's uncertainty is equal to the weighted sum of the future volatility before its realization.
+With the same model in mind (Equation \ref{AR_process}) and the same information $y_t$, everyone's uncertainty is equal to the weighted sum of the future volatility before its realization.
 (Equation \ref{VarREIndPop}).
-In FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}
+In FIRE, there are neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}
 
@@
 $\sigma^2_{t+h|t}$, $\sigma^2_{t+h+1|t+1}$, etc, depends on the true process of $y$.
-Specifically, it depends if $\sigma^2_\omega$ is time varying.
+Specifically, it depends if $\sigma^2_\omega$ is time-varying.
 If time-invariant, h-period-ahead uncertainty is simply as constant.
-In baseline case we make such an assumption, in general it may not be true.
-\footnote{\citet{xx} on time-varying volatility.}
-
-	The testable implication of rationality lies in the revision in uncertainty.
+In baseline case, I make such an assumption, in general it may not be true.
+\footnote{For example, \citet{justiniano2008time}, \citet{vavra2013inflation} on time-varying volatility of inflation.}
+
+	The testable implication of rationality lies in the revision of uncertainty.
 Hereafter, we refer revision (instead of change) as the difference of moments across vintages of forecast with the fixed terminate date of realization.
@@
 
-	More generally,  denote the forecast of $y_{t+h}$ over horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$. Then the uncertainty at different points of the $k$ is the following.
+	More generally,  denote the forecast of $y_{t+h}$ over the horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$. Then the uncertainty at different points of the $k$ is the following.
 
@@
 
-	Moving from $t$ to $t+1$, for instance, revision in uncertainty can be also expressed as a function of previous revision.
+	Moving from $t$ to $t+1$, for instance, revision in uncertainty can be also expressed as a function of the previous revision.
 
@@
 One tractable assumption is that there is a homogenous Poisson rate $\lambda$ of updating among the population.
-Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.
+Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with the probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since the last update.
 
@@
 	In FIRE, updating at each period $t$ resolves only the uncertainty about the shocks that have just realized in $t$.
-In constrast, in SE each updating resolves the uncertainty about all the realized shocks since last update.
+In contrast, in SE each updating resolves the uncertainty about all the realized shocks since the last update.
 From $t-\tau$ to $t$, the revision in uncertainty is
@@
 
-	FIRE basically assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in previous period.
-So setting $\tau =1$ in above equation gives the reduction in uncertainty in FIRE.
+	FIRE basically assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in the previous period.
+So setting $\tau =1$ in the above equation gives the reduction in uncertainty in FIRE.
 The reduction in uncertainty is greater in SE for any $\tau>1$ than FIRE.
 
-	In individual level, the key difference between FIRE and SE is that the later does not reduce uncertainty  as efficiently as in the former primarily because of the rigidity incorporating new information.
+	In the individual level, the key difference between FIRE and SE is that the later does not reduce uncertainty  as efficiently as in the former primarily because of the rigidity incorporating new information.
 In the same time, note that the rigidity in updating according to SE cannot be systematically observable in the individual level, both in terms of forecasts errors and uncertainty.
-This is because the behaviors of each individual forecast specifically depends on if the she updates or not in that period.
+This is because the behaviors of each individual forecast specifically depend on if she updates or not in that period.
 
 	Relying upon the law of large numbers, one can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$.
-\footnote{\citet{carroll2003macroeconomic} is one notable example of this.}
+\footnote{\citet{carroll2003macroeconomic} is good example of this for households.}
 
@@
 
-	Similarly, the inefficiency of reducing uncertainty in SE takes the following form in aggregate level.
+	Similarly, the inefficiency of reducing uncertainty in SE takes the following form in the aggregate level.
 Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.
@@
 		\begin{aligned}
-			\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
+			\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction of non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
 			& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
@@
 
-	Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibits serial correlation described in Equation \ref{VarSERv}.
+	Since not all agents incorporate the recently realized shocks, the revision in average uncertainty exhibits serial correlation described in Equation \ref{VarSERv}.
 It is a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart.
@@
 
-	In particular, the second component is the information gain from most recent realization of the shock underweighted by $\lambda<1$.
-The first component is the inefficiency sourced from stickiness of updating.
+	In particular, the second component is the information gain from the most recent realization of the shock underweighted by $\lambda<1$.
+The first component is the inefficiency sourced from the stickiness of updating.
 The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction compared to in FIRE.
@@
 
-	A class of models (\citet{lucas1972expectations}, \citet{sims2003implications}, \cite{woodford2001imperfect} etc.), noisy information(NI) hereafter, describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
-The starting assumption is that agent cannot observe the true variable perfectly.
+	A class of models (\citet{lucas1972expectations}, \citet{sims2003implications}, \cite{woodford2001imperfect}, etc.), noisy information(NI) hereafter, describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.
+The starting assumption is that the agent cannot observe the true variable perfectly.
 Unlike SE, it is assumed that agents keep track of the realizations of signals instantaneously all the time.
@@
 	What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$.
-Specifically, mean forecast of individual $i$ is the posterior mean based on her prior and realized signals $s_{i,t}$.
+Specifically, the mean forecast of individual $i$ is the posterior mean based on her prior and realized signals $s_{i,t}$.
 
@@
 it does not only depend on $PH$, but also the forecast horizon $h$.
-As $\rho<1$, the rigidity declines with longer horizon.
-In this regard, the rigidity implied by NI and SE are different because the form is fixed and the later is horizon dependent.
+As $\rho<1$, the rigidity declines with a longer horizon.
+In this regard, the rigidities implied by NI and SE are different because the form is fixed and the later is horizon dependent.
 
 	What differentiates average forecast from individual's is the role played by private signals.
-On average, private signals cancel out across agents, therefore, only public signals enter in average forecast, thus, average forecast errors (Equation \ref{FENIPop}).
+On average, private signals cancel out across agents, therefore, only public signals enter the average forecast, thus, average forecast errors (Equation \ref{FENIPop}).
 
@@
 
-	Kalman filtering also updates the variance according to rule normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in previous period and variance of signals.
+	Kalman filtering also updates the variance according to the rule of normal updating.
+The posterior variance at time $t$ is a linear function of uncertainty in the previous period and variance of signals.
 
@@
 $\Sigma^v \neq 0$, there is inefficiency in reducing uncertainty compared to FIRE.
-This mea
 
@@
 
-	As a result, the revision in h-period-ahead uncertainty from $t-1$ to $t$ only partially reacts to the resolution of  uncertainty from newly realized shock $\omega_t$ in the passed period.
+	As a result, the revision in h-period-ahead uncertainty from $t-1$ to $t$ only partially reacts to the resolution of  uncertainty from newly realized shock $\omega_t$ in the past period.
 
@@
 
-	Figure \ref{IllustrateNI} illustrates the Kalman filtering problem over the $10$ period horizon from to $t$ to $t+10$  following one-time shock of one standard deviation $\omega_t$.
-For illustration purpose, I assume that both private and public signals have the equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e.
+	Figure \ref{IllustrateNI} illustrates the Kalman filtering problem over the $10$-period horizon from to $t$ to $t+10$  following a one-time shock of one standard deviation of $\omega_t$.
+For illustration purpose, I assume that both private and public signals have an equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e.
 $\sqrt{\frac{\sigma^2_\omega}{1-\rho^2}}$.
@@
 
-	The sharp rise in nowcasting uncertainty in the beginning of the period is only humbly reflected in the forecasting uncertainty seems counterintuitive in the first sight.
+	In the first sight, the sharp rise in nowcasting uncertainty at the beginning of the period being only humbly reflected in the forecasting uncertainty seems counterintuitive.
 Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^2(h-k)$.
 (Equation \ref{VarNIEq}).
-It is also interesting that for the particular configurations of noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may have expected compared to FIRE.
+It is also interesting that for the particular configurations of the noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may have expected compared to FIRE.
 This has important quantitative implications for NI models.
-In particular, the nosiness of the signals need to be consistent with the degree of rigidity.
+In particular, the nosiness of the signals needs to be consistent with the degree of rigidity.
 I will return this point in the next section.
@@
 		\centering
-		\includegraphics[width=13cm]{figures/ni_illustration.png}  
+		\includegraphics[width=13cm]{figures/ni_illustration.png}  \\
+		{\footnotesize Note: the top two figures plot the nowcasting of $y_{t+k}$  at time $t+k$ and forecasting of $y_{t+h}$ at time $t+k$  based on a Kalman filtering together with FIRE after a one-time shock of one unit at time $t$.
+The nowcasting and forecasting uncertainty are correspondingly plotted in the bottom.
+Both private signal and public signal have the conditional variance equal to long-run variance of y, i.e.
+$\sigma_\epsilon = \sigma_\xi = \sigma_y$.
+The plotted signals are are a pair of particular draw from their respective conditional distribution.
+}
 		\caption{Nowcasting and Forecasting in Noisy Information}
@@
 
-	NI also predicts non-zero disagreements in the presence of private signals.
-The behavior of disagreements across agents come from the difference in realized private signals.
+	NI also predicts non-zero disagreement in the presence of private signals.
+The behavior of disagreement across agents come from the difference in realized private signals.
 Specifically, it is equal to the following.
@@
 
-	The implications for disagreements are straightforward.
-First, the disagreements decreases with the forecast horizon for the reason of discounting.
-Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
+	The implications for disagreement are straightforward.
+First, the disagreement decrease with the forecast horizon for the reason of discounting.
+Second, the disagreement depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
 Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.
@@
 
-	Taking stock, both SE and NI predict rigidity in expectation incorporating arrival of new information.
+	Taking stock, both SE and NI predict rigidity in incorporating the arrival of new information.
 In the former context, the rigidity comes from the simple non-updating of the most realization of the variable.
-In the later case, the rigidity comes from a partial reaction to new information due to its nosiness.
+In the latter case, the rigidity comes from a partial reaction to new information due to the nosiness of the signals.
 In addition to forecast and disagreements, the rigidity is also reflected in the dynamics of uncertainty.
-Uncertainty in SE does not resolve as rapid as in FIRE because the newly realized shocks do not get updated by some of the agents.
-While in NI, the drop in uncertainty is dampened because the there is positive uncertainty associated with the real-time realization of the variable.
+Uncertainty in SE does not resolve as rapidly as in FIRE because the newly realized shocks do not get updated by some of the agents.
+While in NI, the drop in uncertainty is dampened because there is additional uncertainty associated with the real-time realization of the variable.
 
 	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories.
-Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to the one unconditional standard deviation of $y$.
+Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to one unconditional standard deviation of $y$.
 And the $\lambda$ is set to be $0.25$, implying on average an update interval of four quarters.
@@
 Both pick up in the time of the shock and gradually declines over the horizon as the forecaster approaches terminate date $t+10$.
-The difference is that in NI, both the forecast and forecast errors move up and downs around the the smooth version of the SE since noise is not perfect.
-
-	The dynamic of disagreements and uncertainty, however,  illustrate one parametric differences between SE and NI.
-In particular,  the initial pick in disagreements is higher for NI compared to SE for the particular parameter values.
+The difference is that in NI, both the forecast and forecast errors move up and downs around the smooth version of the SE since signals are not perfect.
+
+	The dynamic of disagreements and uncertainty, however,  illustrate one parametric difference between SE and NI.
+In particular,  the initial increase in disagreements is higher for NI compared to SE for the particular parameter values.
 This implies that the noise of the private signal that drives the disagreements in NI exceeds that the extent to which the agents do not simultaneously update in SE.
@@
 
-	For the same parameters, however, the inefficiency seen in dynamics of uncertainty seem to be way more substantial for SE than in NI.
+	For the same parameters, however, the inefficiency seen in dynamics of uncertainty seems to be much more substantial for SE than in NI.
 Overall, the uncertainty drops almost as efficiently as in FIRE.
-The difference of SE and the FIRE benchmark is more notable.
+The difference between SE and the FIRE benchmark is more notable.
 This is the graphical illustration of Equation \ref{VarSERv}.
@@
 		\includegraphics[width=16cm]{figures/ir_popseni.png} 
-		\caption{Impulse responses of moments to a shock to inflation}
+			{\footnotesize Note: figure 1-6 plot the dynamics of a one-time shock to inflation $\omega_{t+k}$, the realized value of $y_{t+k}$,  average forecast of $\bar y_{t+10|t+k}$, forecasting errors $\overline{FE}_{t+10|t+k}$, disagreements $\overline {Disg}_{t+10|t+k}$, and uncertainty $\bar \sigma^2_{t+10|t+k}$ to a one-time shock  of unit one at time $t$, i.e.
+$\omega_t=1$.
+For NI, public and private signals’ variance is equal to long-run variance of $y$, i.e.
+$\sigma_\epsilon = \sigma_\xi = \sigma_\xi $.
+For SE, $\lambda = 0.75$.
+}
+		\caption{Impulse responses of population moments to a shock to inflation}
 		\label{ir_pop}
@@
 
-	As it is made clear by the Figure, one notable difference of the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time varying.
+	As it is made clear by the Figure, one notable difference between the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time varying.
 In particular, the implied rigidity from NI in the time of the shock, given there is substantial information gain from Kalman filtering in the same period, is quite low.
@@
 		\centering
-		\includegraphics[width=13cm]{figures/rigidity.png} 
+		\includegraphics[width=13cm]{figures/rigidity.png} \\
+		{\footnotesize Note: implied rigidity is $1-\lambda$ in SE and $(1-P_{t+k}H)$ in NI.
+Rigidity from NI are plotted for three values of noisiness of signals, i.e.
+0.1, 1 and 10 times of the unconditional variance of $y$.
+}
 		\caption{Rigidity from Two Models}
@@
 	In summary, although NI and SE both predict the similar qualitative predictions of rigidity when it comes the behavior of FE and disagreements, de facto, the efficiency of forecasting from NI is higher than SE.
-The only additional uncertainty in NI to that FIRE is the nowcasting uncertainty, which is discounted in future.
-While in SE, the uncertainty do come from the lagged update of information, which involve all uncertainty of the shocks that are not yet updated in agents' information set.
+The only additional uncertainty in NI to that in FIRE is the nowcasting uncertainty, which is discounted in future.
+While in SE, the uncertainty do come from the lagged update of information, which involve uncertainties about all the shocks that are not yet updated in agents' information set.
 
@@
 The surveys who have elicited density forecasts of macroeconomic variables for a sufficiently long period has been rare.
-More rare, for the purpose of the paper, is the data structure that allows for compare the revisions across vintages of forecasts that have a terminate date of realization, either in individual level or aggregate level.
-
-	Professional Forecasters(SPF)  meet the both criteria thanks to the density forecasts of a number of macroeconomic variables, including headline CPI and PCE inflation they have started eliciting since 2007.
+Rarer, for the purpose of the paper, is the data structure that allows for comparing the revisions across vintages that have a fixed terminate date of realization, either in individual level or aggregate level.
+
+	Survey of Professional Forecasters(SPF) meet both criteria thanks to the density forecasts of a number of macroeconomic variables, including headline CPI and PCE inflation they have started eliciting since 2007.
 In particular, the density forecasts are both made for current year forecast, basically nowcasting, as well as one-year-ahead forecast.
@@
 	I follow \citet{engelberg2009comparing} to estimate the density distribution of each individual surveyee for SPF.
-This is the same approach adopted by New York Fed stuff \citet{armantier2017overview} has followed the same procedures for SCE and directly provided their estimate of uncertainty.
+\footnote{For the answers with positive probabilities assigned to three bins, the approach fits the the histogram with a generalized beta distribution.
+For those with only two bins with positive probabilities and adjacent, it is fit with a triangular distribution.
+For only one bin with probability, a uniform distribution over the positive probability bin is fit.
+See my online appendix for the detailed steps of estimation of python codes.} This is the same approach adopted by the New York Fed researchers \citet{armantier2017overview} for SCE and directly provided their estimate of uncertainty.
 I directly use them.
@@
 For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentile as these are typically abnormals that are due to measurement errors or other reasons.
-For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extreme values.
-All the results in this paper are robust to a different thresholds such as 10 and 1 percentile.
+For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast are inclined to give extreme values.
+All the results in this paper are robust to a different threshold such as 10 and 1 percentile.
 \footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}
@@
 			Individual Var in Density                      & 1-yr earning growth                     & No                       \\
-			Pannel Structure                               & stay up to 12 months                    & average stay for 5 years \\
+			Panel Structure                               & stay up to 12 months                    & average stay for 5 years \\
 			Demographic Info                        & Education, Income, Age, Location        & Industry    \\
@@
 
-	Throughout the paper, I use two measures of Inflation, headline CPI inflation and PCE inflation. The forecasts-based measures are computed and used correspondingly.
+	Throughout the paper, I use two measures of inflation, headline CPI and PCE . The forecasts-based measures are computed and used correspondingly.
 
@@
 
-	It is widely documented in literature \cite{xxx, xxx} and resonated by anecdotal narrative that high inflation is typically associated with high inflation uncertainty.
+	It is widely documented in literature \footnote{The list literature showing positive inflation and uncertainty is long.
+For example \citet{ball1990inflation}.
+} and resonated by anecdotal narratives that high inflation is typically associated with high inflation uncertainty.
 However, the observable correlation of realized inflation and the directly estimated average uncertainty from both  forecasters and households are, if any, negative during the period between 2007-2019.
@@
 Although according to our benchmark framework in \ref{theory}, there is no mathematical correlation between the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
-The correlation coefficient of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, respectively.
+The correlation coefficients of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, respectively.
 Compared to professional forecasts, households forecasts exhibit such a positive correlation.
 
-	The last row in of Figure \ref{UnceratitnyOtherMoments} explores the relationship between disagreements and uncertainty.
-Many empirical literature in macroeconomics use disagreements and uncertainty as if they are similar concepts.
-Partly this confusion in practice is due to difficulty of finding the appropriate measure of this in the first place.
+	The last row of Figure \ref{UnceratitnyOtherMoments} explores the relationship between disagreement and uncertainty.
+Many empirical literatures in macroeconomics use disagreements and uncertainty as if they are similar concepts.
+Partly this confusion in practice is due to the difficulty of finding appropriate measures of uncertainty in the first place.
 But as we have presented in \ref{theory}, the two are distinct concepts.
@@
 
-	Persistent disagreements in expectations has been used as an important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
-A similar fact checking can be done with respect to individual uncertainty.
-FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREInd}.
+	Persistent disagreement in expectations has been used as an important stylized evidence inconsistent with the assumption of identical expectation embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
+A similar fact-checking can be done with respect to individual uncertainty.
+FIRE predicts individual share an equal degree of uncertainty as  seen in Equation \ref{VarREPop}.
 In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEInd}).
-NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precision of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
-Therefore, presence of dispersion of uncertainty across agents can be read against FIRE.
-
-	Figure \ref{IQR_Unceratitny} plots the median inflation expectation along its 25/75 percentiles in the left and its counterpart in uncertainty in the right column.
+NI allows for the possibility of homogeneity in uncertainty only under the stringent conditions of an equal precision of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
+Therefore, the presence of dispersion of uncertainty across agents can be read against FIRE.
+
+	Figure \ref{IQR_Unceratitny} plots the median inflation expectation along with its 25/75 percentiles in the left and its counterpart in uncertainty in the right column.
 Not only there is long-lasting dispersion in individual forecasts, i.e.
-disagreements, but also notable heterogeneity in uncertainty across agents.
+disagreement, but also notable heterogeneity in uncertainty across agents.
 And not surprisingly, the dispersion of both forecasts and uncertainty of households are both of a much greater magnitude than that of the professionals.
 The 25/75 inter-quantile-range of households point forecasts is 4-5 percentage points compared to 1 percentage point of professionals.
-And the IQR of uncertainty of households are around 150-200 times(12-14 times for standard deviation) as that of professional forecasters.
-
-	Beside, there are cross-agent-type difference and similarity in terms of distribution of uncertainty.
-Households' uncertainty are more skewed toward to the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty.
+And the IQR of the uncertainty of households is around 150-200 times(12-14 times for standard deviation) as that of professional forecasters.
+
+	Besides, in terms of the distribution of uncertainty, there are households/professional difference and similarity.
+Households' uncertainty is more skewed toward to the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty.
 This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernel density estimated distribution of uncertainty by year on.
@@
 \footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UnceratitnyOtherMoments} actually exhibits a gradual decline.
-} This is consistent with the observation in top left two figures Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flatten.
-
-	FIRE also predicts an unambiguous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
+} This is consistent with the observation in the top left two graphs of Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flattened.
+
+	FIRE also predicts an unambiguous reduction in uncertainty as one approaches the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
 Although quantitatively it is hard to check this, one can look if the distribution of the uncertainty revision concentrate in the negative range.
@@
 Looking from the histograms, uncertainty revision shows left-skewness relative to zero.
-This implies on average,  more forecasters feel more certain for her nowcast relative to her forecast made one year before.
-Unfortunately, since SCE does not provide the data structure for this purpose, we cannot make a comparison between two types of agents.
+This implies on average,  forecasters feel more certain for her nowcasts relative to her forecast made one year before.
+Unfortunately, since SCE does not provide the data structure for this purpose, I cannot make a comparison between two types of agents.
 A formal test of revision equal to zero or being negative will be carried out in the Section \ref{NullTest}.
@@
 		\centering
-		\smallskip
 		\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
@@
 		\includegraphics[width=4.5cm]{figures/Q9_disg_varSCEM.png}\\
+		{\footnotesize Note:  From left to right: SPF’s CPI, SPF’s PCE, and SCE’s CPI forecast.
+From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of -0.10, -0.05 and -0.24, respectively; uncertainty (red dash) versus forecast errors (blue dot) with correlation coefficient of 0.13, 0.06, 0.40, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.62.
+}
 		\caption{Unceratinty and Other Moments}
@@
 
-	This section first reproduces a number of statistical tests of FIRE used seen existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests relying on uncertainty in Table \ref{RevEfficency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
+	This section first reproduces a number of statistical tests of FIRE used seen existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests relying on uncertainty in Table \ref{RevEfficiency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
 It is an extension of what \citet{fuhrer2018intrinsic} does to mean forecast to uncertainty.
 
-	The first set of tests, hereafter, referred as FE-based tests, utilize the moment restrictions on forecast errors.
-In plain words, the null hypothesis of the three tests are the following.
-First, since the forecasts are on average unbiased according to FIRE, forecast errors across agents should converge to zero in large sample.
+	The first set of tests, hereafter, referred to as FE-based tests, utilize the moment restrictions on forecast errors.
+In plain words, the null hypotheses of the three tests are the following.
+First, since the forecasts are on average unbiased according to FIRE, forecast errors across agents should converge to zero in a large sample.
 Second, forecast errors of non-overlapping forecasting horizon are not serially correlated (Equation \ref{NoSerialCorrFE} ).
-Third, forecast errors cannot be predicted by any information available at the time of forecast, including the mean forecast itself and other variable that is in the agent's information content.
+Third, forecast errors cannot be predicted by any information available at the time of the forecast, including the mean forecast itself and other variables that are in the agent's information set.
 This follows from Equation \ref{NoPastInfFE}.
@@
 The forecast errors are correlated to the extent of the realized shocks in the overlapping periods.
-So the positive serial correlation does not direct violate FIRE.
-For this reason, looking into the correlation of overlapping forecast errors still contain the useful information about the size of the realized shocks.
+So the positive serial correlation does not directly violates FIRE.
+But the correlation of overlapping forecast errors still contain the useful information about the size of the realized shocks.
 
@@
 Since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE.
-Also,the regressions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE.
+Also, the regressions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE.
 Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.
 
-	First,  all three forecast series easily reject the unbiasedness test in the significance level of $1\%$.
+	First,  all three forecast series easily reject the unbiasedness test at the significance level of $1\%$.
 There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecasters(2.2 versus 0.12) for headline CPI.
@@
 
-	Lastly, test 4 in Table \ref{NullTestTable} presents higher serial correlation of forecast errros produced within a year.
+	Lastly, test 4 in Table \ref{NullTestTable} presents a higher serial correlation of forecast errors produced within a year.
 For SPF forecasts, the serial correlation does not exist beyond 1 quarter, implying relative efficiency of forecasts.
 For the households, the forecast errors are more persistent over the entire year in that current forecast errors are correlated with all past forecast errors over the past three quarters.
-Again, although the persistency of 1-year forecast errors within one year do not directly violate FIRE, the fact that households' forecast errors being more persistent than professionals provide useful clues about the relative rigidity of the two types of agents.
+Again, although the persistence of 1-year forecast errors within one year does not directly violate FIRE, the fact that households' forecast errors being more persistent than professionals provide useful clues about the relative rigidity of the two types of agents.
 
@@
 		\end{tabular}
+	\\
+	{\footnotesize Note: white standard errors reported in the parentheses of estimations.  *** p$<$0.001, ** p$<$0.01 and * p$<$0.05. }
+
 	\end{table}
 
-	The second batch of tests in Table \ref{RevEfficency} focus on estimating forecasting efficiency using revisions of mean forecasts and uncertainty, hereafter referred as revision-based tests.
-In plain words, the revision from 1-year-ahead forecast to nowcast of current-year inflation is efficient according two criteria (1) Forecast revision does not depend on past information, including the past revisions.
-(2) Drop in uncertainy is sufficiently rapid to reflect the uncertainty of all realized shocks.
+	The second batch of tests in Table \ref{RevEfficiency} focus on estimating forecasting efficiency using revisions of mean forecasts and uncertainty, hereafter referred as revision-based tests.
+In plain words, the revision from 1-year-ahead forecast to nowcast of current-year inflation is efficient according to two criteria (1) Forecast revision does not depend on past information, including the past revisions.
+(2) Drop in uncertainty is sufficiently rapid to reflect the uncertainty of all realized shocks.
 
@@
 This regression follows from Equation \ref{VarSERv} for SE and Equation \ref{VarNIRv} for NI.
-Although it  cannot be directly used as a test against FIRE null, the autocorrelation coefficient speaks to the speed of drop in uncertainty.
+Although it  cannot be directly used as a test against FIRE null, the autocorrelation coefficient speaks to the speed of the drop in uncertainty.
 Depending on the model, one can interpret it as the particular structural parameter of rigidity, as shown in Figure \ref{rigidity}.
 
-	Top panel in Table \ref{RevEfficency} and bottom panel presents the results for mean forecast.
-Following \citet{fuhrer2018intrinsic}, I include median forecast available at time $t$ and $t-1$ as an indicator of past information for the revision regression.
+	The top panel in Table \ref{RevEfficiency} presents the results for the mean forecast.
+Following \citet{fuhrer2018intrinsic}, I include the median forecast available at time $t$ and $t-1$ as an indicator of past information for the revision regression.
 In the first column of each panel, I report the regression on a constant.
@@
 
-	The second to fourth columns of each panel in Table \ref{RevEfficency} checks auto correlation of revisions including different lags.
+	The second to fourth columns of each panel in Table \ref{RevEfficiency} checks autocorrelation of revisions including different lags.
 Revisions of forecasts are serially correlated over 4 quarters and the coefficients are all positive and significant.
 Also, the median forecasts as the past information always predicts a negative revision with significant coefficients.
-This is evidence against null hypothesis of FIRE and my estimates are comparable with those by \citet{fuhrer2018intrinsic}.
-
-	In the bottom panel reports auto regression results for revision in uncertainty.
+This is evidence against the null hypothesis of FIRE and my estimates are comparable with those by \citet{fuhrer2018intrinsic}.
+
+	The bottom panel reports autoregression results for revision in uncertainty.
 Again, the first column first test the mean revision against the null being zero.
-The mean revisions in uncertainty are both negative(0.5-0.6 percentage poitns equivalence in standard deviation of uncertainty) and statistically significant, confirming our observation from Figure \ref{RevisionHist} that forecasters are more certain about current inflation compared her previous year forecast.
-
-	The second to fourth column show positive serial correlation of revision in uncertainty for both CPI and PCE forecasts.
+The mean revisions in uncertainty are both negative (0.5-0.6 percentage points equivalence in standard deviation of uncertainty) and statistically significant, confirming our observation from Figure \ref{RevisionHist} that forecasters are more certain about current inflation compared her previous year forecast.
+
+	The second to fourth column show a positive serial correlation of revision in uncertainty for both CPI and PCE forecasts.
 The revision to CPI seems more efficient as serial correlation is with only one quarter lag.
@@
 
-	\begin{table}[ht]
+		\begin{sidewaystable}[ht]
+			\begin{adjustbox}{width={24cm},totalheight={14cm}}
+				\begin{threeparttable}
 					\caption{Tests of Revision Efficiency using Mean Revision and Uncertainty}
-		\label{RevEfficency}
-		\begin{adjustbox}{angle=90}
-
+					\label{RevEfficiency}
 					\begin{tabular}{lllllllll}
@@
 					\end{tabular} 
+					\begin{tablenotes}
+						\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
+					\end{tablenotes}
+				\end{threeparttable}
 			\end{adjustbox}
-	\end{table}
+		\end{sidewaystable}
 
@@
 $y_{t|t-1}$ to $y_{t+1|t}$.
-The auto-correlation of change in mean forecast and uncertainty does embed  tests of null of FIRE (Equation \ref{VarREPop}).
-But if the individual forecasts and their uncertainty turn out to be persistent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
-
-	\begin{table}
-		\centering 
+The auto-correlation of change in mean forecast and uncertainty does not embed tests of null of FIRE (Equation \ref{VarREPop}).
+But if the individual forecasts and their uncertainty are persistent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
+
+	\begin{sidewaystable}[ht]
+		\begin{adjustbox}{width={24cm},totalheight={14cm}}
+			\begin{threeparttable}
 				\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
 				\label{WeakRevEfficiency}
-		\begin{adjustbox}{width={24cm},totalheight={14cm},angle=90}
 				\begin{tabular}{llllllllllllll}
@@
 				\end{tabular}
+				\begin{tablenotes}
+					\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
+				\end{tablenotes}
+			\end{threeparttable}
 		\end{adjustbox}
-	\end{table}
+	\end{sidewaystable}
 
@@
 	\citet{coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
-Unlike the time series regressions that test null hypotheses of FIRE in previous section, this approach allows a more straightforward comparison between the empirical evidence from surveys and the theoretical predictions illustrated in Figure \ref{ir_pop}.
+Unlike the time series regressions that test null hypotheses of FIRE in the previous section, this approach allows a more straightforward comparison between the empirical evidence from surveys and the theoretical predictions illustrated in Figure \ref{ir_pop}.
 The difficulty of this approach lies in identifying a shock $\omega_t$ that is a pure innovation to inflation at time $t$.
 
-	In this paper I use three types of shocks: technology shock from \citet{gali1999technology}, oil price shock from \citet{hamilton1996happened} and monetary policy shocks from  \citet{laseen2011anticipated}.
+	I use three types of shocks: technology(productivity) shock from \citet{gali1999technology}, oil price shock from \citet{hamilton1996happened} and monetary policy shocks from  \citet{laseen2011anticipated}.
 The first two are the same in \citet{coibion2012can}.
@@
 	(3) Monetary policy shocks: target surprise and path surprise in the terminology of \citet{laseen2011anticipated}.
-Target surprise is defined as unexpected change in federal funds rate in a particular date of FOMC meetings.
-It is the OLS residual of federal funds rate change in the past expected change in federal funds rate.
+Target surprise is defined as the unexpected change in federal funds rate in a particular date of FOMC meetings.
+It is the OLS residual of federal funds rate change in the past expected change in the federal funds rate.
 The 2-year ahead path surprise is the regression residual of future implied federal funds rate on the target surprise.
@@
 
-	The reason for including monetary policy shocks, although it turns out to provide less robust evidence, is twofold.
-First, it is well known that the role of expectation in the working and implementation of monetary policy in the post criss period has been of a great relevance.
-Especially, around zero-lower-bound, the central banks have utilized nontraditional tools such as forward guidance which primarily works through influencing expectations of market agents.
+	The reasons for including monetary policy shocks, although it turns out to provide less robust evidence, are twofold.
+First, the role of expectation in the working and implementation of monetary policy in the post-crisis period has been of a great relevance.
+Especially, around zero-lower-bound, central banks have utilized nontraditional tools such as forward guidance which primarily works through influencing expectations of market agents.
 
@@
 
-	For a direct comparison of my results and \citet{coibion2012can}, I first explore the impulse responses of CPI inflation $y_{t+k}$, SPF forecast errors and disagreements to one standard deviation of each shock at time $t$.
-In particular, the responses of disagreements is with respect to the absolute value of the shocks.
+	For a direct comparison of my results and \citet{coibion2012can}, I first explore the impulse responses of CPI inflation $y_{t+k}$, SPF forecast errors and disagreement to one standard deviation of each shock at time $t$.
+In particular, the responses of disagreement is with respect to the absolute value of the shocks.
 Because CPI inflation forecast is available only after 1984, the sample period 1984-2007 is six years shorter than that in Figure 2 from \citet{coibion2012can}: 1976-2007.
@@
 
-	The underlying regression that produces impulse response estimates is  Equation \ref{IRRegression}, according to which inflation(or moments) in current quarter is a function of 4-period lags of itself  and the realized shocks in current and previous period.
+	The underlying regression that produces impulse response estimates is  Equation \ref{IRRegression}, according to which inflation $y_t$ (or moments, $\overline {FE}_{t}$, $\overline{Disg}_t$ and $\bar \sigma^2_t$) in current quarter is a function of 4-period lags of itself and the realized shocks in current and previous period.
 The estimate of autoregression coefficients $\beta_\tau$ and shock-specific coefficients $\beta_{S,k}$ for different lags can be used to compute impulse responses of the variables of interest.
@@
 	\begin{eqnarray}\label{IRRegression}
-		y_{t}  = \alpha + \sum^4_{\tau=1} \beta_{\tau} y_{t-\tau} +  \sum^1_{k=0} \sum_{S \in \{O,T\}}\beta_{S,k}\omega_{S,t-k} + \epsilon_t 
-	\end{eqnarray}
-
-	FIRE predicts $\beta_{S,k}=0\quad \forall k=1$ for the regressions with forecasts moments as dependent variable.
+		x_{t}  = \alpha + \sum^4_{\tau=1} \beta_{\tau} y_{t-\tau} +  \sum^1_{k=0} \sum_{S \in \{O,T\}}\beta_{S,k}\omega_{S,t-k} + \epsilon_t 
+	\end{eqnarray}
+
+	FIRE predicts $\beta_{S,k}=0\quad \forall k=1$ in the regressions with forecasts moments as dependent variable.
 i.e.
@@
 
-	The results  presented in the left panel of the Figure \ref{ReplicateCoibionBefore2007} are consistent with FIRE predictions.
-Responses to productivity and oil price shocks are broadly consistent with \citet{coibion2012can} despite a wider confidence band possibly due to the change in inflation measures and difference in sample period.
-First, one standard deviation of productivity unsurprisingly brings down headline inflation by around 10 percentage points  in the first quarter and the negative impacts gradually mute since then till the 7-th quarter.
+	Left panel of the Figure \ref{ReplicateCoibionBefore2007} show results broadly consistent with \citet{coibion2012can} despite a wider confidence band possibly due to the change in inflation measures and the difference in the sample period.
+Productivity and oil price shocks are deflationary and inflationary, respectively.
+One standard deviation of productivity unsurprisingly brings down headline inflation by around 10 percentage points  in the first quarter and the negative impacts gradually mute since then till the 7-th quarter.
 Oil price shock of one standard deviation increases headline inflation by around 3 percentage points in the first quarter and the inflationary impacts last for 6 quarters.
 PCE inflation responds to both the shocks in a similar manner with slightly different magnitudes.
-The responses coefficients are statistically significant as the $95\%$ confidence interval stays on one side of zero for both shock for the same period.
+The responses coefficients are statistically significant as the $95\%$ confidence interval stays on one side of zero for both shocks for the same period.
 
@@
 
-	Lastly, SE and NI models imply disagreement pick up after shocks and gradually drop over longer horizon.
-Looking into the graph, the average response of Disg to absolute value of  technology and oil shocks exhibit patterns similar to this prediction.
+	Lastly, SE and NI models imply disagreement pick up after shocks and gradually drop over the longer horizon.
+Looking into the graph, the average response of disagreement to absolute value of  technology and oil shocks exhibit patterns similar to this prediction.
 Note now that the initial response is no longer statistically significant(same as the original result) and the pick-up of disagreement after both shocks do not take place immediately in the same quarter but in one quarter after the shock.
@@
 
-	The responses to monetary policy shocks turn out to be nosier than for technology and oil price shocks, as presented in the right panel of Figure \ref{ReplicateCoibionBefore2007}.
+	The responses to monetary policy shocks turn out to be noisier than those for technology and oil price shocks, as presented in the right panel of Figure \ref{ReplicateCoibionBefore2007}.
 On the top, I first plot the impulse response of inflation to path surprises $ED8ut$ and target surprise $MP1ut$, separately.
 On average, inflation reduces by around 10 percentage points after one unit increase of target surprise and increases by 10 percentage points following one unit of path surprise to federal funds rate.
-Both responses are  statistically significant in $10\%$  level.
-The unexpected future tightening causing a rise in inflation is consistent with the literature of price puzzle.
+Both responses are  statistically significant in $10\%$  significance level.
+The unexpected future tightening causing a rise in inflation is consistent with the literature of the price puzzle.
 \footnote{See \cite{nakamura2018high} as an example of inflationary responses to a monetary tightening move of the Fed.}
@@
 Non-response of disagreements could be due to that forecasters ``agree'' on the realization of monetary policy shocks.
-Although the benchmark theory of SE and NI do not differentiate shocks, the evidence here seems to suggest that the degree of rigidity depends on  nature of the shocks.
+Although the benchmark theory of SE and NI do not differentiate shocks, the evidence here seems to suggest that the degree of rigidity depends on the nature of the shocks.
 
 	Or there are other explanations.
-First, overall the monetary policy shocks contribute only a small part of variation in inflation compared to supply shocks.
+First, overall the monetary policy shocks contribute only a small part of the variation in inflation compared to supply shocks.
 This was actually used by \cite{coibion2012can} to justify why monetary policy shock was not used in their exercise.
 Second,  I am just running into the same difficulty in identifying real impacts of monetary policy shocks from low frequency data as all other papers addressing this issue.
-\footnote{Examples of identifying monetary policy shocks.
-\cite{xxx} }
 
@@
 As shown in the top three figures, the results are consistent with that in Figure \ref{ReplicateCoibionBefore2007} for period before 2007.
-Oil shock(technology shock) increases(decreases) inflation in the first quarter by 10 percentage  points, whose impacts last till 7-8th quarters.
+Oil shock(technology shock) increases(decreases) inflation in the first quarter by 0.1 percentage  points, whose impacts last till 7-8th quarters.
 Confidence interval of the responses is smaller compared to previous figure probably due to larger sample size.
@@
 	The primary focus of this paper is the behavior of uncertainty.
-Its responses to the absolute value of various shocks is presented in the bottom of the panel.
-Since  average uncertainty do not directly depend on the realizations and sizes of the shocks in various models, as shown in Equation \ref{VarREEq}  Equation \ref{VarSEPop}, and Equation \ref{VarNIEq}, the response of uncertainty cannot be used as a screening device of  FIRE and rigidity models.
-Instead, it should be taken as a basic consistency check of different theories with respect to the behavior of uncertainty.
+Its responses to the absolute value of various shocks are presented at the bottom of Figure \ref{ReplicateCoibionwholeperiod}.
+Since average uncertainty do not directly depend on the realizations and sizes of the shocks in various models, as shown in Equation \ref{VarREPop},  Equation \ref{VarSEPop}, and Equation \ref{VarNIEq}, the response of uncertainty cannot be used as a screening device of  FIRE from rigidity models.
+Instead, it checks the consistency of different theories with respect to the behavior of uncertainty.
 
@@
 future monetary policy stances, again brings about the inflationary effect as before.
-One standard deviation of true tightening shock increases headline CPI inflation by around 15 percentage points in the first period.
+One standard deviation of true tightening shock increases headline CPI inflation by around 0.15 percentage points in the first period.
 In the same time, unexpected rate change does not affect inflation significantly once we include the post-2007 period.
@@
 Interestingly, even though the target surprise does not affect inflation itself, forecast errors do react to it in an inflationary manner.
-The magnitude of the response is as large as 25 percentage points in the first quarter.
+The magnitude of the response is as large as 0.25 percentage points in the first quarter.
 Rigidity models predict forecast errors depend on past shocks, while there does not seem to be strong evidence for this when it comes to monetary policy shocks.
@@
 In the context of NI model, the disagreements can only arise with the presence of private signals.
-Therefore, monetary policy being a more public signal can help explain the muted response of disagreements in comparison of the other shocks.
+Therefore, monetary policy being a more public signal can help explain the muted response of disagreements in comparison with other shocks.
 \footnote{Another explanation is that monetary policy actually coordinates agents' expectations, thus accordingly reduce disagreements, according to \citet{morris2002social}.
@@
 
-	It is widely documented in the literature that behaviors of households expectations more idiosyncratic in comparison with that of professional forecasters.
+	It is widely documented in the literature that behaviors of households expectations are more idiosyncratic in comparison with professional forecasters.
 \footnote{\cite{carroll2003macroeconomic}, for instance, uses median professional forecasts as an approximate of the ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.
@@
 
-	Oil price shock increases CPI by  7-8 percentage points in the first period and the impacts last over the entire 10 months. This is not surprising from the previous results on quarterly data.
-
-	Estimated in higher frequency, the response to target surprise is on average 2.5 percentage points and statistically significant in $10\%$ level.
+	Oil price shock increases CPI by 0.07-0.08 percentage points in the first period and the impacts last over the entire 10 months. This is not surprising from the previous results on quarterly data.
+
+	Estimated in higher frequency, the response to target surprise is on average 0.25 percentage points and statistically significant in $10\%$ level.
 This confirms the wide practice of the literature that identifies monetary non-neutrality using high frequency data.
-In contrast, the inflation responses to path surprise is not significant.
+In contrast, the inflation responses to path surprise are not significant.
 
@@
 	One interesting exception is the response of disagreements to oil price changes.
-Households' disagreements concerning inflation drop by 1 percentage point in the first period after an oil price shock and the response has a reasonably small standard error.
+Households' disagreements concerning inflation drop by 1 percentage point in the first period after an oil price shock and the response have a reasonably small standard error.
 The drop only lasts for 1 month and immediately return to zero since then.
@@
 
-	It is widely conjectured (in spite of limited evidence) that salient items such as gasoline price plays an important role in affecting household inflation expectation.
+	Researchers have also conjectured (in spite of limited evidence) that salient items such as gasoline price plays an important role in affecting household inflation expectation.
 The evidence presented here seems to be consistent with such a prediction.
@@
 		\centering
-		\includegraphics[width=3cm,height=2cm]{figures/CPIAU_ashocks_nmpM.png}  
-		\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocksM.png} \\
-		\smallskip
-		\includegraphics[width=3cm,height=2cm]{figures/SCEFE_ashocks_nmpM.png} 
-		\includegraphics[width=6cm,height=2cm]{figures/SCEFE_ashocksM.png} \\
-		\smallskip
-		\includegraphics[width=3cm,height=2cm]{figures/SCEDisg_ab_ashocks_nmpM.png} 
-		\includegraphics[width=6cm,height=2cm]{figures/SCEDisg_ab_ashocksM.png} \\
-		\smallskip 
-		\includegraphics[width=3cm,height=2cm]{figures/SCEVar_ab_ashocks_nmpM.png} 
-		\includegraphics[width=6cm,height=2cm]{figures/SCEVar_ab_ashocksM.png} 
+		\includegraphics[width=4.5cm,height=3.5cm]{figures/CPIAU_ashocks_nmpM.png}  
+		\includegraphics[width=9cm,height=3.5cm]{figures/CPIAU_ashocksM.png} \\
+		\smallskip
+		\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEFE_ashocks_nmpM.png} 
+		\includegraphics[width=9cm,height=3.5cm]{figures/SCEFE_ashocksM.png} \\
+		\smallskip
+		\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEDisg_ab_ashocks_nmpM.png} 
+		\includegraphics[width=9cm,height=3.5cm]{figures/SCEDisg_ab_ashocksM.png} \\
+		\smallskip 
+		\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEVar_ab_ashocks_nmpM.png} 
+		\includegraphics[width=9cm,height=3.5cm]{figures/SCEVar_ab_ashocksM.png} 
 		\caption{ Responses of Inflation and Household Forecast Moments: 2013-2019}
@@
 It is true that the distinction of public and private signals within NI provides one possibility of reconciling difference in response to shocks.
-If we interpret different ``shocks'' considered here as noisy signals instead of shocks to fundamental variable as defined in \ref{AR_process}, then the difference across ``shocks'' in their degree of publicity may account for the difference in rigidity.
+If we interpret different ``shocks'' considered here as noisy signals instead of shocks to fundamental variable as defined in Equation \ref{AR_process}, then the difference across ``shocks'' in their degree of publicity may account for the difference in rigidity.
 But this implicitly implies redefining the  framework presented in this paper.
@@
 
-	Efficient revision implies  uncertainty drop as much as the volatility of the shock as one approach the terminate date.
-Given the volatility of of different shock are different, this provides the possibility of identifying rigidity by directly comparing the observed revision in uncertainty and that is consistent with the volatility of the shock.
+	Efficient revision implies  uncertainty drop as much as the volatility of the realized shock as one approach the terminate date.
+Given the volatility of shocks are different, this provides the possibility of identifying rigidity by directly comparing the observed revision in uncertainty with the externally identified volatility of various shocks.
 This will be the next step of the analysis.
@@
 
-	Second, rigidity of expectation from either inattention or under-reaction due to noisiness of the signals imply agents do not revise forecasts as efficiently as they do in FIRE in the face of new information.
+	Second, rigidity of expectation from either inattention or under-reaction due to noisiness of the signals implies agents do not revise forecasts as efficiently as they do in FIRE in the face of new information.
 This can be seen from both a sluggish pattern of forecast revision or uncertainty reduction across different vintages of the forecast.
-A weaker test of this spirit uses change of forecasts with fixed horizon.
-These tests support rigidity models in addition to other null hypotheses of rational expectation including unbiasedness,  non-serial-correlation of forecast error.
-etc.
+A weaker test of this spirit uses the changes in mean forecasts and uncertainty with fixed forecasting horizon.
+These tests support rigidity models in addition to other null hypotheses tests of rational expectation including unbiasedness,  non-serial-correlation of forecast errors, etc.
 
@@
 In particular, professional forecasters are more responsive to monetary policy shocks and households are more responsive to oil price shocks.
-This motivates next-step analysis of how much resolution of uncertainty can be attributed to the volatility of various shocks.
+This motivates a next-step analysis of how much resolution of uncertainty can be attributed to the volatility of various shocks.
 This shows the use of uncertainty.
@@
 	So far, the dynamics of moments are separately estimated for each moment.
-Therefore, as a natural extension of the current analysis, one can  undertake a generalized method of moment (GMM) estimation that simultaneously utilize multi-moment restrictions to recover a better estimate of the rigidity parameters.
+Therefore, as a natural extension of the current analysis, one can undertake a generalized method of moment (GMM) estimation that simultaneously utilizes multi-moment restrictions to recover a better estimate of the rigidity parameters.
 This will provide a better parameter that can be used in structural macro models that build in rigidity of expectations.

### 2019-07-01 paper/Draft.tex
Improved the formatting of figures with only IR left.

@@
 \usepackage{threeparttable}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 	The paper is organized as followed.
-Section \label{theory} first sets up a common framework in which testable various theories can be compared.
+Section \ref{theory} first sets up a common framework in which testable various theories can be compared.
 Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments.
@@
 Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to one unconditional standard deviation of $y$.
-And the $\lambda$ is set to be $0.25$, implying on average an update interval of four quarters.
+And the $\lambda$ is set to be $0.75$, implying on average an update interval of four quarters.
 
@@
 		\centering
-		\includegraphics[width=16cm]{figures/ir_popseni.png} 
+		\includegraphics[width=\textwidth]{figures/ir_popseni.png} 
+		\begin{flushleft}
 			{\footnotesize Note: figure 1-6 plot the dynamics of a one-time shock to inflation $\omega_{t+k}$, the realized value of $y_{t+k}$,  average forecast of $\bar y_{t+10|t+k}$, forecasting errors $\overline{FE}_{t+10|t+k}$, disagreements $\overline {Disg}_{t+10|t+k}$, and uncertainty $\bar \sigma^2_{t+10|t+k}$ to a one-time shock  of unit one at time $t$, i.e.
@@
 $\sigma_\epsilon = \sigma_\xi = \sigma_\xi $.
-For SE, $\lambda = 0.75$.
+For SE, $\lambda = 0.25$.
 }
+		\end{flushleft}
 		\caption{Impulse responses of population moments to a shock to inflation}
@@
 		\centering
-		\includegraphics[width=13cm]{figures/rigidity.png} \\
+		\includegraphics[width=0.7\textwidth]{figures/rigidity.png} 
+		\begin{flushleft}
 			{\footnotesize Note: implied rigidity is $1-\lambda$ in SE and $(1-P_{t+k}H)$ in NI.
@@
 }
+		\end{flushleft}
 		\caption{Rigidity from Two Models}
@@
 		\centering
-		\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
-		\includegraphics[width=4.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
-		\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}\\
-		\smallskip
-		\includegraphics[width=4.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
-		\includegraphics[width=4.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
-		\includegraphics[width=4.5cm]{figures/SCE_FE_varSCEM.png}\\
-		\smallskip	
-		\includegraphics[width=4.5cm]{figures/CPI_disg_varSPFCPIQ.png}
-		\includegraphics[width=4.5cm]{figures/PCE_disg_varSPFPCEQ.png}
-		\includegraphics[width=4.5cm]{figures/Q9_disg_varSCEM.png}\\
+		\begin{subfigure}[b]{\textwidth}
+			\centering
+			\caption{Realized Inflation and Uncertainty}
+			\label{InfVar}
+			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
+			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCE_varSPFPCEQ.png}
+		\end{subfigure}
+	    \vspace{1em}
+		\vfill
+		\begin{subfigure}[b]{\textwidth}
+			\centering
+			\caption{Forecast Errors and Uncertainty}
+			\label{FEVar}
+			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_FE_varSPFCPIQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_FE_varSPFPCEQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/SCE_FE_varSCEM.png}
+		\end{subfigure}
+	 \vspace{0.5em}
+		\vfill
+		\begin{subfigure}[b]{\textwidth}
+			\centering
+			\caption{Disagreements and Uncertainty}
+			\label{DisgVar}
+			\includegraphics[width=0.3\textwidth]{figures/CPI_disg_varSPFCPIQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/PCE_disg_varSPFPCEQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/Q9_disg_varSCEM.png}\\
+		\end{subfigure}
+		\\
+		\begin{flushleft}
 			{\footnotesize Note:  From left to right: SPF’s CPI, SPF’s PCE, and SCE’s CPI forecast.
@@
 }
-		\caption{Unceratinty and Other Moments}
+		\end{flushleft}
+		\caption{Uncertainty and Other Moments}
 		\label{UnceratitnyOtherMoments}
@@
 	\begin{figure}[ht]
-		\centering
+		\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\caption{Mean Forecasts}
 		\includegraphics[width=7cm]{figures/IQRmeanCPIQ.png} 
-		\includegraphics[width=7cm]{figures/IQRvarCPIQ.png} \\
 		\smallskip
 		\includegraphics[width=7cm]{figures/IQRmeanPCEQ.png}
-		\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}\\
 		\smallskip
 		\includegraphics[width=7cm]{figures/IQRmeanSCEM.png}
-		\includegraphics[width=7cm]{figures/IQRvarSCEM.png}\\
-		\caption{Dispersion in Mean Forecast and Unceratinty }
+		\end{subfigure}
+	    \hfill 
+		\begin{subfigure}[b]{0.5\textwidth}
+		\centering 
+		\caption{Uncertainty}
+		\includegraphics[width=7cm]{figures/IQRvarCPIQ.png}
+		\smallskip
+		\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}
+		\smallskip
+		\includegraphics[width=7cm]{figures/IQRvarSCEM.png}
+		\end{subfigure}
+		\caption{Dispersion of Mean Forecasts and Unceratinty }
 		\label{IQR_Unceratitny}
@@
 	\begin{figure}[ht]
-		\centering
+		\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\caption{Revision in Mean Forecasts}
 		\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
-		\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  \\
 		\smallskip
 		\includegraphics[width=7cm]{figures/PRCPCEMean1_hist.png} 
-		\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  \\
 		\smallskip
 		\includegraphics[width=7cm]{figures/SCEmean_hist.png} 
-		\includegraphics[width=7cm]{figures/SCEvar_hist.png}  \\
+		\end{subfigure}
+	   \hfill 
+	  	\begin{subfigure}[b]{0.5\textwidth}
+	  	\caption{Revision in Uncertainty}
+		\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  
+		\smallskip
+		\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  
+		\smallskip
+		\includegraphics[width=7cm]{figures/SCEvar_hist.png}  
+		\end{subfigure}
 		\caption{Distribution of Mean Forecast and Uncertainty }
@@
 	\begin{figure}[ht]
+		\begin{subfigure}[b]{0.5\textwidth}
 		\centering
 		\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
-		\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  \\
 		\smallskip
 		\includegraphics[width=7cm]{figures/PRCPCEMean01_rv_true_hist.png} 
-		\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png}  \\
+		\end{subfigure}
+		   \hfill 
+		\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  
+		\smallskip
+		\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png} 
+		\end{subfigure}
 		\caption{Distribution of Revision in Forecasts and Uncertainty}
@@
 		\centering
-		\includegraphics[width=12cm]{figures/inf_shocksQ.png}
+		\includegraphics[width=0.7\textwidth]{figures/inf_shocksQ.png}
+			\begin{flushleft}
+			{\footnotesize Note: all the shocks are normalized by their sample standard deviation.
+Technology shock is idetified by long-run restriction of structural VAR with labor productivity, hours and inflation.
+Oil shock is defined as the max \{0, the largest increase of oil price over the past 12 months.\} }
+		\end{flushleft}
 		\caption{ Shocks to Inflation}
@@
 		\centering
-		\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
-		\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_before2007.png} \\
-		\smallskip
-		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
-		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_before2007.png} \\
-		\smallskip
-		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
-		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
+		\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=7cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
+				\smallskip
+			\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
+					\smallskip
+				\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
+		\end{subfigure}	
+	    \hfill 
+	    \begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=7cm]{figures/CPIAU_ashocks_before2007.png} 
+		\smallskip
+		\includegraphics[width=7cm]{figures/SPFFE_ashocks_before2007.png} 
+		\smallskip
+		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
+	\end{subfigure}
 		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}

### 2019-07-01 paper/Draft.tex
Revised formatting of figures

@@
 
-	In Figure \ref{Inflationshocks}, all four shocks are plotted in quarterly between 1985-2019. All shocks are normalized by its respective sample standard deviations.
+	In Figure \ref{Inflationshocks}, all four shocks are plotted in quarterly between 1985-2019 and normalized by its respective sample standard deviations.
 
@@
 \begin{figure}[ht]
-		\centering
 	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\caption{Technology and Oil Shocks}
 		\includegraphics[width=7cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
@@
 	\end{subfigure}
+	\hspace{1em}
 	\hfill
 	\begin{subfigure}[b]{0.5\textwidth}
+		\caption{Monetary Policy Shocks}
 		\includegraphics[width=7cm]{figures/CPIAU_ashocks_before2007.png} 
@@
 		\begin{figure}[ht]
-		\centering
+		\begin{subfigure}[b]{0.5\textwidth}
+			\centering
+			\caption{Technology and Oil Shocks}
 			\includegraphics[width=7cm]{figures/Inf_ashocks_nmp.png}  
-		\includegraphics[width=7cm]{figures/Inf_ashocks.png} \\
 			\smallskip
 			\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp.png} 
-		\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} \\
 			\smallskip 
 			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
-		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} \\
 			\smallskip 
 			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks_nmp.png} 
+		\end{subfigure}
+		\hfill
+		\hspace{1em}
+		\begin{subfigure}[b]{0.5\textwidth}
+			\caption{Monetary Policy Shocks}
+			\includegraphics[width=7cm]{figures/Inf_ashocks.png} 
+			\smallskip
+			\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} 
+			\smallskip
+			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} 
+			\smallskip
 			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks.png} 
+		\end{subfigure} 
 		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
@@
 	\begin{figure}[ht]
-		\centering
+
+		\begin{subfigure}[b]{0.35\textwidth}
+			\centering
+			\caption{Technology Shocks}
 			\includegraphics[width=4.5cm,height=3.5cm]{figures/CPIAU_ashocks_nmpM.png}
-		\includegraphics[width=9cm,height=3.5cm]{figures/CPIAU_ashocksM.png} \\
 			\smallskip
 			\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEFE_ashocks_nmpM.png} 
-		\includegraphics[width=9cm,height=3.5cm]{figures/SCEFE_ashocksM.png} \\
 			\smallskip
 			\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEDisg_ab_ashocks_nmpM.png}
-		\includegraphics[width=9cm,height=3.5cm]{figures/SCEDisg_ab_ashocksM.png} \\
 			\smallskip
 			\includegraphics[width=4.5cm,height=3.5cm]{figures/SCEVar_ab_ashocks_nmpM.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.65\textwidth}
+			\centering
+			\caption{Monetary Policy Shocks}
+			\includegraphics[width=9cm,height=3.5cm]{figures/CPIAU_ashocksM.png} 
+			\smallskip
+			\includegraphics[width=9cm,height=3.5cm]{figures/SCEFE_ashocksM.png} 
+			\smallskip
+			\includegraphics[width=9cm,height=3.5cm]{figures/SCEDisg_ab_ashocksM.png} 
+			\smallskip 
 			\includegraphics[width=9cm,height=3.5cm]{figures/SCEVar_ab_ashocksM.png} 
+		\end{subfigure}
 		\caption{ Responses of Inflation and Household Forecast Moments: 2013-2019}

### 2019-07-02 paper/Draft.tex
Created a new version of slides for Draft results. Working on it.

@@
 %opening
-\title{Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households}
+\title{Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households}
 \author{Tao Wang}
@@
 	\begin{abstract}
-		Surveys on density forecasts of macroeconomic variable that are not available until recent provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
+		Surveys on density forecasts of macroeconomic variable that are not availables until recently provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
 This paper first documents the persistent dispersion in uncertainty about future inflation as well as other stylized facts across economists and households.
@@
 	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade.
-This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.
+This has been also accompanied by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.
 On one hand, various theories built upon different micro foundations produce somewhat similar macro patterns.
@@
 Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models.
-In the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.
+In the same time, the degree of rigidity appears to be shock-specific and bears the difference between households and professional forecasters.
 
@@
 Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency.
-Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely looked by the literature, such as forecast errors and disagreements provide many insights as to how the agents expectation actually work.
+Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely examined by the literature, such as forecast errors and disagreements provide many insights as to how the agents expectation actually work.
 
@@
 	\begin{eqnarray}\label{AR_process}
-		y_{t+1} = \rho y_t + \omega_t
+		y_{t} = \rho y_{t-1} + \omega_t
 	\end{eqnarray}
@@
 
-	Researchers have also conjectured (in spite of limited evidence) that salient items such as gasoline price plays an important role in affecting household inflation expectation.
+	Researchers have also conjectured (in spite of limited evidence) that salient items such as gasoline price plays an important role in affecting household inflation expectations.
 The evidence presented here seems to be consistent with such a prediction.
@@
 			\centering
-			\caption{Technology Shocks}
+			\caption{Oil Shocks}
 			\includegraphics[width=4.5cm,height=3.5cm]{figures/CPIAU_ashocks_nmpM.png}

### 2019-07-02 slides/ExpSlidesAfterDraft.tex
Created a new version of slides for Draft results. Working on it.

--- 2019-06-17 slides/ExpSlides.tex
@@
 \usepackage{adjustbox}  % Allows for fitting tables into slide
+
+\usepackage{threeparttable}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 %\usetheme{boxes}
-\usetheme{CambridgeUS}
+%\usetheme{CambridgeUS}
 %\usetheme{Copenhagen}
@@
 %\usetheme{Madrid}
-%\usetheme{Malmoe}
+\usetheme{Malmoe}
 %\usetheme{Marburg}
@@
 
-$$y_{t+1} = \rho y_t + \omega_t  $$ 
+$$y_{t} = \rho y_{t-1} + \omega_t  $$ 
 $$\omega_t \sim N(0,\sigma^2_{\omega})$$
@@
 	\item if $\rho =0$, no way to forecast at all
-	\item $\omega_t$ is i.i.d 
+	\item $\omega_t$ is i.i.d. (allowing for $\sigma^2$ to be time-varying) 
 \end{itemize}
@@
 
-\subsection{Sticky Expectation}
+\subsection{Sticky Expectation(SE)}
 
@@
 \begin{figure}
-	\includegraphics[scale=0.25]{figures/ir_indse} 
+	\includegraphics[scale=0.25]{figuresDraft/ir_indse} 
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[scale=0.25]{figures/ir_popse} 
+	\includegraphics[scale=0.25]{figuresDraft/ir_popse} 
 \end{figure}
@@
 
-\subsection{Other theories}
+\subsection{Noisy Information(NI)}
 
@@
 \begin{figure}
-	\includegraphics[height=6.3cm,width=10cm]{figures/ir_indseni} 
+	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_indseni} 
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[height=6.3cm,width=10cm]{figures/ir_popseni} 
+	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_popseni} 
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[height=8cm,width=8cm]{figures/ni_illustration} 
+	\includegraphics[height=8cm,width=8cm]{figuresDraft/ni_illustration} 
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[height=5cm,width=8cm]{figures/rigidity} 
+	\includegraphics[height=5cm,width=8cm]{figuresDraft/rigidity} 
 \end{figure}
@@
 
-\begin{frame}{Population moments: average}
+\begin{frame}{Uncertainty and Realized Inflation}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_med.png} 
+	\centering
+\label{InfVar}
+\includegraphics[width=0.33\textwidth]{figuresDraft/Inf1yf_CPIAU_varSCEM.png}
+\includegraphics[width=0.33\textwidth]{figuresDraft/Inf1yf_CPIAU_varSPFCPIQ.png}
+\includegraphics[width=0.33\textwidth]{figuresDraft/Inf1yf_PCE_varSPFPCEQ.png}
 \end{figure}
@@
 
-\begin{frame}{Population moments: average forecast errors}
+\begin{frame}{Uncertainty and Forecast Errors}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/fe_fe.png} 
+	\centering
+	\label{FEVar}
+	\includegraphics[width=0.33\textwidth]{figuresDraft/SPFCPI_FE_varSPFCPIQ.png}
+\includegraphics[width=0.33\textwidth]{figuresDraft/SPFPCE_FE_varSPFPCEQ.png}
+\includegraphics[width=0.33\textwidth]{figuresDraft/SCE_FE_varSCEM.png}
 \end{figure}
@@
 
-\begin{frame}{Population moments: average uncertainty}
+\begin{frame}{Uncertainty and Disagreements}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_var.png} 
+	\centering
+\label{DisgVar}
+\includegraphics[width=0.33\textwidth]{figuresDraft/CPI_disg_varSPFCPIQ.png}
+\includegraphics[width=0.33\textwidth]{figuresDraft/PCE_disg_varSPFPCEQ.png}
+\includegraphics[width=0.33\textwidth]{figuresDraft/Q9_disg_varSCEM.png}
 \end{figure}
@@
 
-\begin{frame}{Population moments: average uncertainty}
+\begin{frame}{Dispersion of Mean Forecast}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/var_var.png} 
+	\includegraphics[width=0.33\textwidth]{figuresDraft/IQRmeanCPIQ.png} 
+\smallskip
+\includegraphics[width=0.33\textwidth]{figuresDraft/IQRmeanPCEQ.png}
+\smallskip
+\includegraphics[width=0.33\textwidth]{figuresDraft/IQRmeanSCEM.png}
 \end{figure}
@@
 
-\begin{frame}{Population moments: disagreements}
+\begin{frame}{Dispersion of Uncertainty}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_disg.png} 
+	\label{IQR_Unceratitny}
+	\includegraphics[width=0.33\textwidth]{figuresDraft/IQRvarCPIQ.png}
+\smallskip
+\includegraphics[width=0.33\textwidth]{figuresDraft/IQRvarPCEQ.png}
+\smallskip
+\includegraphics[width=0.33\textwidth]{figuresDraft/IQRvarSCEM.png}
 \end{figure}
@@
 
-\begin{frame}{Population moments: disagreements}
+\begin{frame}{Distribution of Uncertainty}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_disg.png} 
+		\label{Unceratitny_Histogram}
+	\includegraphics[width=0.33\textwidth]{figuresDraft/PRCCPIVar1_hist.png}  
+\smallskip
+\includegraphics[width=0.33\textwidth]{figuresDraft/PRCPCEVar1_hist.png}  
+\smallskip
+\includegraphics[width=0.33\textwidth]{figuresDraft/SCEvar_hist.png}  
 \end{figure}
@@
 
-\begin{frame}{Population moments: disagreements}
+\begin{frame}{Distribution of Revision in Forecast}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/disg_disg.png} 
+	\includegraphics[width=0.5\textwidth]{figuresDraft/PRCCPIMean01_rv_true_hist.png} 
+\includegraphics[width=0.5\textwidth]{figuresDraft/PRCPCEMean01_rv_true_hist.png} 
 \end{figure}
@@
 
-\begin{frame}{Population moments: uncertainty and disagreements}
+\begin{frame}{Distribution of Revision in Uncertainty}
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/var_disg.png} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Population moments: uncertainty and disagreements}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/var_disg2.png} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Population moments: forecast and realization}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_true.png} 
+	\includegraphics[width=0.5\textwidth]{figuresDraft/PRCCPIVar01_rv_true_hist.png}  
+\includegraphics[width=0.5\textwidth]{figuresDraft/PRCPCEVar01_rv_true_hist.png} 
 \end{figure}
@@
 
-\begin{frame}{Test of Rational Expectation}
-\begin{table}[tbhp] \centering \adjustbox{max height=\dimexpr\textheight-5.5cm\relax, max width=\textwidth}{
-	\begin{tabular}{lllllll}
+\begin{frame}{Tests of rationality using forecast errors}
+	\begin{adjustbox}{totalheight=0.9\textheight}
+	\label{NullTestTable}
+	\centering 
+	\begin{tabular}{llll}
 		\hline 
-		& SPFCPI\_FElvl       & SPFPCE\_FElvl & SPFCPI\_Vardiff & SPFPCE\_Vardiff & SPFCPI\_Disgdiff & SPFPCE\_Disgdiff            \\
+		& SPF CPI          & SPF PCE          & SCE            \\
 		\hline 
-		L.InfExp\_FE        & 0.941***      & 1.195***        &                 &                  &                  &           \\
-		& (0.0840)      & (0.142)         &                 &                  &                  &           \\
-		L2.InfExp\_FE       & -0.313**      & -0.625**        &                 &                  &                  &           \\
-		& (0.116)       & (0.198)         &                 &                  &                  &           \\
-		L3.InfExp\_FE       & 0.114         & 0.0782          &                 &                  &                  &           \\
-		& (0.114)       & (0.196)         &                 &                  &                  &           \\
-		L4.InfExp\_FE       & -0.137        & -0.0162         &                 &                  &                  &           \\
-		& (0.0820)      & (0.131)         &                 &                  &                  &           \\
-		L.InfExp\_Var\_ch   &               &                 & -0.855***       & -0.565**         &                  &           \\
-		&               &                 & (0.189)         & (0.162)          &                  &           \\
-		L2.InfExp\_Var\_ch  &               &                 & -0.780**        & -0.452*          &                  &           \\
-		&               &                 & (0.220)         & (0.186)          &                  &           \\
-		L3.InfExp\_Var\_ch  &               &                 & -0.556*         & -0.429*          &                  &           \\
-		&               &                 & (0.219)         & (0.189)          &                  &           \\
-		L4.InfExp\_Var\_ch  &               &                 & -0.167          & 0.00385          &                  &           \\
-		&               &                 & (0.188)         & (0.172)          &                  &           \\
-		L.InfExp\_Disg\_ch  &               &                 &                 &                  & -0.571***        & -0.640*** \\
-		&               &                 &                 &                  & (0.0699)         & (0.127)   \\
-		L2.InfExp\_Disg\_ch &               &                 &                 &                  & -0.376***        & -0.0944   \\
-		&               &                 &                 &                  & (0.0764)         & (0.141)   \\
-		L3.InfExp\_Disg\_ch &               &                 &                 &                  & -0.0455          & 0.180     \\
-		&               &                 &                 &                  & (0.0661)         & (0.138)   \\
-		L4.InfExp\_Disg\_ch &               &                 &                 &                  & -0.110*          & -0.0364   \\
-		&               &                 &                 &                  & (0.0479)         & (0.123)   \\
+		\multicolumn{4}{l}{Test 1: Unbiasedness}                                                           \\
 		\hline 
-		N                   & 143           & 41              & 44              & 44               & 146              & 44        \\
-		R-sq                & 0.593         & 0.750           & 0.384           & 0.322            & 0.356            & 0.496    \\
+		Constant                            & 0.122***         & 0.586***         & 2.220***       \\
+		& (0.017)          & (0.061)          & (0.019)        \\
+		\hline 
+		N                                   & 4697             & 1208             & 67380          \\
+		\hline 
+		\multicolumn{4}{l}{Test 2: FE does not depend on past information}                                  \\
+		\hline 
+		Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
+		& (0.020)          & (0.061)          & NA             \\
+		Constant                            & -0.655***        & -0.777***        & NA             \\
+		& (0.060)          & (0.116)          & NA             \\
+		\hline 
+		N                                   & 3429             & 1208             & NA             \\
+		$R^2$                 & 0.0721           & 0.118            & NA             \\
+		\hline 
+		\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons not serially correlated} \\
+		\hline 
+		Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
+		& (0.020)          & (0.035)          & NA             \\
+		Constant                            & 0.145***         & 0.275***         & NA             \\
+		& (0.021)          & (0.035)          & NA             \\
+		\hline 
+		N                                   & 3356             & 1208             & NA             \\
+		$R^2$                   & 0.00591          & 0.00264          & NA             \\
+		\hline 
+		\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
+		\hline 
+		Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
+		& (0.025)          & (0.037)          & (0.021)        \\
+		Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
+		& (0.027)          & (0.048)          & (0.046)        \\
+		Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
+		& (0.025)          & (0.038)          & (0.045)        \\
+		Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
+		& (0.019)          & (0.026)          & (0.097)        \\
+		\hline 
+		N                                   & 2536             & 1004             & 2836           \\
+		$R^2$                & 0.439            & 0.552            & 0.232    \\
 		\hline      
 	\end{tabular}
-}
-\end{table}
+\end{adjustbox}
+
 \end{frame}
 
-\begin{frame}{Identified Inflation shocks}
+\begin{frame}{Test of revision efficiency Using mean revisions}
+
+	\begin{adjustbox}{width=0.9\textwidth}
+	\begin{threeparttable}
+		\label{RevEfficiency}
+		\begin{tabular}{lllllllll}
+			\hline 
+			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
+			\hline 
+			\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
+			\hline 
+			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
+			\hline 
+			L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
+			&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
+			L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
+			&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
+			L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
+			&               &           &          & (0.048)  &               &           &           & (0.069)   \\
+			SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
+			&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
+			SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
+			&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
+			& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
+			Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
+			\hline 
+			N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
+			$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
+			\hline 
+		\end{tabular} 
+		\begin{tablenotes}
+			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
+		\end{tablenotes}
+	\end{threeparttable}
+\end{adjustbox}
+
+\end{frame}
+
+\begin{frame}{Test of revision efficiency using uncertainty revisions}
+
+\begin{adjustbox}{width=0.9\textwidth}
+	\begin{threeparttable}
+		\label{RevEfficiency}
+		\begin{tabular}{lllllllll}
+			\hline 
+			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
+			\hline 
+			\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
+			\hline 
+			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
+			\hline 
+			L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
+			&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
+			L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
+			&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
+			L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
+			&               &           &          & (0.121)  &               &           &           & (0.149)   \\
+			Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
+			& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
+			\hline 
+			N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
+			$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
+			\hline 
+		\end{tabular} 
+		\begin{tablenotes}
+			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
+		\end{tablenotes}
+	\end{threeparttable}
+\end{adjustbox}
+
+\end{frame}
+
+\begin{frame}{Weak tests of efficiency using changes in forecasts }
+
+	\begin{adjustbox}{width=\textwidth}
+	\begin{threeparttable}
+		\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
+		\label{WeakRevEfficiency}
+		\begin{tabular}{llllllllllllll}
+			\hline 
+			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
+			\hline 
+			\multicolumn{14}{l}{Test 3.
+Weak revision efficiency of change in forecast}                                                                                                                                    \\
+			\hline 
+			& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
+			\hline 
+			L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
+			&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\
+
+			L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Mean\_ch &         &           & -0.336*** & -0.439*** \\
+
+			&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                                   &         &           & (0.018)    & (0.031)    \\
+			L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Mean\_ch &         &           & -0.143*** & -0.270*** \\
+
+			&             &           &           & (0.032)   &               &           &           & (0.036)   &                                &         &           & (0.012)    & (0.027)    \\
+
+			&             &           &           &           &               &           &           &           & L4.InfExp\_Mean\_ch &         &           &           & -0.183*** \\
+
+			&             &           &           &           &               &           &           &           &                                 &         &           &           & (0.027)    \\
+			&             &           &           &           &               &           &           &           & L5.InfExp\_Mean\_ch &         &           &           & -0.096*** \\
+			&             &           &           &           &               &           &           &           &                      &         &           &           & (0.021)    \\
+			&             &           &           &           &               &           &           &           & L6.InfExp\_Mean\_ch &         &           &           & -0.044**  \\
+			&             &           &           &           &               &           &           &           &                                     &         &           &           & (0.013)    \\
+			Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant              & -0.055* & -0.034    & -0.001    & -0.002    \\
+			& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                                 & -0.023  & -0.023    & -0.028    & -0.033    \\
+			\hline 
+			N                    & 1636        & 1430      & 1266      & 1141      & 1402          & 1190      & 1022      & 898       & N                   & 53016   & 43166     & 28850     & 14445     \\
+			$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ &  0.000       & 0.202     & 0.273     & 0.306   \\
+			\hline 
+		\end{tabular}
+		\begin{tablenotes}
+			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
+		\end{tablenotes}
+	\end{threeparttable}
+\end{adjustbox}
+\end{frame}
+
+\begin{frame}{Weak Tests of Efficiency using changes in uncertainty}
+\begin{adjustbox}{width=\textwidth}
+	\begin{threeparttable}
+				\label{WeakRevEfficiency}
+		\begin{tabular}{llllllllllllll}
+			\hline 
+			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
+			\hline 
+			\multicolumn{14}{l}{Test 4. Weak revision efficiency of change in uncertainty}                \\
+			\hline                                                                                                                 
+			& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean change   & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean change   & t-1       & t-1- t-2  & t-1-t-3   \\
+			\hline 
+			L.InfExp\_Var\_ch    &             & -0.393**  & -0.568*** & -0.543**  &               & -0.444*** & -0.602*** & -0.658*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
+			&             & (0.136)   & (0.146)   & (0.177)   &               & (0.094)   & (0.127)   & (0.145)   &                      &               & -0.015    & -0.022    & -0.037    \\
+			L2.InfExp\_Var\_ch   &             &           & -0.322**  & -0.278*   &               &           & -0.289*   & -0.404**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
+			&             &           & (0.104)   & (0.132)   &               &           & (0.110)   & (0.137)   &                      &               &           & -0.021    & -0.031    \\
+			L3.InfExp\_Var\_ch   &             &           &           & 0.048     &               &           &           & -0.292    & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\
+			&             &           &           & (0.096)   &               &           &           & (0.154)   &                      &               &           & -0.012    & -0.027    \\
+			&             &           &           &           &               &           &           &           & L4.InfExp\_Var\_ch   &               &           &           & -0.130*** \\
+			&             &           &           &           &               &           &           &           &                      &               &           &           & -0.025    \\
+			&             &           &           &           &               &           &           &           & L5.InfExp\_Var\_ch   &               &           &           & -0.058**  \\
+			&             &           &           &           &               &           &           &           &                      &               &           &           & -0.018    \\
+			&             &           &           &           &               &           &           &           & L6.InfExp\_Var\_ch   &               &           &           & -0.025    \\
+			&             &           &           &           &               &           &           &           &                      &               &           &           & -0.012    \\
+			Constant               & -0.002      & -0.001    & 0.004     & 0.004     & 0.000         & 0.002     & 0.004     & 0.005     &   Constant                   & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
+			& (0.005)     & (0.005)   & (0.004)   & (0.004)   & (0.004)       & (0.004)   & (0.004)   & (0.004)   &                      & -0.123        & -0.11     & -0.104    & -0.163    \\
+			\hline 
+			N                    & 1202        & 950       & 765       & 625       & 1078          & 842       & 657       & 519       &                      & 53016         & 43166     & 28850     & 14445     \\
+			$R^2$ & 0.000       & 0.120     & 0.265     & 0.242     & 0.000         & 0.233     & 0.321     & 0.385     &                      & 0             & 0.182     & 0.278     & 0.321  \\
+			\hline    
+		\end{tabular}
+		\begin{tablenotes}
+			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
+		\end{tablenotes}
+	\end{threeparttable}
+\end{adjustbox}
+\end{frame}
+
+\subsection{Shock-Based Rigidity}
+
+\begin{frame}{Inflation shocks}
 
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/inf_shocksQ.png} 
+	\includegraphics[width=0.8\textwidth]{figuresDraft/inf_shocksQ.png} 
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/RigidityJPEFigure2.png} 
+	\includegraphics[width=0.9\textwidth]{figuresDraft/RigidityJPEFigure2.png} 
 \end{figure}
@@
 
-\begin{frame}{Inflation IR to  shocks}
+\begin{frame}{Technology and oil shocks: 1984-2007}
 
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/CPIAU_ashocks.png} 
+	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_nmp_before2007.png}  \\ 
+\smallskip
+\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_nmp_before2007.png} \\
+\smallskip
+\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_nmp_before2007.png} 
 \end{figure}
@@
 
-\begin{frame}{Inflation IR to  shocks}
+\begin{frame}{Monetary policy shocks: 1984-2007}
 
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/PCEPI_ashocks.png} 
+	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_before2007.png}  \\
+	\smallskip 
+	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_before2007.png} \\
+	\smallskip
+	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_before2007.png} 
 \end{figure}
@@
 
-\subsection{Professional forecasters as a baseline }
-
-\begin{frame}{Forecasting errors IR to  shocks}
+\begin{frame}{Technology and oil shocks: 1984-2019}
 
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFFE_ashocks.png} 
+	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks.png} 
+	\smallskip
+	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks.png} \\
+	\smallskip
+	\includegraphics[width=7cm]{figuresDraft/SPFDisg_ab_ashocks.png} 
+	\smallskip
+	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks.png}  
 \end{figure}
@@
 
-\begin{frame}{Disagreements IR to  shocks}
+\begin{frame}{Monetary policy shocks: 1984-2019}
 
 \begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks.png} 
-\end{figure}
+	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks_nmp.png}
 
-\end{frame}
-
-\begin{frame}{Uncertainty IR to shocks}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFVar_ashocks.png} 
+	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks_nmp.png}  \\
+	\smallskip 
+	\includegraphics[width=7cm]{figuresDratf/SPFDisg_ab_ashocks_nmp.png} 
+	\smallskip 
+	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks_nmp.png}  
 \end{figure}

### 2019-07-02 paper/Draft.tex
small changes to the draft

@@
 	I follow \citet{engelberg2009comparing} to estimate the density distribution of each individual surveyee for SPF.
-\footnote{For the answers with positive probabilities assigned to three bins, the approach fits the the histogram with a generalized beta distribution.
+\footnote{Answers with positive probabilities assigned to three bins is fit with a generalized beta distribution.
+Depending on if there is open-ended bin on either side with positive probability, 2-parameters or 4-parameters of the beta distribution are estimated.
 For those with only two bins with positive probabilities and adjacent, it is fit with a triangular distribution.
@@
 All the results in this paper are robust to a different threshold such as 10 and 1 percentile.
-\footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}
+\footnote{For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}
 

### 2019-07-03 paper/Draft.tex
Made two corrections.

@@
 			Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
-			Uncertainty: $\sigma^2_{i,t+h|t}$         & Average uncertainty:  $\bar \sigma^2_{i,t+h|t}$ \\
+			Uncertainty: $\sigma^2_{i,t+h|t}$         & Average uncertainty:  $\bar \sigma^2_{t+h|t}$ \\
 			& Disagreements:  $\overline{Disg}_{t+h|t}$       \\
@@
 			\label{InfVar}
-			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
 			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
 			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCE_varSPFPCEQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
 		\end{subfigure}

### 2019-07-03 slides/ExpSlidesAfterDraft.tex
Made two corrections.

@@
 \usepackage{adjustbox}  % Allows for fitting tables into slide
-
+\usepackage{hyperref}
 \usepackage{threeparttable}
 \usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{subcaption}
+\usepackage{natbib}
 
@@
 
-\title{Understanding Expectation Formation from Probabilistic Surveys}
+\title{Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households}
 
@@
 
-\begin{frame}{What I am doing}
+\begin{frame}{What this paper does?}
 \begin{itemize}
-	\item Use \textcolor{blue}{density information} to 
+	\item Use \textcolor{blue}{uncertainty} from density forecasts to 
 	\begin{itemize}
-		\item test expectation rigidity models 
+		\item test models of expectation rigidity 
 		\item ... and identify differences in various theories 
@@
 %	\begin{itemize}
-%		\item Actually carefully designed. \cite{armantier2017overview}
+%		\item Actually carefully designed. \citet{armantier2017overview}
 %	\end{itemize}
@@
 %	\begin{itemize}
-%		\item Not that bad. \cite{manski2004measuring}, \cite{delavande2014probabilistic}
+%		\item Not that bad. \citet{manski2004measuring}, \citet{delavande2014probabilistic}
 %		\item Better than not.
@@
 \begin{itemize}
-	\item \textbf{Theory}
-	\begin{itemize}
-		\item Sticky expectation \cite{carroll2003macroeconomic}, \cite{reis2006inattentive}
-		\item Rational inattention \cite{sims2003implications},  \cite{gabaix2014sparsity}
-		\item Noisy information \cite{lucas1972expectations}, \cite{woodford2001imperfect}
-	\item Learning \cite{evans2012learning}
-	\item Strategic interaction \cite{morris2002social}, \cite{hellwig2009knowing}
-	\item Diagostic expectation  \cite{bordalo2018diagnostic}
-	\item Model uncertainty \cite{hansen2001robust}, \cite{hansen2008robustness}
+	\item \textbf{Testing theories of expectation formation}
+	\item \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. 
+	\item  \citet{coibion2018firms} 
+	\item  \citet{malmendier2015learning}, \citet{das2017socioeconomic}
+	\item \textcolor{blue}{\citet{coibion2012can} and \citet{fuhrer2018intrinsic}}
 \end{itemize}
-\item \textbf{Empirics}
-\begin{itemize}
-	\item \textbf{Heterogeneity in Expectation:} \cite{mankiw2003disagreement}
-	\item \textbf{Testing Theories:}  \textcolor{blue}{\cite{coibion2012can}, \cite{fuhrer2018intrinsic}}
-\end{itemize}
-\end{itemize}
+
 \end{frame}
@@
 \begin{eqnarray*}
-	\widehat f_{i,t}(y_{t+h}|I_{i,t})
+	f_{i,t+h|t} \equiv f_{i,t}(y_{t+h}|I_{i,t})
 \end{eqnarray*}
@@
 	\item Theories differ in $I_{i,t}$
-	\item May also differ on information processing, i.e. $I_{i,t} \rightarrow \widehat f_{i,t}$
+	\item May also differ on information processing, i.e. $I_{i,t} \rightarrow f_{i,t+h|t}$, i.e. heterogeneous models and priors. \citet{patton2010forecasters}.
 \end{itemize}
@@
 \begin{frame}{Definition and notation}
-\begin{itemize}
-	\item \textcolor{red}{Individual}
-	\begin{itemize}
-		\item  mean forecast $\quad E_{i,t}(y_{t+h})$
-		\item forecast error $\quad FE_{i,t+h|t} = y_{t+h}- E_{i,t}(y_{t+h})$
-		\item \textcolor{blue}{uncertainty} $\quad Var_{i,t}(y_{t+h})$
-	\end{itemize}
-	\item \textcolor{red}{Population}
-	\begin{itemize}
-		\item average forecast  $\quad \bar E_{t}(y_{t+h})$
-		\item average forecast error $\quad \overline {FE}_{t}= y_{t+h}-\bar E_{t}(y_{t+h})$
-		\item \textcolor{blue}{cross-section disagreements}  $\quad Var_t(E_{i,t}(y_{t+h}))$
-		\item \textcolor{blue}{average uncertainty}  $\quad \overline{Var}_t(y_{t+h})$
-	\end{itemize}
-\end{itemize}
+	\begin{table}[ht]
+	\centering
+	\caption{Definition and Notation of Moments}
+	\label{MomSum}
+	\begin{tabular}{ll}
+
+		\hline 
+		Individual Moments                                  & Population Moments                             \\
+		\hline 
+		Mean forecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
+		Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
+		Uncertainty: $\sigma^2_{i,t+h|t}$         & Average uncertainty:  $\bar \sigma^2_{i,t+h|t}$ \\
+		& Disagreements:  $\overline{Disg}_{t+h|t}$       \\
+		\hline 
+	\end{tabular}
+\end{table}
 
@@
 
+\subsection{Full-information Rational Expectation(FIRE)}
+
+\begin{frame}{Full-information rational expectation: assumptions}
+\begin{itemize}
+	\item $y_t$ is perfectly observed in each period
+	\item All agents understand and agree on the process 
+\end{itemize}
+\end{frame}
+
+\begin{frame}{FIRE: predictions}
+\begin{itemize}
+	\item  $$\overline{FE}^{*}_{i,t+h|t} = \sum^{h}_{k=1} \rho^k \omega_{t+k}$$
+	\item  $$\bar \sigma^{*2}_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
+	\item 	
+	$$\bar \sigma^{*2}_{t+h|t+1} - \bar \sigma^{*2}_{t+h|t}  =  \rho (\bar \sigma^{*2}_{t+h|t} - \bar \sigma^{*2}_{t+h|t-1})$$
+\end{itemize}
+\end{frame}
+
 \subsection{Sticky Expectation(SE)}
@@
 	\item A non-updater since $t-\tau$  
-	$$E_{i,t}(y_{t+h}|y_{t-\tau}) =\rho^{h+\tau} y_{t-\tau} $$
-	\item An updater is a special cae  $\tau=0$ 
+	$$y_{i,t+h|t-\tau}=\rho^{h+\tau} y_{t-\tau} $$
+	\item An updater is a special case  $\tau=0$ 
 \end{itemize}
-\end{frame}
-
-\begin{frame}{Impulse responses to shocks: individual moments}
-
-$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
-$$\textrm{SE} \quad \quad  \lambda = 0.4 $$ 
-\begin{figure}
-	\includegraphics[scale=0.25]{figuresDraft/ir_indse} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Impulse responses to shocks: population moments}
-
-$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
-$$\textrm{SE} \quad \quad  \lambda = 0.4 $$
-
-\begin{figure}
-	\includegraphics[scale=0.25]{figuresDraft/ir_popse} 
-\end{figure}
-
 \end{frame}
@@
 
+\begin{frame}{An illustration of noisy information}
+
+\begin{figure}
+	\includegraphics[height=0.8\textheight,width=\textwidth]{figuresDraft/ni_illustration} 
+\end{figure}
+
+\end{frame}
+
 \begin{frame}{Impulse responses to shocks: individual moments}
 
-$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
-$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$
+$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 1, \quad \omega_t = 1$$
+$$ \textrm{SE:} \quad  \lambda = 0.25; \quad \textrm{NI:} \quad \sigma_\xi =  \sigma_\epsilon = \sigma_y$$
 
 \begin{figure}
-	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_indseni} 
+	\includegraphics[height=0.6\textheight,width=\textwidth]{figuresDraft/ir_indseni} 
 \end{figure}
@@
 
-$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
-$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$
+$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 1, \quad \omega_t = 1$$
+$$ \textrm{SE:} \quad  \lambda = 0.25; \quad \textrm{NI:} \quad \sigma_\xi =  \sigma_\epsilon = \sigma_y$$
 
 \begin{figure}
-	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_popseni} 
+	\includegraphics[height=0.6\textheight,width=\textwidth]{figuresDraft/ir_popseni} 
 \end{figure}
@@
 
-\begin{frame}{A detailed look into noisy information}
-
-\begin{figure}
-	\includegraphics[height=8cm,width=8cm]{figuresDraft/ni_illustration} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Implied rigidity of different models}
+\begin{frame}{Comparing FIRE, SE and NI}
 
@@
 \begin{itemize}
-	\item\cite{coibion2012can}
+	\item \citet{coibion2012can}
 	\begin{itemize}
@@
 
-\item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
- \item \textbf{Identification of Shocks}: following \cite{coibion2012can} and monetary policy shocks. 
+\item \textbf{Density Estimation}: generalized beta estimation, \citet{engelberg2009comparing}
+ \item \textbf{Identification of Shocks}: following \citet{coibion2012can} and monetary policy shocks. 
 \end{itemize}
@@
 	\begin{threeparttable}
-		\label{RevEfficiency}
+		\label{MeanRevEfficiency}
 		\begin{tabular}{lllllllll}
@@
 	\begin{threeparttable}
-		\label{RevEfficiency}
+		\label{VarRevEfficiency}
 		\begin{tabular}{lllllllll}
@@
 		\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
-		\label{WeakRevEfficiency}
+		\label{MeanWeakRevEfficiency}
 		\begin{tabular}{llllllllllllll}
@@
 	\begin{threeparttable}
-				\label{WeakRevEfficiency}
+				\label{VarWeakRevEfficiency}
 		\begin{tabular}{llllllllllllll}
@@
 
-\begin{frame}{Results from \cite{coibion2012can}}
+\begin{frame}{Results from \citet{coibion2012can}}
 
@@
 \end{figure}
-
 \end{frame}
@@
 \begin{figure}
-	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks.png} 
-	\smallskip
-	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks.png} \\
-	\smallskip
-	\includegraphics[width=7cm]{figuresDraft/SPFDisg_ab_ashocks.png} 
-	\smallskip
-	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks.png}  
+	\includegraphics[width=0.6\textwidth,totalheight=\0.4\textheight]{figuresDraft/Inf_ashocks_nmp.png}  
+	\includegraphics[[width=0.6\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFFE_ashocks_nmp.png}  \\
+	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFDisg_ab_ashocks_nmp.png} 
+	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFVar_ab_ashocks_nmp.png}  
 \end{figure}
-
 \end{frame}
@@
 \begin{figure}
-	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks_nmp.png}
-
-	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks_nmp.png}  \\
+	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/Inf_ashocks.png} 
 	\smallskip
-	\includegraphics[width=7cm]{figuresDratf/SPFDisg_ab_ashocks_nmp.png} 
+	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFFE_ashocks.png} \\
 	\smallskip
-	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks_nmp.png}  
+	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFDisg_ab_ashocks.png} 
+	\smallskip
+	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFVar_ab_ashocks.png}  
 \end{figure}

### 2019-07-06 paper/Draft.tex
font size change to 12pt
clarify the inflation measures. SPF core CPI and core PCE. SCE headline CPI.

@@
-\documentclass[]{article}
+\documentclass[12pt]{article}
 \usepackage{amsmath}
 \usepackage{adjustbox}
+\usepackage{tabularx}
 \usepackage{graphicx}
@@
 More recent examples include \citet{coibion2018firms} on firms' managers.
-In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics and macroeconomic history experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic},etc.).
+In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics, cognitive abilities and macroeconomic histories experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic} and \citet{d2019iq}, etc.).
 In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.
@@
 	Second, the literature that has been originally developed under the theme of forecast efficiency provides a framework analyzing the dynamics of uncertainty useful for the purpose of this paper.
-The focus of the forecasting efficiency literature is evaluating forecasters' performance and improving forecasting methodology, but it can be adapted into testing the context of understanding expectation formation of different types of agents.
+The focus of the forecasting efficiency literature is evaluating forecasters' performance and improving forecasting methodology, but it can be adapted to test the theories of expectation formation of different types of agents.
 This is especially relevant to this paper as I focus on the uncertainty.
@@
 		\includegraphics[width=13cm]{figures/ni_illustration.png}  \\
+		\begin{flushleft}
 		{\footnotesize Note: the top two figures plot the nowcasting of $y_{t+k}$  at time $t+k$ and forecasting of $y_{t+h}$ at time $t+k$  based on a Kalman filtering together with FIRE after a one-time shock of one unit at time $t$.
@@
 }
+		\end{flushleft}
 		\caption{Nowcasting and Forecasting in Noisy Information}
@@
 		\label{DataInfo}
-		\begin{tabular}{lll}
-
+		\begin{tabularx}{\textwidth}{|X|X|X|}
 			\hline 
@@
 			\hline 
-			Time period                                    & 2013-present                            & 2007-present             \\
+			Time period                                    & 2013-2019                           &
+			 2007-2019             \\
+			 \hline 
 			Frequency                                      & Monthly                                 & Quarterly                \\
+			\hline 
 			Sample Size                                    & 1,300                                   & 30-50                    \\
-			Aggregate Var in Density                       & 1-yr  and 3-yr ahead inflation          & 1-yr CPI and PCE         \\
-			Individual Var in Density                      & 1-yr earning growth                     & No                       \\
+			\hline 
+			Var in Density                       & 1-yr and 2-yr-ahead inflation          & 1-yr-ahead GDP deflator, Core CPI and Core PCE         \\
+			\hline 
 			Panel Structure                               & stay up to 12 months                    & average stay for 5 years \\
-			Demographic Info                        & Education, Income, Age, Location        & Industry    \\
-			\hline 
-		\end{tabular}
+			\hline 
+			Individual Info                        & Education, Income, Age, Location        & Industry    \\
+			\hline 
+		\end{tabularx}
 	\end{table}
 
-	Throughout the paper, I use two measures of inflation, headline CPI and PCE . The forecasts-based measures are computed and used correspondingly.
+	Throughout the paper, I use three measures of inflation: headline CPI, core CPI and core PCE .
+Depending on the specific variable of forecast in the survey series, the realization of the corresponding inflation is used to compute moments such as forecast errors.
+Specifically, SPF has density forecasts for both core CPI and core PCE \footnote{SPF also  has density forecasts for GDP deflator(for GNP prior to 1992:Q1) going back to 1968.
+Since the ranges of the values as we as the definition have not been consistent over time.
+I do not use it in this paper.}.
+For SCE, as the households responders are asked about the overall inflation, It is the most appropriate to be interpreted as  headline CPI inflation.
+To simplify the expression, from now on, core CPI and core PCE are simply referred to as CPI and PCE, respectively.
 

### 2019-07-06 paper/Draft.tex
updated stylized charts with fixed winsorization and new formatting. Also absolute values of FE instead of FE.

@@
 } and resonated by anecdotal narratives that high inflation is typically associated with high inflation uncertainty.
-However, the observable correlation of realized inflation and the directly estimated average uncertainty from both  forecasters and households are, if any, negative during the period between 2007-2019.
-In particular, the correlation coefficients are -0.1, -0.05 and -0.24 for SPF's  CPI forecast, SPF's PCE forecast and SCE's CPI expectation.
-This may suggest that during a period of persistently low inflation, the conventional positive redux of inflation and uncertainty is not a good description of the relation of the two.
-
-	The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between forecast error and uncertainty.
-Although according to our benchmark framework in \ref{theory}, there is no mathematical correlation between the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
-The correlation coefficients of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, respectively.
-Compared to professional forecasts, households forecasts exhibit such a positive correlation.
-
-	The last row of Figure \ref{UnceratitnyOtherMoments} explores the relationship between disagreement and uncertainty.
+However, the observable correlation of realized inflation and the directly estimated average uncertainty from both professionals and households are at most weakly positive during the period between 2007-2019.
+In particular, the correlation coefficients  0.14, -0.05 and -0.24 for SPF's CPI forecast, SPF's PCE forecast and SCE's CPI expectation.
+This may suggest that during a period of persistently low and stable inflation, the conventional positive redux of inflation and uncertainty is not a good description of the relation of the two.
+
+	The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between size of the forecast error and uncertainty.
+Although according to our benchmark framework in \ref{theory}, there is no mathematical correlation between the size of the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
+The correlation coefficients of the two are -0.19, -0.35 and 0.27 for SPF CPI forecasts, SPF PCE forecasts and SCE's forecasts, respectively.
+The two indicators turn out to be negatively correlated for professional forecasts.
+Only households forecasts exhibit such a positive correlation.
+
+	The last row of Figure \ref{UnceratitnyOtherMoments} examines the relationship between disagreement and uncertainty.
 Many empirical literatures in macroeconomics use disagreements and uncertainty as if they are similar concepts.
-Partly this confusion in practice is due to the difficulty of finding appropriate measures of uncertainty in the first place.
-But as we have presented in \ref{theory}, the two are distinct concepts.
+Such a confusion in practice is partly due to the difficulty of finding appropriate measures of uncertainty in the first place.
+But as we have presented in \ref{theory}, the two are concepts with distinct statistical definitions.
 The empirical pattern of the two,  as shown in the plots, also confirms that the two are different objects.
 The correlation coefficients of the two turn out to be negative, -0.29 and -0.46 for SPF forecasts.
-In stark contrast, households seem to bear a strong correlation of 0.62 between the two moments.
+In stark contrast, households seem to bear a strong correlation of 0.43 between the two moments.
 
@@
 			\label{InfVar}
-			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPICore_varSPFCPIQ.png}
 			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCE_varSPFPCEQ.png}
@@
 			\centering
-			\caption{Forecast Errors and Uncertainty}
+			\caption{Size of Forecast Errors and Uncertainty}
 			\label{FEVar}
-			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_FE_varSPFCPIQ.png}
-			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_FE_varSPFPCEQ.png}
-			\includegraphics[width=0.3\textwidth]{figures/SCE_FE_varSCEM.png}
+			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_abFE_varSPFCPIQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_abFE_varSPFPCEQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/SCE_abFE_varSCEM.png}
 		\end{subfigure}
@@
 			\centering
-			\caption{Disagreements and Uncertainty}
+			\caption{Disagreement and Uncertainty}
 			\label{DisgVar}
@@
 		\begin{flushleft}
-			{\footnotesize Note:  From left to right: SPF’s CPI, SPF’s PCE, and SCE’s CPI forecast.
-From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of -0.10, -0.05 and -0.24, respectively; uncertainty (red dash) versus forecast errors (blue dot) with correlation coefficient of 0.13, 0.06, 0.40, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.62.
-}
+			{\footnotesize Note:  From left to right: SPF's  forecasts of core CPI, SPF's core PCE, and SCE's forecast of headline CPI.
+From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of 0.14, -0.05 and -0.25, respectively; uncertainty (red dash) versus absolute value of forecast errors (blue dot) with correlation coefficient of -0.19, 0.35, 0.27, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.43.}
 		\end{flushleft}
@@
 
-	How do we interpret the finding of non-response of forecasting errror and disagreements to monetary policy shocks in the context of rigidity models?
+	How do we interpret the finding of non-response of forecasting error and disagreement to monetary policy shocks in the context of rigidity models?
 Non-response of FE suggests that on average professional forecasters have incorporated the monetary policy changes in their forecasts.
@@
 	One interesting exception is the response of disagreements to oil price changes.
-Households' disagreements concerning inflation drop by 1 percentage point in the first period after an oil price shock and the response have a reasonably small standard error.
+Households' disagreement concerning inflation drops by one percentage point in the first period after an oil price shock and the response have a reasonably small standard error.
 The drop only lasts for 1 month and immediately return to zero since then.

### 2019-07-08 workingfolder/python/InfShocks.py
add core PCE in inflation data. InfM.dta

@@ -79,7 +79,7 @@ from scipy.optimize import minimize
 #
 # The existing SVAR package in *statsmodels* only handles cases with direct zero restrictions on $B$ matrices. Therefore I write my own codes using long-run restrictions here.  
 
-# + {"code_folding": [12]}
+# + {"code_folding": [0, 12]}
 ## loading technology shock data
 ts_data = pd.read_excel('../OtherData/Emp.xls',sheet_name='data')
 ts_data2 = pd.read_excel('../OtherData/EmpSaQ.xls',sheet_name='data')
@@ -142,7 +142,7 @@ LRVar_dt['year'] = LRVar_dt.index.year
 LRVar_dt['quarter'] = LRVar_dt.index.quarter
 LRVar_dt.to_stata('../OtherData/LRVar.dta')
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 # period filter 
 start_t='1948-01-01'
 end_t = '2019-03-30'   # the same period as in Gali (1991)
@@ -449,7 +449,7 @@ plt.plot(sirf_errband_rs[0][:,0,0],label='lb')
 plt.plot(sirf_errband_rs[1][:,0,0],label='ub')
 plt.legend(loc=0)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## IR plot parameters prepared 
 
 ## svar_ma to impulse respulse parameters

### 2019-07-08 paper/Draft.tex
replace all charts with Core PCE and Core CPI for SPF

@@
 However, the observable correlation of realized inflation and the directly estimated average uncertainty from both professionals and households are at most weakly positive during the period between 2007-2019.
-In particular, the correlation coefficients  0.14, -0.05 and -0.24 for SPF's CPI forecast, SPF's PCE forecast and SCE's CPI expectation.
+In particular, the correlation coefficients  0.14, 0.12 and -0.24 for SPF's CPI forecast, SPF's PCE forecast and SCE's CPI expectation.
 This may suggest that during a period of persistently low and stable inflation, the conventional positive redux of inflation and uncertainty is not a good description of the relation of the two.
@@
 Although according to our benchmark framework in \ref{theory}, there is no mathematical correlation between the size of the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
-The correlation coefficients of the two are -0.19, -0.35 and 0.27 for SPF CPI forecasts, SPF PCE forecasts and SCE's forecasts, respectively.
+The correlation coefficients of the two are -0.19, -0.18 and 0.27 for SPF CPI forecasts, SPF PCE forecasts and SCE's forecasts, respectively.
 The two indicators turn out to be negatively correlated for professional forecasts.
@@
 The empirical pattern of the two,  as shown in the plots, also confirms that the two are different objects.
-The correlation coefficients of the two turn out to be negative, -0.29 and -0.46 for SPF forecasts.
+The correlation coefficients of the two turn out to be negative, -0.31 and -0.37 for SPF forecasts.
 In stark contrast, households seem to bear a strong correlation of 0.43 between the two moments.
@@
 			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPICore_varSPFCPIQ.png}
-			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCE_varSPFPCEQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCECore_varSPFPCEQ.png}
 			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
@@
 			\label{DisgVar}
-			\includegraphics[width=0.3\textwidth]{figures/CPI_disg_varSPFCPIQ.png}
-			\includegraphics[width=0.3\textwidth]{figures/PCE_disg_varSPFPCEQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/CORECPI_disg_varSPFCPIQ.png}
+			\includegraphics[width=0.3\textwidth]{figures/COREPCE_disg_varSPFPCEQ.png}
 			\includegraphics[width=0.3\textwidth]{figures/Q9_disg_varSCEM.png}\\
@@
 		\begin{flushleft}
-			{\footnotesize Note:  From left to right: SPF's  forecasts of core CPI, SPF's core PCE, and SCE's forecast of headline CPI.
-From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of 0.14, -0.05 and -0.25, respectively; uncertainty (red dash) versus absolute value of forecast errors (blue dot) with correlation coefficient of -0.19, 0.35, 0.27, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.43.}
+			{\footnotesize Note:  From left to right: SPF's  forecasts of core CPI and core PCE, and SCE's forecast of headline CPI.
+From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of 0.14, 0.12 and -0.25, respectively; uncertainty (red dash) versus absolute value of forecast errors (blue dot) with correlation coefficient of -0.19, -0.18, 0.27, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.31, -0.37 and 0.43,repectively.
+Only the Pearson tests of correlation between disagreement and uncertainty are significant for all.}
 		\end{flushleft}

### 2019-07-10 paper/Draft.tex
Generate Revision efficiency test for Indididual SCE. Using 10-month-apart 2-year forecast and 1-year forecast.
Include revision efficiency tests for SCE using population revisions from 2-year to 1-year. Need to change the texts.

@@
 					\label{RevEfficiency}
-					\begin{tabular}{lllllllll}
-						\hline 
-						& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
-						\hline 
-						\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
-						\hline 
-						& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
-						\hline 
-						L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
-						&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
-						L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
-						&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
-						L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
-						&               &           &          & (0.048)  &               &           &           & (0.069)   \\
-						SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
-						&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
-						SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
-						&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
-						& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
-						Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
-						\hline 
-						N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
-						$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
-						\hline 
-						\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
-						\hline 
-						& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
-						\hline 
-						L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
-						&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
-						L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
-						&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
-						L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
-						&               &           &          & (0.121)  &               &           &           & (0.149)   \\
-						Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
-						& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
-						\hline 
-						N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
-						$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
+				\begin{tabular}{llllllllllllll}
+					\hline 
+					& SPF CPI       &           &          &          & SPF PCE       &           &           &           & \multicolumn{5}{l}{SCE}                                              \\
+					\hline 
+					\multicolumn{14}{l}{Test 1.  Revision efficiency of mean forecast}                                                                                                                               \\
+					\hline 
+					& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                     & Mean revision & t-1      & t-1- t-2 & t-1-t-3  \\
+					\hline 
+					L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  & L.InfExp\_Mean\_rv  &               & 0.884*** & 0.750*** & 0.685**  \\
+					&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   &                     &               & (0.084)  & (0.171)  & (0.211)  \\
+					L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  & L2.InfExp\_Mean\_rv &               &          & 0.206    & 0.199    \\
+					&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   &                     &               &          & (0.173)  & (0.185)  \\
+					L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     & L3.InfExp\_Mean\_rv &               &          & -0.073   & -0.122   \\
+					&               &           &          & (0.048)  &               &           &           & (0.069)   &                     &               &          & (0.191)  & (0.264)  \\
+					SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           & L4.InfExp\_Mean\_rv &               &          &          & 0.055    \\
+					&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           &                     &               &          &          & (0.217)  \\
+					SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** & L5.InfExp\_Mean\_rv &               &          &          & 0.073    \\
+					&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   &                     &               &          &          & (0.242)  \\
+					&               &           &          &          &               &           &           &           & L6.InfExp\_Mean\_rv &               &          &          & -0.016   \\
+					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.140)  \\
+					Constant               & -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   & Constant               & -0.263***     & -0.016   & -0.010   & -0.005   \\
+					& (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   &                     & (0.038)       & (0.029)  & (0.033)  & (0.042)  \\
+					\hline 
+					N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       & N                   & 41            & 40       & 38       & 35       \\
+					$R^2$               & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     & $R^2$               & 0.000         & 0.717    & 0.732    & 0.690    \\
+					\hline 
+					\multicolumn{14}{l}{Test 2. Revision efficiency of uncertainty}             \\
+					\hline                                                                                                                     
+					& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                     & Mean revision & t-1      & t-1- t-2 & t-1-t-3  \\
+					\hline 
+					L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    & L.InfExp\_Var\_rv   &               & 0.731*** & 0.723*** & 0.785*** \\
+					&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   &                     &               & (0.108)  & (0.159)  & (0.161)  \\
+					L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    & L2.InfExp\_Var\_rv  &               &          & 0.283    & 0.174    \\
+					&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   &                     &               &          & (0.197)  & (0.246)  \\
+					L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    & L3.InfExp\_Var\_rv  &               &          & -0.336   & -0.410   \\
+					&               &           &          & (0.121)  &               &           &           & (0.149)   &                     &               &          & (0.186)  & (0.266)  \\
+					&               &           &          &          &               &           &           &           & L4.InfExp\_Var\_rv  &               &          &          & 0.270    \\
+					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.219)  \\
+					&               &           &          &          &               &           &           &           & L5.InfExp\_Var\_rv  &               &          &          & -0.065   \\
+					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.248)  \\
+					&               &           &          &          &               &           &           &           & L6.InfExp\_Var\_rv  &               &          &          & -0.082   \\
+					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.172)  \\
+					Constant               & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   & Constant               & -0.590**      & -0.186   & -0.199   & -0.163   \\
+					& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   &                     & (0.174)       & (0.155)  & (0.164)  & (0.171)  \\
+					\hline 
+					N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       & N                   & 41            & 40       & 38       & 35       \\
+					$R^2$               & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723     & $R^2$               & 0.000         & 0.549    & 0.597    & 0.619 \\
 					\hline    

### 2019-07-10 paper/Draft.tex
rewrote the data section on SCE including 1-year and 2-year ahead

@@
 
-	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probabilistic questions measuring subjective uncertainty in economic surveys.
+	Third, \citet{manski2004measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
 Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have all shown that this is actually less of a concern.
@@
 
-	Survey of Professional Forecasters(SPF) meet both criteria thanks to the density forecasts of a number of macroeconomic variables, including headline CPI and PCE inflation they have started eliciting since 2007.
-In particular, the density forecasts are both made for current year forecast, basically nowcasting, as well as one-year-ahead forecast.
-This allows for directly testing the implications from the revisions in uncertainty.
-
-	The New York Fed Survey of Consumer Expectation(SCE) that started in 2013 has at least met the first criteria.
-In particular, households are asked to provide their perceived probabilities to 1-year-ahead inflation for a range of values.
-\footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one.
-NY Fed stuff has excluded those who do not meet this criteria.} The high-frequency monthly panel structure also provides an invaluable chance to explore the dynamics of uncertainty.
-Around one third of the households are surveyed for 12 months.
+	Survey of Professional Forecasters(SPF) meet both criteria thanks to the density forecasts of a number of macroeconomic variables, including core CPI and core PCE inflation they have started eliciting since 2007, as well as a longer series of GDP deflator dating back to 1968.
+This paper focus on the first two, for which both forecast for current-year inflation, basically nowcast, and one-year-ahead forecast are based on densities.
+This make it possible to directly test the implications about the revisions in uncertainty across different vintages of forecasts.
+
+	The New York Fed Survey of Consumer Expectation(SCE) that started in 2013 meet the first criteria and half of the second.
+In particular, households are asked to provide their perceived probabilities about 1-year-ahead and 2-year-ahead inflation for various ranges of values\footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one.
+NY Fed stuff has excluded those who do not meet this criteria.}.
+This allows for comparing 2-year-ahead forecast at time $t-2$ with 1-year-ahead forecast at $t-1$.
+Since the maximum duration for households to stay in the panel is 12 months (for about one third of the households),  forecast revision can be only examined in the population level.
+The advantage of SCE compared to SPF is its monthly frequency.
+This provides an invaluable chance to explore the dynamics of uncertainty.
 
@@
 
-	\section{Shock-based tests of expectation rigidity }\label{ShockBased}
+	\section{Shock-based Estimates of Expectation Rigidity }\label{ShockBased}
 
@@
 
-	(1) Technology shock is identified from a three variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
+	(1) Technology shock is identified from a three-variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
 Based on Bayes information criterion, I use the lag of 4 quarters as in \citet{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share approach'' developed by \citet{francis2014flexible}.

### 2019-07-10 paper/Draft.tex
Editorial changes

@@
 
-	Denote $ f_{i,t+h|t}$ as agent i's $h$-period-ahead density forecast. $ f_{i,t+h|t}$ is the conditional density of $y_{i,t+h}$ given the information set $I_{i,t}$ available at time $t$.
+	Denote $ f_{t+h|t}$ as agent i's $h$-period-ahead density forecast. $ f_{i,t+h|t}$ is the conditional density of $y_{t+h}$ given the information set $I_{i,t}$ available at time $t$.
 
@@
 
-	Individual forecast error $FE_{i,t+h|t}$ is the difference of ex post realized value of $y_{t+h}$ and individual forecast at time $t$.
+	Individual forecast error $FE_{i,t+h|t}$ is the difference of individual forecast at time $t$ and ex post realized value of $y_{t+h}$.
 
@@
 
-	To abuse the language, I refer to the 3 individual indicators and 4 population indicators as moments and they are  listed in Table \ref{MomSum}
+	To abuse the word moment in a way not completely complying with its statistical definition, I refer to the 3 individual indicators and 4 population indicators defined above as moments and they are  listed in Table \ref{MomSum}.
 
@@
 This is not the case within $h$ periods as the realized shocks in overlapping periods enter both forecast errors.
-These FE-based restrictions of FIRE provide the foundations for the tests used in Table \ref{NullTest}.
+These FE-based restrictions of FIRE provide the foundations for the tests used in Section \ref{NullTest}.
 
@@
 (Equation \ref{VarREIndPop}).
-In FIRE, there are neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}
+In FIRE, there are neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}.
 
@@
 	This directly gives the revision in uncertainty from time $t-1$ to $t$.
-The newly arrived information, although noisy, still brings about information gains, thus leading to an unambiguously drop on uncertainty.
+The newly arrived information, although noisy, still brings about information gains, thus leading to an unambiguously drop in uncertainty.
 But due to the signal is not perfect, i.e.
@@
 Thus the nowcasting remains zero throughout the whole horizon.
-Nowcasting uncertainty picks up in the realization of shock and gradually declines as more and more information signals are realized.
+Nowcasting uncertainty picks up in the realization of shock and gradually declines as more and more signals are learnt.
 This comes from the information gains from Kalman filtering.
@@
 	In the first sight, the sharp rise in nowcasting uncertainty at the beginning of the period being only humbly reflected in the forecasting uncertainty seems counterintuitive.
-Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^2(h-k)$.
+Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^{2(h-k)}$.
 (Equation \ref{VarNIEq}).
@@
 		\begin{flushleft}
-		{\footnotesize Note: the top two figures plot the nowcasting of $y_{t+k}$  at time $t+k$ and forecasting of $y_{t+h}$ at time $t+k$  based on a Kalman filtering together with FIRE after a one-time shock of one unit at time $t$.
+		{\footnotesize Note: the top two figures plot the nowcasting of $y_{t+k}$  at time $t+k$ and forecasting of $y_{t+h}$ at time $t+k$ through Kalman filtering and through FIRE after a one-time shock of size of one unit at time $t$.
 The nowcasting and forecasting uncertainty are correspondingly plotted in the bottom.
@@
 	\begin{itemize}
-		\item Individual and population expectation adjusts in each period, but only partially adjusts to new information. 
+		\item Individual and population expectation adjust in each period, but only partially adjusts to new information. 
 		\item  Individual and population uncertainty unambiguously drop each period as one approaches the period of realization.  
-		\item  Population disagreements rise in each period as time approaches the period of realization. Disagreements will never be zero. 
+		\item  Population disagreement rises in each period as time approaches the period of realization. Disagreements will never be zero. 
 	\end{itemize}
@@
 	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories.
-Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to one unconditional standard deviation of $y$.
+Still, I maintain the assumption in Figure \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to one unconditional standard deviation of $y$.
 And the $\lambda$ is set to be $0.75$, implying on average an update interval of four quarters.
@@
 
-	As it is made clear by the Figure, one notable difference between the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time varying.
+	As it is made clear by the Figure \ref{rigidity}, one notable difference between the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time varying.
 In particular, the implied rigidity from NI in the time of the shock, given there is substantial information gain from Kalman filtering in the same period, is quite low.
@@
 	The focus of this paper naturally restricts my options of the survey data to use compared to other empirical literature of testing theories of expectation formation.
-The surveys who have elicited density forecasts of macroeconomic variables for a sufficiently long period has been rare.
+The surveys that have elicited density forecasts of macroeconomic variables for a sufficiently long period are rare.
 Rarer, for the purpose of the paper, is the data structure that allows for comparing the revisions across vintages that have a fixed terminate date of realization, either in individual level or aggregate level.
@@
 	The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between size of the forecast error and uncertainty.
-Although according to our benchmark framework in \ref{theory}, there is no mathematical correlation between the size of the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
+Although according to our benchmark framework in Section \ref{theory}, there is no mathematical correlation between the size of the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
 The correlation coefficients of the two are -0.19, -0.18 and 0.27 for SPF CPI forecasts, SPF PCE forecasts and SCE's forecasts, respectively.
@@
 	This section first reproduces a number of statistical tests of FIRE used seen existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests relying on uncertainty in Table \ref{RevEfficiency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
-It is an extension of what \citet{fuhrer2018intrinsic} does to mean forecast to uncertainty.
+It is an extension of revision tests on mean forecasts by \citet{fuhrer2018intrinsic} to uncertainty.
 

### 2019-07-11 paper/Draft.tex
finished adding additionl texts about weak efficiency tests

@@
 	\begin{abstract}
-		Surveys on density forecasts of macroeconomic variable that are not availables until recently provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
+		Surveys on density forecasts of macroeconomic variable that are not available until recently provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
 This paper first documents the persistent dispersion in uncertainty about future inflation as well as other stylized facts across economists and households.
@@
 
-	Third, \citet{manski2004measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
-Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have all shown that this is actually less of a concern.
-\citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses.
+	Third, \citet{manski2004measuring},\citet{delavande2011measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
+Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents’ consistent ability and willingness to assign a probability (or “percent chance”) to future events.
+\citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking},\citet{delavande2014probabilistic}.
+etc.}.
 Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
@@
 Specifically, SPF has density forecasts for both core CPI and core PCE \footnote{SPF also  has density forecasts for GDP deflator(for GNP prior to 1992:Q1) going back to 1968.
-Since the ranges of the values as we as the definition have not been consistent over time.
-I do not use it in this paper.}.
+Since the ranges of the values and the definition are not consistent over time, I do not use it in this paper.}.
 For SCE, as the households responders are asked about the overall inflation, It is the most appropriate to be interpreted as  headline CPI inflation.
@@
 75 percentile forecast increases from 1\% to 2\%).
-\footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UnceratitnyOtherMoments} actually exhibits a gradual decline.
+\footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UncertaintyOtherMoments} actually exhibits a gradual decline.
 } This is consistent with the observation in the top left two graphs of Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flattened.
@@
 		\caption{Uncertainty and Other Moments}
-		\label{UnceratitnyOtherMoments}
+		\label{UncertaintyOtherMoments}
 	\end{figure}
@@
 		\centering
-		\caption{Revision in Mean Forecasts}
+		\caption{Mean Forecasts}
 		\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
@@
 	  	\begin{subfigure}[b]{0.5\textwidth}
-	  	\caption{Revision in Uncertainty}
+	  	\caption{Uncertainty}
 		\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  
@@
 		\centering
+		\caption{Revision in Mean Forecasts}
 		\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
@@
 		\begin{subfigure}[b]{0.5\textwidth}
+					\caption{Revision in Uncertainty}
 		\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  
@@
 
-	This section first reproduces a number of statistical tests of FIRE used seen existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests relying on uncertainty in Table \ref{RevEfficiency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
+	This section first reproduces a number of statistical tests of FIRE seen in existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests relying on uncertainty in Table \ref{RevEfficiency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}.
 It is an extension of revision tests on mean forecasts by \citet{fuhrer2018intrinsic} to uncertainty.
@@
 
-	Second, the point forecast one year ago predicts the forecast errors for professionals in the significance level of 1\%.
+	Second, the point forecast one year ago predicts the forecast errors for professionals in the significance level of $1\%$.
 For headline CPI inflation, for instance, one percentage point inflation forecast corresponds to 0.3 percentage points of the forecast errors one year later.
@@
 	Table \ref{WeakRevEfficiency} presents the results with the revision replaced with change in mean forecasts and uncertainty, i.e.
-$y_{t|t-1}$ to $y_{t+1|t}$.
-The auto-correlation of change in mean forecast and uncertainty does not embed tests of null of FIRE (Equation \ref{VarREPop}).
-But if the individual forecasts and their uncertainty are persistent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
+from $y_{t|t-1}$ to $y_{t+1|t}$.
+As we have discussed in Section \ref{theory}, the auto-correlation of change in mean forecast and uncertainty do not bear testable predictions from FIRE (Equation \ref{VarREPop}).
+But if the  forecasts and uncertainty are persistent in its first difference, it may imply that the agent does not react to the news and newly realized shocks sufficiently enough.
+In addition, the auto-correlation regressions of this kind is a useful characterization of the time series dynamics of forecasts.
+With the variable being the first difference, the panel structure of SCE and SPF allows for calculating changes in individual levels for a greater sample size, especially for households.
+Besides autoregression, I also report the constant estimate of the changes in the first column of each sub panel.
+
+    The most noticeable pattern for both professionals and households, and for both mean forecast and uncertainty is that past change predict future changes with universally negative coefficients across different horizons.
+Most of the negative coefficients are statistically significant in the 1\% level.
+For instance, one percentage point of increase in SPF's CPI forecast in the previous quarter predicts around 0.29 percentage points decreases in next quarter.
+This negative correlation are smaller in size but remain significant into further past, i.e.
+-0.24 for two quarters lag and -0.1 for three quarters lag.
+Data on SCE is monthly, so lags are included up to six months.
+The negative correlation between past and current changes are all negative and significant for households.
+The sizes of the correlation coefficients are comparable with professional forecasts when the monthly coefficients are converted to their quarterly average, i.e.
+-0.3 to -0.4.
+
+    Such an auto-correlation of change in mean forecast is very much reflected in the same regression for uncertainty, as reported in the bottom panel of Table \ref{WeakRevEfficiency}.
+For SPF of CPI and PCE, respectively, one unit increase in uncertainty about 1-year-ahead inflation in previous quarter predicts around a 0.39 and 0.44 unit of the drop in next quarter.
+The effect holds up to two quarters for professionals and 5 months for households.
+
+    These evidences suggest that both mean forecast and uncertainty of individuals are mean-reverting.
+An essentially equivalent explanation is that both series are realizations of noisy signals around their respective long-run mean.
+This will lead to exactly negative correlation of first differences as we have seen.
+The mean-reverting patterns might also explain what is observed from Figure \ref{Unceratitny_Histogram}, according to which, there is no significant changes in the distribution across different years.
+
+    The second noticeable result lies in the constant regressions reported in the first column of each sub panel in Table \ref{WeakRevEfficiency}.
+It implies that households constantly lower their mean forecasts as well as uncertainty from month to month, while professional forecasts do not behave in such a way.
+In particular, the constant regression of change in mean forecast for SCE gives an estimated coefficient of -0.05 which is significant in the $5\%$ level.
+Individual households' 1-year-ahead inflation expectations keep being downward adjusted each month compared to their previous answer.
+What is more interesting is that their uncertainty about 1-year-ahead inflation also decrease each month.
+The size of downward adjustment is  $-1.39$ unit and statistically significant in the level of $1\%.$.
+This negative significant constant coefficient remains throughout all auto-regressions, implying it is not driven by time-varying changes.
+
+   The most natural explanation for this that repeatedly surveyed households have become more informative about inflation over time.
+Given the unconditional forecast errors of inflation by households are positive, a downward adjustment of inflation stands for a less-biased forecast.
+\footnote{The possibility that the surveys' information set is influenced by the survey itself is a double-edged sword.
+One one hand, this poses a methodological challenge to the survey designers of expectations as to if surveys can objectively elicit the ``true’’ expectations held by the respondents.
+On the other hand, researchers can use survey as a meaningful intervention tool to identify the effect of factors such as information provision and attention.
+Recent examples of this type of research includes: \citet{coibion2018firms} for firms and \citet{coibion2019monetary} for households.}
 
@@
 
+  In summary, the major additional insights that arise from the empirical tests of this section is that rigidity of incorporating new information in forming expectations imply noticeable inefficiency of revisions in forecasts and drop in uncertainty.
+
 	\section{Shock-based Estimates of Expectation Rigidity }\label{ShockBased}
@@
 The first two are the same in \citet{coibion2012can}.
-\footnote{ Another shock in \citet{coibon2012can} is the news shock by \citet{barsky2011news}.
+\footnote{ \citet{coibion2012can} also uses the news shock by \citet{barsky2011news}.
 This will be included in later version of the paper.}
@@
 		\centering
-		\includegraphics[width=0.7\textwidth]{figures/inf_shocksQ.png}
+		\includegraphics[width=0.8\textwidth,totalheight=0.6\textwidth]{figures/inf_shocksQ.png}
 			\begin{flushleft}
@@
 
-	As to the households forecast, the starkly wider confidence band across  shocks and moments seen in Figure \ref{SCE_IR} are not that surprising given the wide dispersion of the forecasts moments of a dramatically larger magnitude seen in Figure \ref{UnceratitnyOtherMoments}.
+	As to the households forecast, the starkly wider confidence band across  shocks and moments seen in Figure \ref{SCE_IR} are not that surprising given the wide dispersion of the forecasts moments of a dramatically larger magnitude seen in Figure \ref{UncertaintyOtherMoments}.
 

### 2019-07-11 paper/Draft.tex
started NLP task.Notebook importing sample 100 NYT news articles.

@@
 
-	First,  all three forecast series easily reject the unbiasedness test at the significance level of $1\%$.
+	First,  all three forecast series easily reject the unbiasedness test at the significance level of $0.1\%$.
 There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecasters(2.2 versus 0.12) for headline CPI.
 
-	Second, the point forecast one year ago predicts the forecast errors for professionals in the significance level of $1\%$.
+	Second, the point forecast one year ago predicts the forecast errors for professionals in the significance level of $0.1\%$.
 For headline CPI inflation, for instance, one percentage point inflation forecast corresponds to 0.3 percentage points of the forecast errors one year later.
@@
 What is more interesting is that their uncertainty about 1-year-ahead inflation also decrease each month.
-The size of downward adjustment is  $-1.39$ unit and statistically significant in the level of $1\%.$.
+The size of downward adjustment is  $-1.39$ unit and statistically significant in the level of $0.1\%$.
 This negative significant constant coefficient remains throughout all auto-regressions, implying it is not driven by time-varying changes.

### 2019-07-17 paper/Draft.tex
added a section of literature on measuring uncertainty.

@@
 
-	This paper is related to three strands of literature.
+	This paper is related to four strands of literature.
 First, the recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data.
@@
 
-	Second, the literature that has been originally developed under the theme of forecast efficiency provides a framework analyzing the dynamics of uncertainty useful for the purpose of this paper.
+	Second, \citet{manski2004measuring}, \citet{delavande2011measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
+Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents’ consistent ability and willingness to assign a probability (or “percent chance”) to future events.
+\citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking} and \citet{delavande2014probabilistic}, etc.}.
+Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
+This insight holds for not only point forecast, but also and even more importantly, for uncertainty because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.
+
+	Third, by approximating subjective uncertainty directly from density responses, this paper contributes to the literature that develops and uses a variety of measures of uncertainty, especially in the macroeconomic context.
+There is a long tradition of approximating uncertainty by measures that are more directly available in survey data or that can be estimated by econometric methods.
+For instance, \citet{bachmann2013uncertainty} use ex ante disagreement and ex post forecast errors computed from forecasters' surveys as proxies of uncertainty.
+\citet{jurado2015measuring} define the time-varying uncertainty as conditional volatility of the unforecastable component of a macroeconomic variable and estimate it using multiple series of macroeconomic variables.
+\citet{binder2017measuring} approximate uncertainty from rounding in survey data based on the insights from cognitive literature.
+Besides, an emerging approach such as \citet{bloom2009impact} constructs indices of policy uncertainty based on texts of newspaper reporting.
+Although these proxies are all meant to capture the notion of uncertainty,  as shown in the Section \ref{StylizedFacts}, a cross-validation seems to suggest they are statistically uncorrelated or even negatively correlated.
+
+	Fourth, the literature that has been originally developed under the theme of forecast efficiency provides a framework analyzing the dynamics of uncertainty useful for the purpose of this paper.
 The focus of the forecasting efficiency literature is evaluating forecasters' performance and improving forecasting methodology, but it can be adapted to test the theories of expectation formation of different types of agents.
 This is especially relevant to this paper as I focus on the uncertainty.
-
-	Third, \citet{manski2004measuring},\citet{delavande2011measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
-Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents’ consistent ability and willingness to assign a probability (or “percent chance”) to future events.
-\citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking},\citet{delavande2014probabilistic}.
-etc.}.
-Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
-This insight holds for not only point forecast, but also and even more importantly, for uncertainty.
 
@@
 
-	\subsection{Stylized facts}
+	\subsection{Stylized facts}\label{StylizedFacts}
 
@@
 	The last row of Figure \ref{UnceratitnyOtherMoments} examines the relationship between disagreement and uncertainty.
-Many empirical literatures in macroeconomics use disagreements and uncertainty as if they are similar concepts.
+Many empirical literatures in macroeconomics use disagreements and uncertainty as if they are similar concepts\footnote{For instance, \citet{bachmann2013uncertainty} used ex ante disagreement and ex post forecast errors as two measures of uncertainty and find that both uncertainty indicators lead to reduction in real economic activity.}.
 Such a confusion in practice is partly due to the difficulty of finding appropriate measures of uncertainty in the first place.
@@
 	\begin{table}[ht]
-		\caption{Tests of Rationality and Efficiency using Forecast Errors}
+		\caption{Tests of Rationality and Efficiency Using Forecast Errors}
 		\label{NullTestTable}
@@
 				\begin{threeparttable}
-					\caption{Tests of Revision Efficiency using Mean Revision and Uncertainty}
+					\caption{Tests of Revision Efficiency Using Mean Revision and Uncertainty}
 					\label{RevEfficiency}
@@
 			\begin{threeparttable}
-				\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
+				\caption{Weak Tests of Revision Efficiency Using Change in Forecasts and Uncertainty}
 				\label{WeakRevEfficiency}

### 2019-07-17 paper/Draft.tex
small edits

@@
 Specifically, in this paper, I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty.
-Second empirically I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey.
+Second, empirically, I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey.
 Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models.
@@
 	Second, \citet{manski2004measuring}, \citet{delavande2011measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
-Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents’ consistent ability and willingness to assign a probability (or “percent chance”) to future events.
+Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents have consistent ability and willingness to assign a probability (or “percent chance”) to future events.
 \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking} and \citet{delavande2014probabilistic}, etc.}.
 Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
-This insight holds for not only point forecast, but also and even more importantly, for uncertainty because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.
+This insight holds for not only point forecast, but also and even more importantly, for uncertainty, because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.
 
@@
 Therefore, monetary policy being a more public signal can help explain the muted response of disagreements in comparison with other shocks.
-\footnote{Another explanation is that monetary policy actually coordinates agents' expectations, thus accordingly reduce disagreements, according to \citet{morris2002social}.
-This mechanism can mute the response of disagreements.}
+\footnote{Another explanation is that monetary policies actually coordinate agents' expectations, thus reduce the disagreement, according to \citet{morris2002social}.
+This mechanism can mute the response of the disagreement.}
 

### 2019-07-17 paper/Draft.tex
3-year ahead is in SCE instead of 2-year-ahead.Dispersion in uncertainty is discussed in Kurman et al.2015. admitted.

@@
 	The New York Fed Survey of Consumer Expectation(SCE) that started in 2013 meet the first criteria and half of the second.
-In particular, households are asked to provide their perceived probabilities about 1-year-ahead and 2-year-ahead inflation for various ranges of values\footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one.
+In particular, households are asked to provide their perceived probabilities about 1-year-ahead and 3-year-ahead inflation for various ranges of values\footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one.
 NY Fed stuff has excluded those who do not meet this criteria.}.
-This allows for comparing 2-year-ahead forecast at time $t-2$ with 1-year-ahead forecast at $t-1$.
+This allows for comparing 3-year-ahead forecast at time $t-3$ with 1-year-ahead forecast at $t-1$.
 Since the maximum duration for households to stay in the panel is 12 months (for about one third of the households),  forecast revision can be only examined in the population level.
@@
 NI allows for the possibility of homogeneity in uncertainty only under the stringent conditions of an equal precision of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
-Therefore, the presence of dispersion of uncertainty across agents can be read against FIRE.
+Therefore, the presence of dispersion of uncertainty across agents are not consistent with predictions from FIRE.
 
@@
 This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernel density estimated distribution of uncertainty by year on.
-What is common for both types of agents is that the dispersion in uncertainty is persistent over time and do not show much time-variation.
+What is common for both types of agents is that the dispersion in uncertainty is persistent over time and do not show much time-variation \footnote{\citet{kumar2015inflation} also presents the dispersion in uncertainty using a shorter-period of sample for SCE.}.
 

### 2019-07-18 paper/Draft.tex
Added 3000 articles of NYT

@@
 
-	Second, \citet{manski2004measuring}, \citet{delavande2011measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
+	Second, \citet{manski2004measuring}, \citet{delavande2011measuring}, \citet{manski2018survey} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
 Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents have consistent ability and willingness to assign a probability (or “percent chance”) to future events.
 \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking} and \citet{delavande2014probabilistic}, etc.}.
-Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.
+Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumptions.
 This insight holds for not only point forecast, but also and even more importantly, for uncertainty, because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.
@@
 For instance, \citet{bachmann2013uncertainty} use ex ante disagreement and ex post forecast errors computed from forecasters' surveys as proxies of uncertainty.
-\citet{jurado2015measuring} define the time-varying uncertainty as conditional volatility of the unforecastable component of a macroeconomic variable and estimate it using multiple series of macroeconomic variables.
+\citet{jurado2015measuring} define the time-varying uncertainty as conditional volatility of the unforecastable component of a variable and estimate it using multiple macroeconomic series.
 \citet{binder2017measuring} approximate uncertainty from rounding in survey data based on the insights from cognitive literature.
-Besides, an emerging approach such as \citet{bloom2009impact} constructs indices of policy uncertainty based on texts of newspaper reporting.
+Besides, the text-based approach such as \citet{bloom2009impact} constructs indices of policy uncertainty based on texts of newspaper reporting.
 Although these proxies are all meant to capture the notion of uncertainty,  as shown in the Section \ref{StylizedFacts}, a cross-validation seems to suggest they are statistically uncorrelated or even negatively correlated.

### 2019-09-06 paper/Draft.tex
Updated texlive to 2019 and added author's contact and affiliations.
picked up NLP

@@
 \title{Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households}
-\author{Tao Wang}
+\author{Tao Wang \footnote{Department of Economics, Johns Hopkins University; email: twang80@jhu.edu.}}
 
@@
 	\begin{abstract}
-		Surveys on density forecasts of macroeconomic variable that are not available until recently provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
+		Surveys on density forecasts of macroeconomic variables that are not available until recently provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
 This paper first documents the persistent dispersion in uncertainty about future inflation as well as other stylized facts across economists and households.
@@
 Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.
-This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of the analysis.
+This sets the stage for estimating shock-specific rigidity using uncertainty as a next step of the analysis.
 
@@
 This has been also accompanied by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.
-On one hand, various theories built upon different micro foundations produce somewhat similar macro patterns.
-For instance, the notion of expectation rigidity micro-founded by different theories mostly generate a sluggish response to new information.
+On one hand, various theories built upon different micro-foundations produce somewhat similar macro patterns.
+For instance, the notion of expectation rigidity micro-founded by different theories mostly generates a sluggish response to new information.
 On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.
@@
 	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of values of the variable of forecast\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.}.
-With density forecasts,  the variance of individual forecast can be estimated as an indicator of the uncertainty.
+With density forecasts,  the variance of the individual forecast can be estimated as an indicator of the uncertainty.
 Across different vintages of the forecast, the revision in uncertainty is a direct measure of information gain or the degree of forecasting efficiency.
-Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely examined by the literature, such as forecast errors and disagreements provide many insights as to how the agents expectation actually work.
+Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely examined by the literature, such as forecast errors and disagreements provide many insights as to how the agent's expectation actually work.
 
@@
 In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.
-However, all of these research simply rely upon point forecasts instead of density forecast or surveyed uncertainty.
+However, all of these studies simply rely upon point forecasts instead of density forecast or surveyed uncertainty.
 This is one theme on which this paper differs from the existing literature.
@@
 	Second, \citet{manski2004measuring}, \citet{delavande2011measuring}, \citet{manski2018survey} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys.
-Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents have consistent ability and willingness to assign a probability (or “percent chance”) to future events.
-\citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking} and \citet{delavande2014probabilistic}, etc.}.
+Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents have the consistent ability and willingness to assign a probability (or “percent chance”) to future events.
+\citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to ensure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking} and \citet{delavande2014probabilistic}, etc.}.
 Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumptions.
-This insight holds for not only point forecast, but also and even more importantly, for uncertainty, because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.
+This insight holds for not only point forecast but also and even more importantly, for uncertainty, because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.
 
@@
 There is a long tradition of approximating uncertainty by measures that are more directly available in survey data or that can be estimated by econometric methods.
-For instance, \citet{bachmann2013uncertainty} use ex ante disagreement and ex post forecast errors computed from forecasters' surveys as proxies of uncertainty.
+For instance, \citet{bachmann2013uncertainty} use ex-ante disagreement and ex-post forecast errors computed from forecasters' surveys as proxies of uncertainty.
 \citet{jurado2015measuring} define the time-varying uncertainty as conditional volatility of the unforecastable component of a variable and estimate it using multiple macroeconomic series.
@@
 Besides, the text-based approach such as \citet{bloom2009impact} constructs indices of policy uncertainty based on texts of newspaper reporting.
-Although these proxies are all meant to capture the notion of uncertainty,  as shown in the Section \ref{StylizedFacts}, a cross-validation seems to suggest they are statistically uncorrelated or even negatively correlated.
+Although these proxies are all meant to capture the notion of uncertainty,  as shown in Section \ref{StylizedFacts}, cross-validation seems to suggest they are statistically uncorrelated or even negatively correlated.
 
@@
 Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments.
-Section \ref{empirical} discusses the survey data used for this paper and presents both the stylized patterns and time series regressions that test the implications of these theories.
+Section \ref{empirical} discusses the survey data used for this paper and presents both the stylized patterns and time-series regressions that test the implications of these theories.
 Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.
@@
 So we can simply denote the variable as $y_{t+h}$.
-\footnote{Only in the context of aggregate variable, it make sense to study the population moments such as average expectations and disagreements.
+\footnote{Only in the context of aggregate variable, it makes sense to study the population moments such as average expectations and disagreements.
 Studying expectations of idiosyncratic variables requires individual panel data, as well as the idiosyncratic realizations of the variable.
@@
 So the information set may not contain the most recent realization of the variable of forecast $y_t$.
-\footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$.
-For instance, \citet{patton2010forecasters} finds that the disagreements are driven by not only difference in information but also heterogeneity in prior and models.
+\footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent uses to form the conditional density of the variables by agent $i$.
+For instance, \citet{patton2010forecasters} finds that the disagreements are driven by not the only difference in information but also heterogeneity in prior and models.
 More theoretical work includes multi-prior or model uncertainty such as \citet{hansen2001robust}, \citet{hansen2008robustness}, etc.}
 
-	Accordingly, h-period ahead mean forecast at $t$, denoted as $ y_{i,t+h|t}$, is the conditional expectation of $y_{t+h}$ by the agent $i$.
+	Accordingly, h-period-ahead mean forecast at $t$, denoted as $ y_{i,t+h|t}$, is the conditional expectation of $y_{t+h}$ by the agent $i$.
 
@@
 It is easy to see that the forecast error is orthogonal to information available till time $t$.
-This provides the a well known null hypothesis of FIRE.
+This provides a well known null hypothesis of FIRE.
 
@@
 	The testable implication of rationality lies in the revision of uncertainty.
-Hereafter, we refer revision (instead of change) as the difference of moments across vintages of forecast with the fixed terminate date of realization.
+Hereafter, we refer revision (instead of change) as the difference of moments across vintages of the forecast with the fixed terminate date of realization.
 For instance, the difference between the uncertainty about $y_{t+h}$ at time $t$ and the uncertainty about $y_{t+h}$ at time $t-1$.
@@
 
-	Lastly, FIRE has predictions about disagreements. As agents perfect update the same information, there is no disagreements at any point of the time.
+	Lastly, FIRE has predictions about disagreements. As agents perfect update the same information, there is no disagreement at any point of the time.
 
@@
 
-	Another simple result is that both disagreements and uncertainty do not respond to realized shocks any any point of the time. But this does not differentiate FIRE from other models.
+	Another simple result is that both disagreements and uncertainty do not respond to realized shocks at any point of the time. But this does not differentiate FIRE from other models.
 
@@
 
-	Relying upon the law of large numbers, one can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$.
-\footnote{\citet{carroll2003macroeconomic} is good example of this for households.}
-
-	One well known prediction from SE is that the average forecast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
+	Relying upon the law of large numbers, one can derive testable predictions about population moments that allow us to conduct tests of sticky expectation and recover rigidity parameter $\lambda$.
+\footnote{\citet{carroll2003macroeconomic} is a good example of this for households.}
+
+	One well-known prediction from SE is that the average forecast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below.
 \footnote{See \citet{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$.
@@
 	It is easy to show that the average forecast errors are serially correlated(Equation \ref{FESEPop}).
-For double checking, setting $\lambda=1$, SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.
+For double-checking, setting $\lambda=1$, SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.
 
@@
 \citet{coibion2012can} derive the impulse response of dispersion at time $t+k$ to a shock that realized at $t$.
-Disagreements rise after realization of the shock and gradually returns to its steady state level.
+Disagreements increase after realization of the shock and gradually returns to its steady-state level.
 
@@
 	\begin{itemize}
-		\item Population mean forecast partially responds to shocks and with lags. 
+		\item Population's mean forecast partially responds to shocks and with lags. 
 		\item Forecast errors are serially correlated. 
-		\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
+		\item Population disagreements increase in response to new shocks and return to steady-state level gradually. 
 		\item Population average uncertainty revision under-reacts volatility of the shocks.
@@
 	We assume agent $i$ observe two signals $s^{pb}$ and $s^{pr}_i$, with $s^{pb}$ being public signal common to all agents, and $s^{pr}_i$ private signals being individual specific with subscript $i$.
-The generating process of two signals are assumed to be the following.
+The generating process of two signals is assumed to be the following.
 
@@
 It is a function of previous period uncertainty about $y_t$ and noisiness of the signals determined by $\Sigma^v$.
-Note $P$ is time variant as the variance is updated by the agent each period.
-The time varying nature of rigidity will be discussed later.
+Note $P$ is time-variant as the variance is updated by the agent each period.
+The time-varying nature of rigidity will be discussed later.
 For now, I drop time $t$ from $P$ to avoid clustering.
@@
 
-	From the top left figure, the agent's nowcasting $y_{t+k|t+k}$, namely her best real-time guess based on prior and the realized signal at each period roughly tracks the $y_{t+k}$ and responds partially to signals in each period.
+	From the figure on the top left, the agent's nowcasting $y_{t+k|t+k}$, namely her best real-time guess based on prior and the realized signal at each period roughly tracks the $y_{t+k}$ and responds partially to signals in each period.
 Correspondingly, her forecasting of $y$ at $t+10$ also centers around the true value.
@@
 Thus the nowcasting remains zero throughout the whole horizon.
-Nowcasting uncertainty picks up in the realization of shock and gradually declines as more and more signals are learnt.
+Nowcasting uncertainty picks up in the realization of shock and gradually declines as more and more signals are learned.
 This comes from the information gains from Kalman filtering.
@@
 	In the first sight, the sharp rise in nowcasting uncertainty at the beginning of the period being only humbly reflected in the forecasting uncertainty seems counterintuitive.
-Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^{2(h-k)}$.
+Actually, this is due to nowcasting uncertainty is discounted by the factor of $\rho^{2(h-k)}$.
 (Equation \ref{VarNIEq}).
@@
 	The implications for disagreement are straightforward.
-First, the disagreement decrease with the forecast horizon for the reason of discounting.
+First, the disagreement decrease with the forecast horizon due to discounting.
 Second, the disagreement depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
@@
 		\item  Individual and population uncertainty unambiguously drop each period as one approaches the period of realization.  
-		\item  Population disagreement rises in each period as time approaches the period of realization. Disagreements will never be zero. 
+		\item  Population disagreement rises in each period as the time approaches the period of realization. Disagreements will never be zero. 
 	\end{itemize}
 
-	\subsection{Comparing FIRE, SE and NI}
+	\subsection{Comparing FIRE, SE, and NI}
 
@@
 This implies that the noise of the private signal that drives the disagreements in NI exceeds that the extent to which the agents do not simultaneously update in SE.
-\footnote{Another subtle point is that if the disagreements jump the highest in the time of the shock turns out depend on value of $\lambda$.
+\footnote{Another subtle point is that if the disagreements jump the highest in the time of the shock turns out to depend on the value of $\lambda$.
 In the fixed horizon forecasting, $\lambda=0.5$ is the maximizer of disagreements.}
@@
 
-	In order to understand why the rigidity seen from uncertainty is de facto much lower in NI that in SE for a sensible values of the noisiness of signals , I plot the implied rigidity from two models in Figure \ref{rigidity} for three different values of nosiness of signals in NI while fixing rigidity in SE to be $1-\lambda =0.75$.
+	In order to understand why the rigidity seen from uncertainty is de facto much lower in NI that in SE for a sensible values of the noisiness of signals, I plot the implied rigidity from two models in Figure \ref{rigidity} for three different values of nosiness of signals in NI while fixing rigidity in SE to be $1-\lambda =0.75$.
 In particular, the noisiness range from $0.1$, $1$ and $10$ times of the long-run variance of $y$.
 
-	As it is made clear by the Figure \ref{rigidity}, one notable difference between the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time varying.
+	As it is made clear by Figure \ref{rigidity}, one notable difference between the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time-varying.
 In particular, the implied rigidity from NI in the time of the shock, given there is substantial information gain from Kalman filtering in the same period, is quite low.
-For a noisiness of both signals as 10 times as high of the unconditional standard deviation of $y$, the rigidity only reaches the fixed rigidity in SE till the 8-th period.
-But since by that time, the initial information provided by the shock at time $t$ has been mostly absorbed by NI agent, so in fact the uncertainty revision in NI is quite efficient compared to SE models.
+For a noisiness of both signals as 10 times as high of the unconditional standard deviation of $y$, the rigidity only reaches the fixed rigidity in SE till the 8th period.
+But since by that time, the initial information provided by the shock at time $t$ has been mostly absorbed by NI agent, so in fact, the uncertainty revision in NI is quite efficient compared to SE models.
 This echoes our earlier observation in Figure \ref{IllustrateNI}.
+
+	In order to understand why the rigidity seen from uncertainty is de facto much lower in NI that in SE for a sensible values of the noisiness of signals, I plot the implied rigidity from two models in Figure \ref{rigidity} for three different values of nosiness of signals in NI while fixing rigidity in SE to be $1-\lambda =0.75$.
+In particular, the noisiness range from $0.1$, $1$ and $10$ times of the long-run variance of $y$.
 
@@
 
-	In summary, although NI and SE both predict the similar qualitative predictions of rigidity when it comes the behavior of FE and disagreements, de facto, the efficiency of forecasting from NI is higher than SE.
-The only additional uncertainty in NI to that in FIRE is the nowcasting uncertainty, which is discounted in future.
-While in SE, the uncertainty do come from the lagged update of information, which involve uncertainties about all the shocks that are not yet updated in agents' information set.
+	In summary, although NI and SE both predict the similar qualitative predictions of rigidity when it comes to the behavior of FE and disagreements, de facto, the efficiency of forecasting from NI is higher than SE.
+The only additional uncertainty in NI to that in FIRE is the nowcasting uncertainty, which is discounted in the future.
+While in SE, the uncertainty does come from the lagged update of information, which involve uncertainties about all the shocks that are not yet updated in agents' information set.
 
@@
 
-	Survey of Professional Forecasters(SPF) meet both criteria thanks to the density forecasts of a number of macroeconomic variables, including core CPI and core PCE inflation they have started eliciting since 2007, as well as a longer series of GDP deflator dating back to 1968.
-This paper focus on the first two, for which both forecast for current-year inflation, basically nowcast, and one-year-ahead forecast are based on densities.
-This make it possible to directly test the implications about the revisions in uncertainty across different vintages of forecasts.
+	Survey of Professional Forecasters(SPF) meet both criteria thanks to the density forecasts of a number of macroeconomic variables, including core CPI and core PCE inflation they have started eliciting since 2007, as well as a series of GDP deflator dating back to 1968.
+This paper focuses on the first two, for which both forecasts for current-year inflation, basically nowcast, and one-year-ahead forecast are based on densities.
+This makes it possible to directly test the implications of the revisions in uncertainty across different vintages of forecasts.
 
@@
 In particular, households are asked to provide their perceived probabilities about 1-year-ahead and 3-year-ahead inflation for various ranges of values\footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one.
-NY Fed stuff has excluded those who do not meet this criteria.}.
+NY Fed stuff has excluded those who do not meet these criteria.}.
 This allows for comparing 3-year-ahead forecast at time $t-3$ with 1-year-ahead forecast at $t-1$.
-Since the maximum duration for households to stay in the panel is 12 months (for about one third of the households),  forecast revision can be only examined in the population level.
+Since the maximum duration for households to stay in the panel is 12 months (for about one-third of the households),  forecast revision can be only examined in the population level.
 The advantage of SCE compared to SPF is its monthly frequency.
@@
 For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentile as these are typically abnormals that are due to measurement errors or other reasons.
-For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast are inclined to give extreme values.
+For SCE, I drop the top and bottom 5 percent of mean forecasts and uncertainty as households mean forecast are inclined to give extreme values.
 All the results in this paper are robust to a different threshold such as 10 and 1 percentile.
@@
 
-	Throughout the paper, I use three measures of inflation: headline CPI, core CPI and core PCE .
+	Throughout the paper, I use three measures of inflation: headline CPI, core CPI, and core PCE .
 Depending on the specific variable of forecast in the survey series, the realization of the corresponding inflation is used to compute moments such as forecast errors.
-Specifically, SPF has density forecasts for both core CPI and core PCE \footnote{SPF also  has density forecasts for GDP deflator(for GNP prior to 1992:Q1) going back to 1968.
+Specifically, SPF has density forecasts for both core CPI and core PCE \footnote{SPF also has density forecasts for GDP deflator(for GNP prior to 1992: Q1) going back to 1968.
 Since the ranges of the values and the definition are not consistent over time, I do not use it in this paper.}.
@@
 	Although the sheer magnitudes of the differences between professionals' moments and those of households are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency.
-Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty against realized inflation,  forecast errors and disagreements in the first, second and third rows, respectively.
+Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty against realized inflation,  forecast errors, and disagreements in the first, second and third rows, respectively.
 
@@
 However, the observable correlation of realized inflation and the directly estimated average uncertainty from both professionals and households are at most weakly positive during the period between 2007-2019.
-In particular, the correlation coefficients  0.14, 0.12 and -0.24 for SPF's CPI forecast, SPF's PCE forecast and SCE's CPI expectation.
+In particular, the correlation coefficients  0.14, 0.12 and -0.24 for SPF's CPI forecast, SPF's PCE forecast, and SCE's CPI expectation.
 This may suggest that during a period of persistently low and stable inflation, the conventional positive redux of inflation and uncertainty is not a good description of the relation of the two.
@@
 	The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between size of the forecast error and uncertainty.
-Although according to our benchmark framework in Section \ref{theory}, there is no mathematical correlation between the size of the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors.
-The correlation coefficients of the two are -0.19, -0.18 and 0.27 for SPF CPI forecasts, SPF PCE forecasts and SCE's forecasts, respectively.
+Although according to our benchmark framework in Section \ref{theory}, there is no mathematical correlation between the size of the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex-ante uncertainty implies bigger ex post forecast errors.
+The correlation coefficients of the two are -0.19, -0.18 and 0.27 for SPF CPI forecasts, SPF PCE forecasts, and SCE's forecasts, respectively.
 The two indicators turn out to be negatively correlated for professional forecasts.
@@
 	The last row of Figure \ref{UnceratitnyOtherMoments} examines the relationship between disagreement and uncertainty.
-Many empirical literatures in macroeconomics use disagreements and uncertainty as if they are similar concepts\footnote{For instance, \citet{bachmann2013uncertainty} used ex ante disagreement and ex post forecast errors as two measures of uncertainty and find that both uncertainty indicators lead to reduction in real economic activity.}.
-Such a confusion in practice is partly due to the difficulty of finding appropriate measures of uncertainty in the first place.
+Many empirical literature in macroeconomics use disagreements and uncertainty as if they are similar concepts\footnote{For instance, \citet{bachmann2013uncertainty} used ex-ante disagreement and ex-post forecast errors as two measures of uncertainty and find that both uncertainty indicators lead to a reduction in real economic activity.}.
+Such confusion in practice is partly due to the difficulty of finding appropriate measures of uncertainty in the first place.
 But as we have presented in \ref{theory}, the two are concepts with distinct statistical definitions.
@@
 	Overall, professional forecasters' moments exhibit patterns more consistency from a statistical point of view.
-In contrast, the positive correlation across households' ex ante uncertainty, ex post forecast errors, and cross-section disagreements cannot be easily reconciled by the framework we set up in Section \ref{theory}.
-
-	Persistent disagreement in expectations has been used as an important stylized evidence inconsistent with the assumption of identical expectation embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
+In contrast, the positive correlation across households' ex-ante uncertainty, ex-post forecast errors, and cross-section disagreements cannot be easily reconciled by the framework we set up in Section \ref{theory}.
+
+	Persistent disagreement in expectations has been used as important stylized evidence inconsistent with the assumption of identical expectation embedded in FIRE, for instance, \citet{mankiw2003disagreement}.
 A similar fact-checking can be done with respect to individual uncertainty.
@@
 In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEInd}).
-NI allows for the possibility of homogeneity in uncertainty only under the stringent conditions of an equal precision of signals and the same prior of uncertainty (Equation \ref{VarNIEq}).
-Therefore, the presence of dispersion of uncertainty across agents are not consistent with predictions from FIRE.
+NI allows for the possibility of homogeneity in uncertainty only under the stringent conditions of an equal precision of signals and the same prior for uncertainty (Equation \ref{VarNIEq}).
+Therefore, the presence of dispersion of uncertainty across agents is not consistent with predictions from FIRE.
 
@@
 	Besides, in terms of the distribution of uncertainty, there are households/professional difference and similarity.
-Households' uncertainty is more skewed toward to the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty.
+Households' uncertainty is more skewed toward the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty.
 This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernel density estimated distribution of uncertainty by year on.
@@
 75 percentile forecast increases from 1\% to 2\%).
-\footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UncertaintyOtherMoments} actually exhibits a gradual decline.
+\footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in the bottom row of Figure \ref{UncertaintyOtherMoments} actually exhibits a gradual decline.
 } This is consistent with the observation in the top left two graphs of Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flattened.
@@
 	FIRE also predicts an unambiguous reduction in uncertainty as one approaches the date of realization, where the drop is exactly equal to the volatility of the realized shocks.
-Although quantitatively it is hard to check this, one can look if the distribution of the uncertainty revision concentrate in the negative range.
+Although quantitatively it is hard to check this, one can look if the distribution of the uncertainty revision concentrates in the negative range.
 Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty from 1-year-ahead forecast in year $t-1$ to the current-year nowcast in year $t$.
@@
 Unfortunately, since SCE does not provide the data structure for this purpose, I cannot make a comparison between two types of agents.
-A formal test of revision equal to zero or being negative will be carried out in the Section \ref{NullTest}.
+A formal test of revision equal to zero or being negative will be carried out in Section \ref{NullTest}.
 
@@
 The forecast errors are correlated to the extent of the realized shocks in the overlapping periods.
-So the positive serial correlation does not directly violates FIRE.
-But the correlation of overlapping forecast errors still contain the useful information about the size of the realized shocks.
+So the positive serial correlation does not directly violate FIRE.
+But the correlation of overlapping forecast errors still contains useful information about the size of the realized shocks.
 
 	FE-based tests results are presented in Table \ref{NullTestTable}.
-Individual level data are used thanks to the panel structure of both surveys.
+Individual-level data are used thanks to the panel structure of both surveys.
 Since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE.
@@
 Revisions of forecasts are serially correlated over 4 quarters and the coefficients are all positive and significant.
-Also, the median forecasts as the past information always predicts a negative revision with significant coefficients.
+Also, the median forecasts as the past information always predict a negative revision with significant coefficients.
 This is evidence against the null hypothesis of FIRE and my estimates are comparable with those by \citet{fuhrer2018intrinsic}.
@@
 
-	The second to fourth column show a positive serial correlation of revision in uncertainty for both CPI and PCE forecasts.
-The revision to CPI seems more efficient as serial correlation is with only one quarter lag.
+	The second to fourth column shows a positive serial correlation of revision in uncertainty for both CPI and PCE forecasts.
+The revision to CPI seems more efficient as serial correlation is with only one-quarter lag.
 For PCE, the revisions in uncertainty are serially correlated with all past three quarters.
@@
 In addition, the auto-correlation regressions of this kind is a useful characterization of the time series dynamics of forecasts.
-With the variable being the first difference, the panel structure of SCE and SPF allows for calculating changes in individual levels for a greater sample size, especially for households.
-Besides autoregression, I also report the constant estimate of the changes in the first column of each sub panel.
+With the variable being the first difference, the panel structure of SCE and SPF allows for calculating changes in individual levels for greater sample size, especially for households.
+Besides autoregression, I also report the constant estimate of the changes in the first column of each sub-panel.
 
@@
 Most of the negative coefficients are statistically significant in the 1\% level.
-For instance, one percentage point of increase in SPF's CPI forecast in the previous quarter predicts around 0.29 percentage points decreases in next quarter.
-This negative correlation are smaller in size but remain significant into further past, i.e.
+For instance, one percentage point of increase in SPF's CPI forecast in the previous quarter predicts around 0.29 percentage points decrease in the next quarter.
+This negative correlation is smaller in size but remain significant into further past, i.e.
 -0.24 for two quarters lag and -0.1 for three quarters lag.
@@
     Such an auto-correlation of change in mean forecast is very much reflected in the same regression for uncertainty, as reported in the bottom panel of Table \ref{WeakRevEfficiency}.
-For SPF of CPI and PCE, respectively, one unit increase in uncertainty about 1-year-ahead inflation in previous quarter predicts around a 0.39 and 0.44 unit of the drop in next quarter.
+For SPF of CPI and PCE, respectively, one unit increase in uncertainty about 1-year-ahead inflation in previous quarter predicts around a 0.39 and 0.44 unit of the drop in the next quarter.
 The effect holds up to two quarters for professionals and 5 months for households.
 
-    These evidences suggest that both mean forecast and uncertainty of individuals are mean-reverting.
+    These evidence suggest that both the mean forecast and uncertainty of individuals are mean-reverting.
 An essentially equivalent explanation is that both series are realizations of noisy signals around their respective long-run mean.
-This will lead to exactly negative correlation of first differences as we have seen.
-The mean-reverting patterns might also explain what is observed from Figure \ref{Unceratitny_Histogram}, according to which, there is no significant changes in the distribution across different years.
-
-    The second noticeable result lies in the constant regressions reported in the first column of each sub panel in Table \ref{WeakRevEfficiency}.
-It implies that households constantly lower their mean forecasts as well as uncertainty from month to month, while professional forecasts do not behave in such a way.
-In particular, the constant regression of change in mean forecast for SCE gives an estimated coefficient of -0.05 which is significant in the $5\%$ level.
+This will lead to the exact negative correlation of first differences we have seen.
+The mean-reverting patterns might also explain what is observed from Figure \ref{Unceratitny_Histogram}, according to which, there are no significant changes in the distribution across different years.
+
+    The second noticeable result lies in the constant regressions reported in the first column of each sub-panel in Table \ref{WeakRevEfficiency}.
+It implies that households constantly lower their mean forecasts as well as uncertainty from month to month, while professional forecasts do not behave in such a pattern.
+In particular, the constant regression of the change in the mean forecast for SCE gives an estimated coefficient of -0.05 which is significant in the $5\%$ level.
 Individual households' 1-year-ahead inflation expectations keep being downward adjusted each month compared to their previous answer.
-What is more interesting is that their uncertainty about 1-year-ahead inflation also decrease each month.
-The size of downward adjustment is  $-1.39$ unit and statistically significant in the level of $0.1\%$.
-This negative significant constant coefficient remains throughout all auto-regressions, implying it is not driven by time-varying changes.
+What is more interesting is that their uncertainty about 1-year-ahead inflation also decreases each month.
+The size of the downward adjustment is  $-1.39$ unit and statistically significant in the level of $0.1\%$.
+This negative significant and constant coefficient remains throughout all auto-regressions, implying it is not driven by time-varying changes.
 
@@
 \footnote{The possibility that the surveys' information set is influenced by the survey itself is a double-edged sword.
-One one hand, this poses a methodological challenge to the survey designers of expectations as to if surveys can objectively elicit the ``true’’ expectations held by the respondents.
-On the other hand, researchers can use survey as a meaningful intervention tool to identify the effect of factors such as information provision and attention.
+On one hand, this poses a methodological challenge to the survey designers of expectations as to if surveys can objectively elicit the ``true’’ expectations held by the respondents.
+On the other hand, researchers can use the survey as a meaningful intervention tool to identify the effect of factors such as information provision and attention.
 Recent examples of this type of research includes: \citet{coibion2018firms} for firms and \citet{coibion2019monetary} for households.}
@@
 
+	\section{Shock-based Estimates of Expectation Rigidity }\label{ShockBased}
+
+	\citet{coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
+Unlike the time series regressions that test null hypotheses of FIRE in the previous section, this approach allows a more straightforward comparison between the empirical evidence from surveys and the theoretical predictions illustrated in Figure \ref{ir_pop}.
+The difficulty of this approach lies in identifying a shock $\omega_t$ that is a pure innovation to inflation at time $t$.
+
 	(1) Technology shock is identified from a three-variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
@@
 	(3) Monetary policy shocks: target surprise and path surprise in the terminology of \citet{laseen2011anticipated}.
-Target surprise is defined as the unexpected change in federal funds rate in a particular date of FOMC meetings.
+Target surprise is defined as the unexpected change in the federal funds rate in a particular date of FOMC meetings.
 It is the OLS residual of federal funds rate change in the past expected change in the federal funds rate.
@@
 In particular, the responses of disagreement is with respect to the absolute value of the shocks.
-Because CPI inflation forecast is available only after 1984, the sample period 1984-2007 is six years shorter than that in Figure 2 from \citet{coibion2012can}: 1976-2007.
+Because the CPI inflation forecast is available only after 1984, the sample period 1984-2007 is six years shorter than that in Figure 2 from \citet{coibion2012can}: 1976-2007.
 I do not include the results for PCE inflation as there is no PCE forecast during this period.
@@
 
-	Left panel of the Figure \ref{ReplicateCoibionBefore2007} show results broadly consistent with \citet{coibion2012can} despite a wider confidence band possibly due to the change in inflation measures and the difference in the sample period.
+	The left panel of the Figure \ref{ReplicateCoibionBefore2007} show results are broadly consistent with \citet{coibion2012can} despite a wider confidence band possibly due to the change in inflation measures and the difference in the sample period.
 Productivity and oil price shocks are deflationary and inflationary, respectively.
-One standard deviation of productivity unsurprisingly brings down headline inflation by around 10 percentage points  in the first quarter and the negative impacts gradually mute since then till the 7-th quarter.
+One standard deviation of productivity unsurprisingly brings down headline inflation by around 10 percentage points in the first quarter and the negative impacts gradually mute since then till the 7-the quarter.
 Oil price shock of one standard deviation increases headline inflation by around 3 percentage points in the first quarter and the inflationary impacts last for 6 quarters.
@@
 	Second, population forecast errors respond to shocks in a sluggish manner as predicted in rigidity models.
-This is illustrated using both SPF's FE of CPI in the second graph of  left panel in Figure \ref{ReplicateCoibionBefore2007}.
+This is illustrated using both SPF's FE of CPI in the second graph of the left panel in Figure \ref{ReplicateCoibionBefore2007}.
 As we define the forecast error as point forecast minus realized value, forecast error rises(drops) after a positive(negative) shock and gradually return to zero around 4-5th quarters after the shock.
@@
 	Lastly, SE and NI models imply disagreement pick up after shocks and gradually drop over the longer horizon.
-Looking into the graph, the average response of disagreement to absolute value of  technology and oil shocks exhibit patterns similar to this prediction.
+Looking into the graph, the average response of disagreement to the absolute value of technology and oil shocks exhibit patterns similar to this prediction.
 Note now that the initial response is no longer statistically significant(same as the original result) and the pick-up of disagreement after both shocks do not take place immediately in the same quarter but in one quarter after the shock.
 \footnote{In addition, the degree of long-run disagreements sheds light upon one subtle difference between the SE and NI.
-Disagreements always exist in NI with the presence of private signals , in contrast, disagreement is zero over the long run in SE.
+Disagreements always exist in NI with the presence of private signals, in contrast, disagreement is zero over the long run in SE.
 }
@@
 On the top, I first plot the impulse response of inflation to path surprises $ED8ut$ and target surprise $MP1ut$, separately.
-On average, inflation reduces by around 10 percentage points after one unit increase of target surprise and increases by 10 percentage points following one unit of path surprise to federal funds rate.
+On average, inflation reduces by around 10 percentage points after one unit increase of target surprise and increases by 10 percentage points following one unit of path surprise to the federal funds rate.
 Both responses are  statistically significant in $10\%$  significance level.
@@
 
-	In Figure \ref{ReplicateCoibionwholeperiod}, I extend the sample period to include the post-2007 years till 2019.
+	In Figure \ref{ReplicateCoibionwholeperiod}, I extend the sample period to include the post-2007 years up till 2019.
 Importantly, post2007 is the period when SPF starts surveying density forecasts that allow us to study the dynamics of uncertainty.
-In addition, the post crisis period has been characterized by a number of different features in terms of the behavior of macroeconomy(i.e.
+In addition, the post-crisis period has been characterized by a number of different features in terms of the behavior of macroeconomy(i.e.
 persistently low inflation) and monetary policy implementation (i.e.
@@
 	The left panel of  Figure \ref{ReplicateCoibionwholeperiod} presents impulse responses of average uncertainty of SPF in addition to that inflation, forecast error, disagreements in response to technology and oil price shocks.
-As shown in the top three figures, the results are consistent with that in Figure \ref{ReplicateCoibionBefore2007} for period before 2007.
+As shown in the top three figures, the results are consistent with that in Figure \ref{ReplicateCoibionBefore2007} for the period before 2007.
 Oil shock(technology shock) increases(decreases) inflation in the first quarter by 0.1 percentage points, whose impacts last till 7-8th quarters.
-Confidence interval of the responses is smaller compared to previous figure probably due to larger sample size.
+The confidence interval of the responses is smaller compared to the previous figure probably due to the larger sample size.
 Average forecast errors react partially to the shock and gradually return to zero over the 4-5th quarters afterward.
@@
 In the same time, unexpected rate change does not affect inflation significantly once we include the post-2007 period.
-One possible explanation for this is the small variation of target surprise after financial crisis, as illustrated in Figure \ref{Inflationshocks}.
-Except for the dramatic monetary loosening during financial crisis, there was little variation in the unexpected federal fund rate change.
-
-	Similar to results for pre-2007 period, the initial response of average forecast error to future tightening shock is statistically significant in the first period but insignificant soon after.
+One possible explanation for this is the small variation of target surprise after the financial crisis, as illustrated in Figure \ref{Inflationshocks}.
+Except for the dramatic monetary loosening during the financial crisis, there was a little variation in the unexpected federal fund rate change.
+
+	Similar to results for the pre-2007 period, the initial response of average forecast error to future tightening shock is statistically significant in the first period but insignificant soon after.
 Interestingly, even though the target surprise does not affect inflation itself, forecast errors do react to it in an inflationary manner.
@@
 The estimates of these responses are not significantly from zero throughout the entire horizon.
-Non-response of disagreements could arise if forecasters have incorporated the monetary policy shocks (thus the shock no longer qualified as a ``shock'') , or all forecasters simultaneously incorporating the realization of the monetary shocks.
+Non-response of disagreements could arise if forecasters have incorporated the monetary policy shocks (thus the shock no longer qualified as a ``shock''), or all forecasters simultaneously incorporating the realization of the monetary shocks.
 In the context of NI model, the disagreements can only arise with the presence of private signals.
-Therefore, monetary policy being a more public signal can help explain the muted response of disagreements in comparison with other shocks.
+Therefore, the monetary policy being a more public signal can help explain the muted response of disagreements in comparison with other shocks.
 \footnote{Another explanation is that monetary policies actually coordinate agents' expectations, thus reduce the disagreement, according to \citet{morris2002social}.
@@
 
-	Lastly, average uncertainty do not react to monetary policy shocks in the extended period.
+	Lastly, average uncertainty does not react to monetary policy shocks in the extended period.
 None of the response is significantly different from zero.
@@
 \footnote{\cite{carroll2003macroeconomic}, for instance, uses median professional forecasts as an approximate of the ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.
-The monthly data of SCE allows an analysis in a higher frequency but for a shorter period 2013-2019.
-
-	As technology shock can only be recovered from quarterly time series of output, I only present results using oil price shock and monetary policy shocks in Figure \ref{SCE_IR}.
+The monthly data of SCE allows analysis in a higher frequency but for a shorter period 2013-2019.
+
+	As technology shock can only be recovered from the quarterly time series of output, I only present results using oil price shock and monetary policy shocks in Figure \ref{SCE_IR}.
 The responses to oil price shocks, target surprise and path surprise are plotted in column 1, 2 and 3, respectively.
@@
 	Estimated in higher frequency, the response to target surprise is on average 0.25 percentage points and statistically significant in $10\%$ level.
-This confirms the wide practice of the literature that identifies monetary non-neutrality using high frequency data.
+This confirms the wide practice of the literature that identifies monetary non-neutrality using high-frequency data.
 In contrast, the inflation responses to path surprise are not significant.
@@
 	This section presents one major additional insight in addition to \cite{coibion2012can}: expectation rigidity is dependent on the type of shock.
-In particular, professional forecasters are slow in digesting oil and technology shock to resolve disagreements and reduce forecast error while react to monetary policy shocks relatively more efficient.
+In particular, professional forecasters are slow in digesting oil and technology shock to resolve disagreements and reduce forecast error while reacting to monetary policy shocks relatively more efficient.
 This is the easiest seen in the non-response or instantaneous response if any of forecast error and disagreements to monetary policy shocks.
@@
 $\omega_t$ in Equation \ref{AR_process}.
-It is true that the distinction of public and private signals within NI provides one possibility of reconciling difference in response to shocks.
-If we interpret different ``shocks'' considered here as noisy signals instead of shocks to fundamental variable as defined in Equation \ref{AR_process}, then the difference across ``shocks'' in their degree of publicity may account for the difference in rigidity.
+It is true that the distinction between public and private signals within NI provides one possibility of reconciling the difference in response to shocks.
+If we interpret different ``shocks'' considered here as noisy signals instead of shocks to a fundamental variable as defined in Equation \ref{AR_process}, then the difference across ``shocks'' in their degree of publicity may account for the difference in rigidity.
 But this implicitly implies redefining the framework presented in this paper.
@@
 
-	Second, rigidity of expectation from either inattention or under-reaction due to noisiness of the signals implies agents do not revise forecasts as efficiently as they do in FIRE in the face of new information.
+	Second, the rigidity of expectation from either inattention or under-reaction due to noisiness of the signals implies agents do not revise forecasts as efficiently as they do in FIRE in the face of new information.
 This can be seen from both a sluggish pattern of forecast revision or uncertainty reduction across different vintages of the forecast.
@@
 Therefore, as a natural extension of the current analysis, one can undertake a generalized method of moment (GMM) estimation that simultaneously utilizes multi-moment restrictions to recover a better estimate of the rigidity parameters.
-This will provide a better parameter that can be used in structural macro models that build in rigidity of expectations.
+This will provide a better parameter that can be used in structural macro models that build in the rigidity of expectations.
 

### 2019-09-12 paper/Draft.tex
Added two citations in literature

@@
 %opening
-\title{Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households}
-\author{Tao Wang \footnote{Department of Economics, Johns Hopkins University; email: twang80@jhu.edu.}}
+\title{Rigidity of Expectations: Additional Evidence from Density Forecasts of the Inflation by Professionals and Households}
+\author{Tao Wang \footnote{Department of Economics, Johns Hopkins University; email: twang80@jhu.edu. }}
 
@@
 	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade.
-This has been also accompanied by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.
+This has been also accompanied by a welcoming recognition of the usefulness of surveys by macroeconomists in testing these theories empirically.
 On one hand, various theories built upon different micro-foundations produce somewhat similar macro patterns.
 For instance, the notion of expectation rigidity micro-founded by different theories mostly generates a sluggish response to new information.
-On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.
-
-	This paper extends this research effort by bringing an additional moment of forecasts into perspective, i.e.
-uncertainty.
-Specifically, in this paper, I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty.
-Second, empirically, I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey.
-Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models.
+On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecast.
+
+	This paper extends this line of effort by bringing an additional moment of forecasts into perspective, i.e.
+the uncertainty.
+Existing work that studies expectation formation utilizing survey data mostly focus on the individual and cross-sectional patterns of the mean forecast of the variable.
+But there are additional insights from the forecast uncertainty, which is only available if each surveyee is asked to assign their own perceived probabilities to a range of values of the variable\footnote{For a survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.
+See \citet{manski2018survey} for the recent development of the discussion.}.
+For instance, the dispersion of uncertainty across individual forecasters, as that of the average forecasts, are inconsistent with the benchmark full-information rational expectation as the latter assumes that agents agree on the generating process of the data and have the common knowledge of available information.
+Dynamically, across different vintages of the forecast, the revision in uncertainty is a measure of information gain or the degree of forecasting efficiency.
+Besides, the relationship between uncertainty with other moments such as forecast errors and disagreements provides a way to check if the surveyed expectations are consistent with certain theories of expectation formation.
+Using these insights, the paper finds additional evidence from uncertainty consistent with the rigidity models.
 In the same time, the degree of rigidity appears to be shock-specific and bears the difference between households and professional forecasters.
 
-	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of values of the variable of forecast\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.}.
-With density forecasts,  the variance of the individual forecast can be estimated as an indicator of the uncertainty.
-Across different vintages of the forecast, the revision in uncertainty is a direct measure of information gain or the degree of forecasting efficiency.
-Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely examined by the literature, such as forecast errors and disagreements provide many insights as to how the agent's expectation actually work.
+	There are three major contributions of this paper.
+On the theoretical side, I explicitly derive the prediction of various theories of expectation formation about the dynamics of uncertainty.
+For instance,  different theories that entail rigidities in incorporating new information predict the inefficiency in forecast revisions.
+This paper shows that this inefficiency can not only be seen in the average forecast, but also in the forecast uncertainty.
+This imposes additional restrictions on parametric configurations that produce the degree of rigidity seen in the data.
+Specifically, I find that the configurations of parameters in sticky expectation models are more realistic than that in noisy information theories.
+
+	On the empirical side, the contribution is that we provide additional tests of the null of full-information rational expectation using the revision of uncertainty.
+I first replicate the results of tests based on forecast errors using microdata of households and professionals following the existing literature.
+Then, I undertake autoregression-based tests for revisions in mean forecasts and uncertainty, respectively.
+The new result from this paper is that the revision in uncertainty has a serial correlation that is not consistent with the level of forecast efficiency predicted by rational expectation.
+This provides an additional result that rejects the null of the rational expectation hypothesis.
+
+	In addition, using externally identified shocks to inflation, i.e.
+productivity shocks, oil price shocks, and monetary policy shocks, I find evidence that the degree of rigidity is shock-specific.
+In particular, professionals seem to be responsive to monetary policy shocks, while households are more responsive to oil price shocks.
+Unlike testing the null-hypothesis, the externally identified shocks allow us to look into the dynamic impulse responses of different moments of expectations to the particular shock.
+This can be directly compared with the predictions of the theories.
+I follow the framework by \citet{coibion2012can} while making two variations.
+First, I do not only examine the dynamics of forecast error, disagreement, but also the forecast uncertainty.
+Second, I include two monetary policy shocks, the shocks to current federal fund rates and future path of the federal funds rate.
 
 	This paper is related to four strands of literature.
-First, the recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data.
+First, it is realted to a series of empirical work directly testing and evaluating the various theories on expectations theories using survey data.
 For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}.
@@
 The uncertainty about future $y$ simply comes from uncertainty about unrealized shocks between $t$ and $t+h$.
-With the same model in mind (Equation \ref{AR_process}) and the same information $y_t$, everyone's uncertainty is equal to the weighted sum of the future volatility before its realization.
-(Equation \ref{VarREIndPop}).
+With the same model in mind (Equation \ref{AR_process}) and the same information $y_t$, everyone's uncertainty is equal to the weighted sum of the future volatility before its realization (Equation \ref{VarREIndPop}).
 In FIRE, there are neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}.
@@
 
-	It is easy to show that the average forecast errors are serially correlated(Equation \ref{FESEPop}).
+	It is easy to show that the average forecast errors are serially correlated (Equation \ref{FESEPop}).
 For double-checking, setting $\lambda=1$, SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.
@@
 	Although the sheer magnitudes of the differences between professionals' moments and those of households are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency.
-Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty against realized inflation,  forecast errors, and disagreements in the first, second and third rows, respectively.
+Figure \ref{InfVar}, \ref{FEVar}, and \ref{DisgVar} plot the population uncertainty against realized inflation,  forecast errors, and disagreements in the first, second and third rows, respectively.
 
@@
 
-	The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between size of the forecast error and uncertainty.
+	Figure \ref{FEVar} looks into the relationship between size of the forecast error and uncertainty.
 Although according to our benchmark framework in Section \ref{theory}, there is no mathematical correlation between the size of the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex-ante uncertainty implies bigger ex post forecast errors.
@@
 
-	The last row of Figure \ref{UnceratitnyOtherMoments} examines the relationship between disagreement and uncertainty.
+	Figure \ref{DisgVar} examines the relationship between disagreement and uncertainty.
 Many empirical literature in macroeconomics use disagreements and uncertainty as if they are similar concepts\footnote{For instance, \citet{bachmann2013uncertainty} used ex-ante disagreement and ex-post forecast errors as two measures of uncertainty and find that both uncertainty indicators lead to a reduction in real economic activity.}.
 Such confusion in practice is partly due to the difficulty of finding appropriate measures of uncertainty in the first place.
-But as we have presented in \ref{theory}, the two are concepts with distinct statistical definitions.
-The empirical pattern of the two,  as shown in the plots, also confirms that the two are different objects.
+But as we have presented in \ref{theory}, the two are concepts with distinct statistical definitions.\footnote {This point was made very clearly by \citet{zarnowitz1987consensus}.
+\citet{manski2018survey} also points out many empirical work has confused the dispersion with uncertainty.} The empirical pattern of the two,  as shown in the plots, also confirms that the two are different objects.
 The correlation coefficients of the two turn out to be negative, -0.31 and -0.37 for SPF forecasts.
@@
 75 percentile forecast increases from 1\% to 2\%).
-\footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in the bottom row of Figure \ref{UncertaintyOtherMoments} actually exhibits a gradual decline.
+\footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in Figure \ref{DisgVar} actually exhibits a gradual decline.
 } This is consistent with the observation in the top left two graphs of Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flattened.
@@
 		\caption{Uncertainty and Other Moments}
-		\label{UncertaintyOtherMoments}
 	\end{figure}
@@
 
-	\section{Shock-based Estimates of Expectation Rigidity }\label{ShockBased}
-
-	\citet{coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.
-Unlike the time series regressions that test null hypotheses of FIRE in the previous section, this approach allows a more straightforward comparison between the empirical evidence from surveys and the theoretical predictions illustrated in Figure \ref{ir_pop}.
-The difficulty of this approach lies in identifying a shock $\omega_t$ that is a pure innovation to inflation at time $t$.
-
 	(1) Technology shock is identified from a three-variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts.
@@
 
-	\subsection{Replicating \citet{coibion2012can}}
+	\subsection{Forecast errors and disagreement}
 
@@
 
-	As to the households forecast, the starkly wider confidence band across shocks and moments seen in Figure \ref{SCE_IR} are not that surprising given the wide dispersion of the forecasts moments of a dramatically larger magnitude seen in Figure \ref{UncertaintyOtherMoments}.
+	As to the households forecast, the starkly wider confidence band across shocks and moments seen in Figure \ref{SCE_IR} are not that surprising given the wide dispersion of the forecasts moments of a dramatically larger magnitude seen in Figure \ref{IQR_Unceratitny}.
 

### 2019-10-16 workingfolder/python/DoEstimationWithData.py
back to the stage where NI simulator has not been written but codes for SE is confirmed.

@@ -174,7 +174,7 @@ SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']].dropna(how='any')
 # + {"code_folding": []}
 ## Combine expectation data and real-time data 
 
-SPF_est = pd.concat([SPFCPI,real_time_inf,InfQ['Inf1y_CPICore']], join='inner', axis=1)
+SPF_est = pd.concat([SPFCPI,real_time_inf,InfQ['Inf1y_CPICore'],InfQ['Inf1yf_CPICore']], join='inner', axis=1)
 SCE_est = pd.concat([SCECPI,real_time_inf,InfM['Inf1yf_CPIAU']], join='inner', axis=1)
 
 # +
@@ -201,7 +201,7 @@ xx = plt.figure()
 SPF_est[['RTCPI','Inf1y_CPICore']].plot()
 plt.title('Current vintage and real-time Core CPI Inflation')
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## realized 1-year-ahead inflation
 realized_CPIC = np.array(SPF_est['Inf1yf_CPICore'])
 realized_CPI = np.array(SCE_est['Inf1yf_CPIAU'])
@@ -233,7 +233,7 @@ process_paraQ_est = {'rho':rhoQ_est,
 SE_model = se(real_time = real_time,
               history = history_Q,
               process_para = process_paraQ_est)
-SE_model.moments = ['Forecast','Disg','Var']
+SE_model.moments = ['Forecast','FE','Disg']
 SE_model.GetRealization(realized_CPIC)
 SE_model.GetDataMoments(data_moms_dct)
 SE_model.ParaEstimate()
@@ -242,7 +242,7 @@ SE_model.ParaEstimate()
 lbd_est_SPF = SE_model.para_est
 lbd_est_SPF
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## SE estimation for SCE
 real_time = np.array(SCE_est['RTCPI'])
 history_M = historyM['RTCPI']
@@ -255,7 +255,7 @@ process_paraM_est = {'rho':rhoM_est,
 SE_model2 = se(real_time = realized_CPI,
                history = history_M,
                process_para = process_paraM_est)
-SE_model2.moments = ['Forecast','Disg','Var']
+SE_model2.moments = ['Forecast','FE','Disg']
 SE_model2.GetRealization(realized_CPI)
[…]

### 2019-10-16 workingfolder/python/GMMEst-Test.py

@@ -76,7 +76,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [0, 1, 5]}
+# + {"code_folding": [0, 5]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -126,7 +126,7 @@ process_para = {'rho':rho,
 xxx = AR1_simulator(rho,sigma,100)
 
 
-# + {"code_folding": [0, 2, 13, 16, 27]}
+# + {"code_folding": [2, 13, 27]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -150,7 +150,7 @@ class RationalExpectation:
         shocks = np.random.randn(n)*sigma
         realized = np.zeros(n)
         for i in range(n):
-            cum_shock = sum([rho**h*shocks[i+h] for h in range(self.horizon)])
+            cum_shock = sum([rho**h*shocks[h] for h in range(self.horizon)])
             realized[i] = rho**self.horizon*self.real_time[i] + cum_shock
         self.realized = realized        
         
@@ -197,7 +197,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 1, 2, 21, 25, 36, 52, 71, 76, 107, 111, 134, 156, 161, 168, 175]}
+# + {"code_folding": [1, 21, 36, 52, 71, 76, 132, 154, 159, 166, 173]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -230,7 +230,7 @@ class StickyExpectation:
         shocks = np.random.randn(n)*sigma
         realized = np.zeros(n)
         for i in range(n):
-            cum_shock = sum([rho**h*shocks[i+h] for h in range(self.horizon)])
+            cum_shock = sum([rho**h*shocks[h] for h in range(self.horizon)])
             realized[i] = rho**self.horizon*self.real_time[i] + cum_shock
         self.realized = realized
         
@@ -307,12 +307,10 @@ class StickyExpectation:
             for j in range(n_history):
                 if any([x for x in range(j) if update_or_not[i,j-x] == True]):
                     most_recent_when[i,j] = min([x for x in range(j) if update_or_not[i,j-x] == True])
[…]

### 2019-10-16 workingfolder/python/DoEstimationWithData.py
Both NI and SE now take history instead of real time data for estimation

@@ -219,7 +219,7 @@ exp_data_SCE = SCE_est[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']]
 exp_data_SCE.columns = ['Forecast','FE','Disg','Var']
 data_moms_dct_SCE = dict(exp_data_SCE)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## SE estimation for SPF
 real_time = np.array(SPF_est['RTCPI'])
 history_Q = historyQ['RTCPICore']
@@ -271,11 +271,11 @@ print("SCE: "+str(lbd_est_SCE))
 ## quarterly survey of 1-year-ahead forecast
 ## real-time data is yearly 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## compare the data with estimation for SPF
 SE_model.ForecastPlotDiag()
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## compare the data with estimation for SPF
 SE_model2.ForecastPlotDiag()
 
@@ -288,7 +288,10 @@ data_moms_dct = data_moms_dct_SPF
 process_paraQ_est = {'rho':rhoQ_est,
                     'sigma':sigmaQ_est}
 
-NI_model = ni(real_time = real_time,process_para = process_paraQ_est,moments = ['Forecast','FE','Disg'])
+NI_model = ni(real_time = real_time,
+              history = history_Q,
+              process_para = process_paraQ_est,
+              moments = ['Forecast','FE','Disg'])
 NI_model.SimulateSignals()
 NI_model.GetRealization(realized_CPIC)
 NI_model.GetDataMoments(data_moms_dct)
@@ -297,8 +300,8 @@ NI_model.ParaEstimate(para_guess = np.array([0.01,0.01,0.01]))
 sigmas_est_SPF = NI_model.para_est
 # -
 
-plt.plot(NI_model.signals.T,'--')
-plt.plot(NI_model.real_time,'ro',label='real_time')
+plt.plot(NI_model.signals_pb,'--',label='public signals')
+plt.plot(NI_model.history,'r*',label='history')
 plt.legend()
 
 # + {"code_folding": [0]}
@@ -314,7 +317,9 @@ data_moms_dct = data_moms_dct_SCE
 process_paraM_est = {'rho':rhoM_est,
                     'sigma':sigmaM_est}
 
-NI_model2 = ni(real_time = real_time,process_para = process_paraM_est)
[…]

### 2019-10-16 workingfolder/python/GMMEst-Test.py

@@ -424,7 +424,7 @@ NI_para_default = {'sigma_pb':0.1,
                   'var_init':0.01}
 
 
-# + {"code_folding": [0, 3, 74, 98, 158, 183, 188, 194, 203]}
+# + {"code_folding": [74, 98, 158, 183, 188, 194, 203]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:
@@ -720,7 +720,7 @@ print(est_av)
 PL_para_default = SE_para_default
 
 
-# + {"code_folding": [33, 55]}
+# + {"code_folding": [2, 33, 55]}
 ### Paramter Learning(PL) class 
 
 class ParameterLearning:

### 2019-10-16 workingfolder/python/GMMEst.py

@@ -126,7 +126,7 @@ process_para = {'rho':rho,
 xxx = AR1_simulator(rho,sigma,100)
 
 
-# + {"code_folding": [0, 2, 13, 16, 27]}
+# + {"code_folding": [0, 2, 27]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -150,7 +150,7 @@ class RationalExpectation:
         shocks = np.random.randn(n)*sigma
         realized = np.zeros(n)
         for i in range(n):
-            cum_shock = sum([rho**h*shocks[i+h] for h in range(self.horizon)])
+            cum_shock = sum([rho**h*shocks[h] for h in range(self.horizon)])
             realized[i] = rho**self.horizon*self.real_time[i] + cum_shock
         self.realized = realized        
         
@@ -197,7 +197,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 1, 2, 21, 25, 36, 52, 71, 76, 107, 111, 134, 156, 161, 168, 175]}
+# + {"code_folding": [0, 2, 21, 36, 52, 71, 76, 82, 107, 111, 134, 156, 161, 168, 175]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -230,7 +230,7 @@ class StickyExpectation:
         shocks = np.random.randn(n)*sigma
         realized = np.zeros(n)
         for i in range(n):
-            cum_shock = sum([rho**h*shocks[i+h] for h in range(self.horizon)])
+            cum_shock = sum([rho**h*shocks[h] for h in range(self.horizon)])
             realized[i] = rho**self.horizon*self.real_time[i] + cum_shock
         self.realized = realized
         
@@ -407,7 +407,7 @@ mom_sim_and_pop = ForecastPlotDiag(mom_dct,mom_sim_dct)
 
 # + {"code_folding": []}
 ### fake data moments 
-data_moms_dct_fake = SE_instance.Forecaster()
+#data_moms_dct_fake = SE_instance.Forecaster()
 
 # + {"code_folding": []}
 #SE_instance.ForecastPlot()
@@ -423,23 +423,25 @@ data_moms_dct_fake = SE_instance.Forecaster()
 # + {}
 #SE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [0]}
[…]

### 2019-10-17 workingfolder/python/DoEstimationWithData.py
created a seperate developing NI_sim_dev that to draft NI-sim codes. Disg needs to be debugging

@@ -33,7 +33,7 @@ from GMMEst import RationalExpectation as re
 from GMMEst import StickyExpectation as se
 from GMMEst import NoisyInformation as ni
 from GMMEst import ParameterLearning as pl
-from GMMEst import AR1_simulator
+from GMMEst import AR1_simulator, ForecastPlotDiag, ForecastPlot
 
 # + {"code_folding": [0]}
 ## some parameters 
@@ -208,7 +208,7 @@ realized_CPI = np.array(SCE_est['Inf1yf_CPIAU'])
 SPF_est['Inf1yf_CPICore'].plot()
 plt.title('Realized 1-year-ahead Core CPI Inflation')
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## preparing for estimation 
 
 exp_data_SPF = SPF_est[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var']]
@@ -242,7 +242,7 @@ SE_model.ParaEstimate()
 lbd_est_SPF = SE_model.para_est
 lbd_est_SPF
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## SE estimation for SCE
 real_time = np.array(SCE_est['RTCPI'])
 history_M = historyM['RTCPI']
@@ -279,7 +279,7 @@ SE_model.ForecastPlotDiag()
 ## compare the data with estimation for SPF
 SE_model2.ForecastPlotDiag()
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## NI estimation for SPF
 
 real_time = np.array(SPF_est['RTCPI'])
@@ -304,11 +304,11 @@ plt.plot(NI_model.signals_pb,'--',label='public signals')
 plt.plot(NI_model.history,'r*',label='history')
 plt.legend()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## compare the data with estimation for SPF
 NI_model.ForecastPlotDiag()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## NI estimation for SCE
 
 real_time = np.array(SCE_est['RTCPI'])
@@ -340,14 +340,16 @@ NI_model2.ForecastPlotDiag()
 print(str(sigmas_est_SPF))
 print(str(sigmas_est_SCE))
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### simulated method of moment estimation for SPF
[…]

### 2019-10-17 workingfolder/python/GMMEst-NI_sim_dev.py

@@ -76,7 +76,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [0, 5]}
+# + {"code_folding": [0, 1, 5]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -126,7 +126,7 @@ process_para = {'rho':rho,
 xxx = AR1_simulator(rho,sigma,100)
 
 
-# + {"code_folding": [2, 13, 27]}
+# + {"code_folding": [0, 2, 27]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -197,7 +197,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [1, 21, 36, 52, 71, 76, 132, 154, 159, 166, 173]}
+# + {"code_folding": [0, 2, 21, 36, 52, 71, 76, 107, 134, 156, 161, 168, 175]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -307,10 +307,12 @@ class StickyExpectation:
             for j in range(n_history):
                 if any([x for x in range(j) if update_or_not[i,j-x] == True]):
                     most_recent_when[i,j] = min([x for x in range(j) if update_or_not[i,j-x] == True])
+                    nowcasts_to_burn[i,j] = history[j - most_recent_when[i,j]]*rho**most_recent_when[i,j]
+                    Vars_to_burn[i,j] = hstepvar(most_recent_when[i,j]+horizon,sigma,rho)
                 else:
                     most_recent_when[i,j] = j
-                nowcasts_to_burn[i,j] = history[j - most_recent_when[i,j]]*rho**most_recent_when[i,j]
-                Vars_to_burn[i,j]= hstepvar((most_recent_when[i,j]+horizon),sigma,rho)
+                    nowcasts_to_burn[i,j] = history[j - most_recent_when[i,j]]*rho**most_recent_when[i,j]
+                    Vars_to_burn[i,j]= hstepvar((most_recent_when[i,j]+horizon),sigma,rho)
         
         ## burn initial forecasts since history is too short 
         nowcasts = np.array( nowcasts_to_burn[:,n_burn:] )
@@ -383,26 +385,29 @@ class StickyExpectation:
             plt.plot(np.array(self.data_moms_dct[val]),'*',label='data:'+ val)
[…]

### 2019-10-17 workingfolder/python/GMMEst.py

@@ -76,7 +76,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [0, 1, 5]}
+# + {"code_folding": [1, 5]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -197,7 +197,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 21, 36, 52, 71, 76, 82, 107, 111, 134, 156, 161, 168, 175]}
+# + {"code_folding": [2, 21, 36, 52, 71, 76, 107, 134, 156, 161, 168, 175]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -424,12 +424,12 @@ mom_sim_and_pop = ForecastPlotDiag(mom_dct,mom_sim_dct)
 #SE_instance.ForecastPlotDiag()
 
 # + {"code_folding": []}
-NI_para_default = {'sigma_pb':0.1,
+NI_para_default = {'sigma_pb':0.00000001,
                   'sigma_pr':0.1,
-                  'var_init':0.1}
+                  'var_init':1}
 
 
-# + {"code_folding": [3, 36, 97, 142]}
+# + {"code_folding": [2, 3, 102, 147]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:
@@ -491,30 +491,33 @@ class NoisyInformation:
         var_init = self.exp_para['var_init']
         sigma_v = np.asmatrix([[sigma_pb**2,0],[0,sigma_pr**2]])
         horizon = self.horizon      
-        s = self.signals
+        signals = self.signals
         nb_s=len(self.signals) ## # of signals 
         H = np.asmatrix ([[1,1]]).T
         Pkalman = np.zeros([n_history,nb_s])
         nowcast_to_burn = np.zeros(n_history)
-        nowcast_to_burn[0] = real_time[0]
+        nowcast_to_burn[0] = history[0]
         nowvar_to_burn = np.zeros(n_history)
         nowvar_to_burn[0] = var_init
         Var_to_burn = np.zeros(n_history)
      
         ## forecast moments
-        infoset = s
+        infoset = signals
         
         for t in range(n_history-1):
[…]

### 2019-10-17 paper/Draft.tex
NLP tasks put all articles info in a dataframe
Corrected disagreement fomula for NI model in the draft. But codes on estimation from simulated data remains debugging.

@@
 	This paper is related to four strands of literature.
-First, it is realted to a series of empirical work directly testing and evaluating the various theories on expectations theories using survey data.
+First, it is realted to a series of empirical work directly testing and evaluating  various theories on expectations formation using survey data.
 For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}.
@@
 	NI also predicts non-zero disagreement in the presence of private signals.
-The behavior of disagreement across agents come from the difference in realized private signals.
+The behavior of disagreement across agents come from the difference in the entire histories of realized private signals.
 Specifically, it is equal to the following.
@@
 		\begin{aligned}
-			\overline {Disg}_{t+h|t} = \rho^{2h} P^2_\xi \sigma^2_\xi  
+			\overline {Disg}_{t+h|t} =  (1-PH) \overline {Disg}_{t+h|t-1} + \rho^{2h} P^2_\xi \sigma^2_\xi 
 		\end{aligned}
@@
 	The implications for disagreement are straightforward.
-First, the disagreement decrease with the forecast horizon due to discounting.
-Second, the disagreement depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
-Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.
+First, the serial correlation between disagreement is proportional to the rigidity parameter $(1-PH)$ and, similar to SE, it increases with the rigidity parameter $P$ in this model.
+Second, the disagreement decrease with the forecast horizon due to discounting.
+Third, the disagreement depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
 

### 2019-10-17 workingfolder/python/GMMEst-NI_sim_dev.py

@@ -95,12 +95,12 @@ def ForecastPlot(test):
         plt.legend(loc=1)
     return x
         
-def ForecastPlotDiag(test,data):
+def ForecastPlotDiag(test,data,legends=['model','data']):
     x = plt.figure(figsize=([3,13]))
     for i,val in enumerate(test):
         plt.subplot(4,1,i+1)
-        plt.plot(test[val],label='model:'+ val)
-        plt.plot(np.array(data[val]),label='data:'+ val)
+        plt.plot(test[val],label= legends[0]+ ': ' +val)
+        plt.plot(np.array(data[val]),label=legends[1] +': '+ val)
         plt.legend(loc=1)
     return x
         
@@ -423,13 +423,13 @@ mom_sim_and_pop = ForecastPlotDiag(mom_dct,mom_sim_dct)
 # + {}
 #SE_instance.ForecastPlotDiag()
 
-# + {"code_folding": []}
-NI_para_default = {'sigma_pb':0.1,
-                  'sigma_pr':0.1,
+# + {"code_folding": [0]}
+NI_para_default = {'sigma_pb':0.5,
+                  'sigma_pr':0.5,
                   'var_init':1}
 
 
-# + {"code_folding": [2, 3, 21, 25, 31, 36, 47, 74, 78, 86]}
+# + {"code_folding": [0, 3, 21, 25, 31, 36, 47, 76, 104, 138, 168, 193, 198, 204, 213]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:
@@ -492,14 +492,16 @@ class NoisyInformation:
         sigma_v = np.asmatrix([[sigma_pb**2,0],[0,sigma_pr**2]])
         horizon = self.horizon      
         signals = self.signals
-        nb_s=len(self.signals) ## # of signals 
+        nb_s = len(self.signals) ## # of signals 
         H = np.asmatrix ([[1,1]]).T
         Pkalman = np.zeros([n_history,nb_s])
         nowcast_to_burn = np.zeros(n_history)
-        nowcast_to_burn[0] = real_time[0]
+        nowcast_to_burn[0] = history[0]
         nowvar_to_burn = np.zeros(n_history)
         nowvar_to_burn[0] = var_init
         Var_to_burn = np.zeros(n_history)
+        nowdisg_to_burn = np.zeros(n_history)
+        nowdisg_to_burn[0] = sigma_pr**2 
      
[…]

### 2019-10-17 workingfolder/python/GMMEst.py

@@ -429,7 +429,7 @@ NI_para_default = {'sigma_pb':0.00000001,
                   'var_init':1}
 
 
-# + {"code_folding": [2, 3, 102, 147]}
+# + {"code_folding": [3, 47, 102]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:

### 2019-10-17 workingfolder/python/Theories.py

@@ -309,7 +309,7 @@ for t in range(1,T):
     #PopVarSE[t] = sum( [λ*(1-λ)**t*IndVarRE[s] for s in range(t)])
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": [34]}
 ## Noisy information(NI) 
 
 def NI(T,y,sigma_pb=1,sigma_pr=1):

### 2019-10-17 workingfolder/python/Theories.py
Corrected the codes in Theories notebook on NI Disagreement

@@ -309,7 +309,7 @@ for t in range(1,T):
     #PopVarSE[t] = sum( [λ*(1-λ)**t*IndVarRE[s] for s in range(t)])
 
 
-# + {"code_folding": [34]}
+# + {"code_folding": []}
 ## Noisy information(NI) 
 
 def NI(T,y,sigma_pb=1,sigma_pr=1):
@@ -355,7 +355,7 @@ def NI(T,y,sigma_pb=1,sigma_pr=1):
         PopExpNI[t+1]=ρ**(h-t)*((1-Pkalman[t+1]*H)*PopExpNI[t]+Pkalman[t+1,0]*s[0,t+1])
         #print('Kalman gain from public signal is '+ str(Pkalman[t+1,1]))
         #print('Kalman gain from private signal is '+str(Pkalman[t+1,0]))
-        PopDisgNI[t+1]=ρ**(2*(h-t))*(Pkalman[t+1,1]**2)*sigma_xi**2
+        PopDisgNI[t+1]=(1-Pkalman[t+1]*H)**2*PopDisgNI[t] +  ρ**(2*(h-t))*(Pkalman[t+1,1]**2)*sigma_xi**2
         RigidityNI[t+1] = ρ**(h-t)*(1-Pkalman[t+1]*H)
 
     ## individual forecast error

### 2019-10-17 workingfolder/python/GMMEst-NI_sim_dev.py
Wrote seperately estimation functions using simulated model moments instead of general moments. But the estimator did not work directly.

@@ -34,7 +34,7 @@ import copy as cp
 from scipy.stats import bernoulli
 
 
-# + {"code_folding": [0, 1]}
+# + {"code_folding": []}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -43,7 +43,8 @@ def Estimator(obj_func,
     Inputs
     ------
     - moments: a function of the rigidity model parameter  
-    - method: method of optimization 
+    - method: method of optimization, i.e. 
+         -  'L-BFGS-B', bounds=((1e-10, None), (1e-10, None))
     
     Outputs
     -------
@@ -197,7 +198,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 21, 36, 52, 71, 76, 107, 134, 156, 161, 168, 175]}
+# + {"code_folding": [0, 2, 21, 25, 36, 52, 71, 76, 82, 131, 154, 183, 204, 226, 231, 238, 245, 252]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -307,6 +308,55 @@ class StickyExpectation:
             for j in range(n_history):
                 if any([x for x in range(j) if update_or_not[i,j-x] == True]):
                     most_recent_when[i,j] = min([x for x in range(j) if update_or_not[i,j-x] == True])
+                else:
+                    most_recent_when[i,j] = j
+                nowcasts_to_burn[i,j] = history[j - most_recent_when[i,j]]*rho**most_recent_when[i,j]
+                Vars_to_burn[i,j]= hstepvar((most_recent_when[i,j]+horizon),sigma,rho)
+        
+        ## burn initial forecasts since history is too short 
+        nowcasts = np.array( nowcasts_to_burn[:,n_burn:] )
+        forecasts = rho**horizon*nowcasts
+        Vars = np.array( Vars_to_burn[:,n_burn:])
+        
+        ## compuate population moments
+        forecasts_mean = np.mean(forecasts,axis=0)
+        forecasts_var = np.var(forecasts,axis=0)
+        FEs_mean = forecasts_mean - self.realized
+        Vars_mean = np.mean(Vars,axis=0) ## need to change 
+        
+        self.forecast_moments_sim = {"Forecast":forecasts_mean, 
+                "FE":FEs_mean,
+                "Disg":forecasts_var,
+                "Var":Vars_mean}
+        return self.forecast_moments_sim
+    
[…]

### 2019-10-17 workingfolder/python/GMMEst-Test.py

@@ -197,7 +197,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [1, 21, 36, 52, 71, 76, 132, 154, 159, 166, 173]}
+# + {"code_folding": [21, 36, 52, 71, 76, 82, 132, 154, 159, 166, 173]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -383,9 +383,9 @@ class StickyExpectation:
             plt.plot(np.array(self.data_moms_dct[val]),'*',label='data:'+ val)
             plt.legend(loc=1)
 
-# + {"code_folding": [0, 5]}
+# + {"code_folding": [5]}
 ## test of ForecasterbySim
-xx_history = AR1_simulator(rho,sigma,500)
+xx_history = AR1_simulator(rho,sigma,100)
 xx_real_time = xx_history[50:]
 
 ### create a SE instance using fake real time data 
@@ -393,14 +393,13 @@ SE_instance = StickyExpectation(real_time = xx_real_time,
                                 history = xx_history)
 SE_instance.SimulateRealization()
 
-'''
+
 ### simulate a realized series 
 mom_dct =  SE_instance.Forecaster()
-mom_sim_dct = SE_instance.ForecasterbySim(n_sim=1000)
+mom_sim_dct = SE_instance.ForecasterbySim(n_sim=100)
 mom_sim_and_pop = ForecastPlotDiag(mom_dct,mom_sim_dct)
-'''
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### fake data moments 
 data_moms_dct_fake = SE_instance.Forecaster()
 

### 2019-10-17 workingfolder/python/GMMEst.py

@@ -76,7 +76,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [1, 5]}
+# + {"code_folding": [0, 1, 5]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -197,7 +197,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [2, 21, 36, 52, 71, 76, 107, 134, 156, 161, 168, 175]}
+# + {"code_folding": [0, 2, 21, 36, 52, 71, 76, 107, 134, 156, 161, 168, 175]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -424,7 +424,7 @@ mom_sim_and_pop = ForecastPlotDiag(mom_dct,mom_sim_dct)
 #SE_instance.ForecastPlotDiag()
 
 # + {"code_folding": []}
-NI_para_default = {'sigma_pb':0.00000001,
+NI_para_default = {'sigma_pb':0.1,
                   'sigma_pr':0.1,
                   'var_init':1}
 

### 2019-10-17 workingfolder/python/GMMEst-NI_sim_dev.py
RE now has estimation function as well. It estimates process parameters using expectation data moments. No expectation parameter needs to be  estimated itself.

@@ -34,7 +34,7 @@ import copy as cp
 from scipy.stats import bernoulli
 
 
-# + {"code_folding": []}
+# + {"code_folding": [1]}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -122,21 +122,23 @@ sigma = 0.1
 process_para = {'rho':rho,
                 'sigma':sigma}
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### create fake real-time data 
 xxx = AR1_simulator(rho,sigma,100)
 
 
-# + {"code_folding": [0, 2, 27]}
+# + {"code_folding": [0, 1, 2, 15, 18, 29, 52, 57, 65, 75, 79, 86, 93, 94, 100]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
                  real_time,
+                 history,
                  horizon=1,
                  process_para = process_para,
                  exp_para = {},
-                 moments=['Forecast','Disg','Var']):
+                 moments=['Forecast','FE','Disg','Var']):
         self.real_time = real_time
+        self.history = history
         self.horizon = horizon
         self.process_para = process_para
         self.moments = moments
@@ -162,7 +164,6 @@ class RationalExpectation:
         sigma =self.process_para['sigma']
         
         ## parameters
-        max_back = self.max_back
         real_time = self.real_time
         horizon = self.horizon
         
@@ -178,27 +179,92 @@ class RationalExpectation:
                                  "Disg":Disg,
                                  "Var":Var}
         return self.forecast_moments
+        
+    def RE_EstObjfunc(self,
+                      process_para):
+        """
+        input
+        -----
+        process_para: the parameters of process to be estimated. 
+           No expectation parameters because rational expectation
+        
+        output
+        -----
+        the objective function to minmize
+        """
+        moments = self.moments
+        re_process_para = {'rho':process_para[0],
+                  'sigma':process_para[1]}
[…]

### 2019-10-18 workingfolder/python/GMMEst-Test.py
A few important changes. 1. Now the ParaEstimator for RE, SE and NI can take arguments about algorithms. 2. ParaEstSim seems to work with TNC algorithms at least for SE. But the estimates seem to be still problem. 3. Delete GMMEst_test notebook. 4. Updated GMMEst notebook with the most recent developments. 5. Paraest now returns estimates. 6. Need to debug disg for NI Sim still.

@@ -1,848 +1,0 @@
-# ---
-# jupyter:
-#   jupytext:
-#     formats: ipynb,py:light
-#     text_representation:
-#       extension: .py
-#       format_name: light
-#       format_version: '1.4'
-#       jupytext_version: 1.2.3
-#   kernelspec:
-#     display_name: Python 3
-#     language: python
-#     name: python3
-# ---
-
-# ## GMM Estimation of Model Parameters of Expectation Formation
-#
-# - This notebook includes functions that estimate the parameter of rigidity for different models
-# - It allows for flexible choices of moments to be used, forecast error, disagreement, and uncertainty, etc. 
-# - It includes 
-#   - A general function that implements the estimation using the minimum distance algorithm. 
-#   - Model-specific functions that take real-time data and process parameters as inputs and produces forecasts and moments as outputs. It is model-specific because different models of expectation formation bring about different forecasts. 
-#   - Auxiliary functions that compute the moments as well as the difference of data and model prediction, which will be used as inputs for GMM estimator. 
-
-# ### 1. Estimation algorithms 
-
-from scipy.optimize import minimize
-import numpy as np
-import matplotlib.pyplot as plt
-import pandas as pd
-import statsmodels.api as sm
-from statsmodels.tsa.api import AR
-import copy as cp 
-from scipy.stats import bernoulli
-
-
-# + {"code_folding": [0, 1]}
-# a general-purpose estimating function of the parameter
-def Estimator(obj_func,
-              para_guess,
-              method='CG'):
-    """
-    Inputs
-    ------
-    - moments: a function of the rigidity model parameter  
-    - method: method of optimization 
-    
-    Outputs
-    -------
-    - parameter: an array of estimated parameter
-    """
-    
-    parameter = minimize(obj_func,
-                         x0 = para_guess,
-                         method=method,
-                         options={'disp': True})['x']
-    return parameter 
-
-
-# + {"code_folding": [0, 1]}
-# a function that prepares moment conditions. So far the loss being simply the norm of the difference
-def PrepMom(model_moments,
-            data_moments):
-    """
-    Inputs
-    -----
[…]

### 2019-10-18 workingfolder/python/GMMEst.py

@@ -34,16 +34,19 @@ import copy as cp
 from scipy.stats import bernoulli
 
 
-# + {"code_folding": [0, 1]}
+# + {"code_folding": [1]}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
-              method='CG'):
+              method='CG',
+              bounds = None,
+              options = {'disp': True}):
     """
     Inputs
     ------
     - moments: a function of the rigidity model parameter  
-    - method: method of optimization 
+    - method: method of optimization, i.e. 
+         -  'L-BFGS-B', bounds=((1e-10, None), (1e-10, None))
     
     Outputs
     -------
@@ -52,12 +55,13 @@ def Estimator(obj_func,
     
     parameter = minimize(obj_func,
                          x0 = para_guess,
-                         method=method,
-                         options={'disp': True})['x']
+                         method = method,
+                         bounds = bounds,
+                         options = options)['x']
     return parameter 
 
 
-# + {"code_folding": [0, 1]}
+# + {"code_folding": [1]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -95,12 +99,12 @@ def ForecastPlot(test):
         plt.legend(loc=1)
     return x
         
-def ForecastPlotDiag(test,data):
+def ForecastPlotDiag(test,data,legends=['model','data']):
     x = plt.figure(figsize=([3,13]))
     for i,val in enumerate(test):
         plt.subplot(4,1,i+1)
-        plt.plot(test[val],label='model:'+ val)
-        plt.plot(np.array(data[val]),label='data:'+ val)
+        plt.plot(test[val],label= legends[0]+ ': ' +val)
+        plt.plot(np.array(data[val]),label=legends[1] +': '+ val)
         plt.legend(loc=1)
     return x
         
@@ -121,21 +125,19 @@ sigma = 0.1
 process_para = {'rho':rho,
                 'sigma':sigma}
 
-# + {"code_folding": [0]}
-### create fake real-time data 
-xxx = AR1_simulator(rho,sigma,100)
 
-
-# + {"code_folding": [0, 2, 27]}
+# + {"code_folding": [0, 2, 15, 18, 29, 52, 57, 65, 75, 90, 97, 98]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
                  real_time,
+                 history,
                  horizon=1,
                  process_para = process_para,
[…]

### 2019-10-18 workingfolder/python/GMMEst_dev.py

@@ -38,7 +38,9 @@ from scipy.stats import bernoulli
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
-              method='CG'):
+              method='CG',
+              bounds = None,
+              options = {'disp': True}):
     """
     Inputs
     ------
@@ -53,12 +55,13 @@ def Estimator(obj_func,
     
     parameter = minimize(obj_func,
                          x0 = para_guess,
-                         method=method,
-                         options={'disp': True})['x']
+                         method = method,
+                         bounds = bounds,
+                         options = options)['x']
     return parameter 
 
 
-# + {"code_folding": [0, 1]}
+# + {"code_folding": [1]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -122,12 +125,8 @@ sigma = 0.1
 process_para = {'rho':rho,
                 'sigma':sigma}
 
-# + {"code_folding": []}
-### create fake real-time data 
-xxx = AR1_simulator(rho,sigma,100)
 
-
-# + {"code_folding": [0, 1, 2, 15, 18, 29, 52, 57, 65, 75, 79, 86, 93, 94, 100]}
+# + {"code_folding": [0, 2, 15, 18, 29, 52, 57, 65, 75, 90, 97, 98]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -209,10 +208,14 @@ class RationalExpectation:
     
     def ParaEstimate(self,
                      para_guess = np.array([0.5,0.1]),
-                     method='CG'):
+                     method = 'CG',
+                     bounds = None,
+                     options = None):
         self.para_est = Estimator(self.RE_EstObjfunc,
                                   para_guess = para_guess,
-                                  method = method)
+                                  method = method,
+                                  bounds = bounds,
+                                  options = options)
     
     def ForecastPlot(self):
         x = plt.figure(figsize=([3,13]))
@@ -243,11 +246,10 @@ xx_real_time = xx_history[20:]
 RE_instance = RationalExpectation(real_time = xx_real_time,
                                  history = xx_history)
 
[…]

### 2019-10-21 workingfolder/python/DoEstimationWithData.py
Parameter learning model takes history as input now in GMMEst.py. NI remains to be debugged.

@@ -236,7 +236,7 @@ SE_model = se(real_time = real_time,
 SE_model.moments = ['Forecast','FE','Disg']
 SE_model.GetRealization(realized_CPIC)
 SE_model.GetDataMoments(data_moms_dct)
-SE_model.ParaEstimate()
+SE_model.ParaEstimate(options={'disp':True})
 # -
 
 lbd_est_SPF = SE_model.para_est
@@ -258,7 +258,7 @@ SE_model2 = se(real_time = realized_CPI,
 SE_model2.moments = ['Forecast','FE','Disg']
 SE_model2.GetRealization(realized_CPI)
 SE_model2.GetDataMoments(data_moms_dct)
-SE_model2.ParaEstimate()
+SE_model2.ParaEstimate(options={'disp':True})
 
 lbd_est_SCE = SE_model2.para_est
 
@@ -415,5 +415,3 @@ sigmas_est_SCE = sim_para/n_sim
 # -
 
 print(sigmas_est_SCE)
-
-

### 2019-10-21 workingfolder/python/GMMEst.py

@@ -27,7 +27,6 @@
 from scipy.optimize import minimize
 import numpy as np
 import matplotlib.pyplot as plt
-import pandas as pd
 import statsmodels.api as sm
 from statsmodels.tsa.api import AR
 import copy as cp 
@@ -238,7 +237,7 @@ class RationalExpectation:
             plt.legend(loc=1)
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### create a RE instance 
 xx_history = AR1_simulator(rho,sigma,100)
 xx_real_time = xx_history[20:]
@@ -246,7 +245,7 @@ xx_real_time = xx_history[20:]
 RE_instance = RationalExpectation(real_time = xx_real_time,
                                  history = xx_history)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### simulate a realized series 
 #RE_instance.SimulateRealization()
 
@@ -254,7 +253,7 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 #fe_moms = RE_instance.Forecaster()
 #RE_instance.ForecastPlot()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## estimate rational expectation model 
 #RE_instance.GetDataMoments(fe_moms)
 #RE_instance.moments=['Forecast','FE','Var']
@@ -271,7 +270,7 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 25, 36, 52, 71, 76, 82, 131, 154, 183, 204, 226, 243, 255, 257, 262]}
+# + {"code_folding": [2, 25, 36, 52, 71, 76, 82, 131, 154, 183, 204, 226, 243, 255, 257, 262]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -573,20 +572,20 @@ data_moms_dct_fake = SE_instance.Forecaster()
 # + {"code_folding": []}
 #SE_instance.ForecastPlot()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### feed the data moments
 SE_instance.GetDataMoments(data_moms_dct_fake)
+
 
 # + {"code_folding": []}
 #moms_sim_dct = SE_instance.ForecasterbySim(n_sim =100)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### invoke generalized estimation 
[…]

### 2019-10-22 workingfolder/python/DoEstimationWithData.py
Debugged NI class. Now simulated NI and computed NI are consistent.Also tried first round of estimation of NI.

@@ -201,14 +201,14 @@ xx = plt.figure()
 SPF_est[['RTCPI','Inf1y_CPICore']].plot()
 plt.title('Current vintage and real-time Core CPI Inflation')
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## realized 1-year-ahead inflation
 realized_CPIC = np.array(SPF_est['Inf1yf_CPICore'])
 realized_CPI = np.array(SCE_est['Inf1yf_CPIAU'])
 SPF_est['Inf1yf_CPICore'].plot()
 plt.title('Realized 1-year-ahead Core CPI Inflation')
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## preparing for estimation 
 
 exp_data_SPF = SPF_est[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var']]
@@ -219,7 +219,7 @@ exp_data_SCE = SCE_est[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']]
 exp_data_SCE.columns = ['Forecast','FE','Disg','Var']
 data_moms_dct_SCE = dict(exp_data_SCE)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## SE estimation for SPF
 real_time = np.array(SPF_est['RTCPI'])
 history_Q = historyQ['RTCPICore']
@@ -242,7 +242,7 @@ SE_model.ParaEstimate(options={'disp':True})
 lbd_est_SPF = SE_model.para_est
 lbd_est_SPF
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## SE estimation for SCE
 real_time = np.array(SCE_est['RTCPI'])
 history_M = historyM['RTCPI']
@@ -276,7 +276,7 @@ print("SCE: "+str(lbd_est_SCE))
 SE_model.ForecastPlotDiag()
 
 # + {"code_folding": [0]}
-## compare the data with estimation for SPF
+## compare the data with estimation for SCE
 SE_model2.ForecastPlotDiag()
 
 # + {"code_folding": [0]}
@@ -291,24 +291,29 @@ process_paraQ_est = {'rho':rhoQ_est,
 NI_model = ni(real_time = real_time,
               history = history_Q,
               process_para = process_paraQ_est,
-              moments = ['Forecast','FE','Disg'])
+              moments = ['Forecast','FE','Disg','Var'])
 NI_model.SimulateSignals()
[…]

### 2019-10-22 workingfolder/python/GMMEst-Dev.py

@@ -27,7 +27,6 @@
 from scipy.optimize import minimize
 import numpy as np
 import matplotlib.pyplot as plt
-import pandas as pd
 import statsmodels.api as sm
 from statsmodels.tsa.api import AR
 import copy as cp 
@@ -238,7 +237,7 @@ class RationalExpectation:
             plt.legend(loc=1)
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### create a RE instance 
 xx_history = AR1_simulator(rho,sigma,100)
 xx_real_time = xx_history[20:]
@@ -266,12 +265,12 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 #RE_instance.para_est
 #RE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## SE expectation parameters 
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 25, 36, 52, 71, 76, 82, 131, 154, 183, 204, 226, 243, 255, 257, 262]}
+# + {"code_folding": [0, 2, 25, 52, 71, 76, 82, 131, 154, 183, 204, 226, 243, 255, 257, 262]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -577,16 +576,16 @@ data_moms_dct_fake = SE_instance.Forecaster()
 ### feed the data moments
 SE_instance.GetDataMoments(data_moms_dct_fake)
 
+
 # + {"code_folding": []}
 #moms_sim_dct = SE_instance.ForecasterbySim(n_sim =100)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### invoke generalized estimation 
-SE_instance.ParaEstimate(para_guess = 0.4,
-                         method = 'BFGS',
-                         options = {'disp':True})
-SE_instance.para_est
-
+#SE_instance.ParaEstimate(para_guess = 0.4,
+#                         method = 'BFGS',
+#                         options = {'disp':True})
+#SE_instance.para_est
 
 # +
 ### invoke simulated estimation 
@@ -594,13 +593,13 @@ SE_instance.para_est
 #                            method = 'TNC',
 #                            options = {'disp':True})
 
-# +
+# + {"code_folding": []}
 #SE_instance.para_est
 
 # + {"code_folding": []}
[…]

### 2019-10-22 workingfolder/python/GMMEst.py

@@ -245,7 +245,7 @@ xx_real_time = xx_history[20:]
 RE_instance = RationalExpectation(real_time = xx_real_time,
                                  history = xx_history)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### simulate a realized series 
 #RE_instance.SimulateRealization()
 
@@ -253,7 +253,7 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 #fe_moms = RE_instance.Forecaster()
 #RE_instance.ForecastPlot()
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## estimate rational expectation model 
 #RE_instance.GetDataMoments(fe_moms)
 #RE_instance.moments=['Forecast','FE','Var']
@@ -265,12 +265,12 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 #RE_instance.para_est
 #RE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## SE expectation parameters 
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [2, 25, 36, 52, 71, 76, 82, 131, 154, 183, 204, 226, 243, 255, 257, 262]}
+# + {"code_folding": [0, 2, 25, 52, 71, 76, 82, 131, 154, 183, 204, 226, 243, 255, 257, 262]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -572,7 +572,7 @@ data_moms_dct_fake = SE_instance.Forecaster()
 # + {"code_folding": []}
 #SE_instance.ForecastPlot()
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### feed the data moments
 SE_instance.GetDataMoments(data_moms_dct_fake)
 
@@ -599,7 +599,7 @@ SE_instance.GetDataMoments(data_moms_dct_fake)
 # + {"code_folding": []}
 #SE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [3, 22, 26, 32, 37, 48, 77, 105, 169, 198, 203, 211, 219]}
+# + {"code_folding": [22, 26, 32, 37, 75, 94, 101, 133, 163, 187, 192, 197, 205]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:
@@ -608,8 +608,8 @@ class NoisyInformation:
                  history,
                  horizon=1,
                  process_para = process_para, 
[…]

### 2019-10-22 workingfolder/python/GMMEst_dev.py

@@ -1,1037 +1,0 @@
-# ---
-# jupyter:
-#   jupytext:
-#     formats: ipynb,py:light
-#     text_representation:
-#       extension: .py
-#       format_name: light
-#       format_version: '1.4'
-#       jupytext_version: 1.2.3
-#   kernelspec:
-#     display_name: Python 3
-#     language: python
-#     name: python3
-# ---
-
-# ## GMM Estimation of Model Parameters of Expectation Formation
-#
-# - This notebook includes functions that estimate the parameter of rigidity for different models
-# - It allows for flexible choices of moments to be used, forecast error, disagreement, and uncertainty, etc. 
-# - It includes 
-#   - A general function that implements the estimation using the minimum distance algorithm. 
-#   - Model-specific functions that take real-time data and process parameters as inputs and produces forecasts and moments as outputs. It is model-specific because different models of expectation formation bring about different forecasts. 
-#   - Auxiliary functions that compute the moments as well as the difference of data and model prediction, which will be used as inputs for GMM estimator. 
-
-# ### 1. Estimation algorithms 
-
-from scipy.optimize import minimize
-import numpy as np
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from statsmodels.tsa.api import AR
-import copy as cp 
-from scipy.stats import bernoulli
-
-
-# + {"code_folding": [1]}
-# a general-purpose estimating function of the parameter
-def Estimator(obj_func,
-              para_guess,
-              method='CG',
-              bounds = None,
-              options = {'disp': True}):
-    """
-    Inputs
-    ------
-    - moments: a function of the rigidity model parameter  
-    - method: method of optimization, i.e. 
-         -  'L-BFGS-B', bounds=((1e-10, None), (1e-10, None))
-    
-    Outputs
-    -------
-    - parameter: an array of estimated parameter
-    """
-    
-    parameter = minimize(obj_func,
-                         x0 = para_guess,
-                         method = method,
-                         bounds = bounds,
-                         options = options)['x']
-    return parameter 
-
-
-# + {"code_folding": [1]}
-# a function that prepares moment conditions. So far the loss being simply the norm of the difference
-def PrepMom(model_moments,
-            data_moments):
-    """
-    Inputs
[…]

### 2019-10-22 workingfolder/python/Theories.py

@@ -574,12 +574,18 @@ plt.savefig('figures/ir_popseni.png')
 # \end{split}
 # \end{eqnarray}
 #
-# We can stack the two signals into one vector $s_{i,t} = [s^{pb}_t,s^{pr}_{i,t}]'$ and $v_{i,t}= [\epsilon_t,\xi_{i,t}]'$. So in a compact form, it can be written as
+# We can stack the two signals into one vector $s_{i,t} = [s^{pb}_t,s^{pr}_{i,t}]'$ and $v_{i,t}= [\epsilon_t,\xi_{i,t}]' = G \times u_{i,t}$, where $u_{i,t}$ is 2 $\times$ 1 following joint standard normal and G is 2 $\times$ 2 defined as follows. 
+#
+# \begin{eqnarray}
+# G = [\begin{array} & \sigma_\epsilon, 0 \\ 0,\sigma_\xi \end{array}]
+# \end{eqnarray}
+#
+# So in a compact form, it can be written as
 #
 #
 # \begin{eqnarray}
 # \begin{split}
-# s_{i,t} = H y_{t} + v_{i,t} \\
+# s_{i,t} = H y_{t} + G u_{i,t} \\
 # \text{where } & H=[1,1]' \quad \\
 # \end{split}
 # \end{eqnarray}
@@ -612,10 +618,10 @@ plt.savefig('figures/ir_popseni.png')
 # \begin{eqnarray}
 # \begin{split}
 #  E_{i,t|t}(y_{t}) 
-#  & =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
-# & = (1-PH) E_{i,t|t-1}(y_{t}) + Ps_{i,t} \\
-# & = (1-PH) E_{i,t|t-1}(y_{t}) + PH y_{i,t} + P v_{i,t} \\
-# \text{where the Kalman gain }  & P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} \\
+#  & =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P_t \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
[…]

### 2019-10-22 workingfolder/python/GMMEst-StochasticVol.py
created StochasticVol version of GMMEst and started deriving fomula.

@@ -1,0 +1,1098 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:light
+#     text_representation:
+#       extension: .py
+#       format_name: light
+#       format_version: '1.4'
+#       jupytext_version: 1.2.3
+#   kernelspec:
+#     display_name: Python 3
+#     language: python
+#     name: python3
+# ---
+
+# ## GMM Estimation of Model Parameters of Expectation Formation(Stochastic Volatility Process)
+#
+# - This notebook includes functions that estimate the parameter of rigidity for different models
+# - It allows for flexible choices of moments to be used, forecast error, disagreement, and uncertainty, etc. 
+# - It includes 
+#   - A general function that implements the estimation using the minimum distance algorithm. 
+#   - Model-specific functions that take real-time data and process parameters as inputs and produces forecasts and moments as outputs. It is model-specific because different models of expectation formation bring about different forecasts. 
+#   - Auxiliary functions that compute the moments as well as the difference of data and model prediction, which will be used as inputs for GMM estimator. 
+
+# ## 1. A process of time-variant volatility 
+#
+# Assume that the inflation follows a process of unobserved components model with stochastical volatility. 
+#
+# \begin{equation}
+# \begin{split}
+# & y_t = \tau_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
+# & \tau_t = \tau_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
+# & \log\sigma^2_{\eta,t} = \log\sigma^2_{\eta,t-1} + \mu_{\eta,t} \\
+# & \log\sigma^2_{\epsilon,t} = \log\sigma^2_{\epsilon,t-1} + \mu_{\epsilon,t} 
+# \end{split}
+# \end{equation}
+#
+# The distributions of shocks to levels of the components and their volatilities are, respectively, the following.
+#
+# \begin{equation}
+# \begin{split}
+# & \xi_t =[\xi_{\eta,t},\xi_{\epsilon,t}] \sim N(0,I_2) \\
+# & \mu_{t} = [\mu_{\eta,t},\mu_{\epsilon,t}]' \sim N(0,\gamma I_2) \\
+# \end{split}
+# \end{equation}
+#
[…]

### 2019-10-23 workingfolder/python/GMMEst.py
Added joint estimation module for SE in GMMEst. Need to proofread.

@@ -237,7 +237,7 @@ class RationalExpectation:
             plt.legend(loc=1)
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### create a RE instance 
 xx_history = AR1_simulator(rho,sigma,100)
 xx_real_time = xx_history[20:]
@@ -265,12 +265,12 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 #RE_instance.para_est
 #RE_instance.ForecastPlotDiag()
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## SE expectation parameters 
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 25, 52, 71, 76, 82, 131, 154, 183, 204, 226, 243, 255, 257, 262]}
+# + {"code_folding": [0, 2, 23, 27, 39, 57, 76, 87, 114, 129, 131, 142, 163, 184, 209, 214, 226, 238, 249, 251, 256]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -291,6 +291,8 @@ class StickyExpectation:
         self.data_moms_dct ={}
         self.para_est = {}
         self.moments = moments
+        self.realized = None
+        self.sim_realized = None
         
     def GetRealization(self,
                        realized_series):
@@ -301,16 +303,19 @@ class StickyExpectation:
         rho = self.process_para['rho']
         sigma =self.process_para['sigma']
         shocks = np.random.randn(n)*sigma
-        realized = np.zeros(n)
+        sim_realized = np.zeros(n)
         for i in range(n):
             cum_shock = sum([rho**h*shocks[h] for h in range(self.horizon)])
-            realized[i] = rho**self.horizon*self.real_time[i] + cum_shock
-        self.realized = realized
+            sim_realized[i] = rho**self.horizon*self.real_time[i] + cum_shock
+        self.sim_realized = sim_realized
+        return self.sim_realized
         
     def Forecaster(self):
         ## inputs 
         real_time = self.real_time
         history = self.history
+        realized = self.realized
+        sim_realized = self.sim_realized
         n = len(real_time)
         rho = self.process_para['rho']
         sigma =self.process_para['sigma']
@@ -327,19 +332,19 @@ class StickyExpectation:
[…]

### 2019-10-23 notes/GMMResults.tex
1. Created a note file reporting staged results of GMM estimation. 2. Polishing the figures of real-time data analytics.

\documentclass[]{article}
\usepackage{graphicx}

%opening
\title{Note on GMM Estimation of Theories of Expectation Formation}
\author{Tao Wang}

\begin{document}

\maketitle

\section{Generic Framework}

\section{Estimation}
\subsection{Real-Time Data}

\begin{figure}
\includegraphics[width=\textwidth]{figures/hist_rev_realtime.png}
\caption{Revisions of Current-vintage from Real-time Core CPI}
\label{real_time_rev}
	\begin{flushleft}
	{\footnotesize Note: real-time data  at time $t$ is defined the inflation from $t-1$ to $t$ according to the most recent vintage of CPI inflation at time $t$. The period is between 2000 M1-2018 M3.}
\end{flushleft}
\end{figure}

\begin{figure}
	\includegraphics[width=\textwidth]{figures/ts_rev_realtime.png}
	\caption{Current-vintage and Real-time Core CPI}
	\label{ts_real_time_current_vintage}
\end{figure}

\subsection{Results}

\end{document}

### 2019-10-23 workingfolder/python/DoEstimationWithData.py

@@ -16,7 +16,7 @@
 # ## Do the Estimation with SCE and SPF data
 #
 
-# ### 1. Importing estimation algorithms 
+# ### 1. Importing estimation codes
 
 # +
 import matplotlib.pyplot as plt
@@ -110,7 +110,7 @@ SPFCPI = PopQ[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var']].dropna(how
 
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## Inflation data quarterly 
 InfQ = pd.read_stata('../OtherData/InfShocksQClean.dta')
 InfQ = InfQ[-InfQ.date.isnull()]
@@ -119,7 +119,7 @@ dateQ_str2 = dateQ2 .dt.year.astype(int).astype(str) + \
              "Q" + dateQ2 .dt.quarter.astype(int).astype(str)
 InfQ.index = pd.DatetimeIndex(dateQ_str2,freq='infer')
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## process parameters estimation 
 # period filter 
 start_t='1995-01-01'
@@ -135,7 +135,7 @@ ar_rs = ARmodel.fit(1,trend='nc')
 rhoQ_est = ar_rs.params[0]
 sigmaQ_est = np.sqrt(sum(ar_rs.resid**2)/(len(CPICQ)-1))
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## Inflation data monthly
 InfM = pd.read_stata('../OtherData/InfShocksMClean.dta')
 InfM = InfM[-InfM.date.isnull()]
@@ -171,13 +171,13 @@ PopM.index = pd.DatetimeIndex(dateM)
 SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']].dropna(how='any')
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## Combine expectation data and real-time data 
 
 SPF_est = pd.concat([SPFCPI,real_time_inf,InfQ['Inf1y_CPICore'],InfQ['Inf1yf_CPICore']], join='inner', axis=1)
 SCE_est = pd.concat([SCECPI,real_time_inf,InfM['Inf1yf_CPIAU']], join='inner', axis=1)
 
-# +
+# + {"code_folding": []}
 ## hisotries data, the series ends at the same dates with real-time data but startes earlier 
 
 st_t_history = '2000-01-01'
[…]

### 2019-10-23 workingfolder/python/GMMEst.py

@@ -33,7 +33,7 @@ import copy as cp
 from scipy.stats import bernoulli
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": [0, 1]}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -60,7 +60,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": [0, 1]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -270,7 +270,7 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 23, 27, 39, 57, 76, 87, 114, 129, 131, 142, 163, 184, 209, 214, 226, 238, 249, 251, 256]}
+# + {"code_folding": [27, 39, 57, 76, 87, 114, 142, 163, 184, 207, 212, 224, 247, 249, 254, 266]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -471,10 +471,8 @@ class StickyExpectation:
         SE_moms_dct = self.Forecaster().copy()
         SE_moms = np.array([SE_moms_dct[key] for key in moments] )
         data_moms = np.array([data_moms_dct[key] for key in moments] )
-        #print(SE_moms.shape)
         n = len(sim_realized)
         SE_moms_stack = np.concatenate((SE_moms, sim_realized.reshape(1,n)), axis=0)
-        #print(SE_moms_stack.shape)
         data_moms_stack = np.concatenate((data_moms, realized.reshape(1,n)), axis=0)
         obj_func = PrepMom(SE_moms_stack,data_moms_stack)
         return obj_func
@@ -538,28 +536,44 @@ class StickyExpectation:
             plt.plot(self.forecast_moments_est[val],'r-',label='model:'+ val)
             plt.plot(np.array(self.data_moms_dct[val]),'*',label='data:'+ val)
             plt.legend(loc=1)
+            
+    def ForecastPlotDiagJoint(self):
+        lbd,rho,sigma = self.para_est_joint
+        exp_para_est_dct = {'lambda':lbd}
+        process_para_est_dct = {'rho':rho,
+                               'sigma':sigma}
+        new_instance = cp.deepcopy(self)
+        new_instance.exp_para = exp_para_est_dct
[…]

### 2019-10-23 notes/GMMResults.tex
Added generic framework section on the GMMEst note and some verbal discussion of the revisions.

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage[a4paper,bindingoffset=0.2in,%
+left=1.2in,right=1.2in,top=1.2in,bottom=1.2in,%
+footskip=.25in]{geometry}
 
@@
 
+For a given process of inflation and a particular theory of expectation formation, the GMM estimate of the vector of parameters $\Omega$ is defined as the following.
+
+\begin{eqnarray}
+\widehat \Omega = \underset{\Omega }{argmin} (M_{\textrm{data} } - F(\Omega, Y)) W  (M_{\textrm{data} } - F(\Omega, Y))'
+\end{eqnarray}
+
+\begin{itemize}
+	\item  $\Omega$ is a vector of size of $k$, depending on the number of parameters to be estimated. 
+	\item $M_{data}$ is the moments computed from data, i.e.
+mean forecasts, average forecast errors, the average cross-sectional variance of forecasts (disagreement), average uncertainty, etc.
+Also the autocovariance of all the abovementioned.
+
+	\item $F$ is the moments that are generated from a certain theory of expectation formation and inflation process.
+It is a function of parameters $\Omega$ as well as the $Y$, the real-time data(including history) that is available to forecasters at each point of the time $t$.
+	\item For instance, for $T$ periods, $Y$ includes $T$  sequences of real-time inflation data of different lengths that terminate at each point of the forecasting:  $t =0$, $t=1$... $t=T$ . 
+	\item  Both $M$ and $F$ is of the size  $m$, depending on the number of moments used for estimation.
+For instance, if we only estimate expectation formation using mean forecasts, disagreements and forecast errors while taking the inflation process as given, there are three moments, thus $m = 3$.
+If we include autocovariance of forecast errors, then $m=4$.
+
+	\item $W$ is the weighting matrix. For now, I stick to the identity matrix. 
+\end{itemize}
+
+The above procedure is specific to a pair of an assumed inflation process and a theory of expectation.
+It can be estimated only estimated for the theory of expectation formation with exogenous fed parameters of the inflation process using the entire history of inflation data, or we could jointly estimate the parameters of expectation formation and the inflation process.
+
 \section{Estimation}
@@
 
-\begin{figure}
+When agents form their expectations of inflation at any point of the time, what is potentially available to them is the real-time inflation data, namely those released from the most update-to-date vintage of the inflation.
+In order to match as close as possible the information set available to the forecasting agents, we need to use real-time data for each particular point of time.
+
+These real-time vintage inflation data since 1998 were obtained from the Real-Time Data Research Center hosted by the Federal Reserve Bank of Philadelphia.
+
+To get an idea of how much of the differences there are between the real-time inflation and the most recent vintage in 2018, Figure \ref{real_time_rev} and \ref{ts_real_time_current_vintage} plot, respectively, the distributions of the revisions as well as the time series of the inflation.
+Although overall, there is no obvious skewness of the revisions, there have been indeed sizable revisions made for the real-time data.
+
+\begin{figure}[ht]
 \includegraphics[width=\textwidth]{figures/hist_rev_realtime.png}
@@
 
-\begin{figure}
+\begin{figure}[ht]
 	\includegraphics[width=\textwidth]{figures/ts_rev_realtime.png}

### 2019-10-23 workingfolder/python/DoEstimationWithData.py

@@ -73,7 +73,7 @@ def GetRealTimeData(matrix):
     return real_time
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## generate real-time series 
 matrix_cpic = InfCPICMRT.copy().drop(columns=['date','year','month'])
 matrix_cpi = InfCPIMRT.copy().drop(columns=['date','year','month'])
@@ -83,7 +83,7 @@ real_time_cpi =  pd.Series(GetRealTimeData(matrix_cpi) )
 real_time_cpic.index =  InfCPICMRT.index #+ pd.DateOffset(months=1) 
 real_time_cpi.index = InfCPIMRT.index #+ pd.DateOffset(months=1)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## turn index into yearly inflation
 real_time_index =pd.concat([real_time_cpic,real_time_cpi], join='inner', axis=1)
 real_time_index.columns=['RTCPI','RTCPICore']
@@ -177,7 +177,7 @@ SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']].dropna(how='any')
 SPF_est = pd.concat([SPFCPI,real_time_inf,InfQ['Inf1y_CPICore'],InfQ['Inf1yf_CPICore']], join='inner', axis=1)
 SCE_est = pd.concat([SCECPI,real_time_inf,InfM['Inf1yf_CPIAU']], join='inner', axis=1)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## hisotries data, the series ends at the same dates with real-time data but startes earlier 
 
 st_t_history = '2000-01-01'
@@ -187,7 +187,7 @@ ed_t_SCE = SCE_est.index[-1].strftime('%Y-%m-%d')
 historyQ = real_time_inf.copy().loc[st_t_history:ed_t_SPF]
 historyM = real_time_inf.loc[st_t_history:ed_t_SCE]
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 # How large is the difference between current vintage and real-time data
 rev = SPF_est['Inf1y_CPICore'] - SPF_est['RTCPICore']
 
@@ -202,7 +202,7 @@ plt.ylabel('Density(0-1)',size=12)
 plt.xlabel('Current Vintage - Real-Time',size=12)
 plt.savefig('figures/hist_rev_realtime.png')
 
[…]

### 2019-10-23 workingfolder/python/DoEstimationWithData.py
Included loops that estiamte the parameter for different choosen moments for SE and stackes results in one dataframe. Needs to plot the graph as well.

@@ -83,7 +83,7 @@ real_time_cpi =  pd.Series(GetRealTimeData(matrix_cpi) )
 real_time_cpic.index =  InfCPICMRT.index #+ pd.DateOffset(months=1) 
 real_time_cpi.index = InfCPIMRT.index #+ pd.DateOffset(months=1)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## turn index into yearly inflation
 real_time_index =pd.concat([real_time_cpic,real_time_cpi], join='inner', axis=1)
 real_time_index.columns=['RTCPI','RTCPICore']
@@ -282,6 +282,80 @@ SE_model.para_est_joint
 # +
 #se_spf_joint_plot = SE_model.ForecastPlotDiagJoint()
 
+# + {"code_folding": [0, 2, 11]}
+## loop estimation overdifferent choieces of moments for SPF
+
+moments_choices = [['Forecast'],
+                   ['FE'],
+                   ['Forecast','FE'],
+                   ['Forecast','FE','Disg']]
+
+para_est_SPF_holder = []
+
+### loop starts from here for SPF 
+
+for moments_to_use in moments_choices:
+    print("moments used include "+ str(moments_to_use))
+    real_time = np.array(SPF_est['RTCPI'])
+    history_Q = historyQ['RTCPICore']
+    data_moms_dct = data_moms_dct_SPF
+    process_paraQ_est = {'rho':rhoQ_est,
+                         'sigma':sigmaQ_est}
+    SE_model = se(real_time = real_time,
+                  history = history_Q,
+                  process_para = process_paraQ_est)
+    SE_model.moments = moments_to_use
+    SE_model.GetRealization(realized_CPIC)
+    SE_model.GetDataMoments(data_moms_dct)
+    SE_model.ParaEstimate(method='CG',
+                          options={'disp':True})
+    para_est_SPF_holder.append(SE_model.para_est)
+print(para_est_SPF_holder)
+
+# + {"code_folding": [2, 10]}
+## loop estimation overdifferent choieces of moments
+
+moments_choices = [['Forecast'],
+                   ['FE'],
+                   ['Forecast','FE'],
+                   ['Forecast','FE','Disg']]
+
+para_est_SCE_holder = []
+
+
+for moments_to_use in moments_choices:
+    print("moments used include "+ str(moments_to_use))
[…]

### 2019-10-23 workingfolder/python/GMMEst.py

@@ -270,7 +270,7 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [27, 39, 57, 76, 87, 114, 142, 163, 184, 207, 212, 224, 247, 249, 254, 266]}
+# + {"code_folding": [1, 2, 27, 39, 57, 76, 142, 163, 184, 207, 212, 224, 247, 249, 254, 266]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,

### 2019-10-23 workingfolder/python/DoEstimationWithData.py
Make a few changes to the ForecastPlot function. Also plotting and saving the figures in the loop

@@ -256,6 +256,8 @@ SE_model.ParaEstimate(options={'disp':True})
 lbd_est_SPF = SE_model.para_est
 lbd_est_SPF
 
+SE_model.ForecastPlotDiag()
+
 # + {"code_folding": [0]}
 ## Joint estimation for SPF
 
@@ -294,7 +296,7 @@ para_est_SPF_holder = []
 
 ### loop starts from here for SPF 
 
-for moments_to_use in moments_choices:
+for i,moments_to_use in enumerate(moments_choices):
     print("moments used include "+ str(moments_to_use))
     real_time = np.array(SPF_est['RTCPI'])
     history_Q = historyQ['RTCPICore']
@@ -310,9 +312,12 @@ for moments_to_use in moments_choices:
     SE_model.ParaEstimate(method='CG',
                           options={'disp':True})
     para_est_SPF_holder.append(SE_model.para_est)
+    SE_model.ForecastPlotDiag()
+    plt.savefig('figures/spf_est_diag'+str(i)+'.png')
+    
 print(para_est_SPF_holder)
 
-# + {"code_folding": [2, 10]}
+# + {"code_folding": [0, 2]}
 ## loop estimation overdifferent choieces of moments
 
 moments_choices = [['Forecast'],
@@ -339,10 +344,12 @@ for moments_to_use in moments_choices:
     SE_model2.ParaEstimate(method='CG',
                            options={'disp':True})
     para_est_SCE_holder.append(SE_model2.para_est)
+    SE_model2.ForecastPlotDiag()
+    plt.savefig('figures/sce_est_diag'+str(i)+'.png')
 
 print(para_est_SCE_holder)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## tabulate the estimates 
 spf_est_para = pd.DataFrame(para_est_SPF_holder,columns=[r'SE: $\hat\lambda_{SPF}$(Q)'])
 #spf_est_df = pd.concat([spf_est_moms,spf_est_para], join='inner', axis=1)

### 2019-10-23 workingfolder/python/GMMEst.py

@@ -125,7 +125,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [0, 2, 15, 18, 29, 52, 57, 65, 75, 90, 97, 98]}
+# + {"code_folding": [2, 15, 18, 29, 52, 57, 65, 75, 79, 90, 98, 99]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -217,6 +217,7 @@ class RationalExpectation:
                                   options = options)
     
     def ForecastPlot(self):
+        plt.style.use('ggplot')
         x = plt.figure(figsize=([3,13]))
         for i,val in enumerate(self.moments):
             plt.subplot(4,1,i+1)
@@ -229,11 +230,13 @@ class RationalExpectation:
         new_instance = cp.deepcopy(self)
         new_instance.process_para = re_process_est_dct
         self.forecast_moments_est = new_instance.Forecaster()
-        x = plt.figure(figsize=([3,13]))
+        plt.style.use('ggplot')
+        m_ct = len(self.moments)
+        x = plt.figure(figsize=([3,3*m_ct]))
         for i,val in enumerate(self.moments):
             plt.subplot(4,1,i+1)
-            plt.plot(self.forecast_moments_est[val],'r-',label='model:'+ val)
-            plt.plot(np.array(self.data_moms_dct[val]),'*',label='data:'+ val)
+            plt.plot(self.forecast_moments_est[val],'s-',label='model:'+ val)
+            plt.plot(np.array(self.data_moms_dct[val]),'o-',label='data:'+ val)
             plt.legend(loc=1)
 
 
@@ -270,7 +273,7 @@ RE_instance = RationalExpectation(real_time = xx_real_time,
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [1, 2, 27, 39, 57, 76, 142, 163, 184, 207, 212, 224, 247, 249, 254, 266]}
+# + {"code_folding": [2, 27, 39, 57, 76, 87, 142, 163, 184, 207, 212, 224, 236, 247, 251, 256, 270, 273, 282]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -519,7 +522,9 @@ class StickyExpectation:
                                   options = options)
         
     def ForecastPlot(self):
-        x = plt.figure(figsize=([3,13]))
+        plt.style.use('ggplot')
[…]

### 2019-10-24 notes/GMMResults.tex
Debugged the importing errors from GMMEst.But need to simplify the all_moments bools.

@@
 footskip=.25in]{geometry}
+\usepackage{caption}
+\usepackage{subcaption}
 
 %opening
-\title{Note on GMM Estimation of Theories of Expectation Formation}
+\title{A Note on GMM Estimation of Theories of Expectation Formation}
 \author{Tao Wang}
@@
 
-\section{Generic Framework}
+\section{A Generic Framework}
 
@@
 \section{Estimation}
-\subsection{Real-Time Data}
+\subsection{Real-time Data}
 
@@
 \begin{figure}[ht]
-\includegraphics[width=\textwidth]{figures/hist_rev_realtime.png}
+		\centering
+\includegraphics[width=0.7\textwidth]{figures/hist_rev_realtime.png}
 \caption{Revisions of Current-vintage from Real-time Core CPI}
@@
 \begin{figure}[ht]
-	\includegraphics[width=\textwidth]{figures/ts_rev_realtime.png}
+	\centering
+	\includegraphics[width=0.8\textwidth]{figures/ts_rev_realtime.png}
 	\caption{Current-vintage and Real-time Core CPI}
@@
 
+\subsubsection{Professional Forecasters}
+
+Figure \ref{SE_diag_SPF} and \ref{SE_diag_joint_SPF} plot the estimated moments for SE model together with the data moments professional forecasts of SPF.
+
+From left to the right, the four columns of the figures are based on estimation
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SE}
+		\label{SE_diag_SPF}
+		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag0.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag1.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag2.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag3.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{SE_diag_joint_SPF}
+	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag0.png}
+	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag1.png}
+	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag2.png}
+	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag3.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively.
+}
+	\end{flushleft}
+	\caption{SE of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NI}
+		\label{NI_diag_SPF}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag0.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag1.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag2.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag3.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of NI and Inflation Process}
+		\label{NI_diag_joint_SPF}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag0.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag1.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag2.png}
+		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag3.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively.
+}
+	\end{flushleft}
+	\caption{NI of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\subsubsection{Households}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SE}
+		\label{SE_diag_SCE}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag0.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag1.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag2.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag3.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{SE_diag_joint_SCE}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag0.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag1.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag2.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag3.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively.}
+	\end{flushleft}
+	\caption{SE of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NI}
+		\label{NI_diag_SCE}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag0.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag1.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag2.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag3.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{NI_diag_joint_SCE}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag0.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag1.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag2.png}
+		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag3.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively.
+}
+	\end{flushleft}
+	\caption{NI of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
 \end{document}

### 2019-10-24 workingfolder/python/GMMEst.py

@@ -33,7 +33,7 @@ import copy as cp
 from scipy.stats import bernoulli
 
 
-# + {"code_folding": [0, 1]}
+# + {"code_folding": [0]}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -60,7 +60,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [0, 1]}
+# + {"code_folding": [0]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -79,7 +79,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [0, 1, 5]}
+# + {"code_folding": [0, 1, 5, 19]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -91,17 +91,19 @@ def hstepfe(h,sigma,rho):
 
 
 def ForecastPlot(test):
-    x = plt.figure(figsize=([3,13]))
+    m_ct = len(test)
+    x = plt.figure(figsize=([3,3*m_ct]))
     for i,val in enumerate(test):
-        plt.subplot(4,1,i+1)
+        plt.subplot(m_ct,1,i+1)
         plt.plot(test[val],label=val)
         plt.legend(loc=1)
     return x
         
 def ForecastPlotDiag(test,data,legends=['model','data']):
-    x = plt.figure(figsize=([3,13]))
+    m_ct = len(test)
+    x = plt.figure(figsize=([3,3*m_ct]))
     for i,val in enumerate(test):
-        plt.subplot(4,1,i+1)
+        plt.subplot(m_ct,1,i+1)
         plt.plot(test[val],label= legends[0]+ ': ' +val)
         plt.plot(np.array(data[val]),label=legends[1] +': '+ val)
         plt.legend(loc=1)
@@ -117,7 +119,7 @@ def AR1_simulator(rho,sigma,nobs):
     return xxx[1:]
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## some process parameters 
 rho = 0.95
 sigma = 0.1
@@ -125,7 +127,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
[…]

### 2019-10-24 notes/GMMResults.tex
1. Both NI and SE can do the loop estimation. Needs to do NI joint plots. 2. The notes include all figures except for NI joint. 3. Both Se and NI tables are included. But need to debug NI table.

--- 2019-10-23 notes/GMMResults.tex
@@
 \usepackage[a4paper,bindingoffset=0.2in,%
-left=1.2in,right=1.2in,top=1.2in,bottom=1.2in,%
+left=0.9in,right=0.9in,top=1.2in,bottom=1.2in,%
 footskip=.25in]{geometry}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{adjustbox}
+\usepackage{tabularx}
+\usepackage{rotating}
 
 %opening
-\title{Note on GMM Estimation of Theories of Expectation Formation}
+\title{A Note on GMM Estimation of Theories of Expectation Formation}
 \author{Tao Wang}
@@
 
+\subsubsection{Professional Forecasters}
+
+Figure \ref{SE_diag_SPF} and \ref{SE_diag_joint_SPF} plot the estimated moments for SE model together with the data moments professional forecasts of SPF.
+
+From left to the right, the four columns of the figures are based on estimation
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SE for Professionals}
+		\label{SE_diag_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{SE_diag_joint_SPF}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag0.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag1.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag2.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag3.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{SE of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NI for Professionals}
+		\label{NI_diag_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of NI and Inflation Process}
+		\label{NI_diag_joint_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{NI of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\subsubsection{Households}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SE for Households}
+		\label{SE_diag_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{SE_diag_joint_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{SE of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NI  for Households}
+		\label{NI_diag_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{NI_diag_joint_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{NI of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+	\begin{sidewaystable}
+	\caption{GMM Estimates of Parameters of SE and Inflation Process}
+	\label{GMM_Est_SE_Table}
+\begin{tabular}{llllllllllll}
+	\hline 
+	0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(Q) & SE: $\rho$ & SE: $\sigma$ \\
+	\hline 
+	Forecast &    &      &     & 0.21                       & 0.01                       & 1          & 0.1          & 1.8                        & 1                          & 1          & 0.1          \\
+		\hline 
+	FE       &    &      &     & 0.18                       & 0.01                       & 1          & 0.1          & 1.74                       & 1                          & 1          & 0.1          \\
+		\hline 
+	Forecast & FE &      &     & 0.2                        & 0.01                       & 1          & 0.1          & 1.77                       & 1                          & 1          & 0.1          \\
+		\hline 
+	Forecast & FE & Disg &     & 0.23                       & 0.05                       & 1          & 0.1          & 0.02                       & 0.03                       & 0.98       & 0.1          \\
+		\hline 
+	Forecast & FE & Disg & Var & 0.26                       & 0.05                       & 1          & 0.07         & 0.01                       & 0.03                       & 0.98       & 1.11         \\
+		\hline 
+\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+	\caption{GMM Estimates of Parameters of NI and Inflation Process}
+	\label{GMM_Est_NI_Table}
+\begin{tabular}{llllllllllllllllllll}
+	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & NI: $\rho$ & NI: $\sigma$ \\
+	\hline 
+	Forecast &    &      &     & 98.52                     & 1.69                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 98.52                     & 1.69                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	\hline 
+	FE       &    &      &     & 151.59                    & 0.95                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 151.59                    & 0.95                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	\hline 
+	Forecast & FE &      &     & -0.7                      & 336.37                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & -0.7                      & 336.37                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	\hline 
+	Forecast & FE & Disg &     & 1.63                      & 115.06                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 1.63                      & 115.06                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	\hline 
+	Forecast & FE & Disg & Var & -0.63                     & 131.43                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & -0.63                     & 131.43                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1    \\
+	\hline     
+\end{tabular}
+\end{sidewaystable}
+
 \end{document}

### 2019-10-24 workingfolder/python/DoEstimationWithData.py

@@ -171,7 +171,7 @@ PopM.index = pd.DatetimeIndex(dateM)
 SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']].dropna(how='any')
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## Combine expectation data and real-time data 
 
 SPF_est = pd.concat([SPFCPI,real_time_inf,InfQ['Inf1y_CPICore'],InfQ['Inf1yf_CPICore']], join='inner', axis=1)
@@ -202,7 +202,7 @@ plt.ylabel('Density(0-1)',size=12)
 plt.xlabel('Current Vintage - Real-Time',size=12)
 plt.savefig('figures/hist_rev_realtime.png')
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 # real time inflation 
 real_time = np.array(SPF_est['RTCPI'])
 
@@ -233,7 +233,7 @@ exp_data_SCE = SCE_est[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']]
 exp_data_SCE.columns = ['Forecast','FE','Disg','Var']
 data_moms_dct_SCE = dict(exp_data_SCE)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## SE estimation for SPF
 real_time = np.array(SPF_est['RTCPI'])
 history_Q = historyQ['RTCPICore']
@@ -288,13 +288,15 @@ SE_model.para_est_joint
 se_spf_joint_plot = SE_model.ForecastPlotDiagJoint()
 
 
-# + {"code_folding": [2]}
-## loop estimation overdifferent choieces of moments for SPF
+# + {"code_folding": [0, 14]}
+## SE loop estimation overdifferent choieces of moments for SPF
 
+moments_choices_short = [['Forecast']]
 moments_choices = [['Forecast'],
                    ['FE'],
                    ['Forecast','FE'],
-                   ['Forecast','FE','Disg']]
+                   ['Forecast','FE','Disg'],
+                   ['Forecast','FE','Disg','Var']]
 
 para_est_SPF_holder = []
 para_est_SPF_joint_holder = []
@@ -319,15 +321,18 @@ for i,moments_to_use in enumerate(moments_choices):
     SE_model.ParaEstimate(method='CG',
                           options={'disp':True})
     para_est_SPF_holder.append(SE_model.para_est)
[…]

### 2019-10-24 workingfolder/python/GMMEst.py

@@ -119,7 +119,7 @@ def AR1_simulator(rho,sigma,nobs):
     return xxx[1:]
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## some process parameters 
 rho = 0.95
 sigma = 0.1
@@ -127,21 +127,22 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [2, 15, 18, 29, 52, 57, 65, 75, 79, 102]}
+# + {"code_folding": [1, 2, 16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 110]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
                  real_time,
                  history,
-                 horizon=1,
+                 horizon = 1,
                  process_para = process_para,
                  exp_para = {},
-                 moments=['Forecast','FE','Disg','Var']):
+                 moments = ['Forecast','FE','Disg','Var']):
         self.real_time = real_time
         self.history = history
         self.horizon = horizon
         self.process_para = process_para
         self.moments = moments
+        self.all_moments = ['Forecast','FE','Disg','Var']
     
     def GetRealization(self,realized_series):
         self.realized = realized_series
@@ -220,10 +221,17 @@ class RationalExpectation:
     
     def ForecastPlot(self,
                     all_moms = False):
-        m_ct = len(self.moments)
+            
+        ## decide if plot all moments 
+        if all_moms == False:
+            moments_to_plot = self.moments
+        else:
+            moments_to_plot = self.all_moments
+        m_ct = len(moments_to_plot)
         plt.style.use('ggplot')
         x = plt.figure(figsize=([3,3*m_ct]))
-        for i,val in enumerate(self.moments):
+        
+        for i,val in enumerate(moments_to_plot):
             plt.subplot(m_ct,1,i+1)
             plt.plot(self.forecast_moments[val],label=val)
             plt.legend(loc=1)
@@ -235,10 +243,16 @@ class RationalExpectation:
         new_instance = cp.deepcopy(self)
         new_instance.process_para = re_process_est_dct
         self.forecast_moments_est = new_instance.Forecaster()
-        m_ct = len(self.moments)
+        
+        ## decide if plot all moments 
+        if all_moms == False:
[…]

### 2019-10-24 notes/GMMResults.tex
1. Loop estimates and plots for both SE and NI, for both SCE and SPF. 2. The results of reported in the note for meeting with Jonathan.

@@
 \usepackage{rotating}
+\usepackage{hyperref}
 
@@
 
-The above procedure is specific to a pair of an assumed inflation process and a theory of expectation.
-It can be estimated only estimated for the theory of expectation formation with exogenous fed parameters of the inflation process using the entire history of inflation data, or we could jointly estimate the parameters of expectation formation and the inflation process.
+The above procedure is specific to a pair of assumed inflation process and a theory of expectation.
+It can be estimated only for the theory of expectation formation with exogenous fed parameters of the inflation process using the entire history of inflation data, or we could jointly estimate the parameters of expectation formation and the inflation process.
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 		\centering
@@
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 	\centering
@@
 
-From left to the right, the four columns of the figures are based on estimation
+From left to the right, the four columns of the figures are based on estimation using different choices of moments.
+
+Figure \ref{NI_diag_SPF} and \ref{NI_diag_joint_SPF} plot the estimated moments for NI model together with the data moments professional forecasts of SPF.
 
@@
 
-\begin{figure}[ht]
+Figure \ref{SE_diag_SCE} and \ref{SE_diag_joint_SCE} plot the estimated moments for SE model together with the data moments of households inflation forecasts from SCE.
+
+From left to the right, the four columns of the figures are based on estimation using different choices of moments.
+
+Figure \ref{NI_diag_SCE} and \ref{NI_diag_joint_SCE} plot the estimated moments for NI model together with the data moments of households inflation forecasts from SCE.
+
+\begin{figure}[htbp]
 	\centering
@@
 
-	\begin{sidewaystable}
+	\begin{sidewaystable}[t]
+		\centering
 	\caption{GMM Estimates of Parameters of SE and Inflation Process}
@@
 
-\begin{sidewaystable}
+\begin{sidewaystable}[t]
+	\centering
 	\caption{GMM Estimates of Parameters of NI and Inflation Process}
 	\label{GMM_Est_NI_Table}
-\begin{tabular}{llllllllllllllllllll}
-	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & NI: $\rho$ & NI: $\sigma$ \\
+\begin{tabular}{llllllllllllllll}
+	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
 		\hline 
-	Forecast &    &      &     & 98.52                     & 1.69                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 98.52                     & 1.69                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	Forecast &    &      &     & 4.17                      & 164.56                & 0.5                       & 0.5                   & 0.8        & 0.1          & -0.34                     & 32.02                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 		\hline 
-	FE       &    &      &     & 151.59                    & 0.95                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 151.59                    & 0.95                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	FE       &    &      &     & -2.15                     & 167.73                & 0.5                       & 0.5                   & 0.8        & 0.1          & 1.38                      & -0.46                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 		\hline 
-	Forecast & FE &      &     & -0.7                      & 336.37                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & -0.7                      & 336.37                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	Forecast & FE &      &     & 205.05                    & 1.52                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0.47                      & 0.35                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 		\hline 
-	Forecast & FE & Disg &     & 1.63                      & 115.06                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 1.63                      & 115.06                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
+	Forecast & FE & Disg &     & 9.57                      & 3.58                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 1043.13                   & 11.08                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 		\hline 
-	Forecast & FE & Disg & Var & -0.63                     & 131.43                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & -0.63                     & 131.43                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1    \\
+	Forecast & FE & Disg & Var & 76.29                     & 0.69                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 2682.64                   & 334.37                & 0.5                       & 0.5                   & 0.8        & 1.1         \\
 	\hline 
@@
 
+\section{Stochastic volatility model of inflation}
+
+\subsection{Process of inflation}
+
+Assume that the inflation follows a process of unobserved components model with stochastical volatility.
+
+\begin{eqnarray}
+\begin{split}
+& y_t = \tau_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
+& \tau_t = \tau_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
+& \log\sigma^2_{\eta,t} = \log\sigma^2_{\eta,t-1} + \mu_{\eta,t} \\
+& \log\sigma^2_{\epsilon,t} = \log\sigma^2_{\epsilon,t-1} + \mu_{\epsilon,t} 
+\end{split}
+\end{eqnarray}
+
+The distributions of shocks to levels of the components and their volatilities are, respectively, the following.
+
+\begin{eqnarray}
+\begin{split}
+& \xi_t =[\xi_{\eta,t},\xi_{\epsilon,t}] \sim N(0,I_2) \\
+& \mu_{t} = [\mu_{\eta,t},\mu_{\epsilon,t}]' \sim N(0,\gamma I_2) 
+\end{split}
+\end{eqnarray}
+
+The only parameter of the model is $\gamma$, which determines the time-varying volatilities.
+
+\subsection{Different models of expectation formation}
+
+\subsubsection{Rational expectation}
+
+At the point of time $t$, the RE agent sees the realization of all stochastic variables above with subscript $t$, $t-1$, etc, including $y_t$, $\tau_t$, $\eta_t$, $\sigma_{\eta,t}$, $\sigma_{\epsilon,t}$ and their realizations in the whose past.
+Again, $*$ stands for FIRE benchmark.
+
+\begin{eqnarray}
+\begin{split}
+\hat y^*_{t+h|i,t} & =  E^*_{i,t}(y_{t+h}|I_{i,t}) = \tau_t 
+\end{split}
+\end{eqnarray}
+
+Conditional h-step-ahead variance, uncertainty is
+
+\begin{eqnarray}
+\begin{split}
+Var^*_{t+h|i,t} & = \sum^{h}_{t=0} E_{i,t}(\sigma^2_{\eta,t+h}) +  E_{i,t}(\sigma^2_{\epsilon,t+h})  \\
+& = \sum^{h}_{t=1} E_{i,t}(exp^{\log \sigma^2_{\eta,t}+\sum^h_{t=1}\mu_{\eta,t+h}}) +  E_{i,t}(exp^{\log \sigma^2_{\epsilon,t}+\sum^h_{t=0}\mu_{\epsilon,t+h}} ) \\
+& = \sigma^2_{\eta,t} \sum^{h}_{t=0} E_{i,t}(exp^{\sum^h_{t=1}\mu_{t+h,\eta}}) +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{t=1}\mu_{\epsilon,t+h}} ) \\
+& = \sigma^2_{\eta,t} \sum^{h}_{t=0} exp^{E_{i,t}({\sum^h_{t=1}\mu_{t+h,\eta}})- 0.5Var_{i,t}(\sum^h_{t=1}\mu_{t+h,\eta})} +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{t=1}\mu_{\epsilon,t+h}} ) \\
+& = \sigma^2_{\eta,t} \sum^{h}_{t=0} exp^{- 0.5h\gamma_{\eta}} +  \sigma^2_{\epsilon,t} exp^{- 0.5h\gamma_{\epsilon}}  \\
+\end{split} 
+\end{eqnarray}
+
+For instance, set $h=0$, the conditional volatility for the current inflation is
+
+\begin{eqnarray}
+\begin{split}
+Var^*_{t|i,t} =  \sigma^2_{\eta,t}  +  \sigma^2_{\epsilon,t}
+\end{split} 
+\end{eqnarray}
+
 \end{document}

### 2019-10-24 workingfolder/python/DoEstimationWithData.py

@@ -288,7 +288,7 @@ SE_model.para_est_joint
 se_spf_joint_plot = SE_model.ForecastPlotDiagJoint()
 
 
-# + {"code_folding": [0, 14]}
+# + {"code_folding": [0]}
 ## SE loop estimation overdifferent choieces of moments for SPF
 
 moments_choices_short = [['Forecast']]
@@ -321,7 +321,7 @@ for i,moments_to_use in enumerate(moments_choices):
     SE_model.ParaEstimate(method='CG',
                           options={'disp':True})
     para_est_SPF_holder.append(SE_model.para_est)
-    SE_model.all_moments = ['Forecast','FE','Disg']
+    SE_model.all_moments = ['Forecast','FE','Disg','Var']
     SE_model.ForecastPlotDiag(all_moms = True)
     plt.savefig('figures/spf_se_est_diag'+str(i)+'.png')
     
@@ -331,7 +331,7 @@ for i,moments_to_use in enumerate(moments_choices):
                                bounds = ((0,1),(0,1),(0,None)),
                                options={'disp':True})
     para_est_SPF_joint_holder.append(SE_model.para_est_joint)
-    SE_model.all_moments = ['Forecast','FE','Disg']
+    SE_model.all_moments = ['Forecast','FE','Disg','Var']
     SE_model.ForecastPlotDiagJoint(all_moms = True)
     plt.savefig('figures/spf_se_est_joint_diag'+str(i)+'.png')
     
@@ -348,6 +348,8 @@ spf_se_joint_est_para = pd.DataFrame(para_est_SPF_joint_holder,
 # -
 
 spf_se_joint_est_para
+
+spf_se_est_para
 
 # + {"code_folding": [0, 20]}
 ## SE loop estimation over different choieces of moments for SCE
@@ -381,7 +383,7 @@ for i,moments_to_use in enumerate(moments_choices):
     SE_model2.ParaEstimate(method='CG',
                            options={'disp':True})
     para_est_SCE_holder.append(SE_model2.para_est)
-    SE_model2.all_moments = ['Forecast','FE','Disg']
+    SE_model2.all_moments = ['Forecast','FE','Disg','Var']
     SE_model2.ForecastPlotDiag(all_moms = True)
     plt.savefig('figures/sce_se_est_diag'+str(i)+'.png')
     
@@ -392,14 +394,14 @@ for i,moments_to_use in enumerate(moments_choices):
[…]

### 2019-10-24 workingfolder/python/GMMEst.py

@@ -293,7 +293,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [1, 2, 24, 28, 40, 52, 70, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 298, 302]}
+# + {"code_folding": [2, 24, 28, 40, 52, 70, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 298, 302]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -687,7 +687,7 @@ class StickyExpectation:
 # + {"code_folding": []}
 #SE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [2, 3, 8, 29, 35, 41, 52, 110, 178, 201, 207, 210, 228, 233, 245, 257, 272, 274]}
+# + {"code_folding": [0, 3, 8, 29, 35, 41, 52, 110, 178, 201, 207, 210, 228, 233, 245, 257, 272, 294]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:
@@ -974,6 +974,33 @@ class NoisyInformation:
         else:
             moments_to_plot = self.all_moments
             
+        m_ct = len(moments_to_plot)
+        x = plt.figure(figsize=([3,3*m_ct]))
+        for i,val in enumerate(moments_to_plot):
+            plt.subplot(m_ct,1,i+1)
+            plt.plot(self.forecast_moments_est[val],'s-',label='model:'+ val)
+            plt.plot(np.array(self.data_moms_dct[val]),'o-',label='data:'+ val)
+            plt.legend(loc=1)
+            
+    def ForecastPlotDiagJoint(self,
+                              all_moms = False):
+        sigma_pb,sigma_pb,var,rho,sigma = self.para_est_joint
+        exp_para_est_dct = {'sigma_pb':sigma_pb,
+                           'sigma_pr':sigma_pb,
+                           'var_init':var}
+        process_para_est_dct = {'rho':rho,
+                               'sigma':sigma}
+        new_instance = cp.deepcopy(self)
+        new_instance.exp_para = exp_para_est_dct
+        new_instance.process_para = process_para_est_dct
+        self.forecast_moments_est = new_instance.Forecaster()
+        plt.style.use('ggplot')
+        
+        if all_moms == False:
+            moments_to_plot = self.moments
+        else:
[…]

### 2019-10-26 notes/GMMResults.tex
Loop estimates with bounds.So NI for SPF is now more stable. Problems that need to be addressed: 1. add a constant to SCE. 2. try autocovariance instead.

@@
 	\item $M_{data}$ is the moments computed from data, i.e.
-mean forecasts, average forecast errors, the average cross-sectional variance of forecasts (disagreement), average uncertainty, etc.
+mean forecasts, average forecast errors, the cross-sectional variance of forecasts (disagreement), average uncertainty, etc.
 Also the autocovariance of all the abovementioned.
@@
 	\hline 
-	0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(Q) & SE: $\rho$ & SE: $\sigma$ \\
+	0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
 	\hline 
-	Forecast &    &      &     & 0.21                       & 0.01                       & 1          & 0.1          & 1.8                        & 1                          & 1          & 0.1          \\
+	Forecast &    &      &     & 0.21                       & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
 	\hline 
-	FE       &    &      &     & 0.18                       & 0.01                       & 1          & 0.1          & 1.74                       & 1                          & 1          & 0.1          \\
+	FE       &    &      &     & 0.18                       & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
 	\hline 
-	Forecast & FE &      &     & 0.2                        & 0.01                       & 1          & 0.1          & 1.77                       & 1                          & 1          & 0.1          \\
+	Forecast & FE &      &     & 0.2                        & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
 	\hline 
@@
 \begin{tabular}{llllllllllllllll}
+	\hline 
 	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
 	\hline 
-	Forecast &    &      &     & 4.17                      & 164.56                & 0.5                       & 0.5                   & 0.8        & 0.1          & -0.34                     & 32.02                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	Forecast &    &      &     & 376.66                    & 1.26                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0                         & 1.13                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 	\hline 
-	FE       &    &      &     & -2.15                     & 167.73                & 0.5                       & 0.5                   & 0.8        & 0.1          & 1.38                      & -0.46                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	FE       &    &      &     & 1.04                      & 159.74                & 0.5                       & 0.5                   & 0.8        & 0.1          & 0                         & 1.26                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 	\hline 
-	Forecast & FE &      &     & 205.05                    & 1.52                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0.47                      & 0.35                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	Forecast & FE &      &     & 1.14                      & 6.74                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0.59                      & 0.36                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 	\hline 
-	Forecast & FE & Disg &     & 9.57                      & 3.58                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 1043.13                   & 11.08                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	Forecast & FE & Disg &     & 1.39                      & 1.46                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 2354.37                   & 10.93                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
 	\hline 
-	Forecast & FE & Disg & Var & 76.29                     & 0.69                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 2682.64                   & 334.37                & 0.5                       & 0.5                   & 0.8        & 1.1         \\
+	Forecast & FE & Disg & Var & 1.37                      & 1.1                   & 0.5                       & 0.5                   & 0.8        & 0.1          & 35263.31                  & 332.04                & 0.5                       & 0.5                   & 0.8        & 0.1         \\
 	\hline 

### 2019-10-26 workingfolder/python/DoEstimationWithData.py

@@ -288,7 +288,7 @@ SE_model.para_est_joint
 se_spf_joint_plot = SE_model.ForecastPlotDiagJoint()
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": [0, 29, 38]}
 ## SE loop estimation overdifferent choieces of moments for SPF
 
 moments_choices_short = [['Forecast']]
@@ -318,7 +318,8 @@ for i,moments_to_use in enumerate(moments_choices):
     SE_model.GetDataMoments(data_moms_dct)
     
     # only expectation
-    SE_model.ParaEstimate(method='CG',
+    SE_model.ParaEstimate(method='L-BFGS-B',
+                          para_guess =(0.5),
                           options={'disp':True})
     para_est_SPF_holder.append(SE_model.para_est)
     SE_model.all_moments = ['Forecast','FE','Disg','Var']
@@ -380,7 +381,9 @@ for i,moments_to_use in enumerate(moments_choices):
     SE_model2.GetDataMoments(data_moms_dct)
     
     ## only expectation
-    SE_model2.ParaEstimate(method='CG',
+    SE_model2.ParaEstimate(method='L-BFGS-B',
+                           para_guess =(0.5),
+                           bounds = ((0,1),),
                            options={'disp':True})
     para_est_SCE_holder.append(SE_model2.para_est)
     SE_model2.all_moments = ['Forecast','FE','Disg','Var']
@@ -401,11 +404,11 @@ for i,moments_to_use in enumerate(moments_choices):
 print(para_est_SCE_holder)
 print(para_est_SCE_joint_holder)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 sce_se_est_para = pd.DataFrame(para_est_SCE_holder,
                                columns=[r'SE: $\hat\lambda_{SCE}$(M)'])
 sce_se_joint_est_para = pd.DataFrame(para_est_SCE_joint_holder,
-                                     columns=[r'SE: $\hat\lambda_{SCE}$(Q)',
+                                     columns = [r'SE: $\hat\lambda_{SCE}$(M)',
                                               r'SE: $\rho$',
                                               r'SE: $\sigma$'])
 
@@ -423,7 +426,9 @@ se_est_df = pd.concat([est_moms,
                       join='inner', axis=1)
 # -
 
-se_est_df
+sce_se_est_para
+
[…]

### 2019-10-26 workingfolder/python/GMMEst.py

@@ -79,7 +79,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [0, 1, 5, 19]}
+# + {"code_folding": [1, 5, 19]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -104,8 +104,8 @@ def ForecastPlotDiag(test,data,legends=['model','data']):
     x = plt.figure(figsize=([3,3*m_ct]))
     for i,val in enumerate(test):
         plt.subplot(m_ct,1,i+1)
-        plt.plot(test[val],label= legends[0]+ ': ' +val)
-        plt.plot(np.array(data[val]),label=legends[1] +': '+ val)
+        plt.plot(test[val],'s-',label= legends[0]+ ': ' +val)
+        plt.plot(np.array(data[val]),'o-',label=legends[1] +': '+ val)
         plt.legend(loc=1)
     return x
         
@@ -293,7 +293,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [2, 24, 28, 40, 52, 70, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 298, 302]}
+# + {"code_folding": [2, 24, 28, 40, 52, 70, 89, 100, 155, 176, 197, 220, 237, 249, 278, 298, 302]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -617,7 +617,7 @@ class StickyExpectation:
             plt.plot(np.array(self.data_moms_dct[val]),'o-',label='data:'+ val)
             plt.legend(loc=1)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## test of ForecasterbySim
 #xx_history = AR1_simulator(rho,sigma,100)
 #xx_real_time = xx_history[20:]
@@ -636,6 +636,16 @@ class StickyExpectation:
 
 #mom_sim_and_pop = ForecastPlotDiag(mom_dct,mom_sim_dct)
 
+
+# +
+#test of ParaEstimate()
+#mom_sim_fake = mom_sim_dct.copy()
+#SE_instance.GetDataMoments(mom_sim_dct)
+#SE_instance.GetRealization(rho*xx_real_time+sigma*np.random.rand(len(xx_real_time)))
+#SE_instance.ParaEstimate(method='L-BFGS-B',
[…]

### 2019-10-30 workingfolder/python/DoEstimationWithData_Dev.py
Included all_moments = False in RE class. A few other ongoing development features including normalization of moment deviations by percentage, allowing for constant. allowing for diag plot to use two axises, etc, have not been incorporated in the GMMEst.py

@@ -1,0 +1,663 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:light
+#     text_representation:
+#       extension: .py
+#       format_name: light
+#       format_version: '1.4'
+#       jupytext_version: 1.2.3
+#   kernelspec:
+#     display_name: Python 3
+#     language: python
+#     name: python3
+# ---
+
+# ## Do the Estimation with SCE and SPF data
+#
+
+# ### 1. Importing estimation codes
+
+# +
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+
+from scipy.optimize import minimize
+
+import statsmodels.api as sm
+from statsmodels.tsa.api import AR
+# -
+
+from GMMEst import RationalExpectation as re
+from GMMEst_Dev import StickyExpectation as se
+from GMMEst_Dev import NoisyInformation as ni
+from GMMEst import ParameterLearning as pl
+from GMMEst import AR1_simulator, ForecastPlotDiag, ForecastPlot
+
+# + {"code_folding": [0]}
+## some parameters 
+rho = 0.95
+sigma = 0.1
+process_para = {'rho':rho,
+                'sigma':sigma}
+# -
+
+# ### 2. Preparing real-time data 
+
+# + {"code_folding": [0]}
+## CPI Core
+InfCPICMRT=pd.read_stata('../OtherData/InfCPICMRealTime.dta')  
+InfCPICMRT = InfCPICMRT[-InfCPICMRT.date.isnull()]
+
+## CPI 
+InfCPIMRT=pd.read_stata('../OtherData/InfCPIMRealTime.dta')  
+InfCPIMRT = InfCPIMRT[-InfCPIMRT.date.isnull()]
+
+# + {"code_folding": [0]}
+## dealing with dates 
+dateM_cpic = pd.to_datetime(InfCPICMRT['date'],format='%Y%m%d')
+dateM_cpi = pd.to_datetime(InfCPIMRT['date'],format='%Y%m%d')
+
+InfCPICMRT.index = pd.DatetimeIndex(dateM_cpic,freq='infer')
+InfCPIMRT.index = pd.DatetimeIndex(dateM_cpi,freq='infer')
+
+
+# + {"code_folding": [0]}
+## a function that turns vintage matrix to a one-dimension vector of real time data
+def GetRealTimeData(matrix):
+    periods = len(matrix)
+    real_time = np.zeros(periods)
+    for i in range(periods):
[…]

### 2019-10-30 workingfolder/python/GMMEst_Dev.py

@@ -31,7 +31,8 @@ import statsmodels.api as sm
 from statsmodels.tsa.api import AR
 import copy as cp 
 from scipy.stats import bernoulli
-
+import nlopt
+#from numpy import *
 
 # + {"code_folding": [0]}
 # a general-purpose estimating function of the parameter
@@ -60,7 +61,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": [1]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -75,11 +76,42 @@ def PrepMom(model_moments,
     diff: the Euclidean distance of two arrays of data and model 
     
     """
-    diff = np.linalg.norm(model_moments - data_moments)
+    diff = np.linalg.norm((model_moments - data_moments)/data_moments)
     return diff
 
 
-# + {"code_folding": [0, 1, 5, 19]}
+# + {"code_folding": [0]}
+## using nlopt library instead of scipy optimize
+def Estimator2(obj_func,
+               para_guess):
+    """
+    Inputs
+    ------
+    - moments: a function of the rigidity model parameter  
+
+    Outputs
+    -------
+    - parameter: an array of estimated parameter
+    """
+    opt = nlopt.opt(nlopt.LN_COBYLA,2)
+    opt.set_min_objective(obj_func)
+    parameter = opt.optimize(para_guess)
+    return parameter 
+
+
+# + {"code_folding": [0, 6]}
+def myfunc(x, grad):
+    if grad.size > 0:
+        grad[0] = 0.0
+        grad[1] = 0.5 / np.sqrt(x[1])
+    return np.sqrt(x[1])
+
+def myfunc0(x,
+            grad = None):
+    return np.sqrt(x**[0]+x[1]**2)
+
+
+# + {"code_folding": [0, 1, 5, 9, 18]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -88,7 +120,6 @@ np.random.seed(12345)
 def hstepfe(h,sigma,rho):
     return sum([rho**i*(np.random.randn(1)*sigma)*np.random.randn(h)[i] for i in range(h)])
 ## This is not correct. 
-
 
 def ForecastPlot(test):
     m_ct = len(test)
[…]

### 2019-10-30 workingfolder/python/GMMEst.py
add different scale plot for SE and NI class in GMMEst. Other features allowing for initial constants, for joint estimation, using NLOPTs estimations, etc. are still being developed.

@@ -127,7 +127,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [2, 16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 111, 115]}
+# + {"code_folding": [1, 2, 16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 111, 115]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -298,7 +298,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 24, 28, 40, 52, 70, 89, 100, 155, 176, 197, 220, 237, 249, 278, 298, 302]}
+# + {"code_folding": [1, 2, 24, 28, 40, 52, 70, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 308, 312]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -578,7 +578,8 @@ class StickyExpectation:
                 plt.legend(loc=1)
             
     def ForecastPlotDiag(self,
-                         all_moms = False):
+                         all_moms = False,
+                         diff_scale = False):
         exp_para_est_dct = {'lambda':self.para_est[0]}
         new_instance = cp.deepcopy(self)
         new_instance.exp_para = exp_para_est_dct
@@ -591,11 +592,20 @@ class StickyExpectation:
             
         m_ct = len(moments_to_plot)
         x = plt.figure(figsize=([3,3*m_ct]))
-        for i,val in enumerate(moments_to_plot):
-            plt.subplot(m_ct,1,i+1)
-            plt.plot(self.forecast_moments_est[val],'s-',label='model:'+ val)
-            plt.plot(np.array(self.data_moms_dct[val]),'o-',label='data:'+ val)
-            plt.legend(loc=1)
+        if diff_scale == False:
+            for i,val in enumerate(moments_to_plot):
+                plt.subplot(m_ct,1,i+1)
+                plt.plot(self.forecast_moments_est[val],'s-',label='model:'+ val)
+                plt.plot(np.array(self.data_moms_dct[val]),'o-',label='data:'+ val)
+                plt.legend(loc=1)
+        if diff_scale == True:
+            for i,val in enumerate(moments_to_plot):
+                ax1 = plt.subplot(m_ct,1,i+1)
[…]

### 2019-10-30 workingfolder/python/GMMEst_Dev.py

@@ -163,7 +163,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [0, 2, 16, 19, 30, 53, 77, 81, 92, 97, 115, 121]}
+# + {"code_folding": [2, 16, 19, 30, 53, 77, 81, 92, 97, 115, 121]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -340,7 +340,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [0, 2, 24, 28, 40, 52, 89, 93, 99, 154, 176, 197, 220, 225, 237, 249, 260, 278, 308, 312]}
+# + {"code_folding": [2, 24, 28, 40, 52, 89, 93, 99, 154, 176, 197, 220, 225, 237, 249, 260, 278, 308, 312]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -757,7 +757,7 @@ xx_real_time = xx_history[20:]
 # + {"code_folding": []}
 #SE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [0, 3, 27, 31, 37, 43, 55, 116, 184, 209, 215, 218, 236, 241, 253, 265, 280, 300, 315]}
+# + {"code_folding": [3, 27, 31, 37, 43, 55, 116, 184, 209, 215, 218, 236, 241, 253, 265, 280, 300, 315]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:
@@ -1182,7 +1182,7 @@ ni_instance.SimulateSignals()
 PL_para_default = SE_para_default
 
 
-# + {"code_folding": [0, 3, 25, 36, 62, 87, 120]}
+# + {"code_folding": [3, 25, 36, 62, 87, 120]}
 ### Paramter Learning(PL) class 
 
 class ParameterLearning:

### 2019-10-31 notes/GMMResults.tex
derived stochastic vol version of RE, SE, NI. and updated the GMM Est Notes.

@@
 
-\subsection{Different models of expectation formation}
-
-\subsubsection{Rational expectation}
+\subsection{Rational expectation}
 
@@
 	\begin{split}
-\hat y^*_{t+h|i,t} & =  E^*_{i,t}(y_{t+h}|I_{i,t}) = \tau_t 
+		\overline y^*_{t+h|t} \equiv y^*_{t+h|i,t} & =  E^*_{i,t}(y_{t+h}|I_{i,t}) = \theta_t 
+	\end{split}
+\end{eqnarray}
+
+Forecast error is simply the cumulated sum of unrealized shocks from $t$ to $t+h$, which is
+
+\begin{eqnarray}
+	\begin{split}
+		\overline{FE}^*_{t+h|t} \equiv  FE^*_{t+h|i,t} & =  \sum^{h}_{s=1} (\eta_{t+s} + \epsilon_{t+s})
 	\end{split}
@@
 	\begin{split}
-Var^*_{t+h|i,t} & = \sum^{h}_{t=0} E_{i,t}(\sigma^2_{\eta,t+h}) +  E_{i,t}(\sigma^2_{\epsilon,t+h})  \\
-& = \sum^{h}_{t=1} E_{i,t}(exp^{\log \sigma^2_{\eta,t}+\sum^h_{t=1}\mu_{\eta,t+h}}) +  E_{i,t}(exp^{\log \sigma^2_{\epsilon,t}+\sum^h_{t=0}\mu_{\epsilon,t+h}} ) \\
-& = \sigma^2_{\eta,t} \sum^{h}_{t=0} E_{i,t}(exp^{\sum^h_{t=1}\mu_{t+h,\eta}}) +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{t=1}\mu_{\epsilon,t+h}} ) \\
-& = \sigma^2_{\eta,t} \sum^{h}_{t=0} exp^{E_{i,t}({\sum^h_{t=1}\mu_{t+h,\eta}})- 0.5Var_{i,t}(\sum^h_{t=1}\mu_{t+h,\eta})} +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{t=1}\mu_{\epsilon,t+h}} ) \\
-& = \sigma^2_{\eta,t} \sum^{h}_{t=0} exp^{- 0.5h\gamma_{\eta}} +  \sigma^2_{\epsilon,t} exp^{- 0.5h\gamma_{\epsilon}}  \\
+		\overline{Var}^*_{t+h|t} \equiv  Var^*_{t+h|i,t} & = \sum^{h}_{k=1} E_{i,t}(\sigma^2_{\eta,t+k}) +  E_{i,t}(\sigma^2_{\epsilon,t+k})  \\
+		& = \sum^{h}_{k=1} E_{i,t}(exp^{\log \sigma^2_{\eta,t}+\sum^h_{k=1}\mu_{\eta,t+k}}) +  E_{i,t}(exp^{\log \sigma^2_{\epsilon,t}+\sum^h_{f=1}\mu_{\epsilon,t+f}} ) \\
+		& = \sum^{h}_{k=1}\sigma^2_{\eta,t} E_{i,t}(exp^{\sum^h_{k=1}\mu_{t+h,\eta}}) +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{f=1}\mu_{\epsilon,t+f}} ) \\
+		& = \sum^{h}_{k=1}\sigma^2_{\eta,t}  exp^{E_{i,t}({\sum^h_{k=1}\mu_{t+k,\eta}})- 0.5Var_{i,t}(\sum^h_{k=1}\mu_{t+k,\eta})} +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{f=1}\mu_{\epsilon,t+f}} ) \\
+		& = \sigma^2_{\eta,t} \sum^{h}_{k=1} exp^{- 0.5k\gamma_{\eta}} +  \sigma^2_{\epsilon,t} exp^{- 0.5h\gamma_{\epsilon}} 
 	\end{split} 
@@
 
-For instance, set $h=0$, the conditional volatility for the current inflation is
+One immediately see that now the volatility is stochastic at any point of the time.
+
+For instance, set $h=1$, the conditional volatility for the 1-step-ahead inflation is
 
@@
 	\begin{split}
-Var^*_{t|i,t} =  \sigma^2_{\eta,t}  +  \sigma^2_{\epsilon,t}
+		Var^*_{t+1|i,t} =  exp^{- 0.5\gamma_{\eta}} \sigma^2_{\eta,t}  +  exp^{- 0.5\gamma_{\epsilon}} \sigma^2_{\epsilon,t} 
+	\end{split} 
+\end{eqnarray}
+
+Disgreement is zero across agents in RE.
+
+\begin{eqnarray}
+	\begin{split}
+		\overline{Disg}^*_{t+h|t} =  0 
+	\end{split} 
+\end{eqnarray}
+
+\subsection{Sticky Expectation}
+
+An agent whose most recent up-do-date update happened at $t-\tau$, thus she sees all the realizations of stochastic variables up to $t-\tau$, including $y_{t-\tau}$, $\tau_{t-\tau}$, $\eta_{t-\tau}$, $\sigma_{\eta,t-\tau}$, $\sigma_{\epsilon,t-\tau}$.
+
+Her forecast is the permanent component that realized at time $t-\tau$.
+
+\begin{eqnarray}
+\begin{split}
+y_{t+h|i,t-\tau}  = \theta_{t-\tau} 
+\end{split}
+\end{eqnarray}
+
+Her forecast uncertainty is
+
+\begin{eqnarray}
+\begin{split}
+Var_{t+h|i,t-\tau} & = \sigma^2_{\eta,t-\tau} \sum^{h+\tau}_{k=1} exp^{- 0.5k\gamma_{\eta}} +  \sigma^2_{\epsilon,t-\tau} exp^{- 0.5(h+\tau)\gamma_{\epsilon}}
+\end{split} 
+\end{eqnarray}
+
+The population average of the two are, respectively, a weighted average of people whose the most update was in $t, t-1... t-\tau, t-\infty$, respectively.
+
+\begin{eqnarray}
+\begin{split}
+\overline y^{se}_{t+h|t} & = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda y_{t+h|t-\tau} \\
+& = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda \theta_{t-\tau}
+\end{split} 
+\end{eqnarray}
+
+\begin{eqnarray}
+\begin{split}
+\overline {Var}^{se}_{t+h|t} & = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda Var_{t+h|t-\tau} \\
+& = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda [ \sigma^2_{\eta,t-\tau} \sum^{h+\tau}_{k=1} exp^{- 0.5k\gamma_{\eta}} +  \sigma^2_{\epsilon,t-\tau} exp^{- 0.5(h+\tau)\gamma_{\epsilon}}]
+\end{split} 
+\end{eqnarray}
+
+Both forecast errors $\overline{FE}_{t+h|t}$ and disagreements takes similar form to that in AR process with time-invariant volatility.
+
+\begin{eqnarray}
+\begin{split}
+\overline {FE}^{se}_{t+h|t} & = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda {FE}^*_{t+h|t-\tau} 
+& = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda \sum^{\tau+h}_{s=1} (\theta_{t+s} + \epsilon_{t+s})  
+\end{split} 
+\end{eqnarray}
+
+The disagreement is the following.
+
+\begin{eqnarray}
+\begin{split}
+\overline{Disg}^{se}_{t+h|t} & =  \sum^{\infty}_{\tau=0} (1-\lambda)^{2\tau} \lambda^2 (y_{t+h|t-\tau} - \overline y^{se}_{t+h|t})^2  \\
+& = \sum^{\infty}_{\tau=0} (1-\lambda)^{2\tau} \lambda^2 (\theta_{t-\tau} - \overline y^{se}_{t+h|t})^2  \\
+& = \sum^{\infty}_{\tau=0} (1-\lambda)^{2\tau} \lambda^2 \{\theta_{t-\tau} - \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda \theta_{t-\tau}\}^2  
+\end{split} 
+\end{eqnarray}
+
+\subsection{Noisy Information}
+
+Now, the agent at time $t$ needs to recover the real-time permanent component $\theta_t$ to make the best forecast for future $y_{t+h}$ using nosiy signals.
+
+\begin{eqnarray}
+y^{ni}_{t+h|t}  \equiv  y^{ni}_{t+h|i,t} = \bar \theta_{t|t}
+\end{eqnarray}
+
+where $\bar \theta_{t|t}$ is generated through Kalman filtering.
+
+Assume that the nosiy signals of $\theta_t$ consists of a public signals $s^{pb}_{t}$ and the private signals $s^{pr}_{i,t}$.
+For simplicity, let us assume the public signal is basically the $y_t$.
+A more general case would be an independently drawn public signal sequence.
+The two signals can be again stacked into a vector of $2\times 1$ to $s^\theta_{i,t}$.
+
+Then the filterred $\theta_{t}$ by agent $i$ is
+
+\begin{eqnarray}
+\begin{split}
+\bar \theta_{t|t} =  (1-\tilde P_{t} H) \bar \theta_{t|t-1} + \tilde P s^\theta_{i,t} \\
+\end{split}
+\end{eqnarray}
+
+where $\theta_{t|t-k}$ is the filterred forecast of $\theta_t$ using all the information up to $t-k$., and $\tilde Pt$ is the time-specific Kalman gain that is dependent on the noisy ratios of signals.
+
+\begin{eqnarray}
+\begin{split}
+\tilde P_{t} =  \Sigma^\theta_{i,t|t-1} H(H'\Sigma^\theta_{i,t|t-1} H + \Sigma^\theta_{t})^{-1} 
+\end{split}
+\end{eqnarray}
+
+Now the noisiness of signals are time varying as well.
+
+\begin{eqnarray}
+\begin{split}
+\Sigma^\theta_t =  \left[ \begin{matrix} 
+\sigma^2_{\eta,t} &  0 \\ 
+0 & \sigma^2_\xi \end{matrix}\right] 
+\end{split}               
+\end{eqnarray}
+
+where the variance of public signal is the time-varying $\sigma^2_{\eta,t}$ and let us assume the private signals have constant nosiness $\sigma^2_{\xi}$.
+
+The uncertainty matrix evolves in the following manner.
+
+\begin{eqnarray}
+\Sigma^\theta_{i,t|t} = \Sigma^\theta_{i,t|t-1} - \Sigma^\theta_{i,t|t-1} H'(H \Sigma^\theta_{i,t-1} H' +\Sigma^\theta_{t}) H \Sigma^\theta_{i,t|t-1} 
+\end{eqnarray}
+
+Notice now that since prior of $\theta_t$ before time period $t$ is a weighted average of previous realizations of $y$ and past signals, current forecast depends on the past realizations even though the rational forecast is up-to-date $\theta_t$.
+
+Due to the time-varying volatility $\sigma^2_{\eta,t}$, the noisyness of the public signal is also time-varying, which governs the degree of rigidity.
+For instance, if volatility to the transitory shock is high, the Kalman gain is low, the forecast responds less to the new realizations.
+
+It is also worth thinking about what is the one-step ahead uncertainty in the context of stochastic valotility world.
+
+\begin{eqnarray}
+\begin{split}
+\Sigma^\theta_{i,t|t-1} & = \Sigma^\theta_{i,t-1|t-1} + Var^*_{t|t-1}(y_t) \\
+& = \Sigma^\theta_{i,t-1|t-1} +  exp^{- 0.5\gamma_{\eta}} \sigma^2_{\eta,t-1}  +  exp^{- 0.5\gamma_{\epsilon}} \sigma^2_{\epsilon,t-1} 
 \end{split}

### 2019-10-31 workingfolder/python/GMMEst-StochasticVol.py

@@ -13,7 +13,7 @@
 #     name: python3
 # ---
 
-# ## GMM Estimation of Model Parameters of Expectation Formation(Stochastic Volatility Process)
+# ## GMM Estimation of Model Parameters of Expectation Formation (Stochastic Volatility Process)
 #
 # - This notebook includes functions that estimate the parameter of rigidity for different models
 # - It allows for flexible choices of moments to be used, forecast error, disagreement, and uncertainty, etc. 
@@ -22,14 +22,14 @@
 #   - Model-specific functions that take real-time data and process parameters as inputs and produces forecasts and moments as outputs. It is model-specific because different models of expectation formation bring about different forecasts. 
 #   - Auxiliary functions that compute the moments as well as the difference of data and model prediction, which will be used as inputs for GMM estimator. 
 
-# ## 1. A process of time-variant volatility 
+# ## 1. A process of time-varying volatility 
 #
 # Assume that the inflation follows a process of unobserved components model with stochastical volatility. 
 #
 # \begin{equation}
 # \begin{split}
-# & y_t = \tau_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
-# & \tau_t = \tau_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
+# & y_t = \theta_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
+# & \theta_t = \theta_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
 # & \log\sigma^2_{\eta,t} = \log\sigma^2_{\eta,t-1} + \mu_{\eta,t} \\
[…]

### 2019-10-31 workingfolder/python/GMMEst_Dev.py

@@ -80,7 +80,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## using nlopt library instead of scipy optimize
 def Estimator2(obj_func,
                para_guess):
@@ -93,13 +93,14 @@ def Estimator2(obj_func,
     -------
     - parameter: an array of estimated parameter
     """
-    opt = nlopt.opt(nlopt.LN_COBYLA,2)
+    opt = nlopt.opt(nlopt.LN_BOBYQA,2)
+    #opt.set_maxtime(20)
     opt.set_min_objective(obj_func)
     parameter = opt.optimize(para_guess)
     return parameter 
 
 
-# + {"code_folding": [0, 6]}
+# + {"code_folding": [6]}
 def myfunc(x, grad):
     if grad.size > 0:
         grad[0] = 0.0
@@ -107,8 +108,17 @@ def myfunc(x, grad):
     return np.sqrt(x[1])
 
 def myfunc0(x,
-            grad = None):
+            grad):
+    if grad.size>0:
+        grad[0] = None
+        grad[1] = None
     return np.sqrt(x**[0]+x[1]**2)
+
+
+# -
+
+Estimator2(myfunc0,
+          para_guess = [0.1,0.2])
 
 
 # + {"code_folding": [0, 1, 5, 9, 18]}
@@ -163,7 +173,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [2, 16, 19, 30, 53, 77, 81, 92, 97, 115, 121]}
+# + {"code_folding": [0, 2, 16, 19, 30, 53, 77, 104, 108, 119, 124, 142, 148]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -241,6 +251,33 @@ class RationalExpectation:
         obj_func = PrepMom(RE_moms,data_moms)
         return obj_func 
     
+    def RE_EstObjfunc2(self,
+                      process_para,
+                      grad):
+        """
+        input
+        -----
+        process_para: the parameters of process to be estimated. 
+           No expectation parameters because it is rational expectation
+        
+        output
+        -----
+        the objective function to minmize
+        """
+        if grad.size>0:
+            for i in range(len(grad)):
+                grad[i] = None
+        moments = self.moments
+        re_process_para = {'rho':process_para[0],
+                           'sigma':process_para[1]}
[…]

### 2019-11-01 workingfolder/python/GMMEst-StochasticVol.py
stochastical volatility version of RE finished. But first draft. Need to debug. Major changes include the change to information set. Information set contains permanent component and real-time volatility instead of real-time y as in AR1

@@ -24,7 +24,7 @@
 
 # ## 1. A process of time-varying volatility 
 #
-# Assume that the inflation follows a process of unobserved components model with stochastical volatility. 
+# Assume that the inflation follows a process of unobserved component model with stochastical volatility. (UC-SV model by Watson and Stock. 2007)
 #
 # \begin{equation}
 # \begin{split}
@@ -278,20 +278,30 @@ def PrepMom(model_moments,
     diff: the Euclidean distance of two arrays of data and model 
     
     """
-    diff = np.linalg.norm(model_moments - data_moments)
+    diff = np.linalg.norm((model_moments - data_moments)/data_moments)
     return diff
 
 
-# + {"code_folding": [0, 1, 5]}
+# + {"code_folding": [1, 20, 28, 40]}
 ## auxiliary functions 
-def hstepvar(h,sigma,rho):
-    return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
-
-np.random.seed(12345)
-def hstepfe(h,sigma,rho):
-    return sum([rho**i*(np.random.randn(1)*sigma)*np.random.randn(h)[i] for i in range(h)])
-## This is not correct. 
-
+def hstepvarSV(h,
+               sigmas_now,
+               gammas):
+    '''
+    inputs
+    ------
+    h: forecast horizon
+    sigmas_nows, 2 x 1 vector [sigma_eta, sigma_eps]
+    gamma, volatility, 2 x 1 vector [gamma_eta,gamma_eps]
+    
+    outputs
+    -------
+    scalar: h-step-forward variance 
+    '''
+    var_eta = sigmas_now[0]**2*sum([np.exp(-0.5*(k+1)*gammas[0]) for k in range(h)])
+    var_eps = sigmas_now[1]**2*np.exp(-0.5*h*gammas[1])
+    var = var_eta + var_eps
+    return var
 
 def ForecastPlot(test):
     x = plt.figure(figsize=([3,13]))
@@ -301,7 +311,9 @@ def ForecastPlot(test):
         plt.legend(loc=1)
     return x
         
-def ForecastPlotDiag(test,data,legends=['model','data']):
+def ForecastPlotDiag(test,
+                     data,
+                     legends=['model','data']):
     x = plt.figure(figsize=([3,13]))
     for i,val in enumerate(test):
         plt.subplot(4,1,i+1)
[…]

### 2019-11-01 workingfolder/python/GMMEst-StochasticVol.py
Stochastic volatility version is done for SE, NI as well. NI is written in general way for public signals. Now need to write seperate codes to estimate the model parameters as an econometricians.

@@ -364,7 +364,7 @@ process_para = {'gammas':gammas_fake,
                 'eta0':eta0_fake}
 
 
-# + {"code_folding": [1, 2, 15, 20, 38, 71, 94, 98, 109, 116]}
+# + {"code_folding": [0, 2, 16, 20, 38, 70, 93, 97, 110, 115, 116]}
 ## Rational Expectation (RE) class for UCSV model 
 class RationalExpectationSV:
     def __init__(self,
@@ -379,12 +379,12 @@ class RationalExpectationSV:
         self.horizon = horizon
         self.process_para = process_para
         self.moments = moments
+        self.n = len(real_time['eta'])
     
     def GetRealization(self,
                        realized_series):
         self.realized = realized_series
         
-    ## this is not exactly right
     def SimulateRealization(self):
         n = len(self.real_time['eta'])
         ## information set 
@@ -405,11 +405,11 @@ class RationalExpectationSV:
         
     def Forecaster(self):
         ## parameters
-        n = len(self.real_time['eta'])
+        n = self.n
         gammas = self.process_para['gammas']
         eta0 = self.process_para['eta0']
         
-        ## parameters
+        ## inputs
         real_time = self.real_time
         horizon = self.horizon
         
@@ -423,7 +423,6 @@ class RationalExpectationSV:
         sigmas_now = infoset['vols']
         Var = np.zeros(n)
         for i in range(n):
-            #print(sigmas_now[:,i])
             Var[i] = hstepvarSV(horizon,
                                 sigmas_now = sigmas_now[:,i],
                                 gammas = gammas)
@@ -502,6 +501,11 @@ ucsv_fake = UCSV_simulator(gammas_fake,
                            nobs = 100) 
 n_burn = 20
 # the permanent component
+
+xx_history = ucsv_fake[0]
+xx_real_time = xx_history[n_burn:]
+
+
 xx_pc_history = ucsv_fake[1]
 xx_pc_real_time = xx_pc_history[n_burn:]
 
@@ -510,15 +514,17 @@ vol_history = np.array([ucsv_fake[2],ucsv_fake[3]])
 vol_real_time = vol_history[:,n_burn:]
 
 xx_real_time_dct = {'eta':xx_pc_real_time,
-                   'vols':vol_real_time}
+                   'vols':vol_real_time,
+                   'y':xx_real_time}
 
 xx_history_dct = {'eta':xx_pc_history,
-                  'vols':vol_history}
+                  'vols':vol_history,
+                  'y':xx_history}
 
[…]

### 2019-11-01 workingfolder/python/GMMEst.py

@@ -298,7 +298,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [1, 2, 24, 28, 40, 52, 70, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 308, 312]}
+# + {"code_folding": [2, 24, 28, 40, 52, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 308, 312]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,

### 2019-11-02 workingfolder/python/stockwatson.m
have a stockwatson version of the estimation of UCSV.But not working.

@@ -1,0 +1,158 @@
+function [sd_eps,sd_eta,tau]=stockwatson(y,var_eps_min,var_eta_min);
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Code for computing the permanent-transitory decomposition in Stock     %
+%-Watson, JMCB, 2007, by MCMC.                                          %
+%Written by Mark Watson in Gauss (incorporating revision of May 3 2007) %
+%Translated to Matlab by Jonathan Wright                                %
+%Input: The inflation series                                            %
+%Outputs:                                                               %
+%sd_eps: Standard deviation of permanent component                      %
+%sd_eta: Standard deviation of transitory component                     %
+%tau: Estimated permanent component                                     % 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+n=length(y);
+randn('seed',123); rand('seed',123);
+
+vague = 1000;
+burnin=100;
+ndraw=5100;
+
+%Parameters for log-chi-squared errors%
+r_p=.086;
+r_m1=-7.472;
+r_m2=-0.698;
+r_sig2=1.411;
+r_sig=sqrt(r_sig2);
+
+%Parameters for RW Innovation Variance%
+tau1=.20;  
+tau2=.20;  
+q_p=1.0;     %Prob of Regime 1...note that here we are always in regime 1, but it could be otherwise.
+q1=tau1^2;
+q2=tau1^2;
+
+params=[r_p;r_m1;r_m2; r_sig; r_sig2;q_p;q1;q2;tau1;tau2;vague];
+
+
+%Parameters for Initial Conditions, bounds and so forth%
+    tau0=mean(y(1:4));  %average of first few observations
+    dy=y(2:end)-y(1:end-1);
+    var_dy = (std(dy))^2;
[…]

### 2019-11-11 notes/GMMResults.tex
Rewrote the draft of the GMMEst note to include results for SV as well as the theoretical derivations of the SV model.

@@
 \maketitle
-
-\section{A Generic Framework}
-
-For a given process of inflation and a particular theory of expectation formation, the GMM estimate of the vector of parameters $\Omega$ is defined as the following.
-
-\begin{eqnarray}
-\widehat \Omega = \underset{\Omega }{argmin} (M_{\textrm{data} } - F(\Omega, Y)) W  (M_{\textrm{data} } - F(\Omega, Y))'
-\end{eqnarray}
-
-\begin{itemize}
-	\item  $\Omega$ is a vector of size of $k$, depending on the number of parameters to be estimated. 
-	\item $M_{data}$ is the moments computed from data, i.e.
-mean forecasts, average forecast errors, the cross-sectional variance of forecasts (disagreement), average uncertainty, etc.
-Also the autocovariance of all the abovementioned.
-
-	\item $F$ is the moments that are generated from a certain theory of expectation formation and inflation process.
-It is a function of parameters $\Omega$ as well as the $Y$, the real-time data(including history) that is available to forecasters at each point of the time $t$.
-	\item For instance, for $T$ periods, $Y$ includes $T$  sequences of real-time inflation data of different lengths that terminate at each point of the forecasting:  $t =0$, $t=1$... $t=T$ . 
-	\item  Both $M$ and $F$ is of the size  $m$, depending on the number of moments used for estimation.
-For instance, if we only estimate expectation formation using mean forecasts, disagreements and forecast errors while taking the inflation process as given, there are three moments, thus $m = 3$.
-If we include autocovariance of forecast errors, then $m=4$.
-
-	\item $W$ is the weighting matrix. For now, I stick to the identity matrix. 
-\end{itemize}
-
-The above procedure is specific to a pair of assumed inflation process and a theory of expectation.
-It can be estimated only for the theory of expectation formation with exogenous fed parameters of the inflation process using the entire history of inflation data, or we could jointly estimate the parameters of expectation formation and the inflation process.
-
-\section{Estimation}
-\subsection{Real-time Data}
-
-When agents form their expectations of inflation at any point of the time, what is potentially available to them is the real-time inflation data, namely those released from the most update-to-date vintage of the inflation.
-In order to match as close as possible the information set available to the forecasting agents, we need to use real-time data for each particular point of time.
-
-These real-time vintage inflation data since 1998 were obtained from the Real-Time Data Research Center hosted by the Federal Reserve Bank of Philadelphia.
-
-To get an idea of how much of the differences there are between the real-time inflation and the most recent vintage in 2018, Figure \ref{real_time_rev} and \ref{ts_real_time_current_vintage} plot, respectively, the distributions of the revisions as well as the time series of the inflation.
-Although overall, there is no obvious skewness of the revisions, there have been indeed sizable revisions made for the real-time data.
-
-\begin{figure}[htbp]
-		\centering
-\includegraphics[width=0.7\textwidth]{figures/hist_rev_realtime.png}
-\caption{Revisions of Current-vintage from Real-time Core CPI}
-\label{real_time_rev}
-	\begin{flushleft}
-	{\footnotesize Note: real-time data  at time $t$ is defined the inflation from $t-1$ to $t$ according to the most recent vintage of CPI inflation at time $t$. The period is between 2000 M1-2018 M3.}
-\end{flushleft}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.8\textwidth]{figures/ts_rev_realtime.png}
-	\caption{Current-vintage and Real-time Core CPI}
-	\label{ts_real_time_current_vintage}
-\end{figure}
-
-\subsection{Results}
-
-\subsubsection{Professional Forecasters}
-
-Figure \ref{SE_diag_SPF} and \ref{SE_diag_joint_SPF} plot the estimated moments for SE model together with the data moments professional forecasts of SPF.
-
-From left to the right, the four columns of the figures are based on estimation using different choices of moments.
-
-Figure \ref{NI_diag_SPF} and \ref{NI_diag_joint_SPF} plot the estimated moments for NI model together with the data moments professional forecasts of SPF.
-
-\begin{figure}[ht]
-	\centering
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Estimation of SE for Professionals}
-		\label{SE_diag_SPF}
-		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag0.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag1.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag2.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag3.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag4.png}
-	\end{subfigure}
-	\vspace{1em}
-	\vfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Joint Estimation of SE and Inflation Process}
-		\label{SE_diag_joint_SPF}
-	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag0.png}
-	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag1.png}
-	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag2.png}
-	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag3.png}
-	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag4.png}
-	\end{subfigure}
-	\\
-	\begin{flushleft}
-		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
-The bottom panel estimates the parameters of expectation formation and inflation process jointly.
-From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
-}
-	\end{flushleft}
-	\caption{SE of Professionals: Esimated Model Moments and Data Moments}
-\end{figure}
-
-\begin{figure}[ht]
-	\centering
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Estimation of NI for Professionals}
-		\label{NI_diag_SPF}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag0.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag1.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag2.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag3.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag4.png}
-	\end{subfigure}
-	\vspace{1em}
-	\vfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Joint Estimation of NI and Inflation Process}
-		\label{NI_diag_joint_SPF}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag0.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag1.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag2.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag3.png}
-		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag4.png}
-	\end{subfigure}
-	\\
-	\begin{flushleft}
-		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
-The bottom panel estimates the parameters of expectation formation and inflation process jointly.
-From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
-}
-	\end{flushleft}
-	\caption{NI of Professionals: Esimated Model Moments and Data Moments}
-\end{figure}
-
-\subsubsection{Households}
-
-Figure \ref{SE_diag_SCE} and \ref{SE_diag_joint_SCE} plot the estimated moments for SE model together with the data moments of households inflation forecasts from SCE.
-
-From left to the right, the four columns of the figures are based on estimation using different choices of moments.
-
-Figure \ref{NI_diag_SCE} and \ref{NI_diag_joint_SCE} plot the estimated moments for NI model together with the data moments of households inflation forecasts from SCE.
-
-\begin{figure}[htbp]
-	\centering
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Estimation of SE for Households}
-		\label{SE_diag_SCE}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag0.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag1.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag2.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag3.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag4.png}
-	\end{subfigure}
-	\vspace{1em}
-	\vfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Joint Estimation of SE and Inflation Process}
-		\label{SE_diag_joint_SCE}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag0.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag1.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag2.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag3.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag4.png}
-	\end{subfigure}
-	\\
-	\begin{flushleft}
-		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
-The bottom panel estimates the parameters of expectation formation and inflation process jointly.
-From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
-}
-	\end{flushleft}
-	\caption{SE of Households: Esimated Model Moments and Data Moments}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Estimation of NI  for Households}
-		\label{NI_diag_SCE}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag0.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag1.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag2.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag3.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag4.png}
-	\end{subfigure}
-	\vspace{1em}
-	\vfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\caption{Joint Estimation of SE and Inflation Process}
-		\label{NI_diag_joint_SCE}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag0.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag1.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag2.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag3.png}
-		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag4.png}
-	\end{subfigure}
-	\\
-	\begin{flushleft}
-		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
-The bottom panel estimates the parameters of expectation formation and inflation process jointly.
-From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
-}
-	\end{flushleft}
-	\caption{NI of Households: Esimated Model Moments and Data Moments}
-\end{figure}
-
-	\begin{sidewaystable}[t]
-		\centering
-	\caption{GMM Estimates of Parameters of SE and Inflation Process}
-	\label{GMM_Est_SE_Table}
-\begin{tabular}{llllllllllll}
-	\hline 
-	0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
-	\hline 
-	Forecast &    &      &     & 0.21                       & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
-	\hline 
-	FE       &    &      &     & 0.18                       & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
-	\hline 
-	Forecast & FE &      &     & 0.2                        & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
-	\hline 
-	Forecast & FE & Disg &     & 0.23                       & 0.05                       & 1          & 0.1          & 0.02                       & 0.03                       & 0.98       & 0.1          \\
-	\hline 
-	Forecast & FE & Disg & Var & 0.26                       & 0.05                       & 1          & 0.07         & 0.01                       & 0.03                       & 0.98       & 1.11        \\
-	\hline 
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}[t]
-	\centering
-	\caption{GMM Estimates of Parameters of NI and Inflation Process}
-	\label{GMM_Est_NI_Table}
-\begin{tabular}{llllllllllllllll}
-	\hline 
-	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
-	\hline 
-	Forecast &    &      &     & 376.66                    & 1.26                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0                         & 1.13                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
-	\hline 
-	FE       &    &      &     & 1.04                      & 159.74                & 0.5                       & 0.5                   & 0.8        & 0.1          & 0                         & 1.26                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
-	\hline 
-	Forecast & FE &      &     & 1.14                      & 6.74                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0.59                      & 0.36                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
-	\hline 
-	Forecast & FE & Disg &     & 1.39                      & 1.46                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 2354.37                   & 10.93                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
-	\hline 
-	Forecast & FE & Disg & Var & 1.37                      & 1.1                   & 0.5                       & 0.5                   & 0.8        & 0.1          & 35263.31                  & 332.04                & 0.5                       & 0.5                   & 0.8        & 0.1         \\
-	\hline 
-\end{tabular}
-\end{sidewaystable}
 
@@
 
+\section{Estimation: a Generic Framework}
+
+For a given process of inflation and a particular theory of expectation formation, the GMM estimate of the vector of parameters $\Omega$ is defined as the following.
+
+\begin{eqnarray}
+\widehat \Omega = \underset{\Omega }{argmin} (M_{\textrm{data} } - F(\Omega, Y)) W  (M_{\textrm{data} } - F(\Omega, Y))'
+\end{eqnarray}
+
+\begin{itemize}
+	\item  $\Omega$ is a vector of size of $k$, depending on the number of parameters to be estimated. 
+	\item $M_{data}$ is the moments computed from data, i.e.
+mean forecasts, average forecast errors, the cross-sectional variance of forecasts (disagreement), average uncertainty, etc.
+Also the autocovariance of all the abovementioned.
+
+	\item $F$ is the moments that are generated from a certain theory of expectation formation and inflation process.
+It is a function of parameters $\Omega$ as well as the $Y$, the real-time data(including history) that is available to forecasters at each point of the time $t$.
+	\item For instance, for $T$ periods, $Y$ includes $T$  sequences of real-time inflation data of different lengths that terminate at each point of the forecasting:  $t =0$, $t=1$... $t=T$ . 
+	\item  Both $M$ and $F$ is of the size  $m$, depending on the number of moments used for estimation.
+For instance, if we only estimate expectation formation using mean forecasts, disagreements and forecast errors while taking the inflation process as given, there are three moments, thus $m = 3$.
+If we include autocovariance of forecast errors, then $m=4$.
+
+	\item $W$ is the weighting matrix. For now, I stick to the identity matrix. 
+\end{itemize}
+
+The above procedure is specific to a pair of assumed inflation process and a theory of expectation.
+It can be estimated only for the theory of expectation formation with exogenous fed parameters of the inflation process using the entire history of inflation data, or we could jointly estimate the parameters of expectation formation and the inflation process.
+
+\subsection{Real-time Data}
+
+When agents form their expectations of inflation at any point of the time, what is potentially available to them is the real-time inflation data, namely those released from the most update-to-date vintage of the inflation.
+In order to match as close as possible the information set available to the forecasting agents, we need to use real-time data for each particular point of time.
+
+These real-time vintage inflation data since 1998 were obtained from the Real-Time Data Research Center hosted by the Federal Reserve Bank of Philadelphia.
+
+To get an idea of how much of the differences there are between the real-time inflation and the most recent vintage in 2018, Figure \ref{real_time_rev} and \ref{ts_real_time_current_vintage} plot, respectively, the distributions of the revisions as well as the time series of the inflation.
+Although overall, there is no obvious skewness of the revisions, there have been indeed sizable revisions made for the real-time data.
+
+\begin{figure}[htbp]
+		\centering
+\includegraphics[width=0.7\textwidth]{figures/hist_rev_realtime.png}
+\caption{Revisions of Current-vintage from Real-time Core CPI}
+\label{real_time_rev}
+	\begin{flushleft}
+	{\footnotesize Note: real-time data  at time $t$ is defined the inflation from $t-1$ to $t$ according to the most recent vintage of CPI inflation at time $t$. The period is between 2000 M1-2018 M3.}
+\end{flushleft}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.8\textwidth]{figures/ts_rev_realtime.png}
+	\caption{Current-vintage and Real-time Core CPI}
+	\label{ts_real_time_current_vintage}
+\end{figure}
+
+\subsection{Results for AR1}
+
+\subsubsection{Professional Forecasters}
+
+Figure \ref{SE_diag_SPF} and \ref{SE_diag_joint_SPF} plot the estimated moments for SE model together with the data moments professional forecasts of SPF.
+
+From left to the right, the four columns of the figures are based on estimation using different choices of moments.
+
+Figure \ref{NI_diag_SPF} and \ref{NI_diag_joint_SPF} plot the estimated moments for NI model together with the data moments professional forecasts of SPF.
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SE for Professionals}
+		\label{SE_diag_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{SE_diag_joint_SPF}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag0.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag1.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag2.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag3.png}
+	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{SE of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NI for Professionals}
+		\label{NI_diag_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of NI and Inflation Process}
+		\label{NI_diag_joint_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{NI of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Parameter Learning for Professionals}
+		\label{PL_diag_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_pl_est_diag.png}
+	\end{subfigure} \\
+	\begin{flushleft}
+		{\footnotesize Note: the figure plots the predicted moments for a prameter learning (PL) model with AR(1) process of inflation.}
+	\end{flushleft}
+	\caption{PL of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\subsubsection{Households}
+
+Figure \ref{SE_diag_SCE} and \ref{SE_diag_joint_SCE} plot the estimated moments for SE model together with the data moments of households inflation forecasts from SCE.
+
+From left to the right, the four columns of the figures are based on estimation using different choices of moments.
+
+Figure \ref{NI_diag_SCE} and \ref{NI_diag_joint_SCE} plot the estimated moments for NI model together with the data moments of households inflation forecasts from SCE.
+
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SE for Households}
+		\label{SE_diag_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{SE_diag_joint_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{SE of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NI  for Households}
+		\label{NI_diag_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag4.png}
+	\end{subfigure}
+	\vspace{1em}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Joint Estimation of SE and Inflation Process}
+		\label{NI_diag_joint_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag4.png}
+	\end{subfigure}
+	\\
+	\begin{flushleft}
+		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given.
+The bottom panel estimates the parameters of expectation formation and inflation process jointly.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{NI of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+	\begin{sidewaystable}[t]
+		\centering
+	\caption{GMM Estimates of Parameters of SE and Inflation Process}
+	\label{GMM_Est_SE_Table}
+\begin{tabular}{llllllllllll}
+	\hline 
+	& 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
+	\hline 
+	Forecast &    &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
+	FE       &    &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
+	Forecast & FE &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
+	Forecast & FE & Disg &     & 0.7                        & 0.38                       & 0.88       & 0.1          & 0.02                       & 0.03                       & 0.98       & 0.1          \\
+	Forecast & FE & Disg & Var & 0.7                        & 0.38                       & 0.88       & 0.2          & 0.01                       & 0.03                       & 0.98       & 1.11     \\
+	\hline    
+\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}[t]
+	\centering
+	\caption{GMM Estimates of Parameters of NI and Inflation Process}
+	\label{GMM_Est_NI_Table}
+\begin{tabular}{llllllllllllllll}
+	\hline 
+	0        & 1   & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
+	\hline 
+	Forecast &     &      &     & 5.64                      & 804.51                & 0.5                       & 0.5                   & 1          & 0.1          & 93.17                     & 0.64                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	FE       &     &      &     & 2197.33                   & 60.45                 & 0.5                       & 0.5                   & 1          & 0.1          & 0.62                      & 0.34                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	Forecast & FE  &      &     & 8565.83                   & 176.23                & 0.5                       & 0.5                   & 1          & 0.1          & 0.62                      & 0.44                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	Forecast & FE  & Disg &     & 30.39                     & 353.42                & 0.5                       & 0.5                   & 1          & 0.1          & 3154.03                   & 10.93                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	Forecast & FE  & Disg & Var & 2.43                      & 63.03                 & 0.5                       & 0.5                   & 1          & 0.1          & 22970.9                   & 332.03                & 0.5                       & 0.5                   & 0.8        & 0.1          \\
+	Disg     & Var &      &     & 90.12                     & 0.56                  & 0.5                       & 0.5                   & 1          & 0.1          & 3297.11                   & 333.49                & 0.5                       & 0.5                   & 0.8        & 0.1       \\
+	\hline   
+\end{tabular}
+\end{sidewaystable}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Parameter Learning for Households}
+		\label{PL_diag_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_pl_est_diag.png}
+	\end{subfigure} \\
+	\begin{flushleft}
+		{\footnotesize Note: the figure plots the predicted moments for a prameter learning (PL) model with AR(1) process of inflation.}
+	\end{flushleft}
+	\caption{PL of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\subsection{Results for Stochastic Volatility}
+
+\subsubsection{Professionals Forecasters}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SESV for Professionals}
+		\label{SESV_diag_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag4.png}
+	\end{subfigure}
+	\begin{flushleft}
+		{\footnotesize Note: this figures plot the data and estimated moments for a  sticky expectation (SE) model with stochastical volatility to inflation.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{SESV of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NISV for Professionals}
+		\label{NISV_diag_SPF}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag4.png}
+	\end{subfigure}
+	\begin{flushleft}
+		{\footnotesize Note: this figures plot the data and estimated moments for a noisy information (NI) model  with stochastical volatility to inflation.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{NISV of Professionals: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\subsubsection{Households}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of SESV for Households}
+		\label{SESV_diag_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag4.png}
+	\end{subfigure}
+	\begin{flushleft}
+		{\footnotesize Note: this figures plot the data and estimated moments for a  sticky expectation (SE) model with stochastical volatility to inflation.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{SESV of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\caption{Estimation of NISV for Households}
+		\label{NISV_diag_SCE}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag0.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag1.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag2.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag3.png}
+		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag4.png}
+	\end{subfigure}
+	\begin{flushleft}
+		{\footnotesize Note: this figure plots the data and estimated moments for a noisy information (NI) model  with stochastical volatility to inflation.
+From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.
+}
+	\end{flushleft}
+	\caption{NISV of Households: Esimated Model Moments and Data Moments}
+\end{figure}
+
+\begin{sidewaystable}[t]
+	\centering
+	\caption{GMM Estimates of Parameters of SESV}
+	\label{GMM_Est_SE_SV_Table}
+	\begin{tabular}{llllll}
+		\hline 
+		0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
+		\hline 
+		Forecast &    &      &     & 0.23                       & 0.01                       \\
+		FE       &    &      &     & 0.12                       & 1                          \\
+		Forecast & FE &      &     & 0.12                       & 1                          \\
+		Forecast & FE & Disg &     & 0.12                       & 1                          \\
+		Forecast & FE & Disg & Var & 0.12                       & 1           \\
+		\hline               
+	\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}[t]
+	\centering
+	\caption{GMM Estimates of Parameters of NISV}
+	\label{GMM_Est_NI_SV_Table}
+\begin{tabular}{llllllllllllll}
+		\hline 
+	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & $y$ & Disg & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & $y$ & Disg \\
+	\hline 
+	Forecast &    &      &     & 0.05                      & 0.02                  & 0.54  & 1   & 5    & 12.09                     & 12.16                 & 0     & 1   & 2    \\
+	FE       &    &      &     & 0                         & 0.27                  & 1.06  & 1   & 5    & 130.13                    & 764.51                & 30.99 & 1   & 2    \\
+	Forecast & FE &      &     & 0.16                      & 0                     & 1.06  & 1   & 5    & 168.48                    & 695.91                & 43.31 & 1   & 2    \\
+	Forecast & FE & Disg &     & 0                         & 0.22                  & 1.06  & 1   & 5    & 166.89                    & 6.1                   & 0.03  & 1   & 2    \\
+	Forecast & FE & Disg & Var & 0                         & 0.24                  & 1.07  & 1   & 5    & 362.11                    & 6.26                  & 0.04  & 1   & 2   \\
+	\hline 
+\end{tabular}
+\end{sidewaystable}
+
 \end{document}

### 2019-11-11 workingfolder/python/DoEstimationWithData.py

@@ -83,7 +83,7 @@ real_time_cpi =  pd.Series(GetRealTimeData(matrix_cpi) )
 real_time_cpic.index =  InfCPICMRT.index #+ pd.DateOffset(months=1) 
 real_time_cpi.index = InfCPIMRT.index #+ pd.DateOffset(months=1)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## turn index into yearly inflation
 real_time_index =pd.concat([real_time_cpic,real_time_cpi], join='inner', axis=1)
 real_time_index.columns=['RTCPI','RTCPICore']
@@ -95,13 +95,11 @@ real_time_inf.tail()
 # ### 3. Estimating using real-time inflation and expectation data
 #
 
-# + {"code_folding": [0, 6]}
+# + {"code_folding": [6]}
 ## exapectation data from SPF 
 PopQ=pd.read_stata('../SurveyData/InfExpQ.dta')  
 PopQ = PopQ[-PopQ.date.isnull()]
-
 dateQ = pd.to_datetime(PopQ['date'],format='%Y%m%d')
-
 dateQ_str = dateQ.dt.year.astype(int).astype(str) + \
              "Q" + dateQ.dt.quarter.astype(int).astype(str)
 PopQ.index = pd.DatetimeIndex(dateQ_str)
@@ -109,9 +107,25 @@ PopQ.index = pd.DatetimeIndex(dateQ_str)
 SPFCPI = PopQ[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var']].dropna(how='any')
 
 
+## expectation data from SCE
+
+PopM = pd.read_stata('../SurveyData/InfExpM.dta')
+PopM = PopM[-PopM.date.isnull()]
+dateM = pd.to_datetime(PopM['date'],format='%Y%m%d')
+dateM_str = dateM.dt.year.astype(int).astype(str) + \
+             "M" + dateM.dt.month.astype(int).astype(str)
+PopM.index = pd.DatetimeIndex(dateM)
+SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']].dropna(how='any')
+
+
 
 # + {"code_folding": [0]}
-## Inflation data quarterly 
+## Inflation data 
+
+#################
+### quarterly ###
+#################
+
[…]

### 2019-11-11 workingfolder/python/DoEstimationWithData_Dev_SV.py

@@ -27,7 +27,7 @@ import numpy as np
 from scipy.optimize import minimize
 
 import statsmodels.api as sm
-from statsmodels.tsa.api import AR
+#from statsmodels.tsa.api import AR
 #from UCSVEst import UCSVEst as ucsv
 # -
 
@@ -41,11 +41,11 @@ from GMMEstSV import UCSV_simulator, ForecastPlotDiag, ForecastPlot
 
 # + {"code_folding": []}
 ## CPI Core
-InfCPICMRT=pd.read_stata('../OtherData/InfCPICMRealTime.dta')  
+InfCPICMRT = pd.read_stata('../OtherData/InfCPICMRealTime.dta')  
 InfCPICMRT = InfCPICMRT[-InfCPICMRT.date.isnull()]
 
 ## CPI 
-InfCPIMRT=pd.read_stata('../OtherData/InfCPIMRealTime.dta')  
+InfCPIMRT = pd.read_stata('../OtherData/InfCPIMRealTime.dta')  
 InfCPIMRT = InfCPIMRT[-InfCPIMRT.date.isnull()]
 
 # + {"code_folding": []}
@@ -57,7 +57,7 @@ InfCPICMRT.index = pd.DatetimeIndex(dateM_cpic,freq='infer')
 InfCPIMRT.index = pd.DatetimeIndex(dateM_cpi,freq='infer')
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": [1]}
 ## a function that turns vintage matrix to a one-dimension vector of real time data
 def GetRealTimeData(matrix):
     periods = len(matrix)
@@ -79,7 +79,7 @@ real_time_cpi.index = InfCPIMRT.index #+ pd.DateOffset(months=1)
 
 # + {"code_folding": []}
 ## turn index into yearly inflation
-real_time_index =pd.concat([real_time_cpic,real_time_cpi], join='inner', axis=1)
+real_time_index = pd.concat([real_time_cpic,real_time_cpi], join='inner', axis=1)
 real_time_index.columns=['RTCPI','RTCPICore']
 real_time_inf = real_time_index.pct_change(periods=12)*100
 # -
@@ -89,11 +89,11 @@ real_time_inf.tail()
 # ### 3. Estimating using real-time inflation and expectation data
 #
 
-# + {"code_folding": [6]}
+# + {"code_folding": [0, 6]}
 ## exapectation data from SPF 
-PopQ=pd.read_stata('../SurveyData/InfExpQ.dta')  
[…]

### 2019-11-11 workingfolder/python/GMMEst.py

@@ -733,7 +733,7 @@ class StickyExpectation:
 # + {"code_folding": []}
 #SE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [29, 35, 41, 52, 110, 178, 207, 233, 245, 257]}
+# + {"code_folding": [2, 3, 29, 35, 41, 52, 110, 178, 201, 207, 233, 245, 257, 272, 306]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:

### 2019-11-13 workingfolder/python/DoEstimationWithData.py
1. InfExpQ correctly exported now. 2. RE estimation including more ATV moments are done

@@ -246,7 +246,7 @@ exp_data_SCE = SCE_est[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']]
 exp_data_SCE.columns = ['Forecast','FE','Disg','Var']
 data_moms_dct_SCE = dict(exp_data_SCE)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## real time and history 
 
 ################
@@ -429,7 +429,7 @@ for i,moments_to_use in enumerate(moments_choices):
 print(para_est_SCE_holder)
 print(para_est_SCE_joint_holder)
 
-# + {"code_folding": []}
+# + {"code_folding": [0, 2]}
 sce_se_est_para = pd.DataFrame(para_est_SCE_holder,
                                columns=[r'SE: $\hat\lambda_{SCE}$(M)'])
 sce_se_joint_est_para = pd.DataFrame(para_est_SCE_joint_holder,
@@ -440,7 +440,7 @@ sce_se_joint_est_para = pd.DataFrame(para_est_SCE_joint_holder,
 
 
 
-# + {"code_folding": [2]}
+# + {"code_folding": [3]}
 est_moms = pd.DataFrame(moments_choices)
 
 ## combining SCE and SPF 

### 2019-11-13 workingfolder/python/DoEstimationWithData_Dev.py

@@ -30,7 +30,7 @@ from statsmodels.tsa.api import AR
 from UCSVEst import UCSVEst as ucsv
 # -
 
-from GMMEst import RationalExpectation as re
+from GMMEst_Dev import RationalExpectation as re
 #from GMMEst_Dev import StickyExpectation as se
 #from GMMEst_Dev import NoisyInformation as ni
 from GMMEst import ParameterLearning as pl
@@ -84,7 +84,7 @@ real_time_cpi =  pd.Series(GetRealTimeData(matrix_cpi) )
 real_time_cpic.index =  InfCPICMRT.index #+ pd.DateOffset(months=1) 
 real_time_cpi.index = InfCPIMRT.index #+ pd.DateOffset(months=1)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## turn index into yearly inflation
 real_time_index =pd.concat([real_time_cpic,real_time_cpi], join='inner', axis=1)
 real_time_index.columns=['RTCPI','RTCPICore']
@@ -96,7 +96,7 @@ real_time_inf.tail()
 # ### 3. Estimating using real-time inflation and expectation data
 #
 
-# + {"code_folding": [0, 6]}
+# + {"code_folding": []}
 ## exapectation data from SPF 
 PopQ=pd.read_stata('../SurveyData/InfExpQ.dta')  
 PopQ = PopQ[-PopQ.date.isnull()]
@@ -105,26 +105,29 @@ dateQ = pd.to_datetime(PopQ['date'],format='%Y%m%d')
 
 dateQ_str = dateQ.dt.year.astype(int).astype(str) + \
              "Q" + dateQ.dt.quarter.astype(int).astype(str)
-PopQ.index = pd.DatetimeIndex(dateQ_str)
+PopQ.index = pd.DatetimeIndex(dateQ_str,freq='infer')
 
-SPFCPI = PopQ[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var']].dropna(how='any')
+####################################################
+#### specific to including more moments ###########
+####################################################
+SPFCPI = PopQ[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var',
+               'SPFCPI_ATV','SPFCPI_FEVar','SPFCPI_FEATV']].dropna(how='any')
 
 
-
-# + {"code_folding": [0]}
[…]

### 2019-11-13 workingfolder/python/GMMEst.py

@@ -79,7 +79,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [1, 5, 10, 19]}
+# + {"code_folding": [1, 5, 10, 19, 42]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -139,7 +139,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [1, 2, 16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 111, 115]}
+# + {"code_folding": [16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 111, 115]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -310,7 +310,7 @@ class RationalExpectation:
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [2, 24, 28, 40, 52, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 308, 313]}
+# + {"code_folding": [24, 28, 40, 52, 89, 100, 155, 176, 197, 220, 225, 237, 249, 260, 278, 308, 313]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,

### 2019-11-13 workingfolder/python/GMMEst_Dev.py

@@ -171,7 +171,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [0, 2, 16, 19, 30, 53, 77, 104, 108, 119, 124, 142, 148]}
+# + {"code_folding": [2, 16, 19, 57, 81, 108, 112, 123, 128, 152]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -213,16 +213,20 @@ class RationalExpectation:
         horizon = self.horizon
         
         ## forecast moments 
-        Disg =np.zeros(n)
+        Disg = np.zeros(n)
         infoset = real_time
         nowcast = infoset
         forecast = rho**horizon*nowcast
         Var = hstepvar(horizon,sigma,rho)* np.ones(n)
-        FE = forecast - self.realized ## forecast errors depend on realized shocks 
+        FE = forecast - self.realized ## forecast errors depend on realized shocks
+        ATV = rho**horizon*sigma**2/(1-rho**2)*np.ones(n) ## rho times the unconditional variance of y. 
+        FEATV = np.zeros(n)
         self.forecast_moments = {"Forecast":forecast,
                                  "FE":FE,
                                  "Disg":Disg,
-                                 "Var":Var}
+                                 "Var":Var,
+                                 "ATV": ATV,
+                                 "FEATV":FEATV}
         return self.forecast_moments
         
     def RE_EstObjfunc(self,
@@ -348,7 +352,7 @@ xx_history = AR1_simulator(rho,sigma,100)
 xx_real_time = xx_history[20:]
 
 RE_instance = RationalExpectation(real_time = xx_real_time,
-                                 history = xx_history)
+                                  history = xx_history)
 
 # + {"code_folding": []}
 ### simulate a realized series 
@@ -361,7 +365,7 @@ fe_moms = RE_instance.Forecaster()
 # + {"code_folding": []}
 ## estimate rational expectation model 
 RE_instance.GetDataMoments(fe_moms)
-RE_instance.moments=['Forecast','FE','Var']
+RE_instance.moments = ['Forecast','Disg']
 
 #RE_instance.ParaEstimate(para_guess = np.array([0.5,0.3]),
 #                         method = 'L-BFGS-B',
[…]

### 2019-11-13 workingfolder/python/DoEstimationWithData_Dev.py
Developing SE codes for ATV moments. Needs debug still.

@@ -36,7 +36,7 @@ from GMMEst_Dev import RationalExpectation as re
 from GMMEst import ParameterLearning as pl
 from GMMEst import AR1_simulator, ForecastPlotDiag, ForecastPlot
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## some parameters 
 rho = 0.95
 sigma = 0.1
@@ -111,7 +111,7 @@ PopQ.index = pd.DatetimeIndex(dateQ_str,freq='infer')
 #### specific to including more moments ###########
 ####################################################
 SPFCPI = PopQ[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var',
-               'SPFCPI_ATV','SPFCPI_FEVar','SPFCPI_FEATV']].dropna(how='any')
+               'SPFCPI_ATV','SPFCPI_FEATV']].dropna(how='any')
 
 
 # + {"code_folding": []}
@@ -178,7 +178,7 @@ PopM.index = pd.DatetimeIndex(dateM,freq='infer')
 ####################################################
 
 SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var',
-              'SCE_ATV','SCE_FEVar','SCE_FEATV']].dropna(how='any')
+              'SCE_ATV','SCE_FEATV']].dropna(how='any')
 
 
 # + {"code_folding": [0]}
@@ -281,14 +281,14 @@ process_paraM_est = {'rho':rhoM_est,
 
 # ### Rational Expectation 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## RE for SPF #
 ###############
 
 RE_model = re(real_time = real_time_Q,
               history = history_Q,
               process_para = process_paraQ_est)
-RE_model.moments = ['Forecast','FE','Disg','Var','ATV','FEVar','FEATV']
+RE_model.moments = ['Forecast','FE','Disg','Var','ATV','FEATV']
 RE_model.GetRealization(realized_CPIC)
 RE_model.GetDataMoments(data_moms_dct_SPF)
 re_dict = RE_model.Forecaster()

### 2019-11-13 workingfolder/python/GMMEst.py

@@ -139,7 +139,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 111, 115]}
+# + {"code_folding": [1, 16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 111, 115]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,

### 2019-11-13 workingfolder/python/GMMEst_Dev.py

@@ -34,7 +34,7 @@ from scipy.stats import bernoulli
 import nlopt
 #from numpy import *
 
-# + {"code_folding": [0]}
+# + {"code_folding": [1]}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -119,7 +119,7 @@ def myfunc0(x,
 #Estimator2(myfunc0,
 #          para_guess = [0.1,0.2])
 
-# + {"code_folding": [0, 1, 5, 9, 18]}
+# + {"code_folding": [0, 1, 5, 9, 18, 24, 30, 39, 55]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -137,8 +137,29 @@ def ForecastPlot(test):
         plt.plot(test[val],label=val)
         plt.legend(loc=1)
     return x
-        
-def ForecastPlotDiag(test,data,
+     
+def ForecastPlotDiag(test,
+                     data,
+                     legends=['model','data'],
+                     diff_scale = False):
+    m_ct = len(test)
+    x = plt.figure(figsize=([3,3*m_ct]))
+    if diff_scale == False:
+        for i,val in enumerate(test):
+            plt.subplot(m_ct,1,i+1)
+            plt.plot(test[val],'s-',label=legends[0]+ ': ' +val)
+            plt.plot(np.array(data[val]),'o-',label=legends[1] +':'+ val)
+            plt.legend(loc=1)
+    if diff_scale == True:
+        for i,val in enumerate(test):
+            ax1 = plt.subplot(m_ct,1,i+1)
+            ax1.plot(test[val],'rs-',label=legends[0]+ ': ' +val)
+            ax1.legend(loc=0)
+            ax2 = ax1.twinx()
+            ax2.plot(np.array(data[val]),'o-',color='steelblue',label=legends[1] +':'+ val)
+            ax2.legend(loc=3)
+    return x
+def ForecastPlotDiag2(test,data,
                      legends=['model','data']):
     m_ct = len(test)
     x = plt.figure(figsize=([3,3*m_ct]))
@@ -171,7 +192,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [2, 16, 19, 57, 81, 108, 112, 123, 128, 152]}
[…]

### 2019-11-15 workingfolder/python/DoEstimationWithData_Dev.py
SE GMM codes ready in GMMEst_dev.But need to debug. Still does not recover the true parameter.

@@ -27,11 +27,11 @@ from scipy.optimize import minimize
 
 import statsmodels.api as sm
 from statsmodels.tsa.api import AR
-from UCSVEst import UCSVEst as ucsv
+#from UCSVEst import UCSVEst as ucsv
 # -
 
 from GMMEst_Dev import RationalExpectation as re
-#from GMMEst_Dev import StickyExpectation as se
+from GMMEst_Dev import StickyExpectation as se
 #from GMMEst_Dev import NoisyInformation as ni
 from GMMEst import ParameterLearning as pl
 from GMMEst import AR1_simulator, ForecastPlotDiag, ForecastPlot
@@ -240,15 +240,15 @@ realized_CPI = np.array(SCE_est['Inf1yf_CPIAU'])
 ####################################################
 
 exp_data_SPF = SPF_est[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var',
-                        'SPFCPI_ATV','SPFCPI_FEVar','SPFCPI_FEATV']]
+                        'SPFCPI_ATV','SPFCPI_FEATV']]
 exp_data_SPF.columns = ['Forecast','FE','Disg','Var',
-                        'ATV','FEVar','FEATV']
+                        'ATV','FEATV']
 data_moms_dct_SPF = dict(exp_data_SPF)
 
 exp_data_SCE = SCE_est[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var',
-                       'SCE_ATV','SCE_FEVar','SCE_FEATV']]
+                       'SCE_ATV','SCE_FEATV']]
 exp_data_SCE.columns = ['Forecast','FE','Disg','Var',
-                        'ATV','FEVar','FEATV']
+                        'ATV','FEATV']
 data_moms_dct_SCE = dict(exp_data_SCE)
 
 # + {"code_folding": [0]}
@@ -281,7 +281,7 @@ process_paraM_est = {'rho':rhoM_est,
 
 # ### Rational Expectation 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## RE for SPF #
 ###############
 
@@ -302,10 +302,10 @@ plt.savefig('figures/spf_re_est_diag.png')
 
 # ### SE Estimation
 
-# + {"code_folding": [0, 21, 29, 39]}
-## SE loop estimation overdifferent choieces of moments for SPF
+# + {"code_folding": [14, 21, 29, 39]}
+## SE loop estimation over different choieces of moments for SPF
 
[…]

### 2019-11-15 workingfolder/python/GMMEst_Dev.py

@@ -61,7 +61,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": [0]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -76,8 +76,12 @@ def PrepMom(model_moments,
     diff: the Euclidean distance of two arrays of data and model 
     
     """
-    diff = np.linalg.norm((model_moments - data_moments)/data_moments)
+    diff = np.linalg.norm((model_moments - data_moments))
     return diff
+
+#################################
+######## specific to new moments
+################################
 
 
 # + {"code_folding": [1]}
@@ -119,7 +123,7 @@ def myfunc0(x,
 #Estimator2(myfunc0,
 #          para_guess = [0.1,0.2])
 
-# + {"code_folding": [0, 1, 5, 9, 18, 24, 30, 39, 55]}
+# + {"code_folding": [0, 1, 9, 18, 40, 56]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -153,12 +157,13 @@ def ForecastPlotDiag(test,
     if diff_scale == True:
         for i,val in enumerate(test):
             ax1 = plt.subplot(m_ct,1,i+1)
-            ax1.plot(test[val],'rs-',label=legends[0]+ ': ' +val)
+            ax1.plot(test[val],'s-',label=legends[0]+ ': ' +val)
             ax1.legend(loc=0)
             ax2 = ax1.twinx()
             ax2.plot(np.array(data[val]),'o-',color='steelblue',label=legends[1] +':'+ val)
             ax2.legend(loc=3)
     return x
+
 def ForecastPlotDiag2(test,data,
                      legends=['model','data']):
     m_ct = len(test)
@@ -192,7 +197,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [0, 2, 16, 19, 30, 62, 86, 113, 117, 128, 133, 151]}
+# + {"code_folding": [0, 2, 16, 19, 30, 66, 93, 116, 140, 167, 181, 196, 207, 212, 230, 261]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -228,10 +233,10 @@ class RationalExpectation:
         n = len(self.real_time)
         rho = self.process_para['rho']
[…]

### 2019-11-15 workingfolder/python/GMMEst_Dev.py
ongoing working on efficieny matrix for a separate objective function. Singular matrix non-invertible so far. Needs to find the proble.

@@ -61,8 +61,9 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": [2, 24]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
+
 def PrepMom(model_moments,
             data_moments):
     """
@@ -76,12 +77,34 @@ def PrepMom(model_moments,
     diff: the Euclidean distance of two arrays of data and model 
     
     """
-    diff = np.linalg.norm((model_moments - data_moments))
+    distance = model_moments - data_moments
+    diff = np.linalg.norm(distance)
     return diff
+
 
 #################################
 ######## specific to new moments
 ################################
+
+def PrepMomWM(model_moments,
+              data_moments,
+              wmx):
+    """
+    Inputs
+    -----
+    model_moments: an array of moments from a certain model, i.e. forecast error, disagreement and uncertainty. 
+    data_moments: an array of moments computed from the survey data
+    
+    Outputs
+    ------
+    diff: the Euclidean distance of two arrays of data and model 
+    
+    """
+    distance = model_moments - data_moments
+    diff = np.matmul(np.matmul(distance,wmx),
+                     distance.T)
+    return diff
+
 
 
 # + {"code_folding": [1]}
@@ -197,7 +220,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [0, 2, 16, 19, 30, 66, 93, 116, 140, 167, 181, 196, 207, 212, 230, 261]}
+# + {"code_folding": [2, 16, 19, 30, 66, 132, 157, 184, 198, 224, 229, 247, 278]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -281,10 +304,10 @@ class RationalExpectation:
         FEATV = 0
         
         self.GMMMoments = {"FE":FE,
-                    "Disg":Disg,
-                    "Var":Var,
-                    "ATV": ATV,
-                    "FEATV":FEATV}
+                           "Disg":Disg,
+                           "Var":Var,
+                           "ATV": ATV,
+                           "FEATV":FEATV}
         return self.GMMMoments
         
 ###################################
@@ -303,6 +326,7 @@ class RationalExpectation:
         -----
         the objective function to minmize
         """
[…]

### 2019-12-01 paper/InfVar.tex
seperately back up the paper draft latex until before incorporating SV and structural estimations. Then started working on InfVar.tex with new abstract.

--- 2019-10-17 paper/Draft.tex
@@
 	\begin{abstract}
-		Surveys on density forecasts of macroeconomic variables that are not available until recently provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation.
-This paper first documents the persistent dispersion in uncertainty about future inflation as well as other stylized facts across economists and households.
-Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE).
-Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.
-This sets the stage for estimating shock-specific rigidity using uncertainty as a next step of the analysis.
-
+	Density forecasts of macroeconomic variables provide one additional moment restriction, uncertainty, for testing and exploring the implications of theories about how people form expectations differently from full-information rationality benchmark.
+This paper first documents the persistent dispersion in inflation uncertainty of professionals and households, and how it conveys different information from the widely used proxies to uncertainty such as cross-sectional disagreement and forecast errors.
+Second, utilizing the panel data structure of both surveys, I provide additional reduced-form test results as well as structural estimates for each particular theory of ``irrational expectation'' by jointly accounting for its predictions for different moments.
+This is a natural extension of \citet{coibion2012can}, which examines different moments separately.
+Also, motivated by the time-varying pattern of the uncertainty observed from the surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility.
+These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness than the in baseline setting.
+It also illustrates how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.
 	\end{abstract}
@@
 	Individual forecast error $FE_{i,t+h|t}$ is the difference of individual forecast at time $t$ and ex post realized value of $y_{t+h}$.
+By definition.
+positive(negataive) forecast errors mean overpredict (underpredict) the variables.
 
@@
 	\begin{eqnarray}\label{NoPastInfFE}
-		\overline{FE}^{*}_{i,t+h|t} = \sum^{h}_{k=1} \rho^k \omega_{t+k}
+		\overline{FE}^{*}_{i,t+h|t} = - \sum^{h}_{k=1} \rho^k \omega_{t+k}
 	\end{eqnarray}
@@
 	It is easy to show that the average forecast errors are serially correlated (Equation \ref{FESEPop}).
-For double-checking, setting $\lambda=1$, SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.
+For double-checking, setting $\lambda=1$, SE collapses to FIRE, as seen in Equation \ref{NoPastInfFE}, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.
 
@@
 		\begin{aligned}
-			\overline{FE}_{t+h|t}  = (1-\lambda) \overline {FE}_{t+h|t-1} + \lambda \rho^h \omega_t 
+			\overline{FE}_{t+h|t}  = (1-\lambda) \overline {FE}_{t+h|t-1} - \lambda \sum^{h}_{k=1}\rho^k \omega_{t+k} 
 		\end{aligned}
@@
 	\bibliographystyle{apalike}
-	\bibliography{TestingExpectationTheories}
+	\bibliography{InfVar}
 

### 2019-12-01 paper/InfVar_NonSV.tex
seperately back up the paper draft latex until before incorporating SV and structural estimations. Then started working on InfVar.tex with new abstract.

--- 2019-10-17 paper/Draft.tex
@@
 This sets the stage for estimating shock-specific rigidity using uncertainty as a next step of the analysis.
-
 	\end{abstract}

### 2019-12-01 paper/archive/Outline.tex
seperately back up the paper draft latex until before incorporating SV and structural estimations. Then started working on InfVar.tex with new abstract.

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}

%opening
\title{Testing Theories of Expectation Formation using Probabilistic Answers}
\author{Tao Wang}

\begin{document}

\maketitle

\section{Motivation}

The theories on how different agents form expectations have proliferated over the past decade. On one hand, these theories built upon different micro foundations produce some similar macro patterns. For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.

On the other hand, however, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts. My goal of this exercise is to derive the testable predictions based on various theories, and utilize the probablistic questions from both professional forecasters survey and household survey to test them.

The potential contribution lies in the extra insights I may get from using probablistic questions.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \cite{manski2004measuring}.} One obvious advantage of density expectations compared to point one is availability of higher moments, i.e. variance of the forecast indicates the dispersion of the forecasts. Along time dimension, the dynamics of conditional relative likelihood is a useful indicator of information gain or forecasting efficiency. Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions. Although the detailed implementation of these tests involves technical difficulties, the ideas are quite clear.  Lastly, with second moments in individual level expectations, we are allowed to potentialy explore the heterogeneity across agents within one theory. For instance, sticky information typically assume a posson update rate for all agents in the economy. This is partly due to the fact that available data only allows us to recover single parameter of regidity instead of inter-group heterogeneity.

\section{A General Framework}

Agent i's $h$-period ahead density forecast of variable $y_i$ at time $t$ is the conditional density of $y_{i,t+h}$ given the information set $I_{i,t}$ available at time $t$.

$$\widehat f_{i,t}(y^i_{t+h}|I_{i,t})$$

Notice here the $y_{t+h}$ has supscript $i$. This is to remind that in general the variables $y_{t+h}$ can be either aggregate variables or idiosyncratic ones, in the former case, we could drop subscript $i$.

$I_{i,t}$ is the information set available at time t for individual $i$. The information set can be also agent specific, therefore, it has subscript $i$.  The specific content contained in $I_t$ varies from different models. Seemingly a simple and justified assumption is that $x_t \in  I_t$. This, however, may not be ture for all models. For instance, sticky expectation and rational inattention literature all predict that agents are not able to update new information instataneously. Thus the information set may not winclude the recent realization of the variable itself.

Assumption also needs to be made about the underlying model that generates the conditional density of the variables by agent $i$.

Given the forecast density, the expectation of forecast at time $t$ is.

$$E_{i,t}(y_{t+h}|I_{i,t}) =\int \widehat f_{i,t}(y_{t+h}|I_{i,t})y_{t+h} d y_{t+h}\equiv \bar y_{i,t,t+h}$$

The forecasting variance is

$$Var_{i,t}(y_{t+h}|I_{i,t})=\int \widehat f_{i,t}(y_{t+h}|I_{i,t}) (y_{t+h} - \bar y_{i,t,t+h})^2d y_{t+h}$$

The true process of $y_{t}$ depends on the variables. Here, we consider a simple case where true process of $y_t$ is AR(1).

$$y_{t+1} = \rho y_t + \omega_t$$

$$\omega_t \sim N(0,\sigma^2_{\omega})$$

\subsection{Full-information rational expectation}
\subsubsection{Individual moments}

Full information rational expectation implies $y_t \in I_t$

\textbf{Expectation}
$$E_{i,t}(y_{t+h}|y_t) = E_{i,t}(y_{t+h}|y_t) = \rho^h y_t $$

\textbf{Variance} 
$$Var_{i,t}(y_{t+h}|y_t) = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$

Ex post forecast error of individual i $$FE_{i,t} = y_{t+h} - E_{i,t}(y_{t+h}|y_t) = \sum^h_{s=1} \rho^s \omega_{t+h-s}$$ has is mean zero and orthogonal to information at time $t$.

\subsubsection{Population moments}

A special case below.

\section{Sticky Expectation}

Agent does not update information instantaneously, instead at a Possion rate $\lambda$. Specificaly, at any point of time $t$, the agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

\subsection{Individual moments}

For an individual whose most recent update occurs at $\tau$ period before, $I_{i,t|t-\tau} = I_{i,t-\tau} = y_{t-\tau}$. Thus

$$E_{i,t|t-\tau}(y_{t+h}|I_{i,t}) = E_{i,t}(i,y_{t+h}|y_{t-\tau}) = \rho^{h+\tau} y_{t-\tau}$$

$$Var_{i,t|t-\tau}(y_{t+h}|I_{i,t}) = Var_{i,t}(y_{t+h}|y_{t-\tau}) = \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}$$

$Var_{i,t|t-\tau}(y_{t+h}|_{i,t})$ increases as $\tau$ increases. The model collapses to full-information rational expectation if $\tau=0$ for all individuals.

Now, we turn to the case when agent updates infrequently.

\begin{itemize}
\item When the update happens, the variance responds substantially.

$$Var_{i,t}(y_{t+h}|y_t) - Var_{i,t|t-\tau}(y_{t+h}|y_{t-\tau}) = \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega} - \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} = \sum^{\tau}_{s=0} \rho^{2s}\sigma^2_{\omega}$$

\item When the update does not happen, the variance responds little.

$$Var_{i,t|t-\tau-1}(y_{t+h}|y_{t-\tau-1}) - Var_{i,t|\tau}(y_{t+h}|y_{t-\tau}) = \sigma^2_{\omega}$$

At individual level, it is hard to recover the information rigidity parameter $\lambda$ directly. One testable prediction of information rigidity is that the change in forecast variance varies substantially depending on if updated or not. The longer period for which the agent stays unupdated(greater $\tau$), the bigger the change is in the forecasting variance.

However, the difference in average responses in variance to new information may speak to potential heterogeneity in information rigidity. According to the theory above, higher information rigidity implies high volatility of variance responses.  
\end{itemize}

\subsection{Population moments}

\subsubsection{Average forecast}

The mean forecast across population is a weighted average of past rational expectations

\begin{eqnarray}
\begin{aligned}
\bar E_t(y_{t+h}) & = \lambda \underbrace{E_t(y_{t+h})}_{\textrm{rational expectation at t}} + (1-\lambda) \underbrace{\bar E_{t-1}{y_{t+h}}}_{\textrm{average expectation at} t-1} \\
& = \lambda E_t(y_{t+h}) + (1-\lambda) (\lambda E_{t-1}(y_{t+h})+ (1-\lambda) \bar E_{t-2}(y_{t+h}))... \\
& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s E_{t-s}(y_{t+h}) \\
& = \lambda \sum^{\infty}_{s=0} (1-\lambda)^s \rho^{s+h}y_{t-s}
\end{aligned}
\end{eqnarray}

The change in average forecast is

\begin{eqnarray}
\begin{aligned}
\Delta \bar E_t(y_{t+h})&  = (1-\lambda) \Delta \bar E_{t-1}(y_{t+h}) + \lambda (E_t(y_{t+h}) - E_{t-1}(y_{t+h})) \\ 
& = (1-\lambda) \Delta \bar E_{t-1}(y_{t+h}) + \lambda \rho^h \omega_t 
\end{aligned}
\end{eqnarray}

This implies the change in average forecast is serially correlated, depending on the information rigidity, i.e. lower $\lambda$ implies higher serial correlation. Also lower $\lambda$ implies the expectation underreact to the shocks at $t$.

\subsubsection{Cross-sectional disagreements}

According to information rigity model, if everyone is instantaneously udpated, there should not be disagreements. In general, the dispersion in forecasting is non-zero because of different lags in updating. One can also derive variance of forecasts across agents at time $t$

\begin{eqnarray}
\begin{aligned}
Var_t(E_{i,t}(y_{t+h}) ) & = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^{\tau} (E_{t|t-\tau}(y_{t+h}) - \bar E_t(y_{t+h}))^2  
\end{aligned}
\end{eqnarray}

From time $t$ to $t+1$, the change in dispersion comes from two sources. One is newly realized shock at time $t+1$. The other component is from people who did not update at time $t$ and update at time $t+1$.

\begin{eqnarray}
\begin{aligned}
\Delta Var_{t+1}(E_{i,t+1}(y_{t+h})) = \textrm{change due to new updaters} + \textrm{shock at time } t+1 
\end{aligned}
\end{eqnarray}

Notice the change is positive, meaning the dispersion rises in response to a shock. Importantly, the increase is the same regardless of the realization of the shock.

More generally, we can derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.

\begin{eqnarray}
\rho^{2(h+j)} (1-\lambda^{j+1})\lambda^{j+1} \omega^2_t
\end{eqnarray}

A shock increases the disagreements across agents and then it gradually returns to its steady state level.

\subsubsection{Average variance}

Since we have individual level variance, we can also derive average variance of the population. Taking the average of variance across individual agents at time $t$. Here I use the $\bar{}$ to represent population mean of variance.

\begin{eqnarray}
\begin{aligned}
\bar Var_{t}(y_{t+h}) & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who does not update until }t-\tau} \underbrace{Var_{t|t-\tau}(y_{t+h})}_{\text{ Variance of most recent update at }t-\tau} \\
& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
\end{aligned}
\end{eqnarray}

Correspondingly, the change in average uncertainty will be

\begin{eqnarray}
\begin{aligned}
\Delta \bar Var_{t}(y_{t+h}) & = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} - \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega} = 0  
\end{aligned}
\end{eqnarray}

An information rigidity model based on fixed Poisson update rate predicts that the average variance does not change over time. This can be tested.

\subsubsection{Cross-sectional disagreements about variance}

\subsubsection{Summary of predictions of information rigidity}

\begin{itemize}
\item Individual expectation may or may not change depend upon if updating. 
\item Individual variances changes non-monotonically depending on if updating. Always increase with arrival of new information. 
\item Population mean of forecast responds with lags. Change is serially correlated. 
\item Population dispersion of forecasts rise in response to new shocks and return to steady state level gradually. 
\item Population average variance does not change over time. 
\end{itemize}

\section{Noisy information (or signal extraction)}

A class of so-called noisy information model describes the expectation formation as a process extracting or filtering true fundamental state variable $y_t$ from a sequence of realized signals. The starting assumption is that agent cannot observe the true variable perfectly. Unlike information rigidity model, it is assumed that agents keep track of the realizations of the signals instantaneously all the time.

We assume agent $i$ observe two signals $s^{pb}$ and $s^{pr}_i$, with $s^{pb}$ being public signal common to all agents, and $s^{pr}_i$ private signals being individual specific. The generating process of two signals are

\begin{eqnarray}
\begin{aligned}
s^{pb}_t = y_t + \epsilon_t, \quad \epsilon_t \sim N(0,\sigma^2_\epsilon)\\ 
s^{pr}_{i,t} = y_t + \xi_{i,t} \quad \xi_{i,t} \sim N(0,\sigma^2_\epsilon)
\end{aligned}
\end{eqnarray}

We can stack the two signals into one vector $s_{i,t} = [s^{pb}_t,s^{pr}_{i,t}]'$ and $v_{i,t}= [\epsilon_t,\xi_{i,t}]'$. So in a compact form, it can be written as

\begin{eqnarray}
\begin{aligned}
s_{i,t} = H y_{t} + v_{i,t} \\
\text{where } & H=[1,1]' \quad \\
\end{aligned}
\end{eqnarray}

In our general framework, the noisy information implies that the information set $I_{i,t}$ available to individual $i$ at time $t$ only includes past and recent realizations of the signals. The individual density forecast of $y_{t+h}$ is

$$\widehat f_{i,t}(y_{t+h}|I_{i,t}) = \widehat  f_{i,t}(y_{t+h}|s_{i,t},s_{i,t-1}...) \equiv \widehat  f_{i,t|t}(y_{t+h})$$

We use $t|k$ to denote the moments at time t based on information(signals) till time $k$.

Then we are ready to apply Kalman Filter in this context. The posterior distribution of $y_{t}$ after seeing all signals till $t$ is

\begin{eqnarray}
\widehat  f_{i,t|t}(y_{t+h})  \sim  N(E_{i,t|t}(y_{t+h}), Var_{i,t|t}(y_{t+h}))
\end{eqnarray}

where the expectation and variances are functions of noisiness of signals and fundamentals. The expectation also depends on the realized values. But this is not the case for variance.

\subsection{Individual moments }

\subsubsection{Expectation}

Now any agent trying to forecast future variables will have to form her expectation of the contemporaneous state variable, $E_{i,t|t}(y_t)$. Then the best h-period ahead forecast is simply iterated h periods forward based on the AR(1) process.

Thus, we first work out $E_{i,t|t}(y_t)$.

\begin{eqnarray}
\begin{aligned}
E_{i,t|t}(y_{t}) 
& =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
& = (1-PH) E_{i,t|t-1}(y_{t}) + Ps_{i,t} \\
& = (1-PH) E_{i,t|t-1}(y_{t}) + PH y_{i,t} + P v_{i,t} \\
\text{where the Kalman gain }  & P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} \\
\text {where } & \Sigma^y_{i,t|t-1} \text{ is the variance of } y_t \text{ based on prior belief}\\
\text {and } & \Sigma^v =  \left[ \begin{matrix} 
  \sigma^2_{\epsilon} &  0 \\ 0 & \sigma^2_\xi \end{matrix}\right] 
\end{aligned}
\end{eqnarray}

The h-period ahead forecast is

\begin{eqnarray}
\begin{aligned}
E_{i,t|t}(y_{t+h}) & = \rho^{h}E_{i,t|t}(y_{t+h}) 
\end{aligned}
\end{eqnarray}

Individual forecast partially responds to new signals, i.e. $P<1$. $P=1$ is a special case when both signals are perfect thus $\Sigma^v = 0$, then the formula collapses to full rational expectation.

Now, the rigidity parameter is governed by $1-PH$ with multiple signals. It is a function of variance of $y$ from the prior of previous period and noisiness of the signals. Therefore, it is time variant as the variance is updated by the agent each period.

There are a few important distinctions between noisy information and sticky expectation.

$\bullet$  First, the persistence of expectation exists at individual level. There is serially correlation between $E_{i|t|t}(y_t)$ and $E_{i,t|t-1}(y_{t})$, or more generally, between $E_{i,t|t}(y_{t+h})$ and $E_{i,t|t-1}(y_{t+h})$. This pattern can be only observed from population moments according to sticky expectation models.

To see this, the change in individual forecast from $t-1$ to $t$ is

\begin{eqnarray}
\begin{aligned}
\Delta E_{i,t|t}(y_{t+h}) & = \underbrace{\rho^h (1-PH)\Delta E_{i,t-1|t-1}(y_{t})}_{\text{Lagged response}} + \underbrace{\rho^hPH \Delta y_{i,t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
\end{aligned}
\end{eqnarray}

The serial correlation is $\rho^h(1-PH)$, it does not only depend on $PH$, but also the forecast horizon $h$. Therefore, one testable assumption is to see auto regression of change in forecast to see if the coefficient depends on horizon.

$\bullet$  Second, the expectation adjusts in each period as long as there is new information. In sticky expectation, however, the expectation adjusts only when the agent updates.

\subsubsection{Variance}

The posterior variance at time $t$ is a linear function of prior variance and variance of signals.

\begin{eqnarray}
\begin{aligned}
\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} 
\end{aligned}
\end{eqnarray}

There are a few important properties in the variance.

- First, it does not depend on the realizations of the signal.

- Second, it decreases unambigously from $t-1$ to $t$. To see this

\begin{eqnarray}
\Sigma^y_{i,t|t} - \Sigma^y_{i,t|t-1} = - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} <0
\end{eqnarray}

These two properties carry through to the h-period ahead forecast as well. As the forecast variance is the following

\begin{eqnarray}
Var_{i,t|t} (y_{t+h}) = \rho^{2h} \underbrace{Var_{i,t}(y_{t})}_{\Sigma_{i,t|t}} + \sum^{h}_{s=0}\rho^{2s} \sigma^2_{\omega}
\end{eqnarray}

\begin{eqnarray}
\Delta Var_{i,t|t} (y_{t+h}) = \rho^{2h}\Delta \Sigma_{i,t|t} - \rho^{2h} \sigma^2_{\omega}
\end{eqnarray}

From $t$ to $t+1$, when $h\geq 1$, the decline in variance come from two sources. The first source is the pure gain from the new signals, i.e. $\Delta \Sigma^y_{i,t|t}$. It is scalled by the factor $\rho^{2h}$. The second source is present in full information rational expectation model: as time goes from $t-1$ to $t$, there is a reduction of uncertainty about $\omega_t$.

\subsection{Population moments}

\subsubsection{Average forecast}

\begin{eqnarray}
\begin{aligned}
\bar E_{t|t} (y_{t+h}) & = \rho^h [(1-PH) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
& = (1-PH) \bar E_{t-1}(y_{t+h}) + P [\epsilon_t, 0]' \\
& = (1-PH) \bar E_{t-1}(y_{t+h}) + P \epsilon_t
\end{aligned}
\end{eqnarray}

\subsubsection{Change in average forecast}

\begin{eqnarray}
\begin{aligned}
\Delta \bar E_t|t (y_{t+h}) & = \rho^h (1-PH) \Delta \bar E_{t-1}(y_{t+h}) + \rho^h P \Delta \epsilon_t
\end{aligned}
\end{eqnarray}

Same to the individual forecast, the change in average forecasts has serial correlation with the same auto regression parameter $\rho^h(1-PH)$.

\subsubsection{Cross-sectional disagreements}

In this model, the only disagreements across agents come from the difference in realized private signals. Therefore, in short-cut, the disagreements are

\begin{eqnarray}
\begin{aligned}
Var_t(y_{t+h}) & = E((E_{i,t|t}(y_{t+h}) - \bar E_t(y_{t+h}))^2) \\
& = \rho^{2h} P^2_\xi \sigma^2_\xi  
\end{aligned}
\end{eqnarray}

Several properties.

$\bullet$ First, the disagreements increase with the forecast horizon. 
$\bullet$  Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. 
$\bullet$  Third, similar to sticky expectation model, the disagreements also increase with the rigidity parameter $P$ in this model.

\subsubsection{Change in disagreements}

\begin{eqnarray}
\begin{aligned}
\Delta Var_t(y_{t+h}) & = \rho^{2h}(1-\rho^2) P^2_\xi \sigma^2_\xi >0
\end{aligned}
\end{eqnarray}

The disagreements increase as time goes from $t-1$ to $t$. Also, as the time approaches $t+h$, the disagreements increase. This seems counterintuitive. But the reason is that here the disagreenments always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.

\subsubsection{Average variance}

Since the variance does not depend on signals and the precision is the same aross the agents, average variance is equal to the variance of each individual.

\begin{eqnarray}
\begin{aligned}
\bar Var_t (y_{t+h}) = \bar \Sigma^y_t
\end{aligned}
\end{eqnarray}

Also, same as the individual variance, the variance unambiguiously drop as time goes by.

\begin{eqnarray}
\Delta Var_t(y_{t+h}) < 0 
\end{eqnarray}

\subsection{Summary of predictions from noisy information}

$\bullet$  Invididual expectation adjusts in each period, but only partially adjusts to new information. \\
$\bullet$ Unlike sticky expectation, slugishness in adjustment or serial correlation of adjustment exists in individual level. The correlation parameter decreases with forecast horizon, which is not the case in sticky expectation.\\
$\bullet$  Individual variance unambiguously drops each period as one approaches the period of realization. In sticky expectation, it increases regardless of updating or not. \\ 
$\bullet$  Population average forecast partially adjusts to news and has serial correlation as the individual level. \\
$\bullet$  Population disagreements rise in each period as time approaches the period of realization. Disagreetments will never be zero. \\
$\bullet$  Average variance declines unambiguously each period.

\section{Other Theories}

\begin{enumerate}
	\item Backward-looking Adaptive Expectation.

	\item Full-information Forward-looking Rational Expectation.  
	\begin{itemize}
		\item Model-consistency. This is not testable. 
		\item Identical across agents. Most empirical evidence implies wide range of heterogeneity.  \cite{mankiw2003disagreement, coibion2012can} 
	\end{itemize}

\item Learning with bounded rationality.  \cite{evans2012learning} Agents with bounded rationality behaves as if a statistician herself in the model. She makes an assumption about the model. And then she recovers the parameter of the model using observed realizations of the data. It could be a simly random walk process, AR(1), or with other known explanatory variables. It could be Markov finite state. It could hidden markov with continous state of the world, in which, Kalman filter needes to be invoked.

\item Rational inattention. 
\begin{itemize}
	\item Chris Sim's model.\cite{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy. Agents optimally trade off the fixed cost of being attentative versus the gain from uncertainty gain.   
	\item Ricardo Reis's model. \cite{reis2006inattentive}
	\item Xavier Gabaix's sparse matrix model. \cite{gabaix2014sparsity}
\end{itemize}

\item Diagnostic Expectation. \cite{bordalo2018diagnostic}. A different process from Bayes updating. Agents overweight new information that is most salient. For intance, agents believe that a stock that overperforms than average will be more likely to perform well in future.

\item Epidemiologic view. \cite{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.

\item Multiple-prior models with model uncertainty, or concerned about model mis-specification. \cite{hansen2001robust} A statistician may produce a densitity forecast to her best based on certain models but in the same time has preservation as to if the model is the correct one.

\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \cite{angeletos2009incomplete}

\item Behaviorial explanations. 
\begin{itemize}
	\item Macroeconomic experiences. \cite{malmendier2015learning}
	\item Demographical or social-economic patterns.

\end{itemize}

\end{enumerate}

\section{Data}

\begin{itemize}

	\item \textbf{Michigan Household Survey}
	\begin{itemize}
		\item Examples of probablistic questions:
		``Probability of Real Income Gains During the Next 5 Years;
		``Probability of Losing a Job in the Next 5 Years'';
		``Probability That Personal Income Will Increase During the Next Year''.
		\item Information set: ``News Heard of Recent Changes in Business Conditions''; 
		``News Heard About Price Changes'', etc 
		\item Both individual and aggregate variables. 
	\end{itemize}
		\item \textbf{New York Fed Survey of Consumer Expectation}
	\begin{itemize}
			\item Include not only perceived probabilities of binary event as in Michigan Survey does, but also elicit densitity forecasts. 
	\end{itemize}
	\item \textbf{Professional Forecasters}
	\item \textbf{ECB Professional Forecasters}
\end{itemize}

A summary of the data information is as below.

\begin{table}[]
			\caption{Information of Data}
	\begin{tabular}{lll}

		\hline 
		& SCE & SPF        \\
		\hline 
		Time period                                    & 2013-present                            & 2007-present             \\
		Frequency                                      & Monthly                                 & Quarterly                \\
		Sample Size                                    & 1,300                                   & 30-50                    \\
		Aggregate Var in Density                       & 1-yr  and 3-yr ahead inflation          & 1-yr CPI and PCE         \\
		Individual Var in Density                      & 1-yr earning growth                     & No                       \\
		Pannel Structure                               & stay up to 12 months                    & average stay for 5 years \\
		Demographic Info                        & Education, Income, Age, Location        & Industry    \\
		\hline 
	\end{tabular}
\end{table}

\bibliographystyle{apalike}
\bibliography{TestingExpectationTheories}

\end{document}

### 2019-12-01 workingfolder/python/DoEstimationWithData_Dev_SV.py

@@ -89,7 +89,7 @@ real_time_inf.tail()
 # ### 3. Estimating using real-time inflation and expectation data
 #
 
-# + {"code_folding": [0, 6]}
+# + {"code_folding": [6]}
 ## exapectation data from SPF 
 
 PopQ = pd.read_stata('../SurveyData/InfExpQ.dta')  
@@ -175,13 +175,13 @@ CPIM_UCSV_Est.columns = ['sd_eta_est','sd_eps_est','tau']  ## Loading ucsv model
  ######################################################################################
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## Combine expectation data and real-time data 
 
 SPF_est = pd.concat([SPFCPI,real_time_inf,InfQ['Inf1y_CPICore'],InfQ['Inf1yf_CPICore']], join='inner', axis=1)
 SCE_est = pd.concat([SCECPI,real_time_inf,InfM['Inf1yf_CPIAU']], join='inner', axis=1)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## hisotries data, the series ends at the same dates with real-time data but startes earlier 
 
 st_t_history = '2000-01-01'
@@ -241,41 +241,50 @@ realized_CPI = np.array(SCE_est['Inf1yf_CPIAU'])
 #SPF_est['Inf1yf_CPICore'].plot()
 #plt.title('Realized 1-year-ahead Core CPI Inflation')
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## plot estimation of UCSV model quarterly 
 date_historyQ = np.array(list(CPICQ.index[n_burn_rt_historyQ:]) )
 
 ## stochastic vols
-plt.plot(date_historyQ,
-         history_vol_etaQ,'r-.',
+plt.plot(history_vol_etaQ,'r-.',
          label=r'$\widehat\sigma^2_{\eta}$')
-plt.plot(date_historyQ,
-         history_vol_epsQ,'--',
+plt.plot(history_vol_epsQ,'--',
          label=r'$\widehat\sigma^2_{\epsilon}$')
 plt.legend(loc=0)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## inflation and the permanent component quarterly 
 
-plt.plot(date_historyQ,np.array(historyQ['RTCPICore']),'r-.',label='y')
[…]

### 2019-12-01 workingfolder/python/GMMEst_Dev.py

@@ -31,7 +31,7 @@ import statsmodels.api as sm
 from statsmodels.tsa.api import AR
 import copy as cp 
 from scipy.stats import bernoulli
-import nlopt
+#import nlopt
 #from numpy import *
 
 # + {"code_folding": [1]}
@@ -61,7 +61,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [2, 24]}
+# + {"code_folding": [0, 2, 24]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 
 def PrepMom(model_moments,
@@ -220,7 +220,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [2, 16, 19, 30, 66, 132, 157, 184, 198, 224, 229, 247, 278]}
+# + {"code_folding": [1, 2, 16, 19, 30, 66, 93, 135, 160, 187, 201, 216, 229, 232, 250, 281]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -530,7 +530,7 @@ class RationalExpectation:
         return x
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### create a RE instance 
 xx_history = AR1_simulator(rho,sigma,100)
 xx_real_time = xx_history[20:]
@@ -538,7 +538,7 @@ xx_real_time = xx_history[20:]
 RE_instance = RationalExpectation(real_time = xx_real_time,
                                   history = xx_history)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### simulate a realized series 
 RE_instance.SimulateRealization()
 
@@ -546,7 +546,7 @@ RE_instance.SimulateRealization()
 fe_moms = RE_instance.Forecaster()
 #re_plot = RE_instance.ForecastPlot()
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## estimate rational expectation model 
 RE_instance.GetDataMoments(fe_moms)
 #RE_instance.moments = ['Forecast','Disg']
@@ -558,15 +558,15 @@ RE_instance.GetDataMoments(fe_moms)
 #RE_instance.para_est
 #re_plot_diag = RE_instance.ForecastPlotDiag(all_moms=True)
 
-# +
+# + {"code_folding": [0]}
 #################################
 ######## specific to new moments
 ################################
[…]

### 2019-12-01 paper/InfVar.tex
small typo in abstract.

@@
 This is a natural extension of \citet{coibion2012can}, which examines different moments separately.
-Also, motivated by the time-varying pattern of the uncertainty observed from the surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility.
-These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness than the in baseline setting.
+Also, motivated by the time-varying pattern of the uncertainty observed from surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility.
+These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness.
 It also illustrates how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.

### 2019-12-17 slides/ExSlidesScript.tex
slides for brown bag seminar. Will work on following things. 1. true GMM, unconditional moments. 2. randseed lead to SMM.

\documentclass[]{article}

%opening
\title{Script for brown bag seminar presentation}
\author{Tao Wang}

\begin{document}

\maketitle

\begin{itemize}

	\item 
Thanks for coming, everyone.

\item outline page.

Let me start by saying that what I will present today is a subset of what I am doing for the sake of time. I am presenting the challenging part because it is still ongoing and I want to get feedback from you.

\item motivation page

A little big picture.

There have been a variety of theories on how agents form expectation deviating from full-information rational expectation benchmark.

One particular line of literature that gradually taken off since Coibion and Gorednichenco's JPE paper in 2012, is to take these theories to data, deriving implications from the theory and test them using  survey data of different type of agents, households, professionals and central bank economists. By comparable I mean these theories are put together and compared.

One way to check if a particular theory on expectation formation works well is to check if its predictions about different moments from the survey data are relatively consistent with the data. The moments, here, refer to forecast errors, disagreement, uncertainty, etc.

In light of this, the paper is motivated by two ideas.

First, if we have more moments, we have more restrictions on testing these theories. I will particularly brining in an additional moment, uncertainty to this line of work.

Second, instead of using survey purely for studying expectation self, I would try to convince you that survey itself can also helps us understand the variable process itself.

\item paper preview page

So in particular, this paper does the following three things

First is some basic facts about the time-series and cross-sectional pattern of the inflation uncertainty estimated from the density forecasts by households and professionals. A hightlight of this exercise is that although many empirical literature has used alternative indicators all they call uncertainty, say, disagreement, they are not the same things, both as defined statistically or empiricall from the data.

Second, once I have uncertainty, I can do some rational expectation null tests for uncertainty in a similar spirit to what the literature has done for other moments, say forecast errors. This part the results are in my draft already. I will not show it here today.

Third, is my focus today. I extend Coibon and Goridennicheco's JPE paper in two ways. For those of you who do not know what they do exactly, they derive testable predictions according to a particular theory, on forecast error, on disagrrement and then explore the data using impulse resposne.

My extension are twofold. First, instead of examining these predictions seperately. I do it jointly across moments, including uncertainty. 
Second, in their paper, they assume a stylized inflation process of AR(1), my work, however, once guided by the uncertainty from the data, tells me that there is time varying uncertainty. I need to have a stochastic volatility inflation process.

\item  move to literature page

Let me not spend much time on the literature. except for pointing you the 2nd block of literature. When you start talking about probablistic surveys. One may shrug and say, well, people are bad at probabilities and answering surveys. This is not my response, but other researchers' response. They advocate the rationale of eliciting expectation surveys. Also, they show people have willingness and ability to exprese their expectations in a density manner.

\item generic frameowork

Straightforward.

- Different theories of expectation we are talking about here differ in informatio set (a sufficient statistic you need to form expectations for future variables subject to what the theory tells you have access to.)

- Once you get your information set. how you forecast depends on the inflation process, AR(1), or unobservable component. etc.

\item moments

let me make sure we are on the same pape when we talk about these moments.

upper bar to denote population moments. Also it has no subscript $i$.

The purpose of this paper, average uncertainty.

 \item Data  
 Two kinds agents. For households, SCE from New York Fed.

 SPF for professionals. has a longer sample but lower frequency. Density forecasts of core inflation goes back to 2007.

 To be clear, the orginal answer in the survey is not eactly a density distribution itself. Instead, it is a histogram with predefined bin size.  Then I need to turn that to a density so that I can compute variance of each one's distribution, i.e. uncertainty.  I follow this paper. So does the New York Fed.

 Also, I exclude throughout the whole sample some extrem values.

\item basic pattern 1 page

time series pattern of the uncertainty. 
Always from left to right, the first wo are SPF for CPI and PCE core. The thrid is for households.

On professionals
- an upward trend in uncertainty.

On housheolds
- more volatile.

Let me remind that the sheer magnitude is not comparable across two types of agents.

\item basic pattern 2 page

Size of the forecast error. Not the forecsast error.

higher ex ante uncertainty do not necessarily mean bigger size of the ex post  forecast errors.

\item basic pattern 3 page

average uncertainty is not the same as disagreement for professionals.

trending down disagreement in the period between 2007 till now. but upward uncertainty.

but for households, correlated and covement.

\item summary page

two main messages for me.

first, uncertainty changes over time.

second, the dynamics are not the same as other moments. has useful things to say about expectation formation and inflation.

\item AR(1) page

Now I want to choose a combination of inflation process and expectation formation and see if it better explains the dynamcis we have seen above.

I have derive for each moment according to each combination. But I just show uncertainty here, to give you a flavor.

Benchmark, AR(1) model.

REVar is simly the summation of the variance of unrealized shocks.  Constant size each period by definition.

SEVar is a weighted average of the REvar standing at different point of time depending on the last update at $\tau$.

NIvar has two parts. Since now you cannot real-time inflation well. Noisy. So you have uncertainty about it at time $t$. conditional on that, you are like a rational agent standing at time t. Your uncertainty about future shocks are othognol to the nowcasting uncertainty.

\item SV model. following stock and watson.

Now two componenets, unobservable to agents $\theta_t$ and $\eta_t$.

The permanent component $\theta_t$ is a marginale with the shock $\epsilon$.

Transitory $\eta_t$ and permanent shock $\epsilon_t$ are of the size $\sigma_\eta$ and $\sigma_\epsilon$, both of which are time varying. the stocastic shock happens to the volatility itself.

Both the variance of permanent and transitory shocks are time varying now because there is a time-specific shock to the volatility of each compoenent.

\item Uncertainty SV page

Full-information reationality states that you know all the stocastic variables that realized up to t.

So your uncertainty now depends on the most recent volatility level of two components

SE again is a weighted avearge.

NI. now has two components as well. One part has your uncertainty about filtering true component theta. the second part is the same as a rational agent standing at time t.

The bottom line from this, time varying volatility. This has a hope to match with the uncertainty better.

 \item estimation page.

 \end{itemize}

\end{document}

### 2019-12-17 slides/ExpSlides.tex
slides for brown bag seminar. Will work on following things. 1. true GMM, unconditional moments. 2. randseed lead to SMM.

--- 2019-06-17 slides/ExpSlides.tex
@@
 \usepackage{adjustbox}  % Allows for fitting tables into slide
-
+\usepackage{hyperref}
+\usepackage{threeparttable}
+\usepackage{caption}
+%\usepackage{subcaption}
+\usepackage{natbib}
+\usepackage{adjustbox}
+\usepackage{subcaption}
 %\usetheme{AnnArbor}
@@
 %\usetheme{Berlin}
-%\usetheme{Boadilla}
+\usetheme{Boadilla}
 %\usetheme{boxes}
-\usetheme{CambridgeUS}
+%\usetheme{CambridgeUS}
 %\usetheme{Copenhagen}
@@
 
-\date{April, 2019}
+\date{\today}
 % - Either use conference name or its abbreviation.
@@
 
-%\begin{frame}{Why studying expectation}
-%\begin{itemize}
-%	\item Both theories and empirical evidence on deviation from full-information rational expectation(FIRE)
-%	\item ``Sluggish'' macro: i.e. ``excessive smoothing'' in consumption, sticky price adjustment by firms and UIP puzzle, forward guidance puzzle, etc
-%	\item Heterogeneity in expectation matters for asset pricing
-%	\item From \textcolor{blue}{revealed preference(belief)} to \textcolor{blue}{elicited beliefs}  	
-%\end{itemize}
-%\end{frame}
-
-\begin{frame}{What I am doing}
+\begin{frame}{Motivation}
 	\begin{itemize}
-	\item Use \textcolor{blue}{density information} to 
-	\begin{itemize}
-		\item test expectation rigidity models 
-		\item ... and identify differences in various theories 
-	\end{itemize}
-	\item Both \textcolor{blue}{individual} and population moments 
-	\item \textcolor{blue}{Households} and professional forecasters 
-	\begin{itemize}
-		\item drivers of difference in rigidity across two types of agents
-	\end{itemize}
-	%\item Focus on aggregate variable inflation first, and then try \textcolor{blue}{individual variables} 
+		\item there are various theories on  ``irrational expectation''
+		\item different theories can be tested using survey data  in a comparable manner  (\citet{coibion2012can})
+		\item a good theory needs to be (relatively) consistent in predictions across different moments
+		\item higher moments, i.e. uncertainty, brings about one more restriction
+		\item survey also contains information about data generating process itself
 	\end{itemize}
@@
 
-\begin{frame}{Why density is important}
+\begin{frame}{What this paper does}
+	\begin{enumerate}
+		\item time series and cross-sectional pattern of \textcolor{blue}{uncertainty} from \textbf{density} forecasts of the inflation 
+		\item additional reduced-form tests of the full-information rationality null using the uncertainty 
+		\item extend \citet{coibion2012can} in two ways 
 		\begin{itemize}
-\item \textbf{Identification:} different theories have testable predictions on the second moments   
+		\item cross-moment estimation for each one of the particular theories on expectation 
+		\item allowing for stochastic volatility of inflation process 
+		\end{itemize}
+	\end{enumerate}
+\end{frame}
+
+\begin{frame}{Literature}
 \begin{itemize}
-		\item Scenario 1. Two people think the chance of raining is 50\%. 
-		\item Scenario 2. One person thinks 100\% and the other 0\%. 
+	\item empirical tests on expectation formation
+	\begin{itemize}
+		\item \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}, \citet{malmendier2015learning}, \citet{das2017socioeconomic}, \citet{coibion2012can}, \citet{fuhrer2018intrinsic}
 	\end{itemize}
-\item \textbf{Modeling Implications:}  both mean and variance affect economic decisions
+    \item density and probabilistic questions in expectation surveys
     \begin{itemize}
-	\item precautionary saving with income risks
-	\item portfolio choice with risky asset
+    	\item  \citet{manski2004measuring}, \citet{delavande2011measuring}, \citet{manski2018survey} 
+    	\item  \citet{bertrand2001people},  \citet{van2008rethinking},  \citet{delavande2014probabilistic}
+    \end{itemize}
+    \item different measures of uncertainty
+    \begin{itemize}
+    	\item \citet{bachmann2013uncertainty},  \citet{jurado2015measuring}, \citet{binder2017measuring},  \citet{bloom2009impact}
     \end{itemize}
@@
 
-%
-%\begin{frame}{Objections}
-%\begin{itemize}
-%	\item ``Subjective surveys are not trustworthy'' 
-%	\begin{itemize}
-%		\item Actually carefully designed. \cite{armantier2017overview}
-%	\end{itemize}
-%	\item ``People are bad at answering surveys, and worse on probabilities''  
-%	\begin{itemize}
-%		\item Not that bad. \cite{manski2004measuring}, \cite{delavande2014probabilistic}
-%		\item Better than not.
-%	\end{itemize}
-%	\item ``A single parameter is enough for matching macro dynamics''
-%	\begin{itemize}
-%		\item No, heterogeneity in expectation could interact with other characteristics. 
-%	\end{itemize}
-%\end{itemize}
-%\end{frame}
-
-\begin{frame}{Literature}
-\begin{itemize}
-	\item \textbf{Theory}
-	\begin{itemize}
-		\item Sticky expectation \cite{carroll2003macroeconomic}, \cite{reis2006inattentive}
-		\item Rational inattention \cite{sims2003implications},  \cite{gabaix2014sparsity}
-		\item Noisy information \cite{lucas1972expectations}, \cite{woodford2001imperfect}
-	\item Learning \cite{evans2012learning}
-	\item Strategic interaction \cite{morris2002social}, \cite{hellwig2009knowing}
-	\item Diagostic expectation  \cite{bordalo2018diagnostic}
-	\item Model uncertainty \cite{hansen2001robust}, \cite{hansen2008robustness}
-	\end{itemize}
-\item \textbf{Empirics}
-\begin{itemize}
-	\item \textbf{Heterogeneity in Expectation:} \cite{mankiw2003disagreement}
-	\item \textbf{Testing Theories:}  \textcolor{blue}{\cite{coibion2012can}, \cite{fuhrer2018intrinsic}}
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\section{Theories}
-
-\begin{frame}{Unified Framework}
+\begin{frame}{A generic framework}
 
@@
 	\begin{eqnarray*}
-	\widehat f_{i,t}(y_{t+h}|I_{i,t})
+		f_{i,t+h|t} \equiv f_{i,t}(y_{t+h}|I_{i,t})
 	\end{eqnarray*}
@@
 	\begin{itemize}
-	\item Theories differ in $I_{i,t}$
-	\item May also differ on information processing, i.e. $I_{i,t} \rightarrow \widehat f_{i,t}$
+		\item theories of expectation differ in $I_{i,t}$ 
+		\begin{itemize}
+			\item rational expectation (FIRE): $I_{i,t} = y_{i,t}$
+			\item sticky expectation (SE):  $I_{i,t} = y_{t-\tau}$, $\tau$ being the most recent update date
+			\item noisy information (NI): $I_{i,t} = s_{i,t}(y_t)$, where $s_{i,t}$ is a vector of noisy signal(s)
 		\end{itemize}
-
+		\item the process of variable determines the mapping from $I_{i,t}$ to $f_{i,t+h|t}$
+	\end{itemize}
 \end{frame}
@@
 \begin{frame}{Definition and notation}
-\begin{itemize}
-	\item \textcolor{red}{Individual}
-	\begin{itemize}
-		\item  mean forecast $\quad E_{i,t}(y_{t+h})$
-		\item forecast error $\quad FE_{i,t+h|t} = y_{t+h}- E_{i,t}(y_{t+h})$
-		\item \textcolor{blue}{uncertainty} $\quad Var_{i,t}(y_{t+h})$
-	\end{itemize}
-	\item \textcolor{red}{Population}
-	\begin{itemize}
-		\item average forecast  $\quad \bar E_{t}(y_{t+h})$
-		\item average forecast error $\quad \overline {FE}_{t}= y_{t+h}-\bar E_{t}(y_{t+h})$
-		\item \textcolor{blue}{cross-section disagreements}  $\quad Var_t(E_{i,t}(y_{t+h}))$
-		\item \textcolor{blue}{average uncertainty}  $\quad \overline{Var}_t(y_{t+h})$
-	\end{itemize}
-\end{itemize}
+	\begin{table}[ht]
+		\centering
+		\label{MomSum}
+		\begin{tabular}{ll}
+
+			\hline 
+			Individual moments                                  & Population moments                             \\
+			\hline 
+			Mean forecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
+			Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
+			Uncertainty: $Var_{i,t+h|t}$         & \textbf{Average uncertainty}:  $\overline{Var}_{t+h|t}$ \\
+			& Disagreement:  $\overline{Disg}_{t+h|t}$       \\
+			\hline 
+		\end{tabular}
+	\end{table}
 
 \end{frame}
-
-\begin{frame}{Assumption about true process}
-
-$$y_{t+1} = \rho y_t + \omega_t  $$ 
-$$\omega_t \sim N(0,\sigma^2_{\omega})$$
-
-\begin{itemize}
-	\item $0 < \rho \leq 1$
-	\item if $\rho =0$, no way to forecast at all
-	\item $\omega_t$ is i.i.d 
-\end{itemize}
-
-\end{frame}
-
-\subsection{Sticky Expectation}
-
-\begin{frame}{Sticky Expectation: assumptions}
-\begin{itemize}
-	\item At time $t$, agent $i$ learns about $y_t$ at a fixed Poisson rate $\lambda$ 
-	\item A non-updater since $t-\tau$  
-	$$E_{i,t}(y_{t+h}|y_{t-\tau}) =\rho^{h+\tau} y_{t-\tau} $$
-	\item An updater is a special cae  $\tau=0$ 
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Impulse responses to shocks: individual moments}
-
-$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
-$$\textrm{SE} \quad \quad  \lambda = 0.4 $$ 
-\begin{figure}
-	\includegraphics[scale=0.25]{figures/ir_indse} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Impulse responses to shocks: population moments}
-
-$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
-$$\textrm{SE} \quad \quad  \lambda = 0.4 $$
-
-\begin{figure}
-	\includegraphics[scale=0.25]{figures/ir_popse} 
-\end{figure}
-
-\end{frame}
-
-\subsection{Other theories}
-
-\begin{frame}{Noisy Information: assumptions}
-\begin{itemize}
-	\item Individual only observes noisy signals 
-	\begin{eqnarray*}
-		\begin{aligned}
-			& s_{i,t}=[s^{pb}_t, s^{pr}_{i,t}]' \in I_{i,t} \\
-			&\text{public signal:} \quad s^{pb}_t = y_t + \epsilon_t, \quad \epsilon_t \sim N(0,\sigma^2_\epsilon)\\ 
-			& \text{private signal:} \quad s^{pr}_{i,t} = y_t + \xi_{i,t} \quad \xi_{i,t} \sim N(0,\sigma^2_\xi)
-		\end{aligned}
-	\end{eqnarray*}
-
-	\item Kalman filtering (simply normal updating if $\rho$=0)
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Impulse responses to shocks: individual moments}
-
-$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
-$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$
-
-\begin{figure}
-	\includegraphics[height=6.3cm,width=10cm]{figures/ir_indseni} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Impulse responses to shocks: population moments}
-
-$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
-$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$
-
-\begin{figure}
-	\includegraphics[height=6.3cm,width=10cm]{figures/ir_popseni} 
-\end{figure}
-
-\end{frame}
-
-%\begin{frame}{Noisy Information: predictions}
-%\begin{itemize}
-%	\item \textbf{Similar to Sticky Expectation}
-%	\begin{enumerate}
-%\item \textbf{Macro rigidity}: population forecasts partially respond to shocks
-% \item \textbf{Non-response of variance}: both individual and population variance \textcolor{blue}{does not respond to} shocks.   
-% \end{enumerate}
-%\item \textbf{Different from Sticky Expectation}
-
-%	\begin{enumerate}
-%	\item \textbf{Micro rigidity}: both individual and population forecast \textcolor{blue}{partially} respond to shocks 
-%	\item \textbf{Horizon-sensitive rigidity}: rigidity decreases with horizon
-%	\item \textbf{Increasing disagreements:} population disagreements \textcolor{blue}{increase} over time as approaching $t+h$
-%	\item \textbf{Shock-specific responses:} different impacts of fundamental shocks, or simply news shocks 
-%\end{enumerate}
-%\end{itemize}
-
-%\end{frame}
-
-\begin{frame}{A detailed look into noisy information}
-
-\begin{figure}
-	\includegraphics[height=8cm,width=8cm]{figures/ni_illustration} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Implied rigidity of different models}
-
-\begin{figure}
-	\includegraphics[height=5cm,width=8cm]{figures/rigidity} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Other theories on to-do-list}
-\begin{itemize}
-	\item \textbf{Rational Inattention:} attentiveness endogenously respond to variances
-	\item \textbf{Learning}: the structural parameter $\rho$ is not known, thus the agent learns about it as if an econometrician does
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Identification strategies 1: testing rigidity models}
-
-\begin{itemize}
-	\item\cite{coibion2012can}
-	\begin{itemize}
-		\item \textcolor{blue}{FEs} respond to shocks and serially correlated. 
-	\end{itemize}
-	\item \textbf{Additional in this paper}
-	\begin{itemize}
-		\item \textcolor{blue}{Uncertainty} does not depend on shocks; and serially correlated. 
-	\end{itemize}
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Identification strategies 2: differentiating theories}
-\begin{itemize}
-	\item\cite{coibion2012can}
-	\begin{itemize}
-		\item \textcolor{blue}{FEs} do not depend on past realizations according to baseline SE and NI; but do so according to heterogeneous priors or precision models. 
-		\item Implied rigidity does not differ across shocks according to SE but differs according to NI. 
-		\item \textcolor{blue}{Disagreements} rise after shocks according to baseline SE, strategic interactions and heterogeneous priors but invariant according to baseline NI.
-	\end{itemize}
-	\item \textbf{Additional in this paper}
-	\begin{itemize}
-		\item \textcolor{blue}{Uncertainty} do not depend on shocks per se according to baseline SE and NI, instead on degree of information rigidity.
-	\end{itemize}
-\end{itemize}
-
-\end{frame}
-
-\section{Data and Methodology}
 
@@
 				\hline 
-		Time period                                    & 2013-present                            & 2007-present             \\
+				Time period                                    & 2013M6-2018M6                            & 2007Q1-2018Q4             \\
 				Frequency                                      & Monthly                                 & Quarterly                \\
 				Sample Size                                    & 1,300                                   & 30-50                    \\
-		Aggregate Var in Density                       & \textcolor{blue}{1-yr and 3-yr inflation}          & \textcolor{blue}{1-yr and 3-yr CPI and PCE}         \\
+				Aggregate Var in Density                       & \textcolor{blue}{1-yr-ahead inflation}          & \textcolor{blue}{1-yr and 3-yr core CPI and core PCE}         \\
 				Pannel Structure                               & stay up to 12 months                    & average stay for 5 years \\
@@
 	\end{table}
+\begin{itemize}
+	\item density estimation following (\citet{engelberg2009comparing})
+	\item exclude top and bottom 5\% values for forecast errors and uncertainty
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Basic patterns: uncertainty and realized inflation}
+	\begin{figure}
+		\centering
+		\label{InfVar}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/Inf1yf_CPIAU_varSPFCPIQ.png}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/Inf1yf_PCE_varSPFPCEQ.png}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/Inf1yf_CPIAU_varSCEM.png}
+	\end{figure}
 
@@
 
-\section{Stylized Facts}
-
-\begin{frame}{Population moments: average}
+\begin{frame}{Basic patterns: uncertainty and the size of forecast errors}
 	\begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_med.png} 
+		\centering
+		\label{FEVar}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/SPFCPI_abFE_varSPFCPIQ.png}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/SPFPCE_abFE_varSPFPCEQ.png}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/SCE_abFE_varSCEM.png}
 	\end{figure}
+\begin{itemize}
+\item no evidence for positive correlation betwen high ex ante uncertainty and ex post forecast errors.
+\end{itemize}
 \end{frame}
 
-\begin{frame}{Population moments: average forecast errors}
+\begin{frame}{Basic patterns: uncertainty and disagreement}
 	\begin{figure}
-	\includegraphics[scale=0.3]{figures/fe_fe.png} 
+		\centering
+		\label{DisgVar}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/CPI_disg_varSPFCPIQ.png}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/PCE_disg_varSPFPCEQ.png}
+		\includegraphics[width=0.3\textwidth]{figuresDraft/Q9_disg_varSCEM.png}
 	\end{figure}
+\begin{itemize}
+	\item uncertainty are not the same as disagreement for professionals 
+\end{itemize}
 \end{frame}
 
-\begin{frame}{Population moments: average uncertainty}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_var.png} 
-\end{figure}
+\begin{frame}{Basic patterns: summary}
+	\begin{itemize}
+		\item uncertainty varies across time 
+		\item uncertainty contains different information from widely  proxies such as disagreement and forecast error
+	\end{itemize}
 \end{frame}
 
-\begin{frame}{Population moments: average uncertainty}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/var_var.png} 
-\end{figure}
-\end{frame}
+\section{Theory}
 
-\begin{frame}{Population moments: disagreements}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_disg.png} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Population moments: disagreements}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_disg.png} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Population moments: disagreements}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/disg_disg.png} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Population moments: uncertainty and disagreements}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/var_disg.png} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Population moments: uncertainty and disagreements}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/var_disg2.png} 
-\end{figure}
-\end{frame}
-
-\begin{frame}{Population moments: forecast and realization}
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/mean_true.png} 
-\end{figure}
-\end{frame}
-
-\section{Empirical Results}
-
-\begin{frame}{Empirical execution}
+\begin{frame}{AR(1) model of inflation}
 
@@
 
-\item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
- \item \textbf{Identification of Shocks}: following \cite{coibion2012can} and monetary policy shocks. 
+\item 	\textbf{Inflation process}	
+	$$y_{t} = \rho y_{t-1} + \omega_t  $$ 
+	$$\omega_t \sim N(0,\sigma^2_{\omega})$$
+
+\item \textbf{Uncertainty}
+		\begin{itemize}
+			\item FIRE: time-invariant 
+			\begin{eqnarray*}\label{VarREPop}
+				\overline{Var}^*_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}
+			\end{eqnarray*}
+
+			\item SE: time-invariant 
+			\begin{eqnarray*}\label{VarSEPopRE}
+				\overline{Var}^{se}_{t+h|t} = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \overline{Var}^*_{t+h|t-\tau}
+			\end{eqnarray*}
+
+			\item NI: time-variant but quantitatively tiny due to highly efficient Kalman gain
+
+			\begin{eqnarray*}\label{VarNIPopRE}
+				\overline{Var}^{ni}_{t+h|t} = \rho^{2h} \overline{Var}^{ni}_{t|t} + \overline{Var}^*_{t+h|t}
+			\end{eqnarray*}
+		\end{itemize}
+
 	\end{itemize}
@@
 
-\subsection{Test of Null Hypothesis of Rational Expectation}
+\begin{frame}{Stocastic volatility (UCSV) inflation process (\citet{stock2007has})}
 
-\begin{frame}{Test of Rational Expectation}
-\begin{table}[tbhp] \centering \adjustbox{max height=\dimexpr\textheight-5.5cm\relax, max width=\textwidth}{
+\begin{itemize}
+\item \textbf{Inflation process}
+\begin{eqnarray*}
+\begin{split}
+& y_t = \theta_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
+& \theta_t = \theta_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
+& \log\sigma^2_{\eta,t} = \log\sigma^2_{\eta,t-1} + \mu_{\eta,t} \\
+& \log\sigma^2_{\epsilon,t} = \log\sigma^2_{\epsilon,t-1} + \mu_{\epsilon,t} 
+\end{split}
+\end{eqnarray*}
+
+\begin{eqnarray*}
+\begin{split}
+& \xi_t =[\xi_{\eta,t},\xi_{\epsilon,t}] \sim N(0,I_2) \\
+& \mu_{t} = [\mu_{\eta,t},\mu_{\epsilon,t}]' \sim N(0,\gamma I_2) 
+\end{split}
+\end{eqnarray*}
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{UCSV inflation process}
+
+	\begin{itemize}
+		\item \textbf{Uncertainty}
+		\begin{itemize}
+			\item FIRE: time-varying  \begin{eqnarray*}\label{VARRESVPop}
+			\begin{split}
+			\overline{Var}^*_{t+h|t} = \sum_{k=1}^h exp^{- 0.5k\gamma_{\eta}} \sigma^2_{\eta,t}  +  exp^{- 0.5 h \gamma_{\epsilon}} \sigma^2_{\epsilon,t} 
+			\end{split} 
+			\end{eqnarray*}
+
+			\item SE: time-varying 
+			\begin{eqnarray*}
+		\overline {Var}^{se}_{t+h|t} = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda\overline{Var}^*_{t+h|t-\tau} 
+			\end{eqnarray*}
+
+			\item NI (1-step-ahead): time-varying 
+		\begin{eqnarray*}
+		\overline{Var}^\theta_{t|t-1} = \overline{Var}^\theta_{t-1|t-1} + Var^*_{t|t-1}(y_t) 
+		\end{eqnarray*}
+
+		\end{itemize}
+	\end{itemize}
+
+\end{frame}
+
+\section{Estimation}
+\begin{frame}{Minimum distance estimation}
+
+	\begin{eqnarray*}
+	\widehat \Omega = \underset{\{\Omega \in \Gamma\} }{argmin} (M_{\textrm{data} } - F^{o}(\Omega, Y)) W  (M_{\textrm{data} } - F^{o}(\Omega, Y))'
+	\end{eqnarray*}
+
+	\begin{itemize}
+		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni} \} \times \{ar, sv\}$
+		\item  $\Gamma$: constraints for the parameter. 
+		\item $M_{data}$: data moments
+		\item $F$ model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up to each point of the time $t$
+		\item  $W$: weight matrix, identity matrix for now 
+	\end{itemize}
+
+\end{frame}
+
+\subsection{AR(1)}
+
+\begin{frame}{Results: professionals and SEAR}
+	\begin{figure}[ht]
+		\label{SE_diag_SPF}
+		\begin{subfigure}[b]{0.19\textwidth}
+			\centering
+			\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{forecast/FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag3.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag4.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Results: households and SEAR}
+	\begin{figure}[ht]
+	\label{SE_diag_SCE}
+	\begin{subfigure}[b]{0.19\textwidth}
+		\centering
+		\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.19\textwidth}
+		\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
+	\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.19\textwidth}
+	\caption{forecast/FE}
+	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.19\textwidth}
+	\caption{FE/var}
+	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.19\textwidth}
+	\caption{FE/var/Disg}
+	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag4.png}
+\end{subfigure}
+\end{figure}
+\end{frame}
+
+\begin{frame}{SE parameter estimate}
+	\begin{table}
+		\centering
+		\caption{Minimum Distance Estimates of Parameters of SE}
+		\label{GMM_Est_SE_Table}
+		\begin{tabular}{lllll}
+			\hline 
+			0        & 1    & 2   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
+			\hline 
+			Forecast &      &     & 0.04                       & 1                          \\
+			FE       &      &     & 0.05                       & 0.19                       \\
+			FE       & Disg &     & 0.17                       & 0.19                       \\
+			FE       & Var  &     & 0.16                       & 0.18                       \\
+			FE       & Disg & Var & 0.53                       & 0.18                      \\
+			\hline 
+		\end{tabular}
+	\end{table}
+\begin{itemize}
+	\item $\lambda$: update rate in SE
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Results: professionals and NIAR}
+	\begin{figure}[ht]
+		\label{NI_diag_SPF}
+		\begin{subfigure}[b]{0.19\textwidth}
+			\centering
+			\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{forecast/FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag3.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag4.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Results: households and NIAR}
+	\begin{figure}[ht]
+		\label{NI_diag_SCE}
+		\begin{subfigure}[b]{0.19\textwidth}
+			\centering
+			\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{forecast/FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag3.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag4.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{NIAR parameters}
+	\begin{table}
+		\centering
+		\caption{Minimum Distance Estimates of Parameters of NI}
+		\label{GMM_Est_NI_Table}
+		\begin{tabular}{llllll}
 	\begin{tabular}{lllllll}
 		\hline 
-		& SPFCPI\_FElvl       & SPFPCE\_FElvl & SPFCPI\_Vardiff & SPFPCE\_Vardiff & SPFCPI\_Disgdiff & SPFPCE\_Disgdiff            \\
+		0        & 1    & 2   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ \\
 		\hline 
-		L.InfExp\_FE        & 0.941***      & 1.195***        &                 &                  &                  &           \\
-		& (0.0840)      & (0.142)         &                 &                  &                  &           \\
-		L2.InfExp\_FE       & -0.313**      & -0.625**        &                 &                  &                  &           \\
-		& (0.116)       & (0.198)         &                 &                  &                  &           \\
-		L3.InfExp\_FE       & 0.114         & 0.0782          &                 &                  &                  &           \\
-		& (0.114)       & (0.196)         &                 &                  &                  &           \\
-		L4.InfExp\_FE       & -0.137        & -0.0162         &                 &                  &                  &           \\
-		& (0.0820)      & (0.131)         &                 &                  &                  &           \\
-		L.InfExp\_Var\_ch   &               &                 & -0.855***       & -0.565**         &                  &           \\
-		&               &                 & (0.189)         & (0.162)          &                  &           \\
-		L2.InfExp\_Var\_ch  &               &                 & -0.780**        & -0.452*          &                  &           \\
-		&               &                 & (0.220)         & (0.186)          &                  &           \\
-		L3.InfExp\_Var\_ch  &               &                 & -0.556*         & -0.429*          &                  &           \\
-		&               &                 & (0.219)         & (0.189)          &                  &           \\
-		L4.InfExp\_Var\_ch  &               &                 & -0.167          & 0.00385          &                  &           \\
-		&               &                 & (0.188)         & (0.172)          &                  &           \\
-		L.InfExp\_Disg\_ch  &               &                 &                 &                  & -0.571***        & -0.640*** \\
-		&               &                 &                 &                  & (0.0699)         & (0.127)   \\
-		L2.InfExp\_Disg\_ch &               &                 &                 &                  & -0.376***        & -0.0944   \\
-		&               &                 &                 &                  & (0.0764)         & (0.141)   \\
-		L3.InfExp\_Disg\_ch &               &                 &                 &                  & -0.0455          & 0.180     \\
-		&               &                 &                 &                  & (0.0661)         & (0.138)   \\
-		L4.InfExp\_Disg\_ch &               &                 &                 &                  & -0.110*          & -0.0364   \\
-		&               &                 &                 &                  & (0.0479)         & (0.123)   \\
-		\hline 
-		N                   & 143           & 41              & 44              & 44               & 146              & 44        \\
-		R-sq                & 0.593         & 0.750           & 0.384           & 0.322            & 0.356            & 0.496    \\
+		Forecast &      &     & 39.65                     & 192.22                & 2.35                      & 0.38                  \\
+		FE       &      &     & 12.64                     & 211.14                & 1.64                      & 0                     \\
+		FE       & Disg &     & 112.37                    & 0.34                  & 512.51                    & 0.86                  \\
+		FE       & Var  &     & 1.13                      & 367.43                & 0                         & 1.28                  \\
+		FE       & Disg & Var & 1.29                      & 29.84                 & 2.74                      & 127.86                \\
 		\hline 
 	\end{tabular}  
-}
+		\end{tabular}
+	\end{table}	
+\begin{itemize}
+	\item $\sigma_{pb}$: noisiness of public signals in NI
+	\item $\sigma_{pr}$: noisiness of private signals in Ni 
+\end{itemize}
+\end{frame}
+
+\subsection{Stocastic volatility}
+
+\begin{frame}{Results: professionals and SESV}
+	\begin{figure}[ht]
+		\label{SESV_diag_SPF}
+		\begin{subfigure}[b]{0.19\textwidth}
+			\centering
+			\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{forecast/FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag4.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Results: households and SESV}
+	\begin{figure}[ht]
+		\label{SESV_diag_SCE}
+		\begin{subfigure}[b]{0.19\textwidth}
+			\centering
+			\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{forecast/FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag3.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag4.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{SESV parameters}
+	\begin{table}
+		\centering
+		\caption{Minimum Distance Estimates of Parameters of SESV}
+		\label{GMM_Est_SE_SV_Table}
+	\begin{tabular}{lllll}
+		\hline 
+		0        & 1    & 2   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
+			\hline 
+		Forecast &      &     & 0.1                        & 0.02                       \\
+		FE       &      &     & 0.12                       & 1                          \\
+		FE       & Disg &     & 0.14                       & 1                          \\
+		FE       & Var  &     & 0.12                       & 1                          \\
+		FE       & Disg & Var & 0.14                       & 1                         \\
+			\hline 
+	\end{tabular}
+\begin{itemize}
+	\item $\lambda$: update rate in SE
+\end{itemize}
 	\end{table}	
@@
 
-\begin{frame}{Identified Inflation shocks}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/inf_shocksQ.png} 
+\begin{frame}{Results: professionals and NISV}
+	\begin{figure}[ht]
+		\label{NISV_diag_SPF}
+		\begin{subfigure}[b]{0.19\textwidth}
+			\centering
+			\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{forecast/FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag3.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag4.png}
+		\end{subfigure}
 	\end{figure}
-
 \end{frame}
 
-\begin{frame}{Results from \cite{coibion2012can}}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/RigidityJPEFigure2.png} 
+\begin{frame}{Results: households and NISV}
+	\begin{figure}[ht]
+		\label{NISV_diag_SCE}
+		\begin{subfigure}[b]{0.19\textwidth}
+			\centering
+			\caption{forecast}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{forecast/FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag3.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.19\textwidth}
+			\caption{FE/var/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag4.png}
+		\end{subfigure}
 	\end{figure}
-
 \end{frame}
 
-\begin{frame}{Inflation IR to  shocks}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/CPIAU_ashocks.png} 
-\end{figure}
-
+\begin{frame}{NISV parameters}
+	\begin{table}
+		\centering
+		\caption{Minimum Distance Estimates of Parameters of NISV}
+		\label{GMM_Est_NI_SV_Table}
+	\begin{tabular}{lllllll}
+		\hline 
+		0        & 1    & 2   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ \\
+		\hline 
+		Forecast &      &     & 16.9                      & 21.44                 & 5.21                      & 6.05                  \\
+		FE       &      &     & 67.05                     & 146.8                 & 4.4                       & 4.88                  \\
+		FE       & Disg &     & 62.6                      & 0.57                  & 7.23                      & 3.54                  \\
+		FE       & Var  &     & 787.17                    & 3257.84               & 97.72                     & 95.73                 \\
+		FE       & Disg & Var & 126.68                    & 0.57                  & 215.54                    & 3.64                 \\
+		\hline 
+	\end{tabular}
+	\end{table}	
+\begin{itemize}
+	\item $\sigma_{pb}$: noisiness of public signals in NI
+	\item $\sigma_{pr}$: noisiness of private signals in NI 
+\end{itemize}
 \end{frame}
 
-\begin{frame}{Inflation IR to  shocks}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/PCEPI_ashocks.png} 
-\end{figure}
-
+\begin{frame}{Ongoing work}
+	\begin{itemize}
+		\item I have been matching time-specific conditional moments with data. I will match unconditional moments
+		\item jointly estimate process parameters and expectation formation parameters
+		\item statistical tests of the fitness,  i.e. Sargan–Hansen test in the GMM
+	\end{itemize}	
 \end{frame}
 
-\subsection{Professional forecasters as a baseline }
+\section{Conclusion}
 
-\begin{frame}{Forecasting errors IR to  shocks}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFFE_ashocks.png} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Disagreements IR to  shocks}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks.png} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Uncertainty IR to shocks}
-
-\begin{figure}
-	\includegraphics[scale=0.3]{figures/SPFVar_ashocks.png} 
-\end{figure}
-
+\begin{frame}{Conclusion}
+	\begin{itemize}
+		\item Sticky expectation (SE) matches data of inflation and expectations better compared to noisy information (NI) 
+		\item Within each model,  households are more irrational compared to professionals
+		\item Incorporating higher moments, i.e. uncertainty,  helps ``discipline'' theories on expectation formation
+		\item  Higher moments from surveys also contain useful information about the inflation dynamics itself
+	\end{itemize}	
 \end{frame}
@@
 
-\section{Appendix}
-
-\begin{frame}{Sticky Expectation: individual}
-
-For a non-updater since $t-\tau$ ($\tau=0$ for updater),
-\begin{itemize}
-\item \textbf{Mean} $$E_{i,t}(y_{t+h}|y_{t-\tau}) = \rho^{h+\tau} y_{t-\tau}$$  
-\item \textbf{Forecast Error} $$FE_{i,t+h|t} = \underbrace{\sum^{h+\tau}_{s=0} \rho^s \omega_{t+h-s}}_{\substack{\text{weighted sum of} \\ \text{future realized shocks}} }$$
-\item \textcolor{blue}{\textbf{Variance}} $$Var_{i,t}(y_{t+h}|y_{t-\tau}) = \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}$$	
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Sticky Expectation: individual}
-
-$$\text{updater: } \quad \Delta Var_{i,t}(y_{t+h}|y_t)= \sum^{\tau}_{s=0} \rho^{2s}\sigma^2_{\omega}$$
-$$\text{non-updater: }  \Delta Var_{i,t|t-\tau-1}(y_{t+h}|y_{t-\tau-1})  = \sigma^2_{\omega}$$
-
-\begin{enumerate}
-\item Change in expectation(and variance) depends on if update or not 
-\item Cannot observe systematically sluggish response to shocks at individual level 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Sticky Expectation: population}
-\begin{itemize}
-	\item \textbf{Average forecast} 
-	\begin{eqnarray*}
-		\begin{aligned}
-			\bar E_t(y_{t+h}) & = \lambda \underbrace{E_t(y_{t+h})}_{\text{rational expectation at t}} + (1-\lambda) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{average expectation at } t-1} \\
-			& = \lambda E_t(y_{t+h}) + (1-\lambda) (\lambda E_{t-1}(y_{t+h})+ ...) \\
-			& =\underbrace{ \lambda \sum^{\infty}_{s=0} (1-\lambda)^s E_{t-s}(y_{t+h})}_{\text{weighted sum of past rational expectations}}
-		\end{aligned}
-	\end{eqnarray*}
-	\item \textbf{Change in average forecast}
-	$$\Delta \bar E_t(y_{t+h})=\underbrace{(1-\lambda)}_{\text{stickiness}} \Delta \bar E_{t-1}(y_{t+h}) + \lambda \rho^h \omega_t$$ 
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Sticky Expectation: population}
-\begin{itemize}
-\item \textbf{Disagreements}
-\begin{eqnarray*}
-	\begin{aligned}
-		Var_t(y_{t+h} ) & = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^{\tau} (E_{t|t-\tau}(y_{t+h}) - \bar E_t(y_{t+h}))^2  
-	\end{aligned}
-\end{eqnarray*}
-\item \textbf{Change in disagreements}
-$$\Delta Var_t (y_{t+h}) = \rho^{2h} (1-\lambda)\lambda \underbrace{\omega^2_t}_{\text{shock at time t}}$$
-\end{itemize}
-
-\begin{enumerate}
-\item Disagreements rise after the shock and then gradually decline 
-\item Response of disagreements depends on the size of the shock
-\end{enumerate}
-\end{frame}
-
-\begin{frame}{Sticky Expectation: population}
-\begin{itemize}
-\item \textcolor{blue}{\textbf{Average variance}}
-\begin{eqnarray*}
-\begin{aligned}
-	\overline {Var}_{t}(y_{t+h}) &  =  (1-\lambda)\underbrace{\overline {Var}_{t-1}(y_{t+h})}_{\text{average variance at t-1}} + \underbrace{\lambda Var_{t}(y_{t+h})}_{\text{variance of updater at t} }
-\end{aligned}
-\end{eqnarray*}
-\item \textbf{Change in average variance}
-$$\Delta \overline {Var}_{t}(y_{t+h}) = \underbrace{(1-\lambda)\Delta \overline {Var}_{t-1}(y_{t+h}) - \lambda \rho^{2h}\sigma^2_{\omega}}_{\text{does not depend on shock at t}}$$
-\end{itemize}
-
-\begin{enumerate}
-\item Average variance does not respond to shocks
-\item Average variance has serial correlation with the same rigidity parameter $1-\lambda$ 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: individuals}
-\begin{itemize}
-	\item \textbf{Mean}
-	\begin{eqnarray*}
-		\begin{aligned}
-			E_{i,t}(y_{t+h}) & = \rho^{h}E_{i,t|t}(y_{t}) \\
-			E_{i,t|t}(y_{t}) 
-			& =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
-			& = (1-PH) E_{i,t|t-1}(y_{t}) + Ps_{i,t} \\
-			\text{where }  & P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} \\
-			\text {where } & \Sigma^y_{i,t|t-1} \text{ is the variance of } y_t \text{ based on prior belief}\\
-			\text {and } & \Sigma^v =  \left[ \begin{matrix} 
-				\sigma^2_{\epsilon} &  0 \\ 0 & \sigma^2_\xi \end{matrix}\right] 
-		\end{aligned}
-	\end{eqnarray*}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Noisy Information: individuals}
-\begin{itemize}
-\item \textbf{Change in mean}
-\begin{eqnarray*}
-	\begin{aligned}
-		\Delta E_{i,t|t}(y_{t+h}) & = \underbrace{\rho^h (1-PH)\Delta E_{i,t-1|t-1}(y_{t})}_{\text{Lagged response}} \\
-		& + \underbrace{\rho^hPH \Delta y_{i,t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
-	\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item Rigidity parameter $1-PH$
-	\item Serial correlation at individual level 
-	\item Always respond to shocks 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: individuals}
-\begin{itemize}
-	\item \textbf{Variance}
-
-	\begin{eqnarray*}
-		\begin{aligned}
-			\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) ^{-1}H \Sigma^y_{i,t|t-1} 
-		\end{aligned}
-	\end{eqnarray*}
-	\item \textbf{Change in variance} 
-	$$\Delta \Sigma^y_{i,t|t} <0$$
-
-\end{itemize}
-\begin{enumerate}
-	\item It does not depend on the realizations of the signal. 
-	\item It decreases unambiguously from $t-1$ to $t$. 
-	\item The two properties carry through to h-period ahead forecast 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Mean}
-
-\begin{eqnarray*}
-	\begin{aligned}
-		\bar E_{t|t} (y_{t+h}) & = \rho^h [(1-PH) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
-		& = (1-PH) \bar E_{t-1}(y_{t+h}) + P [\epsilon_t, 0]' \\
-		& = (1-PH) \bar E_{t-1}(y_{t+h}) + P \epsilon_t
-	\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item Same properties to the individual forecast 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Disagreements}
-\begin{eqnarray*}
-\begin{aligned}
-	Var_t(y_{t+h}) & = E((E_{i,t|t}(y_{t+h}) - \bar E_t(y_{t+h}))^2) \\
-	& = \rho^{2h} P^2_\xi \sigma^2_\xi  
-\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item increase with the forecast horizon
-	\item depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$ 
-	\item increase with the rigidity parameter $P$ in this model
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Change in disagreements}
-\begin{eqnarray*}
-\begin{aligned}
-\Delta Var_t(y_{t+h}) & = \rho^{2h}(1-\rho^2) P^2_\xi \sigma^2_\xi >0
-\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item disagreements increase as time goes from $t-1$ to $t$. 
-	\item disagreements increase as approaching the variable of forecast
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Average variance}
-\begin{eqnarray*}
-\begin{aligned}
-\bar Var_t (y_{t+h}) = \bar \Sigma^y_t
-\end{aligned}
-\end{eqnarray*}
-\item \textbf{Change in average variance}
-\begin{eqnarray*}
-\Delta Var_t(y_{t+h}) < 0 
-\end{eqnarray*}
-
-\end{itemize}
-
-\begin{enumerate}
-	\item average variance is the same as individual variance, not depend on signals
-	\item the variance unambiguously drop over time 
-\end{enumerate}
-
-\end{frame}
-
 \end{document}

### 2019-12-17 slides/ExpSlidesnew.tex
slides for brown bag seminar. Will work on following things. 1. true GMM, unconditional moments. 2. randseed lead to SMM.

--- 2019-07-03 slides/ExpSlidesAfterDraft.tex
@@
 \usepackage{natbib}
+\usepackage{adjustbox}
 
@@
 
-\subsection{Shock-Based Rigidity}
-
-\begin{frame}{Inflation shocks}
-
-\begin{figure}
-	\includegraphics[width=0.8\textwidth]{figuresDraft/inf_shocksQ.png} 
-\end{figure}
-
+\begin{frame}{Estimation: minimum distance approach}
+	\begin{itemize}
+\item model-specific moment dynamics as a function real time data and process parameters 
+\item minimize the distance (percent deviation) from the data moments to find the parameter of expectation formation	
+	\end{itemize}
 \end{frame}
 
-\begin{frame}{Results from \citet{coibion2012can}}
-
-\begin{figure}
-	\includegraphics[width=0.9\textwidth]{figuresDraft/RigidityJPEFigure2.png} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Technology and oil shocks: 1984-2007}
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_nmp_before2007.png}  \\ 
-\smallskip
-\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_nmp_before2007.png} \\
-\smallskip
-\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_nmp_before2007.png} 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Monetary policy shocks: 1984-2007}
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_before2007.png}  \\
-	\smallskip 
-	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_before2007.png} \\
-	\smallskip
-	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_before2007.png} 
+\begin{frame}{Results: professionals and SEAR}
+\begin{figure}[ht]
+	\centering
+    \label{SE_diag_SPF}
+		\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/spf_se_est_diag0.png}
+		\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/spf_se_est_diag1.png}
+		\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/spf_se_est_diag2.png}
+		\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/spf_se_est_diag3.png}
+		\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/spf_se_est_diag4.png}
 \end{figure}
@@
 
-\begin{frame}{Technology and oil shocks: 1984-2019}
+\begin{frame}{Results: households and SEAR}
 
-\begin{figure}
-	\includegraphics[width=0.6\textwidth,totalheight=\0.4\textheight]{figuresDraft/Inf_ashocks_nmp.png}  
-	\includegraphics[[width=0.6\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFFE_ashocks_nmp.png}  \\
-	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFDisg_ab_ashocks_nmp.png} 
-	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFVar_ab_ashocks_nmp.png}  
+	\begin{frame}{Results: households and SESV}
+		\begin{figure}[ht]
+			\centering
+			\label{SESV_diag_SCE}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_sv_diag0.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_sv_diag1.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_sv_diag2.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_sv_diag3.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/spf_se_est_sv_diag4.png}
 		\end{figure}
@@
 
-\begin{frame}{Monetary policy shocks: 1984-2019}
+	\begin{frame}{SEAR parameters}
+		\begin{figure}[ht]
+			\centering
+			\label{SE_diag_SCE}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_diag0.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_diag1.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_diag2.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_diag3.png}
+			\includegraphics[width=0.19\textwidth, height = \0.95\textheight]{figures/sce_se_est_diag4.png}
+		\end{figure}
+	\end{frame}
 
-\begin{figure}
-	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/Inf_ashocks.png} 
-	\smallskip
-	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFFE_ashocks.png} \\
-	\smallskip
-	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFDisg_ab_ashocks.png} 
-	\smallskip
-	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFVar_ab_ashocks.png}  
-\end{figure}
+	\begin{frame}{SESV parameters}
+		\begin{table}
+			\centering
+			\caption{GMM Estimates of Parameters of SESV}
+			\label{GMM_Est_SE_SV_Table}
+			\begin{tabular}{llllll}
+				\hline 
+				0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
+				\hline 
+				Forecast &    &      &     & 0.23                       & 0.01                       \\
+				FE       &    &      &     & 0.12                       & 1                          \\
+				Forecast & FE &      &     & 0.12                       & 1                          \\
+				Forecast & FE & Disg &     & 0.12                       & 1                          \\
+				Forecast & FE & Disg & Var & 0.12                       & 1           \\
+				\hline               
+			\end{tabular}
+		\end{table}	
+	\end{frame}
 
+	\begin{frame}{SESV parameters}
+		\begin{table}
+			\centering
+			\caption{GMM Estimates of Parameters of SE and Inflation Process}
+			\label{GMM_Est_SE_Table}
+			\begin{tabular}{llllllllllll}
+				\hline 
+				& 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
+				\hline 
+				Forecast &    &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
+				FE       &    &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
+				Forecast & FE &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
+				Forecast & FE & Disg &     & 0.7                        & 0.38                       & 0.88       & 0.1          & 0.02                       & 0.03                       & 0.98       & 0.1          \\
+				Forecast & FE & Disg & Var & 0.7                        & 0.38                       & 0.88       & 0.2          & 0.01                       & 0.03                       & 0.98       & 1.11     \\
+				\hline    
+			\end{tabular}
+		\end{table}
+\end{frame}
+
+\begin{frame}{Conclusion}
+\begin{itemize}
+	\item Sticky expectation(SE) matches data of inflation and expectations better compared to nosiy information (NI) 
+	\item Within model,  households are more irrational compared professionals
+	\item Incorporating higher moments, i.e. uncertainty helps ``discipline'' theories on expectation formation
+	\item  Higher moments from surveys also contain useful information about the inflation dynamics itself
+\end{itemize}	
 \end{frame}
@@
 
-\begin{frame}{Sticky Expectation: individual}
-
-For a non-updater since $t-\tau$ ($\tau=0$ for updater),
-\begin{itemize}
-\item \textbf{Mean} $$E_{i,t}(y_{t+h}|y_{t-\tau}) = \rho^{h+\tau} y_{t-\tau}$$  
-\item \textbf{Forecast Error} $$FE_{i,t+h|t} = \underbrace{\sum^{h+\tau}_{s=0} \rho^s \omega_{t+h-s}}_{\substack{\text{weighted sum of} \\ \text{future realized shocks}} }$$
-\item \textcolor{blue}{\textbf{Variance}} $$Var_{i,t}(y_{t+h}|y_{t-\tau}) = \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}$$	
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Sticky Expectation: individual}
-
-$$\text{updater: } \quad \Delta Var_{i,t}(y_{t+h}|y_t)= \sum^{\tau}_{s=0} \rho^{2s}\sigma^2_{\omega}$$
-$$\text{non-updater: }  \Delta Var_{i,t|t-\tau-1}(y_{t+h}|y_{t-\tau-1})  = \sigma^2_{\omega}$$
-
-\begin{enumerate}
-\item Change in expectation(and variance) depends on if update or not 
-\item Cannot observe systematically sluggish response to shocks at individual level 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Sticky Expectation: population}
-\begin{itemize}
-	\item \textbf{Average forecast} 
-	\begin{eqnarray*}
-		\begin{aligned}
-			\bar E_t(y_{t+h}) & = \lambda \underbrace{E_t(y_{t+h})}_{\text{rational expectation at t}} + (1-\lambda) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{average expectation at } t-1} \\
-			& = \lambda E_t(y_{t+h}) + (1-\lambda) (\lambda E_{t-1}(y_{t+h})+ ...) \\
-			& =\underbrace{ \lambda \sum^{\infty}_{s=0} (1-\lambda)^s E_{t-s}(y_{t+h})}_{\text{weighted sum of past rational expectations}}
-		\end{aligned}
-	\end{eqnarray*}
-	\item \textbf{Change in average forecast}
-	$$\Delta \bar E_t(y_{t+h})=\underbrace{(1-\lambda)}_{\text{stickiness}} \Delta \bar E_{t-1}(y_{t+h}) + \lambda \rho^h \omega_t$$ 
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Sticky Expectation: population}
-\begin{itemize}
-\item \textbf{Disagreements}
-\begin{eqnarray*}
-	\begin{aligned}
-		Var_t(y_{t+h} ) & = \lambda \sum^{\infty}_{\tau=0} (1-\lambda)^{\tau} (E_{t|t-\tau}(y_{t+h}) - \bar E_t(y_{t+h}))^2  
-	\end{aligned}
-\end{eqnarray*}
-\item \textbf{Change in disagreements}
-$$\Delta Var_t (y_{t+h}) = \rho^{2h} (1-\lambda)\lambda \underbrace{\omega^2_t}_{\text{shock at time t}}$$
-\end{itemize}
-
-\begin{enumerate}
-\item Disagreements rise after the shock and then gradually decline 
-\item Response of disagreements depends on the size of the shock
-\end{enumerate}
-\end{frame}
-
-\begin{frame}{Sticky Expectation: population}
-\begin{itemize}
-\item \textcolor{blue}{\textbf{Average variance}}
-\begin{eqnarray*}
-\begin{aligned}
-	\overline {Var}_{t}(y_{t+h}) &  =  (1-\lambda)\underbrace{\overline {Var}_{t-1}(y_{t+h})}_{\text{average variance at t-1}} + \underbrace{\lambda Var_{t}(y_{t+h})}_{\text{variance of updater at t} }
-\end{aligned}
-\end{eqnarray*}
-\item \textbf{Change in average variance}
-$$\Delta \overline {Var}_{t}(y_{t+h}) = \underbrace{(1-\lambda)\Delta \overline {Var}_{t-1}(y_{t+h}) - \lambda \rho^{2h}\sigma^2_{\omega}}_{\text{does not depend on shock at t}}$$
-\end{itemize}
-
-\begin{enumerate}
-\item Average variance does not respond to shocks
-\item Average variance has serial correlation with the same rigidity parameter $1-\lambda$ 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: individuals}
-\begin{itemize}
-	\item \textbf{Mean}
-	\begin{eqnarray*}
-		\begin{aligned}
-			E_{i,t}(y_{t+h}) & = \rho^{h}E_{i,t|t}(y_{t}) \\
-			E_{i,t|t}(y_{t}) 
-			& =  \underbrace{E_{i,t|t-1}(y_{t})}_{\text{prior}} + P \underbrace {(s_{i,t|t}-s_{i,t|t-1})}_{\text{innovations to signals}} \\
-			& = (1-PH) E_{i,t|t-1}(y_{t}) + Ps_{i,t} \\
-			\text{where }  & P = [P_\epsilon,P_\xi]= \Sigma^y_{i,t|t-1} H(H'\Sigma^y_{i,t|t-1} H + \Sigma^v)^{-1} \\
-			\text {where } & \Sigma^y_{i,t|t-1} \text{ is the variance of } y_t \text{ based on prior belief}\\
-			\text {and } & \Sigma^v =  \left[ \begin{matrix} 
-				\sigma^2_{\epsilon} &  0 \\ 0 & \sigma^2_\xi \end{matrix}\right] 
-		\end{aligned}
-	\end{eqnarray*}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Noisy Information: individuals}
-\begin{itemize}
-\item \textbf{Change in mean}
-\begin{eqnarray*}
-	\begin{aligned}
-		\Delta E_{i,t|t}(y_{t+h}) & = \underbrace{\rho^h (1-PH)\Delta E_{i,t-1|t-1}(y_{t})}_{\text{Lagged response}} \\
-		& + \underbrace{\rho^hPH \Delta y_{i,t} + \rho^h P\Delta v_{i,t}}_{\text{Shocks to signals}}\\
-	\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item Rigidity parameter $1-PH$
-	\item Serial correlation at individual level 
-	\item Always respond to shocks 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: individuals}
-\begin{itemize}
-	\item \textbf{Variance}
-
-	\begin{eqnarray*}
-		\begin{aligned}
-			\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) ^{-1}H \Sigma^y_{i,t|t-1} 
-		\end{aligned}
-	\end{eqnarray*}
-	\item \textbf{Change in variance} 
-	$$\Delta \Sigma^y_{i,t|t} <0$$
-
-\end{itemize}
-\begin{enumerate}
-	\item It does not depend on the realizations of the signal. 
-	\item It decreases unambiguously from $t-1$ to $t$. 
-	\item The two properties carry through to h-period ahead forecast 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Mean}
-
-\begin{eqnarray*}
-	\begin{aligned}
-		\bar E_{t|t} (y_{t+h}) & = \rho^h [(1-PH) \underbrace{\bar E_{t-1}(y_{t+h})}_{\text{Average prior}} + P \underbrace{\bar s_{t}}_{\text{Average Signals}}] \\
-		& = (1-PH) \bar E_{t-1}(y_{t+h}) + P [\epsilon_t, 0]' \\
-		& = (1-PH) \bar E_{t-1}(y_{t+h}) + P \epsilon_t
-	\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item Same properties to the individual forecast 
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Disagreements}
-\begin{eqnarray*}
-\begin{aligned}
-	Var_t(y_{t+h}) & = E((E_{i,t|t}(y_{t+h}) - \bar E_t(y_{t+h}))^2) \\
-	& = \rho^{2h} P^2_\xi \sigma^2_\xi  
-\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item increase with the forecast horizon
-	\item depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$ 
-	\item increase with the rigidity parameter $P$ in this model
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Change in disagreements}
-\begin{eqnarray*}
-\begin{aligned}
-\Delta Var_t(y_{t+h}) & = \rho^{2h}(1-\rho^2) P^2_\xi \sigma^2_\xi >0
-\end{aligned}
-\end{eqnarray*}
-\end{itemize}
-
-\begin{enumerate}
-	\item disagreements increase as time goes from $t-1$ to $t$. 
-	\item disagreements increase as approaching the variable of forecast
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Noisy Information: population}
-\begin{itemize}
-\item \textbf{Average variance}
-\begin{eqnarray*}
-\begin{aligned}
-\bar Var_t (y_{t+h}) = \bar \Sigma^y_t
-\end{aligned}
-\end{eqnarray*}
-\item \textbf{Change in average variance}
-\begin{eqnarray*}
-\Delta Var_t(y_{t+h}) < 0 
-\end{eqnarray*}
-
-\end{itemize}
-
-\begin{enumerate}
-	\item average variance is the same as individual variance, not depend on signals
-	\item the variance unambiguously drop over time 
-\end{enumerate}
-
-\end{frame}
-
 \end{document}

### 2019-12-17 workingfolder/python/DoEstimationWithData.py

@@ -316,9 +316,9 @@ plt.savefig('figures/sce_re_est_diag.png')
 moments_choices_short = [['Forecast']]
 moments_choices = [['Forecast'],
                    ['FE'],
-                   ['Forecast','FE'],
-                   ['Forecast','FE','Disg'],
-                   ['Forecast','FE','Disg','Var']]
+                   ['FE','Disg'],
+                   ['FE','Var'],
+                   ['FE','Disg','Var']]
 
 para_est_SPF_holder = []
 para_est_SPF_joint_holder = []
@@ -341,26 +341,26 @@ for i,moments_to_use in enumerate(moments_choices):
     
     # only expectation
     SE_model.ParaEstimate(method='L-BFGS-B',
-                          para_guess = np.array([0.5]),
+                          para_guess = np.array([0.1]),
                           bounds = ((0,1),),
                           options={'disp':True})
     para_est_SPF_holder.append(SE_model.para_est)
-    SE_model.all_moments = ['Forecast','FE','Disg','Var']
+    SE_model.all_moments = ['Forecast','FE','Disg']
     SE_model.ForecastPlotDiag(all_moms = True)
     plt.savefig('figures/spf_se_est_diag'+str(i)+'.png')
     
     # joint estimate
-    SE_model.ParaEstimateJoint(method='L-BFGS-B',
-                               para_guess =(0.5,0.8,0.1),
-                               bounds = ((0,1),(0,1),(0,None)),
-                               options={'disp':True})
-    para_est_SPF_joint_holder.append(SE_model.para_est_joint)
-    SE_model.all_moments = ['Forecast','FE','Disg','Var']
-    SE_model.ForecastPlotDiagJoint(all_moms = True)
-    plt.savefig('figures/spf_se_est_joint_diag'+str(i)+'.png')
+    #SE_model.ParaEstimateJoint(method='L-BFGS-B',
+    #                           para_guess =(0.5,0.8,0.1),
+    #                           bounds = ((0,1),(0,1),(0,None)),
+    #                           options={'disp':True})
+    #para_est_SPF_joint_holder.append(SE_model.para_est_joint)
+    #SE_model.all_moments = ['Forecast','FE','Disg']
+    #SE_model.ForecastPlotDiagJoint(all_moms = True)
+    #plt.savefig('figures/spf_se_est_joint_diag'+str(i)+'.png')
     
 print(para_est_SPF_holder)
-print(para_est_SPF_joint_holder)
[…]

### 2019-12-17 workingfolder/python/DoEstimationWithData_Dev_SV.py

@@ -304,15 +304,15 @@ data_moms_dct_SCE = dict(exp_data_SCE)
 #
 # #### SPF
 
-# + {"code_folding": [0, 3, 14]}
+# + {"code_folding": [0]}
 ## SE loop estimation overdifferent choieces of moments for SPF
 
 moments_choices_short = [['Forecast']]
 moments_choices = [['Forecast'],
                    ['FE'],
-                   ['Forecast','FE'],
-                   ['Forecast','FE','Disg'],
-                   ['Forecast','FE','Disg','Var']]
+                   ['FE','Disg'],
+                   ['FE','Var'],
+                   ['FE','Disg','Var']]
 
 para_est_SPF_holder = []
 para_est_SPF_joint_holder = []
@@ -383,15 +383,15 @@ spf_se_est_para
 
 # #### SCE
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## SE loop estimation over different choieces of moments for SCE
 
 moments_choices_short =[['Forecast']]
 moments_choices = [['Forecast'],
                    ['FE'],
-                   ['Forecast','FE'],
-                   ['Forecast','FE','Disg'],
-                   ['Forecast','FE','Disg','Var']]
+                   ['FE','Disg'],
+                   ['FE','Var'],
+                   ['FE','Disg','Var']]
 
 para_est_SCE_holder = []
 para_est_SCE_joint_holder =[]
@@ -445,7 +445,7 @@ for i,moments_to_use in enumerate(moments_choices):
 print(para_est_SCE_holder)
 print(para_est_SCE_joint_holder)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 sce_se_est_para = pd.DataFrame(para_est_SCE_holder,
                                columns=[r'SE: $\hat\lambda_{SCE}$(M)'])
 #sce_se_joint_est_para = pd.DataFrame(para_est_SCE_joint_holder,
@@ -460,7 +460,7 @@ est_moms = pd.DataFrame(moments_choices)
 ## combining SCE and SPF 
 se_est_df = pd.concat([est_moms,
                        spf_se_est_para,
-                       sce_se_est_para], 
+                       sce_se_est_para],
                       join='inner', axis=1)
 # -
 
@@ -484,9 +484,9 @@ se_est_df.to_excel('tables/SE_Est_sv.xlsx',
 moments_choices_short = [['Forecast']]
 moments_choices = [['Forecast'],
                    ['FE'],
[…]

### 2019-12-17 workingfolder/python/GMMEst.py

@@ -33,7 +33,7 @@ import copy as cp
 from scipy.stats import bernoulli
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": []}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -60,7 +60,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": []}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -75,7 +75,7 @@ def PrepMom(model_moments,
     diff: the Euclidean distance of two arrays of data and model 
     
     """
-    diff = np.linalg.norm(model_moments - data_moments)
+    diff = np.linalg.norm((model_moments - data_moments)/data_moments)
     return diff
 
 
@@ -331,7 +331,7 @@ class StickyExpectation:
         self.data_moms_dct ={}
         self.para_est = {}
         self.moments = moments
-        self.all_moments = ['Forecast','FE','Disg','Var']
+        self.all_moments = ['Forecast','FE','Disg']
         self.realized = None
         self.sim_realized = None
         

### 2020-02-05 workingfolder/python/GMMEst.py
drafted the codes of GMM for SE in GMM_Dev. Needed to test.

@@ -31,10 +31,12 @@ import statsmodels.api as sm
 from statsmodels.tsa.api import AR
 import copy as cp 
 from scipy.stats import bernoulli
+from numba import jit, njit # njit is just an alias for jit(nopython=True)
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": [2]}
 # a general-purpose estimating function of the parameter
+@jit
 def Estimator(obj_func,
               para_guess,
               method='CG',
@@ -60,8 +62,9 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": []}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
+@jit
 def PrepMom(model_moments,
             data_moments):
     """
@@ -79,7 +82,7 @@ def PrepMom(model_moments,
     return diff
 
 
-# + {"code_folding": [1, 5, 9, 18, 41]}
+# + {"code_folding": [0, 1, 5, 9, 18, 41]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -138,7 +141,7 @@ process_para = {'rho':rho,
                 'sigma':sigma}
 
 
-# + {"code_folding": [1, 16, 19, 30, 53, 58, 66, 76, 80, 91, 109, 111, 115]}
+# + {"code_folding": [2, 16, 19, 31, 54, 59, 67, 77, 82, 93, 111, 113, 117]}
 ## Rational Expectation (RE) class 
 class RationalExpectation:
     def __init__(self,
@@ -168,7 +171,8 @@ class RationalExpectation:
             cum_shock = sum([rho**h*shocks[h] for h in range(self.horizon)])
             realized[i] = rho**self.horizon*self.real_time[i] + cum_shock
         self.realized = realized        
-        
+    
+    @jit
     def Forecaster(self):
         ## parameters
         n = len(self.real_time)
@@ -219,6 +223,7 @@ class RationalExpectation:
                        data_moms_dct):
         self.data_moms_dct = data_moms_dct
     
+    @jit
     def ParaEstimate(self,
                      para_guess = np.array([0.5,0.1]),
                      method = 'CG',
@@ -278,24 +283,25 @@ class RationalExpectation:
 
 # + {"code_folding": []}
 ### create a RE instance 
[…]

### 2020-02-05 workingfolder/python/GMMEst_Dev.py

@@ -127,7 +127,7 @@ def Estimator2(obj_func,
     return parameter 
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": [0, 6]}
 def myfunc(x, grad):
     if grad.size > 0:
         grad[0] = 0.0
@@ -583,7 +583,7 @@ RE_instance.GetDataMoments(fe_moms)
 SE_para_default = {'lambda':0.2}
 
 
-# + {"code_folding": [2, 24, 41, 57, 89, 160, 219, 231, 256, 278, 300, 323, 337, 349, 361, 373, 384, 406, 436, 466, 470]}
+# + {"code_folding": [2, 24, 28, 41, 57, 104, 175, 246, 271, 293, 315, 338, 352, 364, 376, 388, 399, 421, 451, 481]}
 ## Sticky Expectation(SE) class 
 class StickyExpectation:
     def __init__(self,
@@ -659,18 +659,33 @@ class StickyExpectation:
         
         ## moments 
         
+        # FE
         FE = 0  
-        Disg = rho**(2*horizon)*(1-lbd)**2*lbd**2*sigma**2/(1- lbd**2*(1-lbd)**2) ## might be wrong. needs to check 
-        ATV = (1-lbd)**Disg                               
-        Var = sum([(1-lbd)**tau*lbd*hstepvar(horizon+tau,sigma,rho) for tau in range(n + n_burn)])
-        FEVar = lbd**2*rho**(2*horizon)*sigma**2/(1-(1-lbd)**2)
-        FEATV = (1-lbd)*FEVar
+        FEVar = ((1-lbd)*2*sigma**2+lbd**2*hstepvar(horizon,sigma,rho))/(1-(1-lbd)**2*rho**2)
+        #FEVar = lbd**2*rho**(2*horizon)*sigma**2/(1-(1-lbd)**2)
+        ## because FE_t' = (1-lbd)*rho*FE_t + (1-lbd) eps + lbd FE*
+        FEATV = (1-lbd)*rho*FEVar
+        
+        # Disg
+        Disg = rho**(2*horizon)*sigma**2
+        DisgVar = rho**(4*horizon)*sigma**4/(1-rho**(2*horizon)(1-lbd)**2)
+        DisgATV = rho**(2*horizon)(1-lbd)**2*DisgVar
[…]

### 2020-02-06 workingfolder/python/GMMEst_Dev.py
The GMM est based on unconditional mean of FE, Var and Disg can run through, although the estimates seem to be inconsistant.Need to work with the auto covariance of these as well.

@@ -34,7 +34,7 @@ from scipy.stats import bernoulli
 #import nlopt
 #from numpy import *
 
-# + {"code_folding": [0]}
+# + {"code_folding": [1]}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -61,7 +61,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [0, 2, 24]}
+# + {"code_folding": [2, 24]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 
 def PrepMom(model_moments,
@@ -77,7 +77,7 @@ def PrepMom(model_moments,
     diff: the Euclidean distance of two arrays of data and model 
     
     """
-    distance = model_moments - data_moments
+    distance = model_moments-data_moments
     diff = np.linalg.norm(distance)
     return diff
 
@@ -127,7 +127,7 @@ def Estimator2(obj_func,
     return parameter 
 
 
-# + {"code_folding": [0, 6]}
+# + {"code_folding": [6]}
 def myfunc(x, grad):
     if grad.size > 0:
         grad[0] = 0.0
@@ -146,7 +146,7 @@ def myfunc0(x,
 #Estimator2(myfunc0,
 #          para_guess = [0.1,0.2])
 
-# + {"code_folding": [1, 9, 18, 40, 56]}
+# + {"code_folding": [0, 1, 9, 18, 40, 56]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -534,7 +534,7 @@ class RationalExpectation:
         return x
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### create a RE instance 
 xx_history = AR1_simulator(rho,sigma,100)
 xx_real_time = xx_history[20:]
@@ -542,7 +542,7 @@ xx_real_time = xx_history[20:]
 RE_instance = RationalExpectation(real_time = xx_real_time,
                                   history = xx_history)
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ### simulate a realized series 
 RE_instance.SimulateRealization()
 
@@ -580,10 +580,10 @@ RE_instance.GetDataMoments(fe_moms)
 
 # + {"code_folding": []}
 ## SE expectation parameters 
[…]

### 2020-03-06 slides/ExpSlides.tex
1. first round of results with SMM. mostly work. need to clean up the difference between -dev and orginal files.

@@
 \section{Estimation}
-\begin{frame}{Minimum distance estimation}
+\begin{frame}{Simulated method of moment estimation}
 
@@
 		\item $M_{data}$: data moments
-		\item $F$ model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up to each point of the time $t$
+		\item $F$: simulated model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up till each point of the time $t$.
+		\begin{itemize}
+			\item unconditional moments, not specific to time
+			\item moments selected from average forecast, variance and autocovariance of forecasts, average diagreement, variance and autovariance of disagreement, average uncertainty, etc. 
+		\end{itemize}
 		\item  $W$: weight matrix, identity matrix for now 
 	\end{itemize}
+\end{frame}
 
+\begin{frame}{Estimation procedure and algorithm}
+	\begin{enumerate}
+		\item for each theory of expectation formation and the inflation process, start with an initial value for the parameter(s) of interest
+		\item simulate individual forecasts for a large enough ($N=200$) number of forecasters
+		\item compute the average forecast errors, disagreement and average uncertainty across all agents
+		\item compute the time-series moments of the average forecast, disagreement, and uncertainty
+		\item compute the difference between the simulated moments and the data moments 
+		\item keep searching the parameter value until reaching below a threshold of the loss
+	\end{enumerate}
+\end{frame}
+
+\begin{frame}{Two-step and joint estimation}
+	\begin{enumerate}
+		\item two-step estimation:  separately estimate inflation process parameters and then parameters of the inflation process
+		\begin{itemize}
+			\item pros: computationally lighter 
+			\item cons: potential misspecification. does not utilize the expectation data to understand inflation process per se.  
+		\end{itemize}
+		\item joint estimation: targeting both moments of realized inflation series and moments of forecasts to simultaneously estimate both the inflation process and the parameter of expectation formation
+		\begin{itemize}
+			\item pros: additional information gain from expectations data about inflation process itself
+			\item cons: more computation burden  
+		\end{itemize}
+	\end{enumerate}
 \end{frame}
@@
 
-\begin{frame}{Results: professionals and SEAR}
+\begin{frame}{Professionals and SEAR}
 	\begin{figure}[ht]
 		\label{SE_diag_SPF}
-		\begin{subfigure}[b]{0.19\textwidth}
+		\begin{subfigure}[b]{0.2\textwidth}
 			\centering
-			\caption{forecast}
+			\caption{FE}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag0.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag1.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{forecast/FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag2.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag3.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag4.png}
-		\end{subfigure}
 	\end{figure}
@@
 
-\begin{frame}{Results: households and SEAR}
+\begin{frame}{Professionals and SEAR: joint estimation}
+	\begin{figure}[ht]
+		\label{SE_diag_SPF_joint}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag3.png}
+		\end{subfigure}
+		\hfill
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and SEAR}
 	\begin{figure}[ht]
 		\label{SE_diag_SCE}
-	\begin{subfigure}[b]{0.19\textwidth}
+		\begin{subfigure}[b]{0.2\textwidth}
 			\centering
-		\caption{forecast}
+			\caption{FE}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
@@
 		\hfill
-	\begin{subfigure}[b]{0.19\textwidth}
-		\caption{FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
@@
 		\hfill
-\begin{subfigure}[b]{0.19\textwidth}
-	\caption{forecast/FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
@@
 		\hfill
-\begin{subfigure}[b]{0.19\textwidth}
-	\caption{FE/var}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
@@
 		\hfill
-\begin{subfigure}[b]{0.19\textwidth}
-	\caption{FE/var/Disg}
-	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag4.png}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and SEAR: joint estimates}
+	\begin{figure}[ht]
+		\label{SE_diag_SCE_joint}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
 		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
+		\end{subfigure}
+		\hfill
 	\end{figure}
@@
 		\centering
-		\caption{Minimum Distance Estimates of Parameters of SE}
-		\label{GMM_Est_SE_Table}
-		\begin{tabular}{lllll}
+		\caption{SMM Estimates of Parameters of SE}
+		\label{SMM_Est_SE_Table}
+	\begin{tabular}{llllllllllll}
 		\hline 
-			0        & 1    & 2   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
+		0     & 1       & 2       & 3       & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
 		\hline 
-			Forecast &      &     & 0.04                       & 1                          \\
-			FE       &      &     & 0.05                       & 0.19                       \\
-			FE       & Disg &     & 0.17                       & 0.19                       \\
-			FE       & Var  &     & 0.16                       & 0.18                       \\
-			FE       & Disg & Var & 0.53                       & 0.18                      \\
+		FEVar & FEATV   &         &         & 0.47                       & 0.36                       & 1          & 0.08         & 0.2                        & 0.59                       & 0.99       & 0.08         \\
+		FEVar & DisgATV & DisgVar &         & 0.27                       & 0.38                       & 1          & 0.11         & 0.2                        & 0.56                       & 0.98       & 0.08         \\
+		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08         \\
+		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08        \\
 		\hline 
@@
 
-\begin{frame}{Results: professionals and NIAR}
+\begin{frame}{Professionals and NIAR}
 	\begin{figure}[ht]
 		\label{NI_diag_SPF}
-		\begin{subfigure}[b]{0.19\textwidth}
+		\begin{subfigure}[b]{0.2\textwidth}
 			\centering
-			\caption{forecast}
+			\caption{FE}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag0.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag1.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{forecast/FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag3.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag4.png}
 		\end{subfigure}
@@
 
-\begin{frame}{Results: households and NIAR}
+\begin{frame}{Professionals and NIAR: joint estimates}
+	\begin{figure}[ht]
+		\label{NI_diag_SPF_joint}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag3.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and NIAR}
 	\begin{figure}[ht]
 		\label{NI_diag_SCE}
-		\begin{subfigure}[b]{0.19\textwidth}
+		\begin{subfigure}[b]{0.2\textwidth}
 			\centering
-			\caption{forecast}
+			\caption{FE}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag0.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{forecast/FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag3.png}
 		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and NIAR: joint estimates}
+	\begin{figure}[ht]
+		\label{NI_diag_SCE_joint}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag0.png}
+		\end{subfigure}
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag4.png}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag3.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\subsection{Stocastic volatility}
+
+\begin{frame}{Professionals and SESV}
+	\begin{figure}[ht]
+		\label{SESV_diag_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
 		\end{subfigure}
@@
 		\centering
-		\caption{Minimum Distance Estimates of Parameters of NI}
-		\label{GMM_Est_NI_Table}
+		\caption{SMM Estimates of Parameters of NI}
+		\label{SMM_Est_NI_Table}
 		\begin{tabular}{llllll}
-	\begin{tabular}{lllllll}
+		\begin{tabular}{lllllllllllllllll}
 			\hline 
-		0        & 1    & 2   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ \\
+			0       & 1       & 2       & 3       & 4   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
 				\hline 
-		Forecast &      &     & 39.65                     & 192.22                & 2.35                      & 0.38                  \\
-		FE       &      &     & 12.64                     & 211.14                & 1.64                      & 0                     \\
-		FE       & Disg &     & 112.37                    & 0.34                  & 512.51                    & 0.86                  \\
-		FE       & Var  &     & 1.13                      & 367.43                & 0                         & 1.28                  \\
-		FE       & Disg & Var & 1.29                      & 29.84                 & 2.74                      & 127.86                \\
+			FEVar   & FEATV   &         &         &     & 25.32                     & 16.07                 & 0.9                       & 1.09                  & 1          & 0            & 3.4                       & 15.4                  & 3.4                       & 11.29                 & 1          & 0            \\
+			DisgVar & DisgATV &         &         &     & 471301.73                 & 0.85                  & -1.74                     & -0.17                 & 0.91       & 0.42         & 168519.46                 & 1.09                  & 0.67                      & 0.58                  & 1          & 0.03         \\
+			FEVar   & FEATV   & DisgVar & DisgATV &     & 25.32                     & 16.07                 & 0.9                       & 1.09                  & 1          & 0            & 3.4                       & 15.4                  & 3.4                       & 11.29                 & 1          & 0            \\
+			FEVar   & FEATV   & DisgVar & DisgATV & Var & 9.16708E+12               & 2.37                  & 0.9                       & 1.09                  & 1          & 0            & 13.22                     & 59.96                 & 13.22                     & 59.96                 & 1          & -0.03       \\
 			\hline 
@@
 
-\subsection{Stocastic volatility}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{frame}{Results: professionals and SESV}
-	\begin{figure}[ht]
-		\label{SESV_diag_SPF}
-		\begin{subfigure}[b]{0.19\textwidth}
-			\centering
-			\caption{forecast}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{forecast/FE}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag4.png}
-		\end{subfigure}
-	\end{figure}
-\end{frame}
+\subsection{Stocastic volatility (old)}
 

### 2020-03-06 workingfolder/python/DoEstimationWithData_Dev.py

@@ -26,15 +26,15 @@ import numpy as np
 from scipy.optimize import minimize
 
 import statsmodels.api as sm
-from statsmodels.tsa.api import AR
+from statsmodels.tsa.api import AutoReg as AR
 #from UCSVEst import UCSVEst as ucsv
 # -
 
 from GMMEst_Dev import RationalExpectation as re
-from GMMEst_Dev import StickyExpectation as se
-#from GMMEst_Dev import NoisyInformation as ni
-from GMMEst import ParameterLearning as pl
-from GMMEst import AR1_simulator, ForecastPlotDiag, ForecastPlot
+from GMMEst import StickyExpectation as seb
+from GMMEst import NoisyInformation as nib
+#from GMMEst import ParameterLearning as pl
+from GMMEst_Dev import AR1_simulator, ForecastPlotDiag, ForecastPlot
 
 # + {"code_folding": []}
 ## some parameters 
@@ -96,7 +96,7 @@ real_time_inf.tail()
 # ### 3. Estimating using real-time inflation and expectation data
 #
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## exapectation data from SPF 
 PopQ=pd.read_stata('../SurveyData/InfExpQ.dta')  
 PopQ = PopQ[-PopQ.date.isnull()]
@@ -114,7 +114,7 @@ SPFCPI = PopQ[['SPFCPI_Mean','SPFCPI_FE','SPFCPI_Disg','SPFCPI_Var',
                'SPFCPI_ATV','SPFCPI_FEATV']].dropna(how='any')
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## Inflation data quarterly 
 InfQ = pd.read_stata('../OtherData/InfShocksQClean.dta')
 InfQ = InfQ[-InfQ.date.isnull()]
@@ -123,7 +123,7 @@ dateQ_str2 = dateQ2.dt.year.astype(int).astype(str) + \
              "Q" + dateQ2.dt.quarter.astype(int).astype(str)
 InfQ.index = pd.DatetimeIndex(dateQ_str2,freq='infer')
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## process parameters estimation 
 # period filter 
 start_t='1995-01-01'
[…]

### 2020-03-06 workingfolder/python/DoEstimationWithData_Dev_SV.py

@@ -31,10 +31,10 @@ import statsmodels.api as sm
 #from UCSVEst import UCSVEst as ucsv
 # -
 
-from GMMEstSV import RationalExpectationSV as re
-from GMMEstSV import StickyExpectationSV as se
-from GMMEstSV import NoisyInformationSV as ni
-from GMMEstSV import ParameterLearningSV as pl
+from GMMEstSV import RationalExpectationSV as resv
+from GMMEstSV_dev import StickyExpectationSV as sesv
+from GMMEstSV_dev import NoisyInformationSV as nisv
+#from GMMEstSV import ParameterLearningSV as plsv
 from GMMEstSV import UCSV_simulator, ForecastPlotDiag, ForecastPlot
 
 # ### 2. Preparing real-time data 
@@ -79,7 +79,9 @@ real_time_cpi.index = InfCPIMRT.index #+ pd.DateOffset(months=1)
 
 # + {"code_folding": []}
 ## turn index into yearly inflation
-real_time_index = pd.concat([real_time_cpic,real_time_cpi], join='inner', axis=1)
+real_time_index = pd.concat([real_time_cpic,real_time_cpi], 
+                            join='inner', 
+                            axis=1)
 real_time_index.columns=['RTCPI','RTCPICore']
 real_time_inf = real_time_index.pct_change(periods=12)*100
 # -
@@ -89,7 +91,7 @@ real_time_inf.tail()
 # ### 3. Estimating using real-time inflation and expectation data
 #
 
-# + {"code_folding": [6]}
+# + {"code_folding": [0, 6]}
 ## exapectation data from SPF 
 
 PopQ = pd.read_stata('../SurveyData/InfExpQ.dta')  
@@ -120,7 +122,8 @@ SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']].dropna(how='any')
 ## quarterly 
 InfQ = pd.read_stata('../OtherData/InfShocksQClean.dta')
 InfQ = InfQ[-InfQ.date.isnull()]
-dateQ2 = pd.to_datetime(InfQ['date'],format='%Y%m%d')
+dateQ2 = pd.to_datetime(InfQ['date'],
+                        format='%Y%m%d')
 dateQ_str2 = dateQ2 .dt.year.astype(int).astype(str) + \
              "Q" + dateQ2 .dt.quarter.astype(int).astype(str)
[…]

### 2020-03-06 workingfolder/python/GMMEst.py

@@ -25,18 +25,20 @@
 # ### 1. Estimation algorithms 
 
 from scipy.optimize import minimize
+from scipy.optimize import fixed_point as fp
 import numpy as np
 import matplotlib.pyplot as plt
 import statsmodels.api as sm
 from statsmodels.tsa.api import AR
 import copy as cp 
 from scipy.stats import bernoulli
-from numba import jit, njit # njit is just an alias for jit(nopython=True)
+#from numpy import *
+#from numba import jit
+import time
 
 
-# + {"code_folding": [2]}
+# + {"code_folding": [1, 26]}
 # a general-purpose estimating function of the parameter
-@jit
 def Estimator(obj_func,
               para_guess,
               method='CG',
@@ -61,10 +63,7 @@ def Estimator(obj_func,
                          options = options)['x']
     return parameter 
 
-
-# + {"code_folding": []}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
-@jit
 def PrepMom(model_moments,
             data_moments):
     """
@@ -78,19 +77,16 @@ def PrepMom(model_moments,
     diff: the Euclidean distance of two arrays of data and model 
     
     """
-    diff = np.linalg.norm((model_moments - data_moments)/data_moments)
+    distance = model_moments - data_moments
+    diff = np.linalg.norm(distance)
     return diff
 
 
-# + {"code_folding": [0, 1, 5, 9, 18, 41]}
+
+# + {"code_folding": [13, 4]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
-    return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
-
-np.random.seed(12345)
-def hstepfe(h,sigma,rho):
-    return sum([rho**i*(np.random.randn(1)*sigma)*np.random.randn(h)[i] for i in range(h)])
-## This is not correct. 
+    return np.sum([ rho**(2*i)*sigma**2 for i in range(h)])
 
 def ForecastPlot(test):
     m_ct = len(test)
@@ -100,7 +96,7 @@ def ForecastPlot(test):
         plt.plot(test[val],label=val)
         plt.legend(loc=1)
     return x
-        
+     
 def ForecastPlotDiag(test,
                      data,
                      legends=['model','data'],
@@ -110,16 +106,16 @@ def ForecastPlotDiag(test,
     if diff_scale == False:
         for i,val in enumerate(test):
[…]

### 2020-03-06 workingfolder/python/GMMEstSV.py

@@ -236,7 +236,7 @@ import copy as cp
 from scipy.stats import bernoulli
 
 
-# + {"code_folding": [1]}
+# + {"code_folding": [1, 26]}
 # a general-purpose estimating function of the parameter
 def Estimator(obj_func,
               para_guess,
@@ -262,8 +262,6 @@ def Estimator(obj_func,
                          options = options)['x']
     return parameter 
 
-
-# + {"code_folding": [1]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 def PrepMom(model_moments,
             data_moments):
@@ -322,11 +320,16 @@ def ForecastPlotDiag(test,
         plt.plot(np.array(data[val]),label=legends[1] +': '+ val)
         plt.legend(loc=1)
     return x
-        
+     
 ### UC-SV simulator 
 def UCSV_simulator(gamma,
                    nobs,
-                   eta0 = 0):
+                   eta0 = 0,
+                   seed = False):
+    if seed == True:
+        np.random.seed(12344)
+    else:
+        pass
     svols_eta_shock = np.random.randn(nobs+1)*gamma
     svols_eps_shock = np.random.randn(nobs+1)*gamma
     
@@ -365,7 +368,7 @@ process_para = {'gamma':gamma_fake,
                 'eta0':eta0_fake}
 
 
-# + {"code_folding": [0, 110]}
+# + {"code_folding": [0, 2, 20, 38, 70, 97, 110, 115]}
 ## Rational Expectation (RE) class for UCSV model 
 class RationalExpectationSV:
     def __init__(self,
@@ -495,62 +498,14 @@ class RationalExpectationSV:
             plt.legend(loc=1)
 
 
-# + {"code_folding": [0]}
-### create a RE instance 
-ucsv_fake = UCSV_simulator(gamma_fake,
-                           eta0 = eta0_fake,
-                           nobs = 200) 
-n_burn = 30
-# the permanent component
-
-xx_history = ucsv_fake[0]
-xx_real_time = xx_history[n_burn:]
-
-
-xx_pc_history = ucsv_fake[1]
-xx_pc_real_time = xx_pc_history[n_burn:]
-
-# the volatility
-vol_history = np.array([ucsv_fake[2],ucsv_fake[3]])
-vol_real_time = vol_history[:,n_burn:]
-
-xx_real_time_dct = {'eta':xx_pc_real_time,
-                   'vols':vol_real_time,
[…]

### 2020-03-06 workingfolder/python/GMMEstSV_dev.py

@@ -1,0 +1,1786 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:light
+#     text_representation:
+#       extension: .py
+#       format_name: light
+#       format_version: '1.4'
+#       jupytext_version: 1.2.3
+#   kernelspec:
+#     display_name: Python 3
+#     language: python
+#     name: python3
+# ---
+
+# ## GMM Estimation of Model Parameters of Expectation Formation (Stochastic Volatility Process)
+#
+# - This notebook includes functions that estimate the parameter of rigidity for different models
+# - It allows for flexible choices of moments to be used, forecast error, disagreement, and uncertainty, etc. 
+# - It includes 
+#   - A general function that implements the estimation using the minimum distance algorithm. 
+#   - Model-specific functions that take real-time data and process parameters as inputs and produces forecasts and moments as outputs. It is model-specific because different models of expectation formation bring about different forecasts. 
+#   - Auxiliary functions that compute the moments as well as the difference of data and model prediction, which will be used as inputs for GMM estimator. 
+
+# ## 1. A process of time-varying volatility 
+#
+# Assume that the inflation follows a process of unobserved component model with stochastical volatility. (UC-SV model by Watson and Stock. 2007)
+#
+# \begin{equation}
+# \begin{split}
+# & y_t = \theta_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
+# & \theta_t = \theta_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
+# & \log\sigma^2_{\eta,t} = \log\sigma^2_{\eta,t-1} + \mu_{\eta,t} \\
+# & \log\sigma^2_{\epsilon,t} = \log\sigma^2_{\epsilon,t-1} + \mu_{\epsilon,t} 
+# \end{split}
+# \end{equation}
+#
[…]

### 2020-03-06 workingfolder/python/GMMEst_Dev-jit.py

@@ -1,0 +1,2833 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:light
+#     text_representation:
+#       extension: .py
+#       format_name: light
+#       format_version: '1.4'
+#       jupytext_version: 1.2.3
+#   kernelspec:
+#     display_name: Python 3
+#     language: python
+#     name: python3
+# ---
+
+# ## GMM/SMM Estimation of Model Parameters of Expectation Formation
+#
+# - This notebook includes functions that estimate the parameter of rigidity for different models
+# - It allows for flexible choices of moments to be used, forecast error, disagreement, and uncertainty, etc. 
+# - It includes 
+#   - A general function that implements the estimation using the minimum distance algorithm. 
+#   - Model-specific functions that take real-time data and process parameters as inputs and produces forecasts and moments as outputs. It is model-specific because different models of expectation formation bring about different forecasts. 
+#   - Auxiliary functions that compute the moments as well as the difference of data and model prediction, which will be used as inputs for GMM estimator. 
+
+# ### 1. Estimation algorithms 
+
+from scipy.optimize import minimize
+from scipy.optimize import fixed_point as fp
+import numpy as np
+import matplotlib.pyplot as plt
+import statsmodels.api as sm
+from statsmodels.tsa.api import AR
+import copy as cp 
+from scipy.stats import bernoulli
+#import nlopt
+#from numpy import *
+from numba import jit 
+from numba import njit
+import time 
+from numba import jitclass          # import the decorator
+
+from numba import int32, float32
+
+
+# + {"code_folding": [1]}
+# a general-purpose estimating function of the parameter
+def Estimator(obj_func,
+              para_guess,
+              method='CG',
+              bounds = None,
+              options = {'disp': True}):
+    """
+    Inputs
+    ------
+    - moments: a function of the rigidity model parameter  
+    - method: method of optimization, i.e. 
+         -  'L-BFGS-B', bounds=((1e-10, None), (1e-10, None))
+    
+    Outputs
+    -------
+    - parameter: an array of estimated parameter
+    """
+    
+    parameter = minimize(obj_func,
+                         x0 = para_guess,
+                         method = method,
+                         bounds = bounds,
+                         options = options)['x']
+    return parameter 
+
+
+# + {"code_folding": [2, 23]}
[…]

### 2020-03-06 workingfolder/python/GMMEst_Dev.py

@@ -34,6 +34,9 @@ import copy as cp
 from scipy.stats import bernoulli
 #import nlopt
 #from numpy import *
+from numba import jit
+import time
+
 
 # + {"code_folding": [1]}
 # a general-purpose estimating function of the parameter
@@ -62,7 +65,7 @@ def Estimator(obj_func,
     return parameter 
 
 
-# + {"code_folding": [2, 23]}
+# + {"code_folding": [0, 2, 23]}
 # a function that prepares moment conditions. So far the loss being simply the norm of the difference
 
 def PrepMom(model_moments,
@@ -107,7 +110,7 @@ def PrepMomWM(model_moments,
 
 
 
-# + {"code_folding": [1, 9, 18, 40, 56]}
+# + {"code_folding": [0, 1, 9, 18, 40, 56]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return sum([ rho**(2*i)*sigma**2 for i in range(h)] )
@@ -495,35 +498,35 @@ class RationalExpectation:
         return x
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### create a RE instance 
-xx_history = AR1_simulator(rho,sigma,100)
-xx_real_time = xx_history[20:]
+#xx_history = AR1_simulator(rho,sigma,100)
+#xx_real_time = xx_history[20:]
 
-RE_instance = RationalExpectation(real_time = xx_real_time,
-                                  history = xx_history)
+#RE_instance = RationalExpectation(real_time = xx_real_time,
+#                                  history = xx_history)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ### simulate a realized series 
-RE_instance.SimulateRealization()
+#RE_instance.SimulateRealization()
 
 ### forecster
-fe_moms = RE_instance.Forecaster()
+#fe_moms = RE_instance.Forecaster()
 #re_plot = RE_instance.ForecastPlot()
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## estimate rational expectation model 
-RE_instance.GetDataMoments(fe_moms)
+#RE_instance.GetDataMoments(fe_moms)
 #RE_instance.moments = ['Forecast','Disg']
 
-#RE_instance.ParaEstimate(para_guess = np.array([0.5,0.3]),
+# RE_instance.ParaEstimate(para_guess = np.array([0.5,0.3]),
 #                         method = 'L-BFGS-B',
[…]

### 2020-03-31 slides/ExpSlides.tex
1.slides draft before discussion with Jonanthan. need to summarize the results and rewrote the conclusion.

@@
 	\begin{itemize}
-		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni} \} \times \{ar, sv\}$
+		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni},{de},{seni} \} \times \{ar, sv\}$
 		\item  $\Gamma$: constraints for the parameter. 
@@
 
+\begin{frame}{Scoring card for a theory of expectation formation}
+	To look if the parameter and fitness is relatively robust to 
+	\begin{enumerate}
+		\item use of different moments in estimation
+		\item alternative assumption about underlying process 
+		\item two-step estimation or joint-estimation 
+		\item relatively fit with professionals and households  
+	\end{enumerate}
+\end{frame}
+
 \subsection{AR(1)}
+
+%%%%%%%%%%%%%%%%%%%
+\subsubsection{SE}
+
+\begin{frame}{SE parameter estimate}
+	\begin{table}
+		\centering
+		\caption{SMM Estimates of SE}
+		\label{SMM_Est_SE_Table}
+		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
+	\begin{tabular}{lllllllllllll}
+		\hline 
+		0     & 1       & 2       & 3       &     & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
+		\hline 
+		FEVar & FEATV   &         &         &     & 0.47                       & 0.36                       & 1          & 0.08         & 0.2                        & 0.5                        & 0.84       & 0.25         \\
+		FEVar & DisgATV & DisgVar &         &     & 0.47                       & 0.38                       & 1          & 0.1          & 0.21                       & 0.54                       & 0.92       & 0.18         \\
+		FEVar & FEATV   & DisgVar & DisgATV & Var & 0.47                       & 0.36                       & 1          & 0.08         & 0.21                       & 0.5                        & 0.84       & 0.25       \\
+		\hline 
+	\end{tabular}
+	}
+	\end{table}
+	\begin{itemize}
+		\item $\lambda$: update rate in SE
+	\end{itemize}
+\end{frame}
 
@@
 		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag3.png}
-		\end{subfigure}
-		\hfill
 	\end{figure}
@@
 		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag3.png}
-		\end{subfigure}
-		\hfill
 	\end{figure}
@@
 	\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
-		\end{subfigure}
-		\hfill
 	\end{figure}
@@
 		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{DE}
+
+\begin{frame}{DE parameter estimate}
+	\begin{table}
+		\centering
+		\caption{SMM Estimates of DE}
+		\label{SMM_Est_DE_Table}
+		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
+		\begin{tabular}{lllllllllllllllllll}
+			\hline 
+			0  & 1     & 2     & 3    & 4       & 5       & 6   & DE: $\theta_{SPF}$ & DE: $\sigma_{\theta,SPF}$ & DE: $\theta_{SPF}$ & DE: $\sigma_{\theta,SPF}$ & DE: $\rho$ & DE: $\sigma$ & DE: $\theta_{SCE}$ & DE: $\sigma_{\theta,SCE}$ & DE: $\theta_{SCE}$ & DE: $\sigma_{\theta_SCE}$ & DE: $\rho$ & DE: $\sigma$ \\
+			\hline 
+			FE & FEVar & FEATV &      &         &         &     & -0.23              & 0.22                      & NA                 & NA                        & NA         & NA           & 9.35               & 10.65                     & 0.82               & 0.85                      & 1          & 0            \\
+			FE & FEVar & FEATV & Disg & DisgVar & DisgATV &     & -0.26              & 1.41                      & -0.14              & 1.44                      & 0.99       & 0.16         & 8.2                & 9.52                      & 4.79               & 4.59                      & 0.58       & 0.55         \\
+			FE & FEVar & FEATV & Disg & DisgVar & DisgATV & Var & -0.24              & 1.43                      & -0.17              & 1.44                      & 0.99       & 0.16         & 4.78               & 3.01                      & NA                 & NA                        & NA         & NA          \\
+			\hline 
+		\end{tabular}
+		}
+	\end{table}
+	\begin{itemize}
+	\item $\theta$: representativeness parameter, $\theta>0$ according to DE. 
+	\item $\sigma_\theta$: dispersion of representativeness across population
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Professionals and DEAR}
+	\begin{figure}[ht]
+		\label{DE_diag_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Professionals and DEAR: joint estimate}
+	\begin{figure}[ht]
+		\label{DE_diag_joint_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_joint_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and DEAR}
+	\begin{figure}[ht]
+		\label{DE_diag_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_diag1.png}
+		\end{subfigure}
 		\hfill
@@
 			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_diag2.png}
 		\end{subfigure}
-		\hfill
 	\end{figure}
@@
 
-\begin{frame}{SE parameter estimate}
+\begin{frame}{Households and DEAR: joint estimates}
+	\begin{figure}[ht]
+		\label{DE_diag_joint_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_joint_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%
+\subsubsection{NI}
+
+\begin{frame}{NIAR parameters}
 	\begin{table}
 		\centering
-		\caption{SMM Estimates of Parameters of SE}
-		\label{SMM_Est_SE_Table}
-	\begin{tabular}{llllllllllll}
+		\caption{SMM Estimates of NI}
+		\label{SMM_Est_NI_Table}
+		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
+			\begin{tabular}{lllllllllllllllll}
 				\hline 
-		0     & 1       & 2       & 3       & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
+				0     & 1     & 2       & 3       & 4   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
 				\hline 
-		FEVar & FEATV   &         &         & 0.47                       & 0.36                       & 1          & 0.08         & 0.2                        & 0.59                       & 0.99       & 0.08         \\
-		FEVar & DisgATV & DisgVar &         & 0.27                       & 0.38                       & 1          & 0.11         & 0.2                        & 0.56                       & 0.98       & 0.08         \\
-		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08         \\
-		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08        \\
+				FEVar & FEATV &         &         &     & 0.09                      & 2.77                  & 0.093                     & 1.408                 & 0.911      & 0.422        & 3.4                       & 15.4                  & 3.397                     & 15.395                & 0.997      & 0.027        \\
+				FEVar & FEATV & DisgVar & DisgATV &     & 0.09                      & 2.77                  & 0.093                     & 1.408                 & 0.911      & 0.422        & 3.4                       & 15.4                  & 3.397                     & 15.395                & 0.997      & 0.027        \\
+				FEVar & FEATV & DisgVar & DisgATV & Var & 0.14                      & 3.85                  & 0.133                     & 1.359                 & 0.911      & 0.422        & 4.9                       & 22.4                  & 4.860                     & 22.367                & 0.997      & 0.027       \\
 				\hline 
 			\end{tabular}
+	}
 	\end{table}	
 	\begin{itemize}
-	\item $\lambda$: update rate in SE
+		\item $\sigma_{pb}$: noisiness of public signals in NI
+		\item $\sigma_{pr}$: noisiness of private signals in NI
 	\end{itemize}
@@
 		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg}
+			\caption{FE/Disg/Var}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag3.png}
 		\end{subfigure}
@@
 		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag3.png}
-		\end{subfigure}
 	\end{figure}
@@
 		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{Disg}
+			\caption{FE/Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
@@
 		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg}
+			\caption{FE/Disg/Var}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag3.png}
 		\end{subfigure}
@@
 		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{Disg}
+			\caption{FE/Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag1.png}
@@
 		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%
+\subsubsection{Hybird of NI and SE}
+
+\begin{frame}{SENIAR parameters}
+	\begin{table}
+		\centering
+		\caption{SMM Estimates of SENI}
+		\label{SMM_Est_SENI_Table}
+		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
+		\begin{tabular}{lllllllllllll}
+			\hline 
+			0  & 1     & 2     & 3    & 4       & 5       & 6   & SENI: $\lambda$ & SENI: $\sigma_{pb,SPF}$ & SENI: $\sigma_{pr,SPF}$ & SENI: $\lambda$ & SENI: $\sigma_{pb,SCE}$ & SENI: $\sigma_{pr,SCE}$ \\
+			\hline 
+			FE & FEVar & FEATV &      &         &         &     & 0.64            & 0.16                    & 0                       & 0.19            & 0.2                     & 0.21                    \\
+			FE & FEVar & FEATV & Disg & DisgVar & DisgATV &     & 0.62            & 4.77                    & 0.17                    & 0.25            & 0.1                     & 0.35                    \\
+			FE & FEVar & FEATV & Disg & DisgVar & DisgATV & Var & 0.62            & 13.7                    & 0.17                   & NA              & NA                      & NA                     \\
+			\hline 
+		\end{tabular}
+		}
+	\end{table}	
+	\begin{itemize}
+		\item $\sigma_{pb}$: noisiness of public signals in NI
+		\item $\sigma_{pr}$: noisiness of private signals in NI
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Professionals and SENIAR}
+	\begin{figure}[ht]
+		\label{SENI_diag_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_seni_est_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
 			\caption{FE/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag2.png}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_seni_est_diag1.png}
 		\end{subfigure}
@@
 			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag3.png}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_seni_est_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and SENIAR}
+	\begin{figure}[ht]
+		\label{SENI_diag_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_seni_est_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_seni_est_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_seni_est_diag2.png}
 		\end{subfigure}
@@
 \subsection{Stocastic volatility}
+
+\subsubsection{SE}
+
+\begin{frame}{SESV parameters}
+	\begin{table}
+		\centering
+		\caption{SMM Estimates of Parameters of SESV}
+		\label{SMM_Est_SE_SV_Table}
+		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
+\begin{tabular}{llllllllll}
+	\hline 
+	0       & 1       & 2       & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\gamma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\gamma$ \\
+	\hline 
+	DisgATV & Var     &         &     & 0.3                        & 0.46                       & 2.52         & 0.09                       & 0.09                       & 0.7          \\
+	FEATV   & DisgVar & DisgATV &     & 0.3                        & 0.46                       & 2.53         & 0.07                       & 0.07                       & 0.26         \\
+	FEATV   & DisgVar & DisgATV & Var & 0.3                        & 0.46                       & 1.26         & 0.07                       & 0.07                       & 0.26        \\
+	\hline 
+\end{tabular}
+		}
+		\begin{itemize}
+			\item $\lambda$: update rate in SE
+				\item $\gamma$: size of the innovation to volatility	
+		\end{itemize}
+	\end{table}	
+\end{frame}
 
@@
 		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Professionals and SESV: joint estimates}
+	\begin{figure}[ht]
+		\label{SESV_diag_joint_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_joint_diag0.png}
+		\end{subfigure}
 		\hfill
 		\begin{subfigure}[b]{0.2\textwidth}
-			\caption{FE/Disg/Var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
+			\caption{Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+	\begin{subfigure}[b]{0.2\textwidth}
+		\caption{Disg}
+		\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_joint_diag2.png}
 	\end{subfigure}
@@
 
-\begin{frame}{NIAR parameters}
-	\begin{table}
-		\centering
-		\caption{SMM Estimates of Parameters of NI}
-		\label{SMM_Est_NI_Table}
-		\begin{tabular}{llllll}
-		\begin{tabular}{lllllllllllllllll}
-			\hline 
-			0       & 1       & 2       & 3       & 4   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
-				\hline 
-			FEVar   & FEATV   &         &         &     & 25.32                     & 16.07                 & 0.9                       & 1.09                  & 1          & 0            & 3.4                       & 15.4                  & 3.4                       & 11.29                 & 1          & 0            \\
-			DisgVar & DisgATV &         &         &     & 471301.73                 & 0.85                  & -1.74                     & -0.17                 & 0.91       & 0.42         & 168519.46                 & 1.09                  & 0.67                      & 0.58                  & 1          & 0.03         \\
-			FEVar   & FEATV   & DisgVar & DisgATV &     & 25.32                     & 16.07                 & 0.9                       & 1.09                  & 1          & 0            & 3.4                       & 15.4                  & 3.4                       & 11.29                 & 1          & 0            \\
-			FEVar   & FEATV   & DisgVar & DisgATV & Var & 9.16708E+12               & 2.37                  & 0.9                       & 1.09                  & 1          & 0            & 13.22                     & 59.96                 & 13.22                     & 59.96                 & 1          & -0.03       \\
-			\hline 
-		\end{tabular}
-		\end{tabular}
-	\end{table}	
-	\begin{itemize}
-		\item $\sigma_{pb}$: noisiness of public signals in NI
-		\item $\sigma_{pr}$: noisiness of private signals in Ni 
-	\end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Stocastic volatility (old)}
-
-\begin{frame}{Results: households and SESV}
+\begin{frame}{Households and SESV}
 	\begin{figure}[ht]
 		\label{SESV_diag_SCE}
-		\begin{subfigure}[b]{0.19\textwidth}
+		\begin{subfigure}[b]{0.2\textwidth}
 			\centering
-			\caption{forecast}
+			\caption{Disg/Var}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag0.png}
@@
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
 			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag1.png}
 		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{forecast/FE}
+	\hfill	\begin{subfigure}[b]{0.2\textwidth}
+		\caption{FE/Disg/Var}
 		\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag2.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag3.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_diag4.png}
 	\end{subfigure}
@@
 
-\begin{frame}{SESV parameters}
+\begin{frame}{Households and SESV: joint estimates}
+	\begin{figure}[ht]
+		\label{SESV_diag_joint_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_sv_joint_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{DE}
+
+\begin{frame}{DESV parameters}
 	\begin{table}
 		\centering
-		\caption{Minimum Distance Estimates of Parameters of SESV}
-		\label{GMM_Est_SE_SV_Table}
-	\begin{tabular}{lllll}
+		\caption{SMM Estimates of Parameters of DESV}
+		\label{SMM_Est_DE_SV_Table}
+		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
+			\begin{tabular}{lllllllllllllll}
 				\hline 
-		0        & 1    & 2   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
+				0     & 1     & 2       & 3       & 4   & DE: $\theta$ & $\sigma_\theta$ & DE: $\theta$ & $\sigma_\theta$ & $\gamma$ & DE: $\theta$ & $\sigma_\theta$ & DE: $\theta$ & $\sigma_\theta$ & $\gamma$ \\
 				\hline 
-		Forecast &      &     & 0.1                        & 0.02                       \\
-		FE       &      &     & 0.12                       & 1                          \\
-		FE       & Disg &     & 0.14                       & 1                          \\
-		FE       & Var  &     & 0.12                       & 1                          \\
-		FE       & Disg & Var & 0.14                       & 1                         \\
+				FE    & FEVar & FEATV   &         &     & -0.44        & 0.36            & -0.43        & 1.03            & 0.13     & 7.81         & 4.39            & 7.81         & 2.99            & 0.7      \\
+				FEVar & FEATV & DisgVar & DisgATV &     & -0.44        & 0.27            & -0.44        & 0.27           & 0.3      & 7.64         & 6.46            & 7.64         & 6.46            & 0.7      \\
+				FEVar & FEATV & DisgVar & DisgATV & Var & -0.43        & 0.26            & -0.43        & 0.26            & 0.14     & 1.03         & 0               & 1.03         & 0               & 0.2     \\
 				\hline 
 			\end{tabular}
+		}
 		\begin{itemize}
-	\item $\lambda$: update rate in SE
+
+			\item $\theta$: representativeness parameter
+			\item $\sigma_\theta$: dispersion of representativeness across population
+			\item $\gamma$: size of the innovation to volatility	
 		\end{itemize}
@@
 
-\begin{frame}{Results: professionals and NISV}
+\begin{frame}{Professionals and DESV}
 	\begin{figure}[ht]
-		\label{NISV_diag_SPF}
-		\begin{subfigure}[b]{0.19\textwidth}
+		\label{DESV_diag_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
 			\centering
-			\caption{forecast}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag0.png}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_sv_diag0.png}
 		\end{subfigure}
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag1.png}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_sv_diag1.png}
 		\end{subfigure}
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{forecast/FE}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag2.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag3.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag4.png}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_sv_diag2.png}
 		\end{subfigure}
@@
 
-\begin{frame}{Results: households and NISV}
+\begin{frame}{Professionals and DESV: joint estimates}
 	\begin{figure}[ht]
-		\label{NISV_diag_SCE}
-		\begin{subfigure}[b]{0.19\textwidth}
+		\label{DESV_diag_joint_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
 			\centering
-			\caption{forecast}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag0.png}
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_sv_joint_diag0.png}
 		\end{subfigure}
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag1.png}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_sv_joint_diag1.png}
 		\end{subfigure}
 		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{forecast/FE}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag2.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag3.png}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.19\textwidth}
-			\caption{FE/var/Disg}
-			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag4.png}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_de_est_sv_joint_diag2.png}
 		\end{subfigure}
@@
 
+%%%%%%%%%%%
+
+\begin{frame}{Households and DESV}
+	\begin{figure}[ht]
+		\label{DESV_diag_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_sv_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_sv_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and DESV: joint estimates}
+	\begin{figure}[ht]
+		\label{DESV_diag_joint_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_sv_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_sv_joint_diag1.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_de_est_sv_joint_diag2.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{NI}
+
 \begin{frame}{NISV parameters}
@@
 		\centering
-		\caption{Minimum Distance Estimates of Parameters of NISV}
-		\label{GMM_Est_NI_SV_Table}
-	\begin{tabular}{lllllll}
+		\caption{SMM Estimates of Parameters of NISV}
+		\label{SMM_Est_NI_SV_Table}
+		\adjustbox{max height=0.5\textheight, max width=\textwidth}{ 
+			\begin{tabular}{llllllllllll}
 				\hline 
-		0        & 1    & 2   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ \\
+				0       & 1       & 2       & 3       & 4   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $\gamma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ \\
 				\hline 
-		Forecast &      &     & 16.9                      & 21.44                 & 5.21                      & 6.05                  \\
-		FE       &      &     & 67.05                     & 146.8                 & 4.4                       & 4.88                  \\
-		FE       & Disg &     & 62.6                      & 0.57                  & 7.23                      & 3.54                  \\
-		FE       & Var  &     & 787.17                    & 3257.84               & 97.72                     & 95.73                 \\
-		FE       & Disg & Var & 126.68                    & 0.57                  & 215.54                    & 3.64                 \\
+				FEVar   & FEATV   & Var     &         &     & 2.35                      & 2                     & 2.04                      & 23.01                 & 2.53     & 2.00014E+14               & 3.63                  \\
+				FEVar   & FEATV   & DisgVar & DisgATV & Var & 3.33                      & 1.71                  & 2.04                      & 22.96                 & 2.53     & 1.09884E+13               & 3.63            \\
 				\hline      
 			\end{tabular}
-	\end{table}	
+		}
 		\begin{itemize}
@@
 			\item $\sigma_{pr}$: noisiness of private signals in NI
+			\item $\gamma$: size of the innovation to volatility	
 		\end{itemize}
+	\end{table}	
 \end{frame}
 
-\begin{frame}{Ongoing work}
-	\begin{itemize}
-		\item I have been matching time-specific conditional moments with data. I will match unconditional moments
-		\item jointly estimate process parameters and expectation formation parameters
-		\item statistical tests of the fitness,  i.e. Sargan–Hansen test in the GMM
-	\end{itemize}	
+\begin{frame}{Professionals and NISV}
+	\begin{figure}[ht]
+		\label{NISV_diag_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_diag3.png}
+		\end{subfigure}
+	\end{figure}
 \end{frame}
+
+\begin{frame}{Professionals and NISV: joint estimates}
+	\begin{figure}[ht]
+		\label{NISV_diag_joint_SPF}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_sv_joint_diag3.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and NISV}
+	\begin{figure}[ht]
+		\label{NISV_diag_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_diag3.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Households and NISV: joint estimates}
+	\begin{figure}[ht]
+		\label{NISV_diag_joint_SCE}
+		\begin{subfigure}[b]{0.2\textwidth}
+			\centering
+			\caption{FE/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_joint_diag0.png}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.2\textwidth}
+			\caption{FE/Disg/Var}
+			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_sv_joint_diag3.png}
+		\end{subfigure}
+	\end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-03-31 workingfolder/python/DoEstimationWithData_Dev.py

@@ -33,7 +33,9 @@ from statsmodels.tsa.api import AutoReg as AR
 from GMMEst_Dev import RationalExpectation as re
 from GMMEst import StickyExpectation as seb
 from GMMEst import NoisyInformation as nib
-#from GMMEst import ParameterLearning as pl
+from GMMEst import DiagnosticExpectation as de
+from GMMEst import StickyNoisyHybrid as senib
+from GMMEst import ParameterLearning as pl
 from GMMEst_Dev import AR1_simulator, ForecastPlotDiag, ForecastPlot
 
 # + {"code_folding": []}
@@ -283,6 +285,29 @@ data_moms_dctM = data_moms_dct_SCE
 
 process_paraM_est = {'rho':rhoM_est,
                     'sigma':sigmaM_est}
+
+
+# +
+## function of moving average 
+def mvavg(array,
+          window = 3):
+    array_av = np.array([ (array[i]+array[i+1]+array[i+2]/3) for i in range(len(array)-3)])
+    return array_av
+
+## a tweek using 3-month average 
+data_moms_dct_SPF_mv = {}
+data_moms_dct_SCE_mv = {}
+
+for key in data_moms_dct_SPF.keys():
+    data_moms_dct_SPF_mv[key] = mvavg(data_moms_dct_SPF[key],window = 2)
+    
+for key in data_moms_dct_SCE.keys():
+    data_moms_dct_SCE_mv[key] = mvavg(data_moms_dct_SCE[key],window = 3)
+
+## plot
+
+spf_data_mv = ForecastPlot(data_moms_dct_SPF_mv)
+sce_data_mv = ForecastPlot(data_moms_dct_SCE_mv)
 # -
 
 # ### Rational Expectation 
@@ -312,11 +337,11 @@ process_paraM_est = {'rho':rhoM_est,
 # + {"code_folding": [0]}
 ## SE loop SMM estimation over different choieces of moments for SPF
 
-moments_choices_short = [['FE','FEVar','FEATV']]
-moments_choices = [['FEVar','FEATV'],
-                   ['DisgVar','DisgATV'],
-                   ['FEVar','FEATV','DisgVar','DisgATV'],
-                   ['FEVar','FEATV','DisgVar','DisgATV','Var']
+moments_choices_short = [ ['FE','FEVar','FEATV','DisgVar','DisgATV']]
+moments_choices = [['FE','FEVar','FEATV'],
+                   ['Disg','DisgVar','DisgATV'],
[…]

### 2020-03-31 workingfolder/python/DoEstimationWithData_Dev_SV.py

@@ -25,15 +25,17 @@ from pandas.plotting import register_matplotlib_converters
 import numpy as np
 
 from scipy.optimize import minimize
-
 import statsmodels.api as sm
+
 #from statsmodels.tsa.api import AR
 #from UCSVEst import UCSVEst as ucsv
 # -
 
 from GMMEstSV import RationalExpectationSV as resv
-from GMMEstSV_dev import StickyExpectationSV as sesv
-from GMMEstSV_dev import NoisyInformationSV as nisv
+from GMMEstSV import StickyExpectationSV as sesv
+from GMMEstSV import NoisyInformationSV as nisv
+from GMMEstSV import DiagnosticExpectationSV as desvb
+from GMMEstSV import StickyNoisyHybridSV as senisv
 #from GMMEstSV import ParameterLearningSV as plsv
 from GMMEstSV import UCSV_simulator, ForecastPlotDiag, ForecastPlot
 
@@ -264,7 +266,7 @@ plt.plot(history_vol_epsQ,'--',
          label = r'$\widehat\sigma^2_{\epsilon}$')
 plt.legend(loc = 0)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## inflation and the permanent component quarterly 
 
 #plt.plot(np.array(CPICQ),
@@ -300,7 +302,7 @@ plt.plot(history_vol_etaM,'r-.',label=r'$\widehat\sigma^2_{\eta}$')
 plt.plot(history_vol_epsM,'--',label=r'$\widehat\sigma^2_{\epsilon}$')
 plt.legend(loc = 0)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## inflation and the permanent component monthly 
 
 plt.plot(np.array(historyM['RTCPI']),
@@ -322,19 +324,47 @@ data_moms_dct_SPF = dict(exp_data_SPF)
 exp_data_SCE = SCE_est[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var']]
 exp_data_SCE.columns = ['Forecast','FE','Disg','Var']
 data_moms_dct_SCE = dict(exp_data_SCE)
+
+
+# +
+## spf 
+#spf_data = ForecastPlot(data_moms_dct_SPF)
+## sce
+#sce_data = ForecastPlot(data_moms_dct_SCE)
+
+# +
+## function of moving average 
+def mvavg(array,
+          window = 3):
[…]

### 2020-03-31 workingfolder/python/GMMEst.py

@@ -83,7 +83,7 @@ def PrepMom(model_moments,
 
 
 
-# + {"code_folding": [13, 4]}
+# + {"code_folding": [0, 4, 13]}
 ## auxiliary functions 
 def hstepvar(h,sigma,rho):
     return np.sum([ rho**(2*i)*sigma**2 for i in range(h)])
@@ -129,7 +129,7 @@ def AR1_simulator(rho,sigma,nobs):
     return xxx[1:]
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## some process parameters 
 rho = 0.95
 sigma = 0.1
@@ -143,7 +143,7 @@ process_para = {'rho':rho,
 ## SE expectation parameters 
 SE_para_default = {'lambda':0.4}
 
-# + {"code_folding": [0, 3, 4, 30, 43, 59, 111, 145, 181, 250, 320, 349, 378, 388, 577, 606, 631, 645, 672, 684, 696, 711, 726, 738, 760, 814, 830]}
+# + {"code_folding": [0, 4, 30, 43, 59, 110, 144, 180, 249, 319, 348, 377, 387, 395, 418, 441, 468, 506, 544, 576, 605, 630, 644, 671, 683, 695, 710, 725, 737, 813, 829]}
 ## Sticky Expectation(SE) class 
 
 
@@ -249,7 +249,6 @@ class StickyExpectation:
                            "DisgATV":DisgATV,
                            "Var":Var}
         return self.GMMMoments
-    
     
 #################################
 ######## specific to new moments
@@ -930,7 +929,7 @@ class StickyExpectation:
         ## plot 
         new_instance = cp.deepcopy(self)
         new_instance.exp_para = exp_para_est_dct
-        self.forecast_moments_est = new_instance.Forecaster()
+        self.forecast_moments_est = new_instance.ForecasterbySim()
         plt.style.use('ggplot')
         if all_moms == False:
             moments_to_plot = self.moments
@@ -999,7 +998,7 @@ class StickyExpectation:
         self.wm_boot = np.linalg.inv(self.vcv_boot)               
 
 
-# + {"code_folding": [3, 32, 45, 59, 207, 222, 234, 286, 319, 356, 389, 401, 422, 455, 484, 495, 507, 522, 550, 587, 595, 610, 626, 657, 670, 682, 694, 713, 774, 791]}
[…]

### 2020-03-31 workingfolder/python/GMMEstSV.py

@@ -357,7 +357,7 @@ def UCSV_simulator(gamma,
     return xxx,eta,svols_eta,svols_eps
 
 
-# + {"code_folding": []}
+# + {"code_folding": [0]}
 ## some process parameters 
 
 eta0_fake = 0
@@ -503,9 +503,8 @@ class RationalExpectationSV:
 SE_para_default = {'lambda':0.3}
 
 
-# + {"code_folding": [0, 3, 24, 47, 77, 125, 189, 210, 235, 261, 283, 295, 311, 323, 325, 330, 347, 360]}
-## Sticky Expectation(SE) class of UCSV model 
-
+# + {"code_folding": [0, 2, 19, 23, 45, 79, 115, 163, 228, 249, 274, 303, 337, 359, 371, 387, 404, 416, 423]}
+## Sticky Expectation(SE) class 
 class StickyExpectationSV:
     def __init__(self,
                  real_time,
@@ -513,7 +512,7 @@ class StickyExpectationSV:
                  horizon = 1,
                  process_para = process_para,
                  exp_para = SE_para_default,
-                 moments = ['FE','Disg','Var']):
+                 moments = ['Forecast','Disg','Var']):
         self.history = history
         self.real_time = real_time
         self.n = len(real_time['eta'])
@@ -530,7 +529,6 @@ class StickyExpectationSV:
     
     def SimulateRealization(self):
         n = len(self.real_time['eta'])
-        
         ## information set 
         eta_now = self.real_time['eta']
         vol_now = self.real_time['vols']
@@ -547,7 +545,7 @@ class StickyExpectationSV:
                                      )
         self.realized = realized
         
-################################
+#################################
 ######## New
 ################################
 
@@ -565,7 +563,7 @@ class StickyExpectationSV:
         ## SMM moments     
         FE_sim = np.mean(FEs_sim)
         FEVar_sim = np.var(FEs_sim)
-        FEATV_sim = np.cov(np.stack( (FEs_sim[1:],FEs_sim[:-1]),axis = 0 ))[0,1]
+        FEATV_sim = np.cov(np.stack( (FEs_sim[1:],FEs_sim[:-1]),axis = 0))[0,1]
         Disg_sim = np.mean(Disgs_sim)
         DisgVar_sim = np.var(Disgs_sim)
         DisgATV_sim = np.cov(np.stack( (Disgs_sim[1:],Disgs_sim[:-1]),axis = 0))[0,1]
@@ -580,6 +578,46 @@ class StickyExpectationSV:
[…]

### 2020-03-31 workingfolder/python/GMMEstSV_dev.py

@@ -552,7 +552,7 @@ RE_instance = RationalExpectationSV(real_time = xx_real_time_dct,
 SE_para_default = {'lambda':0.3}
 
 
-# + {"code_folding": [2, 23, 45, 79, 115, 163, 228, 249, 274, 303, 337, 359, 371, 387, 404, 416, 418, 453]}
+# + {"code_folding": [0, 2, 23, 45, 79, 115, 163, 228, 249, 274, 303, 337, 359, 371, 387, 404, 416, 418, 423, 453]}
 ## Sticky Expectation(SE) class 
 class StickyExpectationSV:
     def __init__(self,
@@ -1073,7 +1073,7 @@ class StickyExpectationSV:
 # + {"code_folding": []}
 #SE_instance.ForecastPlotDiag()
 
-# + {"code_folding": [3, 25, 43, 60, 71, 144, 189, 228, 258, 280, 307, 333, 353, 358, 368, 383, 395, 404, 457]}
+# + {"code_folding": [3, 25, 43, 60, 71, 144, 189, 228, 258, 280, 307, 333, 353, 358, 368, 383, 395, 457]}
 ## Noisy Information(NI) class 
 
 class NoisyInformationSV:
@@ -1479,6 +1479,7 @@ class NoisyInformationSV:
     ## diagostic plots 
     
     def ForecastPlotDiag(self,
+                         how = 'GMMs',
                          all_moms = False,
                          diff_scale = False):
         

### 2020-04-02 paper/InfVar.tex
drafted the codes of GMM for SE in GMM_Dev. Needed to test.
started revission drafting. finished first draft of the introduction.

@@
 %opening
-\title{Rigidity of Expectations: Additional Evidence from Density Forecasts of the Inflation by Professionals and Households}
+\title{How do agents form inflation expectations? evidences from cross-moment estimation and the uncertainty}
 \author{Tao Wang \footnote{Department of Economics, Johns Hopkins University; email: twang80@jhu.edu. }}
@@
 
-	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade.
-This has been also accompanied by a welcoming recognition of the usefulness of surveys by macroeconomists in testing these theories empirically.
+	Theories on how agents form expectations in ways deviating from rational expectations (RE) have proliferated over the past decade.
+This has been facilitated by a welcoming recognition of the usefulness of surveys by macroeconomists in testing these theories empirically.
 On one hand, various theories built upon different micro-foundations produce somewhat similar macro patterns.
@@
 On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecast.
-
-	This paper extends this line of effort by bringing an additional moment of forecasts into perspective, i.e.
+The seminal work by \cite{coibion2012can} examines predictions from different theories in a comparable manner using historical data on inflation expectations.
+The authors derive testable predictions for a variety of theory and exmains the impulse responses of the inflation expectations to different externally estimated shocks to inflation.
+
+	This paper extends the abovementioned effort by estimating each theory parametrically accounting for cross-moment restrictions.
+This is a natural step forward from reduced-form tests of rationality widely seen in the literature.
+With comparable estimates of different theories, one can evaluate to what extent each theory fits the observed expectation data and inflation dynamics.
+I evaluate each model of expectation in terms of its sensitivity of specification with respect to four criteria (1) what moments are used for estimation.
+(2) the specification of the underlying process of the inflation.
+(3)  if estimating the underlying process and expectations separately or jointly.
+The former basicaly assumes recovers the inflation process only based on inflation data while the later let the expectations to provide information used for inflation estimation as well.
+(4) if it accounts for households and forecasters' expectations equally well.
+Broadly speaking, this framework is closer to the original spirit of rational expectation in the sense it focuses on the consistency of the model specification instead of the absolute rationality.
+
+	This is not the first research that estimates theory using cross-moment restrictions (For instance, \cite{giacomini2020heterogeneity}).
+But one novel aspect of this paper lies in utilizing an additional moment of forecasts in estimation, i.e.
 the uncertainty.
-Existing work that studies expectation formation utilizing survey data mostly focus on the individual and cross-sectional patterns of the mean forecast of the variable.
-But there are additional insights from the forecast uncertainty, which is only available if each surveyee is asked to assign their own perceived probabilities to a range of values of the variable\footnote{For a survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.
-See \citet{manski2018survey} for the recent development of the discussion.}.
+Existing work that studies expectation formation utilizing survey data mostly focuses on the individual and cross-sectional patterns of the mean forecast of the variable.
+But there are additional insights from the forecast uncertainty, which is only available if each surveyee is asked to assign their own perceived probabilities to a range of values of the variable.
 For instance, the dispersion of uncertainty across individual forecasters, as that of the average forecasts, are inconsistent with the benchmark full-information rational expectation as the latter assumes that agents agree on the generating process of the data and have the common knowledge of available information.
@@
 Besides, the relationship between uncertainty with other moments such as forecast errors and disagreements provides a way to check if the surveyed expectations are consistent with certain theories of expectation formation.
-Using these insights, the paper finds additional evidence from uncertainty consistent with the rigidity models.
-In the same time, the degree of rigidity appears to be shock-specific and bears the difference between households and professional forecasters.
-
-	There are three major contributions of this paper.
-On the theoretical side, I explicitly derive the prediction of various theories of expectation formation about the dynamics of uncertainty.
+In addition, although some theories have similar qualitative predictions about the forecasting moments, the configurations of the model parameters consistent with the theory may not be empirically realistic.
+
+	With the framework of estimation presented above, this paper evaluates three workhorse theories on expectation formation.
+(1) Sticky expectation (SE).
+(2) Noisy information (NI).
+(3) Diagnostic expectations (DE).
+One major distinction between the first two and DE is that the former predict underreaction due to rigidity and the latter predicts overreaction.
+The distinction between SE and NI subtly depends on the quantitative realism of the data implied parameters.
+
+	The findings from the paper are the following.
+	Overall, sticky expectation (SE) augmented with inflation of stochastic volatility (SV) fits the joint dynamics of inflation expectation and inflations better than other theories, for both households and professionals.
+	Three theories perform indistinguishably well in matching dynamics of forecast errors but differ in matching dynamics of disagreement and uncertainty. 
+	All of the three theories' parameter estimates are not particularly sensitive to the use of moments in estimation. 
+	Both SE and DE perform well in that the parameter estimate is not sensitive to if allowing for expectation data to be used to estimate the inflation process itself.
+In contrast, the NI coefficient estimate changes substantially if the process of inflation is jointly done, particularly for households.
+	In terms of sensitivity to the specification of the inflation process, SE and DE have done a relatively good job for professionals but less consistent for households.
+NI estimates are very sensitive to the assumption about the inflation process.
+	Compared to professional forecasters, households show a limited degree of consistency within many theories.
+This evidence of inconsistency adds to the evidence rejecting full-information-rationality based on reduced-form tests.
+
+	Because this paper adds uncertainty to the moments used for estimation, another contribution of this paper is that I derive explicitly prediction of various theories of expectation formation about the dynamics of uncertainty.
 For instance, different theories that entail rigidities in incorporating new information predict the inefficiency in forecast revisions.
@@
 This imposes additional restrictions on parametric configurations that produce the degree of rigidity seen in the data.
-Specifically, I find that the configurations of parameters in sticky expectation models are more realistic than that in noisy information theories.
-
-	On the empirical side, the contribution is that we provide additional tests of the null of full-information rational expectation using the revision of uncertainty.
+
+	On the empirical side, besides structural estimation, I also provide additional tests of the null of full-information rational expectation using the revision of uncertainty.
 I first replicate the results of tests based on forecast errors using microdata of households and professionals following the existing literature.
-Then, I undertake autoregression-based tests for revisions in mean forecasts and uncertainty, respectively.
+Then, I undertake autoregression- based tests for revisions in mean forecasts and uncertainty, respectively.
 The new result from this paper is that the revision in uncertainty has a serial correlation that is not consistent with the level of forecast efficiency predicted by rational expectation.
@@
 This can be directly compared with the predictions of the theories.
-I follow the framework by \citet{coibion2012can} while making two variations.
+I follow the framework by \cite{coibion2012can} while making two variations.
 First, I do not only examine the dynamics of forecast error, disagreement, but also the forecast uncertainty.
 Second, I include two monetary policy shocks, the shocks to current federal fund rates and future path of the federal funds rate.
-
+	Related literature
+
+	\subsection{Related Literature}
 	This paper is related to four strands of literature.
@@
 In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics, cognitive abilities and macroeconomic histories experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic} and \citet{d2019iq}, etc.).
-In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.
+In terms of the methodology, this paper is closest to \cite{giacomini2020heterogeneity}, which estimates theories of expectation formation using cross-moments restrictions.
 However, all of these studies simply rely upon point forecasts instead of density forecast or surveyed uncertainty.
@@
 Section \ref{Conclusion} concludes the paper and discusses the plan for the next step.
+
+	%%%%%%%%%%%%%%%%%
 
@@
 	\begin{eqnarray}\label{NoPastInfFE}
-		\overline{FE}^{*}_{i,t+h|t} = - \sum^{h}_{k=1} \rho^k \omega_{t+k}
+		\overline{FE}^{*}_{i,t+h|t} = - \sum^{h-1}_{k=0} \rho^k \omega_{t+h-k}
 	\end{eqnarray}
@@
 		\begin{aligned}
-			\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} 
+			\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'{(H \Sigma^y_{i,t-1} H' +\Sigma^v)}^{-1} H \Sigma^y_{i,t|t-1} 
 		\end{aligned}
@@
 	\begin{eqnarray}\label{VarNIRv}
-		\Sigma^y_{i,t|t} - \Sigma^y_{i,t|t-1} = - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} <0
+		\Sigma^y_{i,t|t} - \Sigma^y_{i,t|t-1} = - \Sigma^y_{i,t|t-1} H'{(H \Sigma^y_{i,t-1} H' +\Sigma^v)}^{-1} H \Sigma^y_{i,t|t-1} <0
 	\end{eqnarray}

### 2020-04-02 slides/ExpSlides.tex
started revission drafting. finished first draft of the introduction.

@@
 \usepackage{subcaption}
+\usepackage{verbatim}
+
 %\usetheme{AnnArbor}
@@
 \begin{frame}{Scoring card for a theory of expectation formation}
-	To look if the parameter and fitness is relatively robust to 
+	To look if the parameter and goodness of fit is robust to 
 	\begin{enumerate}
 		\item use of different moments in estimation
-		\item alternative assumption about underlying process 
+		\item alternative assumption about the underlying process 
 		\item two-step estimation or joint-estimation 
@@
 
+\begin{comment}
 %%%%%%%%%%%%%%%%%%%
@@
 
+\end{comment}
+
 \subsection{Stocastic volatility}
@@
 
+\begin{frame}{Taking stock}
+	\begin{table}[]
+		\caption{A scoring card of different theory} 
+		\begin{tabular}{llll}
+				\hline 
+			Criteria                                    & SE     & NI  & DE     \\
+				\hline 
+			Sensitive to moments used for estimation?   & No     & No  & No     \\
+			Sensitive to the assumed inflation process? & No     & Yes & No     \\
+			Sensitive to a two-step or joint estimate?  & No     & Yes & No     \\
+			Sensitive to the type of agents?            & Yes    & Yes & Yes    \\
+			Matching with FE                            & Yes    & Yes & Yes    \\
+			Matching with disagreement                  & Yes    & No  & Unsure \\
+			Matching with uncertainty                   & Unsure & No  & No    \\
+			\hline 
+		\end{tabular}
+	\end{table}
+
+\end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\begin{itemize}
-		\item Sticky expectation (SE) matches data of inflation and expectations better compared to noisy information (NI) 
-		\item Within each model,  households are more irrational compared to professionals
+		\item Sticky expectation (SE) augmented with stochastic volatility of inflation process matches data of inflation and expectations better than other theories for both professionals and households.
+		\item Within each model,  households are more inconsistent  compared to professionals
 		\item Incorporating higher moments, i.e. uncertainty,  helps ``discipline'' theories on expectation formation

### 2020-04-09 paper/InfVar.tex
started revision. 1. added sv to the theory section. 2. need to finish DE section. 3. Need to add parameter estimate and scoring card section. 4. what is the best way to present the tables.

@@
 In baseline case, I make such an assumption, in general it may not be true.
-\footnote{For example, \citet{justiniano2008time}, \citet{vavra2013inflation} on time-varying volatility of inflation.}
+In the later section, I make the alternative assumptions of the inflation process allowing for  stochastic volatility.\footnote{For example, \citet{justiniano2008time}, \citet{vavra2013inflation} on time-varying volatility of inflation.}
 
@@
 		\item Population disagreements increase in response to new shocks and return to steady-state level gradually. 
-		\item Population average uncertainty revision under-reacts volatility of the shocks.
+		\item Population average uncertainty revision under-reacts to the volatility of the shocks.
 	\end{itemize}
@@
 
-	\subsection{Comparing FIRE, SE, and NI}
+	\subsection{Diagnostic Expectations (DE)}
+
+	Different from the previous two theories, diagnostic expectation (\cite{bordalo2018diagnostic}) is developed in the literature to account for extrapolative expectation formation that features overreactions to news.
+Both SE and NI deviate from FIRE in terms of the information set available to the agents, while DE deviates from FIRE in terms of the process of the otherwise perfect information set.
+
+	\subsection{Comparing Different Theories}
 
@@
 While in SE, the uncertainty does come from the lagged update of information, which involve uncertainties about all the shocks that are not yet updated in agents' information set.
+
+	\subsection{Stochastic volatility model of inflation}
+
+	This section considers an alternative inflation process for which the volatility of shocks to the inflation are stochastic.
+In particular, assume that the inflation has unobserved permanent and transitory components.
+
+	\begin{eqnarray}
+	\begin{split}
+	& y_t = \tau_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
+	& \tau_t = \tau_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
+	& \log\sigma^2_{\eta,t} = \log\sigma^2_{\eta,t-1} + \mu_{\eta,t} \\
+	& \log\sigma^2_{\epsilon,t} = \log\sigma^2_{\epsilon,t-1} + \mu_{\epsilon,t} 
+	\end{split}
+	\end{eqnarray}
+
+	The distributions of shocks to levels of the components and their volatilities are, respectively, the following.
+
+	\begin{eqnarray}
+	\begin{split}
+	& \xi_t =[\xi_{\eta,t},\xi_{\epsilon,t}] \sim N(0,I_2) \\
+	& \mu_{t} = [\mu_{\eta,t},\mu_{\epsilon,t}]' \sim N(0,\gamma I_2) 
+	\end{split}
+	\end{eqnarray}
+
+	The only parameter of the model is $\gamma$, which determines the time-varying volatilities.
+
+	Consider the rational expectation as the benchmark, again.
+At the point of time $t$, the RE agent sees the realization of all stochastic variables above with subscript $t$, $t-1$, etc, including $y_t$, $\tau_t$, $\eta_t$, $\sigma_{\eta,t}$, $\sigma_{\epsilon,t}$ and their realizations in the whose past.
+Again, $*$ stands for FIRE benchmark.
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline y^*_{t+h|t} \equiv y^*_{t+h|i,t} & =  E^*_{i,t}(y_{t+h}|I_{i,t}) = \theta_t 
+	\end{split}
+	\end{eqnarray}
+
+	Forecast error is simply the cumulated sum of unrealized shocks from $t$ to $t+h$, which is
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline{FE}^*_{t+h|t} \equiv  FE^*_{t+h|i,t} & =  \sum^{h}_{s=1} (\eta_{t+s} + \epsilon_{t+s})
+	\end{split}
+	\end{eqnarray}
+
+	h-step-ahead conditional variance, namely the uncertainty is
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline{Var}^*_{t+h|t} \equiv  Var^*_{t+h|i,t} & = \sum^{h}_{k=1} E_{i,t}(\sigma^2_{\eta,t+k}) +  E_{i,t}(\sigma^2_{\epsilon,t+k})  \\
+	& = \sum^{h}_{k=1} E_{i,t}(exp^{\log \sigma^2_{\eta,t}+\sum^h_{k=1}\mu_{\eta,t+k}}) +  E_{i,t}(exp^{\log \sigma^2_{\epsilon,t}+\sum^h_{f=1}\mu_{\epsilon,t+f}} ) \\
+	& = \sum^{h}_{k=1}\sigma^2_{\eta,t} E_{i,t}(exp^{\sum^h_{k=1}\mu_{t+h,\eta}}) +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{f=1}\mu_{\epsilon,t+f}} ) \\
+	& = \sum^{h}_{k=1}\sigma^2_{\eta,t}  exp^{E_{i,t}({\sum^h_{k=1}\mu_{t+k,\eta}})- 0.5Var_{i,t}(\sum^h_{k=1}\mu_{t+k,\eta})} +  \sigma^2_{\epsilon,t} E_{i,t}(exp^{\sum^h_{f=1}\mu_{\epsilon,t+f}} ) \\
+	& = \sigma^2_{\eta,t} \sum^{h}_{k=1} exp^{- 0.5k\gamma_{\eta}} +  \sigma^2_{\epsilon,t} exp^{- 0.5h\gamma_{\epsilon}} 
+	\end{split} 
+	\end{eqnarray}
+
+	One could immediately see that now the volatility is stochastic at any point of the time.
+
+	For instance, set $h=1$, the conditional volatility for the 1-step-ahead inflation is
+
+	\begin{eqnarray}
+	\begin{split}
+	Var^*_{t+1|i,t} =  exp^{- 0.5\gamma_{\eta}} \sigma^2_{\eta,t}  +  exp^{- 0.5\gamma_{\epsilon}} \sigma^2_{\epsilon,t} 
+	\end{split} 
+	\end{eqnarray}
+
+	Disgreement is zero across agents in RE.
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline{Disg}^*_{t+h|t} =  0 
+	\end{split} 
+	\end{eqnarray}
+
+	Under the sticky expectation (SE), an agent whose most recent up-do-date update happened at $t-\tau$, thus she sees all the realizations of stochastic variables up to $t-\tau$, including $y_{t-\tau}$, $\tau_{t-\tau}$, $\eta_{t-\tau}$, $\sigma_{\eta,t-\tau}$, $\sigma_{\epsilon,t-\tau}$.
+
+	Her forecast is the permanent component that realized at time $t-\tau$.
+
+	\begin{eqnarray}
+	\begin{split}
+	y_{t+h|i,t-\tau}  = \theta_{t-\tau} 
+	\end{split}
+	\end{eqnarray}
+
+	Her forecast uncertainty is
+
+	\begin{eqnarray}
+	\begin{split}
+	Var_{t+h|i,t-\tau} & = \sigma^2_{\eta,t-\tau} \sum^{h+\tau}_{k=1} exp^{- 0.5k\gamma_{\eta}} +  \sigma^2_{\epsilon,t-\tau} exp^{- 0.5(h+\tau)\gamma_{\epsilon}}
+	\end{split} 
+	\end{eqnarray}
+
+	The population average of the two are, respectively, a weighted average of people whose the most update was in $t, t-1... t-\tau, t-\infty$, respectively.
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline y^{se}_{t+h|t} & = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda y_{t+h|t-\tau} \\
+	& = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda \theta_{t-\tau}
+	\end{split} 
+	\end{eqnarray}
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline {Var}^{se}_{t+h|t} & = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda Var_{t+h|t-\tau} \\
+	& = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda [ \sigma^2_{\eta,t-\tau} \sum^{h+\tau}_{k=1} exp^{- 0.5k\gamma_{\eta}} +  \sigma^2_{\epsilon,t-\tau} exp^{- 0.5(h+\tau)\gamma_{\epsilon}}]
+	\end{split} 
+	\end{eqnarray}
+
+	Both forecast errors $\overline{FE}_{t+h|t}$ and disagreements takes similar form to that in AR process with time-invariant volatility.
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline {FE}^{se}_{t+h|t} & = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda {FE}^*_{t+h|t-\tau} 
+	& = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda \sum^{\tau+h}_{s=1} (\theta_{t+s} + \epsilon_{t+s})  
+	\end{split} 
+	\end{eqnarray}
+
+	The disagreement is the following.
+
+	\begin{eqnarray}
+	\begin{split}
+	\overline{Disg}^{se}_{t+h|t} & =  \sum^{\infty}_{\tau=0} (1-\lambda)^{2\tau} \lambda^2 (y_{t+h|t-\tau} - \overline y^{se}_{t+h|t})^2  \\
+	& = \sum^{\infty}_{\tau=0} (1-\lambda)^{2\tau} \lambda^2 (\theta_{t-\tau} - \overline y^{se}_{t+h|t})^2  \\
+	& = \sum^{\infty}_{\tau=0} (1-\lambda)^{2\tau} \lambda^2 \{\theta_{t-\tau} - \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda \theta_{t-\tau}\}^2  
+	\end{split} 
+	\end{eqnarray}
+
+	Under nosiy information (NI), the agent at time $t$ needs to recover the real-time permanent component $\theta_t$ to make the best forecast for future $y_{t+h}$ using nosiy signals.
+
+	\begin{eqnarray}
+	y^{ni}_{t+h|t}  \equiv  y^{ni}_{t+h|i,t} = \bar \theta_{t|t}
+	\end{eqnarray}
+
+	where $\bar \theta_{t|t}$ is generated through Kalman filtering.
+
+	Assume that the nosiy signals of $\theta_t$ consists of a public signals $s^{pb}_{t}$ and the private signals $s^{pr}_{i,t}$.
+For simplicity, let us assume the public signal is basically the $y_t$.
+A more general case would be an independently drawn public signal sequence.
+The two signals can be again stacked into a vector of $2\times 1$ to $s^\theta_{i,t}$.
+
+	Then the filterred $\theta_{t}$ by agent $i$ is
+
+	\begin{eqnarray}
+	\begin{split}
+	\bar \theta_{t|t} =  (1-\tilde P_{t} H) \bar \theta_{t|t-1} + \tilde P s^\theta_{i,t} \\
+	\end{split}
+	\end{eqnarray}
+
+	where $\theta_{t|t-k}$ is the filterred forecast of $\theta_t$ using all the information up to $t-k$., and $\tilde Pt$ is the time-specific Kalman gain that is dependent on the noisy ratios of signals.
+
+	\begin{eqnarray}
+	\begin{split}
+	\tilde P_{t} =  \Sigma^\theta_{i,t|t-1} H(H'\Sigma^\theta_{i,t|t-1} H + \Sigma^\theta_{t})^{-1} 
+	\end{split}
+	\end{eqnarray}
+
+	Now the noisiness of signals are time varying as well.
+
+	\begin{eqnarray}
+	\begin{split}
+	\Sigma^\theta_t =  \left[ \begin{matrix} 
+	\sigma^2_{\eta,t} &  0 \\ 
+	0 & \sigma^2_\xi \end{matrix}\right] 
+	\end{split}               
+	\end{eqnarray}
+
+	where the variance of public signal is the time-varying $\sigma^2_{\eta,t}$ and let us assume the private signals have constant nosiness $\sigma^2_{\xi}$.
+
+	The uncertainty matrix evolves in the following manner.
+
+	\begin{eqnarray}
+	\Sigma^\theta_{i,t|t} = \Sigma^\theta_{i,t|t-1} - \Sigma^\theta_{i,t|t-1} H'(H \Sigma^\theta_{i,t-1} H' +\Sigma^\theta_{t}) H \Sigma^\theta_{i,t|t-1} 
+	\end{eqnarray}
+
+	Notice now that since prior of $\theta_t$ before time period $t$ is a weighted average of previous realizations of $y$ and past signals, current forecast depends on the past realizations even though the rational forecast is up-to-date $\theta_t$.
+
+	Due to the time-varying volatility $\sigma^2_{\eta,t}$, the noisyness of the public signal is also time-varying, which governs the degree of rigidity.
+For instance, if volatility to the transitory shock is high, the Kalman gain is low, the forecast responds less to the new realizations.
+
+	It is also worth thinking about what is the one-step ahead uncertainty in the context of stochastic valotility world.
+
+	\begin{eqnarray}
+	\begin{split}
+	\Sigma^\theta_{i,t|t-1} & = \Sigma^\theta_{i,t-1|t-1} + Var^*_{t|t-1}(y_t) \\
+	& = \Sigma^\theta_{i,t-1|t-1} +  exp^{- 0.5\gamma_{\eta}} \sigma^2_{\eta,t-1}  +  exp^{- 0.5\gamma_{\epsilon}} \sigma^2_{\epsilon,t-1} 
+	\end{split}
+	\end{eqnarray}
 
@@
 
-	\subsection{Discussion of the results and next step}
+	\subsection{Discussion of the results}
 
@@
 
-	\section{Conclusion}\label{Conclusion}
-
+	\section{Simulated Method of Moments Estimation of different models}
+
+	For a given process of inflation and a particular theory of expectation formation, the GMM estimate of the vector of parameters $\Omega$ is defined as the following.
+
+	\begin{eqnarray*}
+		\widehat \Omega = \underset{\{\Omega \in \Gamma\} }{argmin} (M_{\textrm{data} } - F^{o}(\Omega, Y)) W  (M_{\textrm{data} } - F^{o}(\Omega, Y))'
+	\end{eqnarray*}
+
+	\begin{itemize}
+		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni},{de},{seni} \} \times \{ar, sv\}$
+		\item  $\Gamma$: constraints for the parameter. 
+		\item $M_{data}$: data moments
+		\item $F$: simulated model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up till each point of the time $t$.
+		\begin{itemize}
+			\item unconditional moments, not specific to time
+			\item moments selected from average forecast, variance and autocovariance of forecasts, average diagreement, variance and autovariance of disagreement, average uncertainty, etc. 
+		\end{itemize}
+		\item  $W$: weight matrix, identity matrix for now 
+	\end{itemize}
+
+The estimation procedure is as followed.
+
+	\begin{enumerate}
+	\item for each theory of expectation formation and the inflation process, start with an initial value for the parameter(s) of interest
+	\item simulate individual forecasts for a large enough ($N=200$) number of forecasters
+	\item compute the average forecast errors, disagreement and average uncertainty across all agents
+	\item compute the time-series moments of the average forecast, disagreement, and uncertainty
+	\item compute the difference between the simulated moments and the data moments 
+	\item keep searching the parameter value until reaching below a threshold of the loss
+\end{enumerate}
+
+We evaluate a particular theory of expectation formation based on following four sensitivity criteria: if the parameter and goodness of fit is robust to 
+\begin{enumerate}
+	\item use of different moments in estimation
+	\item alternative assumption about the underlying process 
+	\item two-step estimation or joint-estimation 
+	\item relatively fit with professionals and households  
+\end{enumerate}
+
+\subsection{Moments matching and parameter estimates}
+
+\subsection{The scoring card of different theories}
+
+\section{Conlusion}	
 	In summary, three major conclusions can be drawn from this paper.

### 2020-04-10 paper/InfVar.tex
finished the short draft of DE theory.

@@
 With comparable estimates of different theories, one can evaluate to what extent each theory fits the observed expectation data and inflation dynamics.
-I evaluate each model of expectation in terms of its sensitivity of specification with respect to four criteria (1) what moments are used for estimation.
-(2) the specification of the underlying process of the inflation.
-(3)  if estimating the underlying process and expectations separately or jointly.
-The former basicaly assumes recovers the inflation process only based on inflation data while the later let the expectations to provide information used for inflation estimation as well.
-(4) if it accounts for households and forecasters' expectations equally well.
-Broadly speaking, this framework is closer to the original spirit of rational expectation in the sense it focuses on the consistency of the model specification instead of the absolute rationality.
+I evaluate each model of expectation in terms of its sensitivity of the parameter estimates with respect to four criteria (1) what moments are used for estimation; (2) the specification of the underlying process of the inflation; (3)  if estimating the underlying process and expectations separately or jointly.
+The former basicaly recovers the inflation process only based on inflation data while the later let the expectations to provide information in estimating the inflation process.
+(4) If it accounts for households and forecasters' expectations equally well.
+Broadly speaking, this framework is closer to the essence of the rational expectation assumption in the sense that it focuses on the consistency of the model specification instead of the absolute rationality.
 
@@
 the uncertainty.
-Existing work that studies expectation formation utilizing survey data mostly focuses on the individual and cross-sectional patterns of the mean forecast of the variable.
+Existing work that studies expectation formation utilizing survey data mostly focuses on the individual and cross-sectional patterns of the mean forecast and forecast errors.
 But there are additional insights from the forecast uncertainty, which is only available if each surveyee is asked to assign their own perceived probabilities to a range of values of the variable.
@@
 One major distinction between the first two and DE is that the former predict underreaction due to rigidity and the latter predicts overreaction.
-The distinction between SE and NI subtly depends on the quantitative realism of the data implied parameters.
+The distinction between SE and NI subtly depends on the quantitative realism of the data-implied parameters.
 
@@
 
-	Different from the previous two theories, diagnostic expectation (\cite{bordalo2018diagnostic}) is developed in the literature to account for extrapolative expectation formation that features overreactions to news.
-Both SE and NI deviate from FIRE in terms of the information set available to the agents, while DE deviates from FIRE in terms of the process of the otherwise perfect information set.
+	Different from the previous two theories, diagnostic expectation (\cite{bordalo2018diagnostic}) is developed in the literature to account for extrapolative expectations that feature overreactions to the news.
+Both SE and NI deviate from FIRE in terms of the information set available to the agents, while DE deviates from FIRE in terms of the processing of an otherwise fully updated information set.
+
+Omitting the micro foundation, the following equation captures the essence of DE's mechanism.
+Each individual $i$'s h-period-ahead forecast consists of two components.
+The first component can be considered as a rational forecast based on the fully updated $y_t$.
+The second component corresponds to the potential overreaction to the unexpected shock to inflation at time t, i.e.
+the forecast error.
+The degree of overreaction is governed by the parameter $\theta$.
+The premise of DE models is that $\theta \geq 0$.
+The forecast collapses to the FIRE when $\theta = 0$.
+Any $\theta>0$ implies cases in which the agent revises her forecast overly to the realized forecast error in the same direction.
+
+ while since agents extrapolates whatever is considered 
+		\begin{eqnarray}
+		\begin{aligned}
+			\bar y_{i,t+h|t}  =  \rho^h y_{t} + \theta_i (\rho^h y_t - \bar y_{i,t+h|t-1})
+		\end{aligned}
+	\end{eqnarray}
+
+	 I allow $\theta$ to be different across different agents, therefore, I add the subscript $i$ to the parameter.
+Since agents are equally informed about the realizations of the variable, the only room for disagreement to rise is either difference in the initial information set or the degree of overreaction differs across people.
+To capture this, I assume $\theta_i$ to follow a normal distribution across the population with a variance of $\sigma_{\epsilon}$.
+It will be estimated along with $\theta$.
+
+	 Finally as to the uncertainty, since the mechanism of extrapolation in DE does not change the agent's perceived distribution of the future shocks, benchmark DE theory predicts the forecast uncertainty to remain the same as the rational expectation.
 
@@
 
-	For a given process of inflation and a particular theory of expectation formation, the GMM estimate of the vector of parameters $\Omega$ is defined as the following.
+	For a given process of inflation and a particular theory of expectation formation, the SMM estimate of the vector of parameters $\Omega$ is defined as the following.
 
@@
 	\begin{itemize}
-		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni},{de},{seni} \} \times \{ar, sv\}$
+		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni},{de} \} \times \{ar, sv\}$
 		\item  $\Gamma$: constraints for the parameter. 

### 2020-04-12 paper/InfVar.tex
a rough draft before the submission to Oxford Phd macro.

@@
 Also, motivated by the time-varying pattern of the uncertainty observed from surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility.
-These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness.
-It also illustrates how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.
+These extensions allow me to match the joint dynamics of inflation and forecast moments in better goodness of fit.
+It also testifies how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.
 	\end{abstract}
@@
 
-	\begin{table}[ht]
+	\begin{table}[p]
 		\centering
@@
 
-	\begin{figure}[ht]
+	\begin{figure}[p]
 		\centering
@@
 
-	\begin{table}[ht]
+	\begin{table}[p]
 		\caption{Information of Data}
@@
 
-	\begin{figure}[ht]
+	\begin{figure}[p]
 		\begin{subfigure}[b]{0.5\textwidth}
@@
 
-	\begin{table}[ht]
+	\begin{table}[p]
 		\caption{Tests of Rationality and Efficiency Using Forecast Errors}
@@
 
-		\begin{sidewaystable}[ht]
+		\begin{sidewaystable}[p]
 			\begin{adjustbox}{width={24cm},totalheight={14cm}}
@@
 
-	\begin{sidewaystable}[ht]
+	\begin{sidewaystable}[p]
 		\begin{adjustbox}{width={24cm},totalheight={14cm}}
@@
 
-\begin{figure}[ht]
+\begin{figure}[p]
 	\begin{subfigure}[b]{0.5\textwidth}
@@
 
-		\begin{figure}[ht]
+		\begin{figure}[p]
 		\begin{subfigure}[b]{0.5\textwidth}
@@
 
-	\begin{figure}[ht]
+	\begin{figure}[p]
 
@@
 
-\subsection{Moments matching and parameter estimates}
-
-\subsection{The scoring card of different theories}
+\subsection{Moments matching and parameter estimates (draft in process)}
+
+Table \ref{SMM_Est_SPF} presents the SMM estimates of different model parameters.
+For each theory, I estimate the theory both in two-steps or jointly using expectation and inflation data.
+Different rows without each panel reports the estimates by using different sets of moments:forecast errors only,  forecast error and disagreement, and the two plus uncertainty.
+
+\begin{table}[p]
+	\caption{SMM Estimates of Different Models: Professionals}
+	\label{SMM_Est_SPF}
+	\begin{tabular}{lllllll}
+		\hline 
+		\multicolumn{7}{c}{SE}                            \\
+		\hline 
+		Moments Used & \multicolumn{1}{c}{2-Step Estimate} & \multicolumn{3}{c}{Joint Estimate}                                                 &            &              \\
+			\hline 
+		& SE: $\hat\lambda_{SPF}$(Q)          & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$                & SE: $\sigma$              &            &              \\
+			\hline 
+		FE       & 0.47                                & 0.36                       & 1                         & 0.08                      &            &              \\
+		FE+Disg      & 0.47                                & 0.38                       & 1                         & 0.1                       &            &              \\
+		FE+Disg+Var  & 0.47                                & 0.36                       & 1                         & 0.08                      &            &              \\
+			\hline 
+		\multicolumn{7}{c}{NI}                                                                                                                                              \\
+			\hline 
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                              & \multicolumn{4}{c}{Joint Estimate}              
+		                                  \\
+		                                  	\hline 
+		& NI: $\hat\sigma_{pb,SPF}$           & $\hat\sigma_{pr,SPF}$      & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$     & NI: $\rho$ & NI: $\sigma$ \\
+			\hline 
+		FE        & 0.09                                & 2.77                       & 0.093                     & 1.408                     & 0.911      & 0.422        \\
+		FE+Disg      & 0.09                                & 2.77                       & 0.093                     & 1.408                     & 0.911      & 0.422        \\
+		FE+Disg+Var  & 0.14                                & 3.85                       & 0.133                     & 1.359                     & 0.911      & 0.422        \\
+			\hline 
+		\multicolumn{7}{c}{DE}                                                                                                                                              \\
+			\hline 
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                              & \multicolumn{4}{c}{Joint Estimate}                                                \\
+			\hline 
+		& DE: $\theta_{SPF}$                  & DE: $\sigma_{\theta,SPF}$  & DE: $\theta_{SPF}$        & DE: $\sigma_{\theta,SPF}$ & DE: $\rho$ & DE: $\sigma$ \\
+			\hline 
+		FE       & -0.23                               & 0.22                       & NA                        & NA                        & NA         & NA           \\
+		FE+Disg      & -0.26                               & 1.41                       & -0.14                     & 1.44                      & 0.99       & 0.16         \\
+		FE+Disg+Var  & -0.24                               & 1.43                       & -0.17                     & 1.44                      & 0.99       & 0.16       \\ 
+			\hline 
+	\end{tabular}
+\end{table}
+
+\begin{table}[p]
+	\caption{SMM Estimates of Different Models: Households}
+	\label{SMM_Est_SCE}
+	\begin{tabular}{lllllll}
+		\hline 
+		\multicolumn{7}{c}{SE}                                                               
+		                                                      \\
+		                                          \hline 
+		Moments Used & 2-Step Estimate            & \multicolumn{3}{c}{Joint Estimate}                                                 &            &              \\
+		\hline 
+		& SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$                & SE: $\sigma$              &            &              \\
+			\hline   
+		FE        & 0.2                        & 0.5                        & 0.84                      & 0.25                      &            &              \\
+		FE+Disg      & 0.21                       & 0.54                       & 0.92                      & 0.18                      &            &              \\
+		FE+Disg+Var  & 0.21                       & 0.5                        & 0.84                      & 0.25                      &            &              \\
+			\hline   
+		\multicolumn{7}{c}{NI}                                                                                                                                   \\
+			\hline   
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                     & \multicolumn{4}{c}{Joint Estimate}                                                \\
+		\hline 
+		& NI: $\hat\sigma_{pb,SPF}$  & $\hat\sigma_{pr,SPF}$      & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$     & NI: $\rho$ & NI: $\sigma$ \\
+		\hline 
+		FE        & 3.4                        & 15.4                       & 3.397                     & 15.395                    & 0.997      & 0.027        \\
+		FE+Disg      & 3.4                        & 15.4                       & 3.397                     & 15.395                    & 0.997      & 0.027        \\
+		FE+Disg+Var  & 4.9                        & 22.4                       & 4.860                     & 22.367                    & 0.997      & 0.027        \\
+		\hline 
+		\multicolumn{7}{c}{DE}                                                                                                                                     \\
+		\hline 
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                     & \multicolumn{4}{c}{Joint Estimate}                                                \\
+		\hline 
+		& DE: $\theta_{SPF}$         & DE: $\sigma_{\theta,SPF}$  & DE: $\theta_{SPF}$        & DE: $\sigma_{\theta,SPF}$ & DE: $\rho$ & DE: $\sigma$ \\
+		\hline 
+		FE       & 9.35                       & 10.65                      & 0.82                      & 0.85                      & 1          & 0            \\
+		FE+Disg      & 8.2                        & 9.52                       & 4.79                      & 4.59                      & 0.58       & 0.55         \\
+		FE+Disg+Var  & 4.78                       & 3.01                       & NA                        & NA                        & NA         & NA          \\
+		\hline 
+	\end{tabular}
+\end{table}
+
+\begin{table}[p]
+		\centering
+		\caption{SMM Estimates of Different Models under Stocastic Volatility: Professionals}
+	\label{SMM_Est_sv_SPF}
+	\begin{tabular}{llllll}
+			\hline 
+		\multicolumn{6}{c}{SE}                                                                                                                         \\
+			\hline 
+		Moments Used & \multicolumn{1}{c}{2-Step Estimate} & \multicolumn{2}{c}{Joint Estimate}                     &                       &          \\
+			\hline 
+		& SE: $\hat\lambda_{SPF}$(Q)          & SE: $\hat\lambda_{SPF}$(Q) & SE: $\gamma$              &                       &          \\
+			\hline 
+		FE        & 0.3                                 & 0.46                       & 2.52                      &                       &          \\
+		FE+Disg      & 0.3                                 & 0.46                       & 2.53                      &                       &          \\
+		FE+Disg+Var  & 0.3                                 & 0.46                       & 1.26                      &                       &          \\
+			\hline 
+		\multicolumn{6}{c}{NI}                                                                                                                         \\
+			\hline 
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                              & \multicolumn{3}{l}{Joint Estimate}                           \\
+			\hline 
+		& NI: $\hat\sigma_{pb,SPF}$           & $\hat\sigma_{pr,SPF}$      & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $\gamma$ \\
+			\hline 
+		FE       & 2.35                                & 2                          & 2.04                      & 23.01                 & 2.53     \\
+		FE+Disg      & 37475663924                         & 4.8                        & 70269682.39               & 10.18                 & -2.91    \\
+		FE+Disg+Var  & 3.33                                & 1.71                       & 2.04                      & 22.96                 & 2.53     \\
+			\hline 
+		\multicolumn{6}{c}{DE}                                                                                                                         \\
+			\hline 
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                              & \multicolumn{3}{c}{Joint Estimate}                           \\
+		& DE: $\theta$                        & $\sigma_\theta$            & DE: $\theta$              & $\sigma_\theta$       & $\gamma$ \\
+			\hline 
+		FE        & -0.44                               & 0.36                       & -0.43                     & 1.03                  & 0.13     \\
+		FE+Disg      & -0.44                               & 0.27                       & -0.44                     & -0.27                 & 0.3      \\
+		FE+Disg+Var  & -0.43                               & 0.26                       & -0.43                     & 0.26                  & 0.14    \\
+		\hline 
+	\end{tabular}
+\end{table}
+
+\begin{table}[p]
+		\centering
+		\caption{SMM Estimates of Different Models under Stocastic Volatility: Households}
+	\label{SMM_Est_sv_SCE}
+	\begin{tabular}{llllll}
+			\hline 
+		\multicolumn{6}{c}{SE}         \\
+			\hline            
+		Moments Used & 2-Step Estimate            & \multicolumn{2}{c}{Joint Estimate}                     &                       &          \\
+			\hline 
+		& SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\gamma$      
+		        &                       &          \\
+		        	\hline 
+		FE           & 0.09                       & 0.09                       & 0.7                       &                       &          \\
+		FE+Disg      & 0.07                       & 0.07                       & 0.26                      &                       &          \\
+		FE+Disg+Var  & 0.07                       & 0.07                       & 0.26                      &                       &          \\
+			\hline 
+		\multicolumn{6}{c}{NI}                                                                                                                \\
+			\hline 
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                     & \multicolumn{3}{c}{Joint Estimate}                           \\
+			\hline 
+		& NI: $\hat\sigma_{pb,SPF}$  & $\hat\sigma_{pr,SPF}$      & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $\gamma$ \\
+			\hline 
+		FE           & NA                         & NA                         & NA                        & NA                    & NA       \\
+		FE+Disg      & NA                         & NA                         & NA                        & NA                    & NA       \\
+		FE+Disg+Var  & NA                         & NA                         & NA                        & NA                    & NA       \\
+			\hline 
+		\multicolumn{6}{l}{DE}                                                                                                                \\
+			\hline 
+		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                     & \multicolumn{3}{c}{Joint Estimate}                           \\
+			\hline 
+		& DE: $\theta$               & $\sigma_\theta$            & DE: $\theta$              & $\sigma_\theta$       & $\gamma$ \\
+			\hline 
+		FE           & 7.81                       & 4.39                       & 7.81                      & 2.99                  & 0.7      \\
+		FE+Disg      & 7.64                       & 6.46                       & 7.64                      & 6.46                  & 0.7      \\
+		FE+Disg+Var  & 1.03                       & 0                          & 1.03                      & 0                     & 0.2     \\
+		\hline 
+	\end{tabular}
+\end{table}
+
+\subsection{The scoring card of different theories (draft in process)}}
+
+Table \ref{scoringcard} presents the evaluation of the three theories based on its sensitivity of goodnedss of fit and parameter estimate with respect to four criteria.
+Based on the evaluation, sticky expectation seems to capture the average behavior of expectations better than the other two theories.
+Diagnostic expectation shows similar degree of performance according to these criteria, but the average estimation does not show overreaction in lign with the premise of the theory.
+
+	\begin{table}[p]
+	\caption{A scoring card of different theory} 
+	\label{scoringcard}
+	\centering
+	\begin{tabular}{llll}
+		\hline 
+		Criteria                                    & SE     & NI  & DE     \\
+		\hline 
+		Sensitive to moments used for estimation?   & No     & No  & No     \\
+		Sensitive to the assumed inflation process? & No     & Yes & No     \\
+		Sensitive to a two-step or joint estimate?  & No     & Yes & No     \\
+		Sensitive to the type of agents?            & Yes    & Yes & Yes    \\
+		Matching with FE                            & Yes    & Yes & Yes    \\
+		Matching with disagreement                  & Yes    & No  & Unsure \\
+		Matching with uncertainty                   & Unsure & No  & No    \\
+		\hline 
+	\end{tabular}
+\end{table}
 
@@
 
-	So far, the dynamics of moments are separately estimated for each moment.
-Therefore, as a natural extension of the current analysis, one can undertake a generalized method of moment (GMM) estimation that simultaneously utilizes multi-moment restrictions to recover a better estimate of the rigidity parameters.
-This will provide a better parameter that can be used in structural macro models that build in the rigidity of expectations.
+	Finally, the cross-moment estimation developed by this paper jointly accounting for the moments predictions provides a unified framework of evaluating different theories.
+The estimation suggest that among all combined theory of expectation formation and inflation process, sticky expectation (SE) augmented with stochastic volatility of inflation process matches data of inflation and expectations better than other theories for both professionals and households.
+The exercise also shows that incorporating higher moments, i.e.
+uncertainty,  helps ``discipline'' theories on expectation formation.
+Besides, higher moments from surveys also contain useful information about the inflation dynamics itself
 

### 2020-08-20 paper/InfVar.tex
moved out the literature folder.

@@
 
-	Different from the previous two theories, diagnostic expectation (\cite{bordalo2018diagnostic}) is developed in the literature to account for extrapolative expectations that feature overreactions to the news.
+	Different from the previous two theories, diagnostic expectation (\cite{bordalo2018diagnostic}) is developed in the literature to account for extrapolative expectations that feature overreactions to the news  (\cite{bordalo2018over}).
 Both SE and NI deviate from FIRE in terms of the information set available to the agents, while DE deviates from FIRE in terms of the processing of an otherwise fully updated information set.
@@
 
- while since agents extrapolates whatever is considered 
 		\begin{eqnarray}
@@
 To capture this, I assume $\theta_i$ to follow a normal distribution across the population with a variance of $\sigma_{\epsilon}$.
-It will be estimated along with $\theta$.
+It will be estimated along with $\theta_i$.
 
@@
 Table \ref{SMM_Est_SPF} presents the SMM estimates of different model parameters.
-For each theory, I estimate the theory both in two-steps or jointly using expectation and inflation data.
-Different rows without each panel reports the estimates by using different sets of moments:forecast errors only,  forecast error and disagreement, and the two plus uncertainty.
+For each theory, I estimate the theory both in two steps or jointly using expectations and inflation data.
+Different rows within each panel reports the estimates depending on various choices of moments used for estimation: forecast errors only,  forecast error and disagreement, and the two plus uncertainty.
 
@@
 
-\subsection{The scoring card of different theories (draft in process)}}
-
-Table \ref{scoringcard} presents the evaluation of the three theories based on its sensitivity of goodnedss of fit and parameter estimate with respect to four criteria.
-Based on the evaluation, sticky expectation seems to capture the average behavior of expectations better than the other two theories.
+\subsection{The scoring card of different theories (draft in process)}
+
+Table \ref{scoringcard} reports my evaluation of the three theories based on four sensitivity criteria we discussed in the previous section.
+According to this evaluation, the sticky expectation seems to capture the average behavior of expectations better than the other two theories.
 Diagnostic expectation shows similar degree of performance according to these criteria, but the average estimation does not show overreaction in lign with the premise of the theory.
@@
 	\begin{table}[p]
-	\caption{A scoring card of different theory} 
+	\caption{A scoring card of different theories} 
 	\label{scoringcard}

### 2020-08-21 workingfolder/python/DoEstimationWithData.py
small changes

@@ -26,10 +26,10 @@ import numpy as np
 from scipy.optimize import minimize
 
 import statsmodels.api as sm
-from statsmodels.tsa.api import AR
+from statsmodels.tsa.api import AutoReg as AR
 # -
 
-from GMMEst import RationalExpectation as re
+#from GMMEst import RationalExpectation as re
 from GMMEst import StickyExpectation as se
 from GMMEst import NoisyInformation as ni
 from GMMEst import ParameterLearning as pl
@@ -160,21 +160,21 @@ CPICQ = InfQ['Inf1y_CPICore'].copy().loc[start_t:end_t]
 Y = np.array(CPICQ[1:])
 X = np.array(CPICQ[:-1])
 
-ARmodel = AR(CPICQ)
-ar_rs = ARmodel.fit(1,trend='nc')
+ARmodel = AR(CPICQ,lags=1,trend='n')
+ar_rs = ARmodel.fit()
 rhoQ_est = ar_rs.params[0]
 sigmaQ_est = np.sqrt(sum(ar_rs.resid**2)/(len(CPICQ)-1))
 
 ###################
 ### monthly data ##
-####################
+###################
 
 CPIM = InfM['Inf1y_CPIAU'].copy().loc[start_t:end_t]
 Y = np.array(CPIM[1:])
 X = np.array(CPIM[:-1])
 
-ARmodel2 = AR(CPIM)
-ar_rs2 = ARmodel2.fit(1,trend='nc')
+ARmodel2 = AR(CPIM,lags=1,trend='n')
+ar_rs2 = ARmodel2.fit()
 rhoM_est = ar_rs2.params[0]
 sigmaM_est = np.sqrt(sum(ar_rs2.resid**2)/(len(CPIM)-1))
 
@@ -195,7 +195,12 @@ ed_t_SCE = SCE_est.index[-1].strftime('%Y-%m-%d')
 indexQ = CPICQ.index
 
 ## get history data quarterly and monthly respectively 
-historyQ = real_time_inf.loc[indexQ].loc[st_t_history:ed_t_SPF] ## this is monthly. wrong. 
+af = indexQ >= st_t_history 
+bf = indexQ <=ed_t_SPF
+time_filter = np.logical_and(af,bf)
+time_filter_idx = indexQ[time_filter]
+
+historyQ = real_time_inf.loc[time_filter_idx] ## this is monthly. wrong. 
 historyM = real_time_inf.loc[st_t_history:ed_t_SCE]
 
 # + {"code_folding": [0]}
[…]

### 2020-08-21 workingfolder/python/DoEstimationWithData_Dev.py

@@ -98,7 +98,7 @@ real_time_inf.tail()
 # ### 3. Estimating using real-time inflation and expectation data
 #
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## exapectation data from SPF 
 PopQ=pd.read_stata('../SurveyData/InfExpQ.dta')  
 PopQ = PopQ[-PopQ.date.isnull()]
@@ -125,7 +125,7 @@ dateQ_str2 = dateQ2.dt.year.astype(int).astype(str) + \
              "Q" + dateQ2.dt.quarter.astype(int).astype(str)
 InfQ.index = pd.DatetimeIndex(dateQ_str2,freq='infer')
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## process parameters estimation 
 # period filter 
 start_t='1995-01-01'
@@ -195,7 +195,7 @@ SCECPI = PopM[['SCE_Mean','SCE_FE','SCE_Disg','SCE_Var',
 SPF_est = pd.concat([SPFCPI,real_time_inf,InfQ['Inf1y_CPICore'],InfQ['Inf1yf_CPICore']], join='inner', axis=1)
 SCE_est = pd.concat([SCECPI,real_time_inf,InfM['Inf1yf_CPIAU']], join='inner', axis=1)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## hisotries data, the series ends at the same dates with real-time data but startes earlier 
 
 st_t_history = '2000-01-01'
@@ -204,6 +204,9 @@ ed_t_SCE = SCE_est.index[-1].strftime('%Y-%m-%d')
 
 historyQ = real_time_inf.copy().loc[st_t_history:ed_t_SPF]
 historyM = real_time_inf.loc[st_t_history:ed_t_SCE]
+# -
+
+historyQ.index
 
 # + {"code_folding": [0]}
 # How large is the difference between current vintage and real-time data
@@ -287,7 +290,7 @@ process_paraM_est = {'rho':rhoM_est,
                     'sigma':sigmaM_est}
 
 
-# +
+# + {"code_folding": [0]}
 ## function of moving average 
 def mvavg(array,
           window = 3):

### 2020-08-21 workingfolder/python/GMMEst.py

@@ -15,7 +15,7 @@
 
 # ## GMM Estimation of Model Parameters of Expectation Formation
 #
-# - This notebook includes functions that estimate the parameter of rigidity for different models
+# - This notebook includes functions that estimate the parameters of different theories
 # - It allows for flexible choices of moments to be used, forecast error, disagreement, and uncertainty, etc. 
 # - It includes 
 #   - A general function that implements the estimation using the minimum distance algorithm. 
@@ -129,21 +129,21 @@ def AR1_simulator(rho,sigma,nobs):
     return xxx[1:]
 
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## some process parameters 
 rho = 0.95
 sigma = 0.1
 process_para = {'rho':rho,
                 'sigma':sigma}
 
-# +
+# + {"code_folding": []}
 ## Rational Expectation
 
 # + {"code_folding": []}
 ## SE expectation parameters 
 SE_para_default = {'lambda':0.4}
 
-# + {"code_folding": [0, 4, 30, 43, 59, 110, 144, 180, 249, 319, 348, 377, 387, 395, 418, 441, 468, 506, 544, 576, 605, 630, 644, 671, 683, 695, 710, 725, 737, 813, 829]}
+# + {"code_folding": [3, 30, 43, 59, 110, 144, 180, 249, 319, 348, 377, 387, 395, 418, 441, 468, 506, 544, 576, 605, 630, 644, 671, 683, 695, 710, 725, 737, 813, 829]}
 ## Sticky Expectation(SE) class 
 
 
@@ -998,7 +998,7 @@ class StickyExpectation:
         self.wm_boot = np.linalg.inv(self.vcv_boot)               
 
 
-# + {"code_folding": [3, 32, 45, 59, 129, 207, 222, 234, 286, 319, 356, 389, 401, 422, 455, 484, 495, 507, 522, 550, 587, 595, 610, 626, 657, 670, 682, 694, 774, 791]}
+# + {"code_folding": [2, 3, 32, 45, 59, 129, 207, 222, 234, 286, 319, 356, 389, 401, 422, 455, 484, 495, 507, 522, 550, 587, 595, 610, 626, 657, 670, 682, 694, 774, 791]}
 ## Noisy Information(NI) class 
 
 class NoisyInformation:
[…]

### 2020-09-14 workingfolder/python/DoSMMEst.py
Drafting

@@ -26,6 +26,7 @@
 #   3.  The general function is to be used to compute the specific objective function that takes parameter as the only input for the minimizor to work
 #   4.  Then a general function that does optimization algorithm takes the specific objective function and estimates the parameters
 
+# +
 import numpy as np
 from scipy.optimize import minimize
 import matplotlib.pyplot as plt
@@ -37,6 +38,10 @@ import pandas as pd
 from statsmodels.tsa.api import AutoReg as AR
 import copy as cp
 
+pd.options.display.float_format = '{:,.2f}'.format
+
+
+# -
 
 # ## Model 
 
@@ -520,7 +525,7 @@ def np_min(array, axis):
     return np_apply_along_axis(np.min, axis, array)
 
 
-# + {"code_folding": [18]}
+# + {"code_folding": [2, 18, 81, 113]}
 @jitclass(model_data)
 class StickyExpectationAR:
     def __init__(self,
@@ -903,7 +908,20 @@ def Objsear_joint(paras):
 # ### Noisy Information (NI) + AR1
 #
 
-# + {"code_folding": [1, 2, 14, 18, 115]}
+# + {"code_folding": [1]}
+@njit
+def SteadyStateVar(process_para,
+                   exp_para):
+    ρ,σ = process_para
+    sigma_pb,sigma_pr = exp_para
+    a = ρ**2*(sigma_pb**2+sigma_pr**2)
+    b = (sigma_pb**2+sigma_pr**2)*σ**2+(1-ρ**2)*sigma_pb**2*sigma_pr**2
+    c = -σ**2*sigma_pb**2*sigma_pr**2
+    nowcast_var_ss = (-b+np.sqrt(b**2-4*a*c))/(2*a)
+    return nowcast_var_ss
+
+
+# + {"code_folding": [2, 18, 62, 117]}
 @jitclass(model_data)
 class NoisyInformationAR:
     def __init__(self,
@@ -938,7 +956,9 @@ class NoisyInformationAR:
         sigma_pb,sigma_pr = self.exp_para
 
         #######################
-        var_init = 5    ## some initial level of uncertainty, will be washed out after long simulation
+        ## using uncertainty at steady state of the Kalman filtering
+        var_init = SteadyStateVar(self.process_para,
+                                  self.exp_para)    ## some initial level of uncertainty, will be washed out after long simulation
         ##################
[…]

### 2020-09-14 workingfolder/python/DoSMMEst.py
new draft be (incomplete) from overleaf.

@@ -3207,7 +3207,7 @@ for agent_id,agent in enumerate(agents_list):
                 print(paras_joint_est)
                 paras_joint_list.append(paras_joint_est)
 
-# + {"code_folding": [0]}
+# + {"code_folding": []}
 ## create multiple index to save coefficients estimates 
 
 iterables = [agents_list, process_list, ex_model_list,moments_list_general]
@@ -3314,7 +3314,7 @@ mom_joint_compare_spf = smm_data_spf.append(smm_joint_model.loc['spf','ar'])
 mom_joint_compare_sce = smm_data_sce.append(smm_joint_model.loc['sce','ar'])
 # -
 
-mom_joint_compare_spf
+mom_compare_spf
 
 mom_joint_compare_sce
 
